### 2019-09-14 Ecol_Analysis/Manuscript_Draft.Rmd
Migrated documents to github

---
title: "Challenges to transboundary fisheries management in North America under climate change"
author: "Juliano Palacios-Abrantes^1^ U. Rashid Sumaila^1^ William W. L. Cheung^1^"
subtitle: "[THIRD DRAFT]"
date: "^1^ Institute for the Oceans and Fisheries, University of British Columbia, Vancouver, Canada"
output:
  word_document: default
  pdf_document: default
bibliography: Oceans_Canada_Biblio.bib
editor_options: 
  chunk_output_type: console
csl: harvard.csl
---

```{r setup, eval=T, echo=F, warning=F,message=F, results='hide'}

#### READ ME !!! ####
# Run this chunk before knit so you make sure you have all pkgs installed in R

ipak <- function(pkg){
  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
  if (length(new.pkg)) 
    install.packages(new.pkg, dependencies = TRUE,repos = "http://cran.us.r-project.org")
  sapply(pkg, require, character.only = TRUE)
}

#### Library ####
packages <- c(
  "readxl", # Read dataframe
  "dplyr", # Data manipulation
  "tidyr", # Data manipulation
  "ggplot2", #Nice grpahs and spatial analysis
  "cowplot",
  "rgdal",
  "RColorBrewer",
  "knitr",
  "kableExtra",
  "data.table",
  "ggrepel",
  "gridExtra",
  "ggmap",
  "rgeos",
  "sf",
  "sp",
  "rgdal", #Spatial analysis 
  "tools", #Spatial analysis 
  "png", # For reading plots in chunk codes
  "grid" # For reading plots in chunk codes
)

ipak(packages)

##________________________________________________##

# source("/Users/jpalacios/Documents/UBC/Oceans_Project/Distribution/Functions/DBEM_imp_F.R") #Imports a single species

ggtheme_plot <- function() {
  theme(
    plot.title = element_text(size = rel(1), hjust = 0, face = "bold"),
    panel.background = element_blank(),
    strip.background = element_blank(),
    # strip.text       = element_text(size = base_size, face = "italic"),
    panel.border     = element_blank(),
    panel.grid.minor = element_blank(),
    panel.grid.major = element_blank(),
    axis.ticks = element_blank(),
    axis.text.x = element_text(size = 14,
                               angle = 0,
                               face = "plain"),
    axis.text.y = element_text(size = 14),
    axis.title = element_text(size = 14),
    legend.key = element_rect(colour = NA, fill = NA),
    legend.position  = "top",
    legend.title = element_text(size = 16),
    legend.text = element_text(size = 14),
    strip.text.x = element_text(size = 10, colour = "black"),
    strip.text = element_text(size = 18)
  )
}

ggtheme_map <- function(base_size = 9, Region = "NA") {

  theme(text             = element_text(#family = "Helvetica",
    color = "gray30", size = base_size),
    plot.title       = element_text(size = rel(1.25), hjust = 0, face = "bold"),
    panel.background = element_blank(),
    panel.border     = element_blank(),
    panel.grid.minor = element_blank(),
    panel.grid.major = element_line(color = "transparent"),
    strip.background =element_rect(fill = "transparent"),
    strip.text.x = element_text(size = 18, colour = "black",face= "bold.italic", angle = 0),
    axis.line        = element_blank(), # element_line(colour = "grey30", size = .5))
    axis.ticks       = element_blank(),
    axis.text        = element_blank(),
    axis.title       = element_blank(),
    # legend.key       = element_rect(colour = NA, fill = NA, size = 4),
    legend.position = "bottom"#,
    # legend.key.width =unit(6,"line")
  )
}

  # Current time
Beg_In <- paste(2005); Beg_In
Beg_End <- paste(2014); Beg_End

# Mid century
Mid_In <- paste(2041);Mid_In # 2046
Mid_End <- paste(2060);Mid_End

# End Century
End_In <- paste(2080);End_In # 2090
End_End <- paste(2099);End_End
```

# Abstract

Climate change is shifting the distribution of fish stocks that straddle between Exclusive Economic Zones (EEZ), challenging transboundary fisheries management. In this paper, we examine the projected sharing of jointly managed transboundary fish stocks between the EEZs of Canada and the United States. We hypothesize that ocean warming will alter the sharing of fish stocks between the two countries, and that such changes will intensify under a high carbon emission scenario impacting the stock-share ratio of different stocks. Firstly, we projected changes in potential catch of 33 transboundary stocks of North America in the 21^st^ century based on multiple Earth system models’ simulations and species distribution models, under two climate change scenarios. We then look at the specific cases of the International Pacific Halibut Commission that manages pacific halibut (*Hippoglossus stenolepis*) and a resource sharing agreement in the Gulf of Maine for cod (*Gadus morhua*), haddock (*Melanogrammus aeglefinus*) and yellowtail flounder (*Limanda ferruginea*). Results show that, even under a low emission scenario, most transboundary fish stocks sharing ratios, i.e., the proportion of the total catch of a fish stock taken by a given country, will change by 2050 relative to present in the direction as expected from the effects of ocean warming. The overall reduction in catch potential, in addition to the changes in stock-share will further exacerbate trade-offs between changes in species catch potential. Such trade-offs in the Atlantic and Pacific regions will be amplified if a high emission scenario is followed, relative to a low carbon emission scenario. Our paper highlights the challenges that transboundary fisheries management will face as species shift their current distribution under a changing climate.[^Acknowledgements]

Keywords: *Transboundary fisheries management; climate change; joint fisheries management; species distribution shift*

[^Acknowledgements]: This is a product of the *OceanCanada* Partnership funded by the Social Sciences and Humanities Research Council of Canada.

# INTRODUCTION

<!-- ##### First paragraph of paper summary -->
Transboundary fisheries are defined as fish stocks that move freely between (*i*) Countries economic exclusive zones (EEZs) and (*ii*) between EEZs and the high seas (also called straddling stocks) [@Song:2017iua]. The management of transboundary stocks can be analized using game theory, as often, success depends on effective cooperation between parties [@Munro:2002uf; @Sumaila:2013hv]. Therefore, in 1985, the United Nations incentivized actions to cooperate on the management of transboundary fisheries through the Law of the Seas (UNCLOS) [@UnitedNations:1986tl]. Today, an estimated 347 [@Teh:2015gd] to 1500 [@Caddy:1997ue] fish stocks cross national borders, some of them jointly managed by two or more countries. These stocks are responsible for almost 50% of these countries total fish catches [@Teh:2015gd]. Transboundary stocks such as salmon (*Oncorhynchus spp.*), Pacific halibut (*Hippoglossus stenolepis*), and Atlantic cod (*Gadus morhua*) are of utmost importance for Canada and the United States (US). Management of these stocks is extremely hard due to the participation of several fishing “players”, different countries and sometimes jurisdictions within a country, the migration patterns of the stock, and their abundance fluctuation within space and time [@Munro:2002uf].

<!-- ##### Climate Change and Transboundary Fisheries -->

The ocean is getting warmer [@Rheim:2013fv], less oxygenated [@Schmidtko:2017cl], and increasing in acidity [@Ross:2011kd]. To cope with these changes in ocean biophysic properties, marine species, including transboundary fish stocks, have been shifting their distribution towards the poles and/or deeper waters [@Poloczanska:2016kk]. As climate change reshapes the ocean's environment worldwide [@Gattuso:2015jz], transboundary fisheries' delicate governance is threatened as new migration patterns may arise [@Miller:2013iv; @Pinsky:2018cb], historic distribution and abundances might shift [@Cheung:2010dt], and species basic natural traits may modify [@Pauly:2017hpa]. Catches of shared stocks like tropical tunas, have significantly increased in subtropical regions of the Atlantic and western Pacific Oceans [@MonllorHurtado:2017cm]. Multiple transboundary species in North America have been observed to shift in distribution following changes in optimal conditions such as sockeye salmon (*Oncorhynchus nerka*) [@McDaniels:2010vn], Atlantic cod [@Pershing:2015gq], and flounders [@Pinsky:2012kq]. Moreover, these shifts are projected to continue towards the end of the 21^st^ century [@Cheung:2018hz] at a rate of tens to hundreds of km and/or tens of meters per decade towards the poles and/or deeper waters, respectively, although there will be regional variations [@Morley:2018fn]. As a result, some countries or management jurisdictions may see more transboundary stocks and their catches shifting into their waters while others will stand to lose [@Miller:2013iv; @Pinsky:2018cb]. Nevertheless, management rules for shared stocks (e.g. quota or spatial delimitation) are often determined based on current and historic knowledge of the stock's distribution and do not consider future shifts in distributions [@FredstonHermann:2018kp]. In addition, many international treaties do not directly consider climate change in their management scheme, despite evidence of target species shifting their distribution.

<!-- ##### Past Conflicts of shifting stocks -->

The shifts in distribution of transboundary fish stocks would impact the economics of their fisheries [@Lam:2016dy; @Pinsky:2012kq; @Sumaila:2011bq, @Sumaila:2019gh], and create international disputes in the sharing of fish stocks between nation's EEZs [@Munro:2002uf; @Spijkers:2017ij]. As climate change alters the sharing of fish stocks between countries to an extent that is beyond historical changes, existing policies and governance structures may not be able to cope with these changes. Consequently, countries may not be satisfied with the sharing or allocation of access to resources, leading to international disputes [@Pinsky:2018cb]. Disputes over Pacific salmon between Canada and the US arose in the 1990s because of climate-related changes in stock abundance and migratory behavior [@Miller:2013iv; @Munro:2002uf; @Song:2017va]. Currently, Europe is involved in an unsolved dispute over *Scomber scombrus* known as the "mackerel wars". The conflict erupted in 2007 when the stock shifted their distribution from the Norwegian Sea towards northern and western regions of the Nordic Seas, consequently spreading into Iceland's national waters [@Spijkers:2017ij].

<!-- ##### Bring it home, treaties between CA/US -->

Transboundary fisheries between Canada and the US offer a unique lens to understand the extent to which climate-induced distributional shifts will challenge the future sustainability of these fisheries. Canada and the US have a long history of fisheries cooperation [@Song:2017va]. They participate in diverse, jointly managed, commercial transboundary stocks through various fisheries management organizations [@Merten:2015tu]. Cooperation schemes vary by fisheries stocks, regulatory areas, legal terms of agreement, and management measures, among others (Fig. 1). In the Atlantic coast, Canada and the US are part of the Northwest Atlantic Fisheries Organization (NAFO) that oversees the management of 19 stocks of 11 transboundary species (although around 41 taxa are fished within Canadian and US waters) from southern Gulf of Maine to Greenland[^NAFO]. Within NAFO's region 5Z, Canada and the US have a "Resource Sharing Understanding" (hereafter referred to "GoM agreement") to set catch-limits of Atlantic cod (*Gadus morhua*), haddock (*Melanogrammus aeglefinus*) and, yellowtail flounder (*Limanda ferruginea*) [@Soboil:2006gw; @CIA:2017uta]. In the Pacific coast, Pacific halibut (*Hippoglossus stenolepis*) is managed under the International Pacific Halibut Commission (IPHC) [@IPHCSecreatriat:2017uz]. All five salmon species (chinook, *Oncorhynchus tshawytscha*; chum, *O. keta*; coho, *O. kisutch*; pink, *O. gorbuscha*; and sockeye *O. nerka*), are managed by the Pacific Salmon Commission [@PSC:2017tb]. Finally, under the Pacific Whiting Treaty, Canada and the United states jointly manage the coastal stock of this Pacific hake species (*Merluccius productus*) [@Merten:2015tu].

[^NAFO]: Northwest Atlantic Fisheries Organization, Available at https://www.nafo.int/Science/Species

```{r Study_Area_Map, eval = F, echo = F, warning=F, message=F}

Countries <- c("Canada","United States")

### North America Initial Map ####

path_world <- "~/Documents/Github/Oceana_LA/international/information/raw_databases/Spatial/TM_WORLD_BORDERS-0.3"
file_name <- "TM_WORLD_BORDERS"

World_Land_sf <- st_read(dsn = path_world, 
layer = file_path_sans_ext(file_name)
) %>% 
st_transform(crs = 3832)

# names(World_Land_sf)

North_America_Land <- World_Land_sf %>% 
filter(NAME %in% Countries) %>% 
st_transform(crs = 3832)

# head(North_America)

# ggplot(North_America_Land) +
#   geom_sf() +
#   coord_sf(ylim = c(3051701,11528813)
#   )

### North America EEZs Map ####

path_eez <- ("/Users/jpalacios/Documents/R CODE/Spatial_Analysis/Data/World_EEZ_v10_2018")
#The File
fnam_eez <- "eez_v10.shp"

eez_world_sf <- st_read(dsn = path_eez, 
                        layer = file_path_sans_ext(fnam_eez)
) %>% 
  st_transform(crs = 3832)

Nort_America_EEZ <- eez_world_sf %>% 
filter(Territory1 %in% Countries)

# Testing
ggplot(Nort_America_EEZ) +
geom_sf()

# Testing together

ggplot(North_America_Land) +
  geom_sf() +
  geom_sf(data = Nort_America_EEZ, colour = "black") +
  coord_sf(ylim = c(3051701,11528813)
  )

#### IPHC Regulatory Areas ####

path_IPHC <- ("/Users/jpalacios/Documents/UBC/Oceans_Project/Distribution/Data/IPHC/IPHC_RegulatoryAreas/")

# The Canada file
fnam_IPHC_C <- "IPHC_RegulatoryAreas_CAN"

IPHC_Reg_C <- st_read(dsn = path_IPHC, 
                      layer = file_path_sans_ext(fnam_IPHC_C)
) %>% 
  select(
    ID,
    Country = COUNTRY,
    State = PROV_EN,
    RegArea
  ) %>% 
  mutate(Comments = "NA") %>% 
  st_transform(crs = 3832)

# 4326 use this to merge with DBEM data
# 3832 use this to center the map and plot

# ggplot(IPHC_Reg_C) +
# geom_sf()

# The US File
fnam_IPHC_US <- "IPHC_RegulatoryAreas_US"

IPHC_Reg_US <- st_read(dsn = path_IPHC,
                       layer = file_path_sans_ext(fnam_IPHC_US)
) %>%
  st_transform(crs = 3832)

# head(IPHC_Reg_US)
ggplot(IPHC_Reg_US) +
  geom_sf()

### Combine both shapefiles

IPHC_Reg <- rbind(IPHC_Reg_US,IPHC_Reg_C)

ggplot(IPHC_Reg) +
  geom_sf()

##### NAFO Regulatory Area ####

path_NAFO <- ("/Users/jpalacios/Documents/UBC/Oceans_Project/Distribution/Data/Spatial/NAFO")
#The File
fnam_NAFO <- "Divisions"

NAFO_Area <- st_read(dsn = path_NAFO,
                     layer =file_path_sans_ext(fnam_NAFO))%>% 
  st_transform(crs = 3832)

Zones <- c(
  "5Ze",
  # "5Zw",
  "5Y",
  "4X"
)

NAFO_5z <- NAFO_Area %>% 
filter(ZONE %in% Zones)

# head(NAFO_5z)

ggplot() +
geom_sf(data = North_America_Land,
        fill = "lightgrey",
        colour = "black") +
  ggtheme_map()

#### The final Map ####

# Homonize collors 
brewer.pal(name="Set2",5)

# Canada "#grey80"
# US "#grey40", 
# NAFO "#66CC99"
# IPHC #f01282

#North America point of view

North_A <- ggplot() +
  geom_sf(data = North_America_Land, 
          aes(fill = NAME),
          colour = "black"
  ) +
  geom_sf(data = IPHC_Reg, 
          aes(fill = "IPHC") ,
          colour = "black"
  ) +
  geom_sf(data = NAFO_5z, 
          aes(fill = "NAFO"),
          colour = "black"
  ) +
  ggtheme_map() +
  scale_fill_manual("Region",
                    breaks = c("Canada","IPHC","NAFO", "United States"), 
                    values=c("grey80","#CC6666","#66CC99","grey40")
                    ) +
  theme(legend.position = "right")

Path_Save <- "/Users/jpalacios/Documents/UBC/Oceans_Project/Manuscript/Results/Others/"

ggsave("Fig1_NA.png",
       plot = North_A,
       width = 6,
       height = 5,
       units = "in",
       path = Path_Save)

#NAFO #

NAFO <- ggplot() +
  geom_sf(data = NAFO_5z, #NAFO regions
          aes(fill = "NAFO"),
          colour = "black"
  )+
  geom_sf_label(data = NAFO_5z, # RegAreas labels
                aes(
                  label = ZONE#,
                  # fill = "NAFO"
                ),
                alpha = 0.5
  ) +
  geom_sf(data = North_America_Land, # North America Land
          aes(fill=NAME),
          colour = "black"
  ) +
  coord_sf(ylim = c(5951701,4728813),
           xlim = c(15373019,16573019)
  ) +
  # scale_fill_brewer("Region",palette = "Set2") +
  theme(
    panel.background = element_blank(),
    panel.border     = element_blank(),
    panel.grid.minor = element_blank(),
    panel.grid.major = element_line(color = "transparent"),
    legend.position = "bottom",
    axis.title = element_blank()
  ) +
  scale_fill_manual("Region",breaks = c("Canada", "NAFO", "United States"), 
                    # values = c("#E78AC3","#A6D854","8DA0CB")
                    values=c("grey80", "#66CC99", "grey40")
                    ); NAFO

# Save plot for manuscrip
ggsave("Fig1_NAFO.png",
       plot = NAFO,
       width = 6,
       height = 5,
       units = "in",
       path = Path_Save)

# IPHC

IPHC_Reg$RegArea <- gsub("Closed Area","CA",IPHC_Reg$RegArea)

IPHC <- ggplot() +
  geom_sf(data = IPHC_Reg,
          aes(fill = "IPHC"),
          colour = "black"
  ) + 
  geom_sf(data = North_America_Land, # North America Land
          aes(fill=NAME),
          colour = "black"
  ) +
  geom_sf_label(data = IPHC_Reg, # RegAreas labels
                aes(
                  label = RegArea#,
                  # fill = Percentage
                ),
                alpha = 0.5
  ) +

  coord_sf(xlim = c(1963800, 10041910), # Subsets north america
           ylim = c(3651701,9728813)
  ) +
  theme(
    panel.background = element_blank(),
    panel.border     = element_blank(),
    panel.grid.minor = element_blank(),
    panel.grid.major = element_line(color = "transparent"),
    legend.position = "bottom",
    axis.title = element_blank()
  ) +
  scale_fill_manual("Region",breaks = c("Canada", "IPHC", "United States"), 
                    values=c("grey80", "#CC6666", "grey40")
                    )

# Save plot for manuscrip
ggsave("Fig1_IPHC.png",
       plot = IPHC,
       width = 6,
       height = 5,
       units = "in",
       path = Path_Save)

```

![Fig 1. Map of North America with the regulatory areas of the IPHC and the NAFO sub-region related to the Gulf of Main agreement](./Results/Fig1.png)

It is expected that climate induced shifts in stock distribution affect the rules in place that keeps these treaties alive. Therefore, the main objective of this paper is to assess the level of exposure of international fisheries management treaties between Canada and the US to climate change impacts through shifts in stock distributions. Specifically, we rely on a species distribution model and scenario planning to project the changes in the distribution of 33 fish stocks jointly managed by Canada and the US. Moreover, we use two specific treaties as case studies (IPHC and the GoM agreement) to explore the potential impacts that climate change will have on selected transboundary fisheries management. Finally, we explore similar situations around the world and identify opportunities to improve the adaptability of transboundary fisheries management to climate change in North America. Despite an overall expectation of species following a poleward shift, important geographic features (e.g. Gulf of Alaska representing a latitudinal block), geo-political (e.g. the localization of Alaska in reference to Canada and the contiguous states), and management rules (e.g. quota allocations, spatial management rules) may play an important role in the redistribution of benefits. Understanding these stocks shifts will shed a light on future conditions and inform decision makers on the paths to follow under a changing climate.

# METHODS

#### Study Area and Fisheries

The current study focuses on transboundary fisheries jointly managed by Canada and the US for both the Atlantic and the Pacific coasts. The analysis was carried out within the 200 nautical miles of both nation's EEZ from the Gulf of Mexico to The Labrador Sea in the Atlantic, and from California to Chukchi Sea, in the Pacific coast (Fig. 1). Subsets of the total area were carried for both the IPHC and the Gulf of Maine agreement. For the IPHC, we used the most updated spatial regulatory data provided by the Commission [@IPHCSecreatriat:2017uz]. For this specific case, we considered Alaska as a separate entity, the US contiguous states as a second one (Washington, Oregon and California), and lastly British Columbia (Canada). For the GoM agreement we used NAFO's divisions 5Y, 5Ze, and 4X within latitudes 46.2°N and 41.5°S, and longitudes -72°W and -64°E (Fig. 1).

```{r Spatial_data, eval = T, echo = F, warning=F, message=F, results = 'hide'}

# List of DBEM INDEX within the EEZ
#Data provided by Vicki Lam
EEZIDs_List <- read_excel("~/Documents/UBC/Oceans_Project/Distribution/By Cell/Cell_Data/Updated_EEZList_17June2016.xlsx")
EEZ_CellID <- read_excel("~/Documents/UBC/Oceans_Project/Distribution/By Cell/Cell_Data/EEZ_CellID.xlsx")

colnames(EEZ_CellID) <- c("EEZID","INDEX")

# DBEM Coordinate system
Coor <- fread("~/Documents/UBC/Oceans_Project/Distribution/DBEM/Data/Lon_Lat_DBEM.txt",header = FALSE)
colnames(Coor) <- c("INDEX","Longitude","Latitude")

### Select EEZs
EEZs <- c(
  "Canada (Pacific)",
  "Canada (Arctic)",
  "USA (West Coast)",
  "USA (Alaska, Arctic)",
  "USA (Alaska, Subarctic)",
  "Canada (Arctic)",
  "Canada (East Coast)",
  "USA (East Coast)"
)

### North America Initial Map ####

path_world <- "~/Documents/UBC/Oceans_Project/Manuscript/Data/Spatial_Data/TM_WORLD_BORDERS"
file_name <- "TM_WORLD_BORDERS"

World_Land_sf <- st_read(dsn = path_world, 
                         layer = file_path_sans_ext(file_name)
) %>% 
  st_transform(crs = 4326)

# names(World_Land_sf)

North_America_Land <- World_Land_sf %>% 
  filter(NAME %in% c("Canada","United States")) %>% 
  st_transform(crs = 3832) # 4326 use this to merge with DBEM data
# 3832 use this to center the map and plot

#### _____________________TEST _____________________ #
# head(North_America_Land)
# ggplot(North_America_Land) +
#   geom_sf() +
#   coord_sf(xlim = c(-120, -179),
#            ylim = c(30,70)
#   )
##__________________________________________ #

### North America EEZs Map ####

path_eez <- ("~/Documents/UBC/Oceans_Project/Manuscript/Data/Spatial_Data/World_EEZ_v10_2018")
#The File
fnam_eez <- "eez_v10.shp"

eez_world_sf <- st_read(dsn = path_eez, 
layer = file_path_sans_ext(fnam_eez)
) %>% 
st_transform(crs = 4326)# 4326 use this to merge with DBEM data
# 3832 use this to center the map and plot

#### _____________________TEST _____________________ #
# head(eez_world_sf)
### Test this map
# ggplot(ezz_North_America) +
#   geom_sf()
##__________________________________________##

#### IPHC Regulatory areas ####

## Correct DBEM for Alaska ####
IHPC_EEZs <- c(
  "Canada (Pacific)",
  # "Canada (Arctic)"
  "USA (West Coast)",
  "USA (Alaska, Arctic)",
  "USA (Alaska, Subarctic)"#,
  # "Russia (Far East)"
)

IPHC_EEZsID <- EEZIDs_List %>% 
  filter(Name %in%IHPC_EEZs) %>% 
  left_join(EEZ_CellID,
            by = "EEZID") %>% 
  left_join(Coor,
            by = "INDEX")

# "Move" the map so results are not in the other side of the world and it matches the projection I want
IPHC_Coor_Corrected <- IPHC_EEZsID %>% 
  filter(Longitude > 0) %>% 
  mutate(Longitude = Longitude-360)

IPHC_Coor_Corrected <- IPHC_EEZsID %>% 
  filter(Longitude < 0) %>% 
  bind_rows(IPHC_Coor_Corrected) %>% 
  filter(Latitude > 25)

# Create new column to merge with shapefiles

IPHC_Coor_Corrected_Clean <- IPHC_Coor_Corrected %>% 
  mutate(
    State = ifelse(Name == "Canada (Pacific)", "British Columbia",
                   ifelse(Name == "USA (West Coast)","WAORCA","Alaska"))
  ) %>% 
  select(
    # State,
    INDEX,
    longitude = Longitude,
    latitude = Latitude)

# Now we load IPHC shapefiles ####
path_IPHC <- ("~/Documents/UBC/Oceans_Project/Distribution/Data/IPHC/IPHC_RegulatoryAreas/")

# The Canada file
fnam_IPHC_C <- "IPHC_RegulatoryAreas_CAN"

IPHC_Reg_C <- st_read(dsn = path_IPHC, 
                      layer = file_path_sans_ext(fnam_IPHC_C)
) %>% 
  select(
    ID,
    Country = COUNTRY,
    State = PROV_EN,
    RegArea
  ) %>% 
  mutate(Comments = "NA") %>% 
  st_transform(crs = 4326)

# 4326 use this to merge with DBEM data
# 3832 use this to center the map and plot

#### _____________________TEST _____________________##
# head(IPHC_Reg_C)
# ggplot(IPHC_Reg_C) +
# geom_sf()
##_________________________________________________##
# The US File
fnam_IPHC_US <- "IPHC_RegulatoryAreas_US"

IPHC_Reg_US <- st_read(dsn = path_IPHC, 
                       layer = file_path_sans_ext(fnam_IPHC_US)
) %>% 
  st_transform(crs = 4326)

#### _____________________TEST _____________________ #
# head(IPHC_Reg_US)
# ggplot(IPHC_Reg_US) +
#   geom_sf()
##_________________________________________________##

### Combine both shapefiles

IPHC_Reg <- rbind(IPHC_Reg_US,IPHC_Reg_C)

#### _____________________TEST _____________________ #
# head(IPHC_Reg,12)
# tail(IPHC_Reg)
# unique(IPHC_Reg$State)

# It's going to take a while... 
# ggplot(IPHC_Reg) +
#   geom_sf()
##_________________________________________________##

# Now join the Shapefile with the DBEM lat/long dataset

# Convert DBEM to sf
IPHC_Coor_sf = st_as_sf(IPHC_Coor_Corrected_Clean,
                        coords = c("longitude", "latitude")) %>% 
  st_set_crs(4326) %>% # to match shapefiles
  st_transform(4326) # to match shapefiles

# head(IPHC_Coor_sf)

# Merge DBEM sf to polygons
IPHC_Reg_DBEM <- st_join(IPHC_Reg,
                         IPHC_Coor_sf, join = st_contains) %>% 
  filter(!is.na(INDEX)) %>%
  arrange(INDEX) 
# %>% 
#   st_transform(3832) # Go back to original projection otherwise doesnt like to plot

IPHC_Reg_DBEM_df <- as.data.frame(IPHC_Reg_DBEM) %>% 
  select(INDEX,RegArea)

#### _____________________TEST _____________________ #
# head(IPHC_Reg_DBEM_df)
# IPHC_Reg_DBEM_df %>% 
#   arrange(INDEX) %>% 
# head()
##_________________________________________________##

### STOP 
## Go to the results and now estimate the %change by region using IPHC_Reg_DBEM_df then, convert it to sf and merge it with IPHC_Reg

# Gulf of Maine ####
#### NAFO data ####

path_NAFO <- ("~/Documents/UBC/Oceans_Project/Distribution/Data/Spatial/NAFO/")
#The File
fnam_NAFO <- "Divisions"

NAFO_Area <- st_read(dsn = path_NAFO,
layer =file_path_sans_ext(fnam_NAFO))

Zones <- c(
  "5Ze",
  # "5Zw",
  "5Y",
  "4X"
)

NAFO_5z <- NAFO_Area %>% 
filter(ZONE %in% Zones)

#### _____________________TEST _____________________ #
# head(NAFO_5z)

# ggplot(NAFO_5z) +
# geom_sf()
# geom_sf(aes (fill = ZONE))
##_________________________________________________##

### Atlantic EEZ polygon (I don't think we need this for now) ####

Atlantic_EEZs <- c(
  "Canada (Arctic)",
  "Canada (East Coast)",
  "USA (East Coast)"
)

Atlantic_EEZsID <- EEZIDs_List %>%
  filter(Name %in% Atlantic_EEZs) %>%
  left_join(EEZ_CellID,
            by = "EEZID") %>%
  left_join(Coor,
            by = "INDEX")

### Atlantic DBEM Data ####

GB_Coor <- Coor %>% 
  filter(INDEX %in% Atlantic_EEZsID$INDEX) %>% 
  mutate(one = 1)

# Atlantic Land polygon ####

Countries <- c(
  "Canada",
  "United States"
)

### EEZ GM ####
eez_GM <- eez_world_sf %>% 
  filter(Territory1 %in% Countries)

#### _____________________TEST _____________________ #
# ggplot() +
#   geom_sf(data = eez_GM) +
#   coord_sf(xlim = c(-71.0592, -63.33333),
#            ylim = c(40.5,45.9759)
#            )
##_________________________________________________##

GM_Land <- World_Land_sf %>% 
  filter(NAME %in% Countries)

```

The species analyzed (**Table A2.1**) were selected based on five treaties in both the Atlantic and Pacific coast of North America (Table 1). All species under the IPHC, PSC, WT, and the GoM agreement were analyzed as these treaties are management agreements between Canada and the US. However, in the case of NAFO, their management covers over 41 taxa and its governance extends to international waters and the EEZ of Greenland. Therefore, a subset of 26 species reported was made based on those fished in NAFO regions that fall within the EEZs of Canada and the US (NAFO subareas 2's, 3's with the exception of 3M and 3N and limited to the EEZ, 4's,5's and 6 A,B, and C.) [@NAFO]. Data related to fisheries was gathered from the *Sea Around Us* from 1951 to 2014 [@Zeller2016].

```{r Treaties_Table, eval = T, echo = F}

# Foot note
fn <- "*These species are also part of NAFO"

data.table::data.table(Treaty =
                         c("International Pacific Halibut Coomission (IPHC)",
                           "Pacific Salmon Coomission (PSC)",
                           "Pacific Whiting Treaty (PWT)",
                           "Northwest Atlantic Fisheries Organization (NAFO)",
                           "Gulf of Main's Agreement (GoM Agreement)"),
                       Species =
                         c(1,
                           5,
                           1,
                           26,
                           "3*"),
                       Coast =
                         c("Pacific",
                           "Pacific",
                           "Pacific",
                           "Atlantic",
                           "Atlantic")
) %>% 
  kable("latex",
        caption = "Treaties and number of species included in the current analysis."
        ) %>% 
  add_footnote(fn)
```

#### Projecting Future Species Distribution

We used a Dynamic Bioclimatic Envelope Model (DBEM) to project the distribution of species from 2015 to 2100, under two scenarios of climate change [@Cheung:2016hf; @Cheung:2016jd]. The DBEM algorithm integrated ecophysiology, habitat suitability with spatial population dynamics of exploited fishes and invertebrates to project shifts in abundance, and potential fisheries catches  under climate change. The algorithm predicted species distribution based on depth range, latitudinal range, habitat preferences and an index of species association with major habitat types to estimate changes in abundance distribution over a 0.5' x 0.5' grid of the world oceans. For each grid cell and time step, the model then calculated species carrying capacity according to sea surface temperature, salinity, oxygen content, sea ice extent (for polar species) and bathymetry, as well as the species preferences to these conditions. It then incorporated the intrinsic population growth, settled larvae, and net migration of adults from surrounding cells using an advection-diffusion-reaction equation. Finally, the model also simulated the effects of changes in temperature and oxygen content on growth of individuals [@Cheung:2013gk]. Ultimately, the model simulates spatial and temporal population dynamics, and estimates a proxy of maximum sustainable yield (MSY) by applying fishing at MSY level for each grid cell, hereafter referred as maximum catch potential (MCP).

The DBEM was projected using three earth system models (ESM), the Geophysical Fluid Dynamics Laboratory Earth System Models 2M (GFDL)[^GFDL], the Institute Pierre Simon Laplace Climate Model 5 (IPSL-CM5)[^IPSL], and the Max Planck Institute for Meteorology Earth System Model (MPI)[^MPI]. Each model was downscaled to match the DBEM 0.5' x 0.5' grid using the nearest neighbor method, and in some cases, bilinear interpolation [@Cheung:2016hf]. Finally, we used the model outputs for two scenarios of the Intergovernmental Panel on Climate Change (IPPC)-Representative Concentration Pathways (RCP); 2.6 (RCP 2.6) and 8.5 (RCP 8.5) representing a low greenhouse gas emission (strong mitigation) and a high greenhouse gas emission (business-as-usual) scenario, respectively [@IPCC:2014bz]. To estimate model robustness and capture the structural uncertanty build within ESM models we averaged the DBEM results for all three models ($\mu±\sigma$) and marked regions where at least one ESM disagree with the rest.

[^GFDL]: More information related to the Geophysical Fluid Dynamics Laboratory Earth System Models 2M can be found at www.gfdl.noaa.gov
[^IPSL]: More information related to the Institute Pierre Simon Laplace Climate Model 5 can be found at www.icmc.ipsl.fr/
[^MPI]: More information related to the Max Planck Institute for Meteorology Earth System Model can be found at www.mpimet.mpg.de/en/science/models/

```{r Data_Loading_For_DBEM, eval = F, echo = F, warning = F ,message = F}

# Species data (Names, treaties, etc)
# DBEM exploited species list 
exploited_species_list <- fread("/Volumes/DATA/PROJECTION exploited species ENM/exploited_species_list.csv")

# IPHC and GB species
Selected_Species <- fread("~/Documents/UBC/Oceans_Project/Distribution/By Cell/Cell_Data/List_Species.csv")

# NAFO Species
# This is the subset of species Fished on canada and US waters of all NAFO's species list
NAFO_Species <- read.csv("~/Documents/UBC/Oceans_Project/Distribution/DBEM/Data/NAFO_Species.csv") %>%
  mutate(Treaty = "NAFO")

```

```{r DBEM_Data_For_All, eval = F, echo = F, warning = F, message = F}

All_Species <- exploited_species_list %>% 
  # filter(TaxonName  %in% c("Hippoglossus stenolepis","Anoplopoma fimbria")) %>% 
  filter(TaxonName %in% NAFO_Species$TaxonName) %>%
  mutate(Treaty = "NAFO") %>% 
  bind_rows(Selected_Species) %>% 
  filter(! duplicated(TaxonName)) %>% # Removes duplicated
  select(TaxonName,
         TaxonKey,
         CommonName,
         Treaty)

# For suplement Material ####
# Suplemental_table <- All_Species %>% 
#   select(-TaxonKey) %>% 
#   mutate(Treaty = ifelse(TaxonName %in% NAFO_Species$TaxonName,"NAFO",
#                          ifelse(TaxonName %in% c("Hippoglossus stenolepis",
#                                                  "Anoplopoma fimbria"),
#                                 "IPHC",
#                                 "PSC")
#                          )
#   ) %>% 
#   rename("Scientific name" = TaxonName,
#          "Common name" = CommonName) 
# 
#   write.csv(Suplemental_table,
#             "Final_Species_List.csv",
#             row.names = F)

#_____________________________END SUPLEMENTAL TABLE_______________________________#

Models <- c(
  "GFDL26F1",
  "GFDL85F1",
  "IPSL26F1",
  "IPSL85F1",
  "MPI26F1",
  "MPI85F1"
)

for(m in 1:length(Models)){
  # for(s in 1:2){ #For tensting models
  for(s in 1:nrow(All_Species)){

    # Imports all data once#

    x <-dbem_Import(All_Species[s,2],# Include Treaties information
                    2005,
                    2099,
                    Model = Models[m],
                    Data_Type= "Catch"
    )

    # } # For testing the dbem_Import function

    ### If statement for abstent species ##

    if(length(x >= 1)){

      # Merging with lat/long ###
      Spp_Pro <- x %>% 
        left_join(Coor,
                  by = "INDEX")

      # If statement for those species not found within national EEZ
      if(nrow(Spp_Pro) <= 1){

        print("No data within Area Selected")

      }else{

        # Include Species Name
        Spp_Pro$Species <- paste(All_Species[s,1])
        # Include Treaties information
        Spp_Pro$Treaty <- paste(All_Species[s,4])

        Spp_Pro_I <- as.data.table(Spp_Pro)

        # Groups all species together in one database
        if(s == 1){
          Data_P <- copy(Spp_Pro_I) # <- copies the previouse data.table
        }else{
          setkey(Data_P, # <- sets the data.table as "reference" ?setkey
                 Species); setkey(Spp_Pro_I,
                                  Species);
          list <- list(Data_P, # <- creates a list to merge the tables
                       Spp_Pro_I)

          Data_P <- rbindlist(list, #<- Merges all the data in one single file.
                              use.names = TRUE, # <- This will merge columns by Name
                              fill = TRUE, # <- This allows for the NA's
                              idcol =  NULL)  # Columns id
        }
      }
    } #if statement for species outside EEZ
  } # Species loop end

  #Include wich model the data is from
  Data_P$Model <- paste(Models[m])

  # Groups all models together in one database
  if(m == 1){
    DBEM_Results <- copy(Data_P) # <- copies the previouse data.table
  }else{
    setkey(DBEM_Results, # <- sets the data.table as "reference" ?setkey
           Species); setkey(Data_P,
                            Species);
    list <- list(DBEM_Results, # <- creates a list to merge the tables
                 Data_P)

    DBEM_Results <- rbindlist(list, #<- Merges all the data in one single file.
                              use.names = TRUE, # <- This will merge columns by Name
                              fill = TRUE, # <- This allows for the NA's
                              idcol =  NULL)  # Columns id
  }

} #End of loops

#### _____________________TEST _____________________ #
# names(DBEM_Results)
# unique(DBEM_Results$Model)
# unique(DBEM_Results$Species)
# unique(DBEM_Results$Treaty)
# length(unique(DBEM_Results$Species))
# head(DBEM_Results)

# Check that each species has 6 per INDEX or less (GFDL x2 + IPSL x2 + MPIS x2)

# DBEM_Results %>%
#   group_by(Species,INDEX) %>%
#   summarise(n()) %>%
#   View()

# DBEM_Results %>% 
#   filter(Species == "Alosa pseudoharengus",
#          INDEX == 52809)

# Checked!

# Test that NAFO species are actually NAFO species

# DBEM_Results %>% 
#   filter(Treaty == "NAFO") %>% 
#   group_by(Species) %>% 
#   summarise(n())

# Checked!

### Check for potential repeated cells

# DBEM_Results <- Raw_DBEM_Results %>% 
#   select(INDEX,Species,Model,everything())
# 
# DBEM_Results_Clean <- DBEM_Results[!duplicated(DBEM_Results[1:3]), ]

# Checked!

### Russia distribution check ###
# In the Far East sea... 
# 
# Russia <- EEZIDs_List %>% 
#   filter(Name == "Russia (Far East)") 
# 
# Russia_EEZsID <- EEZIDs_List %>% 
#   filter(Name %in% Russia$Name) %>% 
#   left_join(EEZ_CellID,
#             by = "EEZID")
# 
# names(Russia_EEZsID)[3] <- "INDEX"
# 
# unique(Russia_EEZsID$Name)
# 
# Salmones <- c("Oncorhynchus tshawytscha",
#               "Oncorhynchus keta",
#               "Oncorhynchus kisutch",
#               "Oncorhynchus gorbuscha"
#               )
# 
# DBEM_Results %>% 
#   filter(INDEX %in% Russia_EEZsID$INDEX) %>%
#   filter(Longitude > 0 ) %>% 
#   group_by(INDEX, Longitude, Latitude) %>%
#   summarise(n =n()) %>%
#   ggplot(.,
#          aes(x = Longitude,
#              y = Latitude,
#              fill = n
#          ),
#          size = 0.05,
#          alpha = 0.5) +
#   geom_tile() + 
#   coord_map(projection = "mercator")

# Looks fine... Just like when you past it the other way...

#### _____________________END TEST _____________________ #

### Save the dataset
# write.csv(DBEM_Results,
#           "Raw_Data.csv",
#           row.names = FALSE)

```

#### Estimation of Maximum Catch Potential Change

For estimating the percentage change of MCP at the regional scale, we frst aggregated the yearly mean MCP of all species per region ($X_{ry}$) and period:

$$ X_{yr} = \sum_{s = 1}^n \hat{MCP_s}$$

where *y* is year, *r* is region, *s* is species, *n* is total number of species, and $\hat{MCP}$ is the MCP averaged by the three ESMs. In the case of North America and the GoM agrement, region is defined as the 0.5' x 0.5' grid-cell within the EEZ and the specific NAFO regulatory areas, respectiveley. For the IPHC analysis, region is defined as the comission's regulatory areas (Fig. 1). We then average the values in three time periods (*t*) to reduce temporal model sensitivity. Thus, we computed the regional percentage change in MCP ($\Delta MCP_r$) as follows:

$$\Delta MCP_r = -(1-\frac{X_{t}}{X_{t0}})*100 $$

where $X_{t}$ is the future agregated MCP for two periods, $t_1$ = mid 21^st^ century (2045-2055); and $t_3$ = end of 21^st^ century (2090-2099), and $t_0$ is the present aggregated MCP ($\mu$ 2005-2014).

<!-- #### Estimation of Changes in Catch Proportion  -->

In addition, we borrowed the concept of “threat point” from game theory (see Sumaila et al., this Volume) and estimate the change in the $\hat{MCP}$ that each country would have for each species (hereafter referred as stock-share ratio), for both the IPHC and the GoM agreement. For this, we first modify equation 1, to estimate the aggregated yearly mean MCP of each species per region. We then average the results by the same previouslly metioned periods (present, mid and end of the 21^st^ century). Next, for each species we estimated the stock-share ratio ($\alpha$) that each region had during each time period:

$$\alpha_{ts} = \frac{\theta_{rt}}{\delta_{ts}}$$

where $\theta_{r}$ is the aggregated $\hat{MCP}$ of each region, and *t* is period. Finally, we estimated the percentage change in stock-share ratio substituting $X_f$ and $X_p$ by $\alpha_{fs}$ and $\alpha_{ps}$, respectively in equation 2.

<!-- Finally, we estimated the ($\alpha$) percentage change ($\Delta\alpha$) for each region as follows: -->
<!-- $$\Delta\alpha = -(-1-\frac{\alpha_{f}}{\alpha_{p}})*100 $$ -->
<!-- where $\alpha_{f}$ is the future MCP proportion of each region (mid 21^st^ century and end of the 21^st^ century). -->

# RESULTS

```{r Load_Data, echo = F, eval = T, results='hide', warning=F,message=F}

# List of DBEM INDEX within the EEZ
#Data provided by Vicki Lam

EEZIDs_List <- read_excel("~/Documents/UBC/Oceans_Project/Distribution/By Cell/Cell_Data/Updated_EEZList_17June2016.xlsx")

EEZ_CellID <- read_excel("~/Documents/UBC/Oceans_Project/Distribution/By Cell/Cell_Data/EEZ_CellID.xlsx")

colnames(EEZ_CellID) <- c("EEZID","INDEX")

# DBEM Coordinate system
Coor <- fread("~/Documents/UBC/Oceans_Project/Distribution/DBEM/Data/Lon_Lat_DBEM.txt",header = FALSE)
colnames(Coor) <- c("INDEX","Longitude","Latitude")

# From (/Users/jpalacios/Documents/UBC/Oceans_Project/Distribution/By Cell/By_Cell_Analysis.Rmd)
Raw_DBEM_Results <- data.table::fread("~/Documents/UBC/Oceans_Project/Manuscript/Data/Raw_Data.csv") %>% 
  filter(Species != "Anoplopoma fimbria") #Remove

### Number of stocks per treaty##
Raw_DBEM_Results %>%
  group_by(Treaty) %>%
  summarise(x= length(unique(Species)))

#### North American EEZs ####

EEZs <- c(
  "Canada (Pacific)",
  "USA (West Coast)",
  "USA (Alaska, Arctic)",
  "USA (Alaska, Subarctic)",
  "Canada (Arctic)",
  "Canada (East Coast)",
  "USA (East Coast)"
)

All_EEZs <- EEZIDs_List %>% 
  filter(Name %in% EEZs) %>% 
  left_join(EEZ_CellID,
            by = "EEZID")

names(All_EEZs)[3] <- "INDEX"

# LAT LONG Corrections for Alaska

DBEM_Corrected <- Raw_DBEM_Results %>% 
  filter(INDEX %in% All_EEZs$INDEX) %>% 
  filter(Longitude > 0) %>% 
  mutate(Longitude = Longitude - 360)

DBEM_Corrected <- Raw_DBEM_Results %>% 
  filter(INDEX %in% All_EEZs$INDEX) %>% 
  filter(Longitude < 0) %>% 
  bind_rows(DBEM_Corrected)

#### __________________TEST NA Map _____________________ #

# DBEM_Corrected %>%
#   group_by(INDEX, Longitude, Latitude) %>%
#   summarise(n =n()) %>%
#   ggplot(.,
#          aes(x = Longitude,
#              y = Latitude,
#              fill = n
#          ),
#          size = 0.05,
#          alpha = 0.5) +
#   geom_tile() #+
# coord_map(projection = "mercator")

#### __________________All good_____________________________ #

### Get ridd of Pacific Species in the Atlantic

NAFO_E <- DBEM_Corrected %>% 
  filter(Longitude >= -100)

Pacific <- DBEM_Corrected %>% 
  filter(Treaty != "NAFO")

DBEM_Corrected <- NAFO_E %>% 
  bind_rows(Pacific)

# Species on dataset
# unique(DBEM_Corrected$Species)

# Number of species on dataset
# length(unique(DBEM_Corrected$Species))

### Get ridd of Atlantic Species in the Pacific

Pacific_Spp <- DBEM_Corrected %>% 
  filter(Longitude <= -100)

Atlantic <- DBEM_Corrected %>% 
  filter(Treaty == "NAFO")

DBEM_Corrected <- Pacific_Spp %>% 
  bind_rows(Atlantic)

###______ Double chack species distributions are correct ###

# DBEM_Corrected %>%
#   ggplot(.,
#          aes(
#            x = Longitude,
#            y = Latitude,
#            fill = log(INDEX)
#          )
#          ) +
#   geom_tile() +
#   facet_wrap(~Treaty+Species)

#### __________________All good_____________________________ #

### Final step for shapefile no need for knitting

DBEM_Coor <- DBEM_Corrected %>%
  group_by(INDEX,Longitude,Latitude) %>%
  summarise(n=n()) %>%
  select(-n,
         longitude =Longitude,
         latitude = Latitude)

## Create  shapefile for merging with analysis and IPHC shapefile

DBEM_Coor_sf = st_as_sf(DBEM_Coor,
                          coords = c("longitude", "latitude")) %>%
  st_set_crs(4326) %>% # to match shapefiles
  st_transform(4326) # to match shapefiles

#### _____________________TEST _____________________ #
# head(DBEM_Coor_sf)
# 
# ggplot(DBEM_Coor_sf) +
#   geom_sf() +
#   geom_sf(data=North_America_Land)
# 
#### _______________________________________________ #

```

### North American transboundary fisheries are shifting poleward

```{r Changes_Data_All, eval =T, echo = F, fig.height=8, fig.width=12}

# Change North America Projection for Map

North_America_Land <- North_America_Land %>% 
  st_transform(crs = 4326)

### Load shapefile the old way ###

# Path to save the plots
Path <- "~/Documents/UBC/Oceans_Project/Manuscript/Results/North_America"
RCP = c("GFDL26F1","IPSL26F1","MPI26F1") #Low RCP

#### New Future Method to account for mean +- sd of models #
MCP_Data <- DBEM_Corrected %>% 
  mutate(RCP = ifelse(Model %in% RCP,"Low_Emission","High_Emission")) %>% 
  group_by(INDEX,
           Model,
           RCP) %>% 
  summarise_at(vars(Beg_In:End_End), sum,na.rm=T) %>% # Sum the MCP of all species in each index by model
  # select(INDEX,Model,Beg_In:Beg_End) %>% 
  gather("Year","MCP",Beg_In:End_End) %>% 
  mutate(  # Indicate the three period times
    Period = ifelse(Year >= Beg_In & Year <= Beg_End,"Begining",
                    ifelse(Year >= Mid_In & Year <= Mid_End,"Mid_Century",
                           ifelse(Year >= End_In & Year <= End_End,"The_End_Century",
                                  "Other_Years"))
    )
  ) %>% 
  group_by(INDEX,Model,RCP,Period) %>% 
  summarise(Mean_T_MCP =mean(MCP,na.rm=T)) %>% #Average pero Time period
  filter(Period != "Other_Years") %>% 
  spread(Period,Mean_T_MCP) %>% #Spread to estimate MCP_Change
  mutate_at(vars(Mid_Century, # Devide future values by present
                 The_End_Century),
            funs(ifelse(Begining > 0, ./Begining,.)) #if no species today value is the future
  ) %>% 
  mutate_at(vars(Mid_Century, # Estimate percentage change
                 The_End_Century),
            funs(ifelse(Begining == 0 & . == 0, 0, # If for no change than 0
                        ifelse(Begining == 0 & . > 0, 100, # If changes from 0 to anything then 100
                               round(-(1-.)*100) # Estimate percentage change
                        )
            )
            )
  ) %>% 
  gather("Period","MCP_Change",Mid_Century,The_End_Century) %>% 
  mutate(Direction = ifelse(MCP_Change >= 0, "Positive","Negative")) %>% 
  group_by(INDEX,Period,RCP) %>% # Average results per ESMs
  summarise_at(vars(MCP_Change),
               funs("Mean_ESM_MCP_Chng"=mean,
                    "sd_ESM_MCP_Chng"=sd,
                    "N_ESMs"=n(),
                    "Model_Agreement" = paste(length(unique(Direction)),collapse = ";")
               )
  ) %>%
  mutate(
    Model_Agreement = ifelse(Model_Agreement == 1, "Agree","Disagree")
  ) %>% 
  left_join(DBEM_Coor,
            by="INDEX") %>% 
  mutate_at(vars(Mean_ESM_MCP_Chng,
                 sd_ESM_MCP_Chng),
            funs(ifelse(. > 100, 100,.)
            )  # set everything over 100 to 100
  )

### Explore model agreement

# ggplot(MCP_Data) +
#   geom_tile(
#     aes(
#       x = longitude,
#       y = latitude,
#       color = Model_Agreement,
#       fill = Model_Agreement
#     )
#   ) +
#   facet_grid(RCP~Period)

### Explore mAtlantic unde 40

# Under40 <- MCP_Data %>% 
#   filter(latitude < 40, longitude > -90)
# 
# ggplot(Under40) +
#   geom_tile(
#     aes(
#       x = longitude,
#       y = latitude,
#       color = Model_Agreement,
#       fill = Model_Agreement
#     )
#   ) +
#   facet_grid(RCP~Period)

Seq <- seq(-100,100,by=5) #Axis

p <- ggplot(MCP_Data) +
  geom_tile(data = subset(MCP_Data, Period == "Mid_Century"),
            aes(
              x = longitude,
              y = latitude,
              color = Mean_ESM_MCP_Chng,
              fill = Mean_ESM_MCP_Chng
            )
  ) +
  geom_point(data = subset(MCP_Data, Period == "Mid_Century" & Model_Agreement == "Disagree"),
             aes(
               x = longitude,
               y = latitude
             ),
             size = 0.01,
             alpha = 0.1,
             shape = 4,
             color = "grey20"
             ) +
  geom_sf(data = North_America_Land, fill = "grey90") +
  facet_wrap(~RCP) +
  coord_sf(xlim = c(-190,-50)) +
  scale_color_gradient2(
    limits=c(-100,
             100),
    breaks = Seq) +
  scale_fill_gradient2(
    limits=c(-100,
             100),
    breaks = Seq) +
  ggtheme_map()

  ggsave("New_plot.tiff",
         plot = p,
         width = 16,
         height = 10,
         units = "in",
         path = Path)

```

Shifts in the distribution of 33 jointly managed transboundary stocks of North America show that by 2050 maximum catch potential (MCP) of transboundary stocks will increase in Atlantic-Canadian and Alaskan waters and decrease in Pacific-Canadian and the US contiguous states (Fig. 2). Despite the overall trend, such changes will be less intense under the low emission scenario (Fig. 2-A). Under the high emission scenario, MCP will be reduced in a larger area and with greater intensity (Fig. 2-B). Such changes are expected to intensify towards the end of the 21st century, although with greater uncertainty (**Fig A1.1**).

![Fig 2. Percentage change of MCP of transboundary fisheries of North America for mid century (2046-2055) referent to 2005-2014 under a A) low emission scenario and; B) high emission scenario.](./Results/Fig2.png)

```{r Changes_Per_Species_T, eval=F, echo=F}

# This table provides the percentage change in MCP for each species, EEZ and RCP as well as the percentage change in Stock-share ratio.

# List of DBEM INDEX within the EEZ
#Data provided by Vicki Lam
EEZIDs_List <- read_excel("~/Documents/UBC/Oceans_Project/Distribution/By Cell/Cell_Data/Updated_EEZList_17June2016.xlsx")
EEZ_CellID <- read_excel("~/Documents/UBC/Oceans_Project/Distribution/By Cell/Cell_Data/EEZ_CellID.xlsx")

colnames(EEZ_CellID) <- c("EEZID","INDEX")

# DBEM Coordinate system
Coor <- fread("~/Documents/UBC/Oceans_Project/Distribution/DBEM/Data/Lon_Lat_DBEM.txt",header = FALSE)
colnames(Coor) <- c("INDEX","Longitude","Latitude")

#### Mid Century result Table ####
Areas <- c(
  "Canada (Arctic)",
  "Canada (East Coast)",
  "Canada (Pacific)",
  "USA (East Coast)",
  "USA (West Coast)",
  "USA (Alaska, Arctic)",
  "USA (Alaska, Subarctic)"
)

RCP <- c("GFDL26F1","IPSL26F1","MPI26F1")

Selected_Areas <- EEZIDs_List %>% 
  filter(Name %in% Areas)

#### NEW ESTIMATES

# Path to save the plots
Path <- "~/Documents/UBC/Oceans_Project/Manuscript/Results/North_America"
RCP = c("GFDL26F1","IPSL26F1","MPI26F1") #Low RCP

# Common data between both

MCP_Species_Data <- DBEM_Corrected %>% 
  left_join(EEZ_CellID,
            by = "INDEX") %>% 
  filter(EEZID %in% Selected_Areas$EEZID) %>% 
  mutate(RCP = ifelse(Model %in% RCP,"Low_Emission","High_Emission"),
         Nation = ifelse(EEZID >= 958, "Alaska",
                         ifelse(EEZID == 925,"Can W",
                                ifelse(EEZID == 851, "USA E",
                                       ifelse( EEZID== 848, "USA W",
                                               "Can E"))
                         )),
         Basin = ifelse(Nation %in% c("USA E","Can E"),"Atlantic","Pacific"),
  ) %>% 
  group_by(
    Species,
    Model,
    RCP,
    Nation,
    Basin
  ) %>%
  summarise_at(vars(Beg_In:End_End), sum,na.rm=T) %>% # Sum the MCP of each species by country
  # select(INDEX,Model,Beg_In:Beg_End) %>%
  gather("Year","MCP",Beg_In:End_End) %>% 
  mutate(  # Indicate the three period times
    Period = ifelse(Year >= Beg_In & Year <= Beg_End,"Begining",
                    ifelse(Year >= Mid_In & Year <= Mid_End,"Mid_Century",
                           ifelse(Year >= End_In & Year <= End_End,"The_End_Century",
                                  "Other_Years"))
    )
  ) %>% 
  group_by(Nation,Basin,Species,Model,RCP,Period) %>% 
  summarise(Mean_T_MCP =mean(MCP,na.rm=T))

### Estimate average change of all species ####

MCP_Species_Change <- MCP_Species_Data %>% 
  filter(Period != "Other_Years") %>% 
  spread(Period,Mean_T_MCP) %>% #Spread to estimate MCP_Change
  mutate_at(vars(Mid_Century, # Devide future values by present
                 The_End_Century),
            funs(ifelse(Begining > 0, ./Begining,.)) #if no species today value is the future
  ) %>% 
  mutate_at(vars(Mid_Century, # Estimate percentage change
                 The_End_Century),
            funs(ifelse(Begining == 0 & . == 0, 0, # If for no change than 0
                        ifelse(Begining == 0 & . > 0, 100, # If changes from 0 to anything then 100
                               round(-(1-.)*100) # Estimate percentage change
                        )
            )
            )
  ) %>% 
  gather("Period","MCP_Change",Mid_Century,The_End_Century) %>% 
  mutate(Direction = ifelse(MCP_Change >= 0, "Positive","Negative")) %>% 
  group_by(Nation,Species,Period,RCP) %>% # Average results per ESMs
  summarise_at(vars(MCP_Change),
               funs("Mean_ESM_MCP_Chng"=mean,
                    "sd_ESM_MCP_Chng"=sd,
                    "N_ESMs"=n(),
                    "Model_Agreement" = paste(length(unique(Direction)),collapse = ";")
               )
  ) %>%
  mutate(
    Model_Agreement = ifelse(Model_Agreement == 1, "Agree","Disagree")
  ) %>% 
  mutate_at(vars(Mean_ESM_MCP_Chng,
                 sd_ESM_MCP_Chng),
            funs(ifelse(. > 100, 100,.)
            )  # set everything over 100 to 100
  )

#### Estimate Stock Share Change ####

SS_Change <- MCP_Species_Data %>% 
  group_by(RCP,Species,Period,Model) %>% 
  summarise(Total_MCP = sum(Mean_T_MCP)) %>% #Estimate todays's total (both EEZs added) MCP for each species 
  left_join(MCP_Species_Data) %>% # Inlude each nation's MCP
  mutate(Proportion = (Mean_T_MCP/Total_MCP)*100) %>%  # estimates each Country's catch proportion per period
  select(-Total_MCP,-Basin,-Mean_T_MCP) %>% 
  group_by(Nation,RCP,Species,Period) %>% #Mean of all species
  summarise(Mean_Spp_Proportion =mean(Proportion),
            sd_Spp_Proportion =sd(Proportion)
  ) %>% #Mean of all ESMs
  group_by(Nation,RCP,Period) %>% 
  summarise(Mean_ESM_Proportion = paste(round(mean(Mean_Spp_Proportion),2)," (",round(sd(Mean_Spp_Proportion),2),")",sep="")
  ) %>% 
  filter(Period %in% c("Mid_Century","The_End_Century")) %>% 
  spread(Period,Mean_ESM_Proportion)

#For paper
write.csv(SS_Change,
          "SS_Change.csv",
          row.names = F)

```

In consequence, country's share-ratio of different species would change in the direction as expected from the effects of ocean warming, regardless of the RCP scenario. Overall, shifts will be amplified under the high emission scenario relative to the low greenhouse emission scenario pathway (Table 2). While in 2050, the average shift of species will be higher for East Canada and lower for East US under the high emission scenario, the stock-share ratio of some species is expected to increase more than 50% as in the case of Atlantic menhaden (*Brevoortia tyrannus*) in Eastern Canada, and decrease by more than 50% for species such as Cusk (*Brosme brosme*) in the Eastern US under a low emission scenario. By the end of the 21^st^ century, losses will intensify with the eastern US potentially losing on average 15.2% or 46% of stock-share, depending on the scenario.

### Projected change to species managed by the IPHC

Even under a low emission scenario, most transboundary fish stocks sharing ratios will change by 2050 in the direction as expected from the effects of ocean warming. However, such changes will vary depending on the species, resulting in management consequences related to the rules placed by the different treaties. In the case of the IPHC, at least three of the 12 regulatory areas will see a reduction in MCP of Pacific halibut by 2050 in reference to current MCP of each area, regardless of the climate change scenario (Fig. 3). Poleward shifts might be constrained by the geopolitical position of countries, as well as geographic design of the coastline. It is likely that the stock shift from the US contiguous states towards Canada will offset the shift of the former towards northern regions, resulting in undetectable changes in areas 2B and 2C. Similarly, to the potential increase in MCP of regulatory areas 3B and 4ABCE along the Aleutian Islands and Bering Sea.

```{r IPHC_Map_Result_Regions, eval=T, echo=F}

### Get the INDEX in each IPHC region

Selected_Species <- c("Hippoglossus stenolepis") # Halibut

# Path for saving plots
Path <- "~/Documents/UBC/Oceans_Project/Manuscript/Results/IPHC/Region"
RCP = c("GFDL26F1","IPSL26F1","MPI26F1") #Low RCP
#### New version

#### New Future Method to account for mean +- sd of models #
IPHC_MCP_Change <- DBEM_Corrected %>% 
  filter(Species %in% Selected_Species) %>% 
  left_join(IPHC_Reg_DBEM_df,
            by = "INDEX") %>% 
  filter(!is.na(RegArea)) %>% 
  mutate(RCP = ifelse(Model %in% RCP,"Low_Emission","High_Emission")) %>% 
  gather("Year","MCP",Beg_In:End_End) %>% 
  mutate(  # Indicate the three period times
    Period = ifelse(Year >= Beg_In & Year <= Beg_End,"Begining",
                    ifelse(Year >= Mid_In & Year <= Mid_End,"Mid_Century",
                           ifelse(Year >= End_In & Year <= End_End,"The_End_Century",
                                  "Other_Years"))
    )
  ) %>% 
  group_by(RegArea,Model,RCP,Year,Period) %>% 
  summarise(Regional_MCP =sum(MCP,na.rm=T)) %>% # Sum of Index per Region
  group_by(RegArea,Model,RCP,Period) %>% 
  summarise(Mean_T_MCP =mean(Regional_MCP,na.rm=T)) %>% #Average pero Time period
  filter(Period != "Other_Years") %>% 
  spread(Period,Mean_T_MCP) %>% #Spread to estimate MCP_Change
  mutate_at(vars(Mid_Century, # Devide future values by present
                 The_End_Century),
            funs(ifelse(Begining > 0, ./Begining,.)) #if no species today value is the future
  ) %>% 
  mutate_at(vars(Mid_Century, # Estimate percentage change
                 The_End_Century),
            funs(ifelse(Begining == 0 & . == 0, 0, # If for no change than 0
                        ifelse(Begining == 0 & . > 0, 100, # If changes from 0 to anything then 100
                               round(-(1-.)*100) # Estimate percentage change
                        )
            )
            )
  ) %>% 
  gather("Period","MCP_Change",Mid_Century,The_End_Century) %>% 
  mutate(Direction = ifelse(MCP_Change >= 0, "Positive","Negative")) %>% 
  group_by(RegArea,Period,RCP) %>% # Average results per ESMs
  summarise_at(vars(MCP_Change),
               funs("Mean_ESM_MCP_Chng"=mean,
                    "sd_ESM_MCP_Chng"=sd,
                    "N_ESMs"=n(),
                    "Model_Agreement_Index" = paste(length(unique(Direction)),collapse = ";"),
                    "Model_Agreement" = paste(Direction,collapse = ";")
               )
  ) %>%
  mutate(
    Model_Agreement = ifelse(Model_Agreement == 1, "Agree","Disagree")
  ) %>% 
  mutate_at(vars(Mean_ESM_MCP_Chng,
                 sd_ESM_MCP_Chng),
            funs(ifelse(. > 100, 100,.)
            )  # set everything over 100 to 100
  )

# Ends new estimation

### Spatial Step for regional analysis ####

IPHC_DBEM_sf <- IPHC_Reg %>% 
  left_join(IPHC_MCP_Change,
            by = "RegArea") %>% 
  st_transform(3832)

# head(IPHC_DBEM_sf)

# Change name so it fits the plot
IPHC_DBEM_sf$RegArea <- gsub("Closed Area","CA",IPHC_DBEM_sf$RegArea)

# Data to plot

# IPHC_DBEM_sf_Data <- IPHC_DBEM_sf

IPHC_DBEM_sf <- IPHC_DBEM_sf %>% 
  filter(Period == "Mid_Century")

North_America_Land <- North_America_Land %>% 
  st_transform(crs = 3832)

Seq <- seq(-30,30,by=5) #Axis

P1 <- ggplot() +
  geom_sf(data = North_America_Land, colour = "lightgrey") + # Land Map of North America
  geom_sf(data = subset(IPHC_DBEM_sf, Country == "United States"), # DBEM Of the US
          aes(fill = Mean_ESM_MCP_Chng)
  ) +
  geom_sf(data = subset(IPHC_DBEM_sf, RegArea == "2B"), # DBEM of Canada
          aes(fill = Mean_ESM_MCP_Chng)
  ) +
  geom_sf_label(data = IPHC_DBEM_sf, # RegAreas labels
                aes(
                  label = RegArea,
                  fill = Mean_ESM_MCP_Chng
                ),
                colour = "black"
  ) +
  geom_label(data=IPHC_DBEM_sf, aes(label = RCP, x =4080637 , y = 4551701, colour = RCP), #RCP labels for grid plot
             show.legend = FALSE,
             size = 10
  ) +
  facet_wrap(~RCP,  # For grid plot, comment in one plot each
             ncol = 2) +
  # scale_colour_manual(values=c("blue", "red")) + #Labels colors for grid plot
  scale_fill_gradient2("",
                       limits=c(-30,30),
                       breaks = Seq) +
  ggtheme_map() +
  theme(
    legend.key = element_rect(size = 4),
    legend.key.width =unit(8,"line"),
    legend.text = element_text(size = 16),
    strip.text.x = element_blank()
  ) +
  coord_sf(xlim = c(1963800, 10041910), # Subsets North America map
           ylim = c(3651701,9728813)
  ) +
  annotate("text", label = "Alaska", x = 6280637, y = 9228813, size = 6, colour = "black") +
  annotate("text", label = "Canada", x = 9629910, y = 9228813, size = 6, colour = "black") +
  annotate("text", label = "US Contiguous\n States", x =10000000, y = 5151701, size = 6, colour = "black", angle = -90)

# Save plot 
Name = paste("New_IPHC_Reg_26_85_2050.png")

ggsave(Name,
       plot = P1,
       width = 15,
       height = 10,
       units = "in",
       path = Path)

### now we average the results from the models for END century ###

# Seq <- seq(-50,50,by=5) #Axis

# P2 <- ggplot() +
#   geom_sf(data = North_America_Land, colour = "lightgrey") + # Land Map of North America
#   geom_sf(data = subset(IPHC_DBEM_sf, Country == "United States"), # DBEM Of the US
#           aes(fill = Percentage_End)
#   ) +
#   geom_sf(data = subset(IPHC_DBEM_sf, RegArea == "2B"), # DBEM of Canada
#           aes(fill = Percentage_End)
#   ) +
#   geom_sf_label(data = IPHC_DBEM_sf, # RegAreas labels
#                 aes(
#                   label = RegArea,
#                   fill = Percentage_End
#                 ),
#                 colour = "black"
#   ) +
#   geom_label(data=IPHC_DBEM_sf, aes(label = RCP, x =4080637 , y = 4551701, colour = RCP), #RCP labels for grid plot
#              show.legend = FALSE,
#              size = 10
#   ) +
#   facet_wrap(~RCP,  # For grid plot, comment in one plot each
#              ncol = 2) +
#   scale_colour_manual(values=c("blue", "red")) + #Labels colors for grid plot
#   scale_fill_gradient2("",
#                        limits=c(-30,30),
#                        breaks = Seq) +
#   ggtheme_map() +
#   theme(
#     legend.key = element_rect(size = 4),
#     legend.key.width =unit(8,"line"),
#     legend.text = element_text(size = 16),
#     strip.text.x = element_blank()
#   ) +
#   coord_sf(xlim = c(1963800, 10041910), # Subsets north america
#            ylim = c(3651701,9728813)
#   ) +
#   annotate("text", label = "Alaska", x = 6280637, y = 9228813, size = 6, colour = "black") +
#   annotate("text", label = "Canada", x = 9629910, y = 9228813, size = 6, colour = "black") +
#   annotate("text", label = "US Contiguous\n States", x =10000000, y = 5151701, size = 6, colour = "black", angle = -90)
# 
# # Save plot 
# Name_End = paste("IPHC_Reg_26_85_2100.png")
# 
# ggsave(Name_End,
#        plot = P2,
#        width = 15,
#        height = 10,
#        units = "in",
#        path = Path)

```

```{r Functions, eval = F}

getTaxInfo <- function(TaxNumber,TaxPath=NA, Sal = "NA"){

  # Set automatic path, change if needed
  TaxPath  <- "/Volumes/DATA/JULIANO_NEYMAR/PristineSeasData/Species/TaxonDataC0/"

  # Sets the tac and path 
  To_Read <- paste(TaxPath,TaxNumber,".txt",sep = "")

  if(Sal == "Y"){
  Spp_Info <- suppressWarnings(
    read_table2(To_Read, 
     col_names = FALSE, col_types = cols(`0` = col_character(), 
         X2 = col_number(), X3 = col_number(), 
         X4 = col_number(), X5 = col_number(), 
         X6 = col_number()), 
     skip = 16)
  ) 
  Spp_Info <- Spp_Info[1,2:6]
  }else{
  # Reads in file
  Spp_Info <- suppressMessages(
    readr::read_delim(To_Read, 
               "\t", escape_double = FALSE, col_names = FALSE, 
               # col_types = cols(X2 = col_number()),
               trim_ws = TRUE)
  )
  }
  return(Spp_Info)
}

getTTP <- function(TaxNumber,yr,TaxPath=NA){

  # Set automatic path, change if needed
  TaxPath  <- paste("/Volumes/DATA/JULIANO_NEYMAR/PristineSeasData/TPP",yr,"",sep="/")

  # Sets the tac and path 
  To_Read <- paste(TaxPath,"TPPotp",TaxNumber,".csv",sep = "")

  TPPotp <- read.csv(To_Read)

  return(TPPotp)
}

getEnvVar=function(yr,ModelRCP,RCP,Variable){

  if(ModelRCP == "IPSL"){
    ModelRCP = "IPSL-CM5A-MR"
    Filepath <- paste("/Volumes/DATA/DATA/Environmental data/Model Climate data/CMIP5/txt CMIP5/Reformatted",ModelRCP,RCP,"",sep="/")
  }

  if(ModelRCP ==  "MPI"){
    ModelRCP = "MPI-ESM-MR"
    Filepath <- paste("/Volumes/DATA/DATA/Environmental data/Model Climate data/CMIP5/txt CMIP5/Reformatted",ModelRCP,RCP,"",sep="/")
  }

  if(ModelRCP = "GFDL"){

    if(RCP == "rcp26"){
    ModelRCP <- "GFDL26"
    }else{
      ModelRCP <- "GFDL85"
    }

  Filepath <- paste("/Volumes/DATA/JULIANO_NEYMAR/PristineSeasData/Climate",ModelRCP,"",sep="/")
  }

  if(Variable == "Ice"){

    Bottom <- paste("IceExt_",yr,".txt",sep="")

  }

    if(Variable == "Temperature"){

      Bottom = paste("botTemp_",2005,".txt",sep="")

    }

    if(Variable == "Salinity"){
      # Bottom
      Bottom = paste("Salinity_btm_",yr,".txt",sep="")

    }

    Read_me <- paste(Filepath,Bottom,sep="")[1]
    Bottom_Data <- read.csv(Read_me,header=F)

   # Retrun

    getTemp <- Bottom_Data  
}

```

```{r 4D_exploration, eval=F, echo=F,message=F, warning=F}

# Exploring wy 4D s negative under 2.6 but positive under 8.5
# This chunk will use functions build for the Pristince seas work

### Exploration at the spatial level

Spatial_4DE <- DBEM_Corrected %>% 
  mutate(RCP = ifelse(Model %in% c("GFDL26F1","IPSL26F1","MPI26F1"),"RCP 2.6","RCP 8.5")) %>% # Set the RCPs
  filter(Species == "Hippoglossus stenolepis") %>% 
  left_join(IPHC_Reg_DBEM_df,
            by = "INDEX") %>% 
  filter(RegArea %in% c("4D","4E")) %>%
  group_by(RegArea,RCP,Model) %>% #Sum grid-cells by regulatory area, RCP and Model
  summarise_at(vars(`2005`:`2099`), sum,na.rm=T) %>% 
  tidyr::gather("Year","Total_MCP",`2005`:`2099`) %>% 
  group_by(RegArea,RCP,Year) %>% 
  summarise(
    m=mean(Total_MCP),
    sd=sd(Total_MCP)
    )

ggplot(Spatial_4DE) +
  geom_point(
    aes(
      x = Year,
      y = m,
      colour = RCP
    )
  ) +
  facet_wrap(~RegArea,
             scales = "free")

### Environmental varibales of the region

## Temp

# Variables
Model = c("GFDL","IPSL","MPIS")
RCP = c("rcp26","rcp85")

Grid <- DBEM_Corrected %>% 
  select(INDEX) %>% 
  left_join(IPHC_Reg_DBEM_df,
            by = "INDEX") %>% 
  filter(RegArea %in% c("4D","4E")) %>% 
  select(INDEX)

Variables <- c("Temperature","Salinity","Ice")

F_BData <- NULL
F_SData <- NULL
F_MData <- NULL
F_RData <- NULL
Years <- seq(2005,2100,1)

all_Grid <- seq(1,259200,1)

for(v in 3:3){
  # Loop through RCPs
  for(r in 1:2){
    # Loop through  variables
    for(m in 1:3){
      # Loop through years
      for(y in 1:length(Years)){

        Data <- getEnvVar(yr = Years[y],
                          Model = Model[m],
                          Variable = Variables[v],
                          RCP = RCP[r]
        ) %>% 
          mutate(INDEX = all_Grid) %>% 
          filter(INDEX %in% Grid$INDEX)

        if(y == 1){

          F_BData <- Data[1]

        }else{

          F_BData <- cbind(Data[1],F_BData)

        }
      }

      colnames(F_BData) <- Years

      F_BData <- F_BData %>% 
        gather(Year,Value,1:426) %>% 
        mutate(Model = Model[m],
               RCP = RCP[r],
               Variable = Variables[v])

      if(m == 1){

        F_MData <- F_BData

      }else{

        F_MData <- rbind(F_BData,F_MData)
      }
    }

    if(r == 1){

      F_RData <- F_MData

    }else{

      F_RData <- rbind(F_RData,F_MData)
    }
  }

  if(v == 1){

    F_VData <- F_RData

  }else{

    F_VData <- rbind(F_VData,F_RData)
  }

} # closes variable loop

write.csv(F_VData,
          "Environmental_Data_Halibut.csv",
          row.names = F)

### Exploration at the biological level

# exploited_species_list <- fread("/Volumes/DATA/PROJECTION exploited species ENM/exploited_species_list.csv")
# 600514

# Isolate Regions

DE <- IPHC_MCP_Change %>% 
  filter(RegArea %in% c("4D","4E"))

#Load Halibut Species preferences
Halibut <- getTaxInfo(600514)
# Demersal
# HabAssocSal 0 1 1 -1 -1
# HabAssocIce 0

# Temp
TTPop <- getTTP(600514,"Avg") %>% 
  filter(TempPP > 0)

Min_T <- min(TTPop$Temp)
Max_T <- max(TTPop$Temp)

# Halibut_Temp 2
# quant05 -2 
# quant25 0 
# quant50 2
# quant75 5
# quant95 11
```

```{r Figure_3, eval =F, echo =F, fig.cap="Percentage Change of MCP for Species managed by the IPHC. A, RCP 2.6 represents a low emission scenario (high mitigation). B, RCP 8.5 represents a high emission scenario (status quo)"}

img <- readPNG("/Users/jpalacios/Documents/UBC/Oceans_Project/Manuscript/Results/Fig3.png")
grid.raster(img)

```

<!-- If rendered to word use ![](), otherwise use chunk -->

![Fig 3. Percentage change of MCP for species managed by the IPHC for mid century (2046-2055) referent to 2005-2014 under a A) low emission scenario and B) high emission scenario.](./Results/Fig3.png)

The same poleward trend is expected in the change of Pacific halibut stock-share ratio with the average proportion increasing up to 25% in some northern regions and decreasing by 10% in southern regions, in relation to the present proportion (Fig. 4). Maintaining emissions to lower levels by 2050 would potentially leave unchanged the stock-share ratio of three regulatory areas (3AC, and 4D) and negatively change regulatory area 2A. On the other hand, failing to achieve such target will decrease the stock-share ratio almost half of the regulatory areas (2AC, 3AB).

```{r IPHC_Proportion_Regions, eval=F, echo = F, message=F, warning=F}

Path <- "./Manuscript/Results/IPHC/Proportion"
# names(DBEM_Results)

IPHC_Species <- c("Hippoglossus stenolepis") # Halibut

#### FIlter EEZs ###

EEZs <- c(
  "Canada (Pacific)",
  "USA (West Coast)",
  "USA (Alaska, Arctic)",
  "USA (Alaska, Subarctic)"
)

RCP <- c("GFDL26F1","IPSL26F1","MPI26F1")

EEZsID <- EEZIDs_List %>% 
  filter(Name %in%EEZs) %>% 
  left_join(EEZ_CellID,
            by = "EEZID")

names(EEZsID)[3] <- "INDEX"

#### New updated method

New_IPHC_Absolutes <- DBEM_Corrected %>% 
  mutate(RCP = ifelse(Model %in% c("GFDL26F1","IPSL26F1","MPI26F1"),"Low Emission","High Emission")) %>%  # Assigns RCP by model
  filter(Species %in% IPHC_Species,
         INDEX %in% IPHC_Reg_DBEM_df$INDEX) %>%  #Selects only IPHC species within regulatory areas
  left_join(IPHC_Reg_DBEM_df,
            by = "INDEX") %>% # Include Regulatory areas
  gather("Year","MCP",`2005`:`2099`) %>% 
  group_by(RCP,RegArea,Year,Model) %>%
  summarise(MCP = sum(MCP, na.rm = T))

# Changes in the proportion in comparrison of the mean (2005-2014) proportion ####

# Estimate total MCP of each RCP per year
New_Proportion_Total <- New_IPHC_Absolutes %>% 
  group_by(RCP,Year,Model) %>% 
  summarise(Total = sum(MCP))

# Estimates the proportion of each RegArea catch pero RCP and Year
New_Proportion <- New_IPHC_Absolutes %>% 
  left_join(New_Proportion_Total,
            by = c("RCP","Year","Model")) %>% 
  mutate(Proportion = (MCP/Total)*100)

# Proportion change in the future (NOTE: not plotting by timeframe because of boxplot)
New_Proportion_Change <- New_Proportion %>% 
  mutate(Time_Step = ifelse(Year <= Beg_End, "Begining_Prop",
                            ifelse(Year >= Mid_In & Year <= Mid_End,"Mid_Century_Prop",
                                   ifelse(Year >= End_In,"The_End_Century_Prop","Others")
                            )
  ),
  Nation = ifelse(RegArea == "2A","US Contiguous",
                  ifelse(RegArea == "2B","Canada","Alaska")
  )
  ) %>% 
  group_by(RCP,
           RegArea,
           Model,
           Time_Step) %>% 
  summarise(Mean_Temp_Prop = mean(Proportion)) %>% 
  spread(Time_Step,Mean_Temp_Prop) %>% 
  mutate_at(vars(Mid_Century_Prop, # Devide future values by present
                 The_End_Century_Prop),
            funs(ifelse(Begining_Prop > 0, ./Begining_Prop,.)) #if no species today value is the future
  ) %>% 
  mutate_at(vars(Mid_Century_Prop, # Estimate percentage change
                 The_End_Century_Prop),
            funs(ifelse(Begining_Prop == 0 & . == 0, 0, # If for no change than 0
                        ifelse(Begining_Prop == 0 & . > 0, 100, # If changes from 0 to anything then 100
                               round(-(1-.)*100) # Estimate percentage change
                        )
            )
            )
  ) %>%
  gather("Time_Step","Prop_Change",Mid_Century_Prop,The_End_Century_Prop) %>% 
  group_by(RegArea,Time_Step,RCP) %>% # Average results per ESMs
  summarise_at(vars(Prop_Change),
               funs("Mean_ESM_MCP_Chng"=mean,
                    "sd_ESM_MCP_Chng"=sd,
                    "N_ESMs"=n()
               )
  ) %>% 
  mutate(Order = as.character(RegArea),
         Nation = ifelse(RegArea == "2A","US Contiguous",
                         ifelse(RegArea == "2B","Canada","Alaska")
         )
  )

New_Proportion_Change$RegArea <- gsub("2B","2B",New_Proportion_Change$RegArea)

#### Option all in one####
ggplot(data = subset(New_Proportion_Change, Time_Step == "Mid_Century_Prop"),
       aes(
         x = reorder(RegArea,Order), # from forcasts` package
         # x = RegArea,
         y = Mean_ESM_MCP_Chng,
         fill = Nation,
         colour = Nation
       )
) +
  geom_bar(stat = "identity") +
  geom_errorbar(data = subset(New_Proportion_Change, Time_Step == "Mid_Century_Prop"),
                aes(
                  x = reorder(RegArea,Order),
                  # x = RegArea,
                  ymin=Mean_ESM_MCP_Chng-sd_ESM_MCP_Chng, # mean +- 2*sd
                  ymax=Mean_ESM_MCP_Chng+sd_ESM_MCP_Chng,
                  colour=Nation,
                ),
                width=.2,
                linetype = 2,
                size = 0.6,
                alpha = 0.5
  ) +
  coord_flip() +
  ylab("") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  ggtheme_plot() +
  scale_fill_brewer("Region",palette = "Set2") +
  scale_colour_brewer("Region",palette = "Set2") +
  scale_y_continuous(breaks = seq(-40,40,20),
                     limits = c(-40,40)
                     )+
  facet_wrap(~RCP,
             nrow = 1) +
  labs(
    x = "",
    y = "Stock Share Ratio Change (%)"
  )

 ggsave("New_Proportion_Mid.png",
       plot = last_plot(),
       width = 8,
       height =8,
       units = "in",
       path = Path
       )

```

```{r Figure_4, eval =F, echo =F, fig.cap="Percentage change of stock-share ratio for IPHC under two RCPs for Mid century (2046-2055)"}

Fig4 <- readPNG("~/Documents/UBC/Oceans_Project/Manuscript/Results/Fig4.png")
grid.raster(Fig4)

```

<!-- If rendered to word use ![](), otherwise use chunk -->

![Fig 4. Percentage change of stock-share ratio for IPHC under A) low emission scenario and B) high emission scenario for mid century (2046-2055) referent to 2005-2014.](./Results/Fig4.png)

### Projected change to species managed under the GoM agreement

While some regulatory areas of the IPHC will see increments in species' MCP, the results for the Gulf of Maine (NAFO area 5Z) show an overall decrease in MCP by 2050, depending on the climate change scenario. MCP of cod and haddock will decrease within the whole Gulf with no apparent win for any country in reference to 2014 (Fig. 5). For yellowtail flounder, some discrete areas are expected to increase with no particular pattern. Despite the overall reduction in MCP in comparison to current values, there is a benefit of achieving a low emission scenario, as reductions intensify under the high emission scenario.

```{r GB_Results_Spp, eval=F, echo = F, fig.width=12}

#### Filter Species  ####

Atlantic_Species <- c(
  "Gadus morhua",  # Cod
  "Limanda ferruginea", # Yellowtail flounder
  "Melanogrammus aeglefinus" # Haddock
)

# Run Spatial chuck for the Atlantic
# NAFO_5z$geometry

# Filter DBEM results for three specific species within the region of the GoM

N_Lim <- 45.9759
S_Lim <- 41
W_Lim <- -72.0592
E_Lim <- -63.33333

Atlantic_DBEM <- Raw_DBEM_Results %>% 
  filter(Species %in% Atlantic_Species) %>% 
  filter( # Limit the area to George's bank
    Latitude < N_Lim, # North
    Latitude > S_Lim, # South 
    Longitude > W_Lim, # West
    Longitude < E_Lim
  )

# Path for saving plots
Path <- "~/Documents/UBC/Oceans_Project/Manuscript/Results/GB/Spp/"

### MCP Change Analysis ####

#### New analysis ####
New_Mean_Data_GoM <- Atlantic_DBEM %>% 
  mutate(RCP = ifelse(Model %in% c("GFDL26F1","IPSL26F1","MPI26F1"),"Low Emission","High Emission")) %>%
  tidyr::gather("Year","Change",`2005`:`2099`) %>%
  mutate(Change = replace_na(Change, 0)) %>% # Convert NA's into 0's
  mutate(# Indicate the three period times
    Period = ifelse(Year >= Beg_In & Year <= Beg_End,"Begining",
                    ifelse(Year >= Mid_In & Year <= Mid_End,"Mid_Century",
                           ifelse(Year >= End_In & Year <= End_End,"The_End_Century",
                                  "Other_Years"))
    )
  ) %>% 
  filter(Period != "Other_Years") %>% # Remove unwanted years
  group_by(INDEX,Model,RCP,Period,Species) %>%
  summarise(
    Mean_Temp = mean(Change, na.rm = T) # Temporal mean
  ) %>% 
  spread(Period,Mean_Temp) %>% 
  mutate_at(vars(Mid_Century, # Devide future values by present
                 The_End_Century),
            funs(ifelse(Begining > 0, ./Begining,.)) #if no species today value is the future
  ) %>% 
  mutate_at(vars(Mid_Century, # Estimate percentage change
                 The_End_Century),
            funs(ifelse(Begining == 0 & . == 0, 0, # If for no change than 0
                        ifelse(Begining == 0 & . > 0, 100, # If changes from 0 to anything then 100
                               round(-(1-.)*100) # Estimate percentage change
                        )
            )
            )
  ) %>% 
  gather("Period","MCP_Chng",Mid_Century,The_End_Century) %>% 
  mutate(Direction = ifelse(MCP_Chng >= 0, "Positive","Negative")) %>% 
  group_by(INDEX,Species,Period,RCP) %>% # Average results per ESMs
  summarise_at(vars(MCP_Chng),
               funs("Mean_ESM_MCP_Chng"=mean,
                    "sd_ESM_MCP_Chng"=sd,
                    "N_ESMs"=n(),
                    "Model_Agreement" = paste(length(unique(Direction)),collapse = ";")
               )
  ) %>%
  mutate(
    Model_Agreement = ifelse(Model_Agreement == 1, "Agree","Disagree")
  ) %>% 
  mutate_at(vars(Mean_ESM_MCP_Chng,
                 sd_ESM_MCP_Chng),
            funs(ifelse(. > 100, 100,.)
            )  # set everything over 100 to 100
  ) %>% 
    left_join(GB_Coor,
            by ="INDEX")

  # Set Bins for better plotting
  New_Mean_Data_GoM$Bins <- cut(New_Mean_Data_GoM$Mean_ESM_MCP_Chng,breaks = 4)
  # unique(New_Mean_Data_GoM$Bins)

# _______________________________________________________

# The plot 
Seq <- seq(-100,100,10)

Lim_Neg <- min(Seq)
Lim_Max <- max(Seq)

# Use bins and collors yellow orange light red and dark red

# Mean_Data_GoMb <- Mean_Data_GoM %>% # In case you want filter a specific species
#   filter(Species == "Limanda ferruginea")

pgm <- ggplot(New_Mean_Data_GoM) +
  geom_tile(data = subset(New_Mean_Data_GoM, Period == "Mid_Century"),
            aes(
              x = Longitude,
              y = Latitude,
              color = Mean_ESM_MCP_Chng,
              fill = Mean_ESM_MCP_Chng
            )
  ) +
  geom_point(data = subset(New_Mean_Data_GoM, Period == "Mid_Century" & Model_Agreement == "Disagree"),
             aes(
               x = Longitude,
               y = Latitude
             ),
             # size = 0.1,
             alpha = 0.3,
             shape = 4,
             color = "grey20"
  ) +
  scale_fill_gradient2(paste("MCP Percentage Change \n",Mid_In,"-",Mid_End,")"), # If not using the bins
                       limits=c(Lim_Neg,
                                Lim_Max),
                       breaks = Seq,
                       na.value = 'darkred' # NA values are present when the species is no more 
  ) +
  scale_colour_gradient2(paste("MCP Percentage Change \n",Mid_In,"-",Mid_End,")"),
                         limits=c(Lim_Neg,
                                  Lim_Max),
                         breaks = Seq,
                         na.value = 'darkred' # NA values are present when the species is no more
  ) +
  geom_sf(data = GM_Land, colour = "lightgrey") +
  geom_sf(data = eez_GM, fill = NA) +
  coord_sf(xlim = c(-71.0592, -63.33333),
           ylim = c(41,45.5)
           ) +
  annotate("text", label = "United States", x = -70, y = 45, size = 4, colour = "black") +
  annotate("text", label = "Canada", x = -66.8, y = 45.4, size = 4, colour = "black") +
  annotate("text", label = "Canada", x = -65.4, y = 44.2, size = 4, colour = "black") +
  ggtheme_map() +
  theme(
    axis.line = element_line(colour = "black", size = .5),
    axis.ticks = element_line(size = .5),
    axis.text.x = element_text(size = 12,
                               angle = 0,
                               face = "plain"),
    axis.text.y = element_text(size = 12),
    legend.key = element_rect(size = 3),
    legend.key.width =unit(8,"line"),
    legend.title = element_text(size = 20),
    legend.text = element_text(size = 18)
  )  +
  facet_wrap(~RCP + Species, 
             ncol = 3
  )

  Name = paste("New_Change_GB_26_85_Mid.png",sep="_")

ggsave(Name,
       plot = pgm,
       width = 20,
       height = 10,
       units = "in",
       path = Path)

```

![Fig 5. Percentage change of MCP in the Gulf of Main under, A) low emission scenario; and B) high emission for mid century (2041-2060) referent to present (2005-2014)](./Results/Fig5.png)

Despite the expected decrease in MCP for the region, changes in the stock-share ratio of MCP for the Gulf of Maine show different outcomes depending on the species in question. Following the high emission path will affect mostly Canada’s share of Y. flounder and in less degree Haddock, with an increase of Cod share. For the low emission scenario, patterns somehow invert with Canada losing a larger share of Haddock versus Y. flounder, while increasing Cod’s share (Fig 6).

```{r GB_Proportion_Species, eval =F, echo=F}
### Analysis by Species ####

Path <- "~/Documents/UBC/Oceans_Project/Manuscript/Results"
# names(DBEM_Results)

Atlantic_Species <- c(
  "Gadus morhua",  # Cod
  "Limanda ferruginea", # Yellowtail flounder
  "Melanogrammus aeglefinus"
)

N_Lim <- 45.9759
S_Lim <- 41
W_Lim <- -72.0592
E_Lim <- -63.33333

# Run Spatial chuck for the Atlantic

Atlantic_DBEM <- Raw_DBEM_Results %>% 
  filter(Species %in% Atlantic_Species) %>% 
  filter( # Limit the area to George's bank
    Latitude < N_Lim, # North
    Latitude > S_Lim, # South 
    Longitude > W_Lim, # West
    Longitude < E_Lim
  )

EEZs <- c(
  "Canada (East Coast)",
  "USA (East Coast)"
)

RCP = c("GFDL26F1","IPSL26F1","MPI26F1")

EEZsID <- EEZIDs_List %>% 
  filter(Name %in%EEZs) %>% 
  left_join(EEZ_CellID,
            by = "EEZID")

names(EEZsID)[3] <- "INDEX"

GB_Coor <- Coor %>% 
  filter(INDEX %in% EEZsID$INDEX) %>% 
  # mutate(one = 1) %>% 
  filter( # Limit the area to George's bank
    Latitude < N_Lim, # North
    Latitude > S_Lim, # South 
    Longitude > -71, # West
    Longitude < E_Lim
  )

#### New updated method

New_GoM_Absolutes <- Atlantic_DBEM %>% 
  mutate(RCP = ifelse(Model %in% c("GFDL26F1","IPSL26F1","MPI26F1"),"Low Emission","High Emission")) %>%  # Assigns RCP by model
  filter(Species %in% Atlantic_Species,
         INDEX %in% GB_Coor$INDEX) %>%  #Selects only IPHC species within regulatory areas
  left_join(EEZsID,
            by = "INDEX") %>% 
  gather("Year","MCP",`2005`:`2099`) %>% 
  group_by(Species,RCP,Name,Year,Model) %>%
  summarise(MCP = sum(MCP, na.rm = T))

# Changes in the proportion in comparrison of the mean (2004-2014) proportion ####

# Estimate total MCP of each RCP per year
New_Proportion_Total <- New_GoM_Absolutes %>% 
  group_by(Species,RCP,Year,Model) %>% 
  summarise(Total = sum(MCP))

# Estimates the proportion of each RegArea catch pero RCP and Year
New_Proportion_GoM <- New_GoM_Absolutes %>% 
  left_join(New_Proportion_Total,
            by = c("RCP","Year","Model","Species")) %>% 
  mutate(Proportion = (MCP/Total)*100)

# Proportion change in the future (NOTE: not plotting by timeframe because of boxplot)
New_Proportion_Change_GoM <- New_Proportion_GoM %>% 
  mutate(Time_Step = ifelse(Year <= Beg_End, "Begining_Prop",
                            ifelse(Year >= Mid_In & Year <= Mid_End,"Mid_Century_Prop",
                                   ifelse(Year >= End_In,"The_End_Century_Prop","Others")
                            )
  )
  ) %>% 
  group_by(Species,
           RCP,
           Name,
           Model,
           Time_Step) %>% 
  summarise(Mean_Temp_Prop = mean(Proportion)) %>% 
  spread(Time_Step,Mean_Temp_Prop) %>% 
  mutate_at(vars(Mid_Century_Prop, # Devide future values by present
                 The_End_Century_Prop),
            funs(ifelse(Begining_Prop > 0, ./Begining_Prop,.)) #if no species today value is the future
  ) %>% 
  mutate_at(vars(Mid_Century_Prop, # Estimate percentage change
                 The_End_Century_Prop),
            funs(ifelse(Begining_Prop == 0 & . == 0, 0, # If for no change than 0
                        ifelse(Begining_Prop == 0 & . > 0, 100, # If changes from 0 to anything then 100
                               round(-(1-.)*100) # Estimate percentage change
                        )
            )
            )
  ) %>%
  gather("Time_Step","Prop_Change",Mid_Century_Prop,The_End_Century_Prop) %>% 
  group_by(Species,Name,Time_Step,RCP) %>% # Average results per ESMs
  summarise_at(vars(Prop_Change),
               funs("Mean_ESM_MCP_Chng"=mean,
                    "sd_ESM_MCP_Chng"=sd,
                    "N_ESMs"=n()
               )
  ) %>% 
  mutate(
    Order = ifelse(Species== "Gadus morhua", 2,
                   ifelse( Species == "Melanogrammus aeglefinus",1,3))
  )

# The plot
ggplot(data = subset(New_Proportion_Change_GoM, Time_Step == "Mid_Century_Prop"),
       aes(
         x = reorder(Species,Order),
         # x = Species
         y = Mean_ESM_MCP_Chng,
         fill = Name,
         colour = Name
       )
) +
  geom_bar(stat = "identity") +
  geom_errorbar(data = subset(New_Proportion_Change_GoM, Time_Step == "Mid_Century_Prop"),
                aes(
                  x = reorder(Species,Order),
                  # x = Species,
                  ymin=Mean_ESM_MCP_Chng-sd_ESM_MCP_Chng, # mean +- 2*sd
                  ymax=Mean_ESM_MCP_Chng+sd_ESM_MCP_Chng,
                  colour=Name,
                ),
                width=.2,
                linetype = 2,
                size = 0.6,
                alpha = 0.5
  ) +
  scale_y_continuous(breaks = seq(-15,15,5),
                     limits = c(-15,15)
                     )+
  xlab ("") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  ggtheme_plot() +
  scale_fill_brewer("Region",palette = "Set2") +
  scale_colour_brewer("Region",palette = "Set2") +
  facet_wrap(~RCP,
             nrow = 1) +
  labs(
    x = "",
    y = "Stock Share Ratio Change (%)"
  ) +
  theme(legend.position = c(0.3, 1),
        legend.direction = "horizontal",
        strip.text.x = element_blank(),
        axis.text.x = element_text(size = 12,
                               # angle = 0,
                               face = "italic",
                               # hjust = 0
                               ),
  )

 ggsave("New_GoM_Proportion_Mid.png",
       plot = last_plot(),
       width = 12,
       height = 6,
       units = "in",
       path = Path
       )

```

![Fig 6. Changes in MCP stock-share ratio for Gulf of Main under (A) low emission scenario; and (B) high emission for mid century (2041-2060) referent to 2005-2014](./Results/Fig6.png)

# DISCUSSION

<!-- ## Species shifting towards the poles  -->

The results of the present study suggest that, by 2050, climate change will alter the MCP of 33 transboundary fish stocks in North America consequently altering Canada’s and the US’s species’ stock-share ratio. For some species, such changes will intensify under the high emission carbon scenario while for others, the change will be scenario depending. These results are aligned with global [@Cheung:2010dt] and regional [@Morley:2018fn] projections suggesting that climate change will push marine species towards the poles and deeper water [@Pinsky:2013jo] in search of their ecological niche [@Poloczanska:2016kk]. Moreover, poleward shifts in Eastern Atlantic off the coast of the US have been previously recorded for American lobster (*Homarus americanus*), summer (*Paralichthys dentatus*) and yellow flounders, and red hake (*Urophycis chuss*) from North Carolina to Main [@Pinsky:2012kq]. Our models suggest that shifts will continue towards the end of the 21^st^ century resulting in changes in the proportion of the catch of important shared stocks between Canada and the US. As the effects of climate change endure, even with high mitigation, joint plans should prepare to face changes in the stock-share ratio of transboundary stocks along the coast of North America.

Geographic barriers [@Cheung:2015fm], local temperature gradients [@Pinsky:2013jo], species interactions and human activities like fishing [@Serpetti:2017he] might change the rate and direction of species shifts. Species such as haddock in the Atlantic [@Morley:2018fn], and big skate (*Raja binoculata*) in the pacific coast [@Pinsky:2013jo] have been projected to shift away from the poles. In this manner, the stock-share gain of yellow flounder and haddock by the US in the GoM (Fig. 5) and the westward increase of stock-share in IPHC regions (Fig. 4) could be a response to a temperature gradient shift, combined with geographic barriers, rather than latitudinal shifts. In recent years, Maine has seen its landings of Y. flounder increased at the expenses of southern states like New York [@Pinsky:2012kq]. Moreover, previous studies have found that under the low emission scenario, haddock is expected to stay at lower latitudes, contrary to what would happen under a high emission scenario [@Morley:2018fn]. Finally, the Gulf of Main is deeper at southern latitudes, hence, some fish are predicted to move south [@Kleisner:2016je; @Pinsky:2017hr]. These particular cases could explain the US gain in MCP in the GoM in relation to Canada as species shift their distribution from lower latitudes naturally reaching the US (lower) region first, and towards colder and deeper waters located at southern latitudes of the Gulf. At the same time, in the North West Pacific region, species can only migrate northward into the Arctic Ocean through the Bering Sea and Bering Strait [@Cheung:2015fm], potentially pushing pacific halibut west of region 3A. This westward displacement could represent a potential loss for both nations as the Gulf of Alaska is historically the most productive region of the fishery [@IPHCSecreatriat:2017uz], and potential international conflict as the stock migrates to the high seas or even reach other westerly countries’ EEZ.

The shifts in the distribution of transboundary species can jeopardize management objectives such as, conservation measures, gear operation, and quota allocations. Hypothetically, fish moving out of fishing grounds and into protected areas could result in a pressure increase to open such area to fishing. Shifting stocks could also interfere in gear-limitation management rules. Bycatch of halibut by other fisheries happen mostly on areas 3A and 4B [@NOAA:JWHvVGvq; @IPHC:2017fs]. Moreover, in past years, the Alaskan trawl fisheries have been closed before reaching annual quota due to the attainment of halibut bycatch quota limits [@Karim:2010ut]. Although not assessed in the present study, some trawling target species like Pacific cod (*Gadus macrocephalus*) are expected to move in similar direction than P. halibut [@Pinsky:2013jo]. Conflicts between fleets already exists and could be extrapolated if the situation is not foreseen [@VanDerVoo:2016uc]. The overlap of target species could be addressed by applying ecosystem-based management and dynamic management tools [@Hazen:2018fa] to manage these fisheries and reduce potential lost of sustainable harvest for both the halibut and the trawl fisheries.

Quota allocation ruled by historic distributions will most likeley be outdated. Changes in the proportion of the quota have created tension between countries [@Spijkers:2017ij] including Canada and the US in the case of the Pacific salmon [@Miller:2013iv; @Munro:2002uf; @Song:2017va]. Poleward shifts along the coast of Oregon, Washington and British Columbia (Canada) were first addressed by the IPHC in 1985 (@McCaughran:1992uw). Changes in the distribution of the stock resulted in an adjustment in the quota allocation method, from a fixed quota allocation to a dynamic one. As climate change continues, these shifts are not expected to stop, and treaties should be flexible enough to cope with the pace and magnitude of change in order to achieve sustainable harvest under a changing climate.

Side payments have been previously used to address changes in species distribution due to environmental forcings. In game theory, a side payment is received by a player as a compensation from the other player, with the idea that keeping cooperation is still better than playing solo [@Bjorndal:2012vd; @Sumaila:2013hv]. Side payments do not have to be in monetary form and are widely used in transboundary fisheries around the world. For example, Norway and Russia have implemented a quota swap strategy for jointly managed stocks of cod, haddock and capelin in the Barents Sea [^NR]. The adaptation of a similar agreement could help the management of fisheries in the Gulf of Main. Another example is the Nauru Agreement (PNA), responsible for managing the world's largest sustainable skipjack tuna (*Katsuwonus pelamis*) purse seine fishery [^PNA]. The PNA has a system of internationally tradable fisheries access that allows members to adapt to the effects of the El Niño Southern Oscillation [@Aqorau:2018bh]. While this is a good way to address climate variation within members of a treaty, it might fall short to address the newcomer issue, a situation that can threaten the sustainability of the stock [@Pinsky:2018cb]. A combination of the methods employed by PNA with the proper modification to incorporate new fishing nations could help mitigate future conflicts in fisheries like the Pacific halibut. Finally, It has been suggested that agreements that make cooperation the preferred strategy for all players are stronger. However, the level of government at which negotiations are held can directly impact management outcomes, as low-level agreements might lack proper penalties for non-cooperative behavior [@Miller:2013iv]. Officializing treaties like the case of the Gulf of Maine could provide better ground for the management rules and increase treaty resilience.

[^NR]: Joint Fish, joint Russian-Norwegian Fisheries Comission available at http://www.jointfish.com/eng/THE-FISHERIES-COMMISSION/HISTORY.html
[^PNA]: The Parties to the Nauru Agreement (PNA), available at http://www.pnatuna.com/

<!-- ## Uncertanty stuff -->

In the current paper we follow a modeling approach to explore the potential impacts that climate change will have in the management of transboundary fisheries in North America. Models are attempts to represent reality (in our case a future reality) based on observational data, previously established theory, and future scenarios, and are thus, subjected to different degrees of uncertainty [@Payne:2016gn]. First, our study incorporates multiple earth system models to project the future distribution of transboundary stocks while accounting the structural uncertainty built within each ESM [@Bopp:2013fg]. In terms of the structural uncertainty build within the DBEM, previous analysis shown that the trends of changes in MCP are not affected by its structural uncertainty [@Cheung:2016jd]. Secondly, scenario planning has been widely used in climate change studies as a method to account for the uncertainty build in future decision making [@vanVuuren:2011ef]. In this aspect we considered two extreme RCPs that comprises the vast spectrum of possibilities proposed by the IPCC [@IPCC:2014bz]. A lower-than-2.6 RCP (1.5º warming) was discussed at the recent Paris Agreement sessions celebrated in Paris France. While we did not include this scenario in our analysis, previous research suggest that stronger mitigation efforts would bring large benefits to fisheries [@Cheung:2016tt]. Finally, future changes to species distributions could be influenced by interactions between species [@Pecl:2017hu], adaptation of species to environmental changes, and anthropogenic factors [@Serpetti:2017he]. However, these factors are expected to increase the rate of range-shifting of the species making our results conservative [@Cheung:2010dt; @Serpetti:2017he].

<!-- Discussion on improoving management  -->
<!-- From global (Cheung et al. 2016c) to regional (Morley et al. 2018) analysis, mitigating the effects of climate change will have positive results on fisheries (Sumaila 2019). In combination with improving management [Costello], fisheries will only be saved by a holistic approach… Indeed, dynamic management tools seem to work better than static strategies for resources expected to shift with changes in ocean condition (Pinsky and Selden 2017). -->

# CONCLUSIONS

Shifts in species distribution due to climate change have the potential of creating local extinction of economically important species while enhancing fisheries in areas where they were not present before. In this paper, we have explored the potential impacts of climate change in the joint management of 33 transboundary stocks managed by Canada and the US. We found that, transboundary species are likely to shift north in the upcoming years changing the proportion of the catch of jointly managed fisheries of Canada and the US. Lessons from other countries can provide solutions to such challenges. More specific, side payments, dynamic management, and interchangeable quotas were identified as potential solutions for North American region. While not directly addressed in this study, socio-economic impacts of shifting transboundary stocks could add an extra layer of complexity to the problem. Addressing shifts in species distribution sooner rather than latter could avert the so called "fish wars", improve sustainability of jointly managed stocks, and secure the livelihood of thousand of families that depend on stocks that move freely between national jurisdictions.

# ACKNOWLEDGEMENTS

We ack

# LITERATURE CITED

```{r Old analysis, eval = F}

#### Old North America Estimation ####

for(r in 1:2){

  if(r == 1){
    RCP = c("GFDL26F1","IPSL26F1","MPI26F1") #Low RCP
  }else{
    RCP = c("GFDL85F1","IPSL85F1","MPI285F1") #High RCP
  }

  # OLD VERSION _________________________________________
  # Mean for each cel from 2005-2014
  Mean_Data <- DBEM_Corrected %>% 
    filter(Model %in% RCP) %>% 
    group_by(INDEX,
             Model) %>% 
    summarise_at(vars(Beg_In:End_End), sum,na.rm=T) %>% # Sum the MCP of all species in each index by model
    select(INDEX,Beg_In:Beg_End) %>% 
    group_by(INDEX) %>% 
    summarise_at(vars(Beg_In:Beg_End), mean,na.rm=T) %>% # Yearly average of three models (Structural uncertanty)
    mutate(Mean = rowMeans(.[,2:11])) %>% # Decal average (2005-2014) of results (Uncertanty related to climate variabillity)
    select(INDEX,Mean) %>% 
    arrange(INDEX)

  #The future
  Future <- DBEM_Corrected %>% 
    filter(Model %in% RCP) %>% 
    group_by(INDEX,
             Model) %>% 
    summarise_at(vars(Beg_In:End_End), sum,na.rm=T) %>% # Sum the MCP of all species in each index by model
    group_by(INDEX) %>% 
    summarise_at(vars(`2015`:End_End), mean,na.rm=T) %>% # Yearly average of three models
    arrange(INDEX)

  #SD future
  # for this we have to first average the temporal variabillity for each model and then average the models, that way we will have the SD resulted of the model average and not the termporal variation

  SD_Future <- DBEM_Corrected %>%
    # filter( INDEX == 67071) %>%
    filter(Model %in% RCP) %>%
    group_by(INDEX,
             Model) %>%
    summarise_at(vars(`2005`:`2099`), sum,na.rm=T) %>% # Sum the MCP of all species in each index by model
    tidyr::gather("Year","Change",3:97) %>%
    filter(Year >= 2045 & Year <= 2054) %>% # Select mid century
    group_by(INDEX,Model) %>%
    summarise(
      Mean_Temp = mean(Change, na.rm = T), # Temporal Mean and SD 
      SD_Temp = sd(Change, na.rm = T)
    ) %>%
    group_by(INDEX) %>%
    summarise(
      Mean_M = mean(Mean_Temp, na.rm = T), # Model mean
      SD_M = sd(Mean_Temp, na.rm = T) # Model SD
    ) %>%
    filter(!is.na(SD_M)) %>%
    mutate(SD_Plus = ifelse((SD_M*2) > Mean_M,"No agreement","Agree")) %>% # If 2xSD is bigger than the mean, then models don't agree, otherwise they do
    # filter(SD_Plus > 0) %>%
    left_join(DBEM_Coor,
              by="INDEX")

  #### Overall agreement. Number of cells where models don't match

  # SD_Future %>%
  #   group_by(SD_Plus) %>%
  #   summarise(n())

  # RCp 2.6 30% of grids don't agree
  # Agree 3825
  # Don't agree 1140

  # RCp 8.5 32% of grids don't agree
  # Agree         3564
  # No agreement  1151

  # #Devide one by the other

  #### _______________________________________________ #

  # Devide future projections by "today's"" projections

  Cell_Index <- sweep(Future[2:86],#Future catch p.
                      1, #1 goes by row and 2 goes by colum
                      Mean_Data$Mean, #the means
                      "/") %>% 
    mutate(INDEX = Future$INDEX) %>% 
    select(INDEX,everything())

  Mid_Century <- Cell_Index %>% 
    select(INDEX,
           Mid_In:Mid_End) %>% 
    mutate(Mean = rowMeans(.[,2:11])) %>% # Temporal average
    # left_join(NorthA_Coor_df,
              # by ="INDEX") %>% 
    mutate(Percentage = round(-(1-Mean)*100)) %>% # Convert to percentage change
    mutate("Percentage Change" = ifelse(Percentage > 100, 100,Percentage)) %>%  # set everything over 100 to 100
    filter(!is.na(`Percentage Change`)) %>% 
    left_join(DBEM_Coor,
              by="INDEX")

    #### North America Transboundary Plot ####

  Seq <- seq(-100,100,by=20) #Axis

  ggplot() +
    geom_tile(data = Mid_Century, # Percentage change data
              aes(
                x = longitude,
                y = latitude,
                colour = `Percentage Change`,
                fill = `Percentage Change`
              )
    ) +
    geom_point(data = subset(SD_Future, SD_Plus == "No agreement"), # ESM model uncertanty
               aes(
                 x = longitude,
                 y = latitude
               ),
               size = 0.05,
               alpha = 0.5,
               shape = 6,
               colour = "grey20") +
    geom_sf(data = North_America_Land, fill = "grey90") + # Base map
    coord_sf(xlim = c(-190,-50)) +
    scale_colour_gradient2(
      limits=c(-100,
               100),
      breaks = Seq) +
    scale_fill_gradient2(
      limits=c(-100,
               100),
      breaks = Seq) +
    ggtheme_map()

   if(r == 1){
    Name = paste("North_America_Change_26_2050.png")
  }else{
    Name = paste("North_America_Change_85_2050.png")
  }

  ggsave(Name,
         plot = last_plot(),
         width = 12,
         height = 10,
         units = "in",
         path = Path)

  ### now we average the results from the models for END century ###

  End_Century <- Cell_Index %>% 
    select(INDEX,
           `2090`:`2099`) %>% 
    mutate(Mean = rowMeans(.[,2:11])) %>% 
    mutate(Percentage = round(-(1-Mean)*100)) %>% # Convert to percentage
    mutate("Percentage Change" = ifelse(Percentage > 100, 100,Percentage)) %>%  # set everything over 100 to 100
    filter(!is.na(`Percentage Change`)) %>% 
    left_join(DBEM_Coor,
              by="INDEX")

  SD_End <- DBEM_Corrected %>% 
    # filter( INDEX == 67071) %>% 
    filter(Model %in% RCP) %>% 
    group_by(INDEX,
             Model) %>% 
    summarise_at(vars(`2005`:`2099`), sum,na.rm=T) %>% 
    tidyr::gather("Year","Change",3:97) %>% 
    filter(Year >= 2090 & Year <= 2099) %>% 
    group_by(INDEX,Model) %>% 
    summarise(
      Mean_Temp = mean(Change, na.rm = T), # Mean temporal
      SD_Temp = sd(Change, na.rm = T) #Sd of 10 years average
    ) %>% 
    group_by(INDEX) %>% 
    summarise(
      Mean_M = mean(Mean_Temp, na.rm = T), # Models mean
      SD_M = sd(Mean_Temp, na.rm = T) #Models Sd
    ) %>% 
    filter(!is.na(SD_M)) %>% 
    mutate(SD_Plus = ifelse((SD_M*2) > Mean_M,"No agreement","Agree")) %>% 
    # filter(SD_Plus > 0) %>% 
    left_join(DBEM_Coor,
              by="INDEX")

  ggplot() +
    geom_tile(data = End_Century,
              aes(
                x = longitude,
                y = latitude,
                colour = `Percentage Change`,
                fill = `Percentage Change`
              )
    ) +
    geom_point(data = subset(SD_End, SD_Plus == "No agreement"),
               aes(
                 x = longitude,
                 y = latitude
               ),
               size = 0.05,
               alpha = 0.5,
               shape = 6,
               colour = "grey20") +
    geom_sf(data = North_America_Land, fill = "grey90") +
    coord_sf(xlim = c(-190,-50)) +
    scale_colour_gradient2(
      limits=c(-100,
               100),
      breaks = Seq) +
    scale_fill_gradient2(
      limits=c(-100,
               100),
      breaks = Seq) +
    ggtheme_map()

  if(r == 1){
    Name_End = paste("North_America_Change_26_2100.png")
  }else{
    Name_End = paste("North_America_Change_85_2100.png")
  }

  ggsave(Name_End,
         plot = last_plot(),
         width = 12,
         height = 10,
         units = "in",
         path = Path)

}

#### Old IPHC estimation ####

# Future change in MCP of IPHC per region
IPHC_MCP_Change <- DBEM_Corrected %>% 
  mutate(RCP = ifelse(Model %in% c("GFDL26F1","IPSL26F1","MPI26F1"),"RCP 2.6","RCP 8.5")) %>% # Set the RCPs
  filter(Species %in% Selected_Species#,
         # INDEX %in% IPHC_Reg_DBEM_df$INDEX
         ) %>% # Filter species to halibut and the region for the IPHC regulatory area
  # group_by(INDEX,Model,RCP,Species) %>% # Add values per species
  # summarise_at(vars(`2005`:`2099`), sum,na.rm=T) %>%
  left_join(IPHC_Reg_DBEM_df,
            by = "INDEX") %>% # Include the regulatory areas info
  group_by(RegArea,RCP,Model) %>% #Sum grid-cells by regulatory area, RCP and Model
  summarise_at(vars(`2005`:`2099`), sum,na.rm=T) %>% 
  tidyr::gather("Year","Change",`2005`:`2099`) %>%
  mutate(# Indicate the three period times
    Period = ifelse(Year >= 2005 & Year <= 2014,"Today",
                    ifelse(Year >= 2046 & Year <= 2055,"Mid Century",
                           ifelse(Year >= 2090 & Year <= 2099,"End Century",
                                  "Other_Years"))
    )
  ) %>% 
  filter(Period != "Other_Years") %>% # Remove unwanted years
  group_by(RegArea,Model,RCP,Period) %>%
  summarise(
    Mean_Temp = mean(Change, na.rm = T), # Temporal mean
    SD_Temp = sd(Change, na.rm = T) #Temporal sd
  ) %>% 
  group_by(RegArea,RCP,Period) %>% # Models (GFDL,IPSL,MPIs) mean and SD
  summarise(
    Mean_M = mean(Mean_Temp, na.rm = T),
    SD_M = sd(Mean_Temp, na.rm = T)
  ) %>% 
  filter(!is.na(SD_M)) %>% 
  mutate(Robust = ifelse((SD_M*2) > Mean_M,"No agreement","Agree"))  %>% # Flags robustness in data
  # filter(Robust > 0) %>%
  select(RegArea,RCP,Period,Mean_M) %>% # They all agree except for 4D mid century
  spread(Period,Mean_M) %>% 
  mutate( # Estimate the percentage change
    Change_Mid = `Mid Century`/Today,
    Change_End = `End Century`/Today,
    Percentage_Mid = round(-(1-Change_Mid)*100),
    Percentage_End = round(-(1-Change_End)*100)
  ) %>% 
  select(RegArea, RCP, Percentage_Mid,Percentage_End)

#### Species Table for SS proportion change ####

#### OLD VERSION

# Average (GFDL, MPI, IPSL) MCP of each species from 2005-2099 for both RCP's
Overall <- DBEM_Corrected %>%
  left_join(EEZ_CellID,
            by = "INDEX") %>% 
  # head() %>%
  filter(EEZID %in% Selected_Areas$EEZID) %>% 
  mutate( # determine what nation is wach region, what result is fr each RCP and Basin
    Nation = ifelse(EEZID >= 958, "Alaska",
                    ifelse(EEZID == 925,"Can W",
                           ifelse(EEZID == 851, "USA E",
                                  ifelse( EEZID== 848, "USA W",
                                          "Can E"))
                    )),
    RCP = ifelse(Model %in% RCP,"Low_Emission","High_Emission"), # determine which model is ehat RCP
    Basin = ifelse(Nation %in% c("USA E","Can E"),"Atlantic","Pacific"),
  ) %>% 
  group_by(Species,Nation,Basin,RCP,Model) %>% # Adds each species' MCP of all INDEX-cells within each "nation" EEZ
  summarise_if(is.numeric,sum,na.rm=T) %>% # sum of values 
  group_by(Species,Nation,Basin,RCP) %>%  
  summarise_at(vars(`2005`:`2099`),mean,na.rm=T) %>% # Average the MCP results from the three ESMs
  gather("Year","MCP",`2005`:`2099`) %>% 
  mutate(  # Indicate the three period times
    Period = ifelse(Year >= 2004 & Year <= 2014,"Today",
                    ifelse(Year >= 2046 & Year <= 2055,"Mid_Century",
                           ifelse(Year >= 2090 & Year <= 2099,"End_Century",
                                  "Other_Years"))
    )
  ) %>% # Set the three time periods 
  filter(Period != "Other_Years") %>% # Remove whatever is in the middle
  group_by(Species,Nation,Basin,RCP,Period) %>% 
  summarise(Period_MCP = mean(MCP)) #Temporal average of results

#### Percentage Change in MCP for each species period, and RCP ####

MCP_Spp_Change <- Overall %>%
  spread(Period,Period_MCP) %>% 
  mutate( # Devides the different timeframes by the present and estimates percentage change
    Change_End = `End_Century`/Today,
    Change_Mid = `Mid_Century`/Today,
    Mid_Century = -(1-Change_Mid)*100,
    The_End_Century = -(1-Change_End)*100
  ) %>%
  gather("Period","Percentage_Change",Mid_Century:The_End_Century) %>% 
  ungroup() %>% 
  select(-5)

# group_by(Nation,Period,RCP) %>% # Average the results per species
#   summarise(
#     Mean_All = mean(Percentage_Change, na.rm = T),
#     sd_All = sd(Percentage_Change, na.rm = T)
#   ) %>%
#   View() # Average proportion change of all species

  #### Compare versions

  # Comparring <- MCP_Species_Data %>% 
  #   select(1:5) %>% 
  #   left_join(MCP_Spp_Change) %>% 
  #   mutate(Diff = Mean_ESM_MCP_Chng - Percentage_Change)
  # 
  # 
  #

#### Percentage Change in stock-share ratio for each species period, and RCP ####

SS_Change <- Overall %>%
  group_by(RCP,Basin,Species,Period) %>% 
  summarise(Total_MCP = sum(Period_MCP)) %>% #Estimate todays's total (both EEZs added) MCP for each species (for each Basin!)
  left_join(Overall) %>% # Inlude each nation's MCP
  mutate(
    Proportion = (Period_MCP/Total_MCP)*100 # estimates each Country's catch proportion per period
  ) %>% 
  select(Species,Nation,Basin,RCP,Period,Proportion) %>% 
  spread(Period,Proportion) %>% # Spread for easier mutation
  mutate( # Estimate the percentage change
    SSR_Change_Mid = `Mid Century`/Today,
    SSR_Change_End = `End Century`/Today,
    SSR_Percentage_Mid = round(-(1-SSR_Change_Mid)*100),
    SSR_Percentage_End = round(-(1-SSR_Change_End)*100)
  ) %>% 
  # View() # Average change in MCP proportion per Nation (comment it to have a mean +-sd of all areas)
  group_by(RCP,Nation) %>% 
    summarise(mean = mean(SSR_Percentage_End),
              sd = sd(SSR_Percentage_End)
              )

#### IPHC proportion change

#### Old version

IPHC_Absolutes <- DBEM_Corrected %>% 
  mutate(RCP = ifelse(Model %in% c("GFDL26F1","IPSL26F1","MPI26F1"),"RCP 2.6","RCP 8.5")) %>%  # Assigns RCP by model
  filter(Species %in% IPHC_Species,
         INDEX %in% IPHC_Reg_DBEM_df$INDEX) %>%  #Selects only IPHC species within regulatory areas
  left_join(IPHC_Reg_DBEM_df,
            by = "INDEX") %>% # Include Regulatory areas
  gather("Year","MCP",`2005`:`2099`) %>% 
  group_by(RCP,RegArea,Year,Model) %>%
  summarise(Total_MCP = sum(MCP, na.rm = T)) %>% # Sums INDEX MCP per RegArea
  group_by(RCP,RegArea,Year) %>% 
  summarise(Mean_MCP = mean(Total_MCP, na.rm = T), #Yearly mean per ESM model
            SD_MCP = sd(Total_MCP, na.rm = )
  ) %>% 
  mutate(Year = as.numeric(Year))

# Changes in the proportion in comparrison of the mean (2004-2014) proportion ####

# Estimate total MCP of each RCP per year
Proportion_Total <- IPHC_Absolutes %>% 
  group_by(RCP,Year) %>% 
  summarise(
    Total = sum(Mean_MCP),
    Total_SD = sum(SD_MCP)
  )

# head(Proportion_Total)

# Estimates the proportion of each RegArea catch pero RCP and Year
Proportion_Change <- IPHC_Absolutes %>% 
  left_join(Proportion_Total,
            by = c("RCP","Year")) %>% 
  mutate(Proportion = (Mean_MCP/Total)*100)

# Todays proportion
Early_Proportion <- Proportion_Change %>% 
  filter(Year <= Beg_End) %>% 
  group_by(RCP,
           RegArea) %>% 
  summarise(Mean_Prop = mean(Proportion))

# Proportion change in the future (NOTE: not plotting by timeframe because of boxplot)
Proportion_Change <- IPHC_Absolutes %>% 
  left_join(Proportion_Total,
            by = c("RCP","Year")) %>% # Join with total MCP
  mutate(Proportion = (Mean_MCP/Total)*100) %>% # Get proportions
  left_join(Early_Proportion,
            by= c("RCP","RegArea")) %>% # Include baseline proportion
  mutate(Change = Proportion/Mean_Prop) %>%  # devide future changes by baseline
  mutate(Percentage = round(-(1-Change)*100,2),
         Year = as.numeric(Year)) %>% 
  arrange(RCP) %>% 
   mutate(Time_Step = ifelse(Year >= Mid_In & Year <= Mid_End,"Mid Century",
                            ifelse(Year >= End_In,"End Century","NA")),
          Nation = ifelse(RegArea == "2A","US Contiguous",
                          ifelse(RegArea == "2B","Canada","Alaska")
                          )
          ) %>% 
  filter(Time_Step != "NA",
         RegArea != "NA",
         Time_Step == "End Century")

Proportion_Change$RegArea <- gsub("2B","2B",Proportion_Change$RegArea)

#### Option all in one####
PL <- ggplot(subset(Proportion_Change, RCP == "RCP 2.6"),
         aes(
           x = reorder(RegArea,Percentage, FUN = median), # from forcasts` package
           # x = Nation, # from forcasts` package
             y = Percentage,
             # fill = Nation,
           colour = Nation
         )
  ) +
  geom_boxplot() +
  ylab("") +
  xlab ("") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  ggtheme_plot() +
  # scale_fill_brewer("Region",palette = "Set2") +
  scale_colour_brewer("Region",palette = "Set2") +
  theme(legend.position = c(0.2, 0.98),
        legend.direction = "horizontal") #+ 
  # geom_label(data=Proportion_Change, aes(label = "RCP 2.6", x = "2A" , y = 18, fill = NA), #RCP labels for grid plot
  #            colour = "blue",
  #            show.legend = FALSE,
  #            size = 5
  # )

PH <- ggplot(subset(Proportion_Change, RCP == "RCP 8.5"),
         aes(
           x = reorder(RegArea,Percentage, FUN = median), # from forcasts` package
           # x = Nation, # from forcasts` package
             y = Percentage,
             # fill = Nation,
           colour = Nation
         )
  ) +
  geom_boxplot() +
  ggtheme_plot() +
  ylab("") +
  xlab ("IPHC Regulatory Area") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  ggtheme_plot() +
  # scale_fill_brewer("Region",palette = "Set2",guide=FALSE) + 
  scale_colour_brewer("Region",palette = "Set2",guide=FALSE) #+
  # geom_label(data=Proportion_Change, aes(label = "RCP 8.5", x = "3B" , y = 18, fill = NA), #RCP labels for grid plot
  #            colour = "red",
  #            show.legend = FALSE,
  #            size = 5
  # )

ggdraw() +
  draw_plot(PL, x = 0, y = 0.5, width = 1, height = 0.5) +
  draw_plot(PH, x = 0, y = 0, width = 1, height = 0.5) +
  draw_plot_label(label = c("A", "B"), size = 15,
                  x = c(0, 0), 
                  y = c(1, 0.5)) +
  draw_plot_label(label = "Stock-Share Percentage Change", size = 12, angle = 90, fontface = "plain",
                  x = 0.02,
                  y =0.11999)

### OLD VERION GOM

#### Old analysis ##3
Mean_Data_GoM <- Atlantic_DBEM %>% 
  mutate(RCP = ifelse(Model %in% c("GFDL26F1","IPSL26F1","MPI26F1"),"RCP 2.6","RCP 8.5")) %>%
  tidyr::gather("Year","Change",`2005`:`2099`) %>%
  mutate(# Indicate the three period times
    Period = ifelse(Year >= 2005 & Year <= 2014,"Today",
                    ifelse(Year >= 2046 & Year <= 2055,"Mid Century",
                           ifelse(Year >= 2090 & Year <= 2099,"End Century",
                                  "Other_Years"))
    )
  ) %>% 
  filter(Period != "Other_Years") %>% # Remove unwanted years
  group_by(INDEX,Model,RCP,Period,Species) %>%
  summarise(
    Mean_Temp = mean(Change, na.rm = T), # Temporal mean
    SD_Temp = sd(Change, na.rm = T) #Temporal sd
  ) %>% 
  group_by(INDEX,RCP,Period,Species) %>% # Models (GFDL,IPSL,MPIs) mean and SD
  summarise(
    Mean_M = mean(Mean_Temp, na.rm = T),
    SD_M = sd(Mean_Temp, na.rm = T)
  ) %>% 
  filter(!is.na(SD_M)) %>% 
  mutate(Robust = ifelse((SD_M*2) > Mean_M,"No agreement","Agree"))  %>% # Flags robustness in data
  filter(Robust > 0) %>%
  select(INDEX,Species,RCP,Period,Mean_M) %>% # They all agree except for 4D mid century
  spread(Period,Mean_M) %>% 
  mutate( # Estimate the percentage change
    Change_Mid = `Mid Century`/Today,
    Change_End = `End Century`/Today,
    Percentage_Mid = ifelse(round(-(1-Change_Mid)*100) > 100, 100,round(-(1-Change_Mid)*100)),
    Percentage_End = ifelse(round(-(1-Change_End)*100) > 100, 100,round(-(1-Change_End)*100))
    ) %>% 
  select(INDEX, Species, RCP, Percentage_Mid,Percentage_End) %>% 
    left_join(GB_Coor,
            by ="INDEX")

#   mutate("Percentage Change" = ifelse(Percentage > 100, 100,Percentage)) %>%  # set everything over 100 to 
#   filter(!is.na(Longitude)) %>% 
#   filter(Latitude <= 50)

Mean_Data_GoM$Bins <- cut(Mean_Data_GoM$Mid_Century,breaks = 4)
# unique(Mid_Century$Bins)

# _______________________________________________________

# The plot 
Seq <- seq(-100,100,10)

Lim_Neg <- min(Seq)
Lim_Max <- max(Seq)

# Use bins and collors yellow orange light red and dark red

# Mean_Data_GoMb <- Mean_Data_GoM %>% # In case you want filter a specific species
#   filter(Species == "Limanda ferruginea")

ggplot() +
  geom_tile(data = Mean_Data_GoM,
            aes(
              x = Longitude,
              y = Latitude,
              fill = Percentage_Mid,
              colour = Percentage_Mid
              # fill = reorder(Bins,-Percentage),
              # colour = reorder(Bins,-Percentage)
            )
  ) +
  # scale_color_manual("MCP % Change",values=c("darkblue","lightblue","red","darkred")) + # for Bins option A
  # scale_fill_manual("MCP % Change",values=c("darkblue","lightblue","red","darkred")) + # for Bins option A
  # scale_color_brewer("MCP % Change",type='seq', palette='Reds') + # for Bins option B
  # scale_fill_brewer("MCP % Change",type='seq', palette='Reds') + # for Bins option B
  scale_fill_gradient2("MCP Percentage Change \n(2046-2055)", # If not using the bins
                       limits=c(Lim_Neg,
                                Lim_Max),
                       breaks = Seq,
                       na.value = 'darkred' # NA values are present when the species is no more 
  ) +
  scale_colour_gradient2("MCP Percentage Change \n(2046-2055)",
                         limits=c(Lim_Neg,
                                  Lim_Max),
                         breaks = Seq,
                         na.value = 'darkred' # NA values are present when the species is no more
  ) +
  # geom_label(data = Mean_Data_GoMb,
  #            aes(
  #              x = Longitude,
  #              y = Latitude,
  #              label = INDEX
  #            )
  # ) +
  geom_sf(data = GM_Land, colour = "lightgrey") +
  geom_sf(data = eez_GM, fill = NA) +
  annotate("text", label = "United States", x = -70, y = 45, size = 4, colour = "black") +
  annotate("text", label = "Canada", x = -66.8, y = 45.4, size = 4, colour = "black") +
  annotate("text", label = "Canada", x = -65.4, y = 44.2, size = 4, colour = "black") +
  coord_sf(xlim = c(-71.0592, -63.33333),
           ylim = c(41,45.5)
  ) +
  ggtheme_map() +
  theme(
    axis.line = element_line(colour = "black", size = .5),
    axis.ticks = element_line(size = .5),
    axis.text.x = element_text(size = 12,
                               angle = 0,
                               face = "plain"),
    axis.text.y = element_text(size = 12),
    legend.key = element_rect(size = 3),
    legend.key.width =unit(8,"line"),
    legend.title = element_text(size = 20),
    legend.text = element_text(size = 18)
  ) +
  facet_wrap(~RCP + Species, 
             ncol = 3
  )

Name = paste("Change_GB_26_85_2050.png",sep="_")

ggsave(Name,
       plot = last_plot(),
       width = 20,
       height = 10,
       units = "in",
       path = Path)

```

```{r IPHC_Proportion_EEZ, eval=F, echo = F, message=F, warning=F}

Path <- "/Users/jpalacios/Documents/UBC/Oceans_Project/Manuscript/Results"
# names(DBEM_Results)

IPHC_Species <- c(
  "Anoplopoma fimbria",  # Sablefish
  "Hippoglossus stenolepis" # Halibut
)

#### FIlter EEZs ###

EEZs <- c(
  "Canada (Pacific)",
  "USA (West Coast)",
  # "USA (Alaska, Arctic)",
  "USA (Alaska, Subarctic)"
)

RCP <- c("GFDL26F1","IPSL26F1","MPI26F1")

EEZsID <- EEZIDs_List %>% 
  filter(Name %in%EEZs) %>% 
  left_join(EEZ_CellID,
            by = "EEZID")

names(EEZsID)[3] <- "INDEX"
# 
# head(EEZsID)
# head(EEZIDs_List)
# unique(EEZsID$Name)

IPHC_Absolutes <- DBEM_Results %>% 
  filter(Species %in% IPHC_Species) %>%  #Selects only IPHC species
  filter(INDEX %in% EEZsID$INDEX) %>% # Inside EEZ
  left_join(EEZsID,
            by = "INDEX",
            all = FALSE) %>%
  # filter(!duplicated(.)) %>% 
  gather("Year","MCP",2:96) %>%  # Removes duplicated
  mutate(RCP = ifelse(Model %in% RCP, "RCP 2.6","RCP 8.5"),
         Nation = ifelse(grepl('Alaska',Name),"Alaska",Name)) %>% 
  group_by(Model,RCP,Nation,Year) %>%
  summarise(Total_MCP = sum(MCP, na.rm = T)) %>% # Sums MCP per EEZ
  group_by(RCP,Nation,Year) %>% 
  summarise(Mean_MCP = mean(Total_MCP, na.rm = T), #Mean per ESM model
            SD_MCP = sd(Total_MCP, na.rm = )
  ) %>% 
  mutate(Year = as.numeric(Year))

# Changes in the proportion in comparrison of the mean (2004-2014) proportion ####

Proportion_Total <- IPHC_Absolutes %>% 
  group_by(RCP,Year) %>% 
  summarise(
    Total = sum(Mean_MCP),
    Total_SD = sum(SD_MCP)
  )

# head(Proportion_Total)

Proportion_Change <- IPHC_Absolutes %>% 
  left_join(Proportion_Total,
            by = c("RCP","Year")) %>% 
  mutate(Proportion = (Mean_MCP/Total)*100)

Early_Proportion <- Proportion_Change %>% 
  filter(Year <= 2014) %>% 
  group_by(RCP,
           Nation) %>% 
  summarise(Mean_Prop = mean(Proportion))

Proportion_Change <- IPHC_Absolutes %>% 
  left_join(Proportion_Total,
            by = c("RCP","Year")) %>% 
  mutate(Proportion = (Mean_MCP/Total)*100) %>% 
  left_join(Early_Proportion,
            by= c("RCP",
                  "Nation")) %>% 
  mutate(Change = Proportion/Mean_Prop) %>% 
  mutate(Percentage = round(-(1-Change)*100,2)) %>% 
  arrange(RCP)

#### The actual plot ####

ggplot(Proportion_Change) +
  aes(x = Year,
      y = Percentage,
      color = Nation) +
  geom_line() +
  # geom_smooth(method = "lm", se = TRUE) +
  ylim(-15,10)+
  ylab("Percentage Change")+
  facet_wrap(~RCP,
             nrow = 1
             # scales = "free_y"
  ) +
  scale_colour_manual(
    values = c("purple","red","blue"),
    labels = c("Alaska", "Canada", "US")
  )+
  geom_hline(yintercept = 0) +
  theme_classic()+
  theme(plot.title=element_blank(), #clears title
        panel.background=element_blank(), #clears background 
        axis.text.x=element_text(size=20), # Size of axis labels
        axis.text.y =element_text(size=20), # Size of axis labels
        axis.title=element_text(size=20), # Size of axis title
        axis.title.x = element_text(vjust = .5), # Alignment of axis title
        # axis.ticks = element_blank(), # Removes axis ticks
        # axis.line = element_blank(), # Removes axis line,
        legend.position = "top", # bottom, top, right, left
        # legend.key = element_rect(size = 15), # Legend box size
        # legend.key.height =unit(1,"line"),
        # legend.key.width =unit(1,"line"),
        legend.background = element_rect(),
        legend.text = element_text(size = 18), #Legend text size
        legend.title = element_blank(), # Legend title size
        strip.background = element_blank(), #Facewrap options
        strip.text = element_text(size = 20)
  )

# Save figure

# ggsave("Fig3.png",
#        plot = last_plot(),
#        width = 12,
#        height = 6,
#        units = "in",
#        path = Path)

### Box plot ###

Proportion_Change %>% 
  mutate(Time_Step = ifelse(Year >= 2046 & Year <= 2055,"Mid Century",
                            ifelse(Year >= 2089,"End Century","NA"))) %>% 
  filter(Time_Step != "NA") %>% 
  ggplot(.,
         aes(x = fct_rev(Time_Step), # from forcasts` package
             y = Percentage,
             fill = Nation
         )
  ) +
  geom_boxplot() +
  ylab("Percentage Change") +
  xlab ("Time Step") +
  facet_wrap(~RCP,
             nrow = 1#,
             # scales = "free_y"
  ) +
  scale_fill_manual(
    values = c("purple","red","blue"),
    labels = c("Alaska", "Canada", "US")
  )+
  geom_hline(yintercept = 0) +
  theme_classic() +
  theme(plot.title=element_blank(), #clears title
        panel.background=element_blank(), #clears background 
        axis.text.x=element_text(size=20), # Size of axis labels
        axis.text.y =element_text(size=20), # Size of axis labels
        axis.title=element_text(size=20), # Size of axis title
        axis.title.x = element_text(vjust = .5), # Alignment of axis title
        # axis.ticks = element_blank(), # Removes axis ticks
        # axis.line = element_blank(), # Removes axis line,
        legend.position = "top", # bottom, top, right, left
        # legend.key = element_rect(size = 15), # Legend box size
        # legend.key.height =unit(1,"line"),
        # legend.key.width =unit(1,"line"),
        legend.background = element_rect(),
        legend.text = element_text(size = 18), #Legend text size
        legend.title = element_blank(), # Legend title size
        strip.background = element_blank(), #Facewrap options
        strip.text = element_text(size = 20)
  )

```

```{r GB_Results_All, eval=F, echo = F}

#### Filter Species  ####

Atlantic_Species <- c(
  "Gadus morhua",  # Cod
  "Limanda ferruginea", # Yellowtail flounder
  "Melanogrammus aeglefinus"
)

# Run Spatial chuck for the Atlantic
# NAFO_5z$geometry

Atlantic_DBEM <- DBEM_Results %>% 
  filter(Species %in% Atlantic_Species) %>% 
  filter( # Limit the area to George's bank
    Latitude < 45.9759, # North
    Latitude > 35, # South 
    Longitude > -71.0592, # West
    Longitude < -63.33333
  )

# Path for saving plots
Path <- "/Users/jpalacios/Documents/UBC/Oceans_Project/Manuscript/Results/GB/All"

### MCP Change Analysis ####

for(r in 1:2){

  if(r == 1){
    RCP = c("GFDL26F1","IPSL26F1","MPI26F1") #Low RCP
  }else{
    RCP = c("GFDL85F1","IPSL85F1","MPI285F1") #High RCP
  }

  # Mean for each cel from 2004-2014
  Mean_Data <- Atlantic_DBEM %>% 
    filter(Model %in% RCP) %>% 
    group_by(INDEX,
             Model) %>% 
    summarise_at(vars(`2005`:`2099`), sum,na.rm=T) %>% 
    select(INDEX,`2005`:`2014`) %>% 
    group_by(INDEX) %>% 
    summarise_at(vars(`2005`:`2014`), mean,na.rm=T) %>% 
    mutate(Mean = rowMeans(.[,2:11])) %>%
    # mutate(SD = rowSds(.[,2:11])) %>%
    select(INDEX,Mean) %>% 
    arrange(INDEX)

  #The future
  Future <- Atlantic_DBEM %>% 
    filter(Model %in% RCP) %>% 
    group_by(INDEX,
             Model) %>% 
    summarise_at(vars(`2005`:`2099`), sum,na.rm=T) %>% 
    group_by(INDEX) %>% 
    summarise_at(vars(`2015`:`2099`), mean,na.rm=T) %>% 
    arrange(INDEX)

  # #Devide one by the other
  Cell_Index <- sweep(Future[2:86],#Future catch p.
                      1, #1 goes by row and 2 goes by colum
                      Mean_Data$Mean, #the means
                      "/") %>% 
    mutate(INDEX = Future$INDEX) %>% 
    select(INDEX,everything()) %>% 
    left_join(GB_Coor, #And now we include Lat-Long
              by="INDEX")

  Mid_Century <- Cell_Index %>% 
    select(INDEX,
           `2046`:`2055`) %>% 
    mutate(Mean = rowMeans(.[,2:11])) %>% 
    left_join(GB_Coor,
              by ="INDEX") %>% 
    mutate(Percentage = round(-(1-Mean)*100)) %>% # Convert to percentage
    mutate("Percentage Change" = ifelse(Percentage > 100, 100,Percentage)) %>%  # set everything over 100 to 
    filter(!is.na(Longitude)) %>% 
    filter(Latitude <= 50)

  Mid_Century$Bins <- cut(Mid_Century$Percentage,breaks = 5)

  # _______________________________________________________

  # The plot

  # Lim_Neg <- min(Seq)
  # Lim_Max <- max(Seq)

  ggplot() +
    geom_tile(data = Mid_Century,
              aes(
                x = Longitude,
                y = Latitude,
                # fill = Percentage,
                # colour = Percentage
                fill = reorder(Bins,-Percentage),
                colour = reorder(Bins,-Percentage)
              )
    ) +
    scale_color_brewer("MCP % Change",type='seq', palette='Reds') +
    scale_fill_brewer("MCP % Change",type='seq', palette='Reds') +
    # scale_fill_gradient2(limits=c(Lim_Neg, # If not using the bins
    #                               Lim_Max),
    #                      breaks = Seq#,
    #                      ) +
    # scale_colour_gradient2(limits=c(Lim_Neg,
    #                                 Lim_Max),
    #                        breaks = Seq#,
    #                        ) +
    geom_sf(data = GM_Land, colour = "lightgrey") +
    geom_sf(data = eez_GM, fill = NA) +
    annotate("text", label = "United States", x = -70, y = 45, size = 4, colour = "black") +
    annotate("text", label = "Canada", x = -66.7, y = 45.4, size = 4, colour = "black") +
    annotate("text", label = "Canada", x = -65.4, y = 44.2, size = 4, colour = "black") +
    coord_sf(xlim = c(-71.0592, -63.33333),
             ylim = c(40.5,45.5)
    ) +
    ggtheme_map() +
    theme(
      axis.line = element_line(colour = "black", size = .5),
      axis.ticks = element_line(size = .5),
      axis.text.x = element_text(size = 12,
                                 angle = 0,
                                 face = "plain"),
      axis.text.y = element_text(size = 12)
    )

  if(r == 1){
    Name = paste("Change_GB_26_2050.png")
  }else{
    Name = paste("Change_GB_85_2050.png")
  }

  ggsave(Name,
         plot = last_plot(),
         width = 8,
         height = 7,
         units = "in",
         path = Path)

  ### now we average the results from the models for END century ###

  End_Century <- Cell_Index %>% 
    select(INDEX,
           `2090`:`2099`) %>% 
    mutate(Mean = rowMeans(.[,2:11])) %>% 
    left_join(GB_Coor,
              by ="INDEX")%>% 
    mutate(Percentage = round(-(1-Mean)*100)) %>% # Convert to percentage
    mutate("Percentage Change" = ifelse(Percentage > 100, 100,Percentage)) %>% # set everything over 100 to 100
    filter(!is.na(Longitude)) %>% 
    filter(Latitude <= 50)

  End_Century$Bins <- cut(End_Century$Percentage,breaks = 5)

  # _______________________________________________________

  # The plot

  ggplot() +
    geom_tile(data = End_Century,
              aes(
                x = Longitude,
                y = Latitude,
                # fill = Percentage,
                # colour = Percentage
                fill = reorder(Bins,-Percentage),
                colour = reorder(Bins,-Percentage)
              )
    ) +
    scale_color_brewer("MCP % Change",type='seq', palette='Reds') +
    scale_fill_brewer("MCP % Change",type='seq', palette='Reds') +
    # scale_fill_gradient2(limits=c(Lim_Neg, # If not using the bins
    #                               Lim_Max),
    #                      breaks = Seq#,
    #                      ) +
    # scale_colour_gradient2(limits=c(Lim_Neg,
    #                                 Lim_Max),
    #                        breaks = Seq#,
    #                        ) +
    geom_sf(data = GM_Land, colour = "lightgrey") +
    geom_sf(data = eez_GM, fill = NA) +
    annotate("text", label = "United States", x = -70, y = 45, size = 4, colour = "black") +
    annotate("text", label = "Canada", x = -66.7, y = 45.4, size = 4, colour = "black") +
    annotate("text", label = "Canada", x = -65.4, y = 44.2, size = 4, colour = "black") +
    coord_sf(xlim = c(-71.0592, -63.33333),
             ylim = c(40.5,45.5)
    ) +
    ggtheme_map() +
    theme(
      axis.line = element_line(colour = "black", size = .5),
      axis.ticks = element_line(size = .5),
      axis.text.x = element_text(size = 12,
                                 angle = 0,
                                 face = "plain"),
      axis.text.y = element_text(size = 12)
    )

  if(r == 1){
    Name_End = paste("Change_GB_26_2100.png")
  }else{
    Name_End = paste("Change_GB_85_2100.png")
  }

  ggsave(Name_End,
         plot = last_plot(),
         width = 6,
         height = 5,
         units = "in",
         path = Path)

} # Close overall production loop

### Proportion change gom

#### Filter EEZs ###

GB_Absolutes <- Atlantic_DBEM %>%
  mutate(RCP = ifelse(Model %in% c("GFDL26F1","IPSL26F1","MPI26F1"),"RCP 2.6","RCP 8.5")) %>%  # Assigns RCP by model
  filter(Species %in% Atlantic_Species,
         INDEX %in% GB_Coor$INDEX) %>%  #Selects only IPHC species within regulatory areas
  left_join(EEZsID,
            by = "INDEX") %>% 
  gather("Year","MCP",`2005`:`2099`) %>%
  group_by(RCP,Name,Year,Model,Species) %>%
  summarise(Total_MCP = sum(MCP, na.rm = T)) #%>% # Sums INDEX MCP per EEZ
  # group_by(RCP,Name,Year,Species) %>%
  # summarise(Mean_MCP = mean(Total_MCP, na.rm = T), #Yearly mean per ESM model
  #           SD_MCP = sd(Total_MCP, na.rm = )
  # )

# Changes in the proportion in comparrison of the mean (2004-2014) proportion ####

Proportion_Total <- GB_Absolutes %>% 
  group_by(RCP,Year,Species,Model) %>% 
  summarise(
    Total = sum(Total_MCP)
  )

# head(Proportion_Total)

Proportion_Change <- GB_Absolutes %>% 
  left_join(Proportion_Total,
            by = c("RCP","Year","Species","Model")) %>% 
  mutate(Proportion = (Total_MCP/Total)*100)

Early_Proportion <- Proportion_Change %>% 
  filter(Year <= 2014) %>% 
  # group_by(RCP,
  #          Name) %>%
  group_by(RCP,Name,Species,Model) %>%  # Species test
  summarise(Mean_Prop = mean(Proportion))

Proportion_Change <- GB_Absolutes %>% 
  left_join(Proportion_Total,
            by = c("RCP","Year","Species","Model")) %>% 
  mutate(Proportion = (Total_MCP/Total)*100) %>% 
  left_join(Early_Proportion,
            by= c("RCP",
                  "Name",
                  "Species",
                  "Model")) %>% 
  mutate(Change = Proportion/Mean_Prop) %>% 
  mutate(Percentage = round(-(1-Change)*100,2)) %>% 
  arrange(RCP)

#### The actual plot ####

### Box plot ###

PL <- Proportion_Change %>% 
  mutate(Time_Step = ifelse(Year >= 2046 & Year <= 2055,"Mid Century",
                            ifelse(Year >= 2089,"End Century","NA"))) %>% 
  filter(Time_Step == "Mid Century",
         RCP == "RCP 2.6") %>% 
  ggplot(.,
         aes(
           # x = Species,
             x = reorder(Species,Percentage, FUN = median), # from forcasts` package
             # x = (Time_Step), # from forcasts` package
             y = Percentage,
             fill = Name
         )
  ) +
  geom_boxplot() +
  ylab("") +
  xlab ("") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  ggtheme_plot() +
   ylim(-10, 10) +
scale_fill_brewer("Region",palette = "Set2") + 
  geom_label(data=Proportion_Change, 
             aes(label = "RCP 2.6",
                 x = "Melanogrammus aeglefinus", 
                 y = 10,
                 fill = NA), #RCP labels for grid plot
             colour = "blue",
             show.legend = FALSE,
             size = 5,
             hjust = 1.5
  ) +
  theme(legend.position = c(0.2, 0.98),
        legend.direction = "horizontal",
        axis.text.x = element_text(size = 10,
                               angle = 0,
                               face = "italic")
  )

PH <- Proportion_Change %>%
  mutate(Time_Step = ifelse(Year >= 2046 & Year <= 2055,"Mid Century",
                            ifelse(Year >= 2089,"End Century","NA"))) %>% 
  filter(Time_Step == "Mid Century",
         RCP == "RCP 8.5") %>% 
  ggplot(.,
         aes(
           # x = Species,
             x = reorder(Species,Percentage, FUN = median), # from forcasts` package
             # x = (Time_Step), # from forcasts` package
             y = Percentage,
             fill = Name
         )
  ) +
  geom_boxplot() +
  ylab("") +
  xlab ("") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  ggtheme_plot() +
  theme(
         axis.text.x = element_text(size = 10,
                               angle = 0,
                               face = "italic")
  ) +
scale_fill_brewer("Region",palette = "Set2",guide=FALSE) + 
  geom_label(data=Proportion_Change, aes(label = "RCP 8.5", x = "Melanogrammus aeglefinus", y = 10, fill = NA), #RCP labels for grid plot
             colour = "red",
             show.legend = FALSE,
             size = 5,
             hjust = 1.5
  )

ggdraw() +
  draw_plot(PL, x = 0, y = 0.5, width = 1, height = 0.5) +
  draw_plot(PH, x = 0, y = 0, width = 1, height = 0.5) +
  draw_plot_label(label = c("A", "B"), size = 15,
                  x = c(0, 0), 
                  y = c(1, 0.5)) +
  draw_plot_label(label = "Stock-share percentage change",
                  size = 12, angle = 90, fontface = "plain",
                  x = 0.02,
                  y =0.11999)

ggsave("Fig6.png",
       plot = last_plot(),
       width = 8,
       height = 6,
       units = "in",
       path = Path)

```

### 2019-09-14 Econ_Analysis/Econ_Analysis.Rmd
Migrated documents to github

---
title: "Econ Analysis"
author: "Juliano Palacios-Abrantes"
date: 
output:
  word_document: default
---

This document presents the methods and results for the paper Sumaila *et al* (NA) *Climate change, shifting threat points and the management of transboundary fish stocks* published as part of the special issue *Transboundary fish-stocks of North America under Climate Change* in the journal *Ecology and Society*.

```{r setup, eval=T, echo=F, warning=F,message=F, results='hide'}

#### READ ME !!! ####
# Run this chunk before knit so you make sure you have all pkgs installed in R

ipak <- function(pkg){
  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
  if (length(new.pkg)) 
    install.packages(new.pkg, dependencies = TRUE,repos = "http://cran.us.r-project.org")
  sapply(pkg, require, character.only = TRUE)
}

#### Library ####
packages <- c(
  "readxl", # Read dataframe
  "dplyr", # Data manipulation
  "tidyr", # Data manipulation
  "magrittr", # For roll mean
  "ggplot2", #Nice grpahs and spatial analysis
  "cowplot",
  "rgdal",
  "RColorBrewer",
  "wesanderson",
  "zoo", # for rollmean
  "knitr",
  "kableExtra",
  "stringr",
  "data.table",
  "ggrepel",
  "gridExtra",
  "ggmap",
  "rgeos",
  "sf",
  "sp",
  "rgdal", #Spatial analysis 
  "tools", #Spatial analysis 
  "png", # For reading plots in chunk codes
  "grid", # For reading plots in chunk codes
  "rphylopic" #Get silhouettes of organisms from Phylopic.
)

ipak(packages)

##________________________________________________##

# source("/Users/jpalacios/Documents/UBC/Oceans_Project/Distribution/Functions/DBEM_imp_F.R") #Imports a single species

ggtheme_plot <- function() {
  theme(
    plot.title = element_text(size = rel(1), hjust = 0, face = "bold"),
    panel.background = element_blank(),
    strip.background = element_blank(),
    # strip.text       = element_text(size = base_size, face = "italic"),
    panel.border     = element_blank(),
    panel.grid.minor = element_blank(),
    panel.grid.major = element_blank(),
    axis.ticks = element_blank(),
    axis.text.x = element_text(size = 10,
                               angle = 0,
                               face = "plain"),
    axis.text.y = element_text(size = 12),
    axis.title = element_text(size = 14),
    legend.key = element_rect(colour = NA, fill = NA),
    legend.position  = "top",
    legend.title = element_text(size = 16),
    legend.text = element_text(size = 14),
    strip.text.x = element_text(size = 18, colour = "darkgrey"),
    strip.text = element_text(size = 18)
  )
}

ggtheme_map <- function(base_size = 9, Region = "NA") {

  theme(text             = element_text(#family = "Helvetica",
    color = "gray30", size = base_size),
    plot.title       = element_text(size = rel(1.25), hjust = 0, face = "bold"),
    panel.background = element_blank(),
    panel.border     = element_blank(),
    panel.grid.minor = element_blank(),
    panel.grid.major = element_line(color = "transparent"),
    strip.background =element_rect(fill = "transparent"),
    strip.text.x = element_text(size = 18, colour = "black",face= "bold.italic", angle = 0),
    axis.line        = element_blank(), # element_line(colour = "grey30", size = .5))
    axis.ticks       = element_blank(),
    axis.text        = element_blank(),
    axis.title       = element_blank(),
    # legend.key       = element_rect(colour = NA, fill = NA, size = 4),
    legend.position = "bottom"#,
    # legend.key.width =unit(6,"line")
  )
}

### Determine years of analysis

# Current time
Beg_In <- 2005
Beg_End <- 2014

# Mid century
Mid_In <- 2041 # 2046
Mid_End <- 2060

# End Century
End_In <- 2080 # 2090
End_End <- 2099

```

# Methods

## Study Area and Fisheries

The current study focuses on five transboundary fisheries jointly managed by Canada and the US for both the Atlantic and the Pacific coasts (**Table X**). The analysis was carried out within the 200 nautical miles of both nation's EEZ from the Gulf of Mexico to The Labrador Sea in the Atlantic, and from California to Chukchi Sea, in the Pacific coast. Subsets of the total area were carried for the Gulf of Maine agreement according to NAFO's divisions 5Y, 5Ze, and 4X within latitudes 46.2°N and 41.5°S, and longitudes -72°W and -64°E. For the IPHC, we considered Alaska as a separate entity, the US contiguous states as a second one (Washington, Oregon and California), and lastly British Columbia (Canada).

<!-- Methods notes -->
- Right now we are subsetting the GoM-NAFO areas in a square-shape polygon according to the coordinates set (46.2°N and 41.5°S, and longitudes -72°W and -64°E). This method inclues all the way to the easter sinde of Georges Bank, however, it also inclueds waters > 200m (because is a square). We could filter those areas out using the data of [The Gulf of Maine Counsil](http://www.gulfofmaine.org/2/committees-and-programs/gulf-of-maine-mapping-initiative/image-library/).

## Data

### DBEM MCP Data

This chunk loads the DBEM data (previouslly obtained with function `dbem_import()`) and filters out the 4 species analyzed and the IPHC and GoM regions.

```{r Load_DBEM_Data, echo = F, eval = T, results='hide', warning=F,message=F}

###____________ Load Spatial Data____________#
# List of DBEM INDEX within the EEZ
#Data provided by Vicki Lam

EEZIDs_List <- read_excel("~/Documents/UBC/Oceans_Project/Distribution/By Cell/Cell_Data/Updated_EEZList_17June2016.xlsx")

EEZ_CellID <- read_excel("~/Documents/UBC/Oceans_Project/Distribution/By Cell/Cell_Data/EEZ_CellID.xlsx")

colnames(EEZ_CellID) <- c("EEZID","INDEX")

# DBEM Coordinate system
Coor <- fread("~/Documents/UBC/Oceans_Project/Distribution/DBEM/Data/Lon_Lat_DBEM.txt",header = FALSE)
colnames(Coor) <- c("INDEX","Longitude","Latitude")

###____________ Load DBEM Data____________#

# From (/Users/jpalacios/Documents/UBC/Oceans_Project/Distribution/By Cell/By_Cell_Analysis.Rmd)
Raw_DBEM_Results <- data.table::fread("~/Documents/UBC/Oceans_Project/Manuscript/Data/Raw_Data.csv") %>% 
  filter(Species != "Anoplopoma fimbria") #Remove

###____________Subset DBEM Data for specific region and Spp.____________#

#### All North America ####

EEZs <- c(
  "Canada (Arctic)",
  "Canada (East Coast)",
  "Canada (Pacific)",
  "USA (East Coast)",
  "USA (West Coast)",
  "USA (Alaska, Arctic)",
  "USA (Alaska, Subarctic)"
)

All_EEZs <- EEZIDs_List %>% 
  filter(Name %in% EEZs) %>% 
  left_join(EEZ_CellID,
            by = "EEZID")

names(All_EEZs)[3] <- "INDEX"

# LAT LONG Corrections for Alaska (IPHC)

DBEM_Corrected <- Raw_DBEM_Results %>% 
  filter(INDEX %in% All_EEZs$INDEX) %>% 
  filter(Longitude > 0) %>% 
  mutate(Longitude = Longitude - 360)

DBEM_Corrected <- Raw_DBEM_Results %>% 
  filter(INDEX %in% All_EEZs$INDEX) %>% 
  filter(Longitude < 0) %>% 
  bind_rows(DBEM_Corrected)

### Get ridd of Pacific Species in NAFO (P.Halibut model ghost)

NAFO_E <- DBEM_Corrected %>% 
  filter(Longitude >= -100)

Pacific <- DBEM_Corrected %>% 
  filter(Treaty != "NAFO")

DBEM_Corrected <- NAFO_E %>% 
  bind_rows(Pacific)

### Get ridd of Atlantic Species in the Pacific (Just in case)

Pacific_Spp <- DBEM_Corrected %>% 
  filter(Longitude <= -100)

Atlantic <- DBEM_Corrected %>% 
  filter(Treaty == "NAFO")

### Final DBEM data corrected for species overlapping

DBEM_Corrected <- Pacific_Spp %>% 
  bind_rows(Atlantic)

#### Filter results within IPHC region and Gulf of Maine

# GoM Limits
N_Lim <- 46.2
S_Lim <- 41.5
W_Lim <- -72
E_Lim <- -64

EEZsID <- EEZIDs_List %>%
  filter(Name %in%EEZs) %>%
  left_join(EEZ_CellID,
            by = "EEZID")

# # GoM Region
GB_Coor <- Coor %>%
  filter(INDEX %in% EEZsID$INDEX) %>%
  # mutate(one = 1) %>%
  filter( # Limit the area to George's bank
    Latitude < N_Lim, # North
    Latitude > S_Lim, # South
    Longitude > W_Lim, # West
    Longitude < E_Lim
  )

## IPHC Region

Study_Region <- DBEM_Corrected %>%
  filter(Species == "Hippoglossus stenolepis") %>%  #Inlcude all of the INDEXEs from the IPHC
  group_by(INDEX) %>%
  summarise(n()) %>%
  bind_rows(GB_Coor) # Include those within the GOM

### Final DBEM data corrected for species overlapping and Regions
DBEM_Corrected <- DBEM_Corrected %>%
  filter(INDEX %in% Study_Region$INDEX)

# Filter treaties that we want to analyze

Selected_Species <- c("Hippoglossus stenolepis", # Pacific Halibut
                      "Merluccius productus", # Whiting
                      "Gadus morhua",  # Cod
                      "Limanda ferruginea", # Yellowtail flounder
                      "Melanogrammus aeglefinus" # Haddock
                      )

###_____Checkpoint Charly _____ #
# Double check distributions are limited to management areas

# DBEM_Corrected %>%
#   filter(Species %in% Selected_Species) %>%
#   left_join(Coor,
#             by = "INDEX") %>%
#   ggplot(.,
#          aes(
#            x = Longitude.y,
#            y = Latitude.y,
#            fill = log(INDEX)
#          )
#          ) +
#   geom_tile() +
#   facet_wrap(~Species)

# All good
###_____ End Checkpoint Charly _____#

```

```{r Clean_DBEM, eval = T, echo=F}

# This table provides the percentage change in MCP for each species, EEZ and RCP as well as the percentage change in Stock-share ratio.

###________ Variables needed_________#

# To separate RCPs 2.6 and 8.5
RCP <- c("GFDL26F1","IPSL26F1","MPI26F1")

# The Regions we need for the data
Selected_Areas <- EEZIDs_List %>% 
  filter(Name %in% EEZs)

### _______ Estimate MCP data _______ #

### Including each GCM in the analysis

MCP_Data <- DBEM_Corrected %>%
  left_join(EEZ_CellID,
            by = "INDEX") %>% # Link each INDEX with the EEZ
  # head() %>%
  filter(EEZID %in% Selected_Areas$EEZID,
         Species %in% Selected_Species) %>% #Filter out other species and areas
  mutate( # determine what nation is wach region, what result is fr each RCP and Basin
    Nation = ifelse(EEZID >= 958, "USA W", # Alaska
                    ifelse(EEZID == 925,"Can W",
                           ifelse(EEZID == 851, "USA E",
                                  ifelse( EEZID== 848, "USA W",
                                          "Can E"))
                    )),
    RCP = ifelse(Model %in% RCP,"Low Emission","High Emission"), # determine which model is what RCP
    Basin = ifelse(Nation %in% c("USA E","Can E"),"Atlantic","Pacific")
  ) %>% 
  group_by(Species,Nation,Basin,RCP,Model) %>% # Adds each species' MCP of all INDEX-cells within each EEZ
  summarise_if(is.numeric,sum,na.rm=T) %>% # sum of values 
  gather("Year","MCP",`2005`:`2099`) %>% #Tiddy version
  select(-INDEX:-EEZID )

###__________ Checkpoint charly __________#
# unique(MCP_Data$Model)
# unique(MCP_Data$Species)
# unique(MCP_Data$Nation)

#  Looks good to me 
###__________ END Checkpoint charly __________#
```

### Fisheries landings data

For the present study we used reported landings (i.e. excluding discards) from the industrial fishing sector by fishing country (i.e. Canada, USA contiguous states or Alaska), fishing gear (i.e. hook and line or trawling) and species. Data for North Pacific hake (*Merluccius productus*), Atlantic cod (*Gadus morhua*), Yellowtail flounder (*Limanda ferruginea*), and Haddock (*Melanogrammus aeglefinus*) were provided by the Sea Around Us [@Zeller2016]. For the Pacific Halibut (*Hippoglossus stenolepis*), landing data was provided by the IPHC. All landing data was average between 2004 and 2014 for modelling consistency.

```{r Landings_Data, eval = T, echo=F}

#### Landings data ###

####_____ IPHC Data ####
# Data from IPHC https://iphc.int/data/commercialresearch-landing-weights-datasets
# Data in metric tonne
IPHC_Landings <- read_excel("~/Documents/UBC/Oceans_Project/Econ/Data/IPHC/iphc-19912017-commres.xlsx", 
                                    col_types = c("numeric", "text", "text", 
                                                  "numeric", "numeric", "numeric", 
                                                  "text"), skip = 2)
# Clean  landings

Clean_IPHC_Landings <- IPHC_Landings %>% 
  filter(Sector == "Commercial") %>% #Including only commercial fishing (excluding research)
  mutate(EEZ = ifelse(Regulatory_Area == "2B","Canada","USA"))%>% 
  group_by(Year,
           EEZ) %>% 
  summarise(
    Total_Landings = sum(`Net wt (metric tonne)`)
  ) %>% 
  filter(Year >= Beg_In & Year <= Beg_End) %>%
  group_by(EEZ) %>% 
  summarise(Avrg_Landings = mean(Total_Landings)) %>% # Average 10 years of landings data
  mutate(scientific_name = "Hippoglossus stenolepis", # Include information to match with econ data
         gear_type = "hook and line")

# head(Clean_IPHC_Landings)

####_____ GoM Data ####
# Data provided by the Sea Around us for the Gulf of Maine Marine Ecosystem (http://www.seaaroundus.org/data/#/meow/55?chart=catch-chart&dimension=taxon&measure=tonnage&limit=10). DATA IN TONNES

# 
GoM_Landings <- read.csv("~/Documents/UBC/Oceans_Project/Econ/Data/SAU_Landings/GoM/SAU MEOW 55 v47-1.csv")

Clean_GoM_Landings <- GoM_Landings %>% 
  filter(
    scientific_name %in% Selected_Species,
    fishing_sector == "Industrial", # Remove other sectors
    reporting_status == "Reported", # Only reported data
    catch_type == "Landings", # Only landings
    fishing_entity != "Russian Federation" # some very small landings by Russians
    ) %>% 
  group_by(year,scientific_name,fishing_entity,gear_type) %>% 
  summarise(Total_Landings = sum(tonnes)) %>% 
  filter(year >= Beg_In & year <= Beg_End) %>% 
  group_by(EEZ=fishing_entity,scientific_name,gear_type) %>% 
  summarise(Avrg_Landings = mean(Total_Landings)) %>% 
  filter(EEZ %in% c("Canada","USA"))

# head(Clean_GoM_Landings)

##### _____ Whiting  ####
# Not using it for now

# Whiting_Landings <- read.csv("~/Documents/UBC/Oceans_Project/Econ/Data/SAU_Landings/Hake/SAU Taxa 600326 v47-1.csv")
# 
# Clean_Whiting_Landings <- Whiting_Landings %>% 
#   filter(
#     scientific_name %in% Selected_Species,
#     fishing_sector == "Industrial", # Remove other sectors
#     # reporting_status == "Reported", # Only reported data
#     catch_type == "Landings" # Only landings
#     ) %>% 
#   group_by(year,scientific_name,fishing_entity,gear_type) %>% 
#   summarise(Total_Landings = sum(tonnes)) %>% 
#   filter(year >= 2005 & year <= 2014) %>% 
#   group_by(EEZ=fishing_entity,scientific_name,gear_type) %>% 
#   summarise(Avrg_Landings = mean(Total_Landings))

####_____ Joind Landings Data ####
# Join all data and projecting according to DBEM changes

Landings_Data <- Clean_GoM_Landings %>% 
  bind_rows(
    # Clean_Whiting_Landings,
    Clean_IPHC_Landings
  ) %>% 
  rename(Species = scientific_name)

###___ Checkpoint Charly __________ #

# Checking data
# SSR_Change %>%
#   left_join(Landings_Data,
#             by = c("Species","EEZ")) %>%
#   View(.)

###_____END Checkpoint Charly _____ #

```

### Fisheries economics data

Two main fisheries economics databases were used to estimate landings profit between `r Beg_In` and `r Beg_End`. For fish selling price (ex-vessel) we used data provided by Travis Tai published on Tai *et al.* (2017); for fishing cost we used data provided by Vicky Lam published as Lam *et al.* (2011) and converted it to 2010 real USD.

```{r Economics_Data, eval = T, echo=F}

# Fishing cost Data ####
# Data provided by Vicky Lam in Real 2005 USD

Fishing_Cost <- read_excel("~/Documents/UBC/Oceans_Project/Econ/Data/Economic/FishingCost_USA_Canada_20Feb2017.xlsx", 
                           col_types = c("text", "text", "text", 
                                         "numeric", "numeric", "numeric", 
                                         "numeric", "numeric", "numeric", 
                                         "numeric", "numeric", "numeric", 
                                         "numeric", "numeric", "numeric", 
                                         "numeric", "numeric"), 
                           skip = 1)

# Fishing costs are in 2005 so we need to convert them to 2010

# http://www.in2013dollars.com/2005-dollars-in-2010

# According to the Bureau of Labor Statistics consumer price index, prices in 2010 are 11.65% higher than average prices throughout 2005. The dollar experienced an average inflation rate of 2.23% per year during this period.

Clean_Fishing_Cost <- Fishing_Cost %>% 
  select(EEZ = Country,
         gear_type = SuperGear,
         Cost_perTon_2005 = `TotCost (US$ per tonne of catch in 2005 real dollar)`) %>% 
  # bind_rows(Alaska_Cost) %>% 
  mutate(Cost_perTon_2010 = Cost_perTon_2005*1.1165) # Convert to 2010 real USD

# Including mixed gear info as the mean cost af all other gears for each EEZ
mix_gear_dat <- Clean_Fishing_Cost %>% 
  group_by(EEZ) %>% 
  summarise(Cost_perTon_2010 = mean(Cost_perTon_2010),
            Cost_perTon_2005 = mean(Cost_perTon_2005)) %>% 
  mutate(gear_type = "mixed gear")

# Change in names for matching data

Clean_Fishing_Cost$gear_type <- gsub("hand","hand lines",Clean_Fishing_Cost$gear_type)
Clean_Fishing_Cost$gear_type <- gsub("midwater trawl","pelagic trawl",Clean_Fishing_Cost$gear_type)

####_____ Final Fishing Cost dataset ####
Clean_Fishing_Cost <- Clean_Fishing_Cost %>% 
  bind_rows(mix_gear_dat)

####_____ Ex-vessel price ####

# Data provided by Travis 
# Here are the price data (in 2010 real dollars) for the 5 species caught by US (187) and Canada (26) from 1950 to 2014

Ex_Vessel <- read.delim("~/Documents/UBC/Oceans_Project/Econ/Data/Economic/Price_US_Canada_5spp.csv")

# Create a dummy database for data
Species <- data.table(
  "Species"= c(
    "Hippoglossus stenolepis", # Pacific Halibut (600514)
    "Merluccius productus", # Whiting (600326)
    "Gadus morhua",  # Cod (600069)
    "Limanda ferruginea", # Yellowtail flounder (600521)
    "Melanogrammus aeglefinus" # Haddock (601381)
  ),
  "taxon_key" = c(
    600514,
  600326,
  600069,
  600521,
  601381
  )
  )

####_____ Final Ex-Vessel dataset ####
Clean_Ex_Vessel <- Ex_Vessel %>% 
  mutate(EEZ = ifelse(fishing_entity_id == 26,"Canada","USA")) %>% 
  left_join(Species,
            by = "taxon_key") %>% 
  filter(year >= Beg_In & year <= Beg_End) %>% 
  group_by(EEZ,Species) %>% 
  summarise(Price_perTon = mean(price,na.rm = T)) # Average ex-vessel price for study yrs

####_____ Estimated Profits ####
# Profits = ex-vessel - cost

# Final dataset combining all data needed for estimating economics of transboundary fisheries.

# Mean method (NOT USED)
# Profit_Data_Mean <- Landings_Data %>%
#   left_join(Clean_Fishing_Cost,
#             by = c("gear_type","EEZ")) %>% # Joins Fishing cost Data
#   left_join(Clean_Ex_Vessel,
#             by = c("Species","EEZ")) %>%  # Joins Fishing price data
#   mutate(
#     Profit_perTon = Price_perTon-Cost_perTon_2010
#     ) %>%
#   group_by(EEZ,Species) %>%
#   summarise_if(is.numeric,mean) %>%
#   select(EEZ,Species,Profit_perTon)

# Weighted method (USED)
Profit_Data_Weight <- Landings_Data %>% 
  left_join(Clean_Fishing_Cost,
            by = c("gear_type","EEZ")) %>% # Joins Fishing cost Data
  left_join(Clean_Ex_Vessel,
            by = c("Species","EEZ")) %>%  # Joins Fishing price data
  mutate(
    Profit_perTon = Price_perTon-Cost_perTon_2010
    )

####___ Landings Data for Paper ####
# Table 1

Profit_Data_Paper <- Profit_Data_Weight %>% 
  mutate_at(vars(Cost_perTon_2010,Price_perTon,Profit_perTon),
            funs(round((.*Avrg_Landings)/1000000,2)) # million USD
            ) %>% 
  group_by(EEZ,Species) %>% 
  summarise_if(is.numeric,sum,na.rm=T)

# Average fishing cost for Notes in Table 1
Avg_Clean_Fishing_Cost <- Profit_Data_Weight %>% 
  group_by(EEZ,Species) %>% 
  summarise(
    Mean = mean(Cost_perTon_2010,na.rm=T),
    sd = sd(Cost_perTon_2010,na.rm=T)
  )

```

To estimate profits we can follow two methods; Average and weighted.

- The Average method. This method uses the average profit of each species and region by fishing gear which gives you an average for each species based on landings, cost and ex-vessel per gear. This method is skewed since some species like Cod have very few landings in some gears that are higlhy profitable (e.g. *Gadus morhua* in the US).

`r Profit_Data_Mean`

- Weighted methodd. This methods estimates a proportion of each species' total landings per gear. It then estimates profits per gear and country and uses that initial proportion to proyect landings into the future assuming that it will mantain constant.

## Projecting results into the future

In this section we combanie present landings and fisheries economics data with the results of the DBEM MCP to proyect fish profits into the future.

### Estimating changes in MCP

We adopted the methodology presented by Palacios-Abrantes et al. previously used in the present volume (see previous article) to estimate projected changes in stock share ratio (SSH) and maximum catch potential (MCP) of the five transboundary stocks previously selected. Thus, for each species we estimated the stock-share ratio ($\alpha$) that each EEZ will have during each time period:

$$\alpha_{ts} = \frac{\theta_{rt}}{\delta_{ts}}$$

where $\theta_{r}$ is the aggregated $\hat{MCP}$ of each region, and *t* is period. Three time periods (*t*) were considered to reduce temporal model sensitivity; $t_1$, present (`r Beg_In`-`r Beg_End`), $t_2$, mid 21^st^ century (`r Mid_In`-`r Mid_End`), and $t_3$, end of 21^st^ century (`r End_In`-`r End_End`). Similarly to the previous paper in this volume, we estimated the change in $\alpha_{ts}$ by dividing $t_2$ and $t_3$ by $t_1$.

For the present analysis, we used the projected change in MCP and the current landings to estimate the changes in revenue at both future time periods as fallows.

$$ X_{yr} = \sum_{s = 1}^n \hat{MCP_s}$$

where *y* is year, *r* is EEZ, *s* is species, *n* is total number of species, and $\hat{MCP}$ is the MCP averaged by the three GCMs. The same time periods than before were averaged. Thus, we computed the regional percentage change in MCP ($\Delta MCP_r$) as follows:

$$\Delta MCP_r = -(1-\frac{X_{t_{2,3}}}{X_{t_1}})*100 $$

where $X_{f}$ if the future aggregated MCP ($t_1$ mid and $t_2$ end of 21^st^ century) and $X_{t_1}$ is the present aggregated MCP ($\mu$ (`r Beg_In`-`r Beg_End`).

```{r Change_per_Period, eval = T, echo = F}

#### Estimate today's MCP proportion of each country per stock
Today_MCP <- MCP_Data %>% 
  filter(Year >= Beg_In & Year <= Beg_End) %>% 
  group_by(Species,
           Basin,
           RCP,
           Nation,
           Model) %>%
  summarise(MCP_Today = mean(MCP)) %>%   #average of 2005 to 2014
  mutate(Period = "Today")

#### Estimate change in MCP
MCP_Change <- MCP_Data %>% 
  left_join(Today_MCP) %>% 
  mutate( # Devides the different timeframes by the present and estimates percentage change
    Prop_Change = MCP/MCP_Today,
    Percentage_Ch = round(-(1-Prop_Change),2)
  ) %>% 
  mutate(  # Indicate the three period times
    Period = ifelse(Year >= Beg_In & Year <= Beg_End,"Begining",
                    ifelse(Year >= Mid_In & Year <= Mid_End,"Mid Century",
                           ifelse(Year >= End_In & Year <= End_End,"End Century",
                                  "Other_Years"))
                    ),
    EEZ = ifelse(str_detect(Nation, "Can "),"Canada","USA")
  ) %>% 
  ungroup() %>% 
  select(Species,EEZ,Model,RCP,Year,Period,Prop_Change)

```

## Fisheries economics

We then multiply $\Delta MCP_r$ by the average landings (2004-2014 for modeling consistency) to simulate a potential volume of MCP for each species and EEZ. Finally, revenue per fished tonne was computed in 2010 real US dollars by subtracting fishing cost from fishing price, and the multiplied by the total MCP of each time period.

```{r Projected_profits, eval = T, echo = F}

#_____ Estimate Projected Profits ####

# Estimate the future profit of each fishery based on current economic variables and landings multiplied by the change in MCP

# Using weighted method of Landings `Economics_Data` chunk

# Mean Profits method (NOT USED FOR NOW)
# Profit_Projection <- Landings_Data %>%
#   group_by(EEZ, Species) %>%
#   summarise(Avrg_Landings = sum(Avrg_Landings)) %>%
#   left_join(Profit_Data_Mean,
#             by = c("Species","EEZ")) %>%
#   left_join(MCP_Change,
#             by = c("Species","EEZ")) %>%
#   arrange(Species,EEZ,RCP,Model) %>%
#   mutate(
#     Future_Landings = Avrg_Landings*Prop_Change,
#     Profit = Future_Landings*Profit_perTon
#   ) %>%
#   select(Species,EEZ,Model,RCP,Year,Period,Profit)

# Mean Profits method (USED IN PAPER) ####

### For Discounting
# Discounted at 0.05 (5%)
dr <- 0.05
# Min and max years
Max_Y <- max(MCP_Change$Year)
Min_Y <- min(MCP_Change$Year)

# Get the number of years proyected times species and models
Years <- data.frame(Years_Dis = rep(seq(0,94,1), each = 102)) # each = number of species

#### Estimating Future Profits non and discounted

Projected_Profits <- Profit_Data_Weight %>%
  left_join(MCP_Change,
            by = c("Species","EEZ")) %>%
  arrange(Year) %>% # so the bumber of years match the actual year
  bind_cols(Years) %>% 
  mutate(
    Future_Landings = Avrg_Landings*Prop_Change,
    Profit = Future_Landings*Profit_perTon,
    Discounted_Profit = Profit/(1*(1 +dr)^Years_Dis)
  ) %>%
  group_by(Species,EEZ,Model,RCP,Year,Period) %>% # Summ all profits per gear
  summarise(
    Non_Discounted_Profits = sum(Profit),
    Discounted_Profits = sum(Discounted_Profit)
  ) %>%
  filter(Period != "Other_Years") %>%
  ungroup() %>%
  group_by(Species,Model,Period,EEZ,RCP) %>%
  summarise_if(is.numeric,mean,na.rm=T)

```

```{r Projected_profits_Proportion, eval = T, echo = F}

#_____ Estimate Profit Proportions ####
# First we estimate the projected profits totals for both nations according to the species, period and CC model

Projected_Profits_Totals <- Projected_Profits %>% 
  group_by(Species,Period,Model,RCP) %>%
  summarise(
    NonD_Total_Profit= sum(Non_Discounted_Profits,na.rm = T),
    Dis_Total_Profit= sum(Discounted_Profits,na.rm = T)
    )

# Then we estimate actual proportion of profits
Projected_Profits_Proportions <- Projected_Profits %>% 
  left_join(Projected_Profits_Totals,
            by = c("Model","Species","RCP","Period","Model")
  ) %>% 
  mutate(
    NonD_Proportion = Non_Discounted_Profits/NonD_Total_Profit,
    Dis_Proportion = Discounted_Profits/Dis_Total_Profit,
    Time_Sector = ifelse(Period == "Begining",1,
                         ifelse(Period == "Mid Century",2,
                                3)
    )
  ) %>% 
  filter(Species != "Melanogrammus aeglefinus")

```

# Results

```{r Paper_Plot, eval = T, echo=TRUE, message=FALSE, warning=FALSE}

# New facet label names for Species names
Common_Names <- c("Atlantic Cod","Pacific Halibut", "Y. Flounder")
names(Common_Names) <- c("Gadus morhua","Hippoglossus stenolepis", "Limanda ferruginea")

# Create data with average values for numbers in plot and tables in manuscript
Average_Prop_Plot <- Projected_Profits_Proportions %>% 
  group_by(Species,Period,Time_Sector,EEZ,RCP) %>% 
  summarise_at(vars(Non_Discounted_Profits,Discounted_Profits,
                    Dis_Proportion,NonD_Proportion),funs(mean,sd)
  ) %>% 
   mutate_at(vars(Non_Discounted_Profits_mean,Discounted_Profits_mean,
                  Non_Discounted_Profits_sd,Discounted_Profits_sd),
               funs(round(./1000000,2))
             )

# Plot for now (see next chunk for more options)
pd<-position_dodge(0.05)

ggplot() +
  geom_line(data = Average_Prop_Plot,
            aes(
              x=Time_Sector,
              y=NonD_Proportion_mean*100, # Percentage
              colour=EEZ
            )
  ) +
  geom_errorbar(data = Average_Prop_Plot,
                aes(
                  x=Time_Sector,
                  ymin=(NonD_Proportion_mean-(2*NonD_Proportion_sd))*100, # mean +- 2*sd
                  ymax=(NonD_Proportion_mean+(2*NonD_Proportion_sd))*100,
                  # ymin=(NonD_Proportion_mean-NonD_Proportion_sd)*100, # mean +- sd
                  # ymax=(NonD_Proportion_mean+NonD_Proportion_sd)*100,
                  colour=EEZ
                ),
                # alpha=0.5,
                width=.2,
                position=position_dodge(0.05),
                size = 0.6
  ) +
  geom_label_repel(data = subset(Average_Prop_Plot, Time_Sector == 2),
                   aes(
                     x = Time_Sector,
                     y = NonD_Proportion_mean*100, # Percentage
                     label = round(NonD_Proportion_mean*100),
                     fill = EEZ
                   ),
                   colour = "white",
                   size = 3,
                   show.legend = FALSE, # Don't display "a" in legend
                   point.padding = 0,
                   position=position_dodge(0.5)
  ) +
  geom_label_repel(data = subset(Average_Prop_Plot, Time_Sector != 2),
                   aes(
                     x = Time_Sector,
                     y = NonD_Proportion_mean*100, # Percentage
                     label = round(NonD_Proportion_mean*100),
                     fill = EEZ
                   ),
                   colour = "white",
                   size = 3,
                   show.legend = FALSE, # Don't display "a" in legend
                   point.padding = 0
  ) +
  scale_fill_manual(values = wes_palette("IsleofDogs1")) +
  scale_colour_manual(values = wes_palette("IsleofDogs1")) +
  scale_x_continuous(breaks=c(1, 2, 3),
                     labels=c("Present-day", "Mid-century", "End-century")) +
  # ylim(0,100)+
  facet_grid(Species ~ RCP,
             labeller = labeller(Species = Common_Names)
  ) +
  labs(
    x = "",
    y = "Proportion of total profits (%)"
  ) +
  theme(
    axis.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    axis.title = element_text(size = 18),
    legend.title = element_text(size = 18),
    legend.text = element_text(size = 12),
    # strip.text = element_text(size = 18),
    strip.text = element_text(size = 16),
    panel.spacing.x = unit(3.5, "lines")
  )

# Save plot 
ggsave("Econ_Plot.tiff",
       plot = last_plot(),
       width = 10,
       height = 8,
       units = "in",
       path = "./Results")
```

# Others

```{r Plots_Examples, eval = F, echo=TRUE, message=FALSE, warning=FALSE}

# New facet label names for Species names
Common_Names <- c("Atlantic Cod","Pacific Halibut", "Y. Flounder")
names(Common_Names) <- c("Gadus morhua","Hippoglossus stenolepis", "Limanda ferruginea")

# Create data with average values for numbers in plot and tables in manuscript
Average_Prop_Plot <- Projected_Profits_Proportions %>% 
  group_by(Species,Period,Time_Sector,EEZ,RCP) %>% 
  summarise_at(vars(Non_Discounted_Profits,Discounted_Profits,
                    Dis_Proportion,NonD_Proportion),funs(mean,sd)
  ) %>% 
   mutate_at(vars(Non_Discounted_Profits_mean,Discounted_Profits_mean,
                  Non_Discounted_Profits_sd,Discounted_Profits_sd),
               funs(round(./1000000,2))
             )

# Plot of lines per model
ggplot() +
  geom_line(data = Projected_Profits_Proportions,
              aes(
                x=Time_Sector,
                y=NonD_Proportion*100, # Percentage
                colour=Model,
                shape=EEZ
              )
  ) +
  facet_grid(Species ~ RCP,
             labeller = labeller(Species = Common_Names)
             )

# Plot of average +- sd
ggplot() +
  geom_line(data = Average_Prop_Plot,
              aes(
                x=Time_Sector,
                y=NonD_Proportion_mean*100, # Percentage
                colour=EEZ
              )
  ) +
  geom_point(data = Average_Prop_Plot,
              aes(
                x=Time_Sector,
                y=(NonD_Proportion_mean+NonD_Proportion_sd)*100, # Percentage
                colour=EEZ
              )
  ) +
  geom_point(data = Average_Prop_Plot,
              aes(
                x=Time_Sector,
                y=(NonD_Proportion_mean-NonD_Proportion_sd)*100, # Percentage
                colour=EEZ
              )
  ) +
  facet_grid(Species ~ RCP,
             labeller = labeller(Species = Common_Names)
             )

# Plot geom_ribbon(aes(ymin=menlelb, ymax=menleub), alpha=0.2)
ggplot() +
  geom_line(data = Average_Prop_Plot,
            aes(
              x=Time_Sector,
              y=NonD_Proportion_mean*100, # Percentage
              colour=EEZ
            )
  ) +
  geom_ribbon(data = Average_Prop_Plot,
              aes(
                x=Time_Sector,
                ymin=(NonD_Proportion_mean-NonD_Proportion_sd)*100,
                ymax=(NonD_Proportion_mean+NonD_Proportion_sd)*100,
                fill=EEZ
              ),
              alpha=0.2
  ) +
  facet_grid(Species ~ RCP,
             labeller = labeller(Species = Common_Names)
  ) +
  geom_label_repel(data = Average_Prop_Plot,
                   aes(
                     x = Time_Sector,
                     y = NonD_Proportion_mean*100, # Percentage
                     label = round(NonD_Proportion_mean*100),
                     fill = EEZ
                   ),
                   size = 3,
                   show.legend = FALSE, # Don't display "a" in legend
                   point.padding = 0
  ) +
  facet_grid(Species ~ RCP,
             labeller = labeller(Species = Common_Names)
  )

# geom_smoth using (Locally Weighted Scatterplot Smoothing), sometimes called LOESS
ggplot() +
  geom_smooth(data = Projected_Profits_Proportions,
              aes(
                x=Time_Sector,
                y=NonD_Proportion*100, # Percentage
                colour=EEZ,
                fill=EEZ
              ),
              se = TRUE,
              alpha = 0.5
  ) +
  geom_label_repel(data = Average_Prop_Plot,
                   aes(
                     x = Time_Sector,
                     y = NonD_Proportion_mean*100, # Percentage
                     label = round(NonD_Proportion_mean*100),
                     fill = EEZ
                   ),
                   size = 3,
                   show.legend = FALSE, # Don't display "a" in legend
                   point.padding = 0
  ) +
  facet_grid(Species ~ RCP,
             labeller = labeller(Species = Common_Names)
  )

# geom_errorbar
ggplot() +
  geom_line(data = Average_Prop_Plot,
            aes(
              x=Time_Sector,
              y=NonD_Proportion_mean*100, # Percentage
              colour=EEZ
            )
  ) +
  geom_errorbar(data = Average_Prop_Plot,
                aes(
                  x=Time_Sector,
                  ymin=(NonD_Proportion_mean-NonD_Proportion_sd)*100,
                  ymax=(NonD_Proportion_mean+NonD_Proportion_sd)*100,
                  colour=EEZ
                ),
                alpha=0.5,
                width=.1
  )  +
  facet_grid(Species ~ RCP,
             labeller = labeller(Species = Common_Names)
  )

```

```{r}
###______________________ EXPLORING DATA RESULTS ______________________#

Phalibut <- Profit_Data %>% 
  filter(Species =="Hippoglossus stenolepis")

ggplot(subset(Phalibut, Model == "Average")) +
  geom_line(aes(
    x = as.numeric(Year),
    # y = Profit_Disc/1000000,
    y = Profit/1000000,
    color = RCP
  ),
  alpha = 1,
  size = 2
  ) +
  geom_line(data =subset(Phalibut, Model != "Average"),
            aes(
    x = as.numeric(Year),
    # y = Profit_Disc/1000000,
    y = Profit/1000000,
    color = RCP,
    size = Model
  ),
  alpha = 0.1
  ) +
  facet_wrap(~EEZ, scales = "free") +
  labs(x = "Year",
       y = "Not-Discounted Profits (Million 2010 USD)") +
  scale_color_manual(values = c("red", "royalblue2")) +
  theme(legend.position = "")
  # scale_color_brewer(palette="Dark2")

ggsave("Non-Dis_Profits.png",
         plot = last_plot(),
         width = 10,
         height = 5,
         units = "in"#,
         # path = Fig_path_out
         )

# ______________________ END EXPLORING ______________________#

```

```{r Tradeoff_plots, eval = F}
#### Trdeoffs

Today <- Profit_Data %>% 
  filter(Period == "Begining") %>% 
  group_by(Species,EEZ) %>% 
  summarise(Mean_Profit= mean(Mean_Profit)) %>% 
  spread("EEZ","Mean_Profit") %>% 
  mutate(Period = "Begining")

### Explore tradeoff graphs

unique(Prop_Change$Species)
RCP_List <- c("GFDL26F1","IPSL26F1","MPI26F1")

Selected_Species <- c(
"Gadus morhua",
"Hippoglossus stenolepis",
"Limanda ferruginea",
"Melanogrammus aeglefinus",
"Merluccius productus"
)

s = 1
for (s in 1:5){

Spp <- Selected_Species[s]

Pd <- Profit_Data %>% 
  filter(Species %in% Spp,
         !Period %in% c("Other_Years","Begining")
         ) %>%
  select(EEZ,RCP,Period,Mean_Profit,Model)

## Canada data

TodayCad <- Today %>% 
  filter(Species %in% Spp) %>% 
  select(-USA) %>% 
  slice(rep(1:n(), each = 8)) %>% 
  mutate(Model = c(unique(Pd$Model),"Average"),
         RCP = c("High","High","High","High","Low","Low","Low","Low") # determine which model is what RCP
  )

Canada <- Pd %>% 
  filter(EEZ == "Canada") %>% 
  spread("EEZ","Mean_Profit") %>% 
  bind_rows(TodayCad) # We add today twice so the both start at the same point

## USA Data

TodayUSA <- Today %>% 
  filter(Species %in% Spp) %>% 
  select(-Canada) %>% 
  slice(rep(1:n(), each = 8)) %>% 
  mutate(Model = c(unique(Pd$Model),"Average"),
         RCP = c("High","High","High","High","Low","Low","Low","Low") # determine which model is what RCP
  )

USA <- Pd %>% 
  filter(EEZ == "USA") %>% 
  spread("EEZ","Mean_Profit") %>% 
  bind_rows(TodayUSA) # We add today twice so the both start at the same point

## Bind them

Plot_Data <- left_join(Canada,USA)

  ggplot() +
    # geom_line(data = subset(Plot_Data, Model != "Average"),
    #      aes(
    #        y = Canada/1000000,
    #        x = USA/1000000,
    #        colour = RCP,
    #        fill = Model
    #      ),
    #      alpha = 0.3
    #      ) +
    #     geom_line(data = subset(Plot_Data, Model == "Average"),
    #      aes(
    #        y = Canada/1000000,
    #        x = USA/1000000,
    #        colour = RCP
    # ),
    # linetype = "solid",
    # size = 2
    # ) +
  geom_point(data = subset(Plot_Data, Model == "Average"),
             aes(
               y = Canada/1000000,
               x = USA/1000000,
               colour = RCP
             ),
             size = 3
             ) +
  geom_text_repel(data = subset(Plot_Data, Model == "Average"),
             aes(
               y = Canada/1000000,
               x = USA/1000000,
               label = Period#,
               # colour = RCP
             ),
             size = 3
             ) +
  labs(title=paste("Profit tradeoff plot for",Spp, "(Million $US - 2010 real dollars)"),
       y = "USA",
       x = "Canada") +
    scale_color_manual(values = c("red", "blue")
                       )

Fig_name <- paste("Proffit_",Spp,".png",sep ="")

ggsave(Fig_name,
         plot = last_plot(),
         width = 6,
         height = 5,
         units = "in",
         path = Fig_path_out
         )

}

```

```{plots_for_IMBeR, eval = F}

Halibut <- Profit_Data %>% 
  filter(Species == "Hippoglossus stenolepis") %>% 
  mutate(Facet_Order = ifelse(RCP == "High","B","A"))

ggplot(subset(Halibut, Model == "Average")) +
  geom_line(aes(
    x = as.numeric(Year),
    # y = Profit_Disc/1000000,
    y = Profit/1000000,
    color = RCP
  ),
  alpha = 1,
  size = 2
  ) +
  geom_line(data =subset(Halibut, Model != "Average"),
            aes(
    x = as.numeric(Year),
    # y = Profit_Disc/1000000,
    y = Profit/1000000,
    color = RCP,
    size = Model
  ),
  alpha = 0.1
  ) +
  facet_wrap(~EEZ,
             scales = "free") +
  labs(x = "Year",
       y = "Not-Discounted Profits (Million 2010 USD)")

ggsave("Non-Dis_Profits.png",
         plot = last_plot(),
         width = 12,
         height = 5,
         units = "in",
         path = Fig_path_out
         )

```

### 2019-10-10 Ecol_Manuscript_Draft.Rmd
Updates and re-arrenging of documents

--- 2019-09-14 Ecol_Analysis/Manuscript_Draft.Rmd
@@
   pdf_document: default
-bibliography: Oceans_Canada_Biblio.bib
+bibliography: Ecol_Analysis/Oceans_Canada_Biblio.bib
 editor_options: 
   chunk_output_type: console
-csl: harvard.csl
+csl: Ecol_Analysis/harvard.csl
 ---
@@
   "ggplot2", #Nice grpahs and spatial analysis
-  "cowplot",
-  "rgdal",
   "RColorBrewer",
-  "knitr",
-  "kableExtra",
   "data.table",
   "ggrepel",
-  "gridExtra",
-  "ggmap",
-  "rgeos",
   "sf",
-  "sp",
-  "rgdal", #Spatial analysis 
-  "tools", #Spatial analysis 
-  "png", # For reading plots in chunk codes
-  "grid" # For reading plots in chunk codes
+  # "sp",
+  # "rgdal", #Spatial analysis 
+  "tools"#, #Spatial analysis 
+  # "png", # For reading plots in chunk codes
+  # "grid" # For reading plots in chunk codes
 )
@@
     axis.title       = element_blank(),
-    # legend.key       = element_rect(colour = NA, fill = NA, size = 4),
-    legend.position = "bottom"#,
-    # legend.key.width =unit(6,"line")
+    legend.key       = element_rect(colour = NA, fill = NA, size = 4),
+    legend.position = "bottom",
+    legend.key.width =unit(7,"line")
   )
@@
 # End Century
-End_In <- paste(2080);End_In # 2090
+End_In <- paste(2081);End_In # 2090
 End_End <- paste(2099);End_End
@@
 #Data provided by Vicki Lam
-EEZIDs_List <- read_excel("~/Documents/UBC/Oceans_Project/Distribution/By Cell/Cell_Data/Updated_EEZList_17June2016.xlsx")
-EEZ_CellID <- read_excel("~/Documents/UBC/Oceans_Project/Distribution/By Cell/Cell_Data/EEZ_CellID.xlsx")
-
+EEZIDs_List <- read_excel("./Data/Spatial/Updated_EEZList_17June2016.xlsx")
+EEZ_CellID <- read_excel("./Data/Spatial/EEZ_CellID.xlsx")
 colnames(EEZ_CellID) <- c("EEZID","INDEX")
@@
 # DBEM Coordinate system
-Coor <- fread("~/Documents/UBC/Oceans_Project/Distribution/DBEM/Data/Lon_Lat_DBEM.txt",header = FALSE)
+Coor <- fread("./Data/Spatial/Lon_Lat_DBEM.txt",header = FALSE)
 colnames(Coor) <- c("INDEX","Longitude","Latitude")
@@
 
-path_world <- "~/Documents/UBC/Oceans_Project/Manuscript/Data/Spatial_Data/TM_WORLD_BORDERS"
+path_world <- "./Data/Spatial/TM_WORLD_BORDERS"
 file_name <- "TM_WORLD_BORDERS"
@@
 
-path_eez <- ("~/Documents/UBC/Oceans_Project/Manuscript/Data/Spatial_Data/World_EEZ_v10_2018")
+path_eez <- "./Data/Spatial/World_EEZ_v10_2018"
 #The File
@@
 # Now we load IPHC shapefiles ####
-path_IPHC <- ("~/Documents/UBC/Oceans_Project/Distribution/Data/IPHC/IPHC_RegulatoryAreas/")
+path_IPHC <- "./Data/Spatial/IPHC_RegulatoryAreas"
 
@@
 
-path_NAFO <- ("~/Documents/UBC/Oceans_Project/Distribution/Data/Spatial/NAFO/")
+path_NAFO <- "./Data/Spatial/NAFO/"
 #The File
@@
 NAFO_Area <- st_read(dsn = path_NAFO,
-layer =file_path_sans_ext(fnam_NAFO))
+                     layer =file_path_sans_ext(fnam_NAFO)
+                     )
 
@@
 
+###------------------------------- ###
+#### Chunk to be ran with Drobo ###
+###------------------------------- ###
+
 # Species data (Names, treaties, etc)
@@
 ```{r DBEM_Data_For_All, eval = F, echo = F, warning = F, message = F}
+
+###------------------------------- ###
+#### Chunk to be ran with Drobo ###
+###------------------------------- ###
 
@@
 
-EEZIDs_List <- read_excel("~/Documents/UBC/Oceans_Project/Distribution/By Cell/Cell_Data/Updated_EEZList_17June2016.xlsx")
-
-EEZ_CellID <- read_excel("~/Documents/UBC/Oceans_Project/Distribution/By Cell/Cell_Data/EEZ_CellID.xlsx")
-
+#Data provided by Vicki Lam
+EEZIDs_List <- read_excel("./Data/Spatial/Updated_EEZList_17June2016.xlsx")
+EEZ_CellID <- read_excel("./Data/Spatial/EEZ_CellID.xlsx")
 colnames(EEZ_CellID) <- c("EEZID","INDEX")
@@
 # From (/Users/jpalacios/Documents/UBC/Oceans_Project/Distribution/By Cell/By_Cell_Analysis.Rmd)
-Raw_DBEM_Results <- data.table::fread("~/Documents/UBC/Oceans_Project/Manuscript/Data/Raw_Data.csv") %>% 
+Raw_DBEM_Results <- data.table::fread("./Data/Distribution/Raw_Data.csv") %>% 
   filter(Species != "Anoplopoma fimbria") #Remove
@@
 # Path to save the plots
-Path <- "~/Documents/UBC/Oceans_Project/Manuscript/Results/North_America"
+Path <- "./Results/Ecol/North_America"
 RCP = c("GFDL26F1","IPSL26F1","MPI26F1") #Low RCP
@@
                     ifelse(Year >= Mid_In & Year <= Mid_End,"Mid_Century",
-                           ifelse(Year >= End_In & Year <= End_End,"The_End_Century",
+                           ifelse(Year >= End_In & Year <= End_End,"End_Century",
                                   "Other_Years"))
@@
   mutate_at(vars(Mid_Century, # Devide future values by present
-                 The_End_Century),
+                 End_Century),
             funs(ifelse(Begining > 0, ./Begining,.)) #if no species today value is the future
@@
   mutate_at(vars(Mid_Century, # Estimate percentage change
-                 The_End_Century),
+                 End_Century),
             funs(ifelse(Begining == 0 & . == 0, 0, # If for no change than 0
@@
   ) %>% 
-  gather("Period","MCP_Change",Mid_Century,The_End_Century) %>% 
+  gather("Period","MCP_Change",Mid_Century,End_Century) %>% 
   mutate(Direction = ifelse(MCP_Change >= 0, "Positive","Negative")) %>% 
@@
 # ggplot(MCP_Data) +
-#   geom_tile(
-#     aes(
-#       x = longitude,
-#       y = latitude,
-#       color = Model_Agreement,
-#       fill = Model_Agreement
-#     )
-#   ) +
-#   facet_grid(RCP~Period)
-
-### Explore mAtlantic unde 40
-
-# Under40 <- MCP_Data %>% 
-#   filter(latitude < 40, longitude > -90)
-# 
-# ggplot(Under40) +
 #   geom_tile(
@@
 
-  ggsave("New_plot.tiff",
+  ggsave("NA_25_20_Mid.jpg",
          plot = p,
+         width = 16,
+         height = 10,
+         units = "in",
+         path = Path)
+
+  ####------------- ###
+  # End of century For Appendix 
+  #### ------------- ###
+
+  # Plot it
+  ggplot(MCP_Data) +
+    geom_tile(data = subset(MCP_Data, Period == "End_Century"),
+              aes(
+                x = longitude,
+                y = latitude,
+                color = Mean_ESM_MCP_Chng,
+                fill = Mean_ESM_MCP_Chng
+              )
+    ) +
+    geom_point(data = subset(MCP_Data, Period == "End_Century" & Model_Agreement == "Disagree"),
+               aes(
+                 x = longitude,
+                 y = latitude
+               ),
+               size = 0.01,
+               alpha = 0.1,
+               shape = 4,
+               color = "grey20"
+    ) +
+    geom_sf(data = North_America_Land, fill = "grey90") +
+    facet_wrap(~RCP) +
+    coord_sf(xlim = c(-190,-50)) +
+    scale_color_gradient2("MCP Percentage Change",
+      limits=c(-100,
+               100),
+      breaks = Seq) +
+    scale_fill_gradient2("MCP Percentage Change",
+      limits=c(-100,
+               100),
+      breaks = Seq) +
+    ggtheme_map() +
+    theme(
+    legend.key = element_rect(size = 3),
+    legend.key.width =unit(8,"line"),
+    legend.title = element_text(size = 20),
+    legend.text = element_text(size = 18)
+    ) +
+    # And save it
+    ggsave("NA_85_26_End.jpg",
            width = 16,
@@
 # DBEM Coordinate system
-Coor <- fread("~/Documents/UBC/Oceans_Project/Distribution/DBEM/Data/Lon_Lat_DBEM.txt",header = FALSE)
+Coor <- fread("./Data/Spatial/Lon_Lat_DBEM.txt",header = FALSE)
 colnames(Coor) <- c("INDEX","Longitude","Latitude")
-
 #### Mid Century result Table ####
@@
 
-# Path to save the plots
-Path <- "~/Documents/UBC/Oceans_Project/Manuscript/Results/North_America"
 RCP = c("GFDL26F1","IPSL26F1","MPI26F1") #Low RCP
@@
 # Path for saving plots
-Path <- "~/Documents/UBC/Oceans_Project/Manuscript/Results/IPHC/Region"
+Path <- "./Results/Ecol/IPHC/"
 RCP = c("GFDL26F1","IPSL26F1","MPI26F1") #Low RCP
@@
 # Save plot 
-Name = paste("New_IPHC_Reg_26_85_2050.png")
+Name = paste("IPHC_85_26_2050.png")
 
@@
 
-### now we average the results from the models for END century ###
-
-# Seq <- seq(-50,50,by=5) #Axis
-
-# P2 <- ggplot() +
-#   geom_sf(data = North_America_Land, colour = "lightgrey") + # Land Map of North America
-#   geom_sf(data = subset(IPHC_DBEM_sf, Country == "United States"), # DBEM Of the US
-#           aes(fill = Percentage_End)
-#   ) +
-#   geom_sf(data = subset(IPHC_DBEM_sf, RegArea == "2B"), # DBEM of Canada
-#           aes(fill = Percentage_End)
-#   ) +
-#   geom_sf_label(data = IPHC_DBEM_sf, # RegAreas labels
-#                 aes(
-#                   label = RegArea,
-#                   fill = Percentage_End
-#                 ),
-#                 colour = "black"
-#   ) +
-#   geom_label(data=IPHC_DBEM_sf, aes(label = RCP, x =4080637 , y = 4551701, colour = RCP), #RCP labels for grid plot
-#              show.legend = FALSE,
-#              size = 10
-#   ) +
-#   facet_wrap(~RCP,  # For grid plot, comment in one plot each
-#              ncol = 2) +
-#   scale_colour_manual(values=c("blue", "red")) + #Labels colors for grid plot
-#   scale_fill_gradient2("",
-#                        limits=c(-30,30),
-#                        breaks = Seq) +
-#   ggtheme_map() +
-#   theme(
-#     legend.key = element_rect(size = 4),
-#     legend.key.width =unit(8,"line"),
-#     legend.text = element_text(size = 16),
-#     strip.text.x = element_blank()
-#   ) +
-#   coord_sf(xlim = c(1963800, 10041910), # Subsets north america
-#            ylim = c(3651701,9728813)
-#   ) +
-#   annotate("text", label = "Alaska", x = 6280637, y = 9228813, size = 6, colour = "black") +
-#   annotate("text", label = "Canada", x = 9629910, y = 9228813, size = 6, colour = "black") +
-#   annotate("text", label = "US Contiguous\n States", x =10000000, y = 5151701, size = 6, colour = "black", angle = -90)
-# 
-# # Save plot 
-# Name_End = paste("IPHC_Reg_26_85_2100.png")
-# 
-# ggsave(Name_End,
-#        plot = P2,
-#        width = 15,
-#        height = 10,
-#        units = "in",
-#        path = Path)
+####------------- ###
+  # End of century For Appendix 
+#### ------------- ###
+
+Seq <- seq(-50,50,by=10) #Axis
+
+IPHC_DBEM_sf <- IPHC_Reg %>% 
+  left_join(IPHC_MCP_Change,
+            by = "RegArea") %>% 
+  st_transform(3832)
+
+IPHC_DBEM_sf$RegArea <- gsub("Closed Area","CA",IPHC_DBEM_sf$RegArea)
+
+IPHC_DBEM_sf <- IPHC_DBEM_sf %>% 
+  filter(Period == "End_Century")
+
+# max(IPHC_DBEM_sf$Mean_ESM_MCP_Chng)
+
+# Save plot
+Name_End = paste("IPHC_85_26_2100.png")
+
+p_end <- ggplot() +
+  geom_sf(data = North_America_Land, colour = "lightgrey") + # Land Map of North America
+  geom_sf(data = subset(IPHC_DBEM_sf, Country == "United States"), # DBEM Of the US
+          aes(fill = Mean_ESM_MCP_Chng)
+  ) +
+  geom_sf(data = subset(IPHC_DBEM_sf, RegArea == "2B"), # DBEM of Canada
+          aes(fill = Mean_ESM_MCP_Chng)
+  ) +
+  geom_sf_label(data = IPHC_DBEM_sf, # RegAreas labels
+                aes(
+                  label = RegArea,
+                  fill = Mean_ESM_MCP_Chng
+                ),
+                colour = "black"
+  ) +
+  geom_label(data=IPHC_DBEM_sf, aes(label = RCP, x =4080637 , y = 4551701, colour = RCP), #RCP labels for grid plot
+             show.legend = FALSE,
+             size = 10
+  ) +
+  facet_wrap(~RCP,  # For grid plot, comment in one plot each
+             ncol = 2) +
+  scale_fill_gradient2("",
+                       limits=c(-50,50),
+                       breaks = Seq) +
+  ggtheme_map() +
+  theme(
+    legend.key = element_rect(size = 4),
+    legend.key.width =unit(8,"line"),
+    legend.text = element_text(size = 16),
+    strip.text.x = element_blank()
+  ) +
+  coord_sf(xlim = c(1963800, 10041910), # Subsets North America map
+           ylim = c(3651701,9728813)
+  ) +
+  annotate("text", label = "Alaska", x = 6280637, y = 9228813, size = 6, colour = "black") +
+  annotate("text", label = "Canada", x = 9629910, y = 9228813, size = 6, colour = "black") +
+  annotate("text", label = "US Contiguous\n States", x =10000000, y = 5151701, size = 6, colour = "black", angle = -90)
+
+  ggsave(Name_End,
+         plot = p_end,
+         width = 15,
+         height = 10,
+         units = "in",
+         path = Path
+  )
 
@@
 
-Path <- "./Manuscript/Results/IPHC/Proportion"
+Path <- "./Results/Ecol/IPHC/"
 # names(DBEM_Results)
@@
 # Path for saving plots
-Path <- "~/Documents/UBC/Oceans_Project/Manuscript/Results/GB/Spp/"
+Path <- "./Results/Ecol/GoM/"
 
@@
   ) %>% 
-  gather("Period","MCP_Chng",Mid_Century,The_End_Century) %>% 
+  gather("Period","MCP_Chng",Mid_Century,End_Century) %>% 
   mutate(Direction = ifelse(MCP_Chng >= 0, "Positive","Negative")) %>% 
@@
 
-  Name = paste("New_Change_GB_26_85_Mid.png",sep="_")
+  Name = paste("GoM_26_85_Mid.png",sep="_")
+
+ggsave(Name,
+       plot = pgm,
+       width = 20,
+       height = 10,
+       units = "in",
+       path = Path)
+
+###-----------------###
+# Plot for Appendix 
+###-----------------###
+
+pgm <- ggplot(New_Mean_Data_GoM) +
+  geom_tile(data = subset(New_Mean_Data_GoM, Period == "End_Century"),
+            aes(
+              x = Longitude,
+              y = Latitude,
+              color = Mean_ESM_MCP_Chng,
+              fill = Mean_ESM_MCP_Chng
+            )
+  ) +
+  geom_point(data = subset(New_Mean_Data_GoM, Period == "End_Century" & Model_Agreement == "Disagree"),
+             aes(
+               x = Longitude,
+               y = Latitude
+             ),
+             # size = 0.1,
+             alpha = 0.3,
+             shape = 4,
+             color = "grey20"
+  ) +
+  scale_fill_gradient2(paste("MCP Percentage Change \n",End_In,"-",End_End,")"), # If not using the bins
+                       limits=c(Lim_Neg,
+                                Lim_Max),
+                       breaks = Seq,
+                       na.value = 'darkred' # NA values are present when the species is no more 
+  ) +
+  scale_colour_gradient2(paste("MCP Percentage Change \n",End_In,"-",End_End,")"),
+                         limits=c(Lim_Neg,
+                                  Lim_Max),
+                         breaks = Seq,
+                         na.value = 'darkred' # NA values are present when the species is no more
+  ) +
+  geom_sf(data = GM_Land, colour = "lightgrey") +
+  geom_sf(data = eez_GM, fill = NA) +
+  coord_sf(xlim = c(-71.0592, -63.33333),
+           ylim = c(41,45.5)
+           ) +
+  annotate("text", label = "United States", x = -70, y = 45, size = 4, colour = "black") +
+  annotate("text", label = "Canada", x = -66.8, y = 45.4, size = 4, colour = "black") +
+  annotate("text", label = "Canada", x = -65.4, y = 44.2, size = 4, colour = "black") +
+  ggtheme_map() +
+  theme(
+    axis.line = element_line(colour = "black", size = .5),
+    axis.ticks = element_line(size = .5),
+    axis.text.x = element_text(size = 12,
+                               angle = 0,
+                               face = "plain"),
+    axis.text.y = element_text(size = 12),
+    legend.key = element_rect(size = 3),
+    legend.key.width =unit(8,"line"),
+    legend.title = element_text(size = 20),
+    legend.text = element_text(size = 18)
+  )  +
+  facet_wrap(~RCP + Species, 
+             ncol = 3
+  )
+
+  Name = paste("GoM_26_85_End.png",sep="_")
 

### 2019-10-25 Ecol_Manuscript_Draft.Rmd
Updates to manuscript

@@
 
-![Fig 1. Map of North America with the regulatory areas of the IPHC and the NAFO sub-region related to the Gulf of Main agreement](./Results/Fig1.png)
+![Fig 1. Map of North America with the regulatory areas of the IPHC and the NAFO sub-region related to the Gulf of Main agreement](./Figures/Ecol//Fig1.png)
 
@@
 
-```{r Spatial_data, eval = T, echo = F, warning=F, message=F, results = 'hide'}
+```{r Spatial_data, eval = F, echo = F, warning=F, message=F, results = 'hide'}
 
@@
 ![Fig 2.
-Percentage change of MCP of transboundary fisheries of North America for mid century (2046-2055) referent to 2005-2014 under a A) low emission scenario and; B) high emission scenario.](./Results/Fig2.png)
+Percentage change of MCP of transboundary fisheries of North America for mid century (2046-2055) referent to 2005-2014 under a A) low emission scenario and; B) high emission scenario.](./Figures/Ecol/Fig2.png)
 
@@
 
-```{r IPHC_Map_Result_Regions, eval=T, echo=F}
+```{r IPHC_Map_Result_Regions, eval = F, echo=F}
 
@@
 
-```{r Functions, eval = F}
-
-getTaxInfo <- function(TaxNumber,TaxPath=NA, Sal = "NA"){
-
-  # Set automatic path, change if needed
-  TaxPath  <- "/Volumes/DATA/JULIANO_NEYMAR/PristineSeasData/Species/TaxonDataC0/"
-
-  # Sets the tac and path 
-  To_Read <- paste(TaxPath,TaxNumber,".txt",sep = "")
-
-  if(Sal == "Y"){
-  Spp_Info <- suppressWarnings(
-    read_table2(To_Read, 
-     col_names = FALSE, col_types = cols(`0` = col_character(), 
-         X2 = col_number(), X3 = col_number(), 
-         X4 = col_number(), X5 = col_number(), 
-         X6 = col_number()), 
-     skip = 16)
-  ) 
-  Spp_Info <- Spp_Info[1,2:6]
-  }else{
-  # Reads in file
-  Spp_Info <- suppressMessages(
-    readr::read_delim(To_Read, 
-               "\t", escape_double = FALSE, col_names = FALSE, 
-               # col_types = cols(X2 = col_number()),
-               trim_ws = TRUE)
-  )
-  }
-  return(Spp_Info)
-}
-
-getTTP <- function(TaxNumber,yr,TaxPath=NA){
-
-  # Set automatic path, change if needed
-  TaxPath  <- paste("/Volumes/DATA/JULIANO_NEYMAR/PristineSeasData/TPP",yr,"",sep="/")
-
-  # Sets the tac and path 
-  To_Read <- paste(TaxPath,"TPPotp",TaxNumber,".csv",sep = "")
-
-  TPPotp <- read.csv(To_Read)
-
-  return(TPPotp)
-}
-
-getEnvVar=function(yr,ModelRCP,RCP,Variable){
-
-  if(ModelRCP == "IPSL"){
-    ModelRCP = "IPSL-CM5A-MR"
-    Filepath <- paste("/Volumes/DATA/DATA/Environmental data/Model Climate data/CMIP5/txt CMIP5/Reformatted",ModelRCP,RCP,"",sep="/")
-  }
-
-  if(ModelRCP ==  "MPI"){
-    ModelRCP = "MPI-ESM-MR"
-    Filepath <- paste("/Volumes/DATA/DATA/Environmental data/Model Climate data/CMIP5/txt CMIP5/Reformatted",ModelRCP,RCP,"",sep="/")
-  }
-
-  if(ModelRCP = "GFDL"){
-
-    if(RCP == "rcp26"){
-    ModelRCP <- "GFDL26"
-    }else{
-      ModelRCP <- "GFDL85"
-    }
-
-  Filepath <- paste("/Volumes/DATA/JULIANO_NEYMAR/PristineSeasData/Climate",ModelRCP,"",sep="/")
-  }
-
-  if(Variable == "Ice"){
-
-    Bottom <- paste("IceExt_",yr,".txt",sep="")
-
-  }
-
-    if(Variable == "Temperature"){
-
-      Bottom = paste("botTemp_",2005,".txt",sep="")
-
-    }
-
-    if(Variable == "Salinity"){
-      # Bottom
-      Bottom = paste("Salinity_btm_",yr,".txt",sep="")
-
-    }
-
-    Read_me <- paste(Filepath,Bottom,sep="")[1]
-    Bottom_Data <- read.csv(Read_me,header=F)
-
-   # Retrun
-
-    getTemp <- Bottom_Data  
-}
-
-```
-
-```{r 4D_exploration, eval=F, echo=F,message=F, warning=F}
-
-# Exploring wy 4D s negative under 2.6 but positive under 8.5
-# This chunk will use functions build for the Pristince seas work
-
-### Exploration at the spatial level
-
-Spatial_4DE <- DBEM_Corrected %>% 
-  mutate(RCP = ifelse(Model %in% c("GFDL26F1","IPSL26F1","MPI26F1"),"RCP 2.6","RCP 8.5")) %>% # Set the RCPs
-  filter(Species == "Hippoglossus stenolepis") %>% 
-  left_join(IPHC_Reg_DBEM_df,
-            by = "INDEX") %>% 
-  filter(RegArea %in% c("4D","4E")) %>%
-  group_by(RegArea,RCP,Model) %>% #Sum grid-cells by regulatory area, RCP and Model
-  summarise_at(vars(`2005`:`2099`), sum,na.rm=T) %>% 
-  tidyr::gather("Year","Total_MCP",`2005`:`2099`) %>% 
-  group_by(RegArea,RCP,Year) %>% 
-  summarise(
-    m=mean(Total_MCP),
-    sd=sd(Total_MCP)
-    )
-
-ggplot(Spatial_4DE) +
-  geom_point(
-    aes(
-      x = Year,
-      y = m,
-      colour = RCP
-    )
-  ) +
-  facet_wrap(~RegArea,
-             scales = "free")
-
-### Environmental varibales of the region
-
-## Temp
-
-# Variables
-Model = c("GFDL","IPSL","MPIS")
-RCP = c("rcp26","rcp85")
-
-Grid <- DBEM_Corrected %>% 
-  select(INDEX) %>% 
-  left_join(IPHC_Reg_DBEM_df,
-            by = "INDEX") %>% 
-  filter(RegArea %in% c("4D","4E")) %>% 
-  select(INDEX)
-
-Variables <- c("Temperature","Salinity","Ice")
-
-F_BData <- NULL
-F_SData <- NULL
-F_MData <- NULL
-F_RData <- NULL
-Years <- seq(2005,2100,1)
-
-all_Grid <- seq(1,259200,1)
-
-for(v in 3:3){
-  # Loop through RCPs
-  for(r in 1:2){
-    # Loop through  variables
-    for(m in 1:3){
-      # Loop through years
-      for(y in 1:length(Years)){
-
-        Data <- getEnvVar(yr = Years[y],
-                          Model = Model[m],
-                          Variable = Variables[v],
-                          RCP = RCP[r]
-        ) %>% 
-          mutate(INDEX = all_Grid) %>% 
-          filter(INDEX %in% Grid$INDEX)
-
-        if(y == 1){
-
-          F_BData <- Data[1]
-
-        }else{
-
-          F_BData <- cbind(Data[1],F_BData)
-
-        }
-      }
-
-      colnames(F_BData) <- Years
-
-      F_BData <- F_BData %>% 
-        gather(Year,Value,1:426) %>% 
-        mutate(Model = Model[m],
-               RCP = RCP[r],
-               Variable = Variables[v])
-
-      if(m == 1){
-
-        F_MData <- F_BData
-
-      }else{
-
-        F_MData <- rbind(F_BData,F_MData)
-      }
-    }
-
-    if(r == 1){
-
-      F_RData <- F_MData
-
-    }else{
-
-      F_RData <- rbind(F_RData,F_MData)
-    }
-  }
-
-  if(v == 1){
-
-    F_VData <- F_RData
-
-  }else{
-
-    F_VData <- rbind(F_VData,F_RData)
-  }
-
-} # closes variable loop
-
-write.csv(F_VData,
-          "Environmental_Data_Halibut.csv",
-          row.names = F)
-
-### Exploration at the biological level
-
-# exploited_species_list <- fread("/Volumes/DATA/PROJECTION exploited species ENM/exploited_species_list.csv")
-# 600514
-
-# Isolate Regions
-
-DE <- IPHC_MCP_Change %>% 
-  filter(RegArea %in% c("4D","4E"))
-
-#Load Halibut Species preferences
-Halibut <- getTaxInfo(600514)
-# Demersal
-# HabAssocSal 0 1 1 -1 -1
-# HabAssocIce 0
-
-# Temp
-TTPop <- getTTP(600514,"Avg") %>% 
-  filter(TempPP > 0)
-
-Min_T <- min(TTPop$Temp)
-Max_T <- max(TTPop$Temp)
-
-# Halibut_Temp 2
-# quant05 -2 
-# quant25 0 
-# quant50 2
-# quant75 5
-# quant95 11
-```
-
-```{r Figure_3, eval =F, echo =F, fig.cap="Percentage Change of MCP for Species managed by the IPHC.
+```{r Figure_3, eval = F, echo =F, fig.cap="Percentage Change of MCP for Species managed by the IPHC.
 A, RCP 2.6 represents a low emission scenario (high mitigation).
@@
 
-![Fig 3. Percentage change of MCP for species managed by the IPHC for mid century (2046-2055) referent to 2005-2014 under a A) low emission scenario and B) high emission scenario.](./Results/Fig3.png)
+![Fig 3.
+Percentage change of MCP for species managed by the IPHC for mid century (2046-2055) referent to 2005-2014 under a A) low emission scenario and B) high emission scenario.](./Figures/Ecol/Fig3.png)
 
@@
 
-```{r IPHC_Proportion_Regions, eval=F, echo = F, message=F, warning=F}
+```{r IPHC_Proportion_Regions, eval = F, echo = F, message=F, warning=F}
 
@@
 
-```{r Figure_4, eval =F, echo =F, fig.cap="Percentage change of stock-share ratio for IPHC under two RCPs for Mid century (2046-2055)"}
+```{r Figure_4, eval = T, echo =F, fig.cap="Percentage change of stock-share ratio for IPHC under two RCPs for Mid century (2046-2055)"}
 
@@
 
-![Fig 4. Percentage change of stock-share ratio for IPHC under A) low emission scenario and B) high emission scenario for mid century (2046-2055) referent to 2005-2014.](./Results/Fig4.png)
+![Fig 4. Percentage change of stock-share ratio for IPHC under A) low emission scenario and B) high emission scenario for mid century (2046-2055) referent to 2005-2014.](./Figures/Ecol/Fig4.png)
 
@@
 
-```{r GB_Results_Spp, eval=F, echo = F, fig.width=12}
+```{r GB_Results_Spp, eval = F, echo = F, fig.width=12}
 
@@
 
-![Fig 5. Percentage change of MCP in the Gulf of Main under, A) low emission scenario; and B) high emission for mid century (2041-2060) referent to present (2005-2014)](./Results/Fig5.png)
+```{r Figure_5, eval = T, echo =F, fig.cap="Percentage change of MCP in the Gulf of Main under, A) low emission scenario; and B) high emission for mid century (2041-2060) referent to present (2005-2014)"}
+
+Fig4 <- readPNG("./Figures/Ecol/Fig5.png")
+grid.raster(Fig5)
+
+```
+
+![Fig 5. Percentage change of MCP in the Gulf of Main under, A) low emission scenario; and B) high emission for mid century (2041-2060) referent to present (2005-2014)](./Figures/Ecol/Fig5.png)
 
@@
 
-```{r GB_Proportion_Species, eval =F, echo=F}
+```{r GB_Proportion_Species, eval = F, echo=F}
 ### Analysis by Species ####
@@
 
-![Fig 6. Changes in MCP stock-share ratio for Gulf of Main under (A) low emission scenario; and (B) high emission for mid century (2041-2060) referent to 2005-2014](./Results/Fig6.png)
+```{r Figure_6, eval = T, echo =F, fig.cap="Changes in MCP stock-share ratio for Gulf of Main under (A) low emission scenario; and (B) high emission for mid century (2041-2060) referent to 2005-2014"}
+
+Fig4 <- readPNG("./Figures/Ecol/Fig6.png")
+grid.raster(Fig5)
+
+```
+
+![Fig 6. Changes in MCP stock-share ratio for Gulf of Main under (A) low emission scenario; and (B) high emission for mid century (2041-2060) referent to 2005-2014](./Figures/Ecol/Fig6.png)
 
 # DISCUSSION
-
-<!-- ## Species shifting towards the poles  -->
 
@@
 
-<!-- ## Uncertanty stuff -->
-
 In the current paper we follow a modeling approach to explore the potential impacts that climate change will have in the management of transboundary fisheries in North America.
@@
 
-<!-- Discussion on improoving management  -->
-<!-- From global (Cheung et al.
-2016c) to regional (Morley et al.
-2018) analysis, mitigating the effects of climate change will have positive results on fisheries (Sumaila 2019).
-In combination with improving management [Costello], fisheries will only be saved by a holistic approach… Indeed, dynamic management tools seem to work better than static strategies for resources expected to shift with changes in ocean condition (Pinsky and Selden 2017).
--->
-
 # CONCLUSIONS
@@
 
-We ack
-
 # LITERATURE CITED
+
+<!-- # Old Analysis -->
+
+<!-- ## Investigating 4D -->
+
+```{r Functions, eval = F}
+
+getTaxInfo <- function(TaxNumber,TaxPath=NA, Sal = "NA"){
+
+  # Set automatic path, change if needed
+  TaxPath  <- "/Volumes/DATA/JULIANO_NEYMAR/PristineSeasData/Species/TaxonDataC0/"
+
+  # Sets the tac and path 
+  To_Read <- paste(TaxPath,TaxNumber,".txt",sep = "")
+
+  if(Sal == "Y"){
+  Spp_Info <- suppressWarnings(
+    read_table2(To_Read, 
+     col_names = FALSE, col_types = cols(`0` = col_character(), 
+         X2 = col_number(), X3 = col_number(), 
+         X4 = col_number(), X5 = col_number(), 
+         X6 = col_number()), 
+     skip = 16)
+  ) 
+  Spp_Info <- Spp_Info[1,2:6]
+  }else{
+  # Reads in file
+  Spp_Info <- suppressMessages(
+    readr::read_delim(To_Read, 
+               "\t", escape_double = FALSE, col_names = FALSE, 
+               # col_types = cols(X2 = col_number()),
+               trim_ws = TRUE)
+  )
+  }
+  return(Spp_Info)
+}
+
+getTTP <- function(TaxNumber,yr,TaxPath=NA){
+
+  # Set automatic path, change if needed
+  TaxPath  <- paste("/Volumes/DATA/JULIANO_NEYMAR/PristineSeasData/TPP",yr,"",sep="/")
+
+  # Sets the tac and path 
+  To_Read <- paste(TaxPath,"TPPotp",TaxNumber,".csv",sep = "")
+
+  TPPotp <- read.csv(To_Read)
+
+  return(TPPotp)
+}
+
+getEnvVar=function(yr,ModelRCP,RCP,Variable){
+
+  if(ModelRCP == "IPSL"){
+    ModelRCP = "IPSL-CM5A-MR"
+    Filepath <- paste("/Volumes/DATA/DATA/Environmental data/Model Climate data/CMIP5/txt CMIP5/Reformatted",ModelRCP,RCP,"",sep="/")
+  }
+
+  if(ModelRCP ==  "MPI"){
+    ModelRCP = "MPI-ESM-MR"
+    Filepath <- paste("/Volumes/DATA/DATA/Environmental data/Model Climate data/CMIP5/txt CMIP5/Reformatted",ModelRCP,RCP,"",sep="/")
+  }
+
+  if(ModelRCP = "GFDL"){
+
+    if(RCP == "rcp26"){
+    ModelRCP <- "GFDL26"
+    }else{
+      ModelRCP <- "GFDL85"
+    }
+
+  Filepath <- paste("/Volumes/DATA/JULIANO_NEYMAR/PristineSeasData/Climate",ModelRCP,"",sep="/")
+  }
+
+  if(Variable == "Ice"){
+
+    Bottom <- paste("IceExt_",yr,".txt",sep="")
+
+  }
+
+    if(Variable == "Temperature"){
+
+      Bottom = paste("botTemp_",2005,".txt",sep="")
+
+    }
+
+    if(Variable == "Salinity"){
+      # Bottom
+      Bottom = paste("Salinity_btm_",yr,".txt",sep="")
+
+    }
+
+    Read_me <- paste(Filepath,Bottom,sep="")[1]
+    Bottom_Data <- read.csv(Read_me,header=F)
+
+   # Retrun
+
+    getTemp <- Bottom_Data  
+}
+
+```
+
+```{r 4D_exploration, eval = F, echo=F,message=F, warning=F}
+
+# Exploring wy 4D s negative under 2.6 but positive under 8.5
+# This chunk will use functions build for the Pristince seas work
+
+### Exploration at the spatial level
+
+Spatial_4DE <- DBEM_Corrected %>% 
+  mutate(RCP = ifelse(Model %in% c("GFDL26F1","IPSL26F1","MPI26F1"),"RCP 2.6","RCP 8.5")) %>% # Set the RCPs
+  filter(Species == "Hippoglossus stenolepis") %>% 
+  left_join(IPHC_Reg_DBEM_df,
+            by = "INDEX") %>% 
+  filter(RegArea %in% c("4D","4E")) %>%
+  group_by(RegArea,RCP,Model) %>% #Sum grid-cells by regulatory area, RCP and Model
+  summarise_at(vars(`2005`:`2099`), sum,na.rm=T) %>% 
+  tidyr::gather("Year","Total_MCP",`2005`:`2099`) %>% 
+  group_by(RegArea,RCP,Year) %>% 
+  summarise(
+    m=mean(Total_MCP),
+    sd=sd(Total_MCP)
+    )
+
+ggplot(Spatial_4DE) +
+  geom_point(
+    aes(
+      x = Year,
+      y = m,
+      colour = RCP
+    )
+  ) +
+  facet_wrap(~RegArea,
+             scales = "free")
+
+### Environmental varibales of the region
+
+## Temp
+
+# Variables
+Model = c("GFDL","IPSL","MPIS")
+RCP = c("rcp26","rcp85")
+
+Grid <- DBEM_Corrected %>% 
+  select(INDEX) %>% 
+  left_join(IPHC_Reg_DBEM_df,
+            by = "INDEX") %>% 
+  filter(RegArea %in% c("4D","4E")) %>% 
+  select(INDEX)
+
+Variables <- c("Temperature","Salinity","Ice")
+
+F_BData <- NULL
+F_SData <- NULL
+F_MData <- NULL
+F_RData <- NULL
+Years <- seq(2005,2100,1)
+
+all_Grid <- seq(1,259200,1)
+
+for(v in 3:3){
+  # Loop through RCPs
+  for(r in 1:2){
+    # Loop through  variables
+    for(m in 1:3){
+      # Loop through years
+      for(y in 1:length(Years)){
+
+        Data <- getEnvVar(yr = Years[y],
+                          Model = Model[m],
+                          Variable = Variables[v],
+                          RCP = RCP[r]
+        ) %>% 
+          mutate(INDEX = all_Grid) %>% 
+          filter(INDEX %in% Grid$INDEX)
+
+        if(y == 1){
+
+          F_BData <- Data[1]
+
+        }else{
+
+          F_BData <- cbind(Data[1],F_BData)
+
+        }
+      }
+
+      colnames(F_BData) <- Years
+
+      F_BData <- F_BData %>% 
+        gather(Year,Value,1:426) %>% 
+        mutate(Model = Model[m],
+               RCP = RCP[r],
+               Variable = Variables[v])
+
+      if(m == 1){
+
+        F_MData <- F_BData
+
+      }else{
+
+        F_MData <- rbind(F_BData,F_MData)
+      }
+    }
+
+    if(r == 1){
+
+      F_RData <- F_MData
+
+    }else{
+
+      F_RData <- rbind(F_RData,F_MData)
+    }
+  }
+
+  if(v == 1){
+
+    F_VData <- F_RData
+
+  }else{
+
+    F_VData <- rbind(F_VData,F_RData)
+  }
+
+} # closes variable loop
+
+write.csv(F_VData,
+          "Environmental_Data_Halibut.csv",
+          row.names = F)
+
+### Exploration at the biological level
+
+# exploited_species_list <- fread("/Volumes/DATA/PROJECTION exploited species ENM/exploited_species_list.csv")
+# 600514
+
+# Isolate Regions
+
+DE <- IPHC_MCP_Change %>% 
+  filter(RegArea %in% c("4D","4E"))
+
+#Load Halibut Species preferences
+Halibut <- getTaxInfo(600514)
+# Demersal
+# HabAssocSal 0 1 1 -1 -1
+# HabAssocIce 0
+
+# Temp
+TTPop <- getTTP(600514,"Avg") %>% 
+  filter(TempPP > 0)
+
+Min_T <- min(TTPop$Temp)
+Max_T <- max(TTPop$Temp)
+
+# Halibut_Temp 2
+# quant05 -2 
+# quant25 0 
+# quant50 2
+# quant75 5
+# quant95 11
+```
 

### 2019-11-04 Ecol_Manuscript_Draft.Rmd
Inlcuded the here package for knitting to the thesis

@@
 output:
-  word_document: default
+  # word_document: default
   pdf_document: default
@@
 
-```{r setup, eval=T, echo=F, warning=F,message=F, results='hide'}
+```{r Ch3_setup, eval = T, echo=F, warning=F,message=F, results='hide'}
 
@@
 packages <- c(
+  "here", # For all thesis
   "readxl", # Read dataframe
@@
   "sf",
+  "knitr", # Nice tables
+  "kableExtra", # Nice tables
   # "sp",
   # "rgdal", #Spatial analysis 
-  "tools"#, #Spatial analysis 
-  # "png", # For reading plots in chunk codes
-  # "grid" # For reading plots in chunk codes
+  "tools", #Spatial analysis 
+  "png", # For reading plots in chunk codes
+  "grid" # For reading plots in chunk codes
 )
@@
 
-![Fig 1. Map of North America with the regulatory areas of the IPHC and the NAFO sub-region related to the Gulf of Main agreement](./Figures/Ecol//Fig1.png)
+```{r Figure_1, eval = T, echo =F, fig.cap="Map of North America with the regulatory areas of the IPHC and the NAFO sub-region related to the Gulf of Main agreement"}
+
+img <- readPNG(here("Figures/Ecol/Fig1.png"))
+grid.raster(img)
+
+```
+
+<!-- ![Fig 1. Map of North America with the regulatory areas of the IPHC and the NAFO sub-region related to the Gulf of Main agreement](./Figures/Ecol//Fig1.png) -->
 
@@
 
-```{r Load_Data, echo = F, eval = T, results='hide', warning=F,message=F}
+```{r Load_Data, echo = F, eval = F, results='hide', warning=F,message=F}
 
@@
 #Data provided by Vicki Lam
-EEZIDs_List <- read_excel("./Data/Spatial/Updated_EEZList_17June2016.xlsx")
-EEZ_CellID <- read_excel("./Data/Spatial/EEZ_CellID.xlsx")
+EEZIDs_List <- read_excel(here("Data/Spatial/Updated_EEZList_17June2016.xlsx"))
+EEZ_CellID <- read_excel(here("Data/Spatial/EEZ_CellID.xlsx"))
 colnames(EEZ_CellID) <- c("EEZID","INDEX")
@@
 # DBEM Coordinate system
-Coor <- fread("./Data/Spatial/Lon_Lat_DBEM.txt",header = FALSE)
+Coor <- fread(here("Data/Spatial/Lon_Lat_DBEM.txt"),header = FALSE)
 colnames(Coor) <- c("INDEX","Longitude","Latitude")
@@
 # From (/Users/jpalacios/Documents/UBC/Oceans_Project/Distribution/By Cell/By_Cell_Analysis.Rmd)
-Raw_DBEM_Results <- data.table::fread("./Data/Distribution/Raw_Data.csv") %>% 
+Raw_DBEM_Results <- data.table::fread(here("Data/Distribution/Raw_Data.csv")) %>% 
   filter(Species != "Anoplopoma fimbria") #Remove
@@
 
-```{r Changes_Data_All, eval =T, echo = F, fig.height=8, fig.width=12}
+```{r Changes_Data_All, eval = F, echo = F, fig.height=8, fig.width=12}
 
@@
 
-![Fig 2.
-Percentage change of MCP of transboundary fisheries of North America for mid century (2046-2055) referent to 2005-2014 under a A) low emission scenario and; B) high emission scenario.](./Figures/Ecol/Fig2.png)
+```{r Figure_2, eval = T, echo =F, fig.cap="Percentage change of MCP of transboundary fisheries of North America for mid century (2046-2055) referent to 2005-2014 under a A) low emission scenario and; B) high emission scenario."}
+
+img <- readPNG(here("Figures/Ecol/Fig2.png"))
+grid.raster(img)
+
+```
+
+<!-- ![Fig 2.
+Percentage change of MCP of transboundary fisheries of North America for mid century (2046-2055) referent to 2005-2014 under a A) low emission scenario and; B) high emission scenario.](./Figures/Ecol/Fig2.png) -->
 
@@
 
-```{r Figure_3, eval = F, echo =F, fig.cap="Percentage Change of MCP for Species managed by the IPHC.
+```{r Figure_3, eval = T, echo =F, fig.cap="Percentage Change of MCP for Species managed by the IPHC.
 A, RCP 2.6 represents a low emission scenario (high mitigation).
@@
 
-img <- readPNG("/Users/jpalacios/Documents/UBC/Oceans_Project/Manuscript/Results/Fig3.png")
+img <- readPNG(here("Figures/Ecol/Fig3.png"))
 grid.raster(img)
@@
 
-![Fig 3.
-Percentage change of MCP for species managed by the IPHC for mid century (2046-2055) referent to 2005-2014 under a A) low emission scenario and B) high emission scenario.](./Figures/Ecol/Fig3.png)
+<!-- ![Fig 3.
+Percentage change of MCP for species managed by the IPHC for mid century (2046-2055) referent to 2005-2014 under a A) low emission scenario and B) high emission scenario.](./Figures/Ecol/Fig3.png) -->
 
@@
 
-```{r Figure_4, eval = T, echo =F, fig.cap="Percentage change of stock-share ratio for IPHC under two RCPs for Mid century (2046-2055)"}
-
-Fig4 <- readPNG("~/Documents/UBC/Oceans_Project/Manuscript/Results/Fig4.png")
+```{r Figure_4, eval = T, echo =F, fig.cap="Percentage change of stock-share ratio for IPHC under A) low emission scenario and B) high emission scenario for mid century (2046-2055) referent to 2005-2014."}
+
+Fig4 <- readPNG(here("Figures/Ecol/Fig4.png"))
 grid.raster(Fig4)
@@
 
-![Fig 4. Percentage change of stock-share ratio for IPHC under A) low emission scenario and B) high emission scenario for mid century (2046-2055) referent to 2005-2014.](./Figures/Ecol/Fig4.png)
+<!-- ![Fig 4.
+Percentage change of stock-share ratio for IPHC under A) low emission scenario and B) high emission scenario for mid century (2046-2055) referent to 2005-2014.](./Figures/Ecol/Fig4.png) -->
 
@@
 
-Fig4 <- readPNG("./Figures/Ecol/Fig5.png")
+Fig5 <- readPNG(here("Figures/Ecol/Fig5.png"))
 grid.raster(Fig5)
@@
 
-![Fig 5. Percentage change of MCP in the Gulf of Main under, A) low emission scenario; and B) high emission for mid century (2041-2060) referent to present (2005-2014)](./Figures/Ecol/Fig5.png)
+<!-- ![Fig 5.
+Percentage change of MCP in the Gulf of Main under, A) low emission scenario; and B) high emission for mid century (2041-2060) referent to present (2005-2014)](./Figures/Ecol/Fig5.png) -->
 
@@
 
-Fig4 <- readPNG("./Figures/Ecol/Fig6.png")
-grid.raster(Fig5)
+Fig6 <- readPNG(here("Figures/Ecol/Fig6.png"))
+grid.raster(Fig6)
 
@@
 
-![Fig 6. Changes in MCP stock-share ratio for Gulf of Main under (A) low emission scenario; and (B) high emission for mid century (2041-2060) referent to 2005-2014](./Figures/Ecol/Fig6.png)
+<!-- ![Fig 6. Changes in MCP stock-share ratio for Gulf of Main under (A) low emission scenario; and (B) high emission for mid century (2041-2060) referent to 2005-2014](./Figures/Ecol/Fig6.png) -->
 
@@
 
-```{r Functions, eval = F}
+```{r Functions, eval = F, echo = F}
 
@@
 
-```{r Old analysis, eval = F}
+```{r Old analysis, eval = T, echo = T}
 

### 2020-01-15 Ecol_Manuscript_Draft.Rmd
Re- organized files and folders

@@
 
-```{r Ch3_setup, eval = T, echo=F, warning=F,message=F, results='hide'}
+```{r setup, eval = T, echo=F, warning=F,message=F, results='hide'}
 
@@
 
-```{r Figure_1, eval = T, echo =F, fig.cap="Map of North America with the regulatory areas of the IPHC and the NAFO sub-region related to the Gulf of Main agreement"}
+```{r Figure_1, eval = T, echo = F, fig.cap="Map of North America with the regulatory areas of the IPHC and the NAFO sub-region related to the Gulf of Main agreement"}
 
@@
 
-```{r Changes_Per_Species_T, eval=F, echo=F}
+```{r Changes_Per_Species_T, eval = F, echo = F}
 
@@
 
-```{r Figure_4, eval = T, echo =F, fig.cap="Percentage change of stock-share ratio for IPHC under A) low emission scenario and B) high emission scenario for mid century (2046-2055) referent to 2005-2014."}
+```{r Figure_4, eval = T, echo = F, fig.cap="Percentage change of stock-share ratio for IPHC under A) low emission scenario and B) high emission scenario for mid century (2046-2055) referent to 2005-2014."}
 
@@
 
-```{r Figure_5, eval = T, echo =F, fig.cap="Percentage change of MCP in the Gulf of Main under, A) low emission scenario; and B) high emission for mid century (2041-2060) referent to present (2005-2014)"}
+```{r Figure_5, eval = T, echo = F, fig.cap="Percentage change of MCP in the Gulf of Main under, A) low emission scenario; and B) high emission for mid century (2041-2060) referent to present (2005-2014)"}
 
@@
 
-```{r Old analysis, eval = T, echo = T}
+```{r Old analysis, eval = F, echo = F}
 
@@
 
-```{r IPHC_Proportion_EEZ, eval=F, echo = F, message=F, warning=F}
+```{r IPHC_Proportion_EEZ, eval = F, echo = F, message=F, warning=F}
 
@@
 
-```{r GB_Results_All, eval=F, echo = F}
+```{r GB_Results_All, eval = F, echo = F}
 

### 2020-01-24 Manuscript_Draft.Rmd
Started corrections on manuscript

--- 2019-09-14 Ecol_Analysis/Manuscript_Draft.Rmd
@@
 author: "Juliano Palacios-Abrantes^1^ U. Rashid Sumaila^1^ William W. L. Cheung^1^"
-subtitle: "[THIRD DRAFT]"
+subtitle: "[Response to Reviewers]"
 date: "^1^ Institute for the Oceans and Fisheries, University of British Columbia, Vancouver, Canada"
@@
 End_End <- paste(2099);End_End
+
+Data_Path <- "~/Documents/UBC/OC_Special_Issue/Ecol/Data"
+
 ```
@@
 Firstly, we projected changes in potential catch of 33 transboundary stocks of North America in the 21^st^ century based on multiple Earth system models’ simulations and species distribution models, under two climate change scenarios.
-We then look at the specific cases of the International Pacific Halibut Commission that manages pacific halibut (*Hippoglossus stenolepis*) and a resource sharing agreement in the Gulf of Maine for cod (*Gadus morhua*), haddock (*Melanogrammus aeglefinus*) and yellowtail flounder (*Limanda ferruginea*).
+We then look at the specific cases of the International Pacific Halibut Commission that manages pacific halibut (*Hippoglossus stenolepis*) and a resource sharing **DV arrangement** in the Gulf of Maine for cod (*Gadus morhua*), haddock (*Melanogrammus aeglefinus*) and yellowtail flounder (*Limanda ferruginea*).
 Results show that, even under a low emission scenario, most transboundary fish stocks sharing ratios, i.e., the proportion of the total catch of a fish stock taken by a given country, will change by 2050 relative to present in the direction as expected from the effects of ocean warming.
@@
 <!-- ##### First paragraph of paper summary -->
-Transboundary fisheries are defined as fish stocks that move freely between (*i*) Countries economic exclusive zones (EEZs) and (*ii*) between EEZs and the high seas (also called straddling stocks) [@Song:2017iua].
-The management of transboundary stocks can be analized using game theory, as often, success depends on effective cooperation between parties [@Munro:2002uf; @Sumaila:2013hv].
-Therefore, in 1985, the United Nations incentivized actions to cooperate on the management of transboundary fisheries through the Law of the Seas (UNCLOS) [@UnitedNations:1986tl].
-Today, an estimated 347 [@Teh:2015gd] to 1500 [@Caddy:1997ue] fish stocks cross national borders, some of them jointly managed by two or more countries.
+**RA In 1982, the United Nations Law of the Seas (UNCLOS) formalized the concept of economic exclusive zones (EEZs) creating what we know today as transboundary stocks.
+Transboundary stocks move freely between (*i*) Countries EEZs and (*ii*) between EEZs and the high seas (also called straddling stocks) [@Song:2017iua].
+While not a law, UNCLOS incentivized actions to cooperate on the management of transboundary stocks [@UnitedNations:1986tl].
+Today, game theory is one of the most common approaches used to analyze the management of transboundary stocks, as often, success depends on effective cooperation between parties** [@Munro:2002uf; @Sumaila:2013hv].
+An estimated 347 [@Teh:2015gd] to 1500 [@Caddy:1997ue] fish stocks cross national borders, some of them jointly managed by two or more countries.
 These stocks are responsible for almost 50% of these countries total fish catches [@Teh:2015gd].
 Transboundary stocks such as salmon (*Oncorhynchus spp.*), Pacific halibut (*Hippoglossus stenolepis*), and Atlantic cod (*Gadus morhua*) are of utmost importance for Canada and the United States (US).
-Management of these stocks is extremely hard due to the participation of several fishing “players”, different countries and sometimes jurisdictions within a country, the migration patterns of the stock, and their abundance fluctuation within space and time [@Munro:2002uf].
+Management of these stocks **RA can be convoluted** due to the participation of several fishing “players”, different countries and sometimes jurisdictions within a country, the migration patterns of the stock, and their abundance fluctuation within space and time [@Munro:2002uf].
 
@@
 Moreover, these shifts are projected to continue towards the end of the 21^st^ century [@Cheung:2018hz] at a rate of tens to hundreds of km and/or tens of meters per decade towards the poles and/or deeper waters, respectively, although there will be regional variations [@Morley:2018fn].
-As a result, some countries or management jurisdictions may see more transboundary stocks and their catches shifting into their waters while others will stand to lose [@Miller:2013iv; @Pinsky:2018cb].
+As a result, some countries or management jurisdictions may see more transboundary **RA fisheries** and their catches shifting into their waters while others will stand to lose [@Miller:2013iv; @Pinsky:2018cb].
 Nevertheless, management rules for shared stocks (e.g.
@@
 
-Transboundary fisheries between Canada and the US offer a unique lens to understand the extent to which climate-induced distributional shifts will challenge the future sustainability of these fisheries.
+Transboundary **RB stocks** between Canada and the US offer a unique lens to understand the extent to which climate-induced distributional shifts will challenge the future sustainability of these fisheries.
 Canada and the US have a long history of fisheries cooperation [@Song:2017va].
 They participate in diverse, jointly managed, commercial transboundary stocks through various fisheries management organizations [@Merten:2015tu].
-Cooperation schemes vary by fisheries stocks, regulatory areas, legal terms of agreement, and management measures, among others (Fig.
-1).
-In the Atlantic coast, Canada and the US are part of the Northwest Atlantic Fisheries Organization (NAFO) that oversees the management of 19 stocks of 11 transboundary species (although around 41 taxa are fished within Canadian and US waters) from southern Gulf of Maine to Greenland[^NAFO].
-Within NAFO's region 5Z, Canada and the US have a "Resource Sharing Understanding" (hereafter referred to "GoM agreement") to set catch-limits of Atlantic cod (*Gadus morhua*), haddock (*Melanogrammus aeglefinus*) and, yellowtail flounder (*Limanda ferruginea*) [@Soboil:2006gw; @CIA:2017uta].
+Cooperation schemes vary by fisheries stocks, regulatory areas, legal terms of agreement, and management measures, among others.
+In the Atlantic coast, Canada and the US are part of the Northwest Atlantic Fisheries Organization (NAFO) that oversees the management of 19 stocks of 11 transboundary species (although around 41 taxa are fished within Canadian and US waters) from southern Gulf of Maine to Greenland [^NAFO].
 In the Pacific coast, Pacific halibut (*Hippoglossus stenolepis*) is managed under the International Pacific Halibut Commission (IPHC) [@IPHCSecreatriat:2017uz].
@@
 [^NAFO]: Northwest Atlantic Fisheries Organization, Available at https://www.nafo.int/Science/Species
+
+It is expected that climate induced shifts in stock distribution **RA will** affect the rules in place that **RA keep** these treaties alive.
+Therefore, the main objective of this paper is to assess the level of exposure of international fisheries management treaties between Canada and the US to climate change impacts through shifts in stock distributions.
+Specifically, we rely on a species distribution model and scenario planning to project the changes in the distribution of 33 fish stocks jointly managed by Canada and the US.
+Moreover, we use two specific treaties as case studies (IPHC and an **DV arrangement** for the Gulf of Maine) to explore the potential impacts that climate change will have on selected transboundary **RB stocks** management.
+Finally, we explore similar situations around the world and identify opportunities to improve the adaptability of transboundary **RB stocks** management to climate change in North America.
+Despite an overall expectation of species following a poleward shift, **RA important geographic constraints (e.g.
+Gulf of Alaska representing a latitudinal block) [@Kleisner:2016je], geo-political features** (e.g.
+the localization of Alaska in reference to Canada and the contiguous states), and management rules (e.g.
+quota allocations, spatial management rules) may play an important role in the redistribution of benefits.
+Understanding these stocks shifts will shed a light on future conditions and inform decision makers on the paths to follow under a changing climate.
+
+# METHODS
+
+#### Study Area and Fisheries
+
+The current study focuses on transboundary **RB stocks** jointly managed by Canada and the US for both the Atlantic and the Pacific coasts.
+The analysis was carried out within the 200 nautical miles of both nation's EEZ from the Gulf of Mexico to The Labrador Sea in the Atlantic, and from California to Chukchi Sea, in the Pacific coast.
+The species analyzed (**Table A2.1**) were selected based on five treaties in both the Atlantic and Pacific coast of North America (Table 1).
+All species under the IPHC, PSC, WT, and the Gulf of Maine **DV arrangement** were analyzed as these treaties are management agreements between Canada and the US.
+However, in the case of NAFO, their management covers over 41 taxa and its governance extends to international waters and the EEZ of Greenland.
+Therefore, a subset of 26 species reported was made based on those fished in NAFO regions that fall within the EEZs of Canada and the US (NAFO subareas 2's, 3's with the exception of 3M and 3N and limited to the EEZ, 4's,5's and 6 A,B, and C.) [@NAFO].
+Data related to fisheries was gathered from the *Sea Around Us* from 1951 to 2014 [@Zeller2016].
+
+We selected two case studies, the IPHC agreement and the Gulf of Maine arrangement (hereafter refered as GoM arrangement), in order to better discuss the implications that climate chage could have in the management of transboundary stocks.
+For the IPHC, we used the most updated spatial regulatory data provided by the Commission [@IPHCSecreatriat:2017uz; @IPHC:2019wt].
+For this specific case, we considered Alaska as a separate entity, the US contiguous states as a second one (Washington, Oregon and California), and lastly British Columbia (Canada).
+For the GoM **DV arrangement** we used NAFO's divisions 5Y, 5Ze, and 4X within latitudes 46.2°N and 41.5°S, and longitudes -72°W and -64°E (Fig.
+1).
 
@@
 
-![Fig 1. Map of North America with the regulatory areas of the IPHC and the NAFO sub-region related to the Gulf of Main agreement](./Results/Fig1.png)
-
-It is expected that climate induced shifts in stock distribution affect the rules in place that keeps these treaties alive.
-Therefore, the main objective of this paper is to assess the level of exposure of international fisheries management treaties between Canada and the US to climate change impacts through shifts in stock distributions.
-Specifically, we rely on a species distribution model and scenario planning to project the changes in the distribution of 33 fish stocks jointly managed by Canada and the US.
-Moreover, we use two specific treaties as case studies (IPHC and the GoM agreement) to explore the potential impacts that climate change will have on selected transboundary fisheries management.
-Finally, we explore similar situations around the world and identify opportunities to improve the adaptability of transboundary fisheries management to climate change in North America.
-Despite an overall expectation of species following a poleward shift, important geographic features (e.g.
-Gulf of Alaska representing a latitudinal block), geo-political (e.g.
-the localization of Alaska in reference to Canada and the contiguous states), and management rules (e.g.
-quota allocations, spatial management rules) may play an important role in the redistribution of benefits.
-Understanding these stocks shifts will shed a light on future conditions and inform decision makers on the paths to follow under a changing climate.
-
-# METHODS
-
-#### Study Area and Fisheries
-
-The current study focuses on transboundary fisheries jointly managed by Canada and the US for both the Atlantic and the Pacific coasts.
-The analysis was carried out within the 200 nautical miles of both nation's EEZ from the Gulf of Mexico to The Labrador Sea in the Atlantic, and from California to Chukchi Sea, in the Pacific coast (Fig.
-1).
-Subsets of the total area were carried for both the IPHC and the Gulf of Maine agreement.
-For the IPHC, we used the most updated spatial regulatory data provided by the Commission [@IPHCSecreatriat:2017uz].
-For this specific case, we considered Alaska as a separate entity, the US contiguous states as a second one (Washington, Oregon and California), and lastly British Columbia (Canada).
-For the GoM agreement we used NAFO's divisions 5Y, 5Ze, and 4X within latitudes 46.2°N and 41.5°S, and longitudes -72°W and -64°E (Fig.
-1).
+![Fig 1. Map of North America with the regulatory areas of the IPHC and the NAFO sub-region related to the Gulf of Main **DV arrangement**](./Figures/Fig1.png)
 
@@
 #Data provided by Vicki Lam
-EEZIDs_List <- read_excel("~/Documents/UBC/Oceans_Project/Distribution/By Cell/Cell_Data/Updated_EEZList_17June2016.xlsx")
-EEZ_CellID <- read_excel("~/Documents/UBC/Oceans_Project/Distribution/By Cell/Cell_Data/EEZ_CellID.xlsx")
-
+EEZIDs_List <- read_excel(paste(Data_Path,"/Spatial/Updated_EEZList_17June2016.xlsx",sep=""))
+EEZ_CellID <- read_excel(paste(Data_Path,"/Spatial/EEZ_CellID.xlsx",sep=""))
 colnames(EEZ_CellID) <- c("EEZID","INDEX")
@@
 # DBEM Coordinate system
-Coor <- fread("~/Documents/UBC/Oceans_Project/Distribution/DBEM/Data/Lon_Lat_DBEM.txt",header = FALSE)
+Coor <- fread(paste(Data_Path,"/Spatial/Lon_Lat_DBEM.txt",sep=""),header = FALSE)
 colnames(Coor) <- c("INDEX","Longitude","Latitude")
@@
 
-path_world <- "~/Documents/UBC/Oceans_Project/Manuscript/Data/Spatial_Data/TM_WORLD_BORDERS"
+path_world <- paste(Data_Path,"/Spatial/TM_WORLD_BORDERS",sep="")
 file_name <- "TM_WORLD_BORDERS"
@@
 
-path_eez <- ("~/Documents/UBC/Oceans_Project/Manuscript/Data/Spatial_Data/World_EEZ_v10_2018")
+path_eez <- paste(Data_Path,"/Spatial/World_EEZ_v10_2018",sep="")
 #The File
@@
 # Now we load IPHC shapefiles ####
-path_IPHC <- ("~/Documents/UBC/Oceans_Project/Distribution/Data/IPHC/IPHC_RegulatoryAreas/")
+path_IPHC <- paste(Data_Path,"/Spatial/IPHC_RegulatoryAreas/",sep="")
 
@@
 
-path_NAFO <- ("~/Documents/UBC/Oceans_Project/Distribution/Data/Spatial/NAFO/")
+path_NAFO <- paste(Data_Path,"/Spatial/NAFO",sep="")
 #The File
@@
 
-The species analyzed (**Table A2.1**) were selected based on five treaties in both the Atlantic and Pacific coast of North America (Table 1).
-All species under the IPHC, PSC, WT, and the GoM agreement were analyzed as these treaties are management agreements between Canada and the US.
-However, in the case of NAFO, their management covers over 41 taxa and its governance extends to international waters and the EEZ of Greenland.
-Therefore, a subset of 26 species reported was made based on those fished in NAFO regions that fall within the EEZs of Canada and the US (NAFO subareas 2's, 3's with the exception of 3M and 3N and limited to the EEZ, 4's,5's and 6 A,B, and C.) [@NAFO].
-Data related to fisheries was gathered from the *Sea Around Us* from 1951 to 2014 [@Zeller2016].
+##### The International Pacific Halibut Comission (IPHC)
+
+The IPHC is a convention established in 1923 by Canada and the United States that oversees the management of Pacific halibut (*Hippoglossus stenolepis*), a flatfish that can grow as much as 500 pounds (2.4 m) which inhabits the continental shelf of the northern Pacific Ocean [@IPHC:2014tz].
+The IPHC Convention Area covers the Pacific EEZ of Canada and the US from California to the Berring Sea [@IPHC:2019wt] and is divided in 12 regions (Fig 1).
+Most of the Pacific halibut population is estimated to be in region 3 (51.2%), followed by regions 2 and 4ACDE (23.1% and 20.4%, respectively), and lastly region 4B with only 5.2% of the stock distribution [@IPHC:2018vz].
+In terms of management, the IPHC implements a total allowable catch (TAC) in addition to a series of regulations to control fishing effort.
+Every year, the IPHC carries an fishery-independent set-line survey from Oregon to the Berring sea to support the estimation of next fishing season's fishing limits [@IPHC:2018vz].
+Thus, the TAC is allocated by region according to the population distribution with sector 3A historically having almost 1/3 of the TAC and almost half of the commercial catch.
+The TAC is divided between recreational, subsistence and commercial fishery, with a portion set aside for bycatch of other fisheries [@IPHC:2019wt].
+The commercial fishing season starts in March ending around November whith restrictions allowing only set line gear with J-type hooks targeting individuals over 81.3 cm (32 inches) with head on [@IPHC:2019wt].
+
+##### The Gulf of Maine Agreement
+
+Since 1998 Canada and the US celebrate a "Resource Sharing Understanding" to manage three groundfish stocks within the Gulf of Maine (Georges Bank) [@TRAC:2016wu].
+Under the GoM **DV arrangement**", both countries set catch-limits for George Bank's Atlantic cod (*Gadus morhua*), and Eastern George Bank's haddock (*Melanogrammus aeglefinus*) and, yellowtail flounder (*Limanda ferruginea*) [@Pudden:2007bo; @CIA:2017uta]; **Koubrak and VanderZwaag, this Special Feature**.
+In terms of management, the quota allocation formula includes a combination of future stock's distribution patterns produced by yearly surveys and historical utilization patterns favoring Canda in terms of Cod (82%) and the US for Haddock (66%) and Y.
+flounder (66%), althou these patterns can change on yearly bases [@Pudden:2007bo; @TRAC:2016wu].
+In addition, Canada and the US conduct jointly surveys and enforce activities of the maritime border.
+The task of the committee is just to inform Canada and the US who ultimatley take single management decissions.
+In terms of manangement, the US has a multi species harvest control with area and season cloasures, mesh sizes, effort control.
+US mobile gear vessels that use bottom otter trawl gear [@Soboil:2006gw].
+In contrast, Canada has a more strict regulatory system implaced based on a quota system in addition to limited-entery licensig, fleet allocations, mesh sizes, fish size regulation, among other input controls [@Soboil:2006gw].
+Canada inshore vessels fish Cod with longline and gillnet while haddock is mainly caught with bottom otter trawl gear [@Soboil:2006gw].
 
@@
                            "Northwest Atlantic Fisheries Organization (NAFO)",
-                           "Gulf of Main's Agreement (GoM Agreement)"),
+                           "Gulf of Main's Arrangement (GoM Arrangement)"),
                        Species =
@@
 
-where $X_{t}$ is the future agregated MCP for two periods, $t_1$ = mid 21^st^ century (2045-2055); and $t_3$ = end of 21^st^ century (2090-2099), and $t_0$ is the present aggregated MCP ($\mu$ 2005-2014).
+**RB where $X_{t}$ is the future averaged MCP for each of the two time periods analized in this study and $t_0$ is the present averaged MCP ($\mu$ `r Beg_In`-`r Beg_End`).
+This way, Equ.
+2 shows the percentage change in MCP relative to today ($t_0$) by mid 21^st^ century when $X_T$ = $\mu$ `r Mid_In`-`r Mid_End`, and end of 21^st^ century when $X_T$ = $\mu$ `r End_In`-`r End_End`).
+The rationale between choosing these time periods was to provide a relative short-term projection (mid-century) that would be more policy-relevant but also show the long term trend.**
 
@@
 
-In addition, we borrowed the concept of “threat point” from game theory (see Sumaila et al., this Volume) and estimate the change in the $\hat{MCP}$ that each country would have for each species (hereafter referred as stock-share ratio), for both the IPHC and the GoM agreement.
+In addition, we borrowed the concept of “threat point” from game theory **RA defined as the minimum payoff that a player is willing to receive in order to cooperate with other players** (see Sumaila et al., this Volume).
+Thus we estimate the change in the $\hat{MCP}$ **RA (threat point)** that each country **RA (players)** would have for each species (hereafter referred as stock-share ratio), for both the IPHC and the GoM **DV arrangement**.
+**RA We define stock-share ratio as the proportion of the stock's distribution within the study area that each country has**.
 For this, we first modify equation 1, to estimate the aggregated yearly mean MCP of each species per region.
@@
 #Data provided by Vicki Lam
-
-EEZIDs_List <- read_excel("~/Documents/UBC/Oceans_Project/Distribution/By Cell/Cell_Data/Updated_EEZList_17June2016.xlsx")
-
-EEZ_CellID <- read_excel("~/Documents/UBC/Oceans_Project/Distribution/By Cell/Cell_Data/EEZ_CellID.xlsx")
-
+EEZIDs_List <- read_excel(paste(Data_Path,"/Spatial/Updated_EEZList_17June2016.xlsx",sep=""))
+EEZ_CellID <- read_excel(paste(Data_Path,"/Spatial/EEZ_CellID.xlsx",sep=""))
 colnames(EEZ_CellID) <- c("EEZID","INDEX")
@@
 # From (/Users/jpalacios/Documents/UBC/Oceans_Project/Distribution/By Cell/By_Cell_Analysis.Rmd)
-Raw_DBEM_Results <- data.table::fread("~/Documents/UBC/Oceans_Project/Manuscript/Data/Raw_Data.csv") %>% 
+Raw_DBEM_Results <- data.table::fread(paste(Data_Path,"/Distribution/Raw_Data.csv",sep="")) %>% 
   filter(Species != "Anoplopoma fimbria") #Remove
@@
 
-### North American transboundary fisheries are shifting poleward
+### North American transboundary **RB stocks** are shifting poleward
 
@@
 # Path to save the plots
-Path <- "~/Documents/UBC/Oceans_Project/Manuscript/Results/North_America"
+Path <- "./Results/North_America"
 RCP = c("GFDL26F1","IPSL26F1","MPI26F1") #Low RCP
@@
   summarise_at(vars(Beg_In:End_End), sum,na.rm=T) %>% # Sum the MCP of all species in each index by model
-  # select(INDEX,Model,Beg_In:Beg_End) %>% 
   gather("Year","MCP",Beg_In:End_End) %>% 
@@
   mutate(
-    Model_Agreement = ifelse(Model_Agreement == 1, "Agree","Disagree")
+    Model_Agreement = ifelse(Model_Agreement == 1, "Agree","Disagree"),
+    Model_Agreement_sd = ifelse(abs(Mean_ESM_MCP_Chng) < sd_ESM_MCP_Chng*2,"Disagree","Agree")
   ) %>% 
@@
              ),
-             size = 0.01,
-             alpha = 0.1,
-             shape = 4,
+             size = 0.1,
+             # alpha = 0.5,
+             shape = 16,
              color = "grey20"
@@
 
-  ggsave("New_plot.tiff",
+  ggsave("New_plot.png",
          plot = p,
          width = 16,
-         height = 10,
+         height = 8,
          units = "in",
@@
 ![Fig 2.
-Percentage change of MCP of transboundary fisheries of North America for mid century (2046-2055) referent to 2005-2014 under a A) low emission scenario and; B) high emission scenario.](./Results/Fig2.png)
+Percentage change of MCP of transboundary fisheries of North America for mid century (2046-2055) **RA referenced** to 2005-2014 under a A) low emission scenario and; B) high emission scenario.
+Points represent areas where at least one model do not agree in the direction of change](./Results/Fig2.png)
 
@@
 
-In consequence, country's share-ratio of different species would change in the direction as expected from the effects of ocean warming, regardless of the RCP scenario.
+In consequence, **RA each** country's share-ratio of different species would change in the direction as expected from the effects of ocean warming, regardless of the RCP scenario.
 Overall, shifts will be amplified under the high emission scenario relative to the low greenhouse emission scenario pathway (Table 2).
-While in 2050, the average shift of species will be higher for East Canada and lower for East US under the high emission scenario, the stock-share ratio of some species is expected to increase more than 50% as in the case of Atlantic menhaden (*Brevoortia tyrannus*) in Eastern Canada, and decrease by more than 50% for species such as Cusk (*Brosme brosme*) in the Eastern US under a low emission scenario.
-By the end of the 21^st^ century, losses will intensify with the eastern US potentially losing on average 15.2% or 46% of stock-share, depending on the scenario.
+
+Table 2.
+Average (standard deviation) of 33 transboundary species stock-share of all models for each EEZ and emission scenario for mid and end of the 21st century.
+Averages might not add to 100% due to model differences (e.g., standard deviation)
 
@@
 However, such changes will vary depending on the species, resulting in management consequences related to the rules placed by the different treaties.
-In the case of the IPHC, at least three of the 12 regulatory areas will see a reduction in MCP of Pacific halibut by 2050 in reference to current MCP of each area, regardless of the climate change scenario (Fig.
+In the case of the IPHC, at least one third of regulatory areas will see a reduction in MCP of Pacific halibut by 2050 relative to current MCP of each area, regardless of the climate change scenario (Fig.
 3).
 Poleward shifts might be constrained by the geopolitical position of countries, as well as geographic design of the coastline.
-It is likely that the stock shift from the US contiguous states towards Canada will offset the shift of the former towards northern regions, resulting in undetectable changes in areas 2B and 2C.
-Similarly, to the potential increase in MCP of regulatory areas 3B and 4ABCE along the Aleutian Islands and Bering Sea.
+It is likely that the stock shift from the U.S.
+contiguous states towards Canada will offset the shift of the former towards northern regions, resulting in undetectable changes in areas 2B and 2C under both climate change scenarios.
+The potential movement of halibut westward will increase the MCP of regulatory areas 3B (under a low emission scenario) and 4ABCE along the Aleutian Islands and Bering Sea.
+
+**Region 4D, the most poleward region of the IPHC convention area is expected to gain MCP under high emission as halibut suitable habitat expands as sea ice retreats [@IPCC:2019to].
+In contrast, under a low emission scenario sea ice is expected to stabilize towards mid century, thus providing less habitat suitabillity for halibut, resulting in undetectable changes in MCP for the region (Fig 3.
+B).
+If the high emission scenario continues towards the end of the century only the regions RA-on-the-northwest-of 3B will see a gain in MCP (Fig.
+A1.2).
+In contrast, polar regions 4DE will continue to see a reduction in MCP as sea ice stabilizes**
 
@@
 # Path for saving plots
-Path <- "~/Documents/UBC/Oceans_Project/Manuscript/Results/IPHC/Region"
+Path <- "./Results/IPHC"
 RCP = c("GFDL26F1","IPSL26F1","MPI26F1") #Low RCP
@@
                     "Model_Agreement_Index" = paste(length(unique(Direction)),collapse = ";"),
-                    "Model_Agreement" = paste(Direction,collapse = ";")
+                    "Model_Agreement_Direction" = paste(Direction,collapse = ";")
                )
@@
   mutate(
-    Model_Agreement = ifelse(Model_Agreement == 1, "Agree","Disagree")
-  ) %>% 
+    Model_Agreement = ifelse(Model_Agreement_Index == 1, "","*"),
+    Model_Agreement_sd = ifelse(abs(Mean_ESM_MCP_Chng) < sd_ESM_MCP_Chng*2,"No","Yes")
+  ) %>% 
+  ungroup() %>% 
   mutate_at(vars(Mean_ESM_MCP_Chng,
@@
 IPHC_DBEM_sf <- IPHC_DBEM_sf %>% 
-  filter(Period == "Mid_Century")
+  # filter(Period == "Mid_Century") %>%
+  filter(Period == "The_End_Century") %>% 
+  mutate(RegArea = paste(RegArea,Model_Agreement,sep=""))
 
@@
 
-Seq <- seq(-30,30,by=5) #Axis
+Seq <- seq(-50,50,by=5) #Axis
 
@@
   ) +
-  geom_sf(data = subset(IPHC_DBEM_sf, RegArea == "2B"), # DBEM of Canada
+  geom_sf(data = subset(IPHC_DBEM_sf, RegArea == "2B*"), # DBEM of Canada
           aes(fill = Mean_ESM_MCP_Chng)
@@
   scale_fill_gradient2("",
-                       limits=c(-30,30),
+                       limits=c(-50,50),
                        breaks = Seq) +
@@
 # Save plot 
-Name = paste("New_IPHC_Reg_26_85_2050.png")
+# Name = paste("New_IPHC_Reg_26_85_2050.png")
+Name = paste("New_IPHC_Reg_26_85_2100.png")
 
@@
 
-![Fig 3. Percentage change of MCP for species managed by the IPHC for mid century (2046-2055) referent to 2005-2014 under a A) low emission scenario and B) high emission scenario.](./Results/Fig3.png)
+![Fig 3.
+Percentage change of MCP for species managed by the IPHC for mid century (2046-2055) relative to 2005-2014 under a A) low emission scenario and B) high emission scenario.
+Labels marked with "*" represent regions where models do not agree in direction of change.](./Results/Fig3.png)
 
@@
 4).
-Maintaining emissions to lower levels by 2050 would potentially leave unchanged the stock-share ratio of three regulatory areas (3AC, and 4D) and negatively change regulatory area 2A.
-On the other hand, failing to achieve such target will decrease the stock-share ratio almost half of the regulatory areas (2AC, 3AB).
+Maintaining emissions to lower levels **RA through** 2050 would potentially leave unchanged the stock-share ratio of three regulatory areas (3AC, and 4D) and negatively change regulatory area 2A.
+On the other hand, failing to achieve such target will decrease the stock-share ratio **RA in** almost half of the regulatory areas (2AC, 3AB).
 
@@
 
-![Fig 4. Percentage change of stock-share ratio for IPHC under A) low emission scenario and B) high emission scenario for mid century (2046-2055) referent to 2005-2014.](./Results/Fig4.png)
-
-### Projected change to species managed under the GoM agreement
-
-While some regulatory areas of the IPHC will see increments in species' MCP, the results for the Gulf of Maine (NAFO area 5Z) show an overall decrease in MCP by 2050, depending on the climate change scenario.
+![Fig 4. Percentage change of stock-share ratio for IPHC under A) low emission scenario and B) high emission scenario for mid century (2046-2055) relative to 2005-2014.](./Results/Fig4.png)
+
+### Projected change to species managed under the GoM **DV arrangement**
+
+While some regulatory areas of the IPHC will see **RA an incremental increase** in species' MCP, the results for the Gulf of Maine (NAFO area 5Z) show an overall decrease in MCP by 2050, depending on the climate change scenario.
 MCP of cod and haddock will decrease within the whole Gulf with no apparent win for any country in reference to 2014 (Fig.
@@
 # Path for saving plots
-Path <- "~/Documents/UBC/Oceans_Project/Manuscript/Results/GB/Spp/"
+Path <- "./Results/GoM/"
 
@@
              ),
-             # size = 0.1,
-             alpha = 0.3,
-             shape = 4,
+             size = 1,
+             # alpha = 0.3,
+             shape = 16,
              color = "grey20"
@@
 
-![Fig 5. Percentage change of MCP in the Gulf of Main under, A) low emission scenario; and B) high emission for mid century (2041-2060) referent to present (2005-2014)](./Results/Fig5.png)
-
-Despite the expected decrease in MCP for the region, changes in the stock-share ratio of MCP for the Gulf of Maine show different outcomes depending on the species in question.
+![Fig 5.
+Percentage change of MCP in the Gulf of Main under, A) low emission scenario; and B) high emission for mid century (2041-2060) relative to present (2005-2014).
+Points represent regions where models do not agree in direction of change.](./Results/Fig5.png)
+
+Despite the expected decrease in MCP for the region, changes in the stock-share ratio of MCP for the Gulf of Maine show different outcomes **RA dependent** on the species in question.
 Following the high emission path will affect mostly Canada’s share of Y.
@@
 
-![Fig 6. Changes in MCP stock-share ratio for Gulf of Main under (A) low emission scenario; and (B) high emission for mid century (2041-2060) referent to 2005-2014](./Results/Fig6.png)
+![Fig 6. Changes in MCP stock-share ratio for Gulf of Main under (A) low emission scenario; and (B) high emission for mid century (2041-2060) relative to 2005-2014](./Results/Fig6.png)
 
@@
 
-The shifts in the distribution of transboundary species can jeopardize management objectives such as, conservation measures, gear operation, and quota allocations.
+The shifts in the distribution of transboundary **RB stocks** can jeopardize management objectives such as, conservation measures, gear operation, and quota allocations.
 Hypothetically, fish moving out of fishing grounds and into protected areas could result in a pressure increase to open such area to fishing.
@@
 In game theory, a side payment is received by a player as a compensation from the other player, with the idea that keeping cooperation is still better than playing solo [@Bjorndal:2012vd; @Sumaila:2013hv].
-Side payments do not have to be in monetary form and are widely used in transboundary fisheries around the world.
+Side payments do not have to be in monetary form and are widely used in transboundary **RB stocks** around the world.
 For example, Norway and Russia have implemented a quota swap strategy for jointly managed stocks of cod, haddock and capelin in the Barents Sea [^NR].
@@
 While this is a good way to address climate variation within members of a treaty, it might fall short to address the newcomer issue, a situation that can threaten the sustainability of the stock [@Pinsky:2018cb].
-A combination of the methods employed by PNA with the proper modification to incorporate new fishing nations could help mitigate future conflicts in fisheries like the Pacific halibut.
+A combination of the methods employed by PNA with the proper modification to incorporate new fishing nations could help mitigate future conflicts in **RB stocks** like the Pacific halibut.
 Finally, It has been suggested that agreements that make cooperation the preferred strategy for all players are stronger.
@@
 
-In the current paper we follow a modeling approach to explore the potential impacts that climate change will have in the management of transboundary fisheries in North America.
+In the current paper we follow a modeling approach to explore the potential impacts that climate change will have in the management of transboundary **RB stocks** in North America.
 Models are attempts to represent reality (in our case a future reality) based on observational data, previously established theory, and future scenarios, and are thus, subjected to different degrees of uncertainty [@Payne:2016gn].
@@
 
-Shifts in species distribution due to climate change have the potential of creating local extinction of economically important species while enhancing fisheries in areas where they were not present before.
+Shifts in **RB stocks** distribution due to climate change have the potential of creating local extinction of economically important **RB stocks** while enhancing fisheries in areas where they were not present before.
 In this paper, we have explored the potential impacts of climate change in the joint management of 33 transboundary stocks managed by Canada and the US.
-We found that, transboundary species are likely to shift north in the upcoming years changing the proportion of the catch of jointly managed fisheries of Canada and the US.
+We found that, transboundary **RB stocks** are likely to shift north in the upcoming years changing the proportion of the catch of jointly managed fisheries of Canada and the US.
 Lessons from other countries can provide solutions to such challenges.
@@
 While not directly addressed in this study, socio-economic impacts of shifting transboundary stocks could add an extra layer of complexity to the problem.
-Addressing shifts in species distribution sooner rather than latter could avert the so called "fish wars", improve sustainability of jointly managed stocks, and secure the livelihood of thousand of families that depend on stocks that move freely between national jurisdictions.
+Addressing shifts in **RB stocks** distribution sooner rather than latter could avert the so called "fish wars", improve sustainability of jointly managed stocks, and secure the livelihood of thousand of families that depend on stocks that move freely between national jurisdictions.
 
@@
 # LITERATURE CITED
+
+# OLD ANALYSIS
 
@@
 ```
+
+# OLD TEXT
+
+Transboundary fisheries are defined as **RB those fishing** stocks that move freely between (*i*) Countries economic exclusive zones (EEZs) and (*ii*) between EEZs and the high seas (**RB called transboundary stocks**) [@Song:2017iua].
+**RA Game theory is one of the most common approaches used to analyze the management of transboundary stocks, as often, success depends on effective cooperation between parties** [@Munro:2002uf; @Sumaila:2013hv].
+Therefore, in **DV 1982**, the United Nations incentivized actions to cooperate on the management of transboundary **RB stocks** through the Law of the Seas (UNCLOS) [@UnitedNations:1986tl].
+
+While in 2050, the average shift of species will be higher for East Canada and lower for East US under the high emission scenario, the stock-share ratio of some species is expected to increase more than 50% as in the case of Atlantic menhaden (*Brevoortia tyrannus*) in Eastern Canada, and decrease by more than 50% for species such as Cusk (*Brosme brosme*) in the Eastern US under a low emission scenario.
+By the end of the 21^st^ century, losses will intensify with the eastern US potentially losing on average 15.2% or 46% of stock-share, depending on the scenario.

### 2020-03-04 Manuscript_Draft.Rmd
Updated bibliography and responded to reviewers

@@
   pdf_document: default
-bibliography: Oceans_Canada_Biblio.bib
+bibliography: References/Oceans_Canada_Bibliob.bib
 editor_options: 
   chunk_output_type: console
-csl: harvard.csl
+csl: References/harvard.csl
 ---
@@
 We hypothesize that ocean warming will alter the sharing of fish stocks between the two countries, and that such changes will intensify under a high carbon emission scenario impacting the stock-share ratio of different stocks.
-Firstly, we projected changes in potential catch of 33 transboundary stocks of North America in the 21^st^ century based on multiple Earth system models’ simulations and species distribution models, under two climate change scenarios.
-We then look at the specific cases of the International Pacific Halibut Commission that manages pacific halibut (*Hippoglossus stenolepis*) and a resource sharing **DV arrangement** in the Gulf of Maine for cod (*Gadus morhua*), haddock (*Melanogrammus aeglefinus*) and yellowtail flounder (*Limanda ferruginea*).
+Firstly, we projected changes in potential catch of 33 transboundary stocks of North America in the $21^{st}$ century based on multiple Earth system models’ simulations and species distribution models, under two climate change scenarios.
+We then look at the specific cases of the International Pacific Halibut Commission that manages pacific halibut (*Hippoglossus stenolepis*) and a resource sharing **DV arrangement** in the Gulf of Maine for cod (*Gadus morhua*), haddock (*Melanogrammus aeglefinus*) and yellowtail flounder (*Limanda ferruginea*) **RA to discuss the management consequences of shifts in transboundary stocks**.
 Results show that, even under a low emission scenario, most transboundary fish stocks sharing ratios, i.e., the proportion of the total catch of a fish stock taken by a given country, will change by 2050 relative to present in the direction as expected from the effects of ocean warming.
@@
 Such trade-offs in the Atlantic and Pacific regions will be amplified if a high emission scenario is followed, relative to a low carbon emission scenario.
-Our paper highlights the challenges that transboundary fisheries management will face as species shift their current distribution under a changing climate.[^Acknowledgements]
+Our paper highlights the challenges that transboundary fisheries management will face as species shift their current distribution under a changing climate.
 
@@
 
-[^Acknowledgements]: This is a product of the *OceanCanada* Partnership funded by the Social Sciences and Humanities Research Council of Canada.
-
 # INTRODUCTION
@@
 <!-- ##### First paragraph of paper summary -->
-**RA In 1982, the United Nations Law of the Seas (UNCLOS) formalized the concept of economic exclusive zones (EEZs) creating what we know today as transboundary stocks.
-Transboundary stocks move freely between (*i*) Countries EEZs and (*ii*) between EEZs and the high seas (also called straddling stocks) [@Song:2017iua].
-While not a law, UNCLOS incentivized actions to cooperate on the management of transboundary stocks [@UnitedNations:1986tl].
-Today, game theory is one of the most common approaches used to analyze the management of transboundary stocks, as often, success depends on effective cooperation between parties** [@Munro:2002uf; @Sumaila:2013hv].
-An estimated 347 [@Teh:2015gd] to 1500 [@Caddy:1997ue] fish stocks cross national borders, some of them jointly managed by two or more countries.
+**RA In 1982, the United Nations Law of the Seas (UNCLOS) formalized the concept of economic exclusive zones (EEZs) creating what we know today as sahred stocks [@UnitedNations:1986tl].
+Shared stocks can move freely between countries EEZs (known as transboundary stocks) or between EEZs and the high seas (also called straddling stocks) [@Song:2017iua].** Today, an estimated 347 [@Teh:2015gd] to 1500 [@Caddy:1997ue] fish stocks cross national borders, some of them jointly managed by two or more countries.
 These stocks are responsible for almost 50% of these countries total fish catches [@Teh:2015gd].
-Transboundary stocks such as salmon (*Oncorhynchus spp.*), Pacific halibut (*Hippoglossus stenolepis*), and Atlantic cod (*Gadus morhua*) are of utmost importance for Canada and the United States (US).
-Management of these stocks **RA can be convoluted** due to the participation of several fishing “players”, different countries and sometimes jurisdictions within a country, the migration patterns of the stock, and their abundance fluctuation within space and time [@Munro:2002uf].
+**RA While not a law, UNCLOS incentivizes actions to cooperate on the management of shared stocks [@UnitedNations:1986tl].
+Today, game theory is one of the most common approaches used to analyze the management of shared stocks, as often, success depends on effective cooperation between parties [@Munro:2002uf; @Sumaila:2013hv].** Management of these stocks' **RA can be convoluted** due to the participation of several fishing “players”, different countries and sometimes jurisdictions within a country, the migration patterns of the stock, and their abundance fluctuation within space and time [@Munro:2002uf].
+In addition, international treaties might not be prepared to address the effects that climate change will bring to shared fish stocks (**Koubrak and VanderZwaag, this Special Feature**), .
 
@@
 The ocean is getting warmer [@Rheim:2013fv], less oxygenated [@Schmidtko:2017cl], and increasing in acidity [@Ross:2011kd].
-To cope with these changes in ocean biophysic properties, marine species, including transboundary fish stocks, have been shifting their distribution towards the poles and/or deeper waters [@Poloczanska:2016kk].
-As climate change reshapes the ocean's environment worldwide [@Gattuso:2015jz], transboundary fisheries' delicate governance is threatened as new migration patterns may arise [@Miller:2013iv; @Pinsky:2018cb], historic distribution and abundances might shift [@Cheung:2010dt], and species basic natural traits may modify [@Pauly:2017hpa].
-Catches of shared stocks like tropical tunas, have significantly increased in subtropical regions of the Atlantic and western Pacific Oceans [@MonllorHurtado:2017cm].
-Multiple transboundary species in North America have been observed to shift in distribution following changes in optimal conditions such as sockeye salmon (*Oncorhynchus nerka*) [@McDaniels:2010vn], Atlantic cod [@Pershing:2015gq], and flounders [@Pinsky:2012kq].
-Moreover, these shifts are projected to continue towards the end of the 21^st^ century [@Cheung:2018hz] at a rate of tens to hundreds of km and/or tens of meters per decade towards the poles and/or deeper waters, respectively, although there will be regional variations [@Morley:2018fn].
-As a result, some countries or management jurisdictions may see more transboundary **RA fisheries** and their catches shifting into their waters while others will stand to lose [@Miller:2013iv; @Pinsky:2018cb].
+To cope with these changes in ocean biophysic properties, marine species, including shared fish stocks, have been shifting their distribution towards the poles and/or deeper waters [@Poloczanska:2016kk].
+As climate change reshapes the ocean's environment worldwide [@Gattuso:2015jz], shared fisheries' delicate governance is threatened as new migration patterns may arise [@Miller:2013iv; @Pinsky:2018cb], historic distribution and abundances might shift [@Cheung:2010dt], and species basic natural traits may modify [@Pauly:2017hpa].
+Catches of shared stocks like tunas, have significantly increased in some regions such as the subtropical Atlantic and western Pacific Oceans and are projected to continue [@MonllorHurtado:2017cm; @ErauskinExtramiana:2019fw].
+Multiple shared species in North America have been observed to shift in distribution following changes in optimal conditions such as sockeye salmon (*Oncorhynchus nerka*) [@McDaniels:2010vn], Atlantic cod [@Pershing:2015gq], and flounders [@Pinsky:2012kq].
+Moreover, these shifts are projected to continue towards the end of the $21^{st}$ century [@Cheung:2018hz].
+As a result, some countries or management jurisdictions may see more shared **RA fisheries** and their catches shifting into their waters while others will stand to lose [@Miller:2013iv; @Pinsky:2018cb].
 Nevertheless, management rules for shared stocks (e.g.
-quota or spatial delimitation) are often determined based on current and historic knowledge of the stock's distribution and do not consider future shifts in distributions [@FredstonHermann:2018kp].
-In addition, many international treaties do not directly consider climate change in their management scheme, despite evidence of target species shifting their distribution.
+quota or spatial delimitation) are often determined based on current and/or historic knowledge of the stock's distribution and do not consider future shifts in distributions [@FredstonHermann:2018kp].
 
@@
 
-The shifts in distribution of transboundary fish stocks would impact the economics of their fisheries [@Lam:2016dy; @Pinsky:2012kq; @Sumaila:2011bq, @Sumaila:2019gh], and create international disputes in the sharing of fish stocks between nation's EEZs [@Munro:2002uf; @Spijkers:2017ij].
-As climate change alters the sharing of fish stocks between countries to an extent that is beyond historical changes, existing policies and governance structures may not be able to cope with these changes.
-Consequently, countries may not be satisfied with the sharing or allocation of access to resources, leading to international disputes [@Pinsky:2018cb].
-Disputes over Pacific salmon between Canada and the US arose in the 1990s because of climate-related changes in stock abundance and migratory behavior [@Miller:2013iv; @Munro:2002uf; @Song:2017va].
-Currently, Europe is involved in an unsolved dispute over *Scomber scombrus* known as the "mackerel wars".
-The conflict erupted in 2007 when the stock shifted their distribution from the Norwegian Sea towards northern and western regions of the Nordic Seas, consequently spreading into Iceland's national waters [@Spijkers:2017ij].
-
-<!-- ##### Bring it home, treaties between CA/US -->
-
-Transboundary **RB stocks** between Canada and the US offer a unique lens to understand the extent to which climate-induced distributional shifts will challenge the future sustainability of these fisheries.
-Canada and the US have a long history of fisheries cooperation [@Song:2017va].
-They participate in diverse, jointly managed, commercial transboundary stocks through various fisheries management organizations [@Merten:2015tu].
-Cooperation schemes vary by fisheries stocks, regulatory areas, legal terms of agreement, and management measures, among others.
-In the Atlantic coast, Canada and the US are part of the Northwest Atlantic Fisheries Organization (NAFO) that oversees the management of 19 stocks of 11 transboundary species (although around 41 taxa are fished within Canadian and US waters) from southern Gulf of Maine to Greenland [^NAFO].
-In the Pacific coast, Pacific halibut (*Hippoglossus stenolepis*) is managed under the International Pacific Halibut Commission (IPHC) [@IPHCSecreatriat:2017uz].
-All five salmon species (chinook, *Oncorhynchus tshawytscha*; chum, *O.
-keta*; coho, *O.
-kisutch*; pink, *O.
-gorbuscha*; and sockeye *O.
-nerka*), are managed by the Pacific Salmon Commission [@PSC:2017tb].
-Finally, under the Pacific Whiting Treaty, Canada and the United states jointly manage the coastal stock of this Pacific hake species (*Merluccius productus*) [@Merten:2015tu].
+The shifts in distribution of shared fish stocks will impact the economics of their fisheries [@Pinsky:2012kq; @Sumaila:2019gh]**Sumaila et al., This Volume**), and create international disputes between countries [@Munro:2002uf; @Spijkers:2017ij;@Pinsky:2018cb].
+Canada and the US share important transboundary stocks of salmon (*Oncorhynchus spp.*), Pacific halibut (*Hippoglossus stenolepis*), and Atlantic cod (*Gadus morhua*) offering a unique lens to understand the extent to which climate-induced distributional shifts will challenge the future sustainability of transboundary fisheries.
+These countries have a long history of fisheries cooperation participating in diverse, jointly managed, commercial transboundary stocks through various fisheries management organizations [@Merten:2015tu].
+Furthermore, climate-related fluctuations in stocks' distribution have historically created disputes between Canada and the US, increasing international conflict and threatening the health of diverse transboundary stocks [@Munro:2002uf; @CIA:2017uta].
 
@@
 
-It is expected that climate induced shifts in stock distribution **RA will** affect the rules in place that **RA keep** these treaties alive.
-Therefore, the main objective of this paper is to assess the level of exposure of international fisheries management treaties between Canada and the US to climate change impacts through shifts in stock distributions.
+It is expected that climate induced shifts in stocks' distribution **RA will** affect the rules in place that **RA keep** international treaties alive.
+Therefore, the main objective of this article is to assess the level of exposure that bi-lateral transboundary fisheries treaties between Canada and the US have to climate change through shifts in stock distributions.
 Specifically, we rely on a species distribution model and scenario planning to project the changes in the distribution of 33 fish stocks jointly managed by Canada and the US.
-Moreover, we use two specific treaties as case studies (IPHC and an **DV arrangement** for the Gulf of Maine) to explore the potential impacts that climate change will have on selected transboundary **RB stocks** management.
+Moreover, we use two specific case studies (the International Pacific Halibut Comission -IPHC- and a **DV fisheries arrangement** for the Gulf of Maine -GoMA-) to explore the potential impacts that climate change will have on selected transboundary **RB stocks** management.
 Finally, we explore similar situations around the world and identify opportunities to improve the adaptability of transboundary **RB stocks** management to climate change in North America.
 Despite an overall expectation of species following a poleward shift, **RA important geographic constraints (e.g.
-Gulf of Alaska representing a latitudinal block) [@Kleisner:2016je], geo-political features** (e.g.
-the localization of Alaska in reference to Canada and the contiguous states), and management rules (e.g.
+Gulf of Alaska representing a latitudinal block) [@Kleisner:2016je], geo-political features (e.g.
+the localization of Alaska in reference to Canada and the contiguous states)**, and management rules (e.g.
 quota allocations, spatial management rules) may play an important role in the redistribution of benefits.
-Understanding these stocks shifts will shed a light on future conditions and inform decision makers on the paths to follow under a changing climate.
+Understanding these stocks shifts will shed a light on future conditions and inform decision-makers on the paths to follow under a changing climate.
 
@@
 
-The current study focuses on transboundary **RB stocks** jointly managed by Canada and the US for both the Atlantic and the Pacific coasts.
+The current study focuses on 33 transboundary **RB stocks** jointly managed by Canada and the US for both the Atlantic and the Pacific coasts.
 The analysis was carried out within the 200 nautical miles of both nation's EEZ from the Gulf of Mexico to The Labrador Sea in the Atlantic, and from California to Chukchi Sea, in the Pacific coast.
 The species analyzed (**Table A2.1**) were selected based on five treaties in both the Atlantic and Pacific coast of North America (Table 1).
-All species under the IPHC, PSC, WT, and the Gulf of Maine **DV arrangement** were analyzed as these treaties are management agreements between Canada and the US.
-However, in the case of NAFO, their management covers over 41 taxa and its governance extends to international waters and the EEZ of Greenland.
-Therefore, a subset of 26 species reported was made based on those fished in NAFO regions that fall within the EEZs of Canada and the US (NAFO subareas 2's, 3's with the exception of 3M and 3N and limited to the EEZ, 4's,5's and 6 A,B, and C.) [@NAFO].
-Data related to fisheries was gathered from the *Sea Around Us* from 1951 to 2014 [@Zeller2016].
-
-We selected two case studies, the IPHC agreement and the Gulf of Maine arrangement (hereafter refered as GoM arrangement), in order to better discuss the implications that climate chage could have in the management of transboundary stocks.
-For the IPHC, we used the most updated spatial regulatory data provided by the Commission [@IPHCSecreatriat:2017uz; @IPHC:2019wt].
-For this specific case, we considered Alaska as a separate entity, the US contiguous states as a second one (Washington, Oregon and California), and lastly British Columbia (Canada).
-For the GoM **DV arrangement** we used NAFO's divisions 5Y, 5Ze, and 4X within latitudes 46.2°N and 41.5°S, and longitudes -72°W and -64°E (Fig.
-1).
-
-```{r Study_Area_Map, eval = F, echo = F, warning=F, message=F}
-
-Countries <- c("Canada","United States")
-
-### North America Initial Map ####
-
-path_world <- "~/Documents/Github/Oceana_LA/international/information/raw_databases/Spatial/TM_WORLD_BORDERS-0.3"
-file_name <- "TM_WORLD_BORDERS"
-
-World_Land_sf <- st_read(dsn = path_world, 
-layer = file_path_sans_ext(file_name)
-) %>% 
-st_transform(crs = 3832)
-
-# names(World_Land_sf)
-
-North_America_Land <- World_Land_sf %>% 
-filter(NAME %in% Countries) %>% 
-st_transform(crs = 3832)
-
-# head(North_America)
-
-# ggplot(North_America_Land) +
-#   geom_sf() +
-#   coord_sf(ylim = c(3051701,11528813)
-#   )
-
-### North America EEZs Map ####
-
-path_eez <- ("/Users/jpalacios/Documents/R CODE/Spatial_Analysis/Data/World_EEZ_v10_2018")
-#The File
-fnam_eez <- "eez_v10.shp"
-
-eez_world_sf <- st_read(dsn = path_eez, 
-                        layer = file_path_sans_ext(fnam_eez)
-) %>% 
-  st_transform(crs = 3832)
-
-Nort_America_EEZ <- eez_world_sf %>% 
-filter(Territory1 %in% Countries)
-
-# Testing
-ggplot(Nort_America_EEZ) +
-geom_sf()
-
-# Testing together
-
-ggplot(North_America_Land) +
-  geom_sf() +
-  geom_sf(data = Nort_America_EEZ, colour = "black") +
-  coord_sf(ylim = c(3051701,11528813)
-  )
-
-#### IPHC Regulatory Areas ####
-
-path_IPHC <- ("/Users/jpalacios/Documents/UBC/Oceans_Project/Distribution/Data/IPHC/IPHC_RegulatoryAreas/")
-
-# The Canada file
-fnam_IPHC_C <- "IPHC_RegulatoryAreas_CAN"
-
-IPHC_Reg_C <- st_read(dsn = path_IPHC, 
-                      layer = file_path_sans_ext(fnam_IPHC_C)
-) %>% 
-  select(
-    ID,
-    Country = COUNTRY,
-    State = PROV_EN,
-    RegArea
-  ) %>% 
-  mutate(Comments = "NA") %>% 
-  st_transform(crs = 3832)
-
-# 4326 use this to merge with DBEM data
-# 3832 use this to center the map and plot
-
-# ggplot(IPHC_Reg_C) +
-# geom_sf()
-
-# The US File
-fnam_IPHC_US <- "IPHC_RegulatoryAreas_US"
-
-IPHC_Reg_US <- st_read(dsn = path_IPHC,
-                       layer = file_path_sans_ext(fnam_IPHC_US)
-) %>%
-  st_transform(crs = 3832)
-
-# head(IPHC_Reg_US)
-ggplot(IPHC_Reg_US) +
-  geom_sf()
-
-### Combine both shapefiles
-
-IPHC_Reg <- rbind(IPHC_Reg_US,IPHC_Reg_C)
-
-ggplot(IPHC_Reg) +
-  geom_sf()
-
-##### NAFO Regulatory Area ####
-
-path_NAFO <- ("/Users/jpalacios/Documents/UBC/Oceans_Project/Distribution/Data/Spatial/NAFO")
-#The File
-fnam_NAFO <- "Divisions"
-
-NAFO_Area <- st_read(dsn = path_NAFO,
-                     layer =file_path_sans_ext(fnam_NAFO))%>% 
-  st_transform(crs = 3832)
-
-Zones <- c(
-  "5Ze",
-  # "5Zw",
-  "5Y",
-  "4X"
-)
-
-NAFO_5z <- NAFO_Area %>% 
-filter(ZONE %in% Zones)
-
-# head(NAFO_5z)
-
-ggplot() +
-geom_sf(data = North_America_Land,
-        fill = "lightgrey",
-        colour = "black") +
-  ggtheme_map()
-
-#### The final Map ####
-
-# Homonize collors 
-brewer.pal(name="Set2",5)
-
-# Canada "#grey80"
-# US "#grey40", 
-# NAFO "#66CC99"
-# IPHC #f01282
-
-#North America point of view
-
-North_A <- ggplot() +
-  geom_sf(data = North_America_Land, 
-          aes(fill = NAME),
-          colour = "black"
-  ) +
-  geom_sf(data = IPHC_Reg, 
-          aes(fill = "IPHC") ,
-          colour = "black"
-  ) +
-  geom_sf(data = NAFO_5z, 
-          aes(fill = "NAFO"),
-          colour = "black"
-  ) +
-  ggtheme_map() +
-  scale_fill_manual("Region",
-                    breaks = c("Canada","IPHC","NAFO", "United States"), 
-                    values=c("grey80","#CC6666","#66CC99","grey40")
-                    ) +
-  theme(legend.position = "right")
-
-Path_Save <- "/Users/jpalacios/Documents/UBC/Oceans_Project/Manuscript/Results/Others/"
-
-ggsave("Fig1_NA.png",
-       plot = North_A,
-       width = 6,
-       height = 5,
-       units = "in",
-       path = Path_Save)
-
-#NAFO #
-
-NAFO <- ggplot() +
-  geom_sf(data = NAFO_5z, #NAFO regions
-          aes(fill = "NAFO"),
-          colour = "black"
-  )+
-  geom_sf_label(data = NAFO_5z, # RegAreas labels
-                aes(
-                  label = ZONE#,
-                  # fill = "NAFO"
-                ),
-                alpha = 0.5
-  ) +
-  geom_sf(data = North_America_Land, # North America Land
-          aes(fill=NAME),
-          colour = "black"
-  ) +
-  coord_sf(ylim = c(5951701,4728813),
-           xlim = c(15373019,16573019)
-  ) +
-  # scale_fill_brewer("Region",palette = "Set2") +
-  theme(
-    panel.background = element_blank(),
-    panel.border     = element_blank(),
-    panel.grid.minor = element_blank(),
-    panel.grid.major = element_line(color = "transparent"),
-    legend.position = "bottom",
-    axis.title = element_blank()
-  ) +
-  scale_fill_manual("Region",breaks = c("Canada", "NAFO", "United States"), 
-                    # values = c("#E78AC3","#A6D854","8DA0CB")
-                    values=c("grey80", "#66CC99", "grey40")
-                    ); NAFO
-
-# Save plot for manuscrip
-ggsave("Fig1_NAFO.png",
-       plot = NAFO,
-       width = 6,
-       height = 5,
-       units = "in",
-       path = Path_Save)
-
-# IPHC
-
-IPHC_Reg$RegArea <- gsub("Closed Area","CA",IPHC_Reg$RegArea)
-
-IPHC <- ggplot() +
-  geom_sf(data = IPHC_Reg,
-          aes(fill = "IPHC"),
-          colour = "black"
-  ) + 
-  geom_sf(data = North_America_Land, # North America Land
-          aes(fill=NAME),
-          colour = "black"
-  ) +
-  geom_sf_label(data = IPHC_Reg, # RegAreas labels
-                aes(
-                  label = RegArea#,
-                  # fill = Percentage
-                ),
-                alpha = 0.5
-  ) +
-
-  coord_sf(xlim = c(1963800, 10041910), # Subsets north america
-           ylim = c(3651701,9728813)
-  ) +
-  theme(
-    panel.background = element_blank(),
-    panel.border     = element_blank(),
-    panel.grid.minor = element_blank(),
-    panel.grid.major = element_line(color = "transparent"),
-    legend.position = "bottom",
-    axis.title = element_blank()
-  ) +
-  scale_fill_manual("Region",breaks = c("Canada", "IPHC", "United States"), 
-                    values=c("grey80", "#CC6666", "grey40")
-                    )
-
-# Save plot for manuscrip
-ggsave("Fig1_IPHC.png",
-       plot = IPHC,
-       width = 6,
-       height = 5,
-       units = "in",
-       path = Path_Save)
-
-```
-
-![Fig 1. Map of North America with the regulatory areas of the IPHC and the NAFO sub-region related to the Gulf of Main **DV arrangement**](./Figures/Fig1.png)
-
-```{r Spatial_data, eval = T, echo = F, warning=F, message=F, results = 'hide'}
-
-# List of DBEM INDEX within the EEZ
-#Data provided by Vicki Lam
-EEZIDs_List <- read_excel(paste(Data_Path,"/Spatial/Updated_EEZList_17June2016.xlsx",sep=""))
-EEZ_CellID <- read_excel(paste(Data_Path,"/Spatial/EEZ_CellID.xlsx",sep=""))
-colnames(EEZ_CellID) <- c("EEZID","INDEX")
-
-# DBEM Coordinate system
-Coor <- fread(paste(Data_Path,"/Spatial/Lon_Lat_DBEM.txt",sep=""),header = FALSE)
-colnames(Coor) <- c("INDEX","Longitude","Latitude")
-
-### Select EEZs
-EEZs <- c(
-  "Canada (Pacific)",
-  "Canada (Arctic)",
-  "USA (West Coast)",
-  "USA (Alaska, Arctic)",
-  "USA (Alaska, Subarctic)",
-  "Canada (Arctic)",
-  "Canada (East Coast)",
-  "USA (East Coast)"
-)
-
-### North America Initial Map ####
-
-path_world <- paste(Data_Path,"/Spatial/TM_WORLD_BORDERS",sep="")
-file_name <- "TM_WORLD_BORDERS"
-
-World_Land_sf <- st_read(dsn = path_world, 
-                         layer = file_path_sans_ext(file_name)
-) %>% 
-  st_transform(crs = 4326)
-
-# names(World_Land_sf)
-
-North_America_Land <- World_Land_sf %>% 
-  filter(NAME %in% c("Canada","United States")) %>% 
-  st_transform(crs = 3832) # 4326 use this to merge with DBEM data
-# 3832 use this to center the map and plot
-
-#### _____________________TEST _____________________ #
-# head(North_America_Land)
-# ggplot(North_America_Land) +
-#   geom_sf() +
-#   coord_sf(xlim = c(-120, -179),
-#            ylim = c(30,70)
-#   )
-##__________________________________________ #
-
-### North America EEZs Map ####
-
-path_eez <- paste(Data_Path,"/Spatial/World_EEZ_v10_2018",sep="")
-#The File
-fnam_eez <- "eez_v10.shp"
-
-eez_world_sf <- st_read(dsn = path_eez, 
-                        layer = file_path_sans_ext(fnam_eez)
-) %>% 
-  st_transform(crs = 4326)# 4326 use this to merge with DBEM data
-# 3832 use this to center the map and plot
-
-#### _____________________TEST _____________________ #
-# head(eez_world_sf)
-### Test this map
-# ggplot(ezz_North_America) +
-#   geom_sf()
-##__________________________________________##
-
-#### IPHC Regulatory areas ####
-
-## Correct DBEM for Alaska ####
-IHPC_EEZs <- c(
-  "Canada (Pacific)",
-  # "Canada (Arctic)"
-  "USA (West Coast)",
-  "USA (Alaska, Arctic)",
-  "USA (Alaska, Subarctic)"#,
-  # "Russia (Far East)"
-)
-
-IPHC_EEZsID <- EEZIDs_List %>% 
-  filter(Name %in%IHPC_EEZs) %>% 
-  left_join(EEZ_CellID,
-            by = "EEZID") %>% 
-  left_join(Coor,
-            by = "INDEX")
-
-# "Move" the map so results are not in the other side of the world and it matches the projection I want
-IPHC_Coor_Corrected <- IPHC_EEZsID %>% 
-  filter(Longitude > 0) %>% 
-  mutate(Longitude = Longitude-360)
-
-IPHC_Coor_Corrected <- IPHC_EEZsID %>% 
-  filter(Longitude < 0) %>% 
-  bind_rows(IPHC_Coor_Corrected) %>% 
-  filter(Latitude > 25)
-
-# Create new column to merge with shapefiles
-
-IPHC_Coor_Corrected_Clean <- IPHC_Coor_Corrected %>% 
-  mutate(
-    State = ifelse(Name == "Canada (Pacific)", "British Columbia",
-                   ifelse(Name == "USA (West Coast)","WAORCA","Alaska"))
-  ) %>% 
-  select(
-    # State,
-    INDEX,
-    longitude = Longitude,
-    latitude = Latitude)
-
-# Now we load IPHC shapefiles ####
-path_IPHC <- paste(Data_Path,"/Spatial/IPHC_RegulatoryAreas/",sep="")
-
-# The Canada file
-fnam_IPHC_C <- "IPHC_RegulatoryAreas_CAN"
-
-IPHC_Reg_C <- st_read(dsn = path_IPHC, 
-                      layer = file_path_sans_ext(fnam_IPHC_C)
-) %>% 
-  select(
-    ID,
-    Country = COUNTRY,
-    State = PROV_EN,
-    RegArea
-  ) %>% 
-  mutate(Comments = "NA") %>% 
-  st_transform(crs = 4326)
-
-# 4326 use this to merge with DBEM data
-# 3832 use this to center the map and plot
-
-#### _____________________TEST _____________________##
-# head(IPHC_Reg_C)
-# ggplot(IPHC_Reg_C) +
-# geom_sf()
-##_________________________________________________##
-# The US File
-fnam_IPHC_US <- "IPHC_RegulatoryAreas_US"
-
-IPHC_Reg_US <- st_read(dsn = path_IPHC, 
-                       layer = file_path_sans_ext(fnam_IPHC_US)
-) %>% 
-  st_transform(crs = 4326)
-
-#### _____________________TEST _____________________ #
-# head(IPHC_Reg_US)
-# ggplot(IPHC_Reg_US) +
-#   geom_sf()
-##_________________________________________________##
-
-### Combine both shapefiles
-
-IPHC_Reg <- rbind(IPHC_Reg_US,IPHC_Reg_C)
-
-#### _____________________TEST _____________________ #
-# head(IPHC_Reg,12)
-# tail(IPHC_Reg)
-# unique(IPHC_Reg$State)
-
-# It's going to take a while... 
-# ggplot(IPHC_Reg) +
-#   geom_sf()
-##_________________________________________________##
-
-# Now join the Shapefile with the DBEM lat/long dataset
-
-# Convert DBEM to sf
-IPHC_Coor_sf = st_as_sf(IPHC_Coor_Corrected_Clean,
-                        coords = c("longitude", "latitude")) %>% 
-  st_set_crs(4326) %>% # to match shapefiles
-  st_transform(4326) # to match shapefiles
-
-# head(IPHC_Coor_sf)
-
-# Merge DBEM sf to polygons
-IPHC_Reg_DBEM <- st_join(IPHC_Reg,
-                         IPHC_Coor_sf, join = st_contains) %>% 
-  filter(!is.na(INDEX)) %>%
-  arrange(INDEX) 
-# %>% 
-#   st_transform(3832) # Go back to original projection otherwise doesnt like to plot
-
-IPHC_Reg_DBEM_df <- as.data.frame(IPHC_Reg_DBEM) %>% 
-  select(INDEX,RegArea)
-
-#### _____________________TEST _____________________ #
-# head(IPHC_Reg_DBEM_df)
-# IPHC_Reg_DBEM_df %>% 
-#   arrange(INDEX) %>% 
-# head()
-##_________________________________________________##
-
-### STOP 
-## Go to the results and now estimate the %change by region using IPHC_Reg_DBEM_df then, convert it to sf and merge it with IPHC_Reg
-
-# Gulf of Maine ####
-#### NAFO data ####
-
-path_NAFO <- paste(Data_Path,"/Spatial/NAFO",sep="")
-#The File
-fnam_NAFO <- "Divisions"
-
-NAFO_Area <- st_read(dsn = path_NAFO,
-layer =file_path_sans_ext(fnam_NAFO))
-
-Zones <- c(
-  "5Ze",
-  # "5Zw",
-  "5Y",
-  "4X"
-)
-
-NAFO_5z <- NAFO_Area %>% 
-filter(ZONE %in% Zones)
-
-#### _____________________TEST _____________________ #
-# head(NAFO_5z)
-
-# ggplot(NAFO_5z) +
-# geom_sf()
-# geom_sf(aes (fill = ZONE))
-##_________________________________________________##
-
-### Atlantic EEZ polygon (I don't think we need this for now) ####
-
-Atlantic_EEZs <- c(
-  "Canada (Arctic)",
-  "Canada (East Coast)",
-  "USA (East Coast)"
-)
-
-Atlantic_EEZsID <- EEZIDs_List %>%
-  filter(Name %in% Atlantic_EEZs) %>%
-  left_join(EEZ_CellID,
-            by = "EEZID") %>%
-  left_join(Coor,
-            by = "INDEX")
-
-### Atlantic DBEM Data ####
-
-GB_Coor <- Coor %>% 
-  filter(INDEX %in% Atlantic_EEZsID$INDEX) %>% 
-  mutate(one = 1)
-
-# Atlantic Land polygon ####
-
-Countries <- c(
-  "Canada",
-  "United States"
-)
-
-### EEZ GM ####
-eez_GM <- eez_world_sf %>% 
-  filter(Territory1 %in% Countries)
-
-#### _____________________TEST _____________________ #
-# ggplot() +
-#   geom_sf(data = eez_GM) +
-#   coord_sf(xlim = c(-71.0592, -63.33333),
-#            ylim = c(40.5,45.9759)
-#            )
-##_________________________________________________##
-
-GM_Land <- World_Land_sf %>% 
-  filter(NAME %in% Countries)
-
-```
-
-##### The International Pacific Halibut Comission (IPHC)
-
-The IPHC is a convention established in 1923 by Canada and the United States that oversees the management of Pacific halibut (*Hippoglossus stenolepis*), a flatfish that can grow as much as 500 pounds (2.4 m) which inhabits the continental shelf of the northern Pacific Ocean [@IPHC:2014tz].
-The IPHC Convention Area covers the Pacific EEZ of Canada and the US from California to the Berring Sea [@IPHC:2019wt] and is divided in 12 regions (Fig 1).
-Most of the Pacific halibut population is estimated to be in region 3 (51.2%), followed by regions 2 and 4ACDE (23.1% and 20.4%, respectively), and lastly region 4B with only 5.2% of the stock distribution [@IPHC:2018vz].
-In terms of management, the IPHC implements a total allowable catch (TAC) in addition to a series of regulations to control fishing effort.
-Every year, the IPHC carries an fishery-independent set-line survey from Oregon to the Berring sea to support the estimation of next fishing season's fishing limits [@IPHC:2018vz].
-Thus, the TAC is allocated by region according to the population distribution with sector 3A historically having almost 1/3 of the TAC and almost half of the commercial catch.
-The TAC is divided between recreational, subsistence and commercial fishery, with a portion set aside for bycatch of other fisheries [@IPHC:2019wt].
-The commercial fishing season starts in March ending around November whith restrictions allowing only set line gear with J-type hooks targeting individuals over 81.3 cm (32 inches) with head on [@IPHC:2019wt].
-
-##### The Gulf of Maine Agreement
-
-Since 1998 Canada and the US celebrate a "Resource Sharing Understanding" to manage three groundfish stocks within the Gulf of Maine (Georges Bank) [@TRAC:2016wu].
-Under the GoM **DV arrangement**", both countries set catch-limits for George Bank's Atlantic cod (*Gadus morhua*), and Eastern George Bank's haddock (*Melanogrammus aeglefinus*) and, yellowtail flounder (*Limanda ferruginea*) [@Pudden:2007bo; @CIA:2017uta]; **Koubrak and VanderZwaag, this Special Feature**.
-In terms of management, the quota allocation formula includes a combination of future stock's distribution patterns produced by yearly surveys and historical utilization patterns favoring Canda in terms of Cod (82%) and the US for Haddock (66%) and Y.
-flounder (66%), althou these patterns can change on yearly bases [@Pudden:2007bo; @TRAC:2016wu].
-In addition, Canada and the US conduct jointly surveys and enforce activities of the maritime border.
-The task of the committee is just to inform Canada and the US who ultimatley take single management decissions.
-In terms of manangement, the US has a multi species harvest control with area and season cloasures, mesh sizes, effort control.
-US mobile gear vessels that use bottom otter trawl gear [@Soboil:2006gw].
-In contrast, Canada has a more strict regulatory system implaced based on a quota system in addition to limited-entery licensig, fleet allocations, mesh sizes, fish size regulation, among other input controls [@Soboil:2006gw].
-Canada inshore vessels fish Cod with longline and gillnet while haddock is mainly caught with bottom otter trawl gear [@Soboil:2006gw].
+All species under the IPHC, Pacific Salmon Comission, the Pacific Whiting Treaty, and the GoMA arrangement were analyzed as these are bi-lateral agreements.
+However, in the case of NAFO, a subset of 26 species reported was made based on those fished in regions that fall within the EEZs of Canada and the United States (NAFO subareas 2s, 3s with the exception of 3M and 3N and limited to the EEZ, 4s, 5s and 6 A,B, and C) (NAFO n.d.).
+Data related to fisheries was gathered from the Sea Around Us from 1951 to 2014  [@Zeller2016].
 
@@
 # Foot note
-fn <- "*These species are also part of NAFO"
+fn <- "*These species are also part of NAFO. **This is an arrangement and not an official agreement between parties."
 
 data.table::data.table(Treaty =
-                         c("International Pacific Halibut Coomission (IPHC)",
-                           "Pacific Salmon Coomission (PSC)",
+                         c("International Pacific Halibut Commission (IPHC)",
+                           "Pacific Salmon Commission (PSC)",
                            "Pacific Whiting Treaty (PWT)",
                            "Northwest Atlantic Fisheries Organization (NAFO)",
-                           "Gulf of Main's Arrangement (GoM Arrangement)"),
+                           "Gulf of Main's Arrangement (GoM Arrangement**)"),
                        Species =
@@
 
+We used the IPHC and the Gulf of Maine arrangement (hereafter refered as GoMA) as case studies to discuss the implications that climate chage could have in the management of transboundary stocks.
+For the IPHC, we used the most updated spatial regulatory data along its 12 regulatory areas [@IPHCSecreatriat:2017uz; @IPHC:2019wt].
+For this specific case, we considered Alaska as a separate entity, the US contiguous states as a second one (Washington, Oregon and California), and lastly British Columbia (Canada).
+For the GoMA we used NAFO's divisions 5Y, 5Ze, and 4X within latitudes 46.2°N and 41.5°S, and longitudes -72°W and -64°E (Fig.
+1).
+
+```{r Study_Area_Map, eval = F, echo = F, warning=F, message=F}
+
+Countries <- c("Canada","United States")
+
+### North America Initial Map ####
+
+path_world <- "~/Documents/Github/Oceana_LA/international/information/raw_databases/Spatial/TM_WORLD_BORDERS-0.3"
+file_name <- "TM_WORLD_BORDERS"
+
+World_Land_sf <- st_read(dsn = path_world, 
+layer = file_path_sans_ext(file_name)
+) %>% 
+st_transform(crs = 3832)
+
+# names(World_Land_sf)
+
+North_America_Land <- World_Land_sf %>% 
+filter(NAME %in% Countries) %>% 
+st_transform(crs = 3832)
+
+# head(North_America)
+
+# ggplot(North_America_Land) +
+#   geom_sf() +
+#   coord_sf(ylim = c(3051701,11528813)
+#   )
+
+### North America EEZs Map ####
+
+path_eez <- ("/Users/jpalacios/Documents/R CODE/Spatial_Analysis/Data/World_EEZ_v10_2018")
+#The File
+fnam_eez <- "eez_v10.shp"
+
+eez_world_sf <- st_read(dsn = path_eez, 
+                        layer = file_path_sans_ext(fnam_eez)
+) %>% 
+  st_transform(crs = 3832)
+
+Nort_America_EEZ <- eez_world_sf %>% 
+filter(Territory1 %in% Countries)
+
+# Testing
+ggplot(Nort_America_EEZ) +
+geom_sf()
+
+# Testing together
+
+ggplot(North_America_Land) +
+  geom_sf() +
+  geom_sf(data = Nort_America_EEZ, colour = "black") +
+  coord_sf(ylim = c(3051701,11528813)
+  )
+
+#### IPHC Regulatory Areas ####
+
+path_IPHC <- ("/Users/jpalacios/Documents/UBC/Oceans_Project/Distribution/Data/IPHC/IPHC_RegulatoryAreas/")
+
+# The Canada file
+fnam_IPHC_C <- "IPHC_RegulatoryAreas_CAN"
+
+IPHC_Reg_C <- st_read(dsn = path_IPHC, 
+                      layer = file_path_sans_ext(fnam_IPHC_C)
+) %>% 
+  select(
+    ID,
+    Country = COUNTRY,
+    State = PROV_EN,
+    RegArea
+  ) %>% 
+  mutate(Comments = "NA") %>% 
+  st_transform(crs = 3832)
+
+# 4326 use this to merge with DBEM data
+# 3832 use this to center the map and plot
+
+# ggplot(IPHC_Reg_C) +
+# geom_sf()
+
+# The US File
+fnam_IPHC_US <- "IPHC_RegulatoryAreas_US"
+
+IPHC_Reg_US <- st_read(dsn = path_IPHC,
+                       layer = file_path_sans_ext(fnam_IPHC_US)
+) %>%
+  st_transform(crs = 3832)
+
+# head(IPHC_Reg_US)
+ggplot(IPHC_Reg_US) +
+  geom_sf()
+
+### Combine both shapefiles
+
+IPHC_Reg <- rbind(IPHC_Reg_US,IPHC_Reg_C)
+
+ggplot(IPHC_Reg) +
+  geom_sf()
+
+##### NAFO Regulatory Area ####
+
+path_NAFO <- ("/Users/jpalacios/Documents/UBC/Oceans_Project/Distribution/Data/Spatial/NAFO")
+#The File
+fnam_NAFO <- "Divisions"
+
+NAFO_Area <- st_read(dsn = path_NAFO,
+                     layer =file_path_sans_ext(fnam_NAFO))%>% 
+  st_transform(crs = 3832)
+
+Zones <- c(
+  "5Ze",
+  # "5Zw",
+  "5Y",
+  "4X"
+)
+
+NAFO_5z <- NAFO_Area %>% 
+filter(ZONE %in% Zones)
+
+# head(NAFO_5z)
+
+ggplot() +
+geom_sf(data = North_America_Land,
+        fill = "lightgrey",
+        colour = "black") +
+  ggtheme_map()
+
+#### The final Map ####
+
+# Homonize collors 
+brewer.pal(name="Set2",5)
+
+# Canada "#grey80"
+# US "#grey40", 
+# NAFO "#66CC99"
+# IPHC #f01282
+
+#North America point of view
+
+North_A <- ggplot() +
+  geom_sf(data = North_America_Land, 
+          aes(fill = NAME),
+          colour = "black"
+  ) +
+  geom_sf(data = IPHC_Reg, 
+          aes(fill = "IPHC") ,
+          colour = "black"
+  ) +
+  geom_sf(data = NAFO_5z, 
+          aes(fill = "NAFO"),
+          colour = "black"
+  ) +
+  ggtheme_map() +
+  scale_fill_manual("Region",
+                    breaks = c("Canada","IPHC","NAFO", "United States"), 
+                    values=c("grey80","#CC6666","#66CC99","grey40")
+                    ) +
+  theme(legend.position = "right")
+
+Path_Save <- "/Users/jpalacios/Documents/UBC/Oceans_Project/Manuscript/Results/Others/"
+
+ggsave("Fig1_NA.png",
+       plot = North_A,
+       width = 6,
+       height = 5,
+       units = "in",
+       path = Path_Save)
+
+#NAFO #
+
+NAFO <- ggplot() +
+  geom_sf(data = NAFO_5z, #NAFO regions
+          aes(fill = "NAFO"),
+          colour = "black"
+  )+
+  geom_sf_label(data = NAFO_5z, # RegAreas labels
+                aes(
+                  label = ZONE#,
+                  # fill = "NAFO"
+                ),
+                alpha = 0.5
+  ) +
+  geom_sf(data = North_America_Land, # North America Land
+          aes(fill=NAME),
+          colour = "black"
+  ) +
+  coord_sf(ylim = c(5951701,4728813),
+           xlim = c(15373019,16573019)
+  ) +
+  # scale_fill_brewer("Region",palette = "Set2") +
+  theme(
+    panel.background = element_blank(),
+    panel.border     = element_blank(),
+    panel.grid.minor = element_blank(),
+    panel.grid.major = element_line(color = "transparent"),
+    legend.position = "bottom",
+    axis.title = element_blank()
+  ) +
+  scale_fill_manual("Region",breaks = c("Canada", "NAFO", "United States"), 
+                    # values = c("#E78AC3","#A6D854","8DA0CB")
+                    values=c("grey80", "#66CC99", "grey40")
+                    ); NAFO
+
+# Save plot for manuscrip
+ggsave("Fig1_NAFO.png",
+       plot = NAFO,
+       width = 6,
+       height = 5,
+       units = "in",
+       path = Path_Save)
+
+# IPHC
+
+IPHC_Reg$RegArea <- gsub("Closed Area","CA",IPHC_Reg$RegArea)
+
+IPHC <- ggplot() +
+  geom_sf(data = IPHC_Reg,
+          aes(fill = "IPHC"),
+          colour = "black"
+  ) + 
+  geom_sf(data = North_America_Land, # North America Land
+          aes(fill=NAME),
+          colour = "black"
+  ) +
+  geom_sf_label(data = IPHC_Reg, # RegAreas labels
+                aes(
+                  label = RegArea#,
+                  # fill = Percentage
+                ),
+                alpha = 0.5
+  ) +
+
+  coord_sf(xlim = c(1963800, 10041910), # Subsets north america
+           ylim = c(3651701,9728813)
+  ) +
+  theme(
+    panel.background = element_blank(),
+    panel.border     = element_blank(),
+    panel.grid.minor = element_blank(),
+    panel.grid.major = element_line(color = "transparent"),
+    legend.position = "bottom",
+    axis.title = element_blank()
+  ) +
+  scale_fill_manual("Region",breaks = c("Canada", "IPHC", "United States"), 
+                    values=c("grey80", "#CC6666", "grey40")
+                    )
+
+# Save plot for manuscrip
+ggsave("Fig1_IPHC.png",
+       plot = IPHC,
+       width = 6,
+       height = 5,
+       units = "in",
+       path = Path_Save)
+
+```
+
+![Fig 1. Map of North America with the regulatory areas of the International Paific Halibut Comission and the NAFO sub-region containing the Gulf of Maine arrangement](./Figures/Fig1.png)
+
+```{r Spatial_data, eval = F, echo = F, warning=F, message=F, results = 'hide'}
+
+# List of DBEM INDEX within the EEZ
+#Data provided by Vicki Lam
+EEZIDs_List <- read_excel(paste(Data_Path,"/Spatial/Updated_EEZList_17June2016.xlsx",sep=""))
+EEZ_CellID <- read_excel(paste(Data_Path,"/Spatial/EEZ_CellID.xlsx",sep=""))
+colnames(EEZ_CellID) <- c("EEZID","INDEX")
+
+# DBEM Coordinate system
+Coor <- fread(paste(Data_Path,"/Spatial/Lon_Lat_DBEM.txt",sep=""),header = FALSE)
+colnames(Coor) <- c("INDEX","Longitude","Latitude")
+
+### Select EEZs
+EEZs <- c(
+  "Canada (Pacific)",
+  "Canada (Arctic)",
+  "USA (West Coast)",
+  "USA (Alaska, Arctic)",
+  "USA (Alaska, Subarctic)",
+  "Canada (Arctic)",
+  "Canada (East Coast)",
+  "USA (East Coast)"
+)
+
+### North America Initial Map ####
+
+path_world <- paste(Data_Path,"/Spatial/TM_WORLD_BORDERS",sep="")
+file_name <- "TM_WORLD_BORDERS"
+
+World_Land_sf <- st_read(dsn = path_world, 
+                         layer = file_path_sans_ext(file_name)
+) %>% 
+  st_transform(crs = 4326)
+
+# names(World_Land_sf)
+
+North_America_Land <- World_Land_sf %>% 
+  filter(NAME %in% c("Canada","United States")) %>% 
+  st_transform(crs = 3832) # 4326 use this to merge with DBEM data
+# 3832 use this to center the map and plot
+
+#### _____________________TEST _____________________ #
+# head(North_America_Land)
+# ggplot(North_America_Land) +
+#   geom_sf() +
+#   coord_sf(xlim = c(-120, -179),
+#            ylim = c(30,70)
+#   )
+##__________________________________________ #
+
+### North America EEZs Map ####
+
+path_eez <- paste(Data_Path,"/Spatial/World_EEZ_v10_2018",sep="")
+#The File
+fnam_eez <- "eez_v10.shp"
+
+eez_world_sf <- st_read(dsn = path_eez, 
+                        layer = file_path_sans_ext(fnam_eez)
+) %>% 
+  st_transform(crs = 4326)# 4326 use this to merge with DBEM data
+# 3832 use this to center the map and plot
+
+#### _____________________TEST _____________________ #
+# head(eez_world_sf)
+### Test this map
+# ggplot(ezz_North_America) +
+#   geom_sf()
+##__________________________________________##
+
+#### IPHC Regulatory areas ####
+
+## Correct DBEM for Alaska ####
+IHPC_EEZs <- c(
+  "Canada (Pacific)",
+  # "Canada (Arctic)"
+  "USA (West Coast)",
+  "USA (Alaska, Arctic)",
+  "USA (Alaska, Subarctic)"#,
+  # "Russia (Far East)"
+)
+
+IPHC_EEZsID <- EEZIDs_List %>% 
+  filter(Name %in%IHPC_EEZs) %>% 
+  left_join(EEZ_CellID,
+            by = "EEZID") %>% 
+  left_join(Coor,
+            by = "INDEX")
+
+# "Move" the map so results are not in the other side of the world and it matches the projection I want
+IPHC_Coor_Corrected <- IPHC_EEZsID %>% 
+  filter(Longitude > 0) %>% 
+  mutate(Longitude = Longitude-360)
+
+IPHC_Coor_Corrected <- IPHC_EEZsID %>% 
+  filter(Longitude < 0) %>% 
+  bind_rows(IPHC_Coor_Corrected) %>% 
+  filter(Latitude > 25)
+
+# Create new column to merge with shapefiles
+
+IPHC_Coor_Corrected_Clean <- IPHC_Coor_Corrected %>% 
+  mutate(
+    State = ifelse(Name == "Canada (Pacific)", "British Columbia",
+                   ifelse(Name == "USA (West Coast)","WAORCA","Alaska"))
+  ) %>% 
+  select(
+    # State,
+    INDEX,
+    longitude = Longitude,
+    latitude = Latitude)
+
+# Now we load IPHC shapefiles ####
+path_IPHC <- paste(Data_Path,"/Spatial/IPHC_RegulatoryAreas/",sep="")
+
+# The Canada file
+fnam_IPHC_C <- "IPHC_RegulatoryAreas_CAN"
+
+IPHC_Reg_C <- st_read(dsn = path_IPHC, 
+                      layer = file_path_sans_ext(fnam_IPHC_C)
+) %>% 
+  select(
+    ID,
+    Country = COUNTRY,
+    State = PROV_EN,
+    RegArea
+  ) %>% 
+  mutate(Comments = "NA") %>% 
+  st_transform(crs = 4326)
+
+# 4326 use this to merge with DBEM data
+# 3832 use this to center the map and plot
+
+#### _____________________TEST _____________________##
+# head(IPHC_Reg_C)
+# ggplot(IPHC_Reg_C) +
+# geom_sf()
+##_________________________________________________##
+# The US File
+fnam_IPHC_US <- "IPHC_RegulatoryAreas_US"
+
+IPHC_Reg_US <- st_read(dsn = path_IPHC, 
+                       layer = file_path_sans_ext(fnam_IPHC_US)
+) %>% 
+  st_transform(crs = 4326)
+
+#### _____________________TEST _____________________ #
+# head(IPHC_Reg_US)
+# ggplot(IPHC_Reg_US) +
+#   geom_sf()
+##_________________________________________________##
+
+### Combine both shapefiles
+
+IPHC_Reg <- rbind(IPHC_Reg_US,IPHC_Reg_C)
+
+#### _____________________TEST _____________________ #
+# head(IPHC_Reg,12)
+# tail(IPHC_Reg)
+# unique(IPHC_Reg$State)
+
+# It's going to take a while... 
+# ggplot(IPHC_Reg) +
+#   geom_sf()
+##_________________________________________________##
+
+# Now join the Shapefile with the DBEM lat/long dataset
+
+# Convert DBEM to sf
+IPHC_Coor_sf = st_as_sf(IPHC_Coor_Corrected_Clean,
+                        coords = c("longitude", "latitude")) %>% 
+  st_set_crs(4326) %>% # to match shapefiles
+  st_transform(4326) # to match shapefiles
+
+# head(IPHC_Coor_sf)
+
+# Merge DBEM sf to polygons
+IPHC_Reg_DBEM <- st_join(IPHC_Reg,
+                         IPHC_Coor_sf, join = st_contains) %>% 
+  filter(!is.na(INDEX)) %>%
+  arrange(INDEX) 
+# %>% 
+#   st_transform(3832) # Go back to original projection otherwise doesnt like to plot
+
+IPHC_Reg_DBEM_df <- as.data.frame(IPHC_Reg_DBEM) %>% 
+  select(INDEX,RegArea)
+
+#### _____________________TEST _____________________ #
+# head(IPHC_Reg_DBEM_df)
+# IPHC_Reg_DBEM_df %>% 
+#   arrange(INDEX) %>% 
+# head()
+##_________________________________________________##
+
+### STOP 
+## Go to the results and now estimate the %change by region using IPHC_Reg_DBEM_df then, convert it to sf and merge it with IPHC_Reg
+
+# Gulf of Maine ####
+#### NAFO data ####
+
+# path_NAFO <- paste(Data_Path,"/Spatial/NAFO",sep="")
+#The File
+# fnam_NAFO <- "Divisions"
+
+# NAFO_Area <- st_read(dsn = path_NAFO,
+# layer =file_path_sans_ext(fnam_NAFO))
+
+Zones <- c(
+  "5Ze",
+  # "5Zw",
+  "5Y",
+  "4X"
+)
+
+# NAFO_5z <- NAFO_Area %>% 
+# filter(ZONE %in% Zones)
+
+#### _____________________TEST _____________________ #
+# head(NAFO_5z)
+
+# ggplot(NAFO_5z) +
+# geom_sf()
+# geom_sf(aes (fill = ZONE))
+##_________________________________________________##
+
+### Atlantic EEZ polygon (I don't think we need this for now) ####
+
+Atlantic_EEZs <- c(
+  "Canada (Arctic)",
+  "Canada (East Coast)",
+  "USA (East Coast)"
+)
+
+Atlantic_EEZsID <- EEZIDs_List %>%
+  filter(Name %in% Atlantic_EEZs) %>%
+  left_join(EEZ_CellID,
+            by = "EEZID") %>%
+  left_join(Coor,
+            by = "INDEX")
+
+### Atlantic DBEM Data ####
+
+GB_Coor <- Coor %>% 
+  filter(INDEX %in% Atlantic_EEZsID$INDEX) %>% 
+  mutate(one = 1)
+
+# Atlantic Land polygon ####
+
+Countries <- c(
+  "Canada",
+  "United States"
+)
+
+### EEZ GM ####
+eez_GM <- eez_world_sf %>% 
+  filter(Territory1 %in% Countries)
+
+#### _____________________TEST _____________________ #
+# ggplot() +
+#   geom_sf(data = eez_GM) +
+#   coord_sf(xlim = c(-71.0592, -63.33333),
+#            ylim = c(40.5,45.9759)
+#            )
+##_________________________________________________##
+
+GM_Land <- World_Land_sf %>% 
+  filter(NAME %in% Countries)
+
+```
+
+##### The International Pacific Halibut Comission
+
+The IPHC was established by Canada and the United States to oversee the management of Pacific halibut (*Hippoglossus stenolepis*) [@IPHC:2014tz].
+There are 12 regulatory areas from wich 3AB holds 51.2% of the stock, followed by regions 2ABC and 4ACDE with 23.1% and 20.4%, respectively, and lastly region 4B with only 5.2% of the stock distribution [@IPHC:2018vz].
+In terms of management, the IPHC implements a total allowable catch (TAC) based on a yearly sampling of the Convention area in addition to a series of regulations to control fishing effort [@IPHC:2018vz].
+The TAC is divided between recreational, subsistence and commercial fishery, with a portion set aside for bycatch of other fisheries [@IPHC:2019wt].
+The commercial fishing season starts in March ending around November whith restrictions allowing only set line gear with J-type hooks targeting individuals over 81.3 cm with head on [@IPHC:2019wt].
+
+##### The Gulf of Maine Arrangement
+
+Since 1998 Canada and the US celebrate a "Resource Sharing Understanding" to inform the management of George Bank's Atlantic cod (*Gadus morhua*), and Eastern George Bank's haddock (*Melanogrammus aeglefinus*) and, yellowtail flounder (*Limanda ferruginea*) [@Pudden:2007bo; @CIA:2017uta; @TRAC:2016wu].
+The GoMA suggests catch-limits based on stocks' distribution produced by quaterly surveys and historical catch [@TRAC:2016wu], and so Canada and the US ultimatley take single management decissions [@Soboil:2006gw].
+In terms of manangement, the US has a multi species harvest control with area and season cloasures, mesh sizes, effort control, and mobile gear vessels that use bottom otter trawl gear [@Soboil:2006gw].
+In contrast, Canada has a quota system in addition to limited-entery licensig, fleet allocations, and mesh and fish size regulation, among other input controls.
+Canada inshore vessels fish Cod with longline and gillnet while haddock is mainly caught with bottom otter trawl gear [@Soboil:2006gw].
+
 #### Projecting Future Species Distribution
 
-We used a Dynamic Bioclimatic Envelope Model (DBEM) to project the distribution of species from 2015 to 2100, under two scenarios of climate change [@Cheung:2016hf; @Cheung:2016jd].
-The DBEM algorithm integrated ecophysiology, habitat suitability with spatial population dynamics of exploited fishes and invertebrates to project shifts in abundance, and potential fisheries catches  under climate change.
-The algorithm predicted species distribution based on depth range, latitudinal range, habitat preferences and an index of species association with major habitat types to estimate changes in abundance distribution over a 0.5' x 0.5' grid of the world oceans.
+We used a Dynamic Bioclimatic Envelope Model (DBEM) to project the distribution of species from 2015 to 2100 under two scenarios of climate change [@Cheung:2010dt; @Cheung:2016jd].
+The DBEM algorithm integrated ecophysiology and habitat suitability with spatial population dynamics of exploited fishes and invertebrates to project shifts in abundance and potential fisheries catches under climate change.
+The algorithm predicted species distribution based on depth and latitudinal range, habitat preferences and an index of species association with major habitat types to estimate changes in abundance distribution over a 0.5º x 0.5º grid of the world ocean.
 For each grid cell and time step, the model then calculated species carrying capacity according to sea surface temperature, salinity, oxygen content, sea ice extent (for polar species) and bathymetry, as well as the species preferences to these conditions.
@@
 Each model was downscaled to match the DBEM 0.5' x 0.5' grid using the nearest neighbor method, and in some cases, bilinear interpolation [@Cheung:2016hf].
-Finally, we used the model outputs for two scenarios of the Intergovernmental Panel on Climate Change (IPPC)-Representative Concentration Pathways (RCP); 2.6 (RCP 2.6) and 8.5 (RCP 8.5) representing a low greenhouse gas emission (strong mitigation) and a high greenhouse gas emission (business-as-usual) scenario, respectively [@IPCC:2014bz].
-To estimate model robustness and capture the structural uncertanty build within ESM models we averaged the DBEM results for all three models ($\mu±\sigma$) and marked regions where at least one ESM disagree with the rest.
+Finally, we used the model outputs for two scenarios of the Intergovernmental Panel on Climate Change (IPCC)-Representative Concentration Pathways (RCP) 2.6 and RCP 8.5 representing a low greenhouse gas emission (strong mitigation) and a high greenhouse gas emission (week mitigation) scenario, respectively  [@IPCC:2014bz].
+To estimate model robustness and capture the structural uncertanty build within ESM models, we averaged the DBEM results for all three models ($\mu±\sigma$) and marked regions where at least one ESM disagree in direction with the rest.
 
@@
 
-For estimating the percentage change of MCP at the regional scale, we frst aggregated the yearly mean MCP of all species per region ($X_{ry}$) and period:
+For estimating the percentage change of MCP at the regional scale, we frst aggregated the yearly mean MCP of all species per region ($X_{yr}$) and period:
 
 $$ X_{yr} = \sum_{s = 1}^n \hat{MCP_s}$$
+<!-- <eqn1> -->
 
 where *y* is year, *r* is region, *s* is species, *n* is total number of species, and $\hat{MCP}$ is the MCP averaged by the three ESMs.
-In the case of North America and the GoM agrement, region is defined as the 0.5' x 0.5' grid-cell within the EEZ and the specific NAFO regulatory areas, respectiveley.
-For the IPHC analysis, region is defined as the comission's regulatory areas (Fig.
+In the case of North America as a whole, and the GoM arrangement, region is defined as the 0.5' x 0.5' grid-cell within the EEZ and the specific NAFO regulatory areas, respectiveley.
+For the IPHC analysis, region is defined as the Comission's regulatory areas (Fig.
 1).
@@
 
-$$\Delta MCP_r = -(1-\frac{X_{t}}{X_{t0}})*100 $$
+$$\Delta MCP_r = -(1-\frac{X_{t}}{X_{t_0}})*100 $$
+<!-- <eqn2> -->
 
@@
 This way, Equ.
-2 shows the percentage change in MCP relative to today ($t_0$) by mid 21^st^ century when $X_T$ = $\mu$ `r Mid_In`-`r Mid_End`, and end of 21^st^ century when $X_T$ = $\mu$ `r End_In`-`r End_End`).
-The rationale between choosing these time periods was to provide a relative short-term projection (mid-century) that would be more policy-relevant but also show the long term trend.**
+2 shows the percentage change in MCP by mid $21^{st}$ century when $X_T$ = $\mu$ `r Mid_In`-`r Mid_End`, and end of $21^{st}$ century when $X_T$ = $\mu$ `r End_In`-`r End_End`, relative to today ($t_0$).
+The rationale between choosing these time periods was to provide a relative short-term projection (mid-century) that would be more policy-relevant but also show the long term trend (end of century).**
 
@@
 
-In addition, we borrowed the concept of “threat point” from game theory **RA defined as the minimum payoff that a player is willing to receive in order to cooperate with other players** (see Sumaila et al., this Volume).
-Thus we estimate the change in the $\hat{MCP}$ **RA (threat point)** that each country **RA (players)** would have for each species (hereafter referred as stock-share ratio), for both the IPHC and the GoM **DV arrangement**.
-**RA We define stock-share ratio as the proportion of the stock's distribution within the study area that each country has**.
-For this, we first modify equation 1, to estimate the aggregated yearly mean MCP of each species per region.
-We then average the results by the same previouslly metioned periods (present, mid and end of the 21^st^ century).
-Next, for each species we estimated the stock-share ratio ($\alpha$) that each region had during each time period:
-
-$$\alpha_{ts} = \frac{\theta_{rt}}{\delta_{ts}}$$
-
-where $\theta_{r}$ is the aggregated $\hat{MCP}$ of each region, and *t* is period.
-Finally, we estimated the percentage change in stock-share ratio substituting $X_f$ and $X_p$ by $\alpha_{fs}$ and $\alpha_{ps}$, respectively in equation 2.
+In addition, we borrowed the concept of “threat point” from game theory **RA defined as the minimum payoff that a player is willing to receive in order to cooperate with other players** (see Sumaila et al., this Special Feature).
+Thus, we estimate the change in the $\hat{MCP}$ **RA (threat point)** that each country **RA (players)** would have for each species (hereafter referred as stock-share ratio), for both the IPHC and the GoMA.
+**RA The stock-share ratio can be seen as the proportion of the stock's distribution within the study area that each country has**.
+For this, we first modify Equ.
+1, to estimate the aggregated yearly mean MCP of each species per region.
+We then average the results by the same previouslly metioned periods (present, mid and end of the $21^{st}$ century).
+Next, for each species we estimated the stock-share ratio ($\alpha_s$) that each region had during each time period:
+
+$$\alpha_{s} = \frac{\theta_{rt}}{\delta_{rt}}$$
+
+where $\theta_{rt}$ is the species' aggregated $\hat{MCP}$ of each region at time period *t*, and $\delta_{rt}$ is the species' aggregated $\hat{MCP}$ of the whole specie's distribution within the study area at the same time period.
+Finally, we estimated the percentage change in stock-share ratio substituting $X_{t_0}$ and $X_{t}$ by $\alpha_{t_0}$ and $\alpha_{t}$, respectively in Equ.
+2.
+The process was carried out for each ESM and results presented as mean standard deviation (sd).
+All of the analysis was done in the statistical software *R* version 3.5.2 (2018-12-20) with the associated packages, *data.table* [@Packagedatatable:2019uh],  *ggrepel* [@PackageggrepelAut:2018to], *gridExtra* [@PackagegridExtraM:2017wx], *knirt* [@PackageknitrAGen:2020wt], *RColorBrewer* [@PackagerColorBrewer:2014uw], *sf* [@PackagesfSimpleF:2018vp], and *tidyverse* [@PackagetidyverseE:2017vq].
+All code is available at https://github.com/jepa/OC_Transboundary.
 
@@
 
-```{r Changes_Data_All, eval =T, echo = F, fig.height=8, fig.width=12}
+```{r Changes_Data_All, eval =F, echo = F, fig.height=8, fig.width=12}
 
@@
 
-Shifts in the distribution of 33 jointly managed transboundary stocks of North America show that by 2050 maximum catch potential (MCP) of transboundary stocks will increase in Atlantic-Canadian and Alaskan waters and decrease in Pacific-Canadian and the US contiguous states (Fig.
+Shifts in the distribution of 33 jointly managed transboundary stocks of North America show that by 2050 MCP of transboundary stocks will increase in Atlantic-Canadian and Alaskan waters and decrease in Pacific-Canadian and the US contiguous states waters (Fig.
 2).
-Despite the overall trend, such changes will be less intense under the low emission scenario (Fig.
+Such changes will be more intense under the high emission scenario (Fig.
 2-A).
-Under the high emission scenario, MCP will be reduced in a larger area and with greater intensity (Fig.
+Under the low emission scenario, MCP will be reduced in a reduced area and with lower intensity (Fig.
 2-B).
-Such changes are expected to intensify towards the end of the 21st century, although with greater uncertainty (**Fig A1.1**).
+Impacts of cliamte change are expected to intensify towards the end of the $21^{st}$ century, although with greater uncertainty (**Fig A1.1**).
 
 ![Fig 2.
-Percentage change of MCP of transboundary fisheries of North America for mid century (2046-2055) **RA referenced** to 2005-2014 under a A) low emission scenario and; B) high emission scenario.
-Points represent areas where at least one model do not agree in the direction of change](./Results/Fig2.png)
-
-```{r Changes_Per_Species_T, eval=F, echo=F}
+Percentage change of MCP of transboundary stocks of North America for mid $21^{st}$ century (2041-2060) **RA relative** to present (2005-2014) under a A) lohighw emission scenario and; B) low emission scenario.
+Points represent areas where at least one model do not agree in the direction of change](./Figures/Fig2.png)
+
+```{r Changes_Per_Species_F, eval=F, echo=F}
 
@@
 
-In consequence, **RA each** country's share-ratio of different species would change in the direction as expected from the effects of ocean warming, regardless of the RCP scenario.
-Overall, shifts will be amplified under the high emission scenario relative to the low greenhouse emission scenario pathway (Table 2).
+**In consequence, RA-each country's share-ratio of different species will change with an overall benefit to northern regions, regardless of the RCP scenario.** Overall, shifts will be amplified under the high emission scenario relative to the low greenhouse emission scenario pathway (Table 2).
 
 Table 2.
-Average (standard deviation) of 33 transboundary species stock-share of all models for each EEZ and emission scenario for mid and end of the 21st century.
+Average (standard deviation) of 33 transboundary species stock-share of all models for each EEZ and emission scenario for mid and end of the $21^{st}$ century.
 Averages might not add to 100% due to model differences (e.g., standard deviation)
@@
 
-Even under a low emission scenario, most transboundary fish stocks sharing ratios will change by 2050 in the direction as expected from the effects of ocean warming.
-However, such changes will vary depending on the species, resulting in management consequences related to the rules placed by the different treaties.
-In the case of the IPHC, at least one third of regulatory areas will see a reduction in MCP of Pacific halibut by 2050 relative to current MCP of each area, regardless of the climate change scenario (Fig.
+In the case of the IPHC, at least one third of regulatory areas will see a reduction in MCP of Pacific halibut by 2050 relative to current MCP, regardless of the climate change scenario (Fig.
 3).
-Poleward shifts might be constrained by the geopolitical position of countries, as well as geographic design of the coastline.
 It is likely that the stock shift from the U.S.
-contiguous states towards Canada will offset the shift of the former towards northern regions, resulting in undetectable changes in areas 2B and 2C under both climate change scenarios.
+contiguous states towards Canada will offset the shift of the **RA later** towards northern regions, resulting in undetectable changes in Canadian area 2B and Alaskan 2C under both climate change scenarios.
 The potential movement of halibut westward will increase the MCP of regulatory areas 3B (under a low emission scenario) and 4ABCE along the Aleutian Islands and Bering Sea.
-
-**Region 4D, the most poleward region of the IPHC convention area is expected to gain MCP under high emission as halibut suitable habitat expands as sea ice retreats [@IPCC:2019to].
-In contrast, under a low emission scenario sea ice is expected to stabilize towards mid century, thus providing less habitat suitabillity for halibut, resulting in undetectable changes in MCP for the region (Fig 3.
-B).
-If the high emission scenario continues towards the end of the century only the regions RA-on-the-northwest-of 3B will see a gain in MCP (Fig.
-A1.2).
-In contrast, polar regions 4DE will continue to see a reduction in MCP as sea ice stabilizes**
-
-```{r IPHC_Map_Result_Regions, eval=T, echo=F}
+**Regions 4DE, the most poleward regulatory areas of the IPHC, are expected to gain MCP by mid (Fig.
+3) and end of the $21^st$ century (Fig.
+A1.2) under a high emission scenario due to the expansion of halibut suitable habitat as sea ice retreats (Fig.
+A3.1).
+In contrast, under a low emission scenario, sea ice is expected to stabilize towards mid $21^st$ century, thus providing less "new" suitable habitat for P.
+halibut and resulting in undetectable changes in MCP for the region (Fig 3.
+B) and decreasing even more towards 2100 (Fig.
+A1.2).**
+
+```{r IPHC_Map_Result_Regions, eval=F, echo=F}
 
@@
 
-  if(ModelRCP = "GFDL"){
+  if(ModelRCP == "GFDL"){
 
@@
     }
-
     Filepath <- paste("/Volumes/DATA/JULIANO_NEYMAR/PristineSeasData/Climate",ModelRCP,"",sep="/")
@@
 
-      Bottom = paste("botTemp_",2005,".txt",sep="")
+      Bottom = paste("botTemp_",yr,".txt",sep="")
 
@@
 
-```{r 4D_exploration, eval=F, echo=F,message=F, warning=F}
+```{r 4DE_exploration, eval=F, echo=F,message=F, warning=F}
 
@@
 # Variables
-Model = c("GFDL","IPSL","MPIS")
+Model = c("GFDL","IPSL","MPI")
 RCP = c("rcp26","rcp85")
@@
 
-for(v in 3:3){
+for(v in 1:3){
   # Loop through RCPs
@@
           row.names = F)
-
-### Exploration at the biological level
-
-# exploited_species_list <- fread("/Volumes/DATA/PROJECTION exploited species ENM/exploited_species_list.csv")
-# 600514
-
-# Isolate Regions
-
-DE <- IPHC_MCP_Change %>% 
-  filter(RegArea %in% c("4D","4E"))
 
@@
 
-```{r Figure_3, eval =F, echo =F, fig.cap="Percentage Change of MCP for Species managed by the IPHC.
-A, RCP 2.6 represents a low emission scenario (high mitigation).
-B, RCP 8.5 represents a high emission scenario (status quo)"}
+```{r halibut_enviro, eval =F, echo = F}
+
+# Read Data
+
+Environmental_Data_Halibut <- read.csv("~/Documents/UBC/OC_Special_Issue/Ecol/Data/Distribution/Environmental_Data_Halibut.csv")
+
+# Isolate Regions
+
+DE_Regions <- IPHC_Reg_DBEM_df %>% 
+  filter(RegArea %in% c("4D","4E")) %>% 
+  left_join(Environmental_Data_Halibut,
+            by ="INDEX") %>% 
+  group_by(Model,RCP,Variable,Year,RegArea) %>% 
+  summarise(
+    Total_Reg = mean(Value,na.rm=T)
+    ) %>% 
+  group_by(RCP,Variable,Year,RegArea) %>% 
+  summarise(
+    Mean_GCMs = mean(Total_Reg,na.rm=T),
+    sd_GCMs = sd(Total_Reg,na.rm=T)
+    ) %>% 
+  group_by(RCP,Variable,RegArea) %>% # Running mean as Kleisner & Pauly 2012
+    mutate(RMean = rollmean(x = Mean_GCMs, 10,
+                            align = "right",
+                            fill = Mean_GCMs),
+           Rsd = rollmean(x = Mean_GCMs, 10,
+                            align = "right",
+                            fill = sd_GCMs)
+    ) %>% 
+  filter(Year >= 2015) %>% 
+  ungroup() %>% 
+  mutate(
+    RCP = ifelse(RCP == "rcp26","Low Emission","High Emission"),
+    Variable = ifelse(Variable == "Ice","Ice Extension",
+                      ifelse(Variable == "Temperature","Bottom Temperature (ºC)","Bottom Salinity")
+                      )
+    )
+
+# Ribbom version
+
+ggplot(DE_Regions) + 
+  geom_ribbon(aes(
+    x = Year,
+    ymin = RMean - sd_GCMs,
+    ymax = RMean + sd_GCMs,
+    # colour = RCP,
+    fill = RCP
+  ),
+  alpha = 0.2
+  ) +
+  geom_line(
+    aes(
+      x = Year,
+      y = RMean,
+      colour = RCP
+    )
+  ) +
+  facet_wrap(~RegArea +Variable,
+             scales ="free_x") +
+  ggtheme_plot() +
+  scale_x_continuous(breaks = seq(2010,2100,30),
+                     limits = c(2010,2100)
+  ) +
+  scale_color_manual("Climate Change Scenario",
+                     values=c("red","blue")
+  ) + 
+  scale_fill_manual("Climate Change Scenario",
+                    values=c("red","blue")
+  ) + 
+  ylab("Running Mean (10 yrs)")
+
+ggsave("Environ_Sup.png",
+       plot = last_plot(),
+       width = 10,
+       height =8,
+       units = "in",
+       path = "./Results/Sup"
+       )
+
+```
+
+```{r DBEM_Uncertanty, eval = F, echo = F}
+
+#### DBEM Uncertanty
+
+### Today
+
+Today_Uncertanty <- DBEM_Corrected %>% 
+  filter(Species %in% Selected_Species) %>% 
+  left_join(IPHC_Reg_DBEM_df,
+            by = "INDEX") %>% 
+  filter(!is.na(RegArea)) %>% 
+  mutate(RCP = ifelse(Model %in% RCP,"Low Emission","High Emission")) %>% 
+  gather("Year","MCP",Beg_In:Beg_End) %>% 
+  mutate(Period = ifelse(Year >= Beg_In & Year <= Beg_End,"Begining","NA")) %>% 
+  group_by(RegArea,Model,RCP,Year,Period) %>% 
+  summarise(Regional_MCP =sum(MCP,na.rm=T)) %>% 
+  group_by(RegArea,Model,RCP) %>% 
+  summarise(Today_MCP =mean(Regional_MCP,na.rm=T))
+
+IPHC_MCP_Change_Uncert <- DBEM_Corrected %>% 
+  filter(Species %in% Selected_Species) %>% 
+  left_join(IPHC_Reg_DBEM_df,
+            by = "INDEX") %>% 
+  filter(!is.na(RegArea)) %>% 
+  mutate(RCP = ifelse(Model %in% RCP,"Low Emission","High Emission")) %>% 
+  gather("Year","MCP",Beg_In:End_End) %>%
+  group_by(Model,RCP,Year,RegArea) %>%
+  summarise(Regional_MCP =sum(MCP,na.rm=T)) %>% 
+  group_by(RCP,Model,RegArea) %>% # Running mean as Kleisner & Pauly 2012
+  mutate(RMean = rollmean(x = Regional_MCP, 10,
+                          align = "right",
+                          fill = Regional_MCP)
+  ) %>% 
+  mutate(GCM = ifelse(Model == "GFDL26F1" | Model == "GFDL85F1","GFDL",
+                      ifelse(Model == "IPSL26F1" | Model == "IPSL85F1", "IPSL",
+                             ifelse(Model == "MPI26F1" | Model == "MPI85F1","MPI","NA"
+                             )
+                             )
+                      )
+  ) %>% 
+  filter(Year >= 2015) %>% 
+  left_join(Today_Uncertanty,
+            by = c("RegArea","Model","RCP")) %>% 
+  mutate(Index = RMean/Today_MCP)
+
+ggplot(IPHC_MCP_Change_Uncert) +
+  geom_line(
+    aes(
+      x = as.numeric(Year),
+      y = Index,
+      color = GCM,
+      linetype = RCP
+    )
+  ) +
+  facet_wrap(~RegArea,
+             scales = "free_y") +
+  labs(
+    x = "Year",
+    y ="Index (Future MCP/Present)"
+    ) +
+  scale_color_manual("Global Circulation model",
+                     values=c("#EEA410","#B53CB9","#2EBC67")
+  ) +
+  scale_x_continuous(breaks = seq(2010,2100,30),
+                     limits = c(2010,2100)
+  ) +
+  ggtheme_plot()
+
+ggsave("Model_Uncer_Sup.png",
+       plot = last_plot(),
+       width = 12,
+       height =8,
+       units = "in",
+       path = "./Results/Sup"
+       )
+
+```
+
+```{r Figure_3, eval =F, echo =F}
 
@@
 ![Fig 3.
-Percentage change of MCP for species managed by the IPHC for mid century (2046-2055) relative to 2005-2014 under a A) low emission scenario and B) high emission scenario.
-Labels marked with "*" represent regions where models do not agree in direction of change.](./Results/Fig3.png)
-
-The same poleward trend is expected in the change of Pacific halibut stock-share ratio with the average proportion increasing up to 25% in some northern regions and decreasing by 10% in southern regions, in relation to the present proportion (Fig.
+Percentage change of MCP for species managed by the IPHC for mid $21^{st}$ century (2041-2060) relative to present 2005-2014 under a A) low emission scenario and B) high emission scenario.
+Labels marked with "*" represent regions where models do not agree in direction of change.](./Figures/Fig3.png)
+
+The same poleward trend is expected in the change of Pacific halibut stock-share ratio with the average proportion increasing up to 25% in some northern regions and decreasing by 10% in southern regions, relative to the present proportion (Fig.
 4).
 Maintaining emissions to lower levels **RA through** 2050 would potentially leave unchanged the stock-share ratio of three regulatory areas (3AC, and 4D) and negatively change regulatory area 2A.
-On the other hand, failing to achieve such target will decrease the stock-share ratio **RA in** almost half of the regulatory areas (2AC, 3AB).
+On the other hand, failing to achieve such target will decrease the stock-share ratio **RA in** the most productive regulatory areas (2AC, 3AB).
 
@@
 
-```{r Figure_4, eval =F, echo =F, fig.cap="Percentage change of stock-share ratio for IPHC under two RCPs for Mid century (2046-2055)"}
+```{r Figure_4, eval =F, echo =F}
 
@@
 
-![Fig 4. Percentage change of stock-share ratio for IPHC under A) low emission scenario and B) high emission scenario for mid century (2046-2055) relative to 2005-2014.](./Results/Fig4.png)
+![Fig 4.
+Percentage change of stock-share ratio for IPHC under A) low emission scenario and B) high emission scenario for mid $21^{st}$ century (2041-2060) relative to present 2005-2014.
+Values represent the mean of 3 ESM; error bars represent $\mp$ sd.](./Figures/Fig4.png)
 
@@
 
-While some regulatory areas of the IPHC will see **RA an incremental increase** in species' MCP, the results for the Gulf of Maine (NAFO area 5Z) show an overall decrease in MCP by 2050, depending on the climate change scenario.
-MCP of cod and haddock will decrease within the whole Gulf with no apparent win for any country in reference to 2014 (Fig.
+While some regulatory areas of the IPHC will see **RA an incremental increase** in P.
+halibut MCP, the results for the Gulf of Maine show an overall decrease in MCP by 2050, regardless of the climate change scenario or ESM (Fig.
+5), intensifying by the end of the $21^{st}$ century (Fig.
+A1.3).
+For cod and haddock, MCP will decrease within the whole Gulf with no apparent win for any country in reference to the current period (Fig.
 5).
-For yellowtail flounder, some discrete areas are expected to increase with no particular pattern.
-Despite the overall reduction in MCP in comparison to current values, there is a benefit of achieving a low emission scenario, as reductions intensify under the high emission scenario.
+For Y.
+founder, despite an overall reduction, some discrete areas are expected to increase with no particular pattern **RA and high uncertainty as ESMs in these regions do not agree in the direction of change.** Despite the overall reduction in MCP for all three species in comparison to current values, there is a benefit of achieving a low emission scenario as reductions intensify under the high emission scenario.
 
@@
 
-# Mean_Data_GoMb <- Mean_Data_GoM %>% # In case you want filter a specific species
-#   filter(Species == "Limanda ferruginea")
+# New_Mean_Data_GoM <- New_Mean_Data_GoM %>% # In case you want filter a specific species
+#   filter(Species == "Limanda ferruginea",
+#          Mean_ESM_MCP_Chng >= 0)
 
@@
 
-  Name = paste("New_Change_GB_26_85_Mid.png",sep="_")
+  # Name = paste("New_Change_GB_26_85_Mid.png",sep="_")
+Name = "Test.png"
 
@@
 
+```{r Figure_out_outliers, eval =F, echo =F}
+
+Outliers <- c(64310,64311,64312,65028,65029,67180,67181,69344,69345,70066)
+
+Environmental_Data_GoM <- read.csv("~/Documents/UBC/OC_Special_Issue/Ecol/Data/Environ/Environmental_Data_GoM.csv")
+
+Outlier_Species <- c(
+  # "Gadus morhua",  # Cod 600069, Demersal, 600 depth
+  "Limanda ferruginea"#, # Yellowtail flounder 600521, Demersal 82 depth
+  # "Melanogrammus aeglefinus" # Haddock 601381, Demersal 450
+)
+
+N_Lim <- 45.9759
+S_Lim <- 41
+W_Lim <- -72.0592
+E_Lim <- -63.33333
+
+### Averag depth data
+EleAvg <- read.table("~/Documents/UBC/OC_Special_Issue/Ecol/Data/Environ/EleAvg.txt", quote="\"", comment.char="") %>% 
+  mutate(INDEX = seq(1,259200,1)) %>% 
+  rename(Depth = V1) %>% 
+  filter(INDEX %in% Atlantic_EEZsID$INDEX) %>% 
+  left_join(Atlantic_EEZsID, by = "INDEX") %>% 
+  filter( # Limit the area to George's bank
+    Latitude < N_Lim, # North
+    Latitude > S_Lim, # South 
+    Longitude > W_Lim, # West
+    Longitude < E_Lim
+  ) %>% 
+  mutate(
+    Outlier = ifelse(INDEX %in% Outliers,"Yes","No"),
+    Depth = ifelse(Depth <= -800,-800,
+                   ifelse(Depth >=0,0,Depth))
+  )
+
+elev_plot <-
+ggplot(EleAvg) +
+  geom_tile(
+    aes(
+      x = Longitude,
+      y = Latitude,
+      # fill = log10(abs(Depth)),
+      fill = Depth
+    )
+  ) +
+  scale_fill_gradientn( "Depth (m)",
+    colours = terrain.colors(10),
+                       limits=c(-1000,0),
+                       breaks =seq(-1000,0,200)
+  ) +
+  geom_sf(data = GM_Land, colour = "lightgrey") +
+  geom_sf(data = eez_GM, fill = NA) +
+  coord_sf(xlim = c(-71.0592, -63.33333),
+           ylim = c(41,45.5)
+  ) +
+  ggtheme_map() +
+  theme(
+    axis.line = element_line(colour = "black", size = .5),
+    axis.ticks = element_line(size = .5),
+    axis.text.x = element_text(size = 8,
+                               angle = 0,
+                               face = "plain"),
+    axis.text.y = element_text(size = 8),
+    # legend.key = element_rect(size = 3),
+    legend.key.height = unit(2,"line"),
+    legend.title = element_text(size = 10),
+    legend.text = element_text(size = 10),
+    legend.position = "right"
+  )
+
+Name = "Elevation_GoM.png"
+
+ggsave(Name,
+       plot = last_plot(),
+       width = 20,
+       height = 10,
+       units = "in",
+       path = Path)
+
+Specie <- "Limanda ferruginea"
+
+Enviro_chng_gom <- Environmental_Data_GoM %>% 
+  mutate(# Indicate the three period times
+    Period = ifelse(Year >= Beg_In & Year <= Beg_End,"Begining",
+                    ifelse(Year >= Mid_In & Year <= Mid_End,"Mid_Century",
+                           ifelse(Year >= End_In & Year <= End_End,"The_End_Century",
+                                  "Other_Years"))
+    )
+  ) %>% 
+  filter(Period != "Other_Years",
+         Variable == "Temperature") %>% # Remove unwanted years
+  group_by(INDEX,Model,RCP,Period,Variable) %>%
+  summarise(
+    Mean_Temp = mean(Value, na.rm = T) # Temporal mean
+  ) %>% 
+  spread(Period,Mean_Temp) %>% 
+  mutate_at(vars(Mid_Century, # Devide future values by present
+                 The_End_Century),
+            funs(ifelse(Begining > 0, ./Begining,.)) #if no species today value is the future
+  ) %>% 
+  mutate_at(vars(Mid_Century, # Estimate percentage change
+                 The_End_Century),
+            funs(ifelse(Begining == 0 & . == 0, 0, # If for no change than 0
+                        ifelse(Begining == 0 & . > 0, 100, # If changes from 0 to anything then 100
+                               round(-(1-.)*100) # Estimate percentage change
+                        )
+            )
+            )
+  ) %>% 
+  ungroup() %>% 
+  mutate(
+    Outlier = ifelse(INDEX %in% Outliers,"Yes","No"),
+    RCP = ifelse(RCP == "rcp26","Low Emisison","High Emission")
+  ) %>% 
+  group_by(INDEX,RCP,Variable,Outlier) %>% 
+  summarise(
+    Mean_Model = mean(Mid_Century,na.rm=T)
+  ) %>% 
+  left_join(Coor)
+
+temp_plot <- ggplot(Enviro_chng_gom) +
+  geom_tile(
+    aes(
+      x = Longitude,
+      y = Latitude,
+      fill = Mean_Model
+    ),
+    size = 0.5
+  ) +
+  scale_fill_gradientn(paste("Percentage Change of bottom temperature\n                     (",Mid_In,"-",Mid_End,")"), 
+                       limits=c(3,18),
+                       breaks =seq(3,18,3),
+                       colours = terrain.colors(10)
+  ) +
+  geom_sf(data = GM_Land, colour = "lightgrey") +
+  geom_sf(data = eez_GM, fill = NA) +
+  coord_sf(xlim = c(-71.0592, -63.33333),
+           ylim = c(41,45.5)
+           ) +
+  facet_wrap(~RCP) +
+  ggtheme_map() +
+  theme(
+    axis.line = element_line(colour = "black", size = .5),
+    axis.ticks = element_line(size = .5),
+    axis.text.x = element_text(size = 8,
+                               angle = 0,
+                               face = "plain"),
+    axis.text.y = element_text(size = 8),
+    # legend.key = element_rect(size = 3),
+    legend.key.width = unit(2,"line"),
+    legend.title = element_text(size = 10),
+    legend.text = element_text(size = 10)
+  )
+
+Name = "Temp_Cnhg_Mid_GoM.png"
+
+ggsave(Name,
+       plot = last_plot(),
+       width = 6,
+       height = 4,
+       units = "in",
+       path = Path)
+
+###### Elevation and temperature plots
+
+temp_ele <- grid.arrange(elev_plot,temp_plot,
+             ncol = 1)
+
+Name = "Temp_ele_GoM.png"
+
+ggsave(Name,
+       plot = temp_ele,
+       width = 6,
+       height = 6,
+       units = "in",
+       path = Path)
+
+#### Make maps PER model
+
+#### New analysis ####
+Per_Model_Chng_GoM <- Atlantic_DBEM %>% 
+  mutate(RCP = ifelse(Model %in% c("GFDL26F1","IPSL26F1","MPI26F1"),"Low Emission","High Emission")) %>%
+  tidyr::gather("Year","Change",`2005`:`2099`) %>%
+  mutate(Change = replace_na(Change, 0)) %>% # Convert NA's into 0's
+  mutate(# Indicate the three period times
+    Period = ifelse(Year >= Beg_In & Year <= Beg_End,"Begining",
+                    ifelse(Year >= Mid_In & Year <= Mid_End,"Mid_Century",
+                           ifelse(Year >= End_In & Year <= End_End,"The_End_Century",
+                                  "Other_Years"))
+    )
+  ) %>% 
+  filter(Period != "Other_Years",
+         Species %in% Outlier_Species) %>% # Remove unwanted years
+  group_by(INDEX,Model,RCP,Period,Species) %>%
+  summarise(
+    Mean_Temp = mean(Change, na.rm = T) # Temporal mean
+  ) %>% 
+  spread(Period,Mean_Temp) %>% 
+  mutate_at(vars(Mid_Century, # Devide future values by present
+                 The_End_Century),
+            funs(ifelse(Begining > 0, ./Begining,.)) #if no species today value is the future
+  ) %>% 
+  mutate_at(vars(Mid_Century, # Estimate percentage change
+                 The_End_Century),
+            funs(ifelse(Begining == 0 & . == 0, 0, # If for no change than 0
+                        ifelse(Begining == 0 & . > 0, 100, # If changes from 0 to anything then 100
+                               round(-(1-.)*100) # Estimate percentage change
+                        )
+            )
+            )
+  )%>% 
+  mutate(
+    Outlier = ifelse(INDEX %in% Outliers,"Yes","No")
+  ) %>% 
+  left_join(Coor) %>% 
+  mutate_at(vars(Mid_Century,
+                 The_End_Century),
+            funs(ifelse(. > 100, 100,.)
+            )  # set everything over 100 to 100
+  ) #%>% 
+  # filter(Outlier == "Yes")
+
+# plot results  
+ggplot(Per_Model_Chng_GoM) +
+  geom_tile(
+    aes(
+      x = Longitude,
+      y = Latitude,
+      fill = Mid_Century,
+      # fill = log10(abs(Mid_Century)),
+      color = Outlier
+      # fill = Depth
+    ),
+    size = 0.5
+  ) +
+  scale_fill_gradient2(paste("MCP Percentage Change of",Outlier_Species,"\n                     (",Mid_In,"-",Mid_End,")"), # If not using the bins
+                       limits=c(Lim_Neg,
+                                Lim_Max),
+                       breaks = Seq,
+                       na.value = 'darkred' # NA values are present when the species is no more 
+  ) +
+  scale_color_manual(values=c(NA,"yellow")) + # for Bins option A
+  geom_sf(data = GM_Land, colour = "lightgrey") +
+  coord_sf(xlim = c(-71.0592, -63.33333),
+           ylim = c(41,45.5)
+  ) +
+  facet_wrap(~RCP+Model) +
+  ggtheme_map() +
+  theme(legend.key.width =unit(6,"line"))
+
+Name = "MCP_Cnhg_Mid_GoM_Outlier.png"
+
+ggsave(Name,
+       plot = last_plot(),
+       width = 14,
+       height = 10,
+       units = "in",
+       path = Path)
+
+#### Check those outliers in the GFDL
+
+GFDL_Out <- Atlantic_DBEM %>% 
+  filter(Model == "GFDL26F1",
+         Species %in% Outlier_Species,
+         INDEX %in% Outliers) %>%
+  tidyr::gather("Year","Change",`2005`:`2099`) %>%
+  # mutate(Change = replace_na(Change, 0)) %>% # Convert NA's into 0's
+  mutate(# Indicate the three period times
+    Period = ifelse(Year >= Beg_In & Year <= Beg_End,"Begining",
+                    ifelse(Year >= Mid_In & Year <= Mid_End,"Mid_Century",
+                           ifelse(Year >= End_In & Year <= End_End,"The_End_Century",
+                                  "Other_Years"))
+    )
+  ) %>% 
+  filter(Period != "Other_Years") %>% # Remove unwanted years
+  group_by(INDEX,Model,Period,Species) %>%
+  summarise(
+    Mean_Temp = mean(Change, na.rm = T) # Temporal mean
+  ) %>% 
+  spread(Period,Mean_Temp) %>% 
+  mutate(
+    Mid_Chng = ifelse(Begining > 0, Mid_Century/Begining,Mid_Century),
+    End_Chng =ifelse(Begining > 0, The_End_Century/Begining,The_End_Century)
+  ) %>% 
+  mutate_at(vars(Mid_Chng, # Estimate percentage change
+                 End_Chng),
+            funs(ifelse(Begining == 0 & . == 0, 0, # If for no change than 0
+                        ifelse(Begining == 0 & . > 0, 100, # If changes from 0 to anything then 100
+                               round(-(1-.)*100) # Estimate percentage change
+                        )
+            )
+            )
+  )
+
+####Plot Time hisotry o
+
+GFDL_Hist_Out <- Atlantic_DBEM %>% 
+  filter(Model == "GFDL26F1",
+         Species %in% Outlier_Species,
+         INDEX %in% Outliers) %>%
+  tidyr::gather("Year","Change",`2005`:`2099`) %>%
+  # mutate(Change = replace_na(Change, 0)) %>% # Convert NA's into 0's
+  mutate(# Indicate the three period times
+    Period = ifelse(Year >= Beg_In & Year <= Beg_End,"Begining",
+                    ifelse(Year >= Mid_In & Year <= Mid_End,"Mid_Century",
+                           ifelse(Year >= End_In & Year <= End_End,"The_End_Century",
+                                  "Other_Years"))
+    )
+  ) %>% 
+  mutate(Change = replace_na(Change, 0))
+
+ggplot(GFDL_Hist_Out) +
+  geom_line(
+    aes(
+      x = as.numeric(Year),
+      y= Change,
+      color = as.character(INDEX)
+    )
+  ) +
+  facet_wrap(~INDEX)
+
+```
+
 ![Fig 5.
-Percentage change of MCP in the Gulf of Main under, A) low emission scenario; and B) high emission for mid century (2041-2060) relative to present (2005-2014).
-Points represent regions where models do not agree in direction of change.](./Results/Fig5.png)
-
-Despite the expected decrease in MCP for the region, changes in the stock-share ratio of MCP for the Gulf of Maine show different outcomes **RA dependent** on the species in question.
-Following the high emission path will affect mostly Canada’s share of Y.
-flounder and in less degree Haddock, with an increase of Cod share.
-For the low emission scenario, patterns somehow invert with Canada losing a larger share of Haddock versus Y.
-flounder, while increasing Cod’s share (Fig 6).
+Percentage change of MCP in the Gulf of Maine under, A) high emission scenario; and B) low emission for mid century (2041-2060) relative to present (2005-2014).
+Points represent regions where models do not agree in direction of change.](./Figures/Fig5.png)
+
+Despite the expected decrease in MCP for the region, changes in the stock-share ratio of species within the Gulf of Maine show different outcomes **RA dependent** on the climate change scenario and species in question.
+Following a high emission path will affect mostly Canada’s share of Y.
+founder and in less degree haddock, with an increase of cod share.
+**RA under the low emission scenario, haddock and cod patterns intensify, while Y.
+founder’s share approaches almost no change (Fig 6).
+Such pattern is likely the combination of the bathymetry or the Gulf, the warming gradient, and the species distribution (see discussion).**
 
@@
 
-![Fig 6. Changes in MCP stock-share ratio for Gulf of Main under (A) low emission scenario; and (B) high emission for mid century (2041-2060) relative to 2005-2014](./Results/Fig6.png)
+![Fig 6.
+Changes in MCP stock-share ratio for Gulf of Maine under (A) high emission; and (B) low emission scenarios for mid $21^{st}$ century (2041-2060) relative to present.
+Values represent the mean of 3 ESM; error bars represent $\mp$ sd.
+(2005-2014)](./Figures/Fig6.png)
 
@@
 
-The results of the present study suggest that, by 2050, climate change will alter the MCP of 33 transboundary fish stocks in North America consequently altering Canada’s and the US’s species’ stock-share ratio.
-For some species, such changes will intensify under the high emission carbon scenario while for others, the change will be scenario depending.
-These results are aligned with global [@Cheung:2010dt] and regional [@Morley:2018fn] projections suggesting that climate change will push marine species towards the poles and deeper water [@Pinsky:2013jo] in search of their ecological niche [@Poloczanska:2016kk].
-Moreover, poleward shifts in Eastern Atlantic off the coast of the US have been previously recorded for American lobster (*Homarus americanus*), summer (*Paralichthys dentatus*) and yellow flounders, and red hake (*Urophycis chuss*) from North Carolina to Main [@Pinsky:2012kq].
-Our models suggest that shifts will continue towards the end of the 21^st^ century resulting in changes in the proportion of the catch of important shared stocks between Canada and the US.
-As the effects of climate change endure, even with high mitigation, joint plans should prepare to face changes in the stock-share ratio of transboundary stocks along the coast of North America.
-
-Geographic barriers [@Cheung:2015fm], local temperature gradients [@Pinsky:2013jo], species interactions and human activities like fishing [@Serpetti:2017he] might change the rate and direction of species shifts.
+The results of the present study suggest that climate change will alter the MCP of 33 transboundary fish stocks in North America consequently altering Canada’s and the US’s species’ stock-share ratio, regardless of the climate change scenario.
+These results are aligned with regional [@Morley:2018fn] projections suggesting that climate change will push marine species towards the poles and deeper water [@Pinsky:2013jo] in search of their ecological niche [@Poloczanska:2016kk].
+Poleward shifts in Eastern Atlantic off the coast of the US include American lobster (*Homarus americanus*), summer (*Paralichthys dentatus*) and yellow flounders, and red hake (*Urophycis chuss*) from North Carolina to Maine [@Pinsky:2012kq].
+However, geographic barriers [@Cheung:2015fm; @Kleisner:2016je], local temperature gradients [@Pinsky:2013jo], species interactions and human activities [@Serpetti:2017he] might change the rate and direction of species shifts.
 Species such as haddock in the Atlantic [@Morley:2018fn], and big skate (*Raja binoculata*) in the pacific coast [@Pinsky:2013jo] have been projected to shift away from the poles.
-In this manner, the stock-share gain of yellow flounder and haddock by the US in the GoM (Fig.
-5) and the westward increase of stock-share in IPHC regions (Fig.
-4) could be a response to a temperature gradient shift, combined with geographic barriers, rather than latitudinal shifts.
-In recent years, Maine has seen its landings of Y.
-flounder increased at the expenses of southern states like New York [@Pinsky:2012kq].
-Moreover, previous studies have found that under the low emission scenario, haddock is expected to stay at lower latitudes, contrary to what would happen under a high emission scenario [@Morley:2018fn].
-Finally, the Gulf of Main is deeper at southern latitudes, hence, some fish are predicted to move south [@Kleisner:2016je; @Pinsky:2017hr].
-These particular cases could explain the US gain in MCP in the GoM in relation to Canada as species shift their distribution from lower latitudes naturally reaching the US (lower) region first, and towards colder and deeper waters located at southern latitudes of the Gulf.
-At the same time, in the North West Pacific region, species can only migrate northward into the Arctic Ocean through the Bering Sea and Bering Strait [@Cheung:2015fm], potentially pushing pacific halibut west of region 3A.
-This westward displacement could represent a potential loss for both nations as the Gulf of Alaska is historically the most productive region of the fishery [@IPHCSecreatriat:2017uz], and potential international conflict as the stock migrates to the high seas or even reach other westerly countries’ EEZ.
-
-The shifts in the distribution of transboundary **RB stocks** can jeopardize management objectives such as, conservation measures, gear operation, and quota allocations.
-Hypothetically, fish moving out of fishing grounds and into protected areas could result in a pressure increase to open such area to fishing.
-Shifting stocks could also interfere in gear-limitation management rules.
-Bycatch of halibut by other fisheries happen mostly on areas 3A and 4B [@NOAA:JWHvVGvq; @IPHC:2017fs].
-Moreover, in past years, the Alaskan trawl fisheries have been closed before reaching annual quota due to the attainment of halibut bycatch quota limits [@Karim:2010ut].
-Although not assessed in the present study, some trawling target species like Pacific cod (*Gadus macrocephalus*) are expected to move in similar direction than P.
+In the Gulf of Maine, the stock-share gain of Y.
+flounder and haddock by the US (Fig.
+6) could be a response to a temperature gradient shift combined with geographic barriers as southern waters are deeper, and warming slower than northern waters (**Fig A3.1.**).
+In the other hand, Maine has seen its landings of Y.
+founder increased at the expenses of southern states [@Pinsky:2012kq].
+This could be influencing the US gain in MCP in the GoM in relation to Canada as species shift their distribution from lower latitudes naturally reaching the US (lower) region first.
+Geographic barriers also affect the westward increase of stock-share in IPHC regions where species can only migrate northward into the Arctic Ocean through the Bering Sea and Bering Strait [@Cheung:2015fm] (Fig.
+4).
+As the effects of climate change endure, even with high mitigation, joint plans should prepare to face changes in the stock-share ratio of transboundary stocks along both coast of North America.
+
+The shifts in the distribution of transboundary **RB stocks** can jeopardize management objectives such as conservation measures and gear operation.
+Fish moving out of fishing grounds and into protected areas could result in a pressure increase to open such area to fishing.
+Moreover, overlapping shifting stocks could interfere in gear-limitation management rules of multiple fisheries generating conflicts between fleets [@VanDerVoo:2016uc].
+The effectiveness of the IPHC-Closed Area ("CA" in Fig 1.) in tems of protecting juveniles has been historically questioned as trawling for other species is still allowed in the area [@Karim:2010ut; @IPHC:2017CA].
+In 2015, for example, 97% of the trawl by-catch in areas 4CDE and the Closed Area were juveniles [@IPHC:2017CA].
+Consequently, the Alaskan trawl fisheries has been closed before reaching annual quota due to the attainment of P.
+halibut bycatch quota limits [@Karim:2010ut].
+Thus the comission has been asked to open the closed area for P.
+halibut fishing, under the premise that the expansion of the trawl fishery is likely reducing any conservation goal for juvenile P.
+halibut [@IPHC:2017CA].
+Although not assessed  in this study, some trawling target species like Pacific cod (*Gadus macrocephalus*), flathead sole (*Hippoglossoides elassodon*), and Alaskan plaice (*Limanda aspera*) have already shift their distributions due to warming waters [@Stram:2009xc] and some are expected to continue shifting in similar direction than P.
 halibut [@Pinsky:2013jo].
-Conflicts between fleets already exists and could be extrapolated if the situation is not foreseen [@VanDerVoo:2016uc].
 The overlap of target species could be addressed by applying ecosystem-based management and dynamic management tools [@Hazen:2018fa] to manage these fisheries and reduce potential lost of sustainable harvest for both the halibut and the trawl fisheries.
 
-Quota allocation ruled by historic distributions will most likeley be outdated.
-Changes in the proportion of the quota have created tension between countries [@Spijkers:2017ij] including Canada and the US in the case of the Pacific salmon [@Miller:2013iv; @Munro:2002uf; @Song:2017va].
-Poleward shifts along the coast of Oregon, Washington and British Columbia (Canada) were first addressed by the IPHC in 1985 (@McCaughran:1992uw).
-Changes in the distribution of the stock resulted in an adjustment in the quota allocation method, from a fixed quota allocation to a dynamic one.
-As climate change continues, these shifts are not expected to stop, and treaties should be flexible enough to cope with the pace and magnitude of change in order to achieve sustainable harvest under a changing climate.
+Quota allocation ruled by historic distributions will most likely be outdated incentivizing maladaptation [@FAO:2018uv; @Gaines:2018sg; @Miller:2013iv].
+In Europe, for example, the EU Common Fisheries Policy quota allocation is based on historic reference period of 1973-1978 [@Harte:2019us].
+However, climate change has shifted the distribution of multiple European commercial stocks [@Baudron:2020dj], outdating the fixed quotas and thus compromising the sustainability of European fisheries [@FAO:2018uv; @Baudron:2020dj].
+Management regimes that inclued a dynamic harvest control (e.g.
+adjusting the quota based on the stocks distribution) have the potential of increasing fish biomass, harvest and profits under climate change [@Gaines:2018sg].
+In North America, poleward shifts of P.
+halibut along the coast of Oregon, Washington and British Columbia have been previouslly addressed by the IPHC resulting in the adoption of a dynamic quota allocation method [@McCaughran:1992uw].
+By allocating quotas based on yearly surveys along the Convention area, the IPHC should be able to capture shifts in P.
+halibut distribution due to climate change, reducing the chances of overexploitation of the stock due to this shifts [@Miller:2013iv].
+Similarly, since 2010 GoMA sets weighted quotas based on stocks distribution and historical catch [@TRAC:2016wu].
+This process is especially important for cod and haddock due to their distribution variation within the gulf [@Soboil:2006gw; @TRAC:2016wu].
 
 Side payments have been previously used to address changes in species distribution due to environmental forcings.
-In game theory, a side payment is received by a player as a compensation from the other player, with the idea that keeping cooperation is still better than playing solo [@Bjorndal:2012vd; @Sumaila:2013hv].
+In game theory, a side payment is received by a player as a compensation from the other player in a shared ressource agreement, with the premise that cooperation will result in a better overall outcome [@Bjorndal:2012vd; @Sumaila:2013hv].
 Side payments do not have to be in monetary form and are widely used in transboundary **RB stocks** around the world.
 For example, Norway and Russia have implemented a quota swap strategy for jointly managed stocks of cod, haddock and capelin in the Barents Sea [^NR].
-The adaptation of a similar agreement could help the management of fisheries in the Gulf of Main.
-Another example is the Nauru Agreement (PNA), responsible for managing the world's largest sustainable skipjack tuna (*Katsuwonus pelamis*) purse seine fishery [^PNA].
-The PNA has a system of internationally tradable fisheries access that allows members to adapt to the effects of the El Niño Southern Oscillation [@Aqorau:2018bh].
-While this is a good way to address climate variation within members of a treaty, it might fall short to address the newcomer issue, a situation that can threaten the sustainability of the stock [@Pinsky:2018cb].
-A combination of the methods employed by PNA with the proper modification to incorporate new fishing nations could help mitigate future conflicts in **RB stocks** like the Pacific halibut.
-Finally, It has been suggested that agreements that make cooperation the preferred strategy for all players are stronger.
-However, the level of government at which negotiations are held can directly impact management outcomes, as low-level agreements might lack proper penalties for non-cooperative behavior [@Miller:2013iv].
-Officializing treaties like the case of the Gulf of Maine could provide better ground for the management rules and increase treaty resilience.
+Similarly, species' quota swaps are permited, up to a degree, within regulatory areas of the European union [@Baudron:2020dj].
+Specifically, for northern European spring spawning Herring (*Clupea harengus*), Norway, Iceland, Faroe Islands, Russia and the EU reached an agreement to manage the stock after its collapsed, partially due to climate variations [@Miller:2013iv].
+Among the implemented rules, the agreement sets a dynamic quota allocation, allows memebers to fish part of their quota within Norway's EEZ, and land the catch in Norwegian ports.
+In North America, Canada and the US have previous history with the utilization of side payments when in the 70's Pacific Salmon shifted its distribution resulting in large interceptions of Canada's salmon by Alaskan fisheries [@Miller:2013iv].
+The conflict was resolved by the implementation of a conservation fund that work as a side payment for both Canada and the state of Alaska [@Miller:2013iv].
+The potential adaptation of side payments in terms of quota swaps or allowing free quota fishing within across the Gulf of Maine EEZs could be a potential solution as stocks shift due to climate change.
 
 [^NR]: Joint Fish, joint Russian-Norwegian Fisheries Comission available at http://www.jointfish.com/eng/THE-FISHERIES-COMMISSION/HISTORY.html
-[^PNA]: The Parties to the Nauru Agreement (PNA), available at http://www.pnatuna.com/
-
-<!-- ## Uncertanty stuff -->
-
-In the current paper we follow a modeling approach to explore the potential impacts that climate change will have in the management of transboundary **RB stocks** in North America.
+
+Transboundary fisheries management have to be prepared for the uncertanty that comes with a changing world.
+Future climate change will depend on the path society as a whole will take, and thus we rely on scenario planning to account for the uncertainty build in future decision making [@vanVuuren:2011ef].
+In our results, the "winners and loosers" of climate change, and the intensity of the change, will be scenario dependant.
+For instance, stock-share of Y.
+flounder under a high emission scenario will be larger for the US while Canada's gain of haddock stock-share will be larger under a low emission scenario (Fig.
+6).
+Applying previouslly describe strategies (e.g.
+quota swaps or EEZ-fishing rights) could increase the resilience of treaties by preventing members from leaving the agreement due to a shift in threat points, as happened in the P.
+salmon case [@Miller:2013iv].
+
 Models are attempts to represent reality (in our case a future reality) based on observational data, previously established theory, and future scenarios, and are thus, subjected to different degrees of uncertainty [@Payne:2016gn].
-First, our study incorporates multiple earth system models to project the future distribution of transboundary stocks while accounting the structural uncertainty built within each ESM [@Bopp:2013fg].
-In terms of the structural uncertainty build within the DBEM, previous analysis shown that the trends of changes in MCP are not affected by its structural uncertainty [@Cheung:2016jd].
-Secondly, scenario planning has been widely used in climate change studies as a method to account for the uncertainty build in future decision making [@vanVuuren:2011ef].
-In this aspect we considered two extreme RCPs that comprises the vast spectrum of possibilities proposed by the IPCC [@IPCC:2014bz].
-A lower-than-2.6 RCP (1.5º warming) was discussed at the recent Paris Agreement sessions celebrated in Paris France.
-While we did not include this scenario in our analysis, previous research suggest that stronger mitigation efforts would bring large benefits to fisheries [@Cheung:2016tt].
-Finally, future changes to species distributions could be influenced by interactions between species [@Pecl:2017hu], adaptation of species to environmental changes, and anthropogenic factors [@Serpetti:2017he].
-However, these factors are expected to increase the rate of range-shifting of the species making our results conservative [@Cheung:2010dt; @Serpetti:2017he].
-
-<!-- Discussion on improoving management  -->
-<!-- From global (Cheung et al.
-2016c) to regional (Morley et al.
-2018) analysis, mitigating the effects of climate change will have positive results on fisheries (Sumaila 2019).
-In combination with improving management [Costello], fisheries will only be saved by a holistic approach… Indeed, dynamic management tools seem to work better than static strategies for resources expected to shift with changes in ocean condition (Pinsky and Selden 2017).
--->
+An ensamble or models is a way to present a more robust result that accounts for differnces in the structural composition of each model [@Cheung:2016gv].
+In here we used three ESMs to project future changes in species maximum catch potential.
+The levels of uncertainty related to the ESMs differ among case studies.
+Overall, results for the Gulf of Maine agree with a reduction in MCP of all three species.
+However, some discrete areas show a positive change for Y.
+flounder by mid $21^{st}$ century (Fig.
+4), mainly driven by the GFDL model (**Fig A3.2**).
+Potential model artifacts could also be contributing to the results, especially in the northern part of the study area (Bay of Fundy) as most disagreeing grids are covered by land, which could be influencing the results.
+In contrast, considerable uncertainty exists in the change of MCP along the IPHC Convention area shown by a disagreement between ESMs (**Fig A3.2**).
+Off the coast of British Columbia, increasing temperature trends are consistant among ESMs, however, other processes such as acidification and deoxygenation are still not well understood from British Columbia to the Gulf of Alaska [@TalloniAlvarez:2019gz].
+Moreover, considerable uncertainty exists along the Berring Sea [@Douglas:2010Mb] and Antartic Pacific regarding the extent and intensity of future sea-ice reduction under climate change [@Steiner:2015hc; @IPCC:2019to].
+**RA Structural uncertainty within the DBEM has been previously tested for agreement against commonly used species distribution algorithms such as Maxent [@Phillips:2006ff] and AquaMaps [@Kaschner:2011hi; @Ready:2010wr] resulting in no qualitative differences in trends between algorithms [@Cheung:2016jd].
+Is worth mentioning that future changes to species distributions could be influenced by factors not captured by our model such as interactions between species [@Pecl:2017hu], adaptation of species to environmental changes, and anthropogenic factors [@Serpetti:2017he].
+However, these factors are expected to increase the rate of range-shifting of the species making our results conservative [@Cheung:2010dt; @Serpetti:2017he].**
 
@@
 In this paper, we have explored the potential impacts of climate change in the joint management of 33 transboundary stocks managed by Canada and the US.
-We found that, transboundary **RB stocks** are likely to shift north in the upcoming years changing the proportion of the catch of jointly managed fisheries of Canada and the US.
+We found that, transboundary **RB stocks** are likely to shift in the upcoming years changing the proportion of the catch of jointly managed fisheries of Canada and the US.
 Lessons from other countries can provide solutions to such challenges.
@@
 Addressing shifts in **RB stocks** distribution sooner rather than latter could avert the so called "fish wars", improve sustainability of jointly managed stocks, and secure the livelihood of thousand of families that depend on stocks that move freely between national jurisdictions.
+Finaly, preparing for an uncertain future is key to achieve sustainable fisheries.
 
@@
 
-We ack
+This is a product of the *OceanCanada* Partnership funded by the Social Sciences and Humanities Research Council of Canada.
 
@@
 
-# OLD ANALYSIS
-
-```{r Old analysis, eval = F}
+<!-- # OLD ANALYSIS -->
+
+```{r Old analysis, eval = F, echo = F}
 
@@
 
-# OLD TEXT
-
-Transboundary fisheries are defined as **RB those fishing** stocks that move freely between (*i*) Countries economic exclusive zones (EEZs) and (*ii*) between EEZs and the high seas (**RB called transboundary stocks**) [@Song:2017iua].
+<!-- # OLD TEXT -->
+
+ <!-- As climate change alters the sharing of fish stocks between countries to an extent that is beyond historical changes, existing policies and governance structures may not be able to cope with these changes [@Pinsky:2012kq].
+Consequently, countries may not be satisfied with the sharing or allocation of access to resources, leading to international disputes [@Pinsky:2018cb].
+-->
+
+<!-- It has been suggested that agreements that make cooperation the preferred strategy for all players are stronger.
+However, the level of government at which negotiations are held can directly impact management outcomes, as unofficial agreements might lack proper penalties for non-cooperative behavior [@Miller:2013iv].
+**In this sence the GoM agreement covers itself quite well**.
+In one hand, the informal quota allocation method has managed to ease tensions between neighbouring countries, implement a share allocation that addresses shifts in species distributions.
+While in the other hand, the oficial enforcement agreement signed by the goverments of Canada and the US [@GovermentofCanada:l5W8_7Lz] has helped reduce illegal fishing in the border [@Pudden:2007bo].
+However, despite the quota suggestions under the GoM agreement are done internationally, Canada and the US ultimately set the quota domestically [@Pudden:2007bo].
+In this sence, the agreement might not be resilient to climate-induced shifts members are not binded to any rule.
+Officializing treaties like the case of the Gulf of Maine could provide better ground for the management rules and increase treaty resilience and capacity to adapt to unpredicted changes [@Miller:2013iv].
+Changes in the distribution of shared stocks have created tension between countries [@Spijkers:2017ij] including Canada and the US in the case of the Pacific salmon [@Miller:2013iv; @Munro:2002uf; @Song:2017va].
+-->
+
+<!-- On the Atlantic coast, Canada and the US are parties to Northwest Atlantic Fisheries Organization (NAFO), which oversees the management of 19 stocks of 11 species, some of which traverse Canada’s EEZ and the Regulatory Area outside the EEZ (although around 41 taxa are fished within Canadian and U.S.
+waters from the southern Gulf of Maine to Greenland) [^NAFO].
+On the Pacific coast, Pacific halibut (*Hippoglossus stenolepis*) is managed under the International Pacific Halibut Commission (IPHC) [@IPHCSecreatriat:2017uz].
+All five salmon species (chinook, *Oncorhynchus tshawytscha*; chum, *O.
+keta*; coho, *O.
+kisutch*; pink, *O.
+gorbuscha*; and sockeye *O.
+nerka*), are managed by the Pacific Salmon Commission [@PSC:2017tb].
+Finally, under the Pacific Whiting Treaty, Canada and the United states jointly manage the coastal stock of this Pacific hake species (*Merluccius productus*) [@Merten:2015tu].
+-->
+
+ <!-- Disputes over Pacific salmon between Canada and the US arose in the 1990s because of climate-related changes in stock abundance and migratory behavior [@Miller:2013iv; @Munro:2002uf; @Song:2017va].
+Currently, Europe is involved in an unsolved dispute over *Scomber scombrus* known as the "mackerel wars".
+The conflict erupted in 2007 when the stock shifted their distribution from the Norwegian Sea towards northern and western regions of the Nordic Seas, consequently spreading into Iceland's national waters [@Spijkers:2017ij].
+-->
+
+<!-- Transboundary fisheries are defined as **RB those fishing** stocks that move freely between (*i*) Countries economic exclusive zones (EEZs) and (*ii*) between EEZs and the high seas (**RB called transboundary stocks**) [@Song:2017iua].
 **RA Game theory is one of the most common approaches used to analyze the management of transboundary stocks, as often, success depends on effective cooperation between parties** [@Munro:2002uf; @Sumaila:2013hv].
 Therefore, in **DV 1982**, the United Nations incentivized actions to cooperate on the management of transboundary **RB stocks** through the Law of the Seas (UNCLOS) [@UnitedNations:1986tl].
-
-While in 2050, the average shift of species will be higher for East Canada and lower for East US under the high emission scenario, the stock-share ratio of some species is expected to increase more than 50% as in the case of Atlantic menhaden (*Brevoortia tyrannus*) in Eastern Canada, and decrease by more than 50% for species such as Cusk (*Brosme brosme*) in the Eastern US under a low emission scenario.
-By the end of the 21^st^ century, losses will intensify with the eastern US potentially losing on average 15.2% or 46% of stock-share, depending on the scenario.
+-->
+
+<!-- While in 2050, the average shift of species will be higher for East Canada and lower for East US under the high emission scenario, the stock-share ratio of some species is expected to increase more than 50% as in the case of Atlantic menhaden (*Brevoortia tyrannus*) in Eastern Canada, and decrease by more than 50% for species such as Cusk (*Brosme brosme*) in the Eastern US under a low emission scenario.
+By the end of the $21^{st}$ century, losses will intensify with the eastern US potentially losing on average 15.2% or 46% of stock-share, depending on the scenario.
+-->
+
+<!-- Another example is the Nauru Agreement (PNA), responsible for managing the world's largest sustainable skipjack tuna (*Katsuwonus pelamis*) purse seine fishery [^PNA].
+The PNA has a system of internationally tradable fisheries access that allows members to adapt to the effects of the El Niño Southern Oscillation [@Aqorau:2018bh].
+While this is a good way to address climate variation within members of a treaty, it might fall short to address the newcomer issue, a situation that can threaten the sustainability of the stock [@Pinsky:2018cb].
+A combination of the methods employed by PNA with the proper modification to incorporate new fishing nations could help mitigate future conflicts in **RB stocks** like the Pacific halibut.
+Finally,  -->
+<!-- [^PNA]: The Parties to the Nauru Agreement (PNA), available at http://www.pnatuna.com/ -->
+
+<!-- In the current paper we follow a modeling approach to explore the potential impacts that climate change will have in the management of transboundary **RB stocks** in North America.
+Models are attempts to represent reality (in our case a future reality) based on observational data, previously established theory, and future scenarios, and are thus, subjected to different degrees of uncertainty [@Payne:2016gn].
+First, our study incorporates multiple earth system models to project the future distribution of transboundary stocks while accounting the structural uncertainty built within each ESM [@Bopp:2013fg].
+In terms of the structural uncertainty build within the DBEM, previous analysis shown that the trends of changes in MCP are not affected by its structural uncertainty [@Cheung:2016jd].
+Secondly, scenario planning has been widely used in climate change studies as a method to account for the uncertainty build in future decision making [@vanVuuren:2011ef].
+In this aspect we considered two extreme RCPs that comprises the vast spectrum of possibilities proposed by the IPCC [@IPCC:2014bz].
+A lower-than-2.6 RCP (1.5º warming) was discussed at the recent Paris Agreement sessions celebrated in Paris France.
+While we did not include this scenario in our analysis, previous research suggest that stronger mitigation efforts would bring large benefits to fisheries [@Cheung:2016tt].
+Finally, future changes to species distributions could be influenced by interactions between species [@Pecl:2017hu], adaptation of species to environmental changes, and anthropogenic factors [@Serpetti:2017he].
+However, these factors are expected to increase the rate of range-shifting of the species making our results conservative [@Cheung:2010dt; @Serpetti:2017he].
+-->

### 2020-03-04 Ecology/Manuscript_Draft.Rmd
Re-organized repository

--- 2020-03-04 Manuscript_Draft.Rmd
@@
   pdf_document: default
-bibliography: References/Oceans_Canada_Bibliob.bib
+bibliography: References/Oceans_Canada_Biblio.bib
 editor_options: 

### 2020-03-04 Econ/Econ_Analysis.Rmd
Re-organized repository

--- 2019-09-14 Econ_Analysis/Econ_Analysis.Rmd
@@
 
-EEZIDs_List <- read_excel("~/Documents/UBC/Oceans_Project/Distribution/By Cell/Cell_Data/Updated_EEZList_17June2016.xlsx")
-
-EEZ_CellID <- read_excel("~/Documents/UBC/Oceans_Project/Distribution/By Cell/Cell_Data/EEZ_CellID.xlsx")
-
+EEZIDs_List <- read_excel("./Econ/Data/Spatial/Updated_EEZList_17June2016.xlsx")
+EEZ_CellID <- read_excel("./Econ/Data/Spatial/EEZ_CellID.xlsx")
 colnames(EEZ_CellID) <- c("EEZID","INDEX")
@@
 # DBEM Coordinate system
-Coor <- fread("~/Documents/UBC/Oceans_Project/Distribution/DBEM/Data/Lon_Lat_DBEM.txt",header = FALSE)
+Coor <- fread("./Econ/Data/Spatial/Lon_Lat_DBEM.txt",header = FALSE)
 colnames(Coor) <- c("INDEX","Longitude","Latitude")
@@
 # From (/Users/jpalacios/Documents/UBC/Oceans_Project/Distribution/By Cell/By_Cell_Analysis.Rmd)
-Raw_DBEM_Results <- data.table::fread("~/Documents/UBC/Oceans_Project/Manuscript/Data/Raw_Data.csv") %>% 
+Raw_DBEM_Results <- data.table::fread("./Ecol/Data/Distribution/Raw_Data.csv") %>% 
   filter(Species != "Anoplopoma fimbria") #Remove
@@
 # Data in metric tonne
-IPHC_Landings <- read_excel("~/Documents/UBC/Oceans_Project/Econ/Data/IPHC/iphc-19912017-commres.xlsx", 
+IPHC_Landings <- read_excel("./Econ/Data/IPHC/iphc-19912017-commres.xlsx", 
                                     col_types = c("numeric", "text", "text", 
@@
 # 
-GoM_Landings <- read.csv("~/Documents/UBC/Oceans_Project/Econ/Data/SAU_Landings/GoM/SAU MEOW 55 v47-1.csv")
+GoM_Landings <- read.csv("./Econ/Data/SAU_Landings/GoM/SAU MEOW 55 v47-1.csv")
 
@@
 
-Fishing_Cost <- read_excel("~/Documents/UBC/Oceans_Project/Econ/Data/Economic/FishingCost_USA_Canada_20Feb2017.xlsx", 
+Fishing_Cost <- read_excel("./Econ/Data/Economic/FishingCost_USA_Canada_20Feb2017.xlsx", 
                            col_types = c("text", "text", "text", 
@@
 
-Ex_Vessel <- read.delim("~/Documents/UBC/Oceans_Project/Econ/Data/Economic/Price_US_Canada_5spp.csv")
+Ex_Vessel <- read.delim("./Econ/Data/Economic/Price_US_Canada_5spp.csv")
 
@@
 Profit_Data_Paper <- Profit_Data_Weight %>% 
-  mutate_at(vars(Cost_perTon_2010,Price_perTon,Profit_perTon),
+  mutate_at(vars(Cost_perTon_2010,Price_perTon,Profit_perTon), # note these are totals and not per tone
             funs(round((.*Avrg_Landings)/1000000,2)) # million USD
@@
   )
+
+### Alternative landed values
+
+# Canada Flounder 134 tonnes for $81,093 = $/t 605
+
+# Canada Cod 5,982 tonnes for $7,007,566	= $/t 1171.442
 
@@
 
+# Figure 1
+
 # Plot for now (see next chunk for more options)
@@
        path = "./Results")
+
+# Figure 2 / Table 2
+
+# Plot for now (see next chunk for more options)
+pd<-position_dodge(0.05)
+
+ggplot() +
+  geom_line(data = Average_Prop_Plot,
+            aes(
+              x=Time_Sector,
+              y=Discounted_Profits_mean, # Percentage
+              colour=EEZ
+            )
+  ) +
+  geom_errorbar(data = Average_Prop_Plot,
+                aes(
+                  x=Time_Sector,
+                  ymin=(Discounted_Profits_mean-Discounted_Profits_sd), # mean +- 2*sd
+                  ymax=(Discounted_Profits_mean+Discounted_Profits_sd),
+                  colour=EEZ
+                ),
+                # alpha=0.5,
+                width=.1,
+                # position=position_dodge(0.05),
+                size = 0.6
+  ) +
+  geom_line(data = Average_Prop_Plot,
+            aes(
+              x=Time_Sector,
+              y=Non_Discounted_Profits_mean, # Percentage
+              colour=EEZ
+            ),
+            alpha = 0.5,
+            linetype = "dashed"
+  ) +
+  geom_errorbar(data = Average_Prop_Plot,
+                aes(
+                  x=Time_Sector,
+                  ymin=(Non_Discounted_Profits_mean-Non_Discounted_Profits_sd), # mean +- 2*sd
+                  ymax=(Non_Discounted_Profits_mean+Non_Discounted_Profits_sd),
+                  colour=EEZ
+                ),
+                alpha=0.5,
+                width=.1,
+                # position=position_dodge(0.05),
+                size = 0.6,
+                linetype = "dashed"
+  ) +
+  scale_fill_manual(values = wes_palette("IsleofDogs1")) +
+  scale_colour_manual(values = wes_palette("IsleofDogs1")) +
+  scale_x_continuous(breaks=c(1, 2, 3),
+                     labels=c("Present-day", "Mid-century", "End-century")) +
+  # ylim(0,100)+
+  facet_grid(Species ~ RCP,
+             labeller = labeller(Species = Common_Names),
+             scales = "free"
+  ) +
+  labs(
+    x = "",
+    y = "Profits"
+  ) +
+  theme(
+    axis.text.x = element_text(size = 12),
+    axis.text.y = element_text(size = 12),
+    axis.title = element_text(size = 18),
+    legend.title = element_text(size = 18),
+    legend.text = element_text(size = 12),
+    strip.text = element_text(size = 16),
+    panel.spacing.x = unit(3.5, "lines")
+  )
+
+# Save plot 
+ggsave("Econ_Plot_2.tiff",
+       plot = last_plot(),
+       width = 10,
+       height = 8,
+       units = "in",
+       path = "./Econ/Results")
+
 ```

### 2020-04-28 Ecol/Manuscript_Draft.Rmd
Updated Ecol after reviewers

--- 2020-03-04 Ecology/Manuscript_Draft.Rmd
@@
  pdf_document: default
-bibliography: References/Oceans_Canada_Biblio.bib
+bibliography: ../References/Oceans_Canada_Biblio.bib
 editor_options: 
  chunk_output_type: console
-csl: References/harvard.csl
+csl: ../References/E&S.csl
 ---
 
-```{r setup, eval=T, echo=F, warning=F,message=F, results='hide'}
+```{r setup_oc, eval = T, echo = F, warning = F, message = F, results = 'hide'}
 
@@
 
-# Abstract
+## Abstract
 
 Climate change is shifting the distribution of fish stocks that straddle between Exclusive Economic Zones (EEZ), challenging transboundary fisheries management.
-In this paper, we examine the projected sharing of jointly managed transboundary fish stocks between the EEZs of Canada and the United States.
-We hypothesize that ocean warming will alter the sharing of fish stocks between the two countries, and that such changes will intensify under a high carbon emission scenario impacting the stock-share ratio of different stocks.
+Here, we examine the projected sharing of jointly managed transboundary fish stocks between Canada and the United States.
+We hypothesize that ocean warming will alter the sharing of fish stocks between the two countries, and that such changes will intensify under a high carbon emission scenario.
 Firstly, we projected changes in potential catch of 33 transboundary stocks of North America in the $21^{st}$ century based on multiple Earth system models’ simulations and species distribution models, under two climate change scenarios.
-We then look at the specific cases of the International Pacific Halibut Commission that manages pacific halibut (*Hippoglossus stenolepis*) and a resource sharing **DV arrangement** in the Gulf of Maine for cod (*Gadus morhua*), haddock (*Melanogrammus aeglefinus*) and yellowtail flounder (*Limanda ferruginea*) **RA to discuss the management consequences of shifts in transboundary stocks**.
+We then look at the specific cases of the International Pacific Halibut Commission that manages pacific halibut (*Hippoglossus stenolepis*) and a resource sharing arrangement in the Gulf of Maine for cod (*Gadus morhua*), haddock (*Melanogrammus aeglefinus*) and yellowtail flounder (*Limanda ferruginea*) to discuss the management consequences of shifts in transboundary stocks.
 Results show that, even under a low emission scenario, most transboundary fish stocks sharing ratios, i.e., the proportion of the total catch of a fish stock taken by a given country, will change by 2050 relative to present in the direction as expected from the effects of ocean warming.
@@
 Such trade-offs in the Atlantic and Pacific regions will be amplified if a high emission scenario is followed, relative to a low carbon emission scenario.
-Our paper highlights the challenges that transboundary fisheries management will face as species shift their current distribution under a changing climate.
+Based on the simulation results, we examine possible solution options to reduce climate risks on transboundary fish stocks and fisheries.
 
@@
 
-# INTRODUCTION
+## INTRODUCTION
 
 <!-- ##### First paragraph of paper summary -->
-**RA In 1982, the United Nations Law of the Seas (UNCLOS) formalized the concept of economic exclusive zones (EEZs) creating what we know today as sahred stocks [@UnitedNations:1986tl].
-Shared stocks can move freely between countries EEZs (known as transboundary stocks) or between EEZs and the high seas (also called straddling stocks) [@Song:2017iua].** Today, an estimated 347 [@Teh:2015gd] to 1500 [@Caddy:1997ue] fish stocks cross national borders, some of them jointly managed by two or more countries.
+In 1982, the United Nations Law of the Seas (UNCLOS) formalized the concept of economic exclusive zones (EEZs) creating what we know today as shared stocks [@UnitedNations:1986tl], i.e.
+stocks migrate freely between countries EEZs (known as transboundary stocks) or between EEZs and the high seas (also called straddling stocks) [@Song:2017iua].
+Today, an estimated 347 [@Teh:2015gd] to 1500 [@Caddy:1997ue] fish stocks cross national borders, some of them jointly managed by two or more countries.
 These stocks are responsible for almost 50% of these countries total fish catches [@Teh:2015gd].
-**RA While not a law, UNCLOS incentivizes actions to cooperate on the management of shared stocks [@UnitedNations:1986tl].
-Today, game theory is one of the most common approaches used to analyze the management of shared stocks, as often, success depends on effective cooperation between parties [@Munro:2002uf; @Sumaila:2013hv].** Management of these stocks' **RA can be convoluted** due to the participation of several fishing “players”, different countries and sometimes jurisdictions within a country, the migration patterns of the stock, and their abundance fluctuation within space and time [@Munro:2002uf].
-In addition, international treaties might not be prepared to address the effects that climate change will bring to shared fish stocks (**Koubrak and VanderZwaag, this Special Feature**), .
+While not a law, UNCLOS incentivizes actions to cooperate on the management of shared stocks [@UnitedNations:1986tl].
+Game theory is one of the most common approaches used to analyze the management of shared stocks, as often, success depends on effective cooperation between parties [@Munro:2002uf; @Sumaila:2013hv].
+Management of these stocks' can be convoluted due to the participation of several fishing “players”, different countries and sometimes jurisdictions within a country, the migration patterns of the stock, and their abundance fluctuation within space and time [@Munro:2002uf], Engler and Saunders this Special Feature).
+In addition, international treaties might not be prepared to address the effects that climate change will bring to shared fish stocks (Engler and Saunders this Special Feature, Koubrak and VanderZwaag, this Special Feature).
 
@@
 
-The ocean is getting warmer [@Rheim:2013fv], less oxygenated [@Schmidtko:2017cl], and increasing in acidity [@Ross:2011kd].
+The ocean is getting warmer [@Rheim:2013fv], less oxygenated [@Schmidtko:2017cl], and increasing in acidity [@Ross:2011kd; @IPCC:2019to].
 To cope with these changes in ocean biophysic properties, marine species, including shared fish stocks, have been shifting their distribution towards the poles and/or deeper waters [@Poloczanska:2016kk].
@@
 Moreover, these shifts are projected to continue towards the end of the $21^{st}$ century [@Cheung:2018hz].
-As a result, some countries or management jurisdictions may see more shared **RA fisheries** and their catches shifting into their waters while others will stand to lose [@Miller:2013iv; @Pinsky:2018cb].
+As a result, some countries or management jurisdictions may see more shared fisheries and their catches shifting into their waters while others will stand to lose [@Miller:2013iv; @Pinsky:2018cb].
 Nevertheless, management rules for shared stocks (e.g.
@@
 
-The shifts in distribution of shared fish stocks will impact the economics of their fisheries [@Pinsky:2012kq; @Sumaila:2019gh]**Sumaila et al., This Volume**), and create international disputes between countries [@Munro:2002uf; @Spijkers:2017ij;@Pinsky:2018cb].
+The shifts in distribution of shared fish stocks will impact the economics of their fisheries [@Pinsky:2012kq; @Sumaila:2019gh]Sumaila et al., this Special Feature), and create international disputes between countries [@Munro:2002uf; @Spijkers:2017ij;@Pinsky:2018cb].
 Canada and the US share important transboundary stocks of salmon (*Oncorhynchus spp.*), Pacific halibut (*Hippoglossus stenolepis*), and Atlantic cod (*Gadus morhua*) offering a unique lens to understand the extent to which climate-induced distributional shifts will challenge the future sustainability of transboundary fisheries.
@@
 
-[^NAFO]: Northwest Atlantic Fisheries Organization, Available at https://www.nafo.int/Science/Species
-
-It is expected that climate induced shifts in stocks' distribution **RA will** affect the rules in place that **RA keep** international treaties alive.
+It is expected that climate induced shifts in stocks' distribution will affect the rules in place that keep international treaties alive.
 Therefore, the main objective of this article is to assess the level of exposure that bi-lateral transboundary fisheries treaties between Canada and the US have to climate change through shifts in stock distributions.
 Specifically, we rely on a species distribution model and scenario planning to project the changes in the distribution of 33 fish stocks jointly managed by Canada and the US.
-Moreover, we use two specific case studies (the International Pacific Halibut Comission -IPHC- and a **DV fisheries arrangement** for the Gulf of Maine -GoMA-) to explore the potential impacts that climate change will have on selected transboundary **RB stocks** management.
-Finally, we explore similar situations around the world and identify opportunities to improve the adaptability of transboundary **RB stocks** management to climate change in North America.
-Despite an overall expectation of species following a poleward shift, **RA important geographic constraints (e.g.
+Moreover, we use two specific case studies (the International Pacific Halibut Commission -IPHC- and a fisheries arrangement for the Gulf of Maine -GoMA-) to explore the potential impacts that climate change will have on selected transboundary stocks management.
+Finally, we explore similar situations around the world and identify opportunities to improve the adaptability of transboundary stocks management to climate change in North America.
+Despite an overall expectation of species following a poleward shift, important geographic constraints (e.g.
 Gulf of Alaska representing a latitudinal block) [@Kleisner:2016je], geo-political features (e.g.
-the localization of Alaska in reference to Canada and the contiguous states)**, and management rules (e.g.
+the localization of Alaska in reference to Canada and the contiguous states), and management rules (e.g.
 quota allocations, spatial management rules) may play an important role in the redistribution of benefits.
@@
 
-# METHODS
-
-#### Study Area and Fisheries
-
-The current study focuses on 33 transboundary **RB stocks** jointly managed by Canada and the US for both the Atlantic and the Pacific coasts.
+## METHODS
+
+### Study Area and Fisheries
+
+The current study focuses on 33 transboundary stocks jointly managed by Canada and the US for both the Atlantic and the Pacific coasts.
 The analysis was carried out within the 200 nautical miles of both nation's EEZ from the Gulf of Mexico to The Labrador Sea in the Atlantic, and from California to Chukchi Sea, in the Pacific coast.
-The species analyzed (**Table A2.1**) were selected based on five treaties in both the Atlantic and Pacific coast of North America (Table 1).
+The species analyzed (Table A2.1) were selected based on five treaties in both the Atlantic and Pacific coast of North America (Table 1).
 All species under the IPHC, Pacific Salmon Comission, the Pacific Whiting Treaty, and the GoMA arrangement were analyzed as these are bi-lateral agreements.
-However, in the case of NAFO, a subset of 26 species reported was made based on those fished in regions that fall within the EEZs of Canada and the United States (NAFO subareas 2s, 3s with the exception of 3M and 3N and limited to the EEZ, 4s, 5s and 6 A,B, and C) (NAFO n.d.).
+However, in the case of Northwest Atlantic Fisheries Organization (NAFO), a subset of 26 species reported was made based on those fished in regions that fall within the EEZs of Canada and the United States (NAFO subareas 2s, 3s with the exception of 3M and 3N and limited to the EEZ, 4s, 5s and 6 A,B, and C) [^NAFO].
 Data related to fisheries was gathered from the Sea Around Us from 1951 to 2014 [@Zeller2016].
 
-```{r Treaties_Table, eval = T, echo = F}
+[^NAFO]: Northwest Atlantic Fisheries Organization, Available at https://www.nafo.int/Science/Species
+
+```{r Treaties_Table, eval = F, echo = F}
 
 # Foot note
-fn <- "*These species are also part of NAFO. **This is an arrangement and not an official agreement between parties."
+fn <- "*These species are also part of NAFO. This is an arrangement and not an official agreement between parties."
 
@@
               "Northwest Atlantic Fisheries Organization (NAFO)",
-                           "Gulf of Main's Arrangement (GoM Arrangement**)"),
+              "Gulf of Main's Arrangement (GoM Arrangement)"),
             Species =
@@
 
-We used the IPHC and the Gulf of Maine arrangement (hereafter refered as GoMA) as case studies to discuss the implications that climate chage could have in the management of transboundary stocks.
+We used the IPHC and the Gulf of Maine arrangement (hereafter referred as GoMA) as case studies to discuss the implications that climate change could have in the management of transboundary stocks.
 For the IPHC, we used the most updated spatial regulatory data along its 12 regulatory areas [@IPHCSecreatriat:2017uz; @IPHC:2019wt].
@@
 
-##### The International Pacific Halibut Comission
+### The International Pacific Halibut Comission
 
 The IPHC was established by Canada and the United States to oversee the management of Pacific halibut (*Hippoglossus stenolepis*) [@IPHC:2014tz].
-There are 12 regulatory areas from wich 3AB holds 51.2% of the stock, followed by regions 2ABC and 4ACDE with 23.1% and 20.4%, respectively, and lastly region 4B with only 5.2% of the stock distribution [@IPHC:2018vz].
+There are 12 regulatory areas from which 3AB holds 51.2% of the stock, followed by regions 2ABC and 4ACDE with 23.1% and 20.4%, respectively, and lastly region 4B with only 5.2% of the stock distribution [@IPHC:2018vz].
 In terms of management, the IPHC implements a total allowable catch (TAC) based on a yearly sampling of the Convention area in addition to a series of regulations to control fishing effort [@IPHC:2018vz].
 The TAC is divided between recreational, subsistence and commercial fishery, with a portion set aside for bycatch of other fisheries [@IPHC:2019wt].
-The commercial fishing season starts in March ending around November whith restrictions allowing only set line gear with J-type hooks targeting individuals over 81.3 cm with head on [@IPHC:2019wt].
-
-##### The Gulf of Maine Arrangement
-
-Since 1998 Canada and the US celebrate a "Resource Sharing Understanding" to inform the management of George Bank's Atlantic cod (*Gadus morhua*), and Eastern George Bank's haddock (*Melanogrammus aeglefinus*) and, yellowtail flounder (*Limanda ferruginea*) [@Pudden:2007bo; @CIA:2017uta; @TRAC:2016wu].
-The GoMA suggests catch-limits based on stocks' distribution produced by quaterly surveys and historical catch [@TRAC:2016wu], and so Canada and the US ultimatley take single management decissions [@Soboil:2006gw].
-In terms of manangement, the US has a multi species harvest control with area and season cloasures, mesh sizes, effort control, and mobile gear vessels that use bottom otter trawl gear [@Soboil:2006gw].
+The commercial fishing season starts in March ending around November whith restrictions allowing only set line gear with J-type hooks targeting individuals over 81.3 cm of total length [@IPHC:2019wt].
+
+### The Gulf of Maine Arrangement
+
+Since 1998 Canada and the US celebrate a "Resource Sharing Understanding" to inform the management of Eastern George Bank's Atlantic cod (*Gadus morhua*) and haddock (*Melanogrammus aeglefinus*) and, yellowtail flounder (*Limanda ferruginea*) [@Pudden:2007bo; @CIA:2017uta; @TRAC:2016wu].
+The GoMA suggests catch-limits based on a weighted method were 10% represents the stocks’ historical distribution (from 1967 to 1994) and 90% current distributions produced by quarterly surveys and historical catch [@TRAC:2016wu].
+In 2017, the allocation proposed for the GoMA was, Atlantic cod 80% Canada to 20 % U.S, haddock 41% Canada and 59% U.S and yellowtail flounder 31% Canada and 69% U.S (TRAC 2016).
+However, because this is an unofficial agreement, Canada and the US ultimately take single management decisions (Soboil and Sutinen 2006).
+In terms of management, the US has a multi species harvest control with area and season cloasures, mesh sizes, effort control, and mobile gear vessels that use bottom otter trawl gear [@Soboil:2006gw].
 In contrast, Canada has a quota system in addition to limited-entery licensig, fleet allocations, and mesh and fish size regulation, among other input controls.
-Canada inshore vessels fish Cod with longline and gillnet while haddock is mainly caught with bottom otter trawl gear [@Soboil:2006gw].
-
-#### Projecting Future Species Distribution
+Canada inshore vessels fish cod with longline and gillnet while haddock is mainly caught with bottom otter trawl gear [@Soboil:2006gw].
+
+### Projecting Future Species Distribution
 
@@
 The DBEM algorithm integrated ecophysiology and habitat suitability with spatial population dynamics of exploited fishes and invertebrates to project shifts in abundance and potential fisheries catches under climate change.
-The algorithm predicted species distribution based on depth and latitudinal range, habitat preferences and an index of species association with major habitat types to estimate changes in abundance distribution over a 0.5º x 0.5º grid of the world ocean.
+The algorithm predicted species distribution based on depth and latitudinal range, habitat preferences and an index of species association with major habitat types to estimate changes in abundance distribution over a $0.5^{\circ}$ x $0.5^{\circ}$ grid of the world ocean.
 For each grid cell and time step, the model then calculated species carrying capacity according to sea surface temperature, salinity, oxygen content, sea ice extent (for polar species) and bathymetry, as well as the species preferences to these conditions.
@@
 The DBEM was projected using three earth system models (ESM), the Geophysical Fluid Dynamics Laboratory Earth System Models 2M (GFDL)[^GFDL], the Institute Pierre Simon Laplace Climate Model 5 (IPSL-CM5)[^IPSL], and the Max Planck Institute for Meteorology Earth System Model (MPI)[^MPI].
-Each model was downscaled to match the DBEM 0.5' x 0.5' grid using the nearest neighbor method, and in some cases, bilinear interpolation [@Cheung:2016hf].
+Each model was downscaled to match the DBEM $0.5^{\circ}$ x $0.5^{\circ}$ grid using the nearest neighbor method, and in some cases, bilinear interpolation [@Cheung:2016hf].
 Finally, we used the model outputs for two scenarios of the Intergovernmental Panel on Climate Change (IPCC)-Representative Concentration Pathways (RCP) 2.6 and RCP 8.5 representing a low greenhouse gas emission (strong mitigation) and a high greenhouse gas emission (week mitigation) scenario, respectively [@IPCC:2014bz].
@@
 
-[^GFDL]: More information related to the Geophysical Fluid Dynamics Laboratory Earth System Models 2M can be found at www.gfdl.noaa.gov
-[^IPSL]: More information related to the Institute Pierre Simon Laplace Climate Model 5 can be found at www.icmc.ipsl.fr/
-[^MPI]: More information related to the Max Planck Institute for Meteorology Earth System Model can be found at www.mpimet.mpg.de/en/science/models/
+[^GFDL]: Geophysical Fluid Dynamics Laboratory Earth System Models 2M [online] www.gfdl.noaa.gov
+[^IPSL]:Institute Pierre Simon Laplace Climate Model 5 [online] www.icmc.ipsl.fr/
+[^MPI]: Max Planck Institute for Meteorology Earth System Model [online] www.mpimet.mpg.de/en/science/models/
 
@@
 
-#### Estimation of Maximum Catch Potential Change
-
-For estimating the percentage change of MCP at the regional scale, we frst aggregated the yearly mean MCP of all species per region ($X_{yr}$) and period:
+### Estimation of Maximum Catch Potential Change
+
+For estimating the percentage change of MCP at the regional scale, we first aggregated the yearly mean MCP of all species per region ($X_{yr}$) and period:
 
@@
 where *y* is year, *r* is region, *s* is species, *n* is total number of species, and $\hat{MCP}$ is the MCP averaged by the three ESMs.
-In the case of North America as a whole, and the GoM arrangement, region is defined as the 0.5' x 0.5' grid-cell within the EEZ and the specific NAFO regulatory areas, respectiveley.
+In the case of North America as a whole, and the GoM arrangement, region is defined as the $0.5^{\circ}$ x $0.5^{\circ}$ grid-cell within the EEZ and the specific NAFO regulatory areas, respectiveley.
 For the IPHC analysis, region is defined as the Comission's regulatory areas (Fig.
@@
 
-**RB where $X_{t}$ is the future averaged MCP for each of the two time periods analized in this study and $t_0$ is the present averaged MCP ($\mu$ `r Beg_In`-`r Beg_End`).
+ where $X_{t}$ is the future averaged MCP for each of the two time periods analized in this study and $t_0$ is the present averaged MCP ($\mu$ `r Beg_In`-`r Beg_End`).
 This way, Equ.
 2 shows the percentage change in MCP by mid $21^{st}$ century when $X_T$ = $\mu$ `r Mid_In`-`r Mid_End`, and end of $21^{st}$ century when $X_T$ = $\mu$ `r End_In`-`r End_End`, relative to today ($t_0$).
-The rationale between choosing these time periods was to provide a relative short-term projection (mid-century) that would be more policy-relevant but also show the long term trend (end of century).**
+The rationale between choosing these time periods was to provide a relative short-term projection (mid-century) that would be more policy-relevant but also show the long term-trend (end of century).
 
@@
 
-In addition, we borrowed the concept of “threat point” from game theory **RA defined as the minimum payoff that a player is willing to receive in order to cooperate with other players** (see Sumaila et al., this Special Feature).
-Thus, we estimate the change in the $\hat{MCP}$ **RA (threat point)** that each country **RA (players)** would have for each species (hereafter referred as stock-share ratio), for both the IPHC and the GoMA.
-**RA The stock-share ratio can be seen as the proportion of the stock's distribution within the study area that each country has**.
+In addition, we borrowed the concept of “threat point” from game theory defined as the minimum payoff that a player is willing to receive in order to cooperate with other players (see Sumaila et al., this Special Feature).
+Thus, we estimate the change in the $\hat{MCP}$ (threat point) that each country (players) would have for each species (hereafter referred as stock-share ratio), for both the IPHC and the GoMA.
+The stock-share ratio can be seen as the proportion of the stock's distribution within the study area that each country has.
 For this, we first modify Equ.
@@
 
-# RESULTS
-
-```{r Load_Data, echo = F, eval = T, results='hide', warning=F,message=F}
+## RESULTS
+
+```{r Load_Data, echo = F, eval = F, results='hide', warning=F,message=F}
 
@@
 
-### North American transboundary **RB stocks** are shifting poleward
-
-```{r Changes_Data_All, eval =F, echo = F, fig.height=8, fig.width=12}
+### North American transboundary stocks are shifting poleward
+
+```{r Changes_Data_All, eval = F, echo = F, fig.height=8, fig.width=12}
 
@@
   mutate(RCP = ifelse(Model %in% RCP,"Low_Emission","High_Emission")) %>% 
+  # Sum the MCP of all species in each index by model
   group_by(INDEX,
@@
            RCP) %>% 
-  summarise_at(vars(Beg_In:End_End), sum,na.rm=T) %>% # Sum the MCP of all species in each index by model
+  summarise_at(vars(Beg_In:End_End), sum,na.rm=T) %>% 
   gather("Year","MCP",Beg_In:End_End) %>% 
-  mutate(  # Indicate the three period times
+  # Indicate the three period times
+  mutate( 
     Period = ifelse(Year >= Beg_In & Year <= Beg_End,"Begining",
@@
   ) %>% 
+  #Average per Time period
   group_by(INDEX,Model,RCP,Period) %>% 
-  summarise(Mean_T_MCP =mean(MCP,na.rm=T)) %>% #Average pero Time period
+  summarise(Mean_T_MCP =mean(MCP,na.rm=T)) %>% 
   filter(Period != "Other_Years") %>% 
   spread(Period,Mean_T_MCP) %>% #Spread to estimate MCP_Change
-  mutate_at(vars(Mid_Century, # Devide future values by present
+  # Divide future values by present
+  mutate_at(vars(Mid_Century, 
                  The_End_Century),
@@
   ) %>% 
-  mutate_at(vars(Mid_Century, # Estimate percentage change
+  # Estimate percentage change
+  mutate_at(vars(Mid_Century, 
                  The_End_Century),
@@
   mutate(Direction = ifelse(MCP_Change >= 0, "Positive","Negative")) %>% 
-  group_by(INDEX,Period,RCP) %>% # Average results per ESMs
+  # Average results per ESMs
+  group_by(INDEX,Period,RCP) %>% 
   summarise_at(vars(MCP_Change),
@@
             by="INDEX") %>% 
+  # set everything over 100 to 100
   mutate_at(vars(Mean_ESM_MCP_Chng,
@@
             funs(ifelse(. > 100, 100,.)
-            )  # set everything over 100 to 100
-  )
-
-### Explore model agreement
-
-# ggplot(MCP_Data) +
-#   geom_tile(
-#     aes(
-#       x = longitude,
-#       y = latitude,
-#       color = Model_Agreement,
-#       fill = Model_Agreement
-#     )
-#   ) +
-#   facet_grid(RCP~Period)
-
-### Explore mAtlantic unde 40
-
-# Under40 <- MCP_Data %>% 
-#   filter(latitude < 40, longitude > -90)
-# 
-# ggplot(Under40) +
-#   geom_tile(
-#     aes(
-#       x = longitude,
-#       y = latitude,
-#       color = Model_Agreement,
-#       fill = Model_Agreement
-#     )
-#   ) +
-#   facet_grid(RCP~Period)
-
+            )
+  )
+
+# Plot map for paper figure 
 Seq <- seq(-100,100,by=5) #Axis
@@
 
-  ggsave("New_plot.png",
+ ggsave("Fig2.png",
      plot = p,
@@
 
-Shifts in the distribution of 33 jointly managed transboundary stocks of North America show that by 2050 MCP of transboundary stocks will increase in Atlantic-Canadian and Alaskan waters and decrease in Pacific-Canadian and the US contiguous states waters (Fig.
+Shifts in the distribution of 33 jointly managed transboundary stocks of North America by 2050 relative to 2010 show that MCP of transboundary stocks will overall increase in Atlantic-Canadian and Alaskan waters and decrease in Pacific-Canadian and the US contiguous states waters (Fig.
 2).
@@
 2-A).
-Under the low emission scenario, MCP will be reduced in a reduced area and with lower intensity (Fig.
-2-B).
-Impacts of cliamte change are expected to intensify towards the end of the $21^{st}$ century, although with greater uncertainty (**Fig A1.1**).
+For most regions, losses of MCP will be more intense under a high emission scenario (Fig 2-A) than under a low emission scenario (Fig 2-B), however, there will be no apparent change in gain intensity between scenarios.
+Impacts of cliamte change are expected to intensify towards the end of the $21^{st}$ century, although with greater uncertainty (Fig A1.1).
 
 ![Fig 2.
-Percentage change of MCP of transboundary stocks of North America for mid $21^{st}$ century (2041-2060) **RA relative** to present (2005-2014) under a A) lohighw emission scenario and; B) low emission scenario.
+Percentage change of MCP of transboundary stocks of North America for mid $21^{st}$ century (2041-2060) relative to present (2005-2014) under a A) high emission scenario and; B) low emission scenario.
 Points represent areas where at least one model do not agree in the direction of change](./Figures/Fig2.png)
 
-```{r Changes_Per_Species_F, eval=F, echo=F}
+```{r Changes_Per_Species_T, eval = F, echo = F }
 
 # This table provides the percentage change in MCP for each species, EEZ and RCP as well as the percentage change in Stock-share ratio.
-
-# List of DBEM INDEX within the EEZ
-#Data provided by Vicki Lam
-EEZIDs_List <- read_excel("~/Documents/UBC/Oceans_Project/Distribution/By Cell/Cell_Data/Updated_EEZList_17June2016.xlsx")
-EEZ_CellID <- read_excel("~/Documents/UBC/Oceans_Project/Distribution/By Cell/Cell_Data/EEZ_CellID.xlsx")
-
-colnames(EEZ_CellID) <- c("EEZID","INDEX")
-
-# DBEM Coordinate system
-Coor <- fread("~/Documents/UBC/Oceans_Project/Distribution/DBEM/Data/Lon_Lat_DBEM.txt",header = FALSE)
-colnames(Coor) <- c("INDEX","Longitude","Latitude")
 
@@
 Areas <- c(
-  "Canada (Arctic)",
  "Canada (East Coast)",
@@
 
-# Common data between both
+# Aggregate MCP per Nation, Species, Model, RCP and Time period
 
@@
   ) %>% 
-  group_by(
-    Species,
-    Model,
-    RCP,
-    Nation,
-    Basin
-  ) %>%
-  summarise_at(vars(Beg_In:End_End), sum,na.rm=T) %>% # Sum the MCP of each species by country
-  # select(INDEX,Model,Beg_In:Beg_End) %>%
+  # Sum the MCP of each species by country
+  group_by(Species, Model, RCP, Nation, Basin) %>%
+  summarise_at(vars(Beg_In:End_End), sum,na.rm=T) %>% 
   gather("Year","MCP",Beg_In:End_End) %>% 
@@
   ) %>% 
+  # Average by time period
   group_by(Nation,Basin,Species,Model,RCP,Period) %>% 
@@
   spread(Period,Mean_T_MCP) %>% #Spread to estimate MCP_Change
-  mutate_at(vars(Mid_Century, # Devide future values by present
+  # Divide future values by present
+  mutate_at(vars(Mid_Century, 
                  The_End_Century),
@@
   mutate(Direction = ifelse(MCP_Change >= 0, "Positive","Negative")) %>% 
-  group_by(Nation,Species,Period,RCP) %>% # Average results per ESMs
+  # Average results per ESMs
+  group_by(Nation,Species,Period,RCP) %>% 
   summarise_at(vars(MCP_Change),
@@
   ) %>% 
+  # set everything over 100 to 100
   mutate_at(vars(Mean_ESM_MCP_Chng,
@@
             funs(ifelse(. > 100, 100,.)
-            )  # set everything over 100 to 100
+            )
   )
@@
 
+# Estimate total MCP of all species per basin
+Basin_Total <- MCP_Species_Data %>% 
+  group_by(Basin,Model,RCP,Period) %>% 
+  summarise(TB_MCP = sum(Mean_T_MCP))
+
+# Stock Share Change per EEZ
 SS_Change <- MCP_Species_Data %>% 
-  group_by(RCP,Species,Period,Model) %>% 
-  summarise(Total_MCP = sum(Mean_T_MCP)) %>% #Estimate todays's total (both EEZs added) MCP for each species 
-  left_join(MCP_Species_Data) %>% # Inlude each nation's MCP
-  mutate(Proportion = (Mean_T_MCP/Total_MCP)*100) %>%  # estimates each Country's catch proportion per period
-  select(-Total_MCP,-Basin,-Mean_T_MCP) %>% 
-  group_by(Nation,RCP,Species,Period) %>% #Mean of all species
-  summarise(Mean_Spp_Proportion =mean(Proportion),
-            sd_Spp_Proportion =sd(Proportion)
-  ) %>% #Mean of all ESMs
-  group_by(Nation,RCP,Period) %>% 
-  summarise(Mean_ESM_Proportion = paste(round(mean(Mean_Spp_Proportion),2)," (",round(sd(Mean_Spp_Proportion),2),")",sep="")
-  ) %>% 
-  filter(Period %in% c("Mid_Century","The_End_Century")) %>% 
+  group_by(RCP,Period,Model,Nation,Basin) %>% # Estimate total MCP of all species per Nation 
+  summarise(Total_MCP = sum(Mean_T_MCP)) %>% 
+  left_join(Basin_Total,
+            by = c("RCP", "Period", "Model","Basin")) %>% 
+  mutate(Proportion = (Total_MCP/TB_MCP)*100) %>% # estimates each Country's catch proportion per period and RCP
+  group_by(Nation,RCP,Period) %>%  # Average ESMs
+  summarise(Mean_ESM_Proportion = paste(round(mean(Proportion),2)," (",round(sd(Proportion),2),")",sep="")
+  ) %>% 
+  filter(Period %in% c("Begining","Mid_Century","The_End_Century")) %>% 
   spread(Period,Mean_ESM_Proportion)
 
-#For paper
+#For paper (Table 2)
 write.csv(SS_Change,
-          "SS_Change.csv",
+     "./Ecology/Results/North_America/SS_Change.csv",
      row.names = F)
@@
 
-**In consequence, RA-each country's share-ratio of different species will change with an overall benefit to northern regions, regardless of the RCP scenario.** Overall, shifts will be amplified under the high emission scenario relative to the low greenhouse emission scenario pathway (Table 2).
+Consequently, each country's share-ratio of different species will change with an overall benefit to northern regions, regardless of the RCP scenario.
+Overall, shifts will be amplified under the high emission scenario relative to the low greenhouse emission scenario pathway (Table 2).
 
 Table 2.
-Average (standard deviation) of 33 transboundary species stock-share of all models for each EEZ and emission scenario for mid and end of the $21^{st}$ century.
-Averages might not add to 100% due to model differences (e.g., standard deviation)
+Total stock-share of all 33 transboundary species by EEZ and emission scenario for the present, and mid and end of the $21^{st}$ century.
+Averages might not add to 100% due to model differences.
+Standard deviation of the projected values are provided in parentheses.
 
@@
 It is likely that the stock shift from the U.S.
-contiguous states towards Canada will offset the shift of the **RA later** towards northern regions, resulting in undetectable changes in Canadian area 2B and Alaskan 2C under both climate change scenarios.
+contiguous states towards Canada will offset the shift of the later towards northern regions, resulting in undetectable changes in Canadian area 2B and Alaskan 2C under both climate change scenarios.
 The potential movement of halibut westward will increase the MCP of regulatory areas 3B (under a low emission scenario) and 4ABCE along the Aleutian Islands and Bering Sea.
-**Regions 4DE, the most poleward regulatory areas of the IPHC, are expected to gain MCP by mid (Fig.
+Regions 4DE, the most poleward regulatory areas of the IPHC, are expected to gain MCP by mid (Fig.
 3) and end of the $21^st$ century (Fig.
@@
 A3.1).
-In contrast, under a low emission scenario, sea ice is expected to stabilize towards mid $21^st$ century, thus providing less "new" suitable habitat for P.
-halibut and resulting in undetectable changes in MCP for the region (Fig 3.
+In contrast, under a low emission scenario, sea ice is expected to stabilize towards mid $21^st$ century, thus providing less "new" suitable habitat for Pacific halibut and resulting in undetectable changes in MCP for the region (Fig 3.
 B) and decreasing even more towards 2100 (Fig.
-A1.2).**
-
-```{r IPHC_Map_Result_Regions, eval=F, echo=F}
-
-### Get the INDEX in each IPHC region
+A1.2).
+
+```{r IPHC_Map_Result_Regions, eval = F, echo = F}
 
@@
 
-#### New Future Method to account for mean +- sd of models #
+# ------------------ #
+# Estimate IPHC change 
+# ------------------ #
+
 IPHC_MCP_Change <- DBEM_Corrected %>% 
@@
   gather("Year","MCP",Beg_In:End_End) %>% 
-  mutate(  # Indicate the three period times
+  # Indicate the three period times
+  mutate( 
     Period = ifelse(Year >= Beg_In & Year <= Beg_End,"Begining",
@@
   ) %>% 
+  # Sum of Index per Region
   group_by(RegArea,Model,RCP,Year,Period) %>% 
-  summarise(Regional_MCP =sum(MCP,na.rm=T)) %>% # Sum of Index per Region
+  summarise(Regional_MCP =sum(MCP,na.rm=T)) %>% 
+  # Average pero Time period
   group_by(RegArea,Model,RCP,Period) %>% 
-  summarise(Mean_T_MCP =mean(Regional_MCP,na.rm=T)) %>% #Average pero Time period
+  summarise(Mean_T_MCP =mean(Regional_MCP,na.rm=T)) %>%
   filter(Period != "Other_Years") %>% 
-  spread(Period,Mean_T_MCP) %>% #Spread to estimate MCP_Change
-  mutate_at(vars(Mid_Century, # Devide future values by present
+  spread(Period,Mean_T_MCP) %>% 
+  # Divide future values by present
+  mutate_at(vars(Mid_Century,
                  The_End_Century),
@@
   mutate(Direction = ifelse(MCP_Change >= 0, "Positive","Negative")) %>% 
-  group_by(RegArea,Period,RCP) %>% # Average results per ESMs
+  # Average results per ESMs
+  group_by(RegArea,Period,RCP) %>% 
   summarise_at(vars(MCP_Change),
@@
   ungroup() %>% 
+  # set everything over 100 to 100
   mutate_at(vars(Mean_ESM_MCP_Chng,
@@
             funs(ifelse(. > 100, 100,.)
-            )  # set everything over 100 to 100
-  )
-
-# Ends new estimation
-
-### Spatial Step for regional analysis ####
+            ) 
+  )
+
+# ------------------ #
+# Plot and save figure
+# ------------------ #
+
+# Spatial Step for regional analysis
 
@@
 
-# IPHC_DBEM_sf_Data <- IPHC_DBEM_sf
+# ------- NOTE ------ # 
+# Change for main figure and S3 figure
+# ---------------------- #
 
 IPHC_DBEM_sf <- IPHC_DBEM_sf %>% 
-  # filter(Period == "Mid_Century") %>%
-  filter(Period == "The_End_Century") %>% 
+ # filter(Period == "Mid_Century") %>% # Paper figure
+ filter(Period == "The_End_Century") %>%# Supplemental figure
  mutate(RegArea = paste(RegArea,Model_Agreement,sep=""))
 
+# North America shapefile
 North_America_Land <- North_America_Land %>% 
@@
 
-Seq <- seq(-50,50,by=5) #Axis
-
+# Limit Axis
+Seq <- seq(-50,50,by=5)
+
+# Plot it!
 P1 <- ggplot() +
@@
 
-### now we average the results from the models for END century ###
-
-# Seq <- seq(-50,50,by=5) #Axis
-
-# P2 <- ggplot() +
-#   geom_sf(data = North_America_Land, colour = "lightgrey") + # Land Map of North America
-#   geom_sf(data = subset(IPHC_DBEM_sf, Country == "United States"), # DBEM Of the US
-#           aes(fill = Percentage_End)
-#   ) +
-#   geom_sf(data = subset(IPHC_DBEM_sf, RegArea == "2B"), # DBEM of Canada
-#           aes(fill = Percentage_End)
-#   ) +
-#   geom_sf_label(data = IPHC_DBEM_sf, # RegAreas labels
-#                 aes(
-#                   label = RegArea,
-#                   fill = Percentage_End
-#                 ),
-#                 colour = "black"
-#   ) +
-#   geom_label(data=IPHC_DBEM_sf, aes(label = RCP, x =4080637 , y = 4551701, colour = RCP), #RCP labels for grid plot
-#              show.legend = FALSE,
-#              size = 10
-#   ) +
-#   facet_wrap(~RCP,  # For grid plot, comment in one plot each
-#              ncol = 2) +
-#   scale_colour_manual(values=c("blue", "red")) + #Labels colors for grid plot
-#   scale_fill_gradient2("",
-#                        limits=c(-30,30),
-#                        breaks = Seq) +
-#   ggtheme_map() +
-#   theme(
-#     legend.key = element_rect(size = 4),
-#     legend.key.width =unit(8,"line"),
-#     legend.text = element_text(size = 16),
-#     strip.text.x = element_blank()
-#   ) +
-#   coord_sf(xlim = c(1963800, 10041910), # Subsets north america
-#            ylim = c(3651701,9728813)
-#   ) +
-#   annotate("text", label = "Alaska", x = 6280637, y = 9228813, size = 6, colour = "black") +
-#   annotate("text", label = "Canada", x = 9629910, y = 9228813, size = 6, colour = "black") +
-#   annotate("text", label = "US Contiguous\n States", x =10000000, y = 5151701, size = 6, colour = "black", angle = -90)
-# 
-# # Save plot 
-# Name_End = paste("IPHC_Reg_26_85_2100.png")
-# 
-# ggsave(Name_End,
-#        plot = P2,
-#        width = 15,
-#        height = 10,
-#        units = "in",
-#        path = Path)
-
 ```
 
-```{r Functions, eval = F, echo = F}
-
-getTaxInfo <- function(TaxNumber,TaxPath=NA, Sal = "NA"){
-
-  # Set automatic path, change if needed
-  TaxPath  <- "/Volumes/DATA/JULIANO_NEYMAR/PristineSeasData/Species/TaxonDataC0/"
-
-  # Sets the tac and path 
-  To_Read <- paste(TaxPath,TaxNumber,".txt",sep = "")
-
-  if(Sal == "Y"){
-  Spp_Info <- suppressWarnings(
-    read_table2(To_Read, 
-     col_names = FALSE, col_types = cols(`0` = col_character(), 
-         X2 = col_number(), X3 = col_number(), 
-         X4 = col_number(), X5 = col_number(), 
-         X6 = col_number()), 
-     skip = 16)
-  ) 
-  Spp_Info <- Spp_Info[1,2:6]
-  }else{
-  # Reads in file
-  Spp_Info <- suppressMessages(
-    readr::read_delim(To_Read, 
-               "\t", escape_double = FALSE, col_names = FALSE, 
-               # col_types = cols(X2 = col_number()),
-               trim_ws = TRUE)
-  )
-  }
-  return(Spp_Info)
-}
-
-getTTP <- function(TaxNumber,yr,TaxPath=NA){
-
-  # Set automatic path, change if needed
-  TaxPath  <- paste("/Volumes/DATA/JULIANO_NEYMAR/PristineSeasData/TPP",yr,"",sep="/")
-
-  # Sets the tac and path 
-  To_Read <- paste(TaxPath,"TPPotp",TaxNumber,".csv",sep = "")
-
-  TPPotp <- read.csv(To_Read)
-
-  return(TPPotp)
-}
-
-getEnvVar=function(yr,ModelRCP,RCP,Variable){
-
-  if(ModelRCP == "IPSL"){
-    ModelRCP = "IPSL-CM5A-MR"
-    Filepath <- paste("/Volumes/DATA/DATA/Environmental data/Model Climate data/CMIP5/txt CMIP5/Reformatted",ModelRCP,RCP,"",sep="/")
-  }
-
-  if(ModelRCP ==  "MPI"){
-    ModelRCP = "MPI-ESM-MR"
-    Filepath <- paste("/Volumes/DATA/DATA/Environmental data/Model Climate data/CMIP5/txt CMIP5/Reformatted",ModelRCP,RCP,"",sep="/")
-  }
-
-  if(ModelRCP == "GFDL"){
-
-    if(RCP == "rcp26"){
-      ModelRCP <- "GFDL26"
-    }else{
-      ModelRCP <- "GFDL85"
-    }
-    Filepath <- paste("/Volumes/DATA/JULIANO_NEYMAR/PristineSeasData/Climate",ModelRCP,"",sep="/")
-  }
-
-  if(Variable == "Ice"){
-
-    Bottom <- paste("IceExt_",yr,".txt",sep="")
-
-  }
-
-    if(Variable == "Temperature"){
-
-      Bottom = paste("botTemp_",yr,".txt",sep="")
-
-    }
-
-    if(Variable == "Salinity"){
-      # Bottom
-      Bottom = paste("Salinity_btm_",yr,".txt",sep="")
-
-    }
-
-    Read_me <- paste(Filepath,Bottom,sep="")[1]
-    Bottom_Data <- read.csv(Read_me,header=F)
-
-   # Retrun
-
-    getTemp <- Bottom_Data  
-}
-
-```
-
-```{r 4DE_exploration, eval=F, echo=F,message=F, warning=F}
-
-# Exploring wy 4D s negative under 2.6 but positive under 8.5
-# This chunk will use functions build for the Pristince seas work
-
-### Exploration at the spatial level
-
-Spatial_4DE <- DBEM_Corrected %>% 
-  mutate(RCP = ifelse(Model %in% c("GFDL26F1","IPSL26F1","MPI26F1"),"RCP 2.6","RCP 8.5")) %>% # Set the RCPs
-  filter(Species == "Hippoglossus stenolepis") %>% 
-  left_join(IPHC_Reg_DBEM_df,
-            by = "INDEX") %>% 
-  filter(RegArea %in% c("4D","4E")) %>%
-  group_by(RegArea,RCP,Model) %>% #Sum grid-cells by regulatory area, RCP and Model
-  summarise_at(vars(`2005`:`2099`), sum,na.rm=T) %>% 
-  tidyr::gather("Year","Total_MCP",`2005`:`2099`) %>% 
-  group_by(RegArea,RCP,Year) %>% 
-  summarise(
-    m=mean(Total_MCP),
-    sd=sd(Total_MCP)
-    )
-
-ggplot(Spatial_4DE) +
-  geom_point(
-    aes(
-      x = Year,
-      y = m,
-      colour = RCP
-    )
-  ) +
-  facet_wrap(~RegArea,
-             scales = "free")
-
-### Environmental varibales of the region
-
-## Temp
-
-# Variables
-Model = c("GFDL","IPSL","MPI")
-RCP = c("rcp26","rcp85")
-
-Grid <- DBEM_Corrected %>% 
-  select(INDEX) %>% 
-  left_join(IPHC_Reg_DBEM_df,
-            by = "INDEX") %>% 
-  filter(RegArea %in% c("4D","4E")) %>% 
-  select(INDEX)
-
-Variables <- c("Temperature","Salinity","Ice")
-
-F_BData <- NULL
-F_SData <- NULL
-F_MData <- NULL
-F_RData <- NULL
-Years <- seq(2005,2100,1)
-
-all_Grid <- seq(1,259200,1)
-
-for(v in 1:3){
-  # Loop through RCPs
-  for(r in 1:2){
-    # Loop through  variables
-    for(m in 1:3){
-      # Loop through years
-      for(y in 1:length(Years)){
-
-        Data <- getEnvVar(yr = Years[y],
-                          Model = Model[m],
-                          Variable = Variables[v],
-                          RCP = RCP[r]
-        ) %>% 
-          mutate(INDEX = all_Grid) %>% 
-          filter(INDEX %in% Grid$INDEX)
-
-        if(y == 1){
-
-          F_BData <- Data[1]
-
-        }else{
-
-          F_BData <- cbind(Data[1],F_BData)
-
-        }
-      }
-
-      colnames(F_BData) <- Years
-
-      F_BData <- F_BData %>% 
-        gather(Year,Value,1:426) %>% 
-        mutate(Model = Model[m],
-               RCP = RCP[r],
-               Variable = Variables[v])
-
-      if(m == 1){
-
-        F_MData <- F_BData
-
-      }else{
-
-        F_MData <- rbind(F_BData,F_MData)
-      }
-    }
-
-    if(r == 1){
-
-      F_RData <- F_MData
-
-    }else{
-
-      F_RData <- rbind(F_RData,F_MData)
-    }
-  }
-
-  if(v == 1){
-
-    F_VData <- F_RData
-
-  }else{
-
-    F_VData <- rbind(F_VData,F_RData)
-  }
-
-} # closes variable loop
-
-write.csv(F_VData,
-          "Environmental_Data_Halibut.csv",
-          row.names = F)
-
-#Load Halibut Species preferences
-Halibut <- getTaxInfo(600514)
-# Demersal
-# HabAssocSal 0 1 1 -1 -1
-# HabAssocIce 0
-
-# Temp
-TTPop <- getTTP(600514,"Avg") %>% 
-  filter(TempPP > 0)
-
-Min_T <- min(TTPop$Temp)
-Max_T <- max(TTPop$Temp)
-
-# Halibut_Temp 2
-# quant05 -2 
-# quant25 0 
-# quant50 2
-# quant75 5
-# quant95 11
-```
-
-```{r halibut_enviro, eval =F, echo = F}
-
-# Read Data
-
-Environmental_Data_Halibut <- read.csv("~/Documents/UBC/OC_Special_Issue/Ecol/Data/Distribution/Environmental_Data_Halibut.csv")
-
-# Isolate Regions
-
-DE_Regions <- IPHC_Reg_DBEM_df %>% 
-  filter(RegArea %in% c("4D","4E")) %>% 
-  left_join(Environmental_Data_Halibut,
-            by ="INDEX") %>% 
-  group_by(Model,RCP,Variable,Year,RegArea) %>% 
-  summarise(
-    Total_Reg = mean(Value,na.rm=T)
-    ) %>% 
-  group_by(RCP,Variable,Year,RegArea) %>% 
-  summarise(
-    Mean_GCMs = mean(Total_Reg,na.rm=T),
-    sd_GCMs = sd(Total_Reg,na.rm=T)
-    ) %>% 
-  group_by(RCP,Variable,RegArea) %>% # Running mean as Kleisner & Pauly 2012
-    mutate(RMean = rollmean(x = Mean_GCMs, 10,
-                            align = "right",
-                            fill = Mean_GCMs),
-           Rsd = rollmean(x = Mean_GCMs, 10,
-                            align = "right",
-                            fill = sd_GCMs)
-    ) %>% 
-  filter(Year >= 2015) %>% 
-  ungroup() %>% 
-  mutate(
-    RCP = ifelse(RCP == "rcp26","Low Emission","High Emission"),
-    Variable = ifelse(Variable == "Ice","Ice Extension",
-                      ifelse(Variable == "Temperature","Bottom Temperature (ºC)","Bottom Salinity")
-                      )
-    )
-
-# Ribbom version
-
-ggplot(DE_Regions) + 
-  geom_ribbon(aes(
-    x = Year,
-    ymin = RMean - sd_GCMs,
-    ymax = RMean + sd_GCMs,
-    # colour = RCP,
-    fill = RCP
-  ),
-  alpha = 0.2
-  ) +
-  geom_line(
-    aes(
-      x = Year,
-      y = RMean,
-      colour = RCP
-    )
-  ) +
-  facet_wrap(~RegArea +Variable,
-             scales ="free_x") +
-  ggtheme_plot() +
-  scale_x_continuous(breaks = seq(2010,2100,30),
-                     limits = c(2010,2100)
-  ) +
-  scale_color_manual("Climate Change Scenario",
-                     values=c("red","blue")
-  ) + 
-  scale_fill_manual("Climate Change Scenario",
-                    values=c("red","blue")
-  ) + 
-  ylab("Running Mean (10 yrs)")
-
-ggsave("Environ_Sup.png",
-       plot = last_plot(),
-       width = 10,
-       height =8,
-       units = "in",
-       path = "./Results/Sup"
-       )
-
-```
-
-```{r DBEM_Uncertanty, eval = F, echo = F}
-
-#### DBEM Uncertanty
-
-### Today
-
-Today_Uncertanty <- DBEM_Corrected %>% 
-  filter(Species %in% Selected_Species) %>% 
-  left_join(IPHC_Reg_DBEM_df,
-            by = "INDEX") %>% 
-  filter(!is.na(RegArea)) %>% 
-  mutate(RCP = ifelse(Model %in% RCP,"Low Emission","High Emission")) %>% 
-  gather("Year","MCP",Beg_In:Beg_End) %>% 
-  mutate(Period = ifelse(Year >= Beg_In & Year <= Beg_End,"Begining","NA")) %>% 
-  group_by(RegArea,Model,RCP,Year,Period) %>% 
-  summarise(Regional_MCP =sum(MCP,na.rm=T)) %>% 
-  group_by(RegArea,Model,RCP) %>% 
-  summarise(Today_MCP =mean(Regional_MCP,na.rm=T))
-
-IPHC_MCP_Change_Uncert <- DBEM_Corrected %>% 
-  filter(Species %in% Selected_Species) %>% 
-  left_join(IPHC_Reg_DBEM_df,
-            by = "INDEX") %>% 
-  filter(!is.na(RegArea)) %>% 
-  mutate(RCP = ifelse(Model %in% RCP,"Low Emission","High Emission")) %>% 
-  gather("Year","MCP",Beg_In:End_End) %>%
-  group_by(Model,RCP,Year,RegArea) %>%
-  summarise(Regional_MCP =sum(MCP,na.rm=T)) %>% 
-  group_by(RCP,Model,RegArea) %>% # Running mean as Kleisner & Pauly 2012
-  mutate(RMean = rollmean(x = Regional_MCP, 10,
-                          align = "right",
-                          fill = Regional_MCP)
-  ) %>% 
-  mutate(GCM = ifelse(Model == "GFDL26F1" | Model == "GFDL85F1","GFDL",
-                      ifelse(Model == "IPSL26F1" | Model == "IPSL85F1", "IPSL",
-                             ifelse(Model == "MPI26F1" | Model == "MPI85F1","MPI","NA"
-                             )
-                             )
-                      )
-  ) %>% 
-  filter(Year >= 2015) %>% 
-  left_join(Today_Uncertanty,
-            by = c("RegArea","Model","RCP")) %>% 
-  mutate(Index = RMean/Today_MCP)
-
-ggplot(IPHC_MCP_Change_Uncert) +
-  geom_line(
-    aes(
-      x = as.numeric(Year),
-      y = Index,
-      color = GCM,
-      linetype = RCP
-    )
-  ) +
-  facet_wrap(~RegArea,
-             scales = "free_y") +
-  labs(
-    x = "Year",
-    y ="Index (Future MCP/Present)"
-    ) +
-  scale_color_manual("Global Circulation model",
-                     values=c("#EEA410","#B53CB9","#2EBC67")
-  ) +
-  scale_x_continuous(breaks = seq(2010,2100,30),
-                     limits = c(2010,2100)
-  ) +
-  ggtheme_plot()
-
-ggsave("Model_Uncer_Sup.png",
-       plot = last_plot(),
-       width = 12,
-       height =8,
-       units = "in",
-       path = "./Results/Sup"
-       )
-
-```
-
-```{r Figure_3, eval =F, echo =F}
+```{r Figure_3, eval =F, echo = F}
 
@@
 4).
-Maintaining emissions to lower levels **RA through** 2050 would potentially leave unchanged the stock-share ratio of three regulatory areas (3AC, and 4D) and negatively change regulatory area 2A.
-On the other hand, failing to achieve such target will decrease the stock-share ratio **RA in** the most productive regulatory areas (2AC, 3AB).
-
-```{r IPHC_Proportion_Regions, eval=F, echo = F, message=F, warning=F}
-
+Maintaining emissions to lower levels through 2050 would potentially leave unchanged the stock-share ratio of three regulatory areas (3AC, and 4D) and negatively change regulatory area 2A.
+On the other hand, failing to achieve such target will decrease the stock-share ratio in the most productive regulatory areas (2AC, 3AB).
+
+```{r IPHC_Proportion_Regions, eval = F, echo = F, message=F, warning=F}
+
+# Set saving path
 Path <- "./Manuscript/Results/IPHC/Proportion"
-# names(DBEM_Results)
 
@@
 
-#### New updated method
-
-New_IPHC_Absolutes <- DBEM_Corrected %>% 
+# ------------------------- #
+# Changes in proportion 
+# referent to (2005-2014)
+# ------------------------- #
+
+# Estimate IPHC total values
+
+IPHC_Absolutes <- DBEM_Corrected %>%
   mutate(RCP = ifelse(Model %in% c("GFDL26F1","IPSL26F1","MPI26F1"),"Low Emission","High Emission")) %>% # Assigns RCP by model
@@
 
-# Changes in the proportion in comparrison of the mean (2005-2014) proportion ####
-
 # Estimate total MCP of each RCP per year
-New_Proportion_Total <- New_IPHC_Absolutes %>% 
+Proportion_Total <- IPHC_Absolutes %>% 
   group_by(RCP,Year,Model) %>% 
@@
 # Estimates the proportion of each RegArea catch pero RCP and Year
-New_Proportion <- New_IPHC_Absolutes %>% 
-  left_join(New_Proportion_Total,
+Proportion_Data <- IPHC_Absolutes %>% 
+  left_join(Proportion_Total,
             by = c("RCP","Year","Model")) %>% 
@@
 # Proportion change in the future (NOTE: not plotting by timeframe because of boxplot)
-New_Proportion_Change <- New_Proportion %>% 
+Proportion_Change <- Proportion_Data %>% 
   mutate(Time_Step = ifelse(Year <= Beg_End, "Begining_Prop",
@@
   ) %>% 
+  # Get mean proportion by timeframe
   group_by(RCP,
@@
   spread(Time_Step,Mean_Temp_Prop) %>% 
-  mutate_at(vars(Mid_Century_Prop, # Devide future values by present
+  # Divide future values by present
+  mutate_at(vars(Mid_Century_Prop, 
                  The_End_Century_Prop),
@@
   ) %>% 
-  mutate_at(vars(Mid_Century_Prop, # Estimate percentage change
+  # Estimate percentage change
+  mutate_at(vars(Mid_Century_Prop, 
                  The_End_Century_Prop),
@@
   gather("Time_Step","Prop_Change",Mid_Century_Prop,The_End_Century_Prop) %>% 
-  group_by(RegArea,Time_Step,RCP) %>% # Average results per ESMs
+  # Average results per ESMs
+  group_by(RegArea,Time_Step,RCP) %>% 
   summarise_at(vars(Prop_Change),
@@
 
-New_Proportion_Change$RegArea <- gsub("2B","2B",New_Proportion_Change$RegArea)
-
-#### Option all in one####
-ggplot(data = subset(New_Proportion_Change, Time_Step == "Mid_Century_Prop"),
+Proportion_Change$RegArea <- gsub("2B","2B",Proportion_Change$RegArea)
+
+# Plot and save figure
+ggplot(data = subset(Proportion_Change, Time_Step == "Mid_Century_Prop"),
        aes(
          x = reorder(RegArea,Order), # from forcasts` package
-         # x = RegArea,
          y = Mean_ESM_MCP_Chng,
@@
   geom_bar(stat = "identity") +
-  geom_errorbar(data = subset(New_Proportion_Change, Time_Step == "Mid_Century_Prop"),
+  geom_errorbar(data = subset(Proportion_Change, Time_Step == "Mid_Century_Prop"),
                 aes(
                   x = reorder(RegArea,Order),
-                  # x = RegArea,
-                  ymin=Mean_ESM_MCP_Chng-sd_ESM_MCP_Chng, # mean +- 2*sd
+                  ymin=Mean_ESM_MCP_Chng-sd_ESM_MCP_Chng, # mean +- sd
                   ymax=Mean_ESM_MCP_Chng+sd_ESM_MCP_Chng,
@@
     y = "Stock Share Ratio Change (%)"
-  )
-
- ggsave("New_Proportion_Mid.png",
-       plot = last_plot(),
+  ) +
+  ggsave("Proportion_gom_Mid.png",
+         plot = .,
          width = 8,
@@
 
-```{r Figure_4, eval =F, echo =F}
+```{r Figure_4, eval = F, echo = F}
 
@@
 
-### Projected change to species managed under the GoM **DV arrangement**
-
-While some regulatory areas of the IPHC will see **RA an incremental increase** in P.
-halibut MCP, the results for the Gulf of Maine show an overall decrease in MCP by 2050, regardless of the climate change scenario or ESM (Fig.
+### Projected change to species managed under the GoM arrangement
+
+While some regulatory areas of the IPHC will see an incremental increase in Pacific halibut MCP, the results for the Gulf of Maine show an overall decrease in MCP by 2050, regardless of the climate change scenario or ESM (Fig.
 5), intensifying by the end of the $21^{st}$ century (Fig.
@@
 5).
-For Y.
-founder, despite an overall reduction, some discrete areas are expected to increase with no particular pattern **RA and high uncertainty as ESMs in these regions do not agree in the direction of change.** Despite the overall reduction in MCP for all three species in comparison to current values, there is a benefit of achieving a low emission scenario as reductions intensify under the high emission scenario.
-
-```{r GB_Results_Spp, eval=F, echo = F, fig.width=12}
+For yellowtail flounder, despite an overall reduction, some discrete areas are expected to increase with no particular pattern and high uncertainty as ESMs in these regions do not agree in the direction of change.
+Despite the overall reduction in MCP for all three species in comparison to current values, there is a benefit of achieving a low emission scenario as reductions intensify under the high emission scenario.
+
+```{r GB_Results_Spp, eval = F, echo = F, fig.width=12}
 
 #### Filter Species ####
-
 Atlantic_Species <- c(
@@
 # Filter DBEM results for three specific species within the region of the GoM
-
 N_Lim <- 45.9759
@@
 
+# Limit the area to GoM species
 Atlantic_DBEM <- Raw_DBEM_Results %>% 
   filter(Species %in% Atlantic_Species) %>% 
-  filter( # Limit the area to George's bank
+  filter( 
     Latitude < N_Lim, # North
@@
 
-### MCP Change Analysis ####
-
-#### New analysis ####
-New_Mean_Data_GoM <- Atlantic_DBEM %>% 
+# -------------------- #
+### MCP Change Analysis
+# -------------------- #
+
+Mean_Data_GoM <- Atlantic_DBEM %>% 
   mutate(RCP = ifelse(Model %in% c("GFDL26F1","IPSL26F1","MPI26F1"),"Low Emission","High Emission")) %>%
@@
   mutate(Change = replace_na(Change, 0)) %>% # Convert NA's into 0's
-  mutate(# Indicate the three period times
+  # Indicate the three period times
+  mutate(
     Period = ifelse(Year >= Beg_In & Year <= Beg_End,"Begining",
@@
   filter(Period != "Other_Years") %>% # Remove unwanted years
+  # Temporal mean
   group_by(INDEX,Model,RCP,Period,Species) %>%
   summarise(
-    Mean_Temp = mean(Change, na.rm = T) # Temporal mean
+    Mean_Temp = mean(Change, na.rm = T) 
   ) %>% 
   spread(Period,Mean_Temp) %>%
-  mutate_at(vars(Mid_Century, # Devide future values by present
+  # Divide future values by present
+  mutate_at(vars(Mid_Century, 
                  The_End_Century),
-            funs(ifelse(Begining > 0, ./Begining,.)) #if no species today value is the future
-  ) %>% 
-  mutate_at(vars(Mid_Century, # Estimate percentage change
+            funs(ifelse(Begining > 0, ./Begining,.)) # if no species today value is the future
+  ) %>% 
+  # Estimate percentage change
+  mutate_at(vars(Mid_Century, 
                  The_End_Century),
@@
   mutate(Direction = ifelse(MCP_Chng >= 0, "Positive","Negative")) %>% 
-  group_by(INDEX,Species,Period,RCP) %>% # Average results per ESMs
+  %>% # Average results per ESMs
+  group_by(INDEX,Species,Period,RCP) 
 summarise_at(vars(MCP_Chng),
@@
             funs(ifelse(. > 100, 100,.)
-            )  # set everything over 100 to 100
+            ) 
   ) %>% 
@@
  # Set Bins for better plotting
-  New_Mean_Data_GoM$Bins <- cut(New_Mean_Data_GoM$Mean_ESM_MCP_Chng,breaks = 4)
+ Mean_Data_GoM$Bins <- cut(Mean_Data_GoM$Mean_ESM_MCP_Chng,breaks = 4)
  # unique(New_Mean_Data_GoM$Bins)
 
-# _______________________________________________________
-
-# The plot 
+# -------------------- #
+# Plotting results
+# -------------------- #
 Seq <- seq(-100,100,10)
@@
 
-# New_Mean_Data_GoM <- New_Mean_Data_GoM %>% # In case you want filter a specific species
+# Mean_Data_GoM <- Mean_Data_GoM %>% # In case you want filter a specific species
 #  filter(Species == "Limanda ferruginea",
@@
 
-pgm <- ggplot(New_Mean_Data_GoM) +
-  geom_tile(data = subset(New_Mean_Data_GoM, Period == "Mid_Century"),
+pgm <- ggplot(Mean_Data_GoM) +
+  geom_tile(data = subset(Mean_Data_GoM, Period == "Mid_Century"),
             aes(
@@
   ) +
-  geom_point(data = subset(New_Mean_Data_GoM, Period == "Mid_Century" & Model_Agreement == "Disagree"),
+  geom_point(data = subset(Mean_Data_GoM, Period == "Mid_Century" & Model_Agreement == "Disagree"),
              aes(
@@
 
-  # Name = paste("New_Change_GB_26_85_Mid.png",sep="_")
-Name = "Test.png"
+# Name and save
+Name = paste("Change_GB_26_85_Mid.png",sep="_")
 
@@
 
-```{r Figure_out_outliers, eval =F, echo =F}
-
-Outliers <- c(64310,64311,64312,65028,65029,67180,67181,69344,69345,70066)
-
-Environmental_Data_GoM <- read.csv("~/Documents/UBC/OC_Special_Issue/Ecol/Data/Environ/Environmental_Data_GoM.csv")
-
-Outlier_Species <- c(
-  # "Gadus morhua",  # Cod 600069, Demersal, 600 depth
-  "Limanda ferruginea"#, # Yellowtail flounder 600521, Demersal 82 depth
-  # "Melanogrammus aeglefinus" # Haddock 601381, Demersal 450
-)
-
-N_Lim <- 45.9759
-S_Lim <- 41
-W_Lim <- -72.0592
-E_Lim <- -63.33333
-
-### Averag depth data
-EleAvg <- read.table("~/Documents/UBC/OC_Special_Issue/Ecol/Data/Environ/EleAvg.txt", quote="\"", comment.char="") %>% 
-  mutate(INDEX = seq(1,259200,1)) %>% 
-  rename(Depth = V1) %>% 
-  filter(INDEX %in% Atlantic_EEZsID$INDEX) %>% 
-  left_join(Atlantic_EEZsID, by = "INDEX") %>% 
-  filter( # Limit the area to George's bank
-    Latitude < N_Lim, # North
-    Latitude > S_Lim, # South 
-    Longitude > W_Lim, # West
-    Longitude < E_Lim
-  ) %>% 
-  mutate(
-    Outlier = ifelse(INDEX %in% Outliers,"Yes","No"),
-    Depth = ifelse(Depth <= -800,-800,
-                   ifelse(Depth >=0,0,Depth))
-  )
-
-elev_plot <-
-ggplot(EleAvg) +
-  geom_tile(
-    aes(
-      x = Longitude,
-      y = Latitude,
-      # fill = log10(abs(Depth)),
-      fill = Depth
-    )
-  ) +
-  scale_fill_gradientn( "Depth (m)",
-    colours = terrain.colors(10),
-                       limits=c(-1000,0),
-                       breaks =seq(-1000,0,200)
-  ) +
-  geom_sf(data = GM_Land, colour = "lightgrey") +
-  geom_sf(data = eez_GM, fill = NA) +
-  coord_sf(xlim = c(-71.0592, -63.33333),
-           ylim = c(41,45.5)
-  ) +
-  ggtheme_map() +
-  theme(
-    axis.line = element_line(colour = "black", size = .5),
-    axis.ticks = element_line(size = .5),
-    axis.text.x = element_text(size = 8,
-                               angle = 0,
-                               face = "plain"),
-    axis.text.y = element_text(size = 8),
-    # legend.key = element_rect(size = 3),
-    legend.key.height = unit(2,"line"),
-    legend.title = element_text(size = 10),
-    legend.text = element_text(size = 10),
-    legend.position = "right"
-  )
-
-Name = "Elevation_GoM.png"
-
-ggsave(Name,
-       plot = last_plot(),
-       width = 20,
-       height = 10,
-       units = "in",
-       path = Path)
-
-Specie <- "Limanda ferruginea"
-
-Enviro_chng_gom <- Environmental_Data_GoM %>% 
-  mutate(# Indicate the three period times
-    Period = ifelse(Year >= Beg_In & Year <= Beg_End,"Begining",
-                    ifelse(Year >= Mid_In & Year <= Mid_End,"Mid_Century",
-                           ifelse(Year >= End_In & Year <= End_End,"The_End_Century",
-                                  "Other_Years"))
-    )
-  ) %>% 
-  filter(Period != "Other_Years",
-         Variable == "Temperature") %>% # Remove unwanted years
-  group_by(INDEX,Model,RCP,Period,Variable) %>%
-  summarise(
-    Mean_Temp = mean(Value, na.rm = T) # Temporal mean
-  ) %>% 
-  spread(Period,Mean_Temp) %>% 
-  mutate_at(vars(Mid_Century, # Devide future values by present
-                 The_End_Century),
-            funs(ifelse(Begining > 0, ./Begining,.)) #if no species today value is the future
-  ) %>% 
-  mutate_at(vars(Mid_Century, # Estimate percentage change
-                 The_End_Century),
-            funs(ifelse(Begining == 0 & . == 0, 0, # If for no change than 0
-                        ifelse(Begining == 0 & . > 0, 100, # If changes from 0 to anything then 100
-                               round(-(1-.)*100) # Estimate percentage change
-                        )
-            )
-            )
-  ) %>% 
-  ungroup() %>% 
-  mutate(
-    Outlier = ifelse(INDEX %in% Outliers,"Yes","No"),
-    RCP = ifelse(RCP == "rcp26","Low Emisison","High Emission")
-  ) %>% 
-  group_by(INDEX,RCP,Variable,Outlier) %>% 
-  summarise(
-    Mean_Model = mean(Mid_Century,na.rm=T)
-  ) %>% 
-  left_join(Coor)
-
-temp_plot <- ggplot(Enviro_chng_gom) +
-  geom_tile(
-    aes(
-      x = Longitude,
-      y = Latitude,
-      fill = Mean_Model
-    ),
-    size = 0.5
-  ) +
-  scale_fill_gradientn(paste("Percentage Change of bottom temperature\n                     (",Mid_In,"-",Mid_End,")"), 
-                       limits=c(3,18),
-                       breaks =seq(3,18,3),
-                       colours = terrain.colors(10)
-  ) +
-  geom_sf(data = GM_Land, colour = "lightgrey") +
-  geom_sf(data = eez_GM, fill = NA) +
-  coord_sf(xlim = c(-71.0592, -63.33333),
-           ylim = c(41,45.5)
-           ) +
-  facet_wrap(~RCP) +
-  ggtheme_map() +
-  theme(
-    axis.line = element_line(colour = "black", size = .5),
-    axis.ticks = element_line(size = .5),
-    axis.text.x = element_text(size = 8,
-                               angle = 0,
-                               face = "plain"),
-    axis.text.y = element_text(size = 8),
-    # legend.key = element_rect(size = 3),
-    legend.key.width = unit(2,"line"),
-    legend.title = element_text(size = 10),
-    legend.text = element_text(size = 10)
-  )
-
-Name = "Temp_Cnhg_Mid_GoM.png"
-
-ggsave(Name,
-       plot = last_plot(),
-       width = 6,
-       height = 4,
-       units = "in",
-       path = Path)
-
-###### Elevation and temperature plots
-
-temp_ele <- grid.arrange(elev_plot,temp_plot,
-             ncol = 1)
-
-Name = "Temp_ele_GoM.png"
-
-ggsave(Name,
-       plot = temp_ele,
-       width = 6,
-       height = 6,
-       units = "in",
-       path = Path)
-
-#### Make maps PER model
-
-#### New analysis ####
-Per_Model_Chng_GoM <- Atlantic_DBEM %>% 
-  mutate(RCP = ifelse(Model %in% c("GFDL26F1","IPSL26F1","MPI26F1"),"Low Emission","High Emission")) %>%
-  tidyr::gather("Year","Change",`2005`:`2099`) %>%
-  mutate(Change = replace_na(Change, 0)) %>% # Convert NA's into 0's
-  mutate(# Indicate the three period times
-    Period = ifelse(Year >= Beg_In & Year <= Beg_End,"Begining",
-                    ifelse(Year >= Mid_In & Year <= Mid_End,"Mid_Century",
-                           ifelse(Year >= End_In & Year <= End_End,"The_End_Century",
-                                  "Other_Years"))
-    )
-  ) %>% 
-  filter(Period != "Other_Years",
-         Species %in% Outlier_Species) %>% # Remove unwanted years
-  group_by(INDEX,Model,RCP,Period,Species) %>%
-  summarise(
-    Mean_Temp = mean(Change, na.rm = T) # Temporal mean
-  ) %>% 
-  spread(Period,Mean_Temp) %>% 
-  mutate_at(vars(Mid_Century, # Devide future values by present
-                 The_End_Century),
-            funs(ifelse(Begining > 0, ./Begining,.)) #if no species today value is the future
-  ) %>% 
-  mutate_at(vars(Mid_Century, # Estimate percentage change
-                 The_End_Century),
-            funs(ifelse(Begining == 0 & . == 0, 0, # If for no change than 0
-                        ifelse(Begining == 0 & . > 0, 100, # If changes from 0 to anything then 100
-                               round(-(1-.)*100) # Estimate percentage change
-                        )
-            )
-            )
-  )%>% 
-  mutate(
-    Outlier = ifelse(INDEX %in% Outliers,"Yes","No")
-  ) %>% 
-  left_join(Coor) %>% 
-  mutate_at(vars(Mid_Century,
-                 The_End_Century),
-            funs(ifelse(. > 100, 100,.)
-            )  # set everything over 100 to 100
-  ) #%>% 
-  # filter(Outlier == "Yes")
-
-# plot results  
-ggplot(Per_Model_Chng_GoM) +
-  geom_tile(
-    aes(
-      x = Longitude,
-      y = Latitude,
-      fill = Mid_Century,
-      # fill = log10(abs(Mid_Century)),
-      color = Outlier
-      # fill = Depth
-    ),
-    size = 0.5
-  ) +
-  scale_fill_gradient2(paste("MCP Percentage Change of",Outlier_Species,"\n                     (",Mid_In,"-",Mid_End,")"), # If not using the bins
-                       limits=c(Lim_Neg,
-                                Lim_Max),
-                       breaks = Seq,
-                       na.value = 'darkred' # NA values are present when the species is no more 
-  ) +
-  scale_color_manual(values=c(NA,"yellow")) + # for Bins option A
-  geom_sf(data = GM_Land, colour = "lightgrey") +
-  coord_sf(xlim = c(-71.0592, -63.33333),
-           ylim = c(41,45.5)
-  ) +
-  facet_wrap(~RCP+Model) +
-  ggtheme_map() +
-  theme(legend.key.width =unit(6,"line"))
-
-Name = "MCP_Cnhg_Mid_GoM_Outlier.png"
-
-ggsave(Name,
-       plot = last_plot(),
-       width = 14,
-       height = 10,
-       units = "in",
-       path = Path)
-
-#### Check those outliers in the GFDL
-
-GFDL_Out <- Atlantic_DBEM %>% 
-  filter(Model == "GFDL26F1",
-         Species %in% Outlier_Species,
-         INDEX %in% Outliers) %>%
-  tidyr::gather("Year","Change",`2005`:`2099`) %>%
-  # mutate(Change = replace_na(Change, 0)) %>% # Convert NA's into 0's
-  mutate(# Indicate the three period times
-    Period = ifelse(Year >= Beg_In & Year <= Beg_End,"Begining",
-                    ifelse(Year >= Mid_In & Year <= Mid_End,"Mid_Century",
-                           ifelse(Year >= End_In & Year <= End_End,"The_End_Century",
-                                  "Other_Years"))
-    )
-  ) %>% 
-  filter(Period != "Other_Years") %>% # Remove unwanted years
-  group_by(INDEX,Model,Period,Species) %>%
-  summarise(
-    Mean_Temp = mean(Change, na.rm = T) # Temporal mean
-  ) %>% 
-  spread(Period,Mean_Temp) %>% 
-  mutate(
-    Mid_Chng = ifelse(Begining > 0, Mid_Century/Begining,Mid_Century),
-    End_Chng =ifelse(Begining > 0, The_End_Century/Begining,The_End_Century)
-  ) %>% 
-  mutate_at(vars(Mid_Chng, # Estimate percentage change
-                 End_Chng),
-            funs(ifelse(Begining == 0 & . == 0, 0, # If for no change than 0
-                        ifelse(Begining == 0 & . > 0, 100, # If changes from 0 to anything then 100
-                               round(-(1-.)*100) # Estimate percentage change
-                        )
-            )
-            )
-  )
-
-####Plot Time hisotry o
-
-GFDL_Hist_Out <- Atlantic_DBEM %>% 
-  filter(Model == "GFDL26F1",
-         Species %in% Outlier_Species,
-         INDEX %in% Outliers) %>%
-  tidyr::gather("Year","Change",`2005`:`2099`) %>%
-  # mutate(Change = replace_na(Change, 0)) %>% # Convert NA's into 0's
-  mutate(# Indicate the three period times
-    Period = ifelse(Year >= Beg_In & Year <= Beg_End,"Begining",
-                    ifelse(Year >= Mid_In & Year <= Mid_End,"Mid_Century",
-                           ifelse(Year >= End_In & Year <= End_End,"The_End_Century",
-                                  "Other_Years"))
-    )
-  ) %>% 
-  mutate(Change = replace_na(Change, 0))
-
-ggplot(GFDL_Hist_Out) +
-  geom_line(
-    aes(
-      x = as.numeric(Year),
-      y= Change,
-      color = as.character(INDEX)
-    )
-  ) +
-  facet_wrap(~INDEX)
-
-```
-
 ![Fig 5.
@@
 
-Despite the expected decrease in MCP for the region, changes in the stock-share ratio of species within the Gulf of Maine show different outcomes **RA dependent** on the climate change scenario and species in question.
-Following a high emission path will affect mostly Canada’s share of Y.
-founder and in less degree haddock, with an increase of cod share.
-**RA under the low emission scenario, haddock and cod patterns intensify, while Y.
-founder’s share approaches almost no change (Fig 6).
-Such pattern is likely the combination of the bathymetry or the Gulf, the warming gradient, and the species distribution (see discussion).**
-
-```{r GB_Proportion_Species, eval =F, echo=F}
+Despite the expected decrease in MCP for the region, changes in the stock-share ratio of species within the Gulf of Maine show different outcomes dependent on the climate change scenario and species in question.
+Following a high emission path will affect mostly Canada’s share of yellowtail flounder and in less degree haddock, with an increase of cod share.
+under the low emission scenario, haddock and cod patterns intensify, while yellowtail flounder’s share approaches almost no change (Fig 6).
+Such pattern is likely the combination of the bathymetry or the Gulf, the warming gradient, and the species distribution (see discussion).
+
+```{r GB_Proportion_Species, eval = F, echo = F}
+
 ### Analysis by Species ####
@@
   "Limanda ferruginea", # Yellowtail flounder
-  "Melanogrammus aeglefinus"
+  "Melanogrammus aeglefinus" # haddock 
 )
@@
 
-#### New updated method
-
-New_GoM_Absolutes <- Atlantic_DBEM %>% 
+# ---------------------------- #
+# Estimate GoM proportion change 
+# ---------------------------- #
+
+GoM_Absolutes <- Atlantic_DBEM %>% 
   mutate(RCP = ifelse(Model %in% c("GFDL26F1","IPSL26F1","MPI26F1"),"Low Emission","High Emission")) %>% # Assigns RCP by model
   filter(Species %in% Atlantic_Species,
-         INDEX %in% GB_Coor$INDEX) %>%  #Selects only IPHC species within regulatory areas
+         INDEX %in% GB_Coor$INDEX) %>% #Selects only GoM species within regulatory areas
   left_join(EEZsID,
@@
 
-# Changes in the proportion in comparrison of the mean (2004-2014) proportion ####
-
 # Estimate total MCP of each RCP per year
-New_Proportion_Total <- New_GoM_Absolutes %>% 
+Proportion_Total <- GoM_Absolutes %>% 
  group_by(Species,RCP,Year,Model) %>% 
@@
 
-# Estimates the proportion of each RegArea catch pero RCP and Year
-New_Proportion_GoM <- New_GoM_Absolutes %>% 
-  left_join(New_Proportion_Total,
+# Estimates Proportion cahnge in each region and species
+Proportion_Change_GoM <- GoM_Absolutes %>% 
+  left_join(Proportion_Total,
             by = c("RCP","Year","Model","Species")) %>% 
-  mutate(Proportion = (MCP/Total)*100)
-
-# Proportion change in the future (NOTE: not plotting by timeframe because of boxplot)
-New_Proportion_Change_GoM <- New_Proportion_GoM %>% 
+  mutate(Proportion = (MCP/Total)*100) %>% 
   mutate(Time_Step = ifelse(Year <= Beg_End, "Begining_Prop",
@@
   ) %>% 
-  group_by(Species,
-           RCP,
-           Name,
-           Model,
-           Time_Step) %>% 
+  # Temporal mean
+  group_by(Species, RCP, Name, Model, Time_Step) %>% 
   summarise(Mean_Temp_Prop = mean(Proportion)) %>% 
   spread(Time_Step,Mean_Temp_Prop) %>% 
-  mutate_at(vars(Mid_Century_Prop, # Devide future values by present
+  mutate_at(vars(Mid_Century_Prop, # Divide future values by present
                  The_End_Century_Prop),
@@
   gather("Time_Step","Prop_Change",Mid_Century_Prop,The_End_Century_Prop) %>% 
-  group_by(Species,Name,Time_Step,RCP) %>% # Average results per ESMs
+  # Average results per ESMs
+  group_by(Species,Name,Time_Step,RCP) %>%
   summarise_at(vars(Prop_Change),
@@
 
+# ------------------- #
+# Create and save plot 
+# ------------------- #
+
 # The plot
-ggplot(data = subset(New_Proportion_Change_GoM, Time_Step == "Mid_Century_Prop"),
+ggplot(data = subset(Proportion_Change_GoM, Time_Step == "Mid_Century_Prop"),
        aes(
@@
   geom_bar(stat = "identity") +
-  geom_errorbar(data = subset(New_Proportion_Change_GoM, Time_Step == "Mid_Century_Prop"),
+  geom_errorbar(data = subset(Proportion_Change_GoM, Time_Step == "Mid_Century_Prop"),
                 aes(
@@
                   # x = Species,
-                  ymin=Mean_ESM_MCP_Chng-sd_ESM_MCP_Chng, # mean +- 2*sd
+                  ymin=Mean_ESM_MCP_Chng-sd_ESM_MCP_Chng, # mean +- sd
                   ymax=Mean_ESM_MCP_Chng+sd_ESM_MCP_Chng,
@@
                                    # hjust = 0
-                               ),
-  )
-
- ggsave("New_GoM_Proportion_Mid.png",
-       plot = last_plot(),
+        )
+  ) + 
+  ggsave("GoM_Proportion_Mid.png",
+    plot = .,
     width = 12,
@@
 
-# DISCUSSION
+## DISCUSSION
 
@@
 
-The results of the present study suggest that climate change will alter the MCP of 33 transboundary fish stocks in North America consequently altering Canada’s and the US’s species’ stock-share ratio, regardless of the climate change scenario.
+The results of the present study suggest that climate change would alter the MCP of 33 transboundary fish stocks in North America consequently altering Canada’s and the US’s species’ stock-share ratio, regardless of the climate change scenario.
 These results are aligned with regional [@Morley:2018fn] projections suggesting that climate change will push marine species towards the poles and deeper water [@Pinsky:2013jo] in search of their ecological niche [@Poloczanska:2016kk].
-Poleward shifts in Eastern Atlantic off the coast of the US include American lobster (*Homarus americanus*), summer (*Paralichthys dentatus*) and yellow flounders, and red hake (*Urophycis chuss*) from North Carolina to Maine [@Pinsky:2012kq].
+Poleward shifts in Eastern Atlantic off the coast of the US include American lobster (*Homarus americanus*), summer (*Paralichthys dentatus*) and flounders, and red hake (*Urophycis chuss*) from North Carolina to Maine [@Pinsky:2012kq].
 However, geographic barriers [@Cheung:2015fm; @Kleisner:2016je], local temperature gradients [@Pinsky:2013jo], species interactions and human activities [@Serpetti:2017he] might change the rate and direction of species shifts.
 Species such as haddock in the Atlantic [@Morley:2018fn], and big skate (*Raja binoculata*) in the pacific coast [@Pinsky:2013jo] have been projected to shift away from the poles.
-In the Gulf of Maine, the stock-share gain of Y.
-flounder and haddock by the US (Fig.
-6) could be a response to a temperature gradient shift combined with geographic barriers as southern waters are deeper, and warming slower than northern waters (**Fig A3.1.**).
-In the other hand, Maine has seen its landings of Y.
-founder increased at the expenses of southern states [@Pinsky:2012kq].
+In the Gulf of Maine, the stock-share gain of yellowtail flounder and haddock by the US (Fig.
+6) could be a response to a temperature gradient shift combined with geographic barriers as southern waters are deeper, and warming slower than northern waters (Fig A3.1.).
+On the other hand, Maine has seen its landings of yellowtail flounder increased at the expenses of southern states [@Pinsky:2012kq].
 This could be influencing the US gain in MCP in the GoM in relation to Canada as species shift their distribution from lower latitudes naturally reaching the US (lower) region first.
@@
 
-The shifts in the distribution of transboundary **RB stocks** can jeopardize management objectives such as conservation measures and gear operation.
+The shifts in the distribution of transboundary stocks can jeopardize management objectives such as conservation measures and gear operation.
 Fish moving out of fishing grounds and into protected areas could result in a pressure increase to open such area to fishing.
@@
 In 2015, for example, 97% of the trawl by-catch in areas 4CDE and the Closed Area were juveniles [@IPHC:2017CA].
-Consequently, the Alaskan trawl fisheries has been closed before reaching annual quota due to the attainment of P.
-halibut bycatch quota limits [@Karim:2010ut].
-Thus the comission has been asked to open the closed area for P.
-halibut fishing, under the premise that the expansion of the trawl fishery is likely reducing any conservation goal for juvenile P.
-halibut [@IPHC:2017CA].
-Although not assessed  in this study, some trawling target species like Pacific cod (*Gadus macrocephalus*), flathead sole (*Hippoglossoides elassodon*), and Alaskan plaice (*Limanda aspera*) have already shift their distributions due to warming waters [@Stram:2009xc] and some are expected to continue shifting in similar direction than P.
-halibut [@Pinsky:2013jo].
+Consequently, the Alaskan trawl fisheries has been closed before reaching annual quota due to the attainment of Pacific halibut bycatch quota limits [@Karim:2010ut].
+Thus the commission has been asked to open the closed area for Pacific halibut fishing, under the premise that the expansion of the trawl fishery is likely reducing any conservation goal for juvenile Pacific halibut [@IPHC:2017CA].
+Although not assessed in this study, some trawling target species like Pacific cod (*Gadus macrocephalus*), flathead sole (*Hippoglossoides elassodon*), and Alaskan plaice (*Limanda aspera*) have already shift their distributions due to warming waters [@Stram:2009xc] and some are expected to continue shifting in similar direction than Pacific halibut [@Pinsky:2013jo].
 The overlap of target species could be addressed by applying ecosystem-based management and dynamic management tools [@Hazen:2018fa] to manage these fisheries and reduce potential lost of sustainable harvest for both the halibut and the trawl fisheries.
@@
 adjusting the quota based on the stocks distribution) have the potential of increasing fish biomass, harvest and profits under climate change [@Gaines:2018sg].
-In North America, poleward shifts of P.
-halibut along the coast of Oregon, Washington and British Columbia have been previouslly addressed by the IPHC resulting in the adoption of a dynamic quota allocation method [@McCaughran:1992uw].
-By allocating quotas based on yearly surveys along the Convention area, the IPHC should be able to capture shifts in P.
-halibut distribution due to climate change, reducing the chances of overexploitation of the stock due to this shifts [@Miller:2013iv].
-Similarly, since 2010 GoMA sets weighted quotas based on stocks distribution and historical catch [@TRAC:2016wu].
+In North America, poleward shifts of Pacific halibut along the coast of Oregon, Washington and British Columbia have been previouslly addressed by the IPHC resulting in the adoption of a dynamic quota allocation method [@McCaughran:1992uw].
+By allocating quotas based on yearly surveys along the Convention area, the IPHC should be able to capture shifts in Pacific halibut distribution due to climate change, reducing the chances of overexploitation of the stock due to this shifts [@Miller:2013iv].
+Similarly, for the Gulf of Maine, since the GoMA’s method to estimate quota allocation is weighted based on stocks distribution (90%) and historical catch (10%) [@TRAC:2016wu].
 This process is especially important for cod and haddock due to their distribution variation within the gulf [@Soboil:2006gw; @TRAC:2016wu].
@@
 Side payments have been previously used to address changes in species distribution due to environmental forcings.
-In game theory, a side payment is received by a player as a compensation from the other player in a shared ressource agreement, with the premise that cooperation will result in a better overall outcome [@Bjorndal:2012vd; @Sumaila:2013hv].
-Side payments do not have to be in monetary form and are widely used in transboundary **RB stocks** around the world.
+In game theory, a side payment is received by a player as a compensation from the other player in a shared resource agreement, with the premise that cooperation will result in a better overall outcome [@Bjorndal:2012vd; @Sumaila:2013hv].
+Side payments do not have to be in monetary form and are widely used in transboundary stocks around the world.
 For example, Norway and Russia have implemented a quota swap strategy for jointly managed stocks of cod, haddock and capelin in the Barents Sea [^NR].
@@
 In our results, the "winners and loosers" of climate change, and the intensity of the change, will be scenario dependant.
-For instance, stock-share of Y.
-flounder under a high emission scenario will be larger for the US while Canada's gain of haddock stock-share will be larger under a low emission scenario (Fig.
+For instance, stock-share of yellowtail flounder under a high emission scenario will be larger for the US while Canada's gain of haddock stock-share will be larger under a low emission scenario (Fig.
 6).
 Applying previouslly describe strategies (e.g.
-quota swaps or EEZ-fishing rights) could increase the resilience of treaties by preventing members from leaving the agreement due to a shift in threat points, as happened in the P.
-salmon case [@Miller:2013iv].
+quota swaps or EEZ-fishing rights) could increase the resilience of treaties by preventing members from leaving the agreement due to a shift in threat points, as happened in the Pacific salmon case [@Miller:2013iv].
 
@@
 Overall, results for the Gulf of Maine agree with a reduction in MCP of all three species.
-However, some discrete areas show a positive change for Y.
-flounder by mid $21^{st}$ century (Fig.
-4), mainly driven by the GFDL model (**Fig A3.2**).
+However, some discrete areas show a positive change for yellowtail flounder by mid $21^{st}$ century (Fig.
+4), mainly driven by the GFDL model (Fig A3.2).
 Potential model artifacts could also be contributing to the results, especially in the northern part of the study area (Bay of Fundy) as most disagreeing grids are covered by land, which could be influencing the results.
-In contrast, considerable uncertainty exists in the change of MCP along the IPHC Convention area shown by a disagreement between ESMs (**Fig A3.2**).
+In contrast, considerable uncertainty exists in the change of MCP along the IPHC Convention area shown by a disagreement between ESMs (Fig A3.2).
 Off the coast of British Columbia, increasing temperature trends are consistant among ESMs, however, other processes such as acidification and deoxygenation are still not well understood from British Columbia to the Gulf of Alaska [@TalloniAlvarez:2019gz].
 Moreover, considerable uncertainty exists along the Berring Sea [@Douglas:2010Mb] and Antartic Pacific regarding the extent and intensity of future sea-ice reduction under climate change [@Steiner:2015hc; @IPCC:2019to].
-**RA Structural uncertainty within the DBEM has been previously tested for agreement against commonly used species distribution algorithms such as Maxent [@Phillips:2006ff] and AquaMaps [@Kaschner:2011hi; @Ready:2010wr] resulting in no qualitative differences in trends between algorithms [@Cheung:2016jd].
+Structural uncertainty within the DBEM has been previously tested for agreement against commonly used species distribution algorithms such as Maxent [@Phillips:2006ff] and AquaMaps [@Kaschner:2011hi; @Ready:2010wr] resulting in no qualitative differences in trends between algorithms [@Cheung:2016jd].
 Is worth mentioning that future changes to species distributions could be influenced by factors not captured by our model such as interactions between species [@Pecl:2017hu], adaptation of species to environmental changes, and anthropogenic factors [@Serpetti:2017he].
-However, these factors are expected to increase the rate of range-shifting of the species making our results conservative [@Cheung:2010dt; @Serpetti:2017he].**
-
-# CONCLUSIONS
-
-Shifts in **RB stocks** distribution due to climate change have the potential of creating local extinction of economically important **RB stocks** while enhancing fisheries in areas where they were not present before.
+However, these factors are expected to increase the rate of range-shifting of the species making our results conservative [@Cheung:2010dt; @Serpetti:2017he].
+
+## CONCLUSIONS
+
+Shifts in stocks distribution due to climate change have the potential of creating local extinction of economically important stocks while enhancing fisheries in areas where they were not present before.
 In this paper, we have explored the potential impacts of climate change in the joint management of 33 transboundary stocks managed by Canada and the US.
-We found that, transboundary **RB stocks** are likely to shift in the upcoming years changing the proportion of the catch of jointly managed fisheries of Canada and the US.
+We found that, transboundary stocks are likely to shift in the upcoming years changing the proportion of the catch of jointly managed fisheries of Canada and the US.
 Lessons from other countries can provide solutions to such challenges.
@@
 While not directly addressed in this study, socio-economic impacts of shifting transboundary stocks could add an extra layer of complexity to the problem.
-Addressing shifts in **RB stocks** distribution sooner rather than latter could avert the so called "fish wars", improve sustainability of jointly managed stocks, and secure the livelihood of thousand of families that depend on stocks that move freely between national jurisdictions.
+Addressing shifts in stocks distribution sooner rather than latter could avert the so called “fish wars”, improve sustainability of jointly managed stocks, and secure the livelihood of thousand of families that depend on stocks that move freely between national jurisdictions.
 Finaly, preparing for an uncertain future is key to achieve sustainable fisheries.
 
-# ACKNOWLEDGEMENTS
-
-This is a product of the *OceanCanada* Partnership funded by the Social Sciences and Humanities Research Council of Canada.
-
-# LITERATURE CITED
+<!-- Comented out for thesis -->
+<!-- # ACKNOWLEDGEMENTS -->
+
+<!-- This is a product of the *OceanCanada* Partnership funded by the Social Sciences and Humanities Research Council of Canada. -->
+
+<!-- # LITERATURE CITED -->
+
+# SUPPLEMENTS
+
+<!-- This was included to address the reviewers comments on the region 4D of Pacific Halibut -->
+<!-- NOTE: Remember to run the Results chunk to load all the data needed -->
+
+```{r Functions, eval = F, echo = F}
+
+# This functions extract the information used for each species to project the changes in MCP.
+
+getTaxInfo <- function(TaxNumber,TaxPath=NA, Sal = "NA"){
+
+  # Set automatic path, change if needed
+  TaxPath <- "/Volumes/DATA/JULIANO_NEYMAR/PristineSeasData/Species/TaxonDataC0/"
+
+  # Sets the tac and path 
+  To_Read <- paste(TaxPath,TaxNumber,".txt",sep = "")
+
+  if(Sal == "Y"){
+    Spp_Info <- suppressWarnings(
+      read_table2(To_Read, 
+                  col_names = FALSE, col_types = cols(`0` = col_character(), 
+                                                      X2 = col_number(), X3 = col_number(), 
+                                                      X4 = col_number(), X5 = col_number(), 
+                                                      X6 = col_number()), 
+                  skip = 16)
+    ) 
+    Spp_Info <- Spp_Info[1,2:6]
+  }else{
+    # Reads in file
+    Spp_Info <- suppressMessages(
+      readr::read_delim(To_Read, 
+                        "\t", escape_double = FALSE, col_names = FALSE, 
+                        # col_types = cols(X2 = col_number()),
+                        trim_ws = TRUE)
+    )
+  }
+  return(Spp_Info)
+}
+
+getTTP <- function(TaxNumber,yr,TaxPath=NA){
+
+  # Set automatic path, change if needed
+  TaxPath <- paste("/Volumes/DATA/JULIANO_NEYMAR/PristineSeasData/TPP",yr,"",sep="/")
+
+  # Sets the tac and path 
+  To_Read <- paste(TaxPath,"TPPotp",TaxNumber,".csv",sep = "")
+
+  TPPotp <- read.csv(To_Read)
+
+  return(TPPotp)
+}
+
+getEnvVar=function(yr,ModelRCP,RCP,Variable){
+
+  if(ModelRCP == "IPSL"){
+    ModelRCP = "IPSL-CM5A-MR"
+    Filepath <- paste("/Volumes/DATA/DATA/Environmental data/Model Climate data/CMIP5/txt CMIP5/Reformatted",ModelRCP,RCP,"",sep="/")
+  }
+
+  if(ModelRCP == "MPI"){
+    ModelRCP = "MPI-ESM-MR"
+    Filepath <- paste("/Volumes/DATA/DATA/Environmental data/Model Climate data/CMIP5/txt CMIP5/Reformatted",ModelRCP,RCP,"",sep="/")
+  }
+
+  if(ModelRCP == "GFDL"){
+
+    if(RCP == "rcp26"){
+      ModelRCP <- "GFDL26"
+    }else{
+      ModelRCP <- "GFDL85"
+    }
+    Filepath <- paste("/Volumes/DATA/JULIANO_NEYMAR/PristineSeasData/Climate",ModelRCP,"",sep="/")
+  }
+
+  if(Variable == "Ice"){
+
+    Bottom <- paste("IceExt_",yr,".txt",sep="")
+
+  }
+
+  if(Variable == "Temperature"){
+
+    Bottom = paste("botTemp_",yr,".txt",sep="")
+
+  }
+
+  if(Variable == "Salinity"){
+    # Bottom
+    Bottom = paste("Salinity_btm_",yr,".txt",sep="")
+
+  }
+
+  Read_me <- paste(Filepath,Bottom,sep="")[1]
+  Bottom_Data <- read.csv(Read_me,header=F)
+
+  # Retrun
+
+  getTemp <- Bottom_Data 
+}
+
+```
+
+<!-- # Explore Regions 4d and 4e -->
+
+```{r 4DE_exploration, eval = F, echo = F,message=F, warning=F}
+
+# Exploring why 4D is negative under RCP 2.6 but positive under RCP 8.5
+# This chunk will use functions build for the work to estimate carring capacity (K)
+
+### Exploration at the spatial level
+
+Spatial_4DE <- DBEM_Corrected %>% 
+  mutate(RCP = ifelse(Model %in% c("GFDL26F1","IPSL26F1","MPI26F1"),"RCP 2.6","RCP 8.5")) %>% # Set the RCPs
+  filter(Species == "Hippoglossus stenolepis") %>% 
+  left_join(IPHC_Reg_DBEM_df,
+            by = "INDEX") %>% 
+  filter(RegArea %in% c("4D","4E")) %>%
+   #Sum grid-cells by regulatory area, RCP and Model
+  group_by(RegArea,RCP,Model) %>%
+  summarise_at(vars(`2005`:`2099`), sum,na.rm=T) %>% 
+  tidyr::gather("Year","Total_MCP",`2005`:`2099`) %>% 
+  group_by(RegArea,RCP,Year) %>% 
+  summarise(
+    m=mean(Total_MCP),
+    sd=sd(Total_MCP)
+  )
+
+# ggplot(Spatial_4DE) +
+#  geom_point(
+#   aes(
+#    x = Year,
+#    y = m,
+#    colour = RCP
+#   )
+#  ) +
+#  facet_wrap(~RegArea,
+#        scales = "free")
+
+### Environmental varibales of the region
+
+## Temp
+
+# Variables
+Model = c("GFDL","IPSL","MPI")
+RCP = c("rcp26","rcp85")
+
+Grid <- DBEM_Corrected %>% 
+  select(INDEX) %>% 
+  left_join(IPHC_Reg_DBEM_df,
+            by = "INDEX") %>% 
+  filter(RegArea %in% c("4D","4E")) %>% 
+  select(INDEX)
+
+Variables <- c("Temperature","Salinity","Ice")
+
+F_BData <- NULL 
+F_SData <- NULL 
+F_MData <- NULL # 
+F_RData <- NULL
+Years <- seq(2005,2100,1)
+
+all_Grid <- seq(1,259200,1)
+
+# Embarrasing for loop to get data
+
+for(v in 1:3){
+  # Loop through RCPs
+  for(r in 1:2){
+    # Loop through variables
+    for(m in 1:3){
+      # Loop through years
+      for(y in 1:length(Years)){
+
+        Data <- getEnvVar(yr = Years[y],
+                          Model = Model[m],
+                          Variable = Variables[v],
+                          RCP = RCP[r]
+        ) %>% 
+          mutate(INDEX = all_Grid) %>% 
+          filter(INDEX %in% Grid$INDEX)
+
+        if(y == 1){
+
+          F_BData <- Data[1]
+
+        }else{
+
+          F_BData <- cbind(Data[1],F_BData)
+
+        }
+      }
+
+      colnames(F_BData) <- Years
+
+      F_BData <- F_BData %>% 
+        gather(Year,Value,1:426) %>% 
+        mutate(Model = Model[m],
+               RCP = RCP[r],
+               Variable = Variables[v])
+
+      if(m == 1){
+
+        F_MData <- F_BData
+
+      }else{
+
+        F_MData <- rbind(F_BData,F_MData)
+      }
+    }
+
+    if(r == 1){
+
+      F_RData <- F_MData
+
+    }else{
+
+      F_RData <- rbind(F_RData,F_MData)
+    }
+  }
+
+  if(v == 1){
+
+    F_VData <- F_RData
+
+  }else{
+
+    F_VData <- rbind(F_VData,F_RData)
+  }
+
+} # closes variable loop
+
+write_csv(F_VData,
+     "Environmental_Data_Halibut.csv")
+
+#Load Halibut Species preferences
+Halibut <- getTaxInfo(600514)
+# Demersal
+# HabAssocSal 0 1 1 -1 -1
+# HabAssocIce 0
+
+# Temp
+TTPop <- getTTP(600514,"Avg") %>% 
+  filter(TempPP > 0)
+
+Min_T <- min(TTPop$Temp)
+Max_T <- max(TTPop$Temp)
+
+# Halibut_Temp 2
+# quant05 -2 
+# quant25 0 
+# quant50 2
+# quant75 5
+# quant95 11
+```
+
+```{r halibut_enviro, eval = F, echo = F}
+
+# Read Data
+Environmental_Data_Halibut <- read.csv("~/Documents/UBC/OC_Special_Issue/Ecol/Data/Distribution/Environmental_Data_Halibut.csv")
+
+# Isolate Regions
+DE_Regions <- IPHC_Reg_DBEM_df %>% 
+  filter(RegArea %in% c("4D","4E")) %>% 
+  left_join(Environmental_Data_Halibut,
+            by ="INDEX") %>% 
+  # Average variable per regulatory area
+  group_by(Model,RCP,Variable,Year,RegArea) %>% 
+  summarise(
+    Mean_Reg = mean(Value,na.rm=T)
+  ) %>% 
+  # Model (GCM) average and sd
+  group_by(RCP,Variable,Year,RegArea) %>% 
+  summarise(
+    Mean_GCMs = mean(Mean_Reg,na.rm=T),
+    sd_GCMs = sd(Mean_Reg,na.rm=T)
+  ) %>% 
+  # Running mean of variables
+  group_by(RCP,Variable,RegArea) %>% 
+  mutate(RMean = rollmean(x = Mean_GCMs, 10,
+                          align = "right",
+                          fill = Mean_GCMs),
+         Rsd = rollmean(x = Mean_GCMs, 10,
+                        align = "right",
+                        fill = sd_GCMs)
+  ) %>% 
+  filter(Year >= 2015) %>% 
+  ungroup() %>% 
+  # For plot
+  mutate(
+    RCP = ifelse(RCP == "rcp26","Low Emission","High Emission"),
+    Variable = ifelse(Variable == "Ice","Ice Extension",
+                      ifelse(Variable == "Temperature","Bottom Temperature (ºC)","Bottom Salinity")
+    )
+  )
+
+# Plot figure for supplements
+ggplot(DE_Regions) + 
+  geom_ribbon(aes(
+    x = Year,
+    ymin = RMean - sd_GCMs,
+    ymax = RMean + sd_GCMs,
+    fill = RCP
+  ),
+  alpha = 0.2
+  ) +
+  geom_line(
+    aes(
+      x = Year,
+      y = RMean,
+      colour = RCP
+    )
+  ) +
+  facet_wrap(~RegArea +Variable,
+             scales ="free_x") +
+  ggtheme_plot() +
+  scale_x_continuous(breaks = seq(2010,2100,30),
+                     limits = c(2010,2100)
+  ) +
+  scale_color_manual("Climate Change Scenario",
+                     values=c("red","blue")
+  ) + 
+  scale_fill_manual("Climate Change Scenario",
+                    values=c("red","blue")
+  ) + 
+  ylab("Running Mean (10 yrs)")
+
+ggsave("Environ_Sup.png",
+    plot = last_plot(),
+    width = 10,
+    height =8,
+    units = "in",
+    path = "./Results/Sup"
+    )
+
+```
+
+<!-- # ESM uncertainty -->
+<!-- This chunk explores the uncertainty build in the ESM-DBEM  -->
+
+```{r DBEM_Uncertanty, eval = F, echo = F}
+
+#### DBEM-ESM Uncertanty
+
+Today_Uncertanty <- DBEM_Corrected %>% 
+  filter(Species %in% Selected_Species) %>% 
+  left_join(IPHC_Reg_DBEM_df,
+            by = "INDEX") %>% 
+  filter(!is.na(RegArea)) %>% 
+  mutate(RCP = ifelse(Model %in% RCP,"Low Emission","High Emission")) %>% 
+  gather("Year","MCP",Beg_In:Beg_End) %>% 
+  mutate(Period = ifelse(Year >= Beg_In & Year <= Beg_End,"Begining","NA")) %>% 
+  group_by(RegArea,Model,RCP,Year,Period) %>% 
+  summarise(Regional_MCP =sum(MCP,na.rm=T)) %>% 
+  group_by(RegArea,Model,RCP) %>% 
+  summarise(Today_MCP =mean(Regional_MCP,na.rm=T))
+
+IPHC_MCP_Change_Uncert <- DBEM_Corrected %>% 
+  filter(Species %in% Selected_Species) %>% 
+  left_join(IPHC_Reg_DBEM_df,
+            by = "INDEX") %>% 
+  filter(!is.na(RegArea)) %>% 
+  mutate(RCP = ifelse(Model %in% RCP,"Low Emission","High Emission")) %>% 
+  gather("Year","MCP",Beg_In:End_End) %>%
+  group_by(Model,RCP,Year,RegArea) %>%
+  summarise(Regional_MCP =sum(MCP,na.rm=T)) %>% 
+  group_by(RCP,Model,RegArea) %>% # Running mean as Kleisner & Pauly 2012
+  mutate(RMean = rollmean(x = Regional_MCP, 10,
+                          align = "right",
+                          fill = Regional_MCP)
+  ) %>% 
+  mutate(GCM = ifelse(Model == "GFDL26F1" | Model == "GFDL85F1","GFDL",
+                      ifelse(Model == "IPSL26F1" | Model == "IPSL85F1", "IPSL",
+                             ifelse(Model == "MPI26F1" | Model == "MPI85F1","MPI","NA"
+                             )
+                      )
+  )
+  ) %>% 
+  filter(Year >= 2015) %>% 
+  left_join(Today_Uncertanty,
+            by = c("RegArea","Model","RCP")) %>% 
+  mutate(Index = RMean/Today_MCP)
+
+# Create and save plot
+
+ggplot(IPHC_MCP_Change_Uncert) +
+  geom_line(
+    aes(
+      x = as.numeric(Year),
+      y = Index,
+      color = GCM,
+      linetype = RCP
+    )
+  ) +
+  facet_wrap(~RegArea,
+             scales = "free_y") +
+  labs(
+    x = "Year",
+    y ="Index (Future MCP/Present)"
+  ) +
+  scale_color_manual("Global Circulation model",
+                     values=c("#EEA410","#B53CB9","#2EBC67")
+  ) +
+  scale_x_continuous(breaks = seq(2010,2100,30),
+                     limits = c(2010,2100)
+  ) +
+  ggtheme_plot() +
+  # Save plot
+  ggsave("Model_Uncer_Sup.png",
+         plot = .,
+         width = 12,
+         height =8,
+         units = "in",
+         path = "./Results/Sup"
+  )
+
+```
+
+```{r GoM_Environ_outliers, eval = F, echo = F}
+
+# ------------------ #
+# Make maps PER model
+# ------------------ #
+
+Per_Model_Chng_GoM <- Atlantic_DBEM %>% 
+ mutate(RCP = ifelse(Model %in% c("GFDL26F1","IPSL26F1","MPI26F1"),"Low Emission","High Emission")) %>%
+ tidyr::gather("Year","Change",`2005`:`2099`) %>%
+ mutate(Change = replace_na(Change, 0)) %>% # Convert NA's into 0's
+ # Indicate the three period times
+  mutate(
+  Period = ifelse(Year >= Beg_In & Year <= Beg_End,"Begining",
+          ifelse(Year >= Mid_In & Year <= Mid_End,"Mid_Century",
+              ifelse(Year >= End_In & Year <= End_End,"The_End_Century",
+                 "Other_Years"))
+  )
+ ) %>% 
+ filter(Period != "Other_Years",
+     Species %in% Outlier_Species) %>% # Remove unwanted years
+  # Temporal mean
+ group_by(INDEX,Model,RCP,Period,Species) %>%
+ summarise(
+  Mean_Temp = mean(Change, na.rm = T) 
+ ) %>% 
+ spread(Period,Mean_Temp) %>%
+  # Divide future values by present
+ mutate_at(vars(Mid_Century, 
+         The_End_Century),
+      funs(ifelse(Begining > 0, ./Begining,.)) #if no species today value is the future
+ ) %>% 
+   # Estimate percentage change
+ mutate_at(vars(Mid_Century,
+         The_End_Century),
+      funs(ifelse(Begining == 0 & . == 0, 0, # If for no change than 0
+            ifelse(Begining == 0 & . > 0, 100, # If changes from 0 to anything then 100
+                round(-(1-.)*100) # Estimate percentage change
+            )
+      )
+      )
+ )%>% 
+  # Set Outliers column
+ mutate(
+  Outlier = ifelse(INDEX %in% Outliers,"Yes","No")
+ ) %>% 
+ left_join(Coor) %>% 
+  # set everything over 100 to 100
+ mutate_at(vars(Mid_Century,
+         The_End_Century),
+      funs(ifelse(. > 100, 100,.)
+      ) 
+ ) #%>% 
+ # filter(Outlier == "Yes")
+
+# ----------- #
+# Plot results 
+# ----------- #
+
+ggplot(Per_Model_Chng_GoM) +
+  geom_tile(
+    aes(
+      x = Longitude,
+      y = Latitude,
+      fill = Mid_Century,
+      # fill = log10(abs(Mid_Century)),
+      color = Outlier
+      # fill = Depth
+    ),
+    size = 0.5
+  ) +
+  scale_fill_gradient2(paste("MCP Percentage Change of",Outlier_Species,"\n           (",Mid_In,"-",Mid_End,")"), # If not using the bins
+                       limits=c(Lim_Neg,
+                                Lim_Max),
+                       breaks = Seq,
+                       na.value = 'darkred' # NA values are present when the species is no more 
+  ) +
+  # Mark outliers in yellow
+  scale_color_manual(values=c(NA,"yellow")) + # for Bins option A
+  geom_sf(data = GM_Land, colour = "lightgrey") +
+  coord_sf(xlim = c(-71.0592, -63.33333),
+           ylim = c(41,45.5)
+  ) +
+  facet_wrap(~RCP+Model) +
+  ggtheme_map() +
+  theme(legend.key.width =unit(6,"line"))
+
+# Name and save plot
+
+Name = "MCP_Chng_Mid_GoM_Outlier.png"
+
+ggsave(Name,
+    plot = last_plot(),
+    width = 14,
+    height = 10,
+    units = "in",
+    path = Path)
+
+```
 
@@
 
-  # #Devide one by the other
+ # #Divide one by the other
 
@@
 
-  # Devide future projections by "today's"" projections
+ # Divide future projections by "today's"" projections
 
@@
  spread(Period,Period_MCP) %>% 
-  mutate( # Devides the different timeframes by the present and estimates percentage change
+ mutate( # Divides the different timeframes by the present and estimates percentage change
   Change_End = `End_Century`/Today,
@@
 
-  # #Devide one by the other
+ # #Divide one by the other
  Cell_Index <- sweep(Future[2:86],#Future catch p.
@@
 
+### Stock share ratio (/Table 2)
+
+SS_Changesp <- MCP_Species_Data %>% 
+ group_by(RCP,Species,Period,Model) %>% 
+ summarise(Total_MCP = sum(Mean_T_MCP)) %>% #Estimate todays's total (both EEZs added) MCP for each species 
+ left_join(MCP_Species_Data) %>% # Inlude each nation's MCP
+ mutate(Proportion = (Mean_T_MCP/Total_MCP)*100) %>% # estimates each Country's catch proportion per period
+ select(-Total_MCP,-Basin,-Mean_T_MCP) %>% 
+ group_by(Nation,RCP,Species,Period) %>% #Mean of all species
+ summarise(Mean_Spp_Proportion =mean(Proportion),
+      sd_Spp_Proportion =sd(Proportion)
+ ) %>% #Mean of all ESMs
+ group_by(Nation,RCP,Period) %>% 
+ summarise(Mean_ESM_Proportion = paste(round(mean(Mean_Spp_Proportion),2)," (",round(sd(Mean_Spp_Proportion),2),")",sep="")
+ ) %>% 
+ filter(Period %in% c("Mid_Century","The_End_Century")) %>% 
+ spread(Period,Mean_ESM_Proportion)
+
+```
+
+```{r Figure_out_outliers, eval = F, echo = F}
+
+Outliers <- c(64310,64311,64312,65028,65029,67180,67181,69344,69345,70066)
+
+Environmental_Data_GoM <- read.csv("~/Documents/UBC/OC_Special_Issue/Ecol/Data/Environ/Environmental_Data_GoM.csv")
+
+Outlier_Species <- c(
+ # "Gadus morhua", # Cod 600069, Demersal, 600 depth
+ "Limanda ferruginea"#, # Yellowtail flounder 600521, Demersal 82 depth
+ # "Melanogrammus aeglefinus" # Haddock 601381, Demersal 450
+)
+
+N_Lim <- 45.9759
+S_Lim <- 41
+W_Lim <- -72.0592
+E_Lim <- -63.33333
+
+### Averag depth data
+EleAvg <- read.table("~/Documents/UBC/OC_Special_Issue/Ecol/Data/Environ/EleAvg.txt", quote="\"", comment.char="") %>% 
+ mutate(INDEX = seq(1,259200,1)) %>% 
+ rename(Depth = V1) %>% 
+ filter(INDEX %in% Atlantic_EEZsID$INDEX) %>% 
+ left_join(Atlantic_EEZsID, by = "INDEX") %>% 
+ filter( # Limit the area to George's bank
+  Latitude < N_Lim, # North
+  Latitude > S_Lim, # South 
+  Longitude > W_Lim, # West
+  Longitude < E_Lim
+ ) %>% 
+ mutate(
+  Outlier = ifelse(INDEX %in% Outliers,"Yes","No"),
+  Depth = ifelse(Depth <= -800,-800,
+          ifelse(Depth >=0,0,Depth))
+ )
+
+elev_plot <-
+ggplot(EleAvg) +
+ geom_tile(
+  aes(
+   x = Longitude,
+   y = Latitude,
+   # fill = log10(abs(Depth)),
+   fill = Depth
+  )
+ ) +
+ scale_fill_gradientn( "Depth (m)",
+  colours = terrain.colors(10),
+            limits=c(-1000,0),
+            breaks =seq(-1000,0,200)
+ ) +
+ geom_sf(data = GM_Land, colour = "lightgrey") +
+ geom_sf(data = eez_GM, fill = NA) +
+ coord_sf(xlim = c(-71.0592, -63.33333),
+      ylim = c(41,45.5)
+ ) +
+ ggtheme_map() +
+ theme(
+  axis.line = element_line(colour = "black", size = .5),
+  axis.ticks = element_line(size = .5),
+  axis.text.x = element_text(size = 8,
+                angle = 0,
+                face = "plain"),
+  axis.text.y = element_text(size = 8),
+  # legend.key = element_rect(size = 3),
+  legend.key.height = unit(2,"line"),
+  legend.title = element_text(size = 10),
+  legend.text = element_text(size = 10),
+  legend.position = "right"
+ )
+
+Name = "Elevation_GoM.png"
+
+ggsave(Name,
+    plot = last_plot(),
+    width = 20,
+    height = 10,
+    units = "in",
+    path = Path)
+
+Specie <- "Limanda ferruginea"
+
+Enviro_chng_gom <- Environmental_Data_GoM %>% 
+ mutate(# Indicate the three period times
+  Period = ifelse(Year >= Beg_In & Year <= Beg_End,"Begining",
+          ifelse(Year >= Mid_In & Year <= Mid_End,"Mid_Century",
+              ifelse(Year >= End_In & Year <= End_End,"The_End_Century",
+                 "Other_Years"))
+  )
+ ) %>% 
+ filter(Period != "Other_Years",
+     Variable == "Temperature") %>% # Remove unwanted years
+ group_by(INDEX,Model,RCP,Period,Variable) %>%
+ summarise(
+  Mean_Temp = mean(Value, na.rm = T) # Temporal mean
+ ) %>% 
+ spread(Period,Mean_Temp) %>% 
+ mutate_at(vars(Mid_Century, # Divide future values by present
+         The_End_Century),
+      funs(ifelse(Begining > 0, ./Begining,.)) #if no species today value is the future
+ ) %>% 
+ mutate_at(vars(Mid_Century, # Estimate percentage change
+         The_End_Century),
+      funs(ifelse(Begining == 0 & . == 0, 0, # If for no change than 0
+            ifelse(Begining == 0 & . > 0, 100, # If changes from 0 to anything then 100
+                round(-(1-.)*100) # Estimate percentage change
+            )
+      )
+      )
+ ) %>% 
+ ungroup() %>% 
+ mutate(
+  Outlier = ifelse(INDEX %in% Outliers,"Yes","No"),
+  RCP = ifelse(RCP == "rcp26","Low Emission","High Emission")
+ ) %>% 
+ group_by(INDEX,RCP,Variable,Outlier) %>% 
+ summarise(
+  Mean_Model = mean(Mid_Century,na.rm=T)
+ ) %>% 
+ left_join(Coor)
+
+temp_plot <- ggplot(Enviro_chng_gom) +
+ geom_tile(
+  aes(
+   x = Longitude,
+   y = Latitude,
+   fill = Mean_Model
+  ),
+  size = 0.5
+ ) +
+ scale_fill_gradientn(paste("Percentage Change of bottom temperature\n           (",Mid_In,"-",Mid_End,")"), 
+            limits=c(3,18),
+            breaks =seq(3,18,3),
+            colours = terrain.colors(10)
+ ) +
+ geom_sf(data = GM_Land, colour = "lightgrey") +
+ geom_sf(data = eez_GM, fill = NA) +
+ coord_sf(xlim = c(-71.0592, -63.33333),
+      ylim = c(41,45.5)
+      ) +
+ facet_wrap(~RCP) +
+ ggtheme_map() +
+ theme(
+  axis.line = element_line(colour = "black", size = .5),
+  axis.ticks = element_line(size = .5),
+  axis.text.x = element_text(size = 8,
+                angle = 0,
+                face = "plain"),
+  axis.text.y = element_text(size = 8),
+  # legend.key = element_rect(size = 3),
+  legend.key.width = unit(2,"line"),
+  legend.title = element_text(size = 10),
+  legend.text = element_text(size = 10)
+ )
+
+Name = "Temp_Cnhg_Mid_GoM.png"
+
+ggsave(Name,
+    plot = last_plot(),
+    width = 6,
+    height = 4,
+    units = "in",
+    path = Path)
+
+###### Elevation and temperature plots
+
+temp_ele <- grid.arrange(elev_plot,temp_plot,
+       ncol = 1)
+
+Name = "Temp_ele_GoM.png"
+
+ggsave(Name,
+    plot = temp_ele,
+    width = 6,
+    height = 6,
+    units = "in",
+    path = Path)
+
+#### Make maps PER model
+
+#### New analysis ####
+Per_Model_Chng_GoM <- Atlantic_DBEM %>% 
+ mutate(RCP = ifelse(Model %in% c("GFDL26F1","IPSL26F1","MPI26F1"),"Low Emission","High Emission")) %>%
+ tidyr::gather("Year","Change",`2005`:`2099`) %>%
+ mutate(Change = replace_na(Change, 0)) %>% # Convert NA's into 0's
+ mutate(# Indicate the three period times
+  Period = ifelse(Year >= Beg_In & Year <= Beg_End,"Begining",
+          ifelse(Year >= Mid_In & Year <= Mid_End,"Mid_Century",
+              ifelse(Year >= End_In & Year <= End_End,"The_End_Century",
+                 "Other_Years"))
+  )
+ ) %>% 
+ filter(Period != "Other_Years",
+     Species %in% Outlier_Species) %>% # Remove unwanted years
+ group_by(INDEX,Model,RCP,Period,Species) %>%
+ summarise(
+  Mean_Temp = mean(Change, na.rm = T) # Temporal mean
+ ) %>% 
+ spread(Period,Mean_Temp) %>% 
+ mutate_at(vars(Mid_Century, # Divide future values by present
+         The_End_Century),
+      funs(ifelse(Begining > 0, ./Begining,.)) #if no species today value is the future
+ ) %>% 
+ mutate_at(vars(Mid_Century, # Estimate percentage change
+         The_End_Century),
+      funs(ifelse(Begining == 0 & . == 0, 0, # If for no change than 0
+            ifelse(Begining == 0 & . > 0, 100, # If changes from 0 to anything then 100
+                round(-(1-.)*100) # Estimate percentage change
+            )
+      )
+      )
+ )%>% 
+ mutate(
+  Outlier = ifelse(INDEX %in% Outliers,"Yes","No")
+ ) %>% 
+ left_join(Coor) %>% 
+ mutate_at(vars(Mid_Century,
+         The_End_Century),
+      funs(ifelse(. > 100, 100,.)
+      ) # set everything over 100 to 100
+ ) #%>% 
+ # filter(Outlier == "Yes")
+
+# plot results 
+ggplot(Per_Model_Chng_GoM) +
+ geom_tile(
+  aes(
+   x = Longitude,
+   y = Latitude,
+   fill = Mid_Century,
+   # fill = log10(abs(Mid_Century)),
+   color = Outlier
+   # fill = Depth
+  ),
+  size = 0.5
+ ) +
+ scale_fill_gradient2(paste("MCP Percentage Change of",Outlier_Species,"\n           (",Mid_In,"-",Mid_End,")"), # If not using the bins
+            limits=c(Lim_Neg,
+                Lim_Max),
+            breaks = Seq,
+            na.value = 'darkred' # NA values are present when the species is no more 
+ ) +
+ scale_color_manual(values=c(NA,"yellow")) + # for Bins option A
+ geom_sf(data = GM_Land, colour = "lightgrey") +
+ coord_sf(xlim = c(-71.0592, -63.33333),
+      ylim = c(41,45.5)
+ ) +
+ facet_wrap(~RCP+Model) +
+ ggtheme_map() +
+ theme(legend.key.width =unit(6,"line"))
+
+Name = "MCP_Cnhg_Mid_GoM_Outlier.png"
+
+ggsave(Name,
+    plot = last_plot(),
+    width = 14,
+    height = 10,
+    units = "in",
+    path = Path)
+
+#### Check those outliers in the GFDL
+
+GFDL_Out <- Atlantic_DBEM %>% 
+ filter(Model == "GFDL26F1",
+     Species %in% Outlier_Species,
+     INDEX %in% Outliers) %>%
+ tidyr::gather("Year","Change",`2005`:`2099`) %>%
+ # mutate(Change = replace_na(Change, 0)) %>% # Convert NA's into 0's
+ mutate(# Indicate the three period times
+  Period = ifelse(Year >= Beg_In & Year <= Beg_End,"Begining",
+          ifelse(Year >= Mid_In & Year <= Mid_End,"Mid_Century",
+              ifelse(Year >= End_In & Year <= End_End,"The_End_Century",
+                 "Other_Years"))
+  )
+ ) %>% 
+ filter(Period != "Other_Years") %>% # Remove unwanted years
+ group_by(INDEX,Model,Period,Species) %>%
+ summarise(
+  Mean_Temp = mean(Change, na.rm = T) # Temporal mean
+ ) %>% 
+ spread(Period,Mean_Temp) %>% 
+ mutate(
+  Mid_Chng = ifelse(Begining > 0, Mid_Century/Begining,Mid_Century),
+  End_Chng =ifelse(Begining > 0, The_End_Century/Begining,The_End_Century)
+ ) %>% 
+ mutate_at(vars(Mid_Chng, # Estimate percentage change
+         End_Chng),
+      funs(ifelse(Begining == 0 & . == 0, 0, # If for no change than 0
+            ifelse(Begining == 0 & . > 0, 100, # If changes from 0 to anything then 100
+                round(-(1-.)*100) # Estimate percentage change
+            )
+      )
+      )
+ )
+
+####Plot Time hisotry o
+
+GFDL_Hist_Out <- Atlantic_DBEM %>% 
+ filter(Model == "GFDL26F1",
+     Species %in% Outlier_Species,
+     INDEX %in% Outliers) %>%
+ tidyr::gather("Year","Change",`2005`:`2099`) %>%
+ # mutate(Change = replace_na(Change, 0)) %>% # Convert NA's into 0's
+ mutate(# Indicate the three period times
+  Period = ifelse(Year >= Beg_In & Year <= Beg_End,"Begining",
+          ifelse(Year >= Mid_In & Year <= Mid_End,"Mid_Century",
+              ifelse(Year >= End_In & Year <= End_End,"The_End_Century",
+                 "Other_Years"))
+  )
+ ) %>% 
+ mutate(Change = replace_na(Change, 0))
+
+ggplot(GFDL_Hist_Out) +
+ geom_line(
+  aes(
+   x = as.numeric(Year),
+   y= Change,
+   color = as.character(INDEX)
+  )
+ ) +
+ facet_wrap(~INDEX)
+
 ```
@@
 However, the level of government at which negotiations are held can directly impact management outcomes, as unofficial agreements might lack proper penalties for non-cooperative behavior [@Miller:2013iv].
-**In this sence the GoM agreement covers itself quite well**.
+In this sence the GoM agreement covers itself quite well.
 In one hand, the informal quota allocation method has managed to ease tensions between neighbouring countries, implement a share allocation that addresses shifts in species distributions.
-While in the other hand, the oficial enforcement agreement signed by the goverments of Canada and the US [@GovermentofCanada:l5W8_7Lz] has helped reduce illegal fishing in the border [@Pudden:2007bo].
+While in the other hand, the official enforcement agreement signed by the governments of Canada and the US [@GovermentofCanada:l5W8_7Lz] has helped reduce illegal fishing in the border [@Pudden:2007bo].
 However, despite the quota suggestions under the GoM agreement are done internationally, Canada and the US ultimately set the quota domestically [@Pudden:2007bo].
-In this sence, the agreement might not be resilient to climate-induced shifts members are not binded to any rule.
-Officializing treaties like the case of the Gulf of Maine could provide better ground for the management rules and increase treaty resilience and capacity to adapt to unpredicted changes [@Miller:2013iv].
+In this sence, the agreement might not be resilient to climate-induced shifts members are not bonded to any rule.
+Officiating treaties like the case of the Gulf of Maine could provide better ground for the management rules and increase treaty resilience and capacity to adapt to unpredictable changes [@Miller:2013iv].
 Changes in the distribution of shared stocks have created tension between countries [@Spijkers:2017ij] including Canada and the US in the case of the Pacific salmon [@Miller:2013iv; @Munro:2002uf; @Song:2017va].
@@
 
-<!-- Transboundary fisheries are defined as **RB those fishing** stocks that move freely between (*i*) Countries economic exclusive zones (EEZs) and (*ii*) between EEZs and the high seas (**RB called transboundary stocks**) [@Song:2017iua].
-**RA Game theory is one of the most common approaches used to analyze the management of transboundary stocks, as often, success depends on effective cooperation between parties** [@Munro:2002uf; @Sumaila:2013hv].
-Therefore, in **DV 1982**, the United Nations incentivized actions to cooperate on the management of transboundary **RB stocks** through the Law of the Seas (UNCLOS) [@UnitedNations:1986tl].
+<!-- Transboundary fisheries are defined as those fishing stocks that move freely between (*i*) Countries economic exclusive zones (EEZs) and (*ii*) between EEZs and the high seas ( called transboundary stocks) [@Song:2017iua].
+Game theory is one of the most common approaches used to analyze the management of transboundary stocks, as often, success depends on effective cooperation between parties [@Munro:2002uf; @Sumaila:2013hv].
+Therefore, in DV 1982, the United Nations incentivized actions to cooperate on the management of transboundary stocks through the Law of the Seas (UNCLOS) [@UnitedNations:1986tl].
 -->
@@
 While this is a good way to address climate variation within members of a treaty, it might fall short to address the newcomer issue, a situation that can threaten the sustainability of the stock [@Pinsky:2018cb].
-A combination of the methods employed by PNA with the proper modification to incorporate new fishing nations could help mitigate future conflicts in **RB stocks** like the Pacific halibut.
+A combination of the methods employed by PNA with the proper modification to incorporate new fishing nations could help mitigate future conflicts in stocks like the Pacific halibut.
 Finally, -->
@@
 
-<!-- In the current paper we follow a modeling approach to explore the potential impacts that climate change will have in the management of transboundary **RB stocks** in North America.
+<!-- In the current paper we follow a modeling approach to explore the potential impacts that climate change will have in the management of transboundary stocks in North America.
 Models are attempts to represent reality (in our case a future reality) based on observational data, previously established theory, and future scenarios, and are thus, subjected to different degrees of uncertainty [@Payne:2016gn].

### 2020-04-28 Econ/Econ_Analysis.Rmd
Updated Econ after reviewers

@@
 
-EEZIDs_List <- read_excel("./Econ/Data/Spatial/Updated_EEZList_17June2016.xlsx")
-EEZ_CellID <- read_excel("./Econ/Data/Spatial/EEZ_CellID.xlsx")
+EEZIDs_List <- read_excel("~/Documents/UBC/OC_Special_Issue/Econ/Data/Spatial/Updated_EEZList_17June2016.xlsx")
+EEZ_CellID <- read_excel("~/Documents/UBC/OC_Special_Issue/Econ/Data/Spatial/EEZ_CellID.xlsx")
 colnames(EEZ_CellID) <- c("EEZID","INDEX")
@@
 # DBEM Coordinate system
-Coor <- fread("./Econ/Data/Spatial/Lon_Lat_DBEM.txt",header = FALSE)
+Coor <- fread("~/Documents/UBC/OC_Special_Issue/Econ/Data/Spatial/Lon_Lat_DBEM.txt",header = FALSE)
 colnames(Coor) <- c("INDEX","Longitude","Latitude")
@@
 # From (/Users/jpalacios/Documents/UBC/Oceans_Project/Distribution/By Cell/By_Cell_Analysis.Rmd)
-Raw_DBEM_Results <- data.table::fread("./Ecol/Data/Distribution/Raw_Data.csv") %>% 
+Raw_DBEM_Results <- data.table::fread("~/Documents/UBC/OC_Special_Issue/Ecol/Data/Distribution/Raw_Data.csv") %>% 
   filter(Species != "Anoplopoma fimbria") #Remove
@@
 # Data in metric tonne
-IPHC_Landings <- read_excel("./Econ/Data/IPHC/iphc-19912017-commres.xlsx", 
+IPHC_Landings <- read_excel("./Data_Econ/IPHC/iphc-19912017-commres.xlsx", 
                                     col_types = c("numeric", "text", "text", 
@@
 # 
-GoM_Landings <- read.csv("./Econ/Data/SAU_Landings/GoM/SAU MEOW 55 v47-1.csv")
+GoM_Landings <- read.csv("~/Documents/UBC/OC_Special_Issue/Econ/Data/SAU_Landings/GoM/SAU MEOW 55 v47-1.csv")
 
@@
 
-Fishing_Cost <- read_excel("./Econ/Data/Economic/FishingCost_USA_Canada_20Feb2017.xlsx", 
+Fishing_Cost <- read_excel("~/Documents/UBC/OC_Special_Issue/Econ/Data/Economic/FishingCost_USA_Canada_20Feb2017.xlsx", 
                            col_types = c("text", "text", "text", 
@@
 
-Ex_Vessel <- read.delim("./Econ/Data/Economic/Price_US_Canada_5spp.csv")
+Ex_Vessel <- read.delim("~/Documents/UBC/OC_Special_Issue/Econ/Data/Economic/Price_US_Canada_5spp.csv")
 
@@
        path = "./Econ/Results")
+
+```
+
+# Sensitivity Analysis
+
+## Multiple fishing cost and price
+
+Run the analysis with increses in prices and costs of 5%, 10% and 15%
+
+```{r fishing_cost_price, eval = F, echo = F}
+
+## -------------------- ##
+#  Create sensitivity data
+## -------------------- ##
+
+# random_price <- runif(3,1.05,1.5)
+# [1] A) 1.362173 B) 1.425854 C) 1.061325
+
+# Ex vessel sensitivity prices
+Sen_ex_vessel_data <- Clean_Ex_Vessel %>% 
+  mutate(
+    Level_A = Price_perTon*random_price[1],
+    Level_B = Price_perTon*random_price[2],
+    Level_C = Price_perTon*random_price[3],
+    Original = Price_perTon
+  ) %>% 
+  gather("Level","Sen_Price",Level_A:Original)
+
+# random_cost <- runif(3,1.05,1.5)
+# [1] A) 1.311245 B) 1.427684 c) 1.323787
+
+# Profit sensitivity
+Sen_cost_data <- Clean_Fishing_Cost %>%
+  mutate(
+    Level_A = Cost_perTon_2010*random_cost[1],
+    Level_B = Cost_perTon_2010*random_cost[2],
+    Level_C = Cost_perTon_2010*random_cost[3],
+    Original = Cost_perTon_2010
+  ) %>% 
+  gather("Level","Sen_Cost",Level_A:Original)
+
+## -------------------- ##
+# Estimate Profits 
+## -------------------- ##
+
+Sen_Profit_Data_Weight <- Landings_Data %>% 
+  left_join(Sen_cost_data,
+            by = c("gear_type","EEZ")) %>% # Joins Fishing cost Data
+  left_join(Sen_ex_vessel_data,
+            by = c("Species","EEZ","Level")) %>% 
+  mutate(
+    Sen_Profit = Sen_Price-Sen_Cost
+  )
+
+####___ Landings Data for Paper ####
+# Table 1
+
+Sen_Profit_Data_Paper <- Sen_Profit_Data_Weight %>% 
+  mutate_at(vars(Sen_Cost,Sen_Price,Sen_Profit), # note these are totals and not per tone
+            funs(round((.*Avrg_Landings)/1000000,2)) # million USD
+            ) %>% 
+  group_by(EEZ,Species,Level) %>% 
+  summarise_if(is.numeric,sum,na.rm=T) %>% 
+  filter(Species != "Melanogrammus aeglefinus")
+
+# Project profits
+
+Sen_Projected_Profits <- Sen_Profit_Data_Weight %>%
+  left_join(MCP_Change,
+            by = c("Species","EEZ")
+            ) %>%
+  arrange(Year) %>% # so the bumber of years match the actual year
+  # bind_cols(Years) %>% 
+  mutate(
+    Future_Landings = Avrg_Landings*Prop_Change,
+    Profit = Future_Landings*Sen_Profit,
+    # Discounted_Profit = Profit/(1*(1 +dr)^Years_Dis)
+  ) %>%
+  group_by(Species,EEZ,Model,RCP,Year,Period,Level) %>% # Summ all profits per gear
+  summarise(
+    Non_Discounted_Profits = sum(Profit)#,
+    # Discounted_Profits = sum(Discounted_Profit)
+  ) %>%
+  filter(Period != "Other_Years") %>%
+  ungroup() %>%
+  # group by time period
+  group_by(Species,Model,Period,EEZ,RCP,Level) %>%
+  summarise_if(is.numeric,mean,na.rm=T) %>% 
+  # group by ESM
+  group_by(Species,Period,EEZ,RCP,Level) %>%
+  summarise_if(is.numeric,mean,na.rm=T) %>% 
+  filter(RCP == "High Emission",
+         Period != "Begining",
+         Species != "Melanogrammus aeglefinus") %>% 
+  mutate(
+    Plot_Labels = gsub("_"," ",Level) # just to fix plot
+  )
+
+# Bar graph for sensitivity
+
+ggplot(Sen_Projected_Profits) +
+  geom_bar(
+    aes(
+      x = reorder(Period,desc(Period)),
+      y = Non_Discounted_Profits/1000000,
+      fill = Plot_Labels
+    ),
+    position="dodge",
+    stat = "identity"
+  ) +
+  labs(x = "",
+       y = "Profits (million USD)"
+       ) +
+  # scale_fill_discrete("Scenario",values=)+
+  scale_fill_brewer("Scenario", type='div', palette="Set3") +
+  facet_wrap(~EEZ+Species,
+             scales = "free")
+
+ggsave("sen_econ.png",
+         plot = last_plot(),
+         width = 10,
+         height = 8,
+         units = "in"#,
+         # path = Fig_path_out
+         )
 

### 2020-04-28 Ecol/Manuscript_Draft.Rmd
Updated document to submited R&R

@@
 
-ipak <- function(pkg){
- new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
- if (length(new.pkg)) 
-  install.packages(new.pkg, dependencies = TRUE,repos = "http://cran.us.r-project.org")
- sapply(pkg, require, character.only = TRUE)
-}
+library(MyFunctions)
 
@@
 
-ipak(packages)
+my_lib(packages)
 
@@
 
-ggtheme_plot <- function() {
+my_ggtheme_p() <- function() {
  theme(
@@
 
-ggtheme_map <- function(base_size = 9, Region = "NA") {
+my_ggtheme_m() <- function(base_size = 9, Region = "NA") {
 
@@
 In 1982, the United Nations Law of the Seas (UNCLOS) formalized the concept of economic exclusive zones (EEZs) creating what we know today as shared stocks [@UnitedNations:1986tl], i.e.
-stocks migrate freely between countries EEZs (known as transboundary stocks) or between EEZs and the high seas (also called straddling stocks) [@Song:2017iua].
+stocks migrate between countries EEZs (known as transboundary stocks) or between EEZs and the high seas (also called straddling stocks) [@Song:2017iua].
 Today, an estimated 347 [@Teh:2015gd] to 1500 [@Caddy:1997ue] fish stocks cross national borders, some of them jointly managed by two or more countries.
 These stocks are responsible for almost 50% of these countries total fish catches [@Teh:2015gd].
-While not a law, UNCLOS incentivizes actions to cooperate on the management of shared stocks [@UnitedNations:1986tl].
+While not a law, UNCLOS incentives actions to cooperate on the management of shared stocks [@UnitedNations:1986tl].
 Game theory is one of the most common approaches used to analyze the management of shared stocks, as often, success depends on effective cooperation between parties [@Munro:2002uf; @Sumaila:2013hv].
@@
 
-The shifts in distribution of shared fish stocks will impact the economics of their fisheries [@Pinsky:2012kq; @Sumaila:2019gh]Sumaila et al., this Special Feature), and create international disputes between countries [@Munro:2002uf; @Spijkers:2017ij;@Pinsky:2018cb].
+The shifts in distribution of shared fish stocks will impact the economics of their fisheries [@Pinsky:2012kq; @Sumaila:2019gh]Sumaila et al., this Special Feature), and create international disputes between countries [@Munro:2002uf; @Spijkers:2017ij; @Pinsky:2018cb].
 Canada and the US share important transboundary stocks of salmon (*Oncorhynchus spp.*), Pacific halibut (*Hippoglossus stenolepis*), and Atlantic cod (*Gadus morhua*) offering a unique lens to understand the extent to which climate-induced distributional shifts will challenge the future sustainability of transboundary fisheries.
-These countries have a long history of fisheries cooperation participating in diverse, jointly managed, commercial transboundary stocks through various fisheries management organizations [@Merten:2015tu].
+These countries have a long history of fisheries cooperation participating in diverse, jointly managed, commercial transboundary stocks through various fisheries management organizations [@NOAA:2018tu].
 Furthermore, climate-related fluctuations in stocks' distribution have historically created disputes between Canada and the US, increasing international conflict and threatening the health of diverse transboundary stocks [@Munro:2002uf; @CIA:2017uta].
 
-It is expected that climate induced shifts in stocks' distribution will affect the rules in place that keep international treaties alive.
+It is expected that climate induced shifts in stocks’ distribution will affect the rules in place that keep international treaties alive.
 Therefore, the main objective of this article is to assess the level of exposure that bi-lateral transboundary fisheries treaties between Canada and the US have to climate change through shifts in stock distributions.
@@
 
-The current study focuses on 33 transboundary stocks jointly managed by Canada and the US for both the Atlantic and the Pacific coasts.
-The analysis was carried out within the 200 nautical miles of both nation's EEZ from the Gulf of Mexico to The Labrador Sea in the Atlantic, and from California to Chukchi Sea, in the Pacific coast.
+The current study focuses on 33 transboundary stocks jointly managed by Canada and the US for both the Atlantic and the Pacific coasts (Table A3.1).
+The analysis was carried out within the 200 nautical miles of both nation’s EEZ from the Gulf of Mexico to The Labrador Sea in the Atlantic, and from California to Chukchi Sea, in the Pacific coast.
 The species analyzed (Table A2.1) were selected based on five treaties in both the Atlantic and Pacific coast of North America (Table 1).
-All species under the IPHC, Pacific Salmon Comission, the Pacific Whiting Treaty, and the GoMA arrangement were analyzed as these are bi-lateral agreements.
-However, in the case of Northwest Atlantic Fisheries Organization (NAFO), a subset of 26 species reported was made based on those fished in regions that fall within the EEZs of Canada and the United States (NAFO subareas 2s, 3s with the exception of 3M and 3N and limited to the EEZ, 4s, 5s and 6 A,B, and C) [^NAFO].
-Data related to fisheries was gathered from the Sea Around Us from 1951 to 2014 [@Zeller2016].
+All species under the IPHC, Pacific Salmon Commission, the Pacific Whiting Treaty, and the GoMA arrangement were analyzed as these are bi-lateral agreements.
+However, in the case of Northwest Atlantic Fisheries Organization (NAFO), a subset of 26 species reported was made based on those fished in regions that fall within the EEZs of Canada and the United States (NAFO subareas 2s, 3s with the exception of 3M and 3N and limited to the EEZ, 4s, 5s and 6 A,B, and C).[^NAFO] Data related to fisheries was gathered from the Sea Around Us from 1951 to 2014 [@Zeller2016].
 
@@
 
-```{r Treaties_Table, eval = F, echo = F}
+```{r Treaties_Table, eval = T, echo = F}
 
@@
               "Northwest Atlantic Fisheries Organization (NAFO)",
-              "Gulf of Main's Arrangement (GoM Arrangement)"),
+              "Gulf of Maine's Arrangement (GoMA)"),
             Species =
@@
     colour = "black") +
- ggtheme_map()
+ my_ggtheme_m()()
 
@@
  ) +
- ggtheme_map() +
+ my_ggtheme_m()() +
  scale_fill_manual("Region",
@@
 
-![Fig 1. Map of North America with the regulatory areas of the International Paific Halibut Comission and the NAFO sub-region containing the Gulf of Maine arrangement](./Figures/Fig1.png)
+![Fig 1. Map of North America with the regulatory areas of the International Paific Halibut Comission and the NAFO sub-region containing the Gulf of Maine arrangement](./Figures/Figure 1.png)
 
@@
 
-### The International Pacific Halibut Comission
+### The International Pacific Halibut Commission
 
@@
 The TAC is divided between recreational, subsistence and commercial fishery, with a portion set aside for bycatch of other fisheries [@IPHC:2019wt].
-The commercial fishing season starts in March ending around November whith restrictions allowing only set line gear with J-type hooks targeting individuals over 81.3 cm of total length [@IPHC:2019wt].
+The commercial fishing season starts in March ending around November with restrictions allowing only set line gear with J-type hooks targeting individuals over 81.3 cm of total length [@IPHC:2019wt].
 
@@
 The GoMA suggests catch-limits based on a weighted method were 10% represents the stocks’ historical distribution (from 1967 to 1994) and 90% current distributions produced by quarterly surveys and historical catch [@TRAC:2016wu].
-In 2017, the allocation proposed for the GoMA was, Atlantic cod 80% Canada to 20 % U.S, haddock 41% Canada and 59% U.S and yellowtail flounder 31% Canada and 69% U.S (TRAC 2016).
-However, because this is an unofficial agreement, Canada and the US ultimately take single management decisions (Soboil and Sutinen 2006).
-In terms of management, the US has a multi species harvest control with area and season cloasures, mesh sizes, effort control, and mobile gear vessels that use bottom otter trawl gear [@Soboil:2006gw].
-In contrast, Canada has a quota system in addition to limited-entery licensig, fleet allocations, and mesh and fish size regulation, among other input controls.
+In 2017, the allocation proposed for the GoMA was, Atlantic cod 80% Canada to 20 % U.S, haddock 41% Canada and 59% U.S, and yellowtail flounder 31% Canada and 69% U.S [@TRAC:2016wu].
+However, because this is an unofficial agreement, Canada and the US ultimately take single management decisions [@Soboil:2006gw].
+In terms of management, the US has a multi species harvest control with area and season closures, mesh sizes, effort control, and mobile gear vessels that use bottom otter trawl gear [@Soboil:2006gw].
+In contrast, Canada has a quota system in addition to limited-entry licensing, fleet allocations, and mesh and fish size regulation, among other input controls.
 Canada inshore vessels fish cod with longline and gillnet while haddock is mainly caught with bottom otter trawl gear [@Soboil:2006gw].
@@
 
-The DBEM was projected using three earth system models (ESM), the Geophysical Fluid Dynamics Laboratory Earth System Models 2M (GFDL)[^GFDL], the Institute Pierre Simon Laplace Climate Model 5 (IPSL-CM5)[^IPSL], and the Max Planck Institute for Meteorology Earth System Model (MPI)[^MPI].
+The DBEM was projected using three Earth system models (ESM), the Geophysical Fluid Dynamics Laboratory Earth System Models 2M (GFDL)[^GFDL], the Institute Pierre Simon Laplace Climate Model 5 (IPSL-CM5)[^IPSL], and the Max Planck Institute for Meteorology Earth System Model (MPI)[^MPI].
 Each model was downscaled to match the DBEM $0.5^{\circ}$ x $0.5^{\circ}$ grid using the nearest neighbor method, and in some cases, bilinear interpolation [@Cheung:2016hf].
-Finally, we used the model outputs for two scenarios of the Intergovernmental Panel on Climate Change (IPCC)-Representative Concentration Pathways (RCP) 2.6 and RCP 8.5 representing a low greenhouse gas emission (strong mitigation) and a high greenhouse gas emission (week mitigation) scenario, respectively [@IPCC:2014bz].
-To estimate model robustness and capture the structural uncertanty build within ESM models, we averaged the DBEM results for all three models ($\mu±\sigma$) and marked regions where at least one ESM disagree in direction with the rest.
-
-[^GFDL]: Geophysical Fluid Dynamics Laboratory Earth System Models 2M [online] www.gfdl.noaa.gov
-[^IPSL]:Institute Pierre Simon Laplace Climate Model 5 [online] www.icmc.ipsl.fr/
-[^MPI]: Max Planck Institute for Meteorology Earth System Model [online] www.mpimet.mpg.de/en/science/models/
+Finally, we used the model outputs for two scenarios of the Intergovernmental Panel on Climate Change (IPCC)-Representative Concentration Pathways (RCP) 2.6 and 8.5 representing a low greenhouse gas emission (strong mitigation) and a high greenhouse gas emission (week mitigation) scenario, respectively [@IPCC:2014bz].
+To estimate model robustness and capture the structural uncertainty build within ESM models, we averaged the DBEM results for all three models ($\mu±\sigma$) and marked regions where at least one ESM disagree in direction with the rest.
+
+[^GFDL]: Geophysical Fluid Dynamics Laboratory Earth System Models 2M [online] https://www.gfdl.noaa.gov
+[^IPSL]:Institute Pierre Simon Laplace Climate Model 5 [online] https://www.icmc.ipsl.fr
+[^MPI]: Max Planck Institute for Meteorology Earth System Model [online] https://www.mpimet.mpg.de/en/science/models
 
@@
 where *y* is year, *r* is region, *s* is species, *n* is total number of species, and $\hat{MCP}$ is the MCP averaged by the three ESMs.
-In the case of North America as a whole, and the GoM arrangement, region is defined as the $0.5^{\circ}$ x $0.5^{\circ}$ grid-cell within the EEZ and the specific NAFO regulatory areas, respectiveley.
-For the IPHC analysis, region is defined as the Comission's regulatory areas (Fig.
+In the case of North America as a whole, and the GoM arrangement, region is defined as the $0.5^{\circ}$ x $0.5^{\circ}$ grid-cell within the EEZ and the specific NAFO regulatory areas, respectively.
+For the IPHC analysis, region is defined as the Commission's regulatory areas (Fig.
 1).
@@
 
- where $X_{t}$ is the future averaged MCP for each of the two time periods analized in this study and $t_0$ is the present averaged MCP ($\mu$ `r Beg_In`-`r Beg_End`).
+Where $X_{t}$ is the future averaged MCP for each of the two time periods analyzed in this study and $t_0$ is the present averaged MCP ($\mu$ `r Beg_In`-`r Beg_End`).
 This way, Equ.
@@
 1, to estimate the aggregated yearly mean MCP of each species per region.
-We then average the results by the same previouslly metioned periods (present, mid and end of the $21^{st}$ century).
+We then average the results by the same previously mentioned periods (present, mid and end of the $21^{st}$ century).
 Next, for each species we estimated the stock-share ratio ($\alpha_s$) that each region had during each time period:
@@
 
-where $\theta_{rt}$ is the species' aggregated $\hat{MCP}$ of each region at time period *t*, and $\delta_{rt}$ is the species' aggregated $\hat{MCP}$ of the whole specie's distribution within the study area at the same time period.
+Where $\theta_{rt}$ is the species' aggregated $\hat{MCP}$ of each region at time period *t*, and $\delta_{rt}$ is the species' aggregated $\hat{MCP}$ of the whole specie's distribution within the study area at the same time period.
 Finally, we estimated the percentage change in stock-share ratio substituting $X_{t_0}$ and $X_{t}$ by $\alpha_{t_0}$ and $\alpha_{t}$, respectively in Equ.
@@
 All of the analysis was done in the statistical software *R* version 3.5.2 (2018-12-20) with the associated packages, *data.table* [@Packagedatatable:2019uh], *ggrepel* [@PackageggrepelAut:2018to], *gridExtra* [@PackagegridExtraM:2017wx], *knirt* [@PackageknitrAGen:2020wt], *RColorBrewer* [@PackagerColorBrewer:2014uw], *sf* [@PackagesfSimpleF:2018vp], and *tidyverse* [@PackagetidyverseE:2017vq].
-All code is available at https://github.com/jepa/OC_Transboundary.
+All code is available at http://www.github.com/jepa/OC_Transboundary.
 
@@
   mutate( 
-    Period = ifelse(Year >= Beg_In & Year <= Beg_End,"Begining",
+    Period = ifelse(Year >= Beg_In & Year <= Beg_End,"Beginning",
                     ifelse(Year >= Mid_In & Year <= Mid_End,"Mid_Century",
@@
   breaks = Seq) +
- ggtheme_map()
+ my_ggtheme_m()()
 
@@
 Such changes will be more intense under the high emission scenario (Fig.
-2-A).
-For most regions, losses of MCP will be more intense under a high emission scenario (Fig 2-A) than under a low emission scenario (Fig 2-B), however, there will be no apparent change in gain intensity between scenarios.
-Impacts of cliamte change are expected to intensify towards the end of the $21^{st}$ century, although with greater uncertainty (Fig A1.1).
-
-![Fig 2.
+2A).
+For most regions, losses of MCP will be more intense under a high emission scenario (Fig 2A) than under a low emission scenario (Fig 2B), however, there will be no apparent change in gain intensity between scenarios.
+Impacts of climate change are expected to intensify towards the end of the $21^{st}$ century, although with greater uncertainty (Fig A1.1).
+
+![Fig.
+2.
 Percentage change of MCP of transboundary stocks of North America for mid $21^{st}$ century (2041-2060) relative to present (2005-2014) under a A) high emission scenario and; B) low emission scenario.
-Points represent areas where at least one model do not agree in the direction of change](./Figures/Fig2.png)
+Points represent areas where at least one model do not agree in the direction of change](./Figures/Figure 2.png)
 
@@
   mutate( # Indicate the three period times
-    Period = ifelse(Year >= Beg_In & Year <= Beg_End,"Begining",
+    Period = ifelse(Year >= Beg_In & Year <= Beg_End,"Beginning",
                     ifelse(Year >= Mid_In & Year <= Mid_End,"Mid_Century",
@@
   ) %>% 
-  filter(Period %in% c("Begining","Mid_Century","The_End_Century")) %>% 
+  filter(Period %in% c("Beginning","Mid_Century","The_End_Century")) %>% 
   spread(Period,Mean_ESM_Proportion)
@@
 
-Consequently, each country's share-ratio of different species will change with an overall benefit to northern regions, regardless of the RCP scenario.
+Consequently, each country’s share-ratio of different species will change with an overall benefit to northern regions, regardless of the RCP scenario.
 Overall, shifts will be amplified under the high emission scenario relative to the low greenhouse emission scenario pathway (Table 2).
@@
 Regions 4DE, the most poleward regulatory areas of the IPHC, are expected to gain MCP by mid (Fig.
-3) and end of the $21^st$ century (Fig.
+3) and end of the $21^{st}$ century (Fig.
 A1.2) under a high emission scenario due to the expansion of halibut suitable habitat as sea ice retreats (Fig.
-A3.1).
-In contrast, under a low emission scenario, sea ice is expected to stabilize towards mid $21^st$ century, thus providing less "new" suitable habitat for Pacific halibut and resulting in undetectable changes in MCP for the region (Fig 3.
-B) and decreasing even more towards 2100 (Fig.
+A2.1).
+In contrast, under a low emission scenario, sea ice is expected to stabilize towards mid 21st century, thus providing less “new” suitable habitat for Pacific halibut and resulting in undetectable changes in MCP for the region (Fig.
+3B) and decreasing even more towards 2100 (Fig.
 A1.2).
@@
                        breaks = Seq) +
-  ggtheme_map() +
+  my_ggtheme_m()() +
   theme(
@@
 ![Fig 3.
-Percentage change of MCP for species managed by the IPHC for mid $21^{st}$ century (2041-2060) relative to present 2005-2014 under a A) low emission scenario and B) high emission scenario.
-Labels marked with "*" represent regions where models do not agree in direction of change.](./Figures/Fig3.png)
+Percentage change of MCP for species managed by the IPHC for mid 21st century (2041-2060) relative to present 2005-2014 under a A) high emission scenario and B) low emission scenario.
+Labels marked with "*" represent regions where models do not agree in direction of change](./Figures/Fig3.png)
 
@@
 Proportion_Change <- Proportion_Data %>% 
-  mutate(Time_Step = ifelse(Year <= Beg_End, "Begining_Prop",
+  mutate(Time_Step = ifelse(Year <= Beg_End, "Beginning_Prop",
                             ifelse(Year >= Mid_In & Year <= Mid_End,"Mid_Century_Prop",
@@
   geom_hline(yintercept = 0, linetype = "dashed") +
-  ggtheme_plot() +
+  my_ggtheme_p()() +
   scale_fill_brewer("Region",palette = "Set2") +
@@
 
-![Fig 4.
-Percentage change of stock-share ratio for IPHC under A) low emission scenario and B) high emission scenario for mid $21^{st}$ century (2041-2060) relative to present 2005-2014.
-Values represent the mean of 3 ESM; error bars represent $\mp$ sd.](./Figures/Fig4.png)
-
-### Projected change to species managed under the GoM arrangement
+![Fig.
+4.
+Percentage change of stock-share ratio for IPHC under A) high emission scenario and B) low emission scenario for mid 21st century (2041-2060) relative to present 2005-2014.
+Values represent the mean of 3 ESM; error bars represent $\mp$ sd.](./Figures/Figure 4.png)
+
+### Projected change to species managed under the Gulf of Maine arrangement
 
@@
   mutate(
-    Period = ifelse(Year >= Beg_In & Year <= Beg_End,"Begining",
+    Period = ifelse(Year >= Beg_In & Year <= Beg_End,"Beginning",
                     ifelse(Year >= Mid_In & Year <= Mid_End,"Mid_Century",
@@
   annotate("text", label = "Canada", x = -65.4, y = 44.2, size = 4, colour = "black") +
-  ggtheme_map() +
+  my_ggtheme_m()() +
   theme(
@@
 
-![Fig 5.
-Percentage change of MCP in the Gulf of Maine under, A) high emission scenario; and B) low emission for mid century (2041-2060) relative to present (2005-2014).
-Points represent regions where models do not agree in direction of change.](./Figures/Fig5.png)
+![Fig.
+5.
+Percentage change of MCP in the Gulf of Maine under, A) high emission scenario; and B) low emission for mid-century (2041-2060) relative to present (2005-2014).
+Points represent regions where models do not agree in direction of change.](./Figures/Figure 5.png)
 
@@
 Following a high emission path will affect mostly Canada’s share of yellowtail flounder and in less degree haddock, with an increase of cod share.
-under the low emission scenario, haddock and cod patterns intensify, while yellowtail flounder’s share approaches almost no change (Fig 6).
+under the low emission scenario, haddock and cod patterns intensify, while yellowtail flounder’s share approaches almost no change (Fig.
+6).
 Such pattern is likely the combination of the bathymetry or the Gulf, the warming gradient, and the species distribution (see discussion).
@@
   mutate(Proportion = (MCP/Total)*100) %>% 
-  mutate(Time_Step = ifelse(Year <= Beg_End, "Begining_Prop",
+  mutate(Time_Step = ifelse(Year <= Beg_End, "Beginning_Prop",
                             ifelse(Year >= Mid_In & Year <= Mid_End,"Mid_Century_Prop",
@@
   geom_hline(yintercept = 0, linetype = "dashed") +
-  ggtheme_plot() +
+  my_ggtheme_p() + 
   scale_fill_brewer("Region",palette = "Set2") +
@@
 
-![Fig 6.
-Changes in MCP stock-share ratio for Gulf of Maine under (A) high emission; and (B) low emission scenarios for mid $21^{st}$ century (2041-2060) relative to present.
+![Fig 6.Changes in MCP stock-share ratio for Gulf of Maine under (A) high emission; and (B) low emission scenarios for mid 21st century (2041-2060) relative to present.
 Values represent the mean of 3 ESM; error bars represent $\mp$ sd.
-(2005-2014)](./Figures/Fig6.png)
+(2005-2014).](./Figures/Fig6.png)
 
@@
 However, geographic barriers [@Cheung:2015fm; @Kleisner:2016je], local temperature gradients [@Pinsky:2013jo], species interactions and human activities [@Serpetti:2017he] might change the rate and direction of species shifts.
-Species such as haddock in the Atlantic [@Morley:2018fn], and big skate (*Raja binoculata*) in the pacific coast [@Pinsky:2013jo] have been projected to shift away from the poles.
+Species such as haddock in the Atlantic [@Morley:2018fn], and big skate (*Raja binoculata*) in the Pacific coast [@Pinsky:2013jo] have been projected to shift away from the poles.
 In the Gulf of Maine, the stock-share gain of yellowtail flounder and haddock by the US (Fig.
@@
 On the other hand, Maine has seen its landings of yellowtail flounder increased at the expenses of southern states [@Pinsky:2012kq].
-This could be influencing the US gain in MCP in the GoM in relation to Canada as species shift their distribution from lower latitudes naturally reaching the US (lower) region first.
+This could be influencing the US gain in MCP in the GoMA in relation to Canada as species shift their distribution from lower latitudes naturally reaching the US (lower) region first.
 Geographic barriers also affect the westward increase of stock-share in IPHC regions where species can only migrate northward into the Arctic Ocean through the Bering Sea and Bering Strait [@Cheung:2015fm] (Fig.
@@
 Moreover, overlapping shifting stocks could interfere in gear-limitation management rules of multiple fisheries generating conflicts between fleets [@VanDerVoo:2016uc].
-The effectiveness of the IPHC-Closed Area ("CA" in Fig 1.) in tems of protecting juveniles has been historically questioned as trawling for other species is still allowed in the area [@Karim:2010ut; @IPHC:2017CA].
+The effectiveness of the IPHC-Closed Area ("CA" in Fig 1.) in terms of protecting juveniles has been historically questioned as trawling for other species is still allowed in the area [@Karim:2010ut; @IPHC:2017CA].
 In 2015, for example, 97% of the trawl by-catch in areas 4CDE and the Closed Area were juveniles [@IPHC:2017CA].
@@
 However, climate change has shifted the distribution of multiple European commercial stocks [@Baudron:2020dj], outdating the fixed quotas and thus compromising the sustainability of European fisheries [@FAO:2018uv; @Baudron:2020dj].
-Management regimes that inclued a dynamic harvest control (e.g.
+Management regimes that include a dynamic harvest control (e.g.
 adjusting the quota based on the stocks distribution) have the potential of increasing fish biomass, harvest and profits under climate change [@Gaines:2018sg].
-In North America, poleward shifts of Pacific halibut along the coast of Oregon, Washington and British Columbia have been previouslly addressed by the IPHC resulting in the adoption of a dynamic quota allocation method [@McCaughran:1992uw].
-By allocating quotas based on yearly surveys along the Convention area, the IPHC should be able to capture shifts in Pacific halibut distribution due to climate change, reducing the chances of overexploitation of the stock due to this shifts [@Miller:2013iv].
+In North America, poleward shifts of Pacific halibut along the coast of Oregon, Washington and British Columbia have been previously addressed by the IPHC resulting in the adoption of a dynamic quota allocation method [@McCaughran:1992uw].
+By allocating quotas based on yearly surveys along the Convention area, the IPHC should be able to capture shifts in Pacific halibut distribution due to climate change, reducing the chances of over exploitation of the stock due to this shifts [@Miller:2013iv].
 Similarly, for the Gulf of Maine, since the GoMA’s method to estimate quota allocation is weighted based on stocks distribution (90%) and historical catch (10%) [@TRAC:2016wu].
-This process is especially important for cod and haddock due to their distribution variation within the gulf [@Soboil:2006gw; @TRAC:2016wu].
+This process is especially important for cod and haddock due to their distribution variation within the Gulf [@Soboil:2006gw; @TRAC:2016wu].
 
@@
 For example, Norway and Russia have implemented a quota swap strategy for jointly managed stocks of cod, haddock and capelin in the Barents Sea [^NR].
-Similarly, species' quota swaps are permited, up to a degree, within regulatory areas of the European union [@Baudron:2020dj].
+Similarly, species' quota swaps are allowed, up to a degree, within regulatory areas of the European union [@Baudron:2020dj].
 Specifically, for northern European spring spawning Herring (*Clupea harengus*), Norway, Iceland, Faroe Islands, Russia and the EU reached an agreement to manage the stock after its collapsed, partially due to climate variations [@Miller:2013iv].
-Among the implemented rules, the agreement sets a dynamic quota allocation, allows memebers to fish part of their quota within Norway's EEZ, and land the catch in Norwegian ports.
-In North America, Canada and the US have previous history with the utilization of side payments when in the 70's Pacific Salmon shifted its distribution resulting in large interceptions of Canada's salmon by Alaskan fisheries [@Miller:2013iv].
+Among the implemented rules, the agreement sets a dynamic quota allocation, allows members to fish part of their quota within Norway's EEZ, and land the catch in Norwegian ports.
+In North America, Canada and the US have previous history of applying side payments when in the 70's Pacific salmon shifted its distribution resulting in large interceptions of Canada's salmon by Alaskan fisheries [@Miller:2013iv].
 The conflict was resolved by the implementation of a conservation fund that work as a side payment for both Canada and the state of Alaska [@Miller:2013iv].
@@
 
-[^NR]: Joint Fish, joint Russian-Norwegian Fisheries Comission available at http://www.jointfish.com/eng/THE-FISHERIES-COMMISSION/HISTORY.html
-
-Transboundary fisheries management have to be prepared for the uncertanty that comes with a changing world.
+[^NR]: Joint Fish, joint Russian-Norwegian Fisheries Commission available at http://www.jointfish.com/eng/THE-FISHERIES-COMMISSION/HISTORY.html
+
+Transboundary fisheries management have to be prepared for the uncertainty that comes with a changing world.
 Future climate change will depend on the path society as a whole will take, and thus we rely on scenario planning to account for the uncertainty build in future decision making [@vanVuuren:2011ef].
-In our results, the "winners and loosers" of climate change, and the intensity of the change, will be scenario dependant.
+In our results, the "winners and losers" of climate change, and the intensity of the change, will be scenario dependent.
 For instance, stock-share of yellowtail flounder under a high emission scenario will be larger for the US while Canada's gain of haddock stock-share will be larger under a low emission scenario (Fig.
 6).
-Applying previouslly describe strategies (e.g.
+Applying previously describe strategies (e.g.
 quota swaps or EEZ-fishing rights) could increase the resilience of treaties by preventing members from leaving the agreement due to a shift in threat points, as happened in the Pacific salmon case [@Miller:2013iv].
@@
 Models are attempts to represent reality (in our case a future reality) based on observational data, previously established theory, and future scenarios, and are thus, subjected to different degrees of uncertainty [@Payne:2016gn].
-An ensamble or models is a way to present a more robust result that accounts for differnces in the structural composition of each model [@Cheung:2016gv].
+An ensemble of models is a way to present a more robust result that accounts for differences in the structural composition of each model [@Cheung:2016gv].).
 In here we used three ESMs to project future changes in species maximum catch potential.
@@
 However, some discrete areas show a positive change for yellowtail flounder by mid $21^{st}$ century (Fig.
-4), mainly driven by the GFDL model (Fig A3.2).
+4), mainly driven by the GFDL model (Fig.
+A2.3).
 Potential model artifacts could also be contributing to the results, especially in the northern part of the study area (Bay of Fundy) as most disagreeing grids are covered by land, which could be influencing the results.
-In contrast, considerable uncertainty exists in the change of MCP along the IPHC Convention area shown by a disagreement between ESMs (Fig A3.2).
-Off the coast of British Columbia, increasing temperature trends are consistant among ESMs, however, other processes such as acidification and deoxygenation are still not well understood from British Columbia to the Gulf of Alaska [@TalloniAlvarez:2019gz].
-Moreover, considerable uncertainty exists along the Berring Sea [@Douglas:2010Mb] and Antartic Pacific regarding the extent and intensity of future sea-ice reduction under climate change [@Steiner:2015hc; @IPCC:2019to].
-Structural uncertainty within the DBEM has been previously tested for agreement against commonly used species distribution algorithms such as Maxent [@Phillips:2006ff] and AquaMaps [@Kaschner:2011hi; @Ready:2010wr] resulting in no qualitative differences in trends between algorithms [@Cheung:2016jd].
-Is worth mentioning that future changes to species distributions could be influenced by factors not captured by our model such as interactions between species [@Pecl:2017hu], adaptation of species to environmental changes, and anthropogenic factors [@Serpetti:2017he].
+In contrast, considerable uncertainty exists in the change of MCP along the IPHC Convention area shown by a disagreement between ESMs (Fig.
+A2.4).
+Off the coast of British Columbia, increasing temperature trends are consistent among ESMs, however, other processes such as acidification and deoxygenation are still not well understood from British Columbia to the Gulf of Alaska  [@TalloniAlvarez:2019gz].
+Moreover, considerable uncertainty exists along the Bering Sea [@Douglas:2010Mb] and Antarctic Pacific regarding the extent and intensity of future sea-ice reduction under climate change [@Steiner:2015hc; @IPCC:2019to].
+Regarding the DBEM, its structural uncertainty has been previously tested for agreement against commonly used species distribution algorithms such as Maxent [@Phillips:2006ff] and AquaMaps [@Kaschner:2011hi; @Ready:2010wr] resulting in no qualitative differences in trends between algorithms [@Cheung:2016jd].
+Finally, is worth mentioning that future changes to species distributions could be influenced by factors not captured by our model such as interactions between species [@Pecl:2017hu], adaptation of species to environmental changes, and anthropogenic factors [@Serpetti:2017he].
 However, these factors are expected to increase the rate of range-shifting of the species making our results conservative [@Cheung:2010dt; @Serpetti:2017he].
@@
 While not directly addressed in this study, socio-economic impacts of shifting transboundary stocks could add an extra layer of complexity to the problem.
-Addressing shifts in stocks distribution sooner rather than latter could avert the so called “fish wars”, improve sustainability of jointly managed stocks, and secure the livelihood of thousand of families that depend on stocks that move freely between national jurisdictions.
-Finaly, preparing for an uncertain future is key to achieve sustainable fisheries.
+Addressing shifts in stocks distribution sooner rather than latter could avert the so called “fish wars”, improve sustainability of jointly managed stocks, and secure the livelihood of thousands of families that depend on stocks that move freely between national jurisdictions.
+Finally, preparing for an uncertain future is key to achieve sustainable fisheries.
 
@@
              scales ="free_x") +
-  ggtheme_plot() +
+  my_ggtheme_p()() +
   scale_x_continuous(breaks = seq(2010,2100,30),
@@
   gather("Year","MCP",Beg_In:Beg_End) %>% 
-  mutate(Period = ifelse(Year >= Beg_In & Year <= Beg_End,"Begining","NA")) %>% 
+  mutate(Period = ifelse(Year >= Beg_In & Year <= Beg_End,"Beginning","NA")) %>% 
   group_by(RegArea,Model,RCP,Year,Period) %>% 
@@
   ) +
-  ggtheme_plot() +
+  my_ggtheme_p()() +
   # Save plot
@@
   mutate(
-  Period = ifelse(Year >= Beg_In & Year <= Beg_End,"Begining",
+  Period = ifelse(Year >= Beg_In & Year <= Beg_End,"Beginning",
           ifelse(Year >= Mid_In & Year <= Mid_End,"Mid_Century",
@@
   facet_wrap(~RCP+Model) +
-  ggtheme_map() +
+  my_ggtheme_m()() +
   theme(legend.key.width =unit(6,"line"))
@@
    breaks = Seq) +
-  ggtheme_map()
+  my_ggtheme_m()()
 
@@
  geom_hline(yintercept = 0, linetype = "dashed") +
- ggtheme_plot() +
+ my_ggtheme_p()() +
  # scale_fill_brewer("Region",palette = "Set2") +
@@
  geom_boxplot() +
- ggtheme_plot() +
+ my_ggtheme_p()() +
  ylab("") +
@@
  geom_hline(yintercept = 0, linetype = "dashed") +
- ggtheme_plot() +
+ my_ggtheme_p()() +
  # scale_fill_brewer("Region",palette = "Set2",guide=FALSE) + 
@@
  ) +
- ggtheme_map() +
+ my_ggtheme_m()() +
  theme(
@@
   ) +
-  ggtheme_map() +
+  my_ggtheme_m()() +
   theme(
@@
  geom_hline(yintercept = 0, linetype = "dashed") +
- ggtheme_plot() +
+ my_ggtheme_p()() +
   ylim(-10, 10) +
@@
  geom_hline(yintercept = 0, linetype = "dashed") +
- ggtheme_plot() +
+ my_ggtheme_p()() +
  theme(
@@
  mutate(# Indicate the three period times
-  Period = ifelse(Year >= Beg_In & Year <= Beg_End,"Begining",
+  Period = ifelse(Year >= Beg_In & Year <= Beg_End,"Beginning",
           ifelse(Year >= Mid_In & Year <= Mid_End,"Mid_Century",
@@
  facet_wrap(~RCP) +
- ggtheme_map() +
+ my_ggtheme_m()() +
  theme(
@@
  facet_wrap(~RCP+Model) +
- ggtheme_map() +
+ my_ggtheme_m()() +
  theme(legend.key.width =unit(6,"line"))

### 2020-04-29 Ecol/Manuscript_Draft.Rmd
Update paths

@@
 
-# source("/Users/jpalacios/Documents/UBC/Oceans_Project/Distribution/Functions/DBEM_imp_F.R") #Imports a single species
-
-my_ggtheme_p() <- function() {
- theme(
-  plot.title = element_text(size = rel(1), hjust = 0, face = "bold"),
-  panel.background = element_blank(),
-  strip.background = element_blank(),
-  # strip.text    = element_text(size = base_size, face = "italic"),
-  panel.border   = element_blank(),
-  panel.grid.minor = element_blank(),
-  panel.grid.major = element_blank(),
-  axis.ticks = element_blank(),
-  axis.text.x = element_text(size = 14,
-                angle = 0,
-                face = "plain"),
-  axis.text.y = element_text(size = 14),
-  axis.title = element_text(size = 14),
-  legend.key = element_rect(colour = NA, fill = NA),
-  legend.position = "top",
-  legend.title = element_text(size = 16),
-  legend.text = element_text(size = 14),
-  strip.text.x = element_text(size = 10, colour = "black"),
-  strip.text = element_text(size = 18)
- )
-}
-
-my_ggtheme_m() <- function(base_size = 9, Region = "NA") {
-
- theme(text       = element_text(#family = "Helvetica",
-  color = "gray30", size = base_size),
-  plot.title    = element_text(size = rel(1.25), hjust = 0, face = "bold"),
-  panel.background = element_blank(),
-  panel.border   = element_blank(),
-  panel.grid.minor = element_blank(),
-  panel.grid.major = element_line(color = "transparent"),
-  strip.background =element_rect(fill = "transparent"),
-  strip.text.x = element_text(size = 18, colour = "black",face= "bold.italic", angle = 0),
-  axis.line    = element_blank(), # element_line(colour = "grey30", size = .5))
-  axis.ticks    = element_blank(),
-  axis.text    = element_blank(),
-  axis.title    = element_blank(),
-  # legend.key    = element_rect(colour = NA, fill = NA, size = 4),
-  legend.position = "bottom"#,
-  # legend.key.width =unit(6,"line")
- )
-}
-
  # Current time
@@
 End_End <- paste(2099);End_End
-
-Data_Path <- "~/Documents/UBC/OC_Special_Issue/Ecol/Data"
-
 ```
@@
 Canada and the US share important transboundary stocks of salmon (*Oncorhynchus spp.*), Pacific halibut (*Hippoglossus stenolepis*), and Atlantic cod (*Gadus morhua*) offering a unique lens to understand the extent to which climate-induced distributional shifts will challenge the future sustainability of transboundary fisheries.
-These countries have a long history of fisheries cooperation participating in diverse, jointly managed, commercial transboundary stocks through various fisheries management organizations [@NOAA:2018tu].
+These countries have a long history of fisheries cooperation participating in diverse, jointly managed, commercial transboundary stocks through various fisheries management organizations [@NOAA:218tu].
 Furthermore, climate-related fluctuations in stocks' distribution have historically created disputes between Canada and the US, increasing international conflict and threatening the health of diverse transboundary stocks [@Munro:2002uf; @CIA:2017uta].
@@
 ### North America Initial Map ####
-
-path_world <- "~/Documents/Github/Oceana_LA/international/information/raw_databases/Spatial/TM_WORLD_BORDERS-0.3"
+path_world <- my_path("G",Extra_Path = "Spatial/TM_WORLD_BORDERS-0.3")
 file_name <- "TM_WORLD_BORDERS"
@@
 ### North America EEZs Map ####
-
-path_eez <- ("/Users/jpalacios/Documents/R CODE/Spatial_Analysis/Data/World_EEZ_v10_2018")
+path_eez <- my_path("G",Extra_Path = "Spatial/World_EEZ_v10_2018-0.3")
 #The File
@@
 
-path_IPHC <- ("/Users/jpalacios/Documents/UBC/Oceans_Project/Distribution/Data/IPHC/IPHC_RegulatoryAreas/")
+path_IPHC <- my_path("D",Extra_Path = "IPHC/IPHC_RegulatoryAreas/")
 
@@
 
-path_NAFO <- ("/Users/jpalacios/Documents/UBC/Oceans_Project/Distribution/Data/Spatial/NAFO")
+path_NAFO <- paste(Data_path,"Spatial/NAFO")
 #The File
@@
 
-Path_Save <- "/Users/jpalacios/Documents/UBC/Oceans_Project/Manuscript/Results/Others/"
-
 ggsave("Fig1_NA.png",
@@
     units = "in",
-    path = Path_Save)
+    path = Results_Path)
 
@@
     units = "in",
-    path = Path_Save)
+    path = my_path("R"))
 
@@
 #Data provided by Vicki Lam
-EEZIDs_List <- read_excel(paste(Data_Path,"/Spatial/Updated_EEZList_17June2016.xlsx",sep=""))
-EEZ_CellID <- read_excel(paste(Data_Path,"/Spatial/EEZ_CellID.xlsx",sep=""))
+EEZIDs_List <- my_path("G",Extra_Path = "Spatial/DBEM",Name="Updated_EEZList_17June2016.xlsx",Read = TRUE)
+
+EEZ_CellID <- my_path("G",Extra_Path = "Spatial/DBEM",Name="EEZ_CellID.xlsx",Read = TRUE)
 colnames(EEZ_CellID) <- c("EEZID","INDEX")
@@
 # DBEM Coordinate system
-Coor <- fread(paste(Data_Path,"/Spatial/Lon_Lat_DBEM.txt",sep=""),header = FALSE)
+Coor <- my_path("G",Extra_Path = "Spatial/DBEM", Name = "Lon_Lat_DBEM.txt", Read = TRUE)
 colnames(Coor) <- c("INDEX","Longitude","Latitude")
@@
 
-path_world <- paste(Data_Path,"/Spatial/TM_WORLD_BORDERS",sep="")
+path_world <- my_path("D",Extra_Path = "Spatial/TM_WORLD_BORDERS")
 file_name <- "TM_WORLD_BORDERS"
@@
 
-path_eez <- paste(Data_Path,"/Spatial/World_EEZ_v10_2018",sep="")
+path_eez <- my_path("D",Extra_Path = "Spatial/World_EEZ_v10_2018")
 #The File
@@
 # Now we load IPHC shapefiles ####
-path_IPHC <- paste(Data_Path,"/Spatial/IPHC_RegulatoryAreas/",sep="")
-
+path_IPHC <- my_path("D",Extra_Path = "Spatial/IPHC_RegulatoryAreas")
 # The Canada file
@@
 # Species data (Names, treaties, etc)
-# DBEM exploited species list 
+# DBEM exploited species list (ONLY ON DROBO)
 exploited_species_list <- fread("/Volumes/DATA/PROJECTION exploited species ENM/exploited_species_list.csv")
@@
 # IPHC and GB species
-Selected_Species <- fread("~/Documents/UBC/Oceans_Project/Distribution/By Cell/Cell_Data/List_Species.csv")
+Selected_Species <- fread(paste(Data_Path,"Species/List_Species.csv",sep=""))
 
@@
 # This is the subset of species Fished on canada and US waters of all NAFO's species list
-NAFO_Species <- read.csv("~/Documents/UBC/Oceans_Project/Distribution/DBEM/Data/NAFO_Species.csv") %>%
+NAFO_Species <- read.csv(paste(Data_Path,"Species/NAFO_Species.csv",sep="")) %>%
  mutate(Treaty = "NAFO")
@@
 ```{r DBEM_Data_For_All, eval = F, echo = F, warning = F, message = F}
+
+#-------------------- NOTE --------------------#
+# Chunk to be ran in Hall100 connected to DROBO
+#---------------------------------------------#
 
@@
 #Data provided by Vicki Lam
-EEZIDs_List <- read_excel(paste(Data_Path,"/Spatial/Updated_EEZList_17June2016.xlsx",sep=""))
-EEZ_CellID <- read_excel(paste(Data_Path,"/Spatial/EEZ_CellID.xlsx",sep=""))
+EEZIDs_List <- read_excel(paste(my_path("G",Extra_Path = "Spatial/DBEM"),"Updated_EEZList_17June2016.xlsx",sep=""))
+
+x <- paste(my_path("G",Extra_Path = "Spatial/DBEM"),"Updated_EEZList_17June2016.xlsx",sep="")
+
+str_detect(x,".xlsx")
+
+EEZ_CellID <- read_excel(paste(my_path("G",Extra_Path = "Spatial/DBEM"),"EEZ_CellID.xlsx",sep=""))
 colnames(EEZ_CellID) <- c("EEZID","INDEX")
@@
 # DBEM Coordinate system
-Coor <- fread(paste(Data_Path,"/Spatial/Lon_Lat_DBEM.txt",sep=""),header = FALSE)
+Coor <- my_path("G",Extra_Path = "Spatial/DBEM", Name = "Lon_Lat_DBEM.txt", Read = TRUE)
 colnames(Coor) <- c("INDEX","Longitude","Latitude")
 
-# From (/Users/jpalacios/Documents/UBC/Oceans_Project/Distribution/By Cell/By_Cell_Analysis.Rmd)
-Raw_DBEM_Results <- data.table::fread(paste(Data_Path,"/Distribution/Raw_Data.csv",sep="")) %>% 
+# Raw DBEM results
+Raw_DBEM_Results <- my_path("D",Extra_Path = "Ecol/Distribution", Name = "Raw_Data.csv", Read = TRUE)
+
+%>% 
  filter(Species != "Anoplopoma fimbria") #Remove
@@
 # Path to save the plots
-Path <- "./Results/North_America"
+Path <- my_path("R",Extra_Path = "North_America")
 RCP = c("GFDL26F1","IPSL26F1","MPI26F1") #Low RCP
@@
 # Path to save the plots
-Path <- "~/Documents/UBC/Oceans_Project/Manuscript/Results/North_America"
+Path <- my_path("R",Extra_Path = "North_America")
 RCP = c("GFDL26F1","IPSL26F1","MPI26F1") #Low RCP
@@
 
+Path <- my_path("R",Extra_Path = "North_America")
+
 #For paper (Table 2)
 write.csv(SS_Change,
-     "./Ecology/Results/North_America/SS_Change.csv",
+     paste(Path,"SS_Change.csv",sep=""),
      row.names = F)
@@
 # Path for saving plots
-Path <- "./Results/IPHC"
+Path <- my_path("R",Extra_Path = "IPHC")
 RCP = c("GFDL26F1","IPSL26F1","MPI26F1") #Low RCP
@@
 
-img <- readPNG("/Users/jpalacios/Documents/UBC/Oceans_Project/Manuscript/Results/Fig3.png")
+img <- readPNG(paste(my_path("F"),"Figure 3.png",sep=""))
 grid.raster(img)
@@
 # Set saving path
-Path <- "./Manuscript/Results/IPHC/Proportion"
-
+Path <- my_path("R",Extra_Path = "IPHC/Proportion")
 IPHC_Species <- c("Hippoglossus stenolepis") # Halibut
@@
 
-Fig4 <- readPNG("~/Documents/UBC/Oceans_Project/Manuscript/Results/Fig4.png")
+Fig4 <- readPNG(paste(my_path("F"),"Figure 4.png",sep=""))
 grid.raster(Fig4)
@@
 # Path for saving plots
-Path <- "./Results/GoM/"
+Path <- my_path("R",Extra_Path = "GoM")
 
@@
 ### Analysis by Species ####
-
-Path <- "~/Documents/UBC/Oceans_Project/Manuscript/Results"
+Path <- my_path("R", Extra_Path = "GoM")
+
 # names(DBEM_Results)
@@
 Values represent the mean of 3 ESM; error bars represent $\mp$ sd.
-(2005-2014).](./Figures/Fig6.png)
+(2005-2014).](./Figures/Figure 6.png)
 
@@
 # Read Data
-Environmental_Data_Halibut <- read.csv("~/Documents/UBC/OC_Special_Issue/Ecol/Data/Distribution/Environmental_Data_Halibut.csv")
+Environmental_Data_Halibut <- read.csv(paste(my_path("D","Distribution"),"Environmental_Data_Halibut.csv",sep=""))
 

### 2020-05-03 Ecol/Manuscript_Draft.Rmd
Changes in file for thesis rendering

@@
 ---
-title: "Challenges to transboundary fisheries management in North America under climate change"
+title: Challenges to transboundary fisheries management in North America under climate
+  change
 author: "Juliano Palacios-Abrantes^1^ U. Rashid Sumaila^1^ William W. L. Cheung^1^"
-subtitle: "[Response to Reviewers]"
-date: "^1^ Institute for the Oceans and Fisheries, University of British Columbia, Vancouver, Canada"
+date: ^1^ Institute for the Oceans and Fisheries, University of British Columbia,
+  Vancouver, Canada
 output:
- word_document: default
- pdf_document: default
-bibliography: ../References/Oceans_Canada_Biblio.bib
+  bookdown::pdf_book:
+    toc : false
+  # pdf_document: default
+  # word_document: default
 editor_options:
@@
 csl: ../References/E&S.csl
+subtitle: '[Response to Reviewers]'
+bibliography: ../References/Oceans_Canada_Biblio.bib
 ---
@@
  "png", # For reading plots in chunk codes
- "grid" # For reading plots in chunk codes
+ "grid", # For reading plots in chunk codes
+ "here"
 )
@@
 
-## INTRODUCTION
+## Introduction
 
@@
 Game theory is one of the most common approaches used to analyze the management of shared stocks, as often, success depends on effective cooperation between parties [@Munro:2002uf; @Sumaila:2013hv].
-Management of these stocks' can be convoluted due to the participation of several fishing “players”, different countries and sometimes jurisdictions within a country, the migration patterns of the stock, and their abundance fluctuation within space and time [@Munro:2002uf], Engler and Saunders this Special Feature).
+Management of these stocks' can be convoluted due to the participation of several fishing “players”, different countries and sometimes jurisdictions within a country, the migration patterns of the stock, and their abundance fluctuation within space and time [@Munro:2002uf; Engler and Saunders this Special Feature].
 In addition, international treaties might not be prepared to address the effects that climate change will bring to shared fish stocks (Engler and Saunders this Special Feature, Koubrak and VanderZwaag, this Special Feature).
@@
 
-The shifts in distribution of shared fish stocks will impact the economics of their fisheries [@Pinsky:2012kq; @Sumaila:2019gh]Sumaila et al., this Special Feature), and create international disputes between countries [@Munro:2002uf; @Spijkers:2017ij; @Pinsky:2018cb].
+The shifts in distribution of shared fish stocks will impact the economics of their fisheries [@Pinsky:2012kq; @Sumaila:2019gh; Sumaila et al., this Special Feature], and create international disputes between countries [@Munro:2002uf; @Spijkers:2017ij; @Pinsky:2018cb].
 Canada and the US share important transboundary stocks of salmon (*Oncorhynchus spp.*), Pacific halibut (*Hippoglossus stenolepis*), and Atlantic cod (*Gadus morhua*) offering a unique lens to understand the extent to which climate-induced distributional shifts will challenge the future sustainability of transboundary fisheries.
@@
 
-## METHODS
+## Methods
 
@@
 The analysis was carried out within the 200 nautical miles of both nation’s EEZ from the Gulf of Mexico to The Labrador Sea in the Atlantic, and from California to Chukchi Sea, in the Pacific coast.
-The species analyzed (Table A2.1) were selected based on five treaties in both the Atlantic and Pacific coast of North America (Table 1).
+The species analyzed (Table A2.1) were selected based on five treaties in both the Atlantic and Pacific coast of North America (Table \ref({tab:Treaties-Table}).
 All species under the IPHC, Pacific Salmon Commission, the Pacific Whiting Treaty, and the GoMA arrangement were analyzed as these are bi-lateral agreements.
@@
 
-```{r Treaties_Table, eval = T, echo = F}
+```{r Treaties-Table, eval = T, echo = F}
 
@@
 ) %>% 
- kable("latex",
+ kable(
     caption = "Treaties and number of species included in the current analysis."
@@
  add_footnote(fn)
+
 ```
@@
 For this specific case, we considered Alaska as a separate entity, the US contiguous states as a second one (Washington, Oregon and California), and lastly British Columbia (Canada).
-For the GoMA we used NAFO's divisions 5Y, 5Ze, and 4X within latitudes 46.2°N and 41.5°S, and longitudes -72°W and -64°E (Fig.
-1).
+For the GoMA we used NAFO's divisions 5Y, 5Ze, and 4X within latitudes 46.2°N and 41.5°S, and longitudes -72°W and -64°E (Figure \@ref(fig:Figure1-map)).
 
@@
 
-![Fig 1. Map of North America with the regulatory areas of the International Paific Halibut Comission and the NAFO sub-region containing the Gulf of Maine arrangement](./Figures/Figure 1.png)
+```{r Figure1-map, eval = T, echo=FALSE, fig.pos= "H", fig.height = 4, fig.width = 6, fig.cap="Map of North America with the regulatory areas of the International Paific Halibut Comission and the NAFO sub-region containing the Gulf of Maine arrangement"}
+
+img <- readPNG("./Figures/Figure 1.png")
+grid.raster(img)
+
+```
 
@@
 In the case of North America as a whole, and the GoM arrangement, region is defined as the $0.5^{\circ}$ x $0.5^{\circ}$ grid-cell within the EEZ and the specific NAFO regulatory areas, respectively.
-For the IPHC analysis, region is defined as the Commission's regulatory areas (Fig.
-1).
+For the IPHC analysis, region is defined as the Commission's regulatory areas (Figure \@ref(fig:Figure1-map)).
 We then average the values in three time periods (*t*) to reduce temporal model sensitivity.
@@
 
-## RESULTS
+## Results
 
@@
 
-Shifts in the distribution of 33 jointly managed transboundary stocks of North America by 2050 relative to 2010 show that MCP of transboundary stocks will overall increase in Atlantic-Canadian and Alaskan waters and decrease in Pacific-Canadian and the US contiguous states waters (Fig.
-2).
-Such changes will be more intense under the high emission scenario (Fig.
-2A).
-For most regions, losses of MCP will be more intense under a high emission scenario (Fig 2A) than under a low emission scenario (Fig 2B), however, there will be no apparent change in gain intensity between scenarios.
+Shifts in the distribution of 33 jointly managed transboundary stocks of North America by 2050 relative to 2010 show that MCP of transboundary stocks will overall increase in Atlantic-Canadian and Alaskan waters and decrease in Pacific-Canadian and the US contiguous states waters (Figure \@ref(fig:Figure2-NA)).
+Such changes will be more intense under the high emission scenario (Figure \@ref(fig:Figure2-NA)A).
+For most regions, losses of MCP will be more intense under a high emission scenario (Figure \@ref(fig:Figure2-NA)A) than under a low emission scenario (Figure \@ref(fig:Figure2-NA)B), however, there will be no apparent change in gain intensity between scenarios.
 Impacts of climate change are expected to intensify towards the end of the $21^{st}$ century, although with greater uncertainty (Fig A1.1).
 
-![Fig.
+```{r Figure2-NA, eval = T, echo=FALSE, fig.pos= "H", fig.cap="Percentage change of MCP of transboundary stocks of North America for mid $21^{st}$ century (2041-2060) relative to present (2005-2014) under a A) high emission scenario and; B) low emission scenario.
+Points represent areas where at least one model do not agree in the direction of change"}
+
+img <- readPNG("./Figures/Figure 2.png")
+grid.raster(img)
+
+```
+
+<!-- ![Fig.
 2.
 Percentage change of MCP of transboundary stocks of North America for mid $21^{st}$ century (2041-2060) relative to present (2005-2014) under a A) high emission scenario and; B) low emission scenario.
-Points represent areas where at least one model do not agree in the direction of change](./Figures/Figure 2.png)
+Points represent areas where at least one model do not agree in the direction of change](./Figures/Figure 2.png) -->
 
@@
 
-In the case of the IPHC, at least one third of regulatory areas will see a reduction in MCP of Pacific halibut by 2050 relative to current MCP, regardless of the climate change scenario (Fig.
-3).
+In the case of the IPHC, at least one third of regulatory areas will see a reduction in MCP of Pacific halibut by 2050 relative to current MCP, regardless of the climate change scenario (Figure \@ref(fig:Figure3-IPHC)).
 It is likely that the stock shift from the U.S.
@@
 The potential movement of halibut westward will increase the MCP of regulatory areas 3B (under a low emission scenario) and 4ABCE along the Aleutian Islands and Bering Sea.
-Regions 4DE, the most poleward regulatory areas of the IPHC, are expected to gain MCP by mid (Fig.
-3) and end of the $21^{st}$ century (Fig.
+Regions 4DE, the most poleward regulatory areas of the IPHC, are expected to gain MCP by mid (Figure \@ref(fig:Figure3-IPHC)) and end of the $21^{st}$ century (Fig.
 A1.2) under a high emission scenario due to the expansion of halibut suitable habitat as sea ice retreats (Fig.
 A2.1).
-In contrast, under a low emission scenario, sea ice is expected to stabilize towards mid 21st century, thus providing less “new” suitable habitat for Pacific halibut and resulting in undetectable changes in MCP for the region (Fig.
-3B) and decreasing even more towards 2100 (Fig.
+In contrast, under a low emission scenario, sea ice is expected to stabilize towards mid 21st century, thus providing less “new” suitable habitat for Pacific halibut and resulting in undetectable changes in MCP for the region (Figure \@ref(fig:Figure3-IPHC)B) and decreasing even more towards 2100 (Fig.
 A1.2).
@@
 
-```{r Figure_3, eval =F, echo = F}
-
-img <- readPNG(paste(my_path("F"),"Figure 3.png",sep=""))
+```{r Figure3-IPHC, eval = T, echo = F, fig.cap= "Percentage change of MCP for species managed by the IPHC for mid 21st century (2041-2060) relative to present 2005-2014 under a A) high emission scenario and B) low emission scenario.
+Labels marked with * represent regions where models do not agree in direction of change"}
+
+img <- readPNG("./Figures/Figure 3.png")
 grid.raster(img)
@@
 
-![Fig 3.
-Percentage change of MCP for species managed by the IPHC for mid 21st century (2041-2060) relative to present 2005-2014 under a A) high emission scenario and B) low emission scenario.
-Labels marked with "*" represent regions where models do not agree in direction of change](./Figures/Fig3.png)
-
-The same poleward trend is expected in the change of Pacific halibut stock-share ratio with the average proportion increasing up to 25% in some northern regions and decreasing by 10% in southern regions, relative to the present proportion (Fig.
-4).
+<!-- ![Percentage change of MCP for species managed by the IPHC for mid 21st century (2041-2060) relative to present 2005-2014 under a A) high emission scenario and B) low emission scenario.
+Labels marked with "*" represent regions where models do not agree in direction of change](./Figures/Figure 3.png) -->
+
+The same poleward trend is expected in the change of Pacific halibut stock-share ratio with the average proportion increasing up to 25% in some northern regions and decreasing by 10% in southern regions, relative to the present proportion (Figure \@ref(fig:Figure-4-iphc-prop)).
 Maintaining emissions to lower levels through 2050 would potentially leave unchanged the stock-share ratio of three regulatory areas (3AC, and 4D) and negatively change regulatory area 2A.
 On the other hand, failing to achieve such target will decrease the stock-share ratio in the most productive regulatory areas (2AC, 3AB).
+
+\clearpage
 
@@
 
-```{r Figure_4, eval = F, echo = F}
+```{r Figure-4-iphc-prop, eval = T, echo = F, fig.pos= "H", fig.height = 6, fig.width = 4,  fig.cap = "Percentage change of stock-share ratio for IPHC under A) high emission scenario and B) low emission scenario for mid 21st century (2041-2060) relative to present 2005-2014.
+Values represent the mean of 3 ESM; error bars represent +- sd."}
 
@@
 
-![Fig.
+<!-- ![Fig.
 4.
 Percentage change of stock-share ratio for IPHC under A) high emission scenario and B) low emission scenario for mid 21st century (2041-2060) relative to present 2005-2014.
-Values represent the mean of 3 ESM; error bars represent $\mp$ sd.](./Figures/Figure 4.png)
+Values represent the mean of 3 ESM; error bars represent $\mp$ sd.](./Figures/Figure 4.png) -->
 
@@
 
-While some regulatory areas of the IPHC will see an incremental increase in Pacific halibut MCP, the results for the Gulf of Maine show an overall decrease in MCP by 2050, regardless of the climate change scenario or ESM (Fig.
-5), intensifying by the end of the $21^{st}$ century (Fig.
+While some regulatory areas of the IPHC will see an incremental increase in Pacific halibut MCP, the results for the Gulf of Maine show an overall decrease in MCP by 2050, regardless of the climate change scenario or ESM (Figure \@ref(fig:Figure5-goma)), intensifying by the end of the $21^{st}$ century (Fig.
 A1.3).
-For cod and haddock, MCP will decrease within the whole Gulf with no apparent win for any country in reference to the current period (Fig.
-5).
+For cod and haddock, MCP will decrease within the whole Gulf with no apparent win for any country in reference to the current period (Figure \@ref(fig:Figure5-goma)).
 For yellowtail flounder, despite an overall reduction, some discrete areas are expected to increase with no particular pattern and high uncertainty as ESMs in these regions do not agree in the direction of change.
 Despite the overall reduction in MCP for all three species in comparison to current values, there is a benefit of achieving a low emission scenario as reductions intensify under the high emission scenario.
+
+\clearpage
 
@@
 
-![Fig.
+```{r Figure5-goma, eval = T, echo = F, fig.pos = "H", fig.height = 4, fig.width = 6, fig.cap = "Percentage change of MCP in the Gulf of Maine under, A) high emission scenario; and B) low emission for mid-century (2041-2060) relative to present (2005-2014).
+Points represent regions where models do not agree in direction of change."}
+
+Fig4 <- readPNG(paste(my_path("F"),"Figure 5.png",sep=""))
+grid.raster(Fig4)
+
+```
+
+<!-- ![Fig.
 5.
 Percentage change of MCP in the Gulf of Maine under, A) high emission scenario; and B) low emission for mid-century (2041-2060) relative to present (2005-2014).
-Points represent regions where models do not agree in direction of change.](./Figures/Figure 5.png)
+Points represent regions where models do not agree in direction of change.](./Figures/Figure 5.png) -->
 
@@
 Following a high emission path will affect mostly Canada’s share of yellowtail flounder and in less degree haddock, with an increase of cod share.
-under the low emission scenario, haddock and cod patterns intensify, while yellowtail flounder’s share approaches almost no change (Fig.
-6).
+under the low emission scenario, haddock and cod patterns intensify, while yellowtail flounder’s share approaches almost no change (Figure \@ref(fig:Figure-6-goma-prop)).
 Such pattern is likely the combination of the bathymetry or the Gulf, the warming gradient, and the species distribution (see discussion).
+
+\clearpage
 
@@
 
-![Fig 6.Changes in MCP stock-share ratio for Gulf of Maine under (A) high emission; and (B) low emission scenarios for mid 21st century (2041-2060) relative to present.
+```{r Figure-6-goma-prop, eval = T, echo = F, fig.pos = "L", fig.cap = "Changes in MCP stock-share ratio for Gulf of Maine under (A) high emission; and (B) low emission scenarios for mid 21st century (2041-2060) relative to present.
+Values represent the mean of 3 ESM; error bars represent +- sd.
+(2005-2014)."}
+
+Fig6 <- readPNG(paste(my_path("F"),"Figure 6.png",sep=""))
+grid.raster(Fig6)
+
+```
+
+<!-- ![Fig 6.Changes in MCP stock-share ratio for Gulf of Maine under (A) high emission; and (B) low emission scenarios for mid 21st century (2041-2060) relative to present.
 Values represent the mean of 3 ESM; error bars represent $\mp$ sd.
-(2005-2014).](./Figures/Figure 6.png)
-
-## DISCUSSION
+(2005-2014).](./Figures/Figure 6.png) -->
+
+## Discussion
 
@@
 Species such as haddock in the Atlantic [@Morley:2018fn], and big skate (*Raja binoculata*) in the Pacific coast [@Pinsky:2013jo] have been projected to shift away from the poles.
-In the Gulf of Maine, the stock-share gain of yellowtail flounder and haddock by the US (Fig.
-6) could be a response to a temperature gradient shift combined with geographic barriers as southern waters are deeper, and warming slower than northern waters (Fig A3.1.).
+In the Gulf of Maine, the stock-share gain of yellowtail flounder and haddock by the US (Figure \@ref(fig:Figure-6-goma-prop)) could be a response to a temperature gradient shift combined with geographic barriers as southern waters are deeper, and warming slower than northern waters (Fig A3.1.).
 On the other hand, Maine has seen its landings of yellowtail flounder increased at the expenses of southern states [@Pinsky:2012kq].
 This could be influencing the US gain in MCP in the GoMA in relation to Canada as species shift their distribution from lower latitudes naturally reaching the US (lower) region first.
-Geographic barriers also affect the westward increase of stock-share in IPHC regions where species can only migrate northward into the Arctic Ocean through the Bering Sea and Bering Strait [@Cheung:2015fm] (Fig.
-4).
+Geographic barriers also affect the westward increase of stock-share in IPHC regions where species can only migrate northward into the Arctic Ocean through the Bering Sea and Bering Strait [@Cheung:2015fm] (Figure \@ref(fig:Figure-4-iphc-prop)).
 As the effects of climate change endure, even with high mitigation, joint plans should prepare to face changes in the stock-share ratio of transboundary stocks along both coast of North America.
@@
 Moreover, overlapping shifting stocks could interfere in gear-limitation management rules of multiple fisheries generating conflicts between fleets [@VanDerVoo:2016uc].
-The effectiveness of the IPHC-Closed Area ("CA" in Fig 1.) in terms of protecting juveniles has been historically questioned as trawling for other species is still allowed in the area [@Karim:2010ut; @IPHC:2017CA].
+The effectiveness of the IPHC-Closed Area ("CA" in figure \@ref(fig:Figure1-map)).
+in terms of protecting juveniles has been historically questioned as trawling for other species is still allowed in the area [@Karim:2010ut; @IPHC:2017CA].
 In 2015, for example, 97% of the trawl by-catch in areas 4CDE and the Closed Area were juveniles [@IPHC:2017CA].
@@
 In our results, the "winners and losers" of climate change, and the intensity of the change, will be scenario dependent.
-For instance, stock-share of yellowtail flounder under a high emission scenario will be larger for the US while Canada's gain of haddock stock-share will be larger under a low emission scenario (Fig.
-6).
+For instance, stock-share of yellowtail flounder under a high emission scenario will be larger for the US while Canada's gain of haddock stock-share will be larger under a low emission scenario (Figure \@ref(fig:Figure-6-goma-prop)).
 Applying previously describe strategies (e.g.
@@
 Overall, results for the Gulf of Maine agree with a reduction in MCP of all three species.
-However, some discrete areas show a positive change for yellowtail flounder by mid $21^{st}$ century (Fig.
-4), mainly driven by the GFDL model (Fig.
+However, some discrete areas show a positive change for yellowtail flounder by mid $21^{st}$ century (Figure \@ref(fig:Figure-4-iphc-prop)), mainly driven by the GFDL model (Fig.
 A2.3).
@@
 
-## CONCLUSIONS
+## Conclusion
 
@@
 
-# SUPPLEMENTS
+## Supplements
 
@@
 }
+
+```
+
+<!-- # ESM uncertainty -->
+<!-- This chunk explores the uncertainty build in the ESM-DBEM  -->
+
+```{r DBEM_Uncertanty, eval = F, echo = F}
+
+#### DBEM-ESM Uncertanty
+
+Today_Uncertanty <- DBEM_Corrected %>% 
+  filter(Species %in% Selected_Species) %>% 
+  left_join(IPHC_Reg_DBEM_df,
+            by = "INDEX") %>% 
+  filter(!is.na(RegArea)) %>% 
+  mutate(RCP = ifelse(Model %in% RCP,"Low Emission","High Emission")) %>% 
+  gather("Year","MCP",Beg_In:Beg_End) %>% 
+  mutate(Period = ifelse(Year >= Beg_In & Year <= Beg_End,"Beginning","NA")) %>% 
+  group_by(RegArea,Model,RCP,Year,Period) %>% 
+  summarise(Regional_MCP =sum(MCP,na.rm=T)) %>% 
+  group_by(RegArea,Model,RCP) %>% 
+  summarise(Today_MCP =mean(Regional_MCP,na.rm=T))
+
+IPHC_MCP_Change_Uncert <- DBEM_Corrected %>% 
+  filter(Species %in% Selected_Species) %>% 
+  left_join(IPHC_Reg_DBEM_df,
+            by = "INDEX") %>% 
+  filter(!is.na(RegArea)) %>% 
+  mutate(RCP = ifelse(Model %in% RCP,"Low Emission","High Emission")) %>% 
+  gather("Year","MCP",Beg_In:End_End) %>%
+  group_by(Model,RCP,Year,RegArea) %>%
+  summarise(Regional_MCP =sum(MCP,na.rm=T)) %>% 
+  group_by(RCP,Model,RegArea) %>% # Running mean as Kleisner & Pauly 2012
+  mutate(RMean = rollmean(x = Regional_MCP, 10,
+                          align = "right",
+                          fill = Regional_MCP)
+  ) %>% 
+  mutate(GCM = ifelse(Model == "GFDL26F1" | Model == "GFDL85F1","GFDL",
+                      ifelse(Model == "IPSL26F1" | Model == "IPSL85F1", "IPSL",
+                             ifelse(Model == "MPI26F1" | Model == "MPI85F1","MPI","NA"
+                             )
+                      )
+  )
+  ) %>% 
+  filter(Year >= 2015) %>% 
+  left_join(Today_Uncertanty,
+            by = c("RegArea","Model","RCP")) %>% 
+  mutate(Index = RMean/Today_MCP)
+
+# Create and save plot
+
+ggplot(IPHC_MCP_Change_Uncert) +
+  geom_line(
+    aes(
+      x = as.numeric(Year),
+      y = Index,
+      color = GCM,
+      linetype = RCP
+    )
+  ) +
+  facet_wrap(~RegArea,
+             scales = "free_y") +
+  labs(
+    x = "Year",
+    y ="Index (Future MCP/Present)"
+  ) +
+  scale_color_manual("Global Circulation model",
+                     values=c("#EEA410","#B53CB9","#2EBC67")
+  ) +
+  scale_x_continuous(breaks = seq(2010,2100,30),
+                     limits = c(2010,2100)
+  ) +
+  my_ggtheme_p()() +
+  # Save plot
+  ggsave("Model_Uncer_Sup.png",
+         plot = .,
+         width = 12,
+         height =8,
+         units = "in",
+         path = "./Results/Sup"
+  )
+
+```
+
+```{r Figure-S1, eval = T, echo = F, fig.pos= "H", fig.cap = "Variation of climate change scenarios"}
+
+FigS21 <- readPNG(paste(my_path("F"),"S21.png",sep=""))
+grid.raster(FigS21)
 
@@
 
-<!-- # ESM uncertainty -->
-<!-- This chunk explores the uncertainty build in the ESM-DBEM  -->
-
-```{r DBEM_Uncertanty, eval = F, echo = F}
-
-#### DBEM-ESM Uncertanty
-
-Today_Uncertanty <- DBEM_Corrected %>% 
-  filter(Species %in% Selected_Species) %>% 
-  left_join(IPHC_Reg_DBEM_df,
-            by = "INDEX") %>% 
-  filter(!is.na(RegArea)) %>% 
-  mutate(RCP = ifelse(Model %in% RCP,"Low Emission","High Emission")) %>% 
-  gather("Year","MCP",Beg_In:Beg_End) %>% 
-  mutate(Period = ifelse(Year >= Beg_In & Year <= Beg_End,"Beginning","NA")) %>% 
-  group_by(RegArea,Model,RCP,Year,Period) %>% 
-  summarise(Regional_MCP =sum(MCP,na.rm=T)) %>% 
-  group_by(RegArea,Model,RCP) %>% 
-  summarise(Today_MCP =mean(Regional_MCP,na.rm=T))
-
-IPHC_MCP_Change_Uncert <- DBEM_Corrected %>% 
-  filter(Species %in% Selected_Species) %>% 
-  left_join(IPHC_Reg_DBEM_df,
-            by = "INDEX") %>% 
-  filter(!is.na(RegArea)) %>% 
-  mutate(RCP = ifelse(Model %in% RCP,"Low Emission","High Emission")) %>% 
-  gather("Year","MCP",Beg_In:End_End) %>%
-  group_by(Model,RCP,Year,RegArea) %>%
-  summarise(Regional_MCP =sum(MCP,na.rm=T)) %>% 
-  group_by(RCP,Model,RegArea) %>% # Running mean as Kleisner & Pauly 2012
-  mutate(RMean = rollmean(x = Regional_MCP, 10,
-                          align = "right",
-                          fill = Regional_MCP)
-  ) %>% 
-  mutate(GCM = ifelse(Model == "GFDL26F1" | Model == "GFDL85F1","GFDL",
-                      ifelse(Model == "IPSL26F1" | Model == "IPSL85F1", "IPSL",
-                             ifelse(Model == "MPI26F1" | Model == "MPI85F1","MPI","NA"
-                             )
-                      )
-  )
-  ) %>% 
-  filter(Year >= 2015) %>% 
-  left_join(Today_Uncertanty,
-            by = c("RegArea","Model","RCP")) %>% 
-  mutate(Index = RMean/Today_MCP)
-
-# Create and save plot
-
-ggplot(IPHC_MCP_Change_Uncert) +
-  geom_line(
-    aes(
-      x = as.numeric(Year),
-      y = Index,
-      color = GCM,
-      linetype = RCP
-    )
-  ) +
-  facet_wrap(~RegArea,
-             scales = "free_y") +
-  labs(
-    x = "Year",
-    y ="Index (Future MCP/Present)"
-  ) +
-  scale_color_manual("Global Circulation model",
-                     values=c("#EEA410","#B53CB9","#2EBC67")
-  ) +
-  scale_x_continuous(breaks = seq(2010,2100,30),
-                     limits = c(2010,2100)
-  ) +
-  my_ggtheme_p()() +
-  # Save plot
-  ggsave("Model_Uncer_Sup.png",
-         plot = .,
-         width = 12,
-         height =8,
-         units = "in",
-         path = "./Results/Sup"
-  )
+```{r Figure_S2, eval = T, echo = F, fig.pos= "H", fig.cap = "Variation of climate change scenarios in IPHC regions 4E and 4D"}
+
+FigS22 <- readPNG(paste(my_path("F"),"S22.png",sep=""))
+grid.raster(FigS22)
 
@@
     path = Path)
+
+```
+
+```{r Figure_S3, eval = T, echo = F, fig.pos= "H", fig.cap = "Outliers GoMA"}
+
+FigS23 <- readPNG(paste(my_path("F"),"S23.png",sep=""))
+grid.raster(FigS23)
 

### 2020-05-03 Ecol/Manuscript_Draft.Rmd
Changes for thesis chapter

@@
 ---
-title: Challenges to transboundary fisheries management in North America under climate
-  change
-author: "Juliano Palacios-Abrantes^1^ U. Rashid Sumaila^1^ William W. L. Cheung^1^"
-date: ^1^ Institute for the Oceans and Fisheries, University of British Columbia,
-  Vancouver, Canada
 output:
@@
 csl: ../References/E&S.csl
-subtitle: '[Response to Reviewers]'
 bibliography: ../References/Oceans_Canada_Biblio.bib
+header-includes: #allows you to add in your own Latex packages
+- \usepackage{float} #use the 'float' package
+- \floatplacement{figure}{H} #make every figure with caption = h
 ---
@@
 
-```{r Figure1-map, eval = T, echo=FALSE, fig.pos= "H", fig.height = 4, fig.width = 6, fig.cap="Map of North America with the regulatory areas of the International Paific Halibut Comission and the NAFO sub-region containing the Gulf of Maine arrangement"}
+```{r Figure1-map, eval = T, echo=FALSE, fig.height = 4, fig.width = 6, fig.cap="Map of North America with the regulatory areas of the International Paific Halibut Comission and the NAFO sub-region containing the Gulf of Maine arrangement"}
 
@@
 
-```{r Figure2-NA, eval = T, echo=FALSE, fig.pos= "H", fig.cap="Percentage change of MCP of transboundary stocks of North America for mid $21^{st}$ century (2041-2060) relative to present (2005-2014) under a A) high emission scenario and; B) low emission scenario.
+```{r Figure2-NA, eval = T, echo=FALSE, fig.cap="Percentage change of MCP of transboundary stocks of North America for mid $21^{st}$ century (2041-2060) relative to present (2005-2014) under a A) high emission scenario and; B) low emission scenario.
 Points represent areas where at least one model do not agree in the direction of change"}
@@
 
-```{r Figure-4-iphc-prop, eval = T, echo = F, fig.pos= "H", fig.height = 6, fig.width = 4,  fig.cap = "Percentage change of stock-share ratio for IPHC under A) high emission scenario and B) low emission scenario for mid 21st century (2041-2060) relative to present 2005-2014.
+```{r Figure-4-iphc-prop, eval = T, echo = F, fig.height = 6, fig.width = 4,  fig.cap = "Percentage change of stock-share ratio for IPHC under A) high emission scenario and B) low emission scenario for mid 21st century (2041-2060) relative to present 2005-2014.
 Values represent the mean of 3 ESM; error bars represent +- sd."}
@@
 
-```{r Figure5-goma, eval = T, echo = F, fig.pos = "H", fig.height = 4, fig.width = 6, fig.cap = "Percentage change of MCP in the Gulf of Maine under, A) high emission scenario; and B) low emission for mid-century (2041-2060) relative to present (2005-2014).
+```{r Figure5-goma, eval = T, echo = F, fig.height = 4, fig.width = 6, fig.cap = "Percentage change of MCP in the Gulf of Maine under, A) high emission scenario; and B) low emission for mid-century (2041-2060) relative to present (2005-2014).
 Points represent regions where models do not agree in direction of change."}
@@
 
-```{r Figure-6-goma-prop, eval = T, echo = F, fig.pos = "L", fig.cap = "Changes in MCP stock-share ratio for Gulf of Maine under (A) high emission; and (B) low emission scenarios for mid 21st century (2041-2060) relative to present.
+```{r Figure-6-goma-prop, eval = T, echo = F, fig.cap = "Changes in MCP stock-share ratio for Gulf of Maine under (A) high emission; and (B) low emission scenarios for mid 21st century (2041-2060) relative to present.
 Values represent the mean of 3 ESM; error bars represent +- sd.
@@
 
-```{r Figure-S1, eval = T, echo = F, fig.pos= "H", fig.cap = "Variation of climate change scenarios"}
+```{r Figure-S1, eval = T, echo = F, fig.cap = "Variation of climate change scenarios"}
 
@@
 
-```{r Figure_S2, eval = T, echo = F, fig.pos= "H", fig.cap = "Variation of climate change scenarios in IPHC regions 4E and 4D"}
+```{r Figure_S2, eval = T, echo = F, fig.cap = "Variation of climate change scenarios in IPHC regions 4E and 4D"}
 
@@
 
-```{r Figure_S3, eval = T, echo = F, fig.pos= "H", fig.cap = "Outliers GoMA"}
+```{r Figure_S3, eval = T, echo = F, fig.cap = "Outliers GoMA"}
 

### 2020-05-04 Ecol/Manuscript_Draft.Rmd
Inclued sup. pictures

@@
 The analysis was carried out within the 200 nautical miles of both nation’s EEZ from the Gulf of Mexico to The Labrador Sea in the Atlantic, and from California to Chukchi Sea, in the Pacific coast.
-The species analyzed (Table A2.1) were selected based on five treaties in both the Atlantic and Pacific coast of North America (Table \ref({tab:Treaties-Table}).
+The species analyzed (Table A2.1) were selected based on five treaties in both the Atlantic and Pacific coast of North America (Table \ref(tab:Treaties-Table).
 All species under the IPHC, Pacific Salmon Commission, the Pacific Whiting Treaty, and the GoMA arrangement were analyzed as these are bi-lateral agreements.
@@
 ) %>% 
- kable(
+  kable("latex",
+        booktabs = T,
         caption = "Treaties and number of species included in the current analysis."
@@
 For most regions, losses of MCP will be more intense under a high emission scenario (Figure \@ref(fig:Figure2-NA)A) than under a low emission scenario (Figure \@ref(fig:Figure2-NA)B), however, there will be no apparent change in gain intensity between scenarios.
-Impacts of climate change are expected to intensify towards the end of the $21^{st}$ century, although with greater uncertainty (Fig A1.1).
-
-```{r Figure2-NA, eval = T, echo=FALSE, fig.cap="Percentage change of MCP of transboundary stocks of North America for mid $21^{st}$ century (2041-2060) relative to present (2005-2014) under a A) high emission scenario and; B) low emission scenario.
+Impacts of climate change are expected to intensify towards the end of the $21^{st}$ century, although with greater uncertainty (Figure \@ref(fig:FigureS11)).
+
+```{r Figure2-NA, eval = T, echo=FALSE, fig.width = 12, fig.height = 6, fig.cap="Percentage change of MCP of transboundary stocks of North America for mid $21^{st}$ century (2041-2060) relative to present (2005-2014) under a A) high emission scenario and; B) low emission scenario.
 Points represent areas where at least one model do not agree in the direction of change"}
@@
 Consequently, each country’s share-ratio of different species will change with an overall benefit to northern regions, regardless of the RCP scenario.
-Overall, shifts will be amplified under the high emission scenario relative to the low greenhouse emission scenario pathway (Table 2).
-
-Table 2.
-Total stock-share of all 33 transboundary species by EEZ and emission scenario for the present, and mid and end of the $21^{st}$ century.
+Overall, shifts will be amplified under the high emission scenario relative to the low greenhouse emission scenario pathway (Table \@ref(tab:Table2)).
+
+```{r Table2, eval = T, echo = F}
+
+read.csv("./Tables/SS_Change.csv") %>% 
+  mutate(RCP = ifelse(RCP == "High_Emission","High Emission","Low Emission")) %>% 
+  mutate(EEZ = ifelse(Nation == "Can E","Canada East",
+                      ifelse(Nation == "Can W","Canada West",
+                             ifelse(Nation == "USA W","USA West",
+                                    ifelse(Nation == "USA E","USA East",paste(Nation)))))) %>% 
+  select(EEZ,everything(),-Nation) %>% 
+  kable("latex",
+        booktabs = T,
+        col.names = c("EEZ","RCP","Begening","Mid of the Century","End of the Century"),
+        caption = "Total stock-share of all 33 transboundary species by EEZ and emission scenario for the present, and mid and end of the $21^{st}$ century.
 Averages might not add to 100% due to model differences.
-Standard deviation of the projected values are provided in parentheses.
+Standard deviation of the projected values are provided in parentheses.") %>%
+  kable_styling(full_width = T) %>%
+  column_spec(1,width = "2cm") %>%   #wraps text in column2
+  collapse_rows(columns = 1, latex_hline = "none", valign = "middle")
+  # collapse_rows(1:2, row_group_label_position = 'stack')
+
+```
 
@@
 The potential movement of halibut westward will increase the MCP of regulatory areas 3B (under a low emission scenario) and 4ABCE along the Aleutian Islands and Bering Sea.
-Regions 4DE, the most poleward regulatory areas of the IPHC, are expected to gain MCP by mid (Figure \@ref(fig:Figure3-IPHC)) and end of the $21^{st}$ century (Fig.
-A1.2) under a high emission scenario due to the expansion of halibut suitable habitat as sea ice retreats (Fig.
-A2.1).
-In contrast, under a low emission scenario, sea ice is expected to stabilize towards mid 21st century, thus providing less “new” suitable habitat for Pacific halibut and resulting in undetectable changes in MCP for the region (Figure \@ref(fig:Figure3-IPHC)B) and decreasing even more towards 2100 (Fig.
-A1.2).
+Regions 4DE, the most poleward regulatory areas of the IPHC, are expected to gain MCP by mid (Figure \@ref(fig:Figure3-IPHC)) and end of the $21^{st}$ century (Figure \@ref(fig:FigureS12)) under a high emission scenario due to the expansion of halibut suitable habitat as sea ice retreats (Figure \@ref(fig:FigureS1)).
+In contrast, under a low emission scenario, sea ice is expected to stabilize towards mid 21st century, thus providing less “new” suitable habitat for Pacific halibut and resulting in undetectable changes in MCP for the region (Figure \@ref(fig:Figure3-IPHC)B) and decreasing even more towards 2100 (Figure \@ref(fig:FigureS12)).
 
@@
 
-While some regulatory areas of the IPHC will see an incremental increase in Pacific halibut MCP, the results for the Gulf of Maine show an overall decrease in MCP by 2050, regardless of the climate change scenario or ESM (Figure \@ref(fig:Figure5-goma)), intensifying by the end of the $21^{st}$ century (Fig.
-A1.3).
+While some regulatory areas of the IPHC will see an incremental increase in Pacific halibut MCP, the results for the Gulf of Maine show an overall decrease in MCP by 2050, regardless of the climate change scenario or ESM (Figure \@ref(fig:Figure5-goma)), intensifying by the end of the $21^{st}$ century (Figure \@ref(fig:FigureS13)).
 For cod and haddock, MCP will decrease within the whole Gulf with no apparent win for any country in reference to the current period (Figure \@ref(fig:Figure5-goma)).
@@
 
-```{r Figure5-goma, eval = T, echo = F, fig.height = 4, fig.width = 6, fig.cap = "Percentage change of MCP in the Gulf of Maine under, A) high emission scenario; and B) low emission for mid-century (2041-2060) relative to present (2005-2014).
+```{r Figure5-goma, eval = T, echo = F, fig.height = 7, fig.width = 9, fig.cap = "Percentage change of MCP in the Gulf of Maine under, A) high emission scenario; and B) low emission for mid-century (2041-2060) relative to present (2005-2014).
 Points represent regions where models do not agree in direction of change."}
@@
 Species such as haddock in the Atlantic [@Morley:2018fn], and big skate (*Raja binoculata*) in the Pacific coast [@Pinsky:2013jo] have been projected to shift away from the poles.
-In the Gulf of Maine, the stock-share gain of yellowtail flounder and haddock by the US (Figure \@ref(fig:Figure-6-goma-prop)) could be a response to a temperature gradient shift combined with geographic barriers as southern waters are deeper, and warming slower than northern waters (Fig A3.1.).
+In the Gulf of Maine, the stock-share gain of yellowtail flounder and haddock by the US (Figure \@ref(fig:Figure-6-goma-prop)) could be a response to a temperature gradient shift combined with geographic barriers as southern waters are deeper, and warming slower than northern waters (Figure \@ref(fig:FigureS13)).
 On the other hand, Maine has seen its landings of yellowtail flounder increased at the expenses of southern states [@Pinsky:2012kq].
@@
 Overall, results for the Gulf of Maine agree with a reduction in MCP of all three species.
-However, some discrete areas show a positive change for yellowtail flounder by mid $21^{st}$ century (Figure \@ref(fig:Figure-4-iphc-prop)), mainly driven by the GFDL model (Fig.
-A2.3).
+However, some discrete areas show a positive change for yellowtail flounder by mid $21^{st}$ century (Figure \@ref(fig:Figure-4-iphc-prop)), mainly driven by the GFDL model (Figure  \@ref(fig:FigureS1)).
 Potential model artifacts could also be contributing to the results, especially in the northern part of the study area (Bay of Fundy) as most disagreeing grids are covered by land, which could be influencing the results.
-In contrast, considerable uncertainty exists in the change of MCP along the IPHC Convention area shown by a disagreement between ESMs (Fig.
-A2.4).
+In contrast, considerable uncertainty exists in the change of MCP along the IPHC Convention area shown by a disagreement between ESMs (Figure \@ref(fig:FigureS2)).
 Off the coast of British Columbia, increasing temperature trends are consistent among ESMs, however, other processes such as acidification and deoxygenation are still not well understood from British Columbia to the Gulf of Alaska  [@TalloniAlvarez:2019gz].
@@
 ## Supplements
+
+```{r FigureS11, eval = T, echo = F, fig.cap = "Outliers GoMA"}
+
+FigS1 <- readPNG(paste(my_path("F"),"S11.png",sep=""))
+grid.raster(FigS11)
+
+```
+
+```{r FigureS12, eval = T, echo = F, fig.cap = "Outliers GoMA"}
+
+FigS12 <- readPNG(paste(my_path("F"),"S12.png",sep=""))
+grid.raster(FigS12)
+
+```
 
@@
 
-```{r Figure-S1, eval = T, echo = F, fig.cap = "Variation of climate change scenarios"}
+```{r FigureS1, eval = T, echo = F, fig.cap = "Variation of climate change scenarios"}
 
@@
 
-```{r Figure_S2, eval = T, echo = F, fig.cap = "Variation of climate change scenarios in IPHC regions 4E and 4D"}
+```{r FigureS2, eval = T, echo = F, fig.cap = "Variation of climate change scenarios in IPHC regions 4E and 4D"}
 
@@
 
-```{r Figure_S3, eval = T, echo = F, fig.cap = "Outliers GoMA"}
+```{r FigureS3, eval = T, echo = F, fig.cap = "Outliers GoMA"}
 
@@
 grid.raster(FigS23)
+
+```
+
+```{r FigureS13, eval = T, echo = F, fig.cap = "Outliers GoMA"}
+
+FigS13 <- readPNG(paste(my_path("F"),"S13.png",sep=""))
+grid.raster(FigS13)
 

### 2020-05-17 Ecol/Manuscript_Draft.Rmd
REsponse to David including NAFO

--- 2020-05-03 Ecol/Manuscript_Draft.Rmd
@@
 ---
+title: "Challenges to transboundary fisheries management in North America under climate change"
+author: "Juliano Palacios-Abrantes^1^ U. Rashid Sumaila^1^ William W. L. Cheung^1^"
+subtitle: "[Response to Reviewers]"
+date: "^1^ Institute for the Oceans and Fisheries, University of British Columbia, Vancouver, Canada"
 output:
-  bookdown::pdf_book:
-    toc : false
-  # pdf_document: default
-  # word_document: default
+ word_document: default
+ pdf_document: default
+bibliography: ../References/Oceans_Canada_Biblio.bib
 editor_options: 
@@
 csl: ../References/E&S.csl
-bibliography: ../References/Oceans_Canada_Biblio.bib
-header-includes: #allows you to add in your own Latex packages
-- \usepackage{float} #use the 'float' package
-- \floatplacement{figure}{H} #make every figure with caption = h
 ---
@@
  "png", # For reading plots in chunk codes
- "grid", # For reading plots in chunk codes
- "here"
+ "grid" # For reading plots in chunk codes
 )
@@
 
-## Introduction
+## INTRODUCTION
 
 <!-- ##### First paragraph of paper summary -->
-In 1982, the United Nations Law of the Seas (UNCLOS) formalized the concept of economic exclusive zones (EEZs) creating what we know today as shared stocks [@UnitedNations:1986tl], i.e.
+In 1982, the United Nations Law of the Seas Convention (UNCLOS) formalized the concept of economic exclusive zones (EEZs) creating what we know today as shared stocks [@UnitedNations:1986tl], i.e.
 stocks migrate between countries EEZs (known as transboundary stocks) or between EEZs and the high seas (also called straddling stocks) [@Song:2017iua].
@@
 These stocks are responsible for almost 50% of these countries total fish catches [@Teh:2015gd].
-While not a law, UNCLOS incentives actions to cooperate on the management of shared stocks [@UnitedNations:1986tl].
+Under Article 63, UNCLOS incentives actions to cooperate on the management of shared stocks [@UnitedNations:1986tl].
 Game theory is one of the most common approaches used to analyze the management of shared stocks, as often, success depends on effective cooperation between parties [@Munro:2002uf; @Sumaila:2013hv].
-Management of these stocks' can be convoluted due to the participation of several fishing “players”, different countries and sometimes jurisdictions within a country, the migration patterns of the stock, and their abundance fluctuation within space and time [@Munro:2002uf; Engler and Saunders this Special Feature].
+Management of these stocks' can be convoluted due to the participation of several fishing “players”, different countries and sometimes jurisdictions within a country, the migration patterns of the stock, and their abundance fluctuation within space and time [@Munro:2002uf], Engler and Saunders this Special Feature).
 In addition, international treaties might not be prepared to address the effects that climate change will bring to shared fish stocks (Engler and Saunders this Special Feature, Koubrak and VanderZwaag, this Special Feature).
@@
 
-The shifts in distribution of shared fish stocks will impact the economics of their fisheries [@Pinsky:2012kq; @Sumaila:2019gh; Sumaila et al., this Special Feature], and create international disputes between countries [@Munro:2002uf; @Spijkers:2017ij; @Pinsky:2018cb].
+The shifts in distribution of shared fish stocks will impact the economics of their fisheries [@Pinsky:2012kq; @Sumaila:2019gh]Sumaila et al., this Special Feature), and create international disputes between countries [@Munro:2002uf; @Spijkers:2017ij; @Pinsky:2018cb].
 Canada and the US share important transboundary stocks of salmon (*Oncorhynchus spp.*), Pacific halibut (*Hippoglossus stenolepis*), and Atlantic cod (*Gadus morhua*) offering a unique lens to understand the extent to which climate-induced distributional shifts will challenge the future sustainability of transboundary fisheries.
@@
 
-## Methods
+## METHODS
 
@@
 
-The current study focuses on 33 transboundary stocks jointly managed by Canada and the US for both the Atlantic and the Pacific coasts (Table A3.1).
+The current study focuses on 33 transboundary stocks, **some of them** jointly managed by Canada and the US for both the Atlantic and the Pacific coasts (Table A3.1).
 The analysis was carried out within the 200 nautical miles of both nation’s EEZ from the Gulf of Mexico to The Labrador Sea in the Atlantic, and from California to Chukchi Sea, in the Pacific coast.
-The species analyzed (Table A2.1) were selected based on five treaties in both the Atlantic and Pacific coast of North America (Table \ref({tab:Treaties-Table}).
+The species analyzed (Table A2.1) were selected based on five treaties in both the Atlantic and Pacific coast of North America (Table 1).
 All species under the IPHC, Pacific Salmon Commission, the Pacific Whiting Treaty, and the GoMA arrangement were analyzed as these are bi-lateral agreements.
-However, in the case of Northwest Atlantic Fisheries Organization (NAFO), a subset of 26 species reported was made based on those fished in regions that fall within the EEZs of Canada and the United States (NAFO subareas 2s, 3s with the exception of 3M and 3N and limited to the EEZ, 4s, 5s and 6 A,B, and C).[^NAFO] Data related to fisheries was gathered from the Sea Around Us from 1951 to 2014 [@Zeller2016].
+**However, in the case of NAFO, the Comission is signed by 12 members and oversees the managment of 11 species in areas beyong national jurisdicions.
+Within the EEZs, NAFOs areas are used for management purposes but the management of stocks is made by each conuntry, unless a bilateral arrangement exists.
+For the purpose of this study, we assume that 26 species reported in NAFO's catch statistics fished in regions that fall within the EEZs of Canada and the United States (NAFO subareas 2s, 3s with the exception of 3M and 3N and limited to the EEZ, 4s, 5s and 6 A,B, and C), were transboundary in ntarue.** Fisheries data used in this study was gathered from the Sea Around Us from 1951 to 2014 [@Zeller2016].
 
@@
 
-```{r Treaties-Table, eval = T, echo = F}
+```{r Treaties_Table, eval = T, echo = F}
 
@@
 ) %>% 
- kable(
+ kable("latex",
     caption = "Treaties and number of species included in the current analysis."
@@
  add_footnote(fn)
-
 ```
@@
 For this specific case, we considered Alaska as a separate entity, the US contiguous states as a second one (Washington, Oregon and California), and lastly British Columbia (Canada).
-For the GoMA we used NAFO's divisions 5Y, 5Ze, and 4X within latitudes 46.2°N and 41.5°S, and longitudes -72°W and -64°E (Figure \@ref(fig:Figure1-map)).
+For the GoMA we used NAFO's divisions 5Y, 5Ze, and 4X within latitudes 46.2°N and 41.5°S, and longitudes -72°W and -64°E (Fig.
+1).
 
@@
 
-```{r Figure1-map, eval = T, echo=FALSE, fig.height = 4, fig.width = 6, fig.cap="Map of North America with the regulatory areas of the International Paific Halibut Comission and the NAFO sub-region containing the Gulf of Maine arrangement"}
-
-img <- readPNG("./Figures/Figure 1.png")
-grid.raster(img)
-
-```
+![Fig 1. Map of North America with the regulatory areas of the International Paific Halibut Comission and the NAFO sub-region containing the Gulf of Maine arrangement](./Figures/Figure 1.png)
 
@@
 
-Since 1998 Canada and the US celebrate a "Resource Sharing Understanding" to inform the management of Eastern George Bank's Atlantic cod (*Gadus morhua*) and haddock (*Melanogrammus aeglefinus*) and, yellowtail flounder (*Limanda ferruginea*) [@Pudden:2007bo; @CIA:2017uta; @TRAC:2016wu].
-The GoMA suggests catch-limits based on a weighted method were 10% represents the stocks’ historical distribution (from 1967 to 1994) and 90% current distributions produced by quarterly surveys and historical catch [@TRAC:2016wu].
+Since 1998 Canada and the US have used a "Resource Sharing Understanding" to inform the management of Eastern George Bank's Atlantic cod (*Gadus morhua*) and haddock (*Melanogrammus aeglefinus*) and, yellowtail flounder (*Limanda ferruginea*) [@Pudden:2007bo; @CIA:2017uta; @TRAC:2016wu].
+The GoMA suggests catch-limits based on a weighted method where 10% represents the stocks’ historical distribution (from 1967 to 1994) and 90% current distributions produced by quarterly surveys and historical catch [@TRAC:2016wu].
 In 2017, the allocation proposed for the GoMA was, Atlantic cod 80% Canada to 20 % U.S, haddock 41% Canada and 59% U.S, and yellowtail flounder 31% Canada and 69% U.S [@TRAC:2016wu].
@@
 In the case of North America as a whole, and the GoM arrangement, region is defined as the $0.5^{\circ}$ x $0.5^{\circ}$ grid-cell within the EEZ and the specific NAFO regulatory areas, respectively.
-For the IPHC analysis, region is defined as the Commission's regulatory areas (Figure \@ref(fig:Figure1-map)).
+For the IPHC analysis, region is defined as the Commission's regulatory areas (Fig.
+1).
 We then average the values in three time periods (*t*) to reduce temporal model sensitivity.
@@
 
-## Results
+## RESULTS
 
@@
 EEZIDs_List <- read_excel(paste(my_path("G",Extra_Path = "Spatial/DBEM"),"Updated_EEZList_17June2016.xlsx",sep=""))
-
-x <- paste(my_path("G",Extra_Path = "Spatial/DBEM"),"Updated_EEZList_17June2016.xlsx",sep="")
-
-str_detect(x,".xlsx")
 
@@
 
-Shifts in the distribution of 33 jointly managed transboundary stocks of North America by 2050 relative to 2010 show that MCP of transboundary stocks will overall increase in Atlantic-Canadian and Alaskan waters and decrease in Pacific-Canadian and the US contiguous states waters (Figure \@ref(fig:Figure2-NA)).
-Such changes will be more intense under the high emission scenario (Figure \@ref(fig:Figure2-NA)A).
-For most regions, losses of MCP will be more intense under a high emission scenario (Figure \@ref(fig:Figure2-NA)A) than under a low emission scenario (Figure \@ref(fig:Figure2-NA)B), however, there will be no apparent change in gain intensity between scenarios.
+Shifts in the distribution of 33 jointly managed transboundary stocks of North America by 2050 relative to 2010 show that MCP of transboundary stocks will overall increase in Atlantic-Canadian and Alaskan waters and decrease in Pacific-Canadian and the US contiguous states waters (Fig.
+2).
+Such changes will be more intense under the high emission scenario (Fig.
+2A).
+For most regions, losses of MCP will be more intense under a high emission scenario (Fig 2A) than under a low emission scenario (Fig 2B), however, there will be no apparent change in gain intensity between scenarios.
 Impacts of climate change are expected to intensify towards the end of the $21^{st}$ century, although with greater uncertainty (Fig A1.1).
 
-```{r Figure2-NA, eval = T, echo=FALSE, fig.cap="Percentage change of MCP of transboundary stocks of North America for mid $21^{st}$ century (2041-2060) relative to present (2005-2014) under a A) high emission scenario and; B) low emission scenario.
-Points represent areas where at least one model do not agree in the direction of change"}
-
-img <- readPNG("./Figures/Figure 2.png")
-grid.raster(img)
-
-```
-
-<!-- ![Fig.
+![Fig.
 2.
 Percentage change of MCP of transboundary stocks of North America for mid $21^{st}$ century (2041-2060) relative to present (2005-2014) under a A) high emission scenario and; B) low emission scenario.
-Points represent areas where at least one model do not agree in the direction of change](./Figures/Figure 2.png) -->
+Points represent areas where at least one model do not agree in the direction of change](./Figures/Figure 2.png)
 
@@
 
-In the case of the IPHC, at least one third of regulatory areas will see a reduction in MCP of Pacific halibut by 2050 relative to current MCP, regardless of the climate change scenario (Figure \@ref(fig:Figure3-IPHC)).
+In the case of the IPHC, at least one third of regulatory areas will see a reduction in MCP of Pacific halibut by 2050 relative to current MCP, regardless of the climate change scenario (Fig.
+3).
 It is likely that the stock shift from the U.S.
@@
 The potential movement of halibut westward will increase the MCP of regulatory areas 3B (under a low emission scenario) and 4ABCE along the Aleutian Islands and Bering Sea.
-Regions 4DE, the most poleward regulatory areas of the IPHC, are expected to gain MCP by mid (Figure \@ref(fig:Figure3-IPHC)) and end of the $21^{st}$ century (Fig.
+Regions 4DE, the most poleward regulatory areas of the IPHC, are expected to gain MCP by mid (Fig.
+3) and end of the $21^{st}$ century (Fig.
 A1.2) under a high emission scenario due to the expansion of halibut suitable habitat as sea ice retreats (Fig.
 A2.1).
-In contrast, under a low emission scenario, sea ice is expected to stabilize towards mid 21st century, thus providing less “new” suitable habitat for Pacific halibut and resulting in undetectable changes in MCP for the region (Figure \@ref(fig:Figure3-IPHC)B) and decreasing even more towards 2100 (Fig.
+In contrast, under a low emission scenario, sea ice is expected to stabilize towards mid 21st century, thus providing less “new” suitable habitat for Pacific halibut and resulting in undetectable changes in MCP for the region (Fig.
+3B) and decreasing even more towards 2100 (Fig.
 A1.2).
@@
 
-```{r Figure3-IPHC, eval = T, echo = F, fig.cap= "Percentage change of MCP for species managed by the IPHC for mid 21st century (2041-2060) relative to present 2005-2014 under a A) high emission scenario and B) low emission scenario.
-Labels marked with * represent regions where models do not agree in direction of change"}
-
-img <- readPNG("./Figures/Figure 3.png")
+```{r Figure_3, eval =F, echo = F}
+
+img <- readPNG(paste(my_path("F"),"Figure 3.png",sep=""))
 grid.raster(img)
@@
 
-<!-- ![Percentage change of MCP for species managed by the IPHC for mid 21st century (2041-2060) relative to present 2005-2014 under a A) high emission scenario and B) low emission scenario.
-Labels marked with "*" represent regions where models do not agree in direction of change](./Figures/Figure 3.png) -->
-
-The same poleward trend is expected in the change of Pacific halibut stock-share ratio with the average proportion increasing up to 25% in some northern regions and decreasing by 10% in southern regions, relative to the present proportion (Figure \@ref(fig:Figure-4-iphc-prop)).
+![Fig 3.
+Percentage change of MCP for species managed by the IPHC for mid 21st century (2041-2060) relative to present 2005-2014 under a A) high emission scenario and B) low emission scenario.
+Labels marked with "*" represent regions where models do not agree in direction of change](./Figures/Fig3.png)
+
+The same poleward trend is expected in the change of Pacific halibut stock-share ratio with the average proportion increasing up to 25% in some northern regions and decreasing by 10% in southern regions, relative to the present proportion (Fig.
+4).
 Maintaining emissions to lower levels through 2050 would potentially leave unchanged the stock-share ratio of three regulatory areas (3AC, and 4D) and negatively change regulatory area 2A.
 On the other hand, failing to achieve such target will decrease the stock-share ratio in the most productive regulatory areas (2AC, 3AB).
-
-\clearpage
 
@@
 
-```{r Figure-4-iphc-prop, eval = T, echo = F, fig.height = 6, fig.width = 4,  fig.cap = "Percentage change of stock-share ratio for IPHC under A) high emission scenario and B) low emission scenario for mid 21st century (2041-2060) relative to present 2005-2014.
-Values represent the mean of 3 ESM; error bars represent +- sd."}
+```{r Figure_4, eval = F, echo = F}
 
@@
 
-<!-- ![Fig.
+![Fig.
 4.
 Percentage change of stock-share ratio for IPHC under A) high emission scenario and B) low emission scenario for mid 21st century (2041-2060) relative to present 2005-2014.
-Values represent the mean of 3 ESM; error bars represent $\mp$ sd.](./Figures/Figure 4.png) -->
+Values represent the mean of 3 ESM; error bars represent $\mp$ sd.](./Figures/Figure 4.png)
 
@@
 
-While some regulatory areas of the IPHC will see an incremental increase in Pacific halibut MCP, the results for the Gulf of Maine show an overall decrease in MCP by 2050, regardless of the climate change scenario or ESM (Figure \@ref(fig:Figure5-goma)), intensifying by the end of the $21^{st}$ century (Fig.
+While some regulatory areas of the IPHC will see an incremental increase in Pacific halibut MCP, the results for the Gulf of Maine show an overall decrease in MCP by 2050, regardless of the climate change scenario or ESM (Fig.
+5), intensifying by the end of the $21^{st}$ century (Fig.
 A1.3).
-For cod and haddock, MCP will decrease within the whole Gulf with no apparent win for any country in reference to the current period (Figure \@ref(fig:Figure5-goma)).
+For cod and haddock, MCP will decrease within the whole Gulf with no apparent win for any country in reference to the current period (Fig.
+5).
 For yellowtail flounder, despite an overall reduction, some discrete areas are expected to increase with no particular pattern and high uncertainty as ESMs in these regions do not agree in the direction of change.
 Despite the overall reduction in MCP for all three species in comparison to current values, there is a benefit of achieving a low emission scenario as reductions intensify under the high emission scenario.
-
-\clearpage
 
@@
 
-```{r Figure5-goma, eval = T, echo = F, fig.height = 4, fig.width = 6, fig.cap = "Percentage change of MCP in the Gulf of Maine under, A) high emission scenario; and B) low emission for mid-century (2041-2060) relative to present (2005-2014).
-Points represent regions where models do not agree in direction of change."}
-
-Fig4 <- readPNG(paste(my_path("F"),"Figure 5.png",sep=""))
-grid.raster(Fig4)
-
-```
-
-<!-- ![Fig.
+![Fig.
 5.
 Percentage change of MCP in the Gulf of Maine under, A) high emission scenario; and B) low emission for mid-century (2041-2060) relative to present (2005-2014).
-Points represent regions where models do not agree in direction of change.](./Figures/Figure 5.png) -->
+Points represent regions where models do not agree in direction of change.](./Figures/Figure 5.png)
 
@@
 Following a high emission path will affect mostly Canada’s share of yellowtail flounder and in less degree haddock, with an increase of cod share.
-under the low emission scenario, haddock and cod patterns intensify, while yellowtail flounder’s share approaches almost no change (Figure \@ref(fig:Figure-6-goma-prop)).
+under the low emission scenario, haddock and cod patterns intensify, while yellowtail flounder’s share approaches almost no change (Fig.
+6).
 Such pattern is likely the combination of the bathymetry or the Gulf, the warming gradient, and the species distribution (see discussion).
-
-\clearpage
 
@@
 
-```{r Figure-6-goma-prop, eval = T, echo = F, fig.cap = "Changes in MCP stock-share ratio for Gulf of Maine under (A) high emission; and (B) low emission scenarios for mid 21st century (2041-2060) relative to present.
-Values represent the mean of 3 ESM; error bars represent +- sd.
-(2005-2014)."}
-
-Fig6 <- readPNG(paste(my_path("F"),"Figure 6.png",sep=""))
-grid.raster(Fig6)
-
-```
-
-<!-- ![Fig 6.Changes in MCP stock-share ratio for Gulf of Maine under (A) high emission; and (B) low emission scenarios for mid 21st century (2041-2060) relative to present.
+![Fig 6.Changes in MCP stock-share ratio for Gulf of Maine under (A) high emission; and (B) low emission scenarios for mid 21st century (2041-2060) relative to present.
 Values represent the mean of 3 ESM; error bars represent $\mp$ sd.
-(2005-2014).](./Figures/Figure 6.png) -->
-
-## Discussion
+(2005-2014).](./Figures/Figure 6.png)
+
+## DISCUSSION
 
@@
 Species such as haddock in the Atlantic [@Morley:2018fn], and big skate (*Raja binoculata*) in the Pacific coast [@Pinsky:2013jo] have been projected to shift away from the poles.
-In the Gulf of Maine, the stock-share gain of yellowtail flounder and haddock by the US (Figure \@ref(fig:Figure-6-goma-prop)) could be a response to a temperature gradient shift combined with geographic barriers as southern waters are deeper, and warming slower than northern waters (Fig A3.1.).
+In the Gulf of Maine, the stock-share gain of yellowtail flounder and haddock by the US (Fig.
+6) could be a response to a temperature gradient shift combined with geographic barriers as southern waters are deeper, and warming slower than northern waters (Fig A3.1.).
 On the other hand, Maine has seen its landings of yellowtail flounder increased at the expenses of southern states [@Pinsky:2012kq].
 This could be influencing the US gain in MCP in the GoMA in relation to Canada as species shift their distribution from lower latitudes naturally reaching the US (lower) region first.
-Geographic barriers also affect the westward increase of stock-share in IPHC regions where species can only migrate northward into the Arctic Ocean through the Bering Sea and Bering Strait [@Cheung:2015fm] (Figure \@ref(fig:Figure-4-iphc-prop)).
+Geographic barriers also affect the westward increase of stock-share in IPHC regions where species can only migrate northward into the Arctic Ocean through the Bering Sea and Bering Strait [@Cheung:2015fm] (Fig.
+4).
 As the effects of climate change endure, even with high mitigation, joint plans should prepare to face changes in the stock-share ratio of transboundary stocks along both coast of North America.
@@
 Moreover, overlapping shifting stocks could interfere in gear-limitation management rules of multiple fisheries generating conflicts between fleets [@VanDerVoo:2016uc].
-The effectiveness of the IPHC-Closed Area ("CA" in figure \@ref(fig:Figure1-map)).
-in terms of protecting juveniles has been historically questioned as trawling for other species is still allowed in the area [@Karim:2010ut; @IPHC:2017CA].
+The effectiveness of the IPHC-Closed Area ("CA" in Fig 1.) in terms of protecting juveniles has been historically questioned as trawling for other species is still allowed in the area [@Karim:2010ut; @IPHC:2017CA].
 In 2015, for example, 97% of the trawl by-catch in areas 4CDE and the Closed Area were juveniles [@IPHC:2017CA].
@@
 In our results, the "winners and losers" of climate change, and the intensity of the change, will be scenario dependent.
-For instance, stock-share of yellowtail flounder under a high emission scenario will be larger for the US while Canada's gain of haddock stock-share will be larger under a low emission scenario (Figure \@ref(fig:Figure-6-goma-prop)).
+For instance, stock-share of yellowtail flounder under a high emission scenario will be larger for the US while Canada's gain of haddock stock-share will be larger under a low emission scenario (Fig.
+6).
 Applying previously describe strategies (e.g.
@@
 Overall, results for the Gulf of Maine agree with a reduction in MCP of all three species.
-However, some discrete areas show a positive change for yellowtail flounder by mid $21^{st}$ century (Figure \@ref(fig:Figure-4-iphc-prop)), mainly driven by the GFDL model (Fig.
+However, some discrete areas show a positive change for yellowtail flounder by mid $21^{st}$ century (Fig.
+4), mainly driven by the GFDL model (Fig.
 A2.3).
@@
 
-## Conclusion
+## CONCLUSIONS
 
@@
 
-## Supplements
+# SUPPLEMENTS
 
@@
 }
-
-```
-
-<!-- # ESM uncertainty -->
-<!-- This chunk explores the uncertainty build in the ESM-DBEM  -->
-
-```{r DBEM_Uncertanty, eval = F, echo = F}
-
-#### DBEM-ESM Uncertanty
-
-Today_Uncertanty <- DBEM_Corrected %>% 
-  filter(Species %in% Selected_Species) %>% 
-  left_join(IPHC_Reg_DBEM_df,
-            by = "INDEX") %>% 
-  filter(!is.na(RegArea)) %>% 
-  mutate(RCP = ifelse(Model %in% RCP,"Low Emission","High Emission")) %>% 
-  gather("Year","MCP",Beg_In:Beg_End) %>% 
-  mutate(Period = ifelse(Year >= Beg_In & Year <= Beg_End,"Beginning","NA")) %>% 
-  group_by(RegArea,Model,RCP,Year,Period) %>% 
-  summarise(Regional_MCP =sum(MCP,na.rm=T)) %>% 
-  group_by(RegArea,Model,RCP) %>% 
-  summarise(Today_MCP =mean(Regional_MCP,na.rm=T))
-
-IPHC_MCP_Change_Uncert <- DBEM_Corrected %>% 
-  filter(Species %in% Selected_Species) %>% 
-  left_join(IPHC_Reg_DBEM_df,
-            by = "INDEX") %>% 
-  filter(!is.na(RegArea)) %>% 
-  mutate(RCP = ifelse(Model %in% RCP,"Low Emission","High Emission")) %>% 
-  gather("Year","MCP",Beg_In:End_End) %>%
-  group_by(Model,RCP,Year,RegArea) %>%
-  summarise(Regional_MCP =sum(MCP,na.rm=T)) %>% 
-  group_by(RCP,Model,RegArea) %>% # Running mean as Kleisner & Pauly 2012
-  mutate(RMean = rollmean(x = Regional_MCP, 10,
-                          align = "right",
-                          fill = Regional_MCP)
-  ) %>% 
-  mutate(GCM = ifelse(Model == "GFDL26F1" | Model == "GFDL85F1","GFDL",
-                      ifelse(Model == "IPSL26F1" | Model == "IPSL85F1", "IPSL",
-                             ifelse(Model == "MPI26F1" | Model == "MPI85F1","MPI","NA"
-                             )
-                      )
-  )
-  ) %>% 
-  filter(Year >= 2015) %>% 
-  left_join(Today_Uncertanty,
-            by = c("RegArea","Model","RCP")) %>% 
-  mutate(Index = RMean/Today_MCP)
-
-# Create and save plot
-
-ggplot(IPHC_MCP_Change_Uncert) +
-  geom_line(
-    aes(
-      x = as.numeric(Year),
-      y = Index,
-      color = GCM,
-      linetype = RCP
-    )
-  ) +
-  facet_wrap(~RegArea,
-             scales = "free_y") +
-  labs(
-    x = "Year",
-    y ="Index (Future MCP/Present)"
-  ) +
-  scale_color_manual("Global Circulation model",
-                     values=c("#EEA410","#B53CB9","#2EBC67")
-  ) +
-  scale_x_continuous(breaks = seq(2010,2100,30),
-                     limits = c(2010,2100)
-  ) +
-  my_ggtheme_p()() +
-  # Save plot
-  ggsave("Model_Uncer_Sup.png",
-         plot = .,
-         width = 12,
-         height =8,
-         units = "in",
-         path = "./Results/Sup"
-  )
-
-```
-
-```{r Figure-S1, eval = T, echo = F, fig.cap = "Variation of climate change scenarios"}
-
-FigS21 <- readPNG(paste(my_path("F"),"S21.png",sep=""))
-grid.raster(FigS21)
 
@@
 
-```{r Figure_S2, eval = T, echo = F, fig.cap = "Variation of climate change scenarios in IPHC regions 4E and 4D"}
-
-FigS22 <- readPNG(paste(my_path("F"),"S22.png",sep=""))
-grid.raster(FigS22)
+<!-- # ESM uncertainty -->
+<!-- This chunk explores the uncertainty build in the ESM-DBEM  -->
+
+```{r DBEM_Uncertanty, eval = F, echo = F}
+
+#### DBEM-ESM Uncertanty
+
+Today_Uncertanty <- DBEM_Corrected %>% 
+  filter(Species %in% Selected_Species) %>% 
+  left_join(IPHC_Reg_DBEM_df,
+            by = "INDEX") %>% 
+  filter(!is.na(RegArea)) %>% 
+  mutate(RCP = ifelse(Model %in% RCP,"Low Emission","High Emission")) %>% 
+  gather("Year","MCP",Beg_In:Beg_End) %>% 
+  mutate(Period = ifelse(Year >= Beg_In & Year <= Beg_End,"Beginning","NA")) %>% 
+  group_by(RegArea,Model,RCP,Year,Period) %>% 
+  summarise(Regional_MCP =sum(MCP,na.rm=T)) %>% 
+  group_by(RegArea,Model,RCP) %>% 
+  summarise(Today_MCP =mean(Regional_MCP,na.rm=T))
+
+IPHC_MCP_Change_Uncert <- DBEM_Corrected %>% 
+  filter(Species %in% Selected_Species) %>% 
+  left_join(IPHC_Reg_DBEM_df,
+            by = "INDEX") %>% 
+  filter(!is.na(RegArea)) %>% 
+  mutate(RCP = ifelse(Model %in% RCP,"Low Emission","High Emission")) %>% 
+  gather("Year","MCP",Beg_In:End_End) %>%
+  group_by(Model,RCP,Year,RegArea) %>%
+  summarise(Regional_MCP =sum(MCP,na.rm=T)) %>% 
+  group_by(RCP,Model,RegArea) %>% # Running mean as Kleisner & Pauly 2012
+  mutate(RMean = rollmean(x = Regional_MCP, 10,
+                          align = "right",
+                          fill = Regional_MCP)
+  ) %>% 
+  mutate(GCM = ifelse(Model == "GFDL26F1" | Model == "GFDL85F1","GFDL",
+                      ifelse(Model == "IPSL26F1" | Model == "IPSL85F1", "IPSL",
+                             ifelse(Model == "MPI26F1" | Model == "MPI85F1","MPI","NA"
+                             )
+                      )
+  )
+  ) %>% 
+  filter(Year >= 2015) %>% 
+  left_join(Today_Uncertanty,
+            by = c("RegArea","Model","RCP")) %>% 
+  mutate(Index = RMean/Today_MCP)
+
+# Create and save plot
+
+ggplot(IPHC_MCP_Change_Uncert) +
+  geom_line(
+    aes(
+      x = as.numeric(Year),
+      y = Index,
+      color = GCM,
+      linetype = RCP
+    )
+  ) +
+  facet_wrap(~RegArea,
+             scales = "free_y") +
+  labs(
+    x = "Year",
+    y ="Index (Future MCP/Present)"
+  ) +
+  scale_color_manual("Global Circulation model",
+                     values=c("#EEA410","#B53CB9","#2EBC67")
+  ) +
+  scale_x_continuous(breaks = seq(2010,2100,30),
+                     limits = c(2010,2100)
+  ) +
+  my_ggtheme_p()() +
+  # Save plot
+  ggsave("Model_Uncer_Sup.png",
+         plot = .,
+         width = 12,
+         height =8,
+         units = "in",
+         path = "./Results/Sup"
+  )
 
@@
     path = Path)
-
-```
-
-```{r Figure_S3, eval = T, echo = F, fig.cap = "Outliers GoMA"}
-
-FigS23 <- readPNG(paste(my_path("F"),"S23.png",sep=""))
-grid.raster(FigS23)
 

### 2020-05-17 Ecol/Reviewers/Submited_Response/Vanderzwagg_recomendatios.Rmd
REsponse to David including NAFO

---
title: "Second Round Reviews"
author: "Juliano Palacios Abrantes"
date: "17/05/2020"
output: pdf_document
---

Recommendation Submitted by: David VanderZwaag
-----------------------------------------------------

 The authors have substantially addressed most of the reviewer comments
 but there are still some wording issues and more substantive issues that
 should be addressed.

 Wording issues:

 Line 22...should read United Nations Law of the Sea Convention

 - We have addressed this comment

 Line 28...UNCLOS is binding international law. Do authors mean not a
 domestic law?

 - We originally meant to state that UNCLOS incentivizes states to cooperate but these are not oblide to do so. We note that this was confusing and have modified the sentence. It now reads:

*Under Article 63, UNCLOS incentives actions to cooperate on the management of shared stocks [@UnitedNations:1986tl].*

 Line 122...celebrate? Better wording might be...have used a.

- We have change the wording as suggested

 Line 125...where nor were.

 - We have addressed this comment

 Line 350...wording needs correction...within across.

 - We have addressed this comment, it now reads:

 *The potential adaptation of side payments in terms of quota swaps or allowing EEZ-fishing rights across the Gulf of Maine EEZs could be a potential solution as stocks shift due to climate change.*

 - We have addressed this comment

 Line 377...Bering Sea not Berring Sea

 - We have addressed this comment

 There are quite a few past/present tense issues which will need to be
 corrected before publication.

 Substantive issues:

 1. A major problem still surrounds the treatment of NAFO in this paper
 and the proposition that NAFO involves joint
     Canada-USA management. NAFO only manages those stocks that are in the
 Regulatory Area ( high seas) and
     those that straddle the EEZs of coastal States and the high seas.
 While NAFO Convention zonal areas are used for domestic   
     management  purposes, NAFO does not manage fisheries within the EEZs
 of Canada and the United States. The NAFO website            
     presently only lists19 stocks and 11 species subject to NAFO
 management. Table 1 suggests 26 NAFO managed species and    
     also states that the Gulf of Maine Agreement (should be Arrangement)
 species are also managed by NAFO. That is not correct.
     If the NAFO treatment is retained in the paper, then the notion that
 the stock share ratio will only be a question between
     Canada and the United States needs to be reconsidered. There are 12
 Parties to the NAFO Convention.

 - We understand the concerns of the edditor and have made very clear that we do not imply that these fisheries are soley co-managed by Canada and the US but that bnecause they are part of NAFO they are, in nature, transboundary. It now reads in the methods section

**All species under the IPHC, Pacific Salmon Commission, the Pacific Whiting Treaty, and the GoMA arrangement were analyzed as these are bi-lateral agreements. However, in the case of NAFO, the Comission is signed by 12 members and oversees the managment of 11 species in areas beyong national jurisdicions. Within the EEZs, NAFOs areas are used for management purposes but the management of stocks is made by each conuntry, unless a bilateral arrangement exists. For the purpose of this study, we assume that 26 species reported in NAFO's catch statistics fished in regions that fall within the EEZs of Canada and the United States (NAFO subareas 2s, 3s with the exception of 3M and 3N and limited to the EEZ, 4s, 5s and 6 A,B, and C), were transboundary in ntarue.**

 Note that we have updated the table to read Gulf of Maine Arrangement.

 2. The paper might provide details on how the distributions of George's
 Bank stocks have actually been shifting or not since 2010 
     when the 90% distribution formula became fully operational. Anonymous
 reviewer A raised this point but it has not been 
     adequately addressed in my opinion.

### 2020-05-19 Ecol/Manuscript_Draft.Rmd
Modifications for second round of reviews

@@
 author: "Juliano Palacios-Abrantes^1^ U. Rashid Sumaila^1^ William W. L. Cheung^1^"
-subtitle: "[Response to Reviewers]"
+subtitle: "[Response to Reviewers - Second Round]"
 date: "^1^ Institute for the Oceans and Fisheries, University of British Columbia, Vancouver, Canada"
@@
 We hypothesize that ocean warming will alter the sharing of fish stocks between the two countries, and that such changes will intensify under a high carbon emission scenario.
-Firstly, we projected changes in potential catch of 33 transboundary stocks of North America in the $21^{st}$ century based on multiple Earth system models’ simulations and species distribution models, under two climate change scenarios.
-We then look at the specific cases of the International Pacific Halibut Commission that manages pacific halibut (*Hippoglossus stenolepis*) and a resource sharing arrangement in the Gulf of Maine for cod (*Gadus morhua*), haddock (*Melanogrammus aeglefinus*) and yellowtail flounder (*Limanda ferruginea*) to discuss the management consequences of shifts in transboundary stocks.
-Results show that, even under a low emission scenario, most transboundary fish stocks sharing ratios, i.e., the proportion of the total catch of a fish stock taken by a given country, will change by 2050 relative to present in the direction as expected from the effects of ocean warming.
+We look at the specific cases of the International Pacific Halibut Commission that manages Pacific halibut (*Hippoglossus stenolepis*) and a resource sharing arrangement in the Gulf of Maine for cod (*Gadus morhua*), haddock (*Melanogrammus aeglefinus*) and yellowtail flounder (*Limanda ferruginea*) to discuss the management consequences of shifts in transboundary stocks.
+We rely on multiple Earth system models’ simulations and species distribution models to estimate the change in catch potential and stock share ratio of each transboundary stock in the $21^{st}$ century under two climate change scenarios.
+Results show that, even under a low emission scenario, most transboundary fish stocks sharing ratios, i.e., the proportion of the total catch of a fish stock taken by a given country, will change by 2050 relative to present.
 The overall reduction in catch potential, in addition to the changes in stock-share will further exacerbate trade-offs between changes in species catch potential.
@@
 In 1982, the United Nations Law of the Seas Convention (UNCLOS) formalized the concept of economic exclusive zones (EEZs) creating what we know today as shared stocks [@UnitedNations:1986tl], i.e.
-stocks migrate between countries EEZs (known as transboundary stocks) or between EEZs and the high seas (also called straddling stocks) [@Song:2017iua].
+stocks that migrate between countries EEZs (known as transboundary stocks) or between EEZs and the high seas (also called straddling stocks) [@Song:2017iua].
 Today, an estimated 347 [@Teh:2015gd] to 1500 [@Caddy:1997ue] fish stocks cross national borders, some of them jointly managed by two or more countries.
 These stocks are responsible for almost 50% of these countries total fish catches [@Teh:2015gd].
-Under Article 63, UNCLOS incentives actions to cooperate on the management of shared stocks [@UnitedNations:1986tl].
-Game theory is one of the most common approaches used to analyze the management of shared stocks, as often, success depends on effective cooperation between parties [@Munro:2002uf; @Sumaila:2013hv].
-Management of these stocks' can be convoluted due to the participation of several fishing “players”, different countries and sometimes jurisdictions within a country, the migration patterns of the stock, and their abundance fluctuation within space and time [@Munro:2002uf], Engler and Saunders this Special Feature).
+Under Article 63, UNCLOS incentives actions to cooperate on the management of shared stocks [@UnitedNations:1986tl] as often management success depends on effective cooperation between parties [@Munro:2002uf; @Sumaila:2013hv].
+Since the definition of shared stocks, game theory has been one of the most common approaches used to analyze the management of these type of stocks.
+However, shared stocks' management can be convoluted due to the participation of several fishing “players”, different countries and sometimes jurisdictions within a country, the migration patterns of the stock, and their abundance fluctuation within space and time [@Munro:2002uf, Engler and Saunders this Special Feature].
 In addition, international treaties might not be prepared to address the effects that climate change will bring to shared fish stocks (Engler and Saunders this Special Feature, Koubrak and VanderZwaag, this Special Feature).
@@
 Moreover, these shifts are projected to continue towards the end of the $21^{st}$ century [@Cheung:2018hz].
-As a result, some countries or management jurisdictions may see more shared fisheries and their catches shifting into their waters while others will stand to lose [@Miller:2013iv; @Pinsky:2018cb].
+As a result, some countries or management jurisdictions may see more shared fisheries and their catches shifting into their waters while others will stand to lose [@Oremus:2020id; @Pinsky:2018cb].
 Nevertheless, management rules for shared stocks (e.g.
@@
 
-The shifts in distribution of shared fish stocks will impact the economics of their fisheries [@Pinsky:2012kq; @Sumaila:2019gh]Sumaila et al., this Special Feature), and create international disputes between countries [@Munro:2002uf; @Spijkers:2017ij; @Pinsky:2018cb].
+The shifts in distribution of shared fish stocks will impact the economics of their fisheries [@Pinsky:2012kq; @Sumaila:2019gh, Sumaila et al., this Special Feature], and create international disputes between countries [@Munro:2002uf; @Spijkers:2017ij; @Pinsky:2018cb].
 Canada and the US share important transboundary stocks of salmon (*Oncorhynchus spp.*), Pacific halibut (*Hippoglossus stenolepis*), and Atlantic cod (*Gadus morhua*) offering a unique lens to understand the extent to which climate-induced distributional shifts will challenge the future sustainability of transboundary fisheries.
-These countries have a long history of fisheries cooperation participating in diverse, jointly managed, commercial transboundary stocks through various fisheries management organizations [@NOAA:218tu].
+These countries have a long history of fisheries cooperation participating in diverse, jointly managed, commercial transboundary stocks through various fisheries management organizations [@NOAA:2018tu].
 Furthermore, climate-related fluctuations in stocks' distribution have historically created disputes between Canada and the US, increasing international conflict and threatening the health of diverse transboundary stocks [@Munro:2002uf; @CIA:2017uta].
@@
 Therefore, the main objective of this article is to assess the level of exposure that bi-lateral transboundary fisheries treaties between Canada and the US have to climate change through shifts in stock distributions.
-Specifically, we rely on a species distribution model and scenario planning to project the changes in the distribution of 33 fish stocks jointly managed by Canada and the US.
-Moreover, we use two specific case studies (the International Pacific Halibut Commission -IPHC- and a fisheries arrangement for the Gulf of Maine -GoMA-) to explore the potential impacts that climate change will have on selected transboundary stocks management.
-Finally, we explore similar situations around the world and identify opportunities to improve the adaptability of transboundary stocks management to climate change in North America.
+Specifically, we rely on a species distribution model and scenario planning to project the changes in the distribution of selected fish stocks jointly managed by Canada and the United States focusing on two case studies (the International Pacific Halibut Commission and a fisheries arrangement for the Gulf of Maine) Finally, we explore similar situations around the world and identify opportunities to improve the adaptability of transboundary stocks management to climate change in North America.
 Despite an overall expectation of species following a poleward shift, important geographic constraints (e.g.
@@
 
-The current study focuses on 33 transboundary stocks, **some of them** jointly managed by Canada and the US for both the Atlantic and the Pacific coasts (Table A3.1).
-The analysis was carried out within the 200 nautical miles of both nation’s EEZ from the Gulf of Mexico to The Labrador Sea in the Atlantic, and from California to Chukchi Sea, in the Pacific coast.
-The species analyzed (Table A2.1) were selected based on five treaties in both the Atlantic and Pacific coast of North America (Table 1).
-All species under the IPHC, Pacific Salmon Commission, the Pacific Whiting Treaty, and the GoMA arrangement were analyzed as these are bi-lateral agreements.
-**However, in the case of NAFO, the Comission is signed by 12 members and oversees the managment of 11 species in areas beyong national jurisdicions.
-Within the EEZs, NAFOs areas are used for management purposes but the management of stocks is made by each conuntry, unless a bilateral arrangement exists.
-For the purpose of this study, we assume that 26 species reported in NAFO's catch statistics fished in regions that fall within the EEZs of Canada and the United States (NAFO subareas 2s, 3s with the exception of 3M and 3N and limited to the EEZ, 4s, 5s and 6 A,B, and C), were transboundary in ntarue.** Fisheries data used in this study was gathered from the Sea Around Us from 1951 to 2014 [@Zeller2016].
-
-[^NAFO]: Northwest Atlantic Fisheries Organization, Available at https://www.nafo.int/Science/Species
-
-```{r Treaties_Table, eval = T, echo = F}
-
-# Foot note
-fn <- "*These species are also part of NAFO. This is an arrangement and not an official agreement between parties."
-
-data.table::data.table(Treaty =
-             c("International Pacific Halibut Commission (IPHC)",
-              "Pacific Salmon Commission (PSC)",
-              "Pacific Whiting Treaty (PWT)",
-              "Northwest Atlantic Fisheries Organization (NAFO)",
-              "Gulf of Maine's Arrangement (GoMA)"),
-            Species =
-             c(1,
-              5,
-              1,
-              26,
-              "3*"),
-            Coast =
-             c("Pacific",
-              "Pacific",
-              "Pacific",
-              "Atlantic",
-              "Atlantic")
-) %>% 
- kable("latex",
-    caption = "Treaties and number of species included in the current analysis."
-    ) %>% 
- add_footnote(fn)
-```
-
-We used the IPHC and the Gulf of Maine arrangement (hereafter referred as GoMA) as case studies to discuss the implications that climate change could have in the management of transboundary stocks.
+The current study used the International Pacific Halibut Commission (IPHC) and the Gulf of Maine arrangement (hereafter referred as GoMA) as case studies to discuss the implications that climate change could have in the management of transboundary stocks.
 For the IPHC, we used the most updated spatial regulatory data along its 12 regulatory areas [@IPHCSecreatriat:2017uz; @IPHC:2019wt].
 For this specific case, we considered Alaska as a separate entity, the US contiguous states as a second one (Washington, Oregon and California), and lastly British Columbia (Canada).
-For the GoMA we used NAFO's divisions 5Y, 5Ze, and 4X within latitudes 46.2°N and 41.5°S, and longitudes -72°W and -64°E (Fig.
+For the GoMA we used the Northwest Atlantic Fisheries Organization's (NAFO) divisions 5Y, 5Ze, and 4X[^NAFO] within latitudes 46.2°N and 41.5°S, and longitudes -72°W and -64°E (Fig.
 1).
+Is worth mention that, while NAFO's regulatory areas were used in this study for domestic management, NAFO does not manage fisheries within the EEZs of Canada and the United States.
+Fisheries data was gathered from the Sea Around Us from 1951 to 2014 [@Zeller2016].
+
+[^NAFO]: Northwest Atlantic Fisheries Organization, Available at https://www.nafo.int/Science/
 
@@
 
-![Fig 1. Map of North America with the regulatory areas of the International Paific Halibut Comission and the NAFO sub-region containing the Gulf of Maine arrangement](./Figures/Figure 1.png)
+![Fig.1. Map of Canada and the US with the regulatory areas of the International Pacific Halibut Commission and the NAFO sub-regions containing the Gulf of Maine arrangement.](./Figures/Figure 1.png)
 
@@
 
-Since 1998 Canada and the US have used a "Resource Sharing Understanding" to inform the management of Eastern George Bank's Atlantic cod (*Gadus morhua*) and haddock (*Melanogrammus aeglefinus*) and, yellowtail flounder (*Limanda ferruginea*) [@Pudden:2007bo; @CIA:2017uta; @TRAC:2016wu].
-The GoMA suggests catch-limits based on a weighted method where 10% represents the stocks’ historical distribution (from 1967 to 1994) and 90% current distributions produced by quarterly surveys and historical catch [@TRAC:2016wu].
-In 2017, the allocation proposed for the GoMA was, Atlantic cod 80% Canada to 20 % U.S, haddock 41% Canada and 59% U.S, and yellowtail flounder 31% Canada and 69% U.S [@TRAC:2016wu].
+Since 1998 Canada and the US have used a "Resource Sharing Understanding" to inform the management of Eastern George Bank's Atlantic cod (*Gadus morhua*) and haddock (*Melanogrammus aeglefinus*) and, yellowtail flounder (*Limanda ferruginea*) [@Pudden:2007bo; @TRAC:2016wu; @Song:2017va].
+The GoMA suggests catch-limits based on a weighted method where 10% represents the stocks’ historical distribution (from 1967 to 1994) and 90% current distributions produced by quarterly surveys and catch [@TRAC:2016wu].
+In 2017, the allocation proposed for the GoMA was, Atlantic cod 80% Canada and 20% U.S, haddock 41% Canada and 59% U.S, and yellowtail flounder 31% Canada and 69% U.S [@TRAC:2016wu].
 However, because this is an unofficial agreement, Canada and the US ultimately take single management decisions [@Soboil:2006gw].
@@
 The DBEM algorithm integrated ecophysiology and habitat suitability with spatial population dynamics of exploited fishes and invertebrates to project shifts in abundance and potential fisheries catches under climate change.
-The algorithm predicted species distribution based on depth and latitudinal range, habitat preferences and an index of species association with major habitat types to estimate changes in abundance distribution over a $0.5^{\circ}$ x $0.5^{\circ}$ grid of the world ocean.
+The algorithm predicted species distribution based on depth and latitudinal range, habitat preferences and an index of species association with major habitat types to estimate changes in abundance distribution over a **0.5º x 0.5º** grid of the world ocean.
 For each grid cell and time step, the model then calculated species carrying capacity according to sea surface temperature, salinity, oxygen content, sea ice extent (for polar species) and bathymetry, as well as the species preferences to these conditions.
 It then incorporated the intrinsic population growth, settled larvae, and net migration of adults from surrounding cells using an advection-diffusion-reaction equation.
-Finally, the model also simulated the effects of changes in temperature and oxygen content on growth of individuals [@Cheung:2013gk].
-Ultimately, the model simulates spatial and temporal population dynamics, and estimates a proxy of maximum sustainable yield (MSY) by applying fishing at MSY level for each grid cell, hereafter referred as maximum catch potential (MCP).
-
-The DBEM was projected using three Earth system models (ESM), the Geophysical Fluid Dynamics Laboratory Earth System Models 2M (GFDL)[^GFDL], the Institute Pierre Simon Laplace Climate Model 5 (IPSL-CM5)[^IPSL], and the Max Planck Institute for Meteorology Earth System Model (MPI)[^MPI].
-Each model was downscaled to match the DBEM $0.5^{\circ}$ x $0.5^{\circ}$ grid using the nearest neighbor method, and in some cases, bilinear interpolation [@Cheung:2016hf].
+Finally, the model also simulated the effects of changes in temperature and oxygen content on growth of individuals [@Cheung:2013gk; @Cheung:2016jd].
+Ultimately, the model simulated spatial and temporal population dynamics, and estimated a proxy of maximum sustainable yield (MSY) by applying fishing at MSY level for each grid cell, hereafter referred as maximum catch potential (MCP).
+
+We projected the DBEM using three Earth system models (ESM), the Geophysical Fluid Dynamics Laboratory Earth System Models 2M (GFDL)[^GFDL], the Institute Pierre Simon Laplace Climate Model 5 (IPSL-CM5)[^IPSL], and the Max Planck Institute for Meteorology Earth System Model (MPI)[^MPI].
+Each model was downscaled to match the DBEM **$0.5^{\circ}$ x $0.5^{\circ}$** grid using the nearest neighbor method, and in some cases, bilinear interpolation [@Cheung:2016hf].
 Finally, we used the model outputs for two scenarios of the Intergovernmental Panel on Climate Change (IPCC)-Representative Concentration Pathways (RCP) 2.6 and 8.5 representing a low greenhouse gas emission (strong mitigation) and a high greenhouse gas emission (week mitigation) scenario, respectively [@IPCC:2014bz].
-To estimate model robustness and capture the structural uncertainty build within ESM models, we averaged the DBEM results for all three models ($\mu±\sigma$) and marked regions where at least one ESM disagree in direction with the rest.
+To estimate model robustness and capture the structural uncertainty build within ESM models, we averaged the DBEM results for all three models **(<mu> +- <sigma>)** and marked regions where at least one ESM disagree in direction with the rest.
 
@@
 where *y* is year, *r* is region, *s* is species, *n* is total number of species, and $\hat{MCP}$ is the MCP averaged by the three ESMs.
-In the case of North America as a whole, and the GoM arrangement, region is defined as the $0.5^{\circ}$ x $0.5^{\circ}$ grid-cell within the EEZ and the specific NAFO regulatory areas, respectively.
-For the IPHC analysis, region is defined as the Commission's regulatory areas (Fig.
+In the case of the GoMA, region was defined as the **$0.5^{\circ}$ x $0.5^{\circ}$** grid-cell within the specific NAFO regulatory areas.
+For the IPHC analysis, region was defined as the Commission's regulatory areas (Fig.
 1).
-We then average the values in three time periods (*t*) to reduce temporal model sensitivity.
-Thus, we computed the regional percentage change in MCP ($\Delta MCP_r$) as follows:
+We then averaged the values in three time periods (*t*) to reduce temporal model sensitivity.
+Thus, we computed the regional percentage change in MCP **(<DELTA>MCPr)** as follows:
 
@@
 
-Where $X_{t}$ is the future averaged MCP for each of the two time periods analyzed in this study and $t_0$ is the present averaged MCP ($\mu$ `r Beg_In`-`r Beg_End`).
+Where $X_{t}$ is the future average MCP for each of the two time periods analyzed in this study and $t_0$ is the present averaged MCP (<mu> `r Beg_In`-`r Beg_End`).
+Note that in cases where $X_{0}$ = 0 and $X_{t}$ > 0, then **(<DELTA>MCPr)** = 100%, consequently, the opposite case would give a -100% result.
 This way, Equ.
-2 shows the percentage change in MCP by mid $21^{st}$ century when $X_T$ = $\mu$ `r Mid_In`-`r Mid_End`, and end of $21^{st}$ century when $X_T$ = $\mu$ `r End_In`-`r End_End`, relative to today ($t_0$).
-The rationale between choosing these time periods was to provide a relative short-term projection (mid-century) that would be more policy-relevant but also show the long term-trend (end of century).
+2 shows the percentage change in MCP by mid $21^{st}$ century when $X_t$ = <mu> `r Mid_In`-`r Mid_End`, and end of $21^{st}$ century when $X_t$ = <mu> `r End_In`-`r End_End`, relative to today ($t_0$).
+The rationale between choosing these time periods was to provide a relative short-term projection (mid-century) that would be more policy-relevant but also show the long-term trend (end of century).
 
@@
 In addition, we borrowed the concept of “threat point” from game theory defined as the minimum payoff that a player is willing to receive in order to cooperate with other players (see Sumaila et al., this Special Feature).
-Thus, we estimate the change in the $\hat{MCP}$ (threat point) that each country (players) would have for each species (hereafter referred as stock-share ratio), for both the IPHC and the GoMA.
-The stock-share ratio can be seen as the proportion of the stock's distribution within the study area that each country has.
-For this, we first modify Equ.
+Thus, we estimated the change in the <DELTA>MCP (threat point) that each country (players) would have for each species (hereafter referred as stock-share ratio), for both the IPHC and the GoMA.
+The stock-share ratio can be seen as the proportion of the stock’s distribution within the study area that each country has.
+For this, we first modified Equ.
 1, to estimate the aggregated yearly mean MCP of each species per region.
-We then average the results by the same previously mentioned periods (present, mid and end of the $21^{st}$ century).
-Next, for each species we estimated the stock-share ratio ($\alpha_s$) that each region had during each time period:
+We then averaged the results by the same previously motioned periods (present, mid and end of the **21st** century).
+Next, for each species we estimated the stock-share ratio **(<alpha> s)** that each region had during each time period:
 
@@
 
-Where $\theta_{rt}$ is the species' aggregated $\hat{MCP}$ of each region at time period *t*, and $\delta_{rt}$ is the species' aggregated $\hat{MCP}$ of the whole specie's distribution within the study area at the same time period.
-Finally, we estimated the percentage change in stock-share ratio substituting $X_{t_0}$ and $X_{t}$ by $\alpha_{t_0}$ and $\alpha_{t}$, respectively in Equ.
+Where **<theta>rt** is the species' aggregated $\hat{MCP}$ of each region at time period *t*, and **<delta>rt** is the species' aggregated $\hat{MCP}$ of the whole specie's distribution within the study area at the same time period.
+Finally, we estimated the percentage change in stock-share ratio substituting $X_{t_0}$ and $X_{t}$ by **<alpha>t0** and **<alpha>t**, respectively in Equ.
 2.
-The process was carried out for each ESM and results presented as mean standard deviation (sd).
+The process was carried out for each ESM and results presented as average **+-** standard deviation (sd).
 All of the analysis was done in the statistical software *R* version 3.5.2 (2018-12-20) with the associated packages, *data.table* [@Packagedatatable:2019uh], *ggrepel* [@PackageggrepelAut:2018to], *gridExtra* [@PackagegridExtraM:2017wx], *knirt* [@PackageknitrAGen:2020wt], *RColorBrewer* [@PackagerColorBrewer:2014uw], *sf* [@PackagesfSimpleF:2018vp], and *tidyverse* [@PackagetidyverseE:2017vq].
@@
 
-### North American transboundary stocks are shifting poleward
-
-```{r Changes_Data_All, eval = F, echo = F, fig.height=8, fig.width=12}
-
-# Change North America Projection for Map
-
-North_America_Land <- North_America_Land %>% 
- st_transform(crs = 4326)
-
-### Load shapefile the old way ###
-
-# Path to save the plots
-Path <- my_path("R",Extra_Path = "North_America")
-RCP = c("GFDL26F1","IPSL26F1","MPI26F1") #Low RCP
-
-#### New Future Method to account for mean +- sd of models #
-MCP_Data <- DBEM_Corrected %>% 
-  mutate(RCP = ifelse(Model %in% RCP,"Low_Emission","High_Emission")) %>% 
-  # Sum the MCP of all species in each index by model
-  group_by(INDEX,
-           Model,
-           RCP) %>% 
-  summarise_at(vars(Beg_In:End_End), sum,na.rm=T) %>% 
-  gather("Year","MCP",Beg_In:End_End) %>% 
-  # Indicate the three period times
-  mutate( 
-    Period = ifelse(Year >= Beg_In & Year <= Beg_End,"Beginning",
-                    ifelse(Year >= Mid_In & Year <= Mid_End,"Mid_Century",
-                           ifelse(Year >= End_In & Year <= End_End,"The_End_Century",
-                                  "Other_Years"))
-    )
-  ) %>% 
-  #Average per Time period
-  group_by(INDEX,Model,RCP,Period) %>% 
-  summarise(Mean_T_MCP =mean(MCP,na.rm=T)) %>% 
-  filter(Period != "Other_Years") %>% 
-  spread(Period,Mean_T_MCP) %>% #Spread to estimate MCP_Change
-  # Divide future values by present
-  mutate_at(vars(Mid_Century, 
-                 The_End_Century),
-            funs(ifelse(Begining > 0, ./Begining,.)) #if no species today value is the future
-  ) %>% 
-  # Estimate percentage change
-  mutate_at(vars(Mid_Century, 
-                 The_End_Century),
-            funs(ifelse(Begining == 0 & . == 0, 0, # If for no change than 0
-                        ifelse(Begining == 0 & . > 0, 100, # If changes from 0 to anything then 100
-                               round(-(1-.)*100) # Estimate percentage change
-                        )
-            )
-            )
-  ) %>% 
-  gather("Period","MCP_Change",Mid_Century,The_End_Century) %>% 
-  mutate(Direction = ifelse(MCP_Change >= 0, "Positive","Negative")) %>% 
-  # Average results per ESMs
-  group_by(INDEX,Period,RCP) %>% 
-  summarise_at(vars(MCP_Change),
-               funs("Mean_ESM_MCP_Chng"=mean,
-                    "sd_ESM_MCP_Chng"=sd,
-                    "N_ESMs"=n(),
-                    "Model_Agreement" = paste(length(unique(Direction)),collapse = ";")
-               )
-  ) %>%
-  mutate(
-    Model_Agreement = ifelse(Model_Agreement == 1, "Agree","Disagree"),
-    Model_Agreement_sd = ifelse(abs(Mean_ESM_MCP_Chng) < sd_ESM_MCP_Chng*2,"Disagree","Agree")
-  ) %>% 
-  left_join(DBEM_Coor,
-            by="INDEX") %>% 
-  # set everything over 100 to 100
-  mutate_at(vars(Mean_ESM_MCP_Chng,
-                 sd_ESM_MCP_Chng),
-            funs(ifelse(. > 100, 100,.)
-            )
-  )
-
-# Plot map for paper figure 
-Seq <- seq(-100,100,by=5) #Axis
-
-p <- ggplot(MCP_Data) +
- geom_tile(data = subset(MCP_Data, Period == "Mid_Century"),
-      aes(
-       x = longitude,
-       y = latitude,
-       color = Mean_ESM_MCP_Chng,
-       fill = Mean_ESM_MCP_Chng
-      )
- ) +
- geom_point(data = subset(MCP_Data, Period == "Mid_Century" & Model_Agreement == "Disagree"),
-       aes(
-        x = longitude,
-        y = latitude
-       ),
-       size = 0.1,
-       # alpha = 0.5,
-       shape = 16,
-       color = "grey20"
-       ) +
- geom_sf(data = North_America_Land, fill = "grey90") +
- facet_wrap(~RCP) +
- coord_sf(xlim = c(-190,-50)) +
- scale_color_gradient2(
-  limits=c(-100,
-       100),
-  breaks = Seq) +
- scale_fill_gradient2(
-  limits=c(-100,
-       100),
-  breaks = Seq) +
- my_ggtheme_m()()
-
- ggsave("Fig2.png",
-     plot = p,
-     width = 16,
-     height = 8,
-     units = "in",
-     path = Path)
-
-```
-
-Shifts in the distribution of 33 jointly managed transboundary stocks of North America by 2050 relative to 2010 show that MCP of transboundary stocks will overall increase in Atlantic-Canadian and Alaskan waters and decrease in Pacific-Canadian and the US contiguous states waters (Fig.
+### Projected change to species managed by the IPHC
+
+At least one third of the IPHC regulatory areas will see a reduction in MCP of Pacific halibut by 2050 relative to current MCP, regardless of the climate change scenario (Fig.
 2).
-Such changes will be more intense under the high emission scenario (Fig.
-2A).
-For most regions, losses of MCP will be more intense under a high emission scenario (Fig 2A) than under a low emission scenario (Fig 2B), however, there will be no apparent change in gain intensity between scenarios.
-Impacts of climate change are expected to intensify towards the end of the $21^{st}$ century, although with greater uncertainty (Fig A1.1).
-
-![Fig.
-2.
-Percentage change of MCP of transboundary stocks of North America for mid $21^{st}$ century (2041-2060) relative to present (2005-2014) under a A) high emission scenario and; B) low emission scenario.
-Points represent areas where at least one model do not agree in the direction of change](./Figures/Figure 2.png)
-
-```{r Changes_Per_Species_T, eval = F, echo = F }
-
-# This table provides the percentage change in MCP for each species, EEZ and RCP as well as the percentage change in Stock-share ratio.
-
-#### Mid Century result Table ####
-Areas <- c(
- "Canada (East Coast)",
- "Canada (Pacific)",
- "USA (East Coast)",
- "USA (West Coast)",
- "USA (Alaska, Arctic)",
- "USA (Alaska, Subarctic)"
-)
-
-RCP <- c("GFDL26F1","IPSL26F1","MPI26F1")
-
-Selected_Areas <- EEZIDs_List %>% 
- filter(Name %in% Areas)
-
-#### NEW ESTIMATES
-
-# Path to save the plots
-Path <- my_path("R",Extra_Path = "North_America")
-RCP = c("GFDL26F1","IPSL26F1","MPI26F1") #Low RCP
-
-# Aggregate MCP per Nation, Species, Model, RCP and Time period
-
-MCP_Species_Data <- DBEM_Corrected %>% 
-  left_join(EEZ_CellID,
-            by = "INDEX") %>% 
-  filter(EEZID %in% Selected_Areas$EEZID) %>% 
-  mutate(RCP = ifelse(Model %in% RCP,"Low_Emission","High_Emission"),
-         Nation = ifelse(EEZID >= 958, "Alaska",
-                         ifelse(EEZID == 925,"Can W",
-                                ifelse(EEZID == 851, "USA E",
-                                       ifelse( EEZID== 848, "USA W",
-                                               "Can E"))
-                         )),
-         Basin = ifelse(Nation %in% c("USA E","Can E"),"Atlantic","Pacific"),
-  ) %>% 
-  # Sum the MCP of each species by country
-  group_by(Species, Model, RCP, Nation, Basin) %>%
-  summarise_at(vars(Beg_In:End_End), sum,na.rm=T) %>% 
-  gather("Year","MCP",Beg_In:End_End) %>% 
-  mutate( # Indicate the three period times
-    Period = ifelse(Year >= Beg_In & Year <= Beg_End,"Beginning",
-                    ifelse(Year >= Mid_In & Year <= Mid_End,"Mid_Century",
-                           ifelse(Year >= End_In & Year <= End_End,"The_End_Century",
-                                  "Other_Years"))
-    )
-  ) %>% 
-  # Average by time period
-  group_by(Nation,Basin,Species,Model,RCP,Period) %>% 
-  summarise(Mean_T_MCP =mean(MCP,na.rm=T))
-
-### Estimate average change of all species ####
-
-MCP_Species_Change <- MCP_Species_Data %>% 
-  filter(Period != "Other_Years") %>% 
-  spread(Period,Mean_T_MCP) %>% #Spread to estimate MCP_Change
-  # Divide future values by present
-  mutate_at(vars(Mid_Century, 
-                 The_End_Century),
-            funs(ifelse(Begining > 0, ./Begining,.)) #if no species today value is the future
-  ) %>% 
-  # Estimate percentage change
-  mutate_at(vars(Mid_Century, 
-                 The_End_Century),
-            funs(ifelse(Begining == 0 & . == 0, 0, # If for no change than 0
-                        ifelse(Begining == 0 & . > 0, 100, # If changes from 0 to anything then 100
-                               round(-(1-.)*100) # Estimate percentage change
-                        )
-            )
-            )
-  ) %>% 
-  gather("Period","MCP_Change",Mid_Century,The_End_Century) %>% 
-  mutate(Direction = ifelse(MCP_Change >= 0, "Positive","Negative")) %>% 
-  # Average results per ESMs
-  group_by(Nation,Species,Period,RCP) %>% 
-  summarise_at(vars(MCP_Change),
-               funs("Mean_ESM_MCP_Chng"=mean,
-                    "sd_ESM_MCP_Chng"=sd,
-                    "N_ESMs"=n(),
-                    "Model_Agreement" = paste(length(unique(Direction)),collapse = ";")
-               )
-  ) %>%
-  mutate(
-    Model_Agreement = ifelse(Model_Agreement == 1, "Agree","Disagree")
-  ) %>% 
-  # set everything over 100 to 100
-  mutate_at(vars(Mean_ESM_MCP_Chng,
-                 sd_ESM_MCP_Chng),
-            funs(ifelse(. > 100, 100,.)
-            )
-  )
-
-#### Estimate Stock Share Change ####
-
-# Estimate total MCP of all species per basin
-Basin_Total <- MCP_Species_Data %>% 
-  group_by(Basin,Model,RCP,Period) %>% 
-  summarise(TB_MCP = sum(Mean_T_MCP))
-
-# Stock Share Change per EEZ
-SS_Change <- MCP_Species_Data %>% 
-  group_by(RCP,Period,Model,Nation,Basin) %>% # Estimate total MCP of all species per Nation 
-  summarise(Total_MCP = sum(Mean_T_MCP)) %>% 
-  left_join(Basin_Total,
-            by = c("RCP", "Period", "Model","Basin")) %>% 
-  mutate(Proportion = (Total_MCP/TB_MCP)*100) %>% # estimates each Country's catch proportion per period and RCP
-  group_by(Nation,RCP,Period) %>%  # Average ESMs
-  summarise(Mean_ESM_Proportion = paste(round(mean(Proportion),2)," (",round(sd(Proportion),2),")",sep="")
-  ) %>% 
-  filter(Period %in% c("Beginning","Mid_Century","The_End_Century")) %>% 
-  spread(Period,Mean_ESM_Proportion)
-
-Path <- my_path("R",Extra_Path = "North_America")
-
-#For paper (Table 2)
-write.csv(SS_Change,
-     paste(Path,"SS_Change.csv",sep=""),
-     row.names = F)
-
-```
-
-Consequently, each country’s share-ratio of different species will change with an overall benefit to northern regions, regardless of the RCP scenario.
-Overall, shifts will be amplified under the high emission scenario relative to the low greenhouse emission scenario pathway (Table 2).
-
-Table 2.
-Total stock-share of all 33 transboundary species by EEZ and emission scenario for the present, and mid and end of the $21^{st}$ century.
-Averages might not add to 100% due to model differences.
-Standard deviation of the projected values are provided in parentheses.
-
-### Projected change to species managed by the IPHC
-
-In the case of the IPHC, at least one third of regulatory areas will see a reduction in MCP of Pacific halibut by 2050 relative to current MCP, regardless of the climate change scenario (Fig.
-3).
 It is likely that the stock shift from the U.S.
@@
 Regions 4DE, the most poleward regulatory areas of the IPHC, are expected to gain MCP by mid (Fig.
-3) and end of the $21^{st}$ century (Fig.
-A1.2) under a high emission scenario due to the expansion of halibut suitable habitat as sea ice retreats (Fig.
+2) and end of the $21^{st}$ century (Fig.
+A1.1) under a high emission scenario due to the expansion of halibut suitable habitat as sea ice retreats (Fig.
 A2.1).
 In contrast, under a low emission scenario, sea ice is expected to stabilize towards mid 21st century, thus providing less “new” suitable habitat for Pacific halibut and resulting in undetectable changes in MCP for the region (Fig.
-3B) and decreasing even more towards 2100 (Fig.
-A1.2).
+2B) and decreasing even more towards 2100 (Fig.
+A1.1).
 
@@
 
-![Fig 3.
+![Fig.
+2.
 Percentage change of MCP for species managed by the IPHC for mid 21st century (2041-2060) relative to present 2005-2014 under a A) high emission scenario and B) low emission scenario.
-Labels marked with "*" represent regions where models do not agree in direction of change](./Figures/Fig3.png)
+Labels marked with "*" represent regions where models do not agree in direction of change.](./Figures/Figure 3.png)
 
 The same poleward trend is expected in the change of Pacific halibut stock-share ratio with the average proportion increasing up to 25% in some northern regions and decreasing by 10% in southern regions, relative to the present proportion (Fig.
-4).
+3).
 Maintaining emissions to lower levels through 2050 would potentially leave unchanged the stock-share ratio of three regulatory areas (3AC, and 4D) and negatively change regulatory area 2A.
@@
 ![Fig.
-4.
+3.
 Percentage change of stock-share ratio for IPHC under A) high emission scenario and B) low emission scenario for mid 21st century (2041-2060) relative to present 2005-2014.
-Values represent the mean of 3 ESM; error bars represent $\mp$ sd.](./Figures/Figure 4.png)
+Values represent the mean of 3 ESM; error bars represent $\pm$ sd.](./Figures/Figure 4.png)
 
@@
 While some regulatory areas of the IPHC will see an incremental increase in Pacific halibut MCP, the results for the Gulf of Maine show an overall decrease in MCP by 2050, regardless of the climate change scenario or ESM (Fig.
-5), intensifying by the end of the $21^{st}$ century (Fig.
-A1.3).
+4), intensifying by the end of the $21^{st}$ century (Fig.
+A1.2).
 For cod and haddock, MCP will decrease within the whole Gulf with no apparent win for any country in reference to the current period (Fig.
-5).
-For yellowtail flounder, despite an overall reduction, some discrete areas are expected to increase with no particular pattern and high uncertainty as ESMs in these regions do not agree in the direction of change.
+4).
+For yellowtail flounder, despite an overall reduction, some discrete areas are expected to increase with no particular pattern and high uncertainty, as ESMs in these regions do not agree in the direction of change (Fig.
+A2.3).
 Despite the overall reduction in MCP for all three species in comparison to current values, there is a benefit of achieving a low emission scenario as reductions intensify under the high emission scenario.
@@
 ![Fig.
-5.
+4.
 Percentage change of MCP in the Gulf of Maine under, A) high emission scenario; and B) low emission for mid-century (2041-2060) relative to present (2005-2014).
@@
 under the low emission scenario, haddock and cod patterns intensify, while yellowtail flounder’s share approaches almost no change (Fig.
-6).
+5).
 Such pattern is likely the combination of the bathymetry or the Gulf, the warming gradient, and the species distribution (see discussion).
@@
 
-![Fig 6.Changes in MCP stock-share ratio for Gulf of Maine under (A) high emission; and (B) low emission scenarios for mid 21st century (2041-2060) relative to present.
-Values represent the mean of 3 ESM; error bars represent $\mp$ sd.
-(2005-2014).](./Figures/Figure 6.png)
+![Fig.
+5.
+Changes in MCP stock-share ratio for Gulf of Maine under (A) high emission; and (B) low emission scenarios for mid 21st century (2041-2060) relative to present (2005-2014).
+Values represent the mean of 3 ESM; error bars represent $\pm$ sd.](./Figures/Figure 6.gif)
 
@@
 
-<!-- ## Species shifting towards the poles -->
-
-The results of the present study suggest that climate change would alter the MCP of 33 transboundary fish stocks in North America consequently altering Canada’s and the US’s species’ stock-share ratio, regardless of the climate change scenario.
+```{r, iphc_distr, eval = F, echo = F}
+
+library("tidyverse")
+
+iphc_2019_tsd_005 <- read_excel("/Volumes/HALL2000/Data/OC_Transboundary/iphc-2019-tsd-005.xlsx")
+
+iphc_2019_tsd_005 %>% 
+  gather("Region","Prop",-Year) %>% 
+  # filter(Year >= 2010) %>% 
+  # group_by(Region) %>% 
+  # summarise(me=mean(Prop)) %>% 
+  ggplot() +
+  # geom_bar(
+  #   aes(
+  #     x = Region,
+  #     y = me,
+  #     color = Region
+  #   ),
+  #   stat="identity"
+  # )
+  geom_line(
+    aes(
+      x = Year,
+      y = Prop,
+      color = Region
+    )
+  )
+
+```
+
+The results of the present study suggest that climate change will alter the MCP of jointly managed transboundary fish stocks in North America consequently altering Canada’s and the US’s species’ stock-share ratio, regardless of the climate change scenario.
 These results are aligned with regional [@Morley:2018fn] projections suggesting that climate change will push marine species towards the poles and deeper water [@Pinsky:2013jo] in search of their ecological niche [@Poloczanska:2016kk].
-Poleward shifts in Eastern Atlantic off the coast of the US include American lobster (*Homarus americanus*), summer (*Paralichthys dentatus*) and flounders, and red hake (*Urophycis chuss*) from North Carolina to Maine [@Pinsky:2012kq].
-However, geographic barriers [@Cheung:2015fm; @Kleisner:2016je], local temperature gradients [@Pinsky:2013jo], species interactions and human activities [@Serpetti:2017he] might change the rate and direction of species shifts.
-Species such as haddock in the Atlantic [@Morley:2018fn], and big skate (*Raja binoculata*) in the Pacific coast [@Pinsky:2013jo] have been projected to shift away from the poles.
-In the Gulf of Maine, the stock-share gain of yellowtail flounder and haddock by the US (Fig.
-6) could be a response to a temperature gradient shift combined with geographic barriers as southern waters are deeper, and warming slower than northern waters (Fig A3.1.).
-On the other hand, Maine has seen its landings of yellowtail flounder increased at the expenses of southern states [@Pinsky:2012kq].
+Moreover, IPHC data[^IPHC] suggest that some of these shits are already happening.
+For example, since 2010, the distribution proportion of Pacific halibut has increased from 9% to 11% in region 2B, from 7.5% to 13% in region 2C, and from 12.3% to 13.5% in region 4CDE.
+On the other hand, regions 3A and 3B have seen the largest decreases in the IPHC regulatory areas since 2010, from 35.3% to 30.6% and 20.6% to 15.9%, respectively.
+Similarly, in the Gulf of Maine, the projected stock-share gain of yellowtail flounder and haddock by the US (Fig.
+5) follows a historical trend where in 2019, Canada's stock-share decreased from 35% to 32% and 60% to 40% relative to 2010, respectively [@Trinko:2019ou].
+
+[^IPHC]: See IPHC Time Series Datasets, Modelled FISS Stock Distribution Estimates [internet] https://www.iphc.int/data/time-series-datasets
+
+Geographic barriers [@Cheung:2015fm; @Kleisner:2016je], local temperature gradients [@Pinsky:2013jo], species interactions and human activities [@Serpetti:2017he] might change the rate and direction of species shifts.
+For the IPHC, geographic barriers might induce a westward increase of stock-share in IPHC regions where species can only migrate northward into the Arctic Ocean through the Bering Sea and Bering Strait [@Cheung:2015fm] (Fig.
+3).
+In the Gulf of Maine, future projections could be a response to a temperature gradient shift combined with geographic barriers as southern waters are deeper and warming slower than northern waters according to the ESMs (Fig.
+A2.2).
+Moreover, Maine has seen its landings of yellowtail flounder increased at the expenses of southern states [@Pinsky:2012kq].
 This could be influencing the US gain in MCP in the GoMA in relation to Canada as species shift their distribution from lower latitudes naturally reaching the US (lower) region first.
-Geographic barriers also affect the westward increase of stock-share in IPHC regions where species can only migrate northward into the Arctic Ocean through the Bering Sea and Bering Strait [@Cheung:2015fm] (Fig.
-4).
 As the effects of climate change endure, even with high mitigation, joint plans should prepare to face changes in the stock-share ratio of transboundary stocks along both coast of North America.
@@
 Moreover, overlapping shifting stocks could interfere in gear-limitation management rules of multiple fisheries generating conflicts between fleets [@VanDerVoo:2016uc].
-The effectiveness of the IPHC-Closed Area ("CA" in Fig 1.) in terms of protecting juveniles has been historically questioned as trawling for other species is still allowed in the area [@Karim:2010ut; @IPHC:2017CA].
+The effectiveness of the IPHC-Closed Area ("CA" in Fig.1.) in terms of protecting juveniles has been historically questioned as trawling for other species is still allowed in the area [@Karim:2010ut; @IPHC:2017CA].
 In 2015, for example, 97% of the trawl by-catch in areas 4CDE and the Closed Area were juveniles [@IPHC:2017CA].
 Consequently, the Alaskan trawl fisheries has been closed before reaching annual quota due to the attainment of Pacific halibut bycatch quota limits [@Karim:2010ut].
-Thus the commission has been asked to open the closed area for Pacific halibut fishing, under the premise that the expansion of the trawl fishery is likely reducing any conservation goal for juvenile Pacific halibut [@IPHC:2017CA].
+Thus, the commission has been asked to open the closed area for Pacific halibut fishing, under the premise that the expansion of the trawl fishery is likely reducing any conservation goal for juvenile Pacific halibut [@IPHC:2017CA].
 Although not assessed in this study, some trawling target species like Pacific cod (*Gadus macrocephalus*), flathead sole (*Hippoglossoides elassodon*), and Alaskan plaice (*Limanda aspera*) have already shift their distributions due to warming waters [@Stram:2009xc] and some are expected to continue shifting in similar direction than Pacific halibut [@Pinsky:2013jo].
-The overlap of target species could be addressed by applying ecosystem-based management and dynamic management tools [@Hazen:2018fa] to manage these fisheries and reduce potential lost of sustainable harvest for both the halibut and the trawl fisheries.
+The overlap of target species could be addressed by applying ecosystem-based management and dynamic management tools [@Hazen:2018fa] to manage these fisheries and reduce potential loss of sustainable harvest for both the halibut and the trawl fisheries.
 
 Quota allocation ruled by historic distributions will most likely be outdated incentivizing maladaptation [@FAO:2018uv; @Gaines:2018sg; @Miller:2013iv].
-In Europe, for example, the EU Common Fisheries Policy quota allocation is based on historic reference period of 1973-1978 [@Harte:2019us].
+In Europe, for example, the EU Common Fisheries Policy quota allocation is based on historic reference period of the 70's [@Harte:2019us].
 However, climate change has shifted the distribution of multiple European commercial stocks [@Baudron:2020dj], outdating the fixed quotas and thus compromising the sustainability of European fisheries [@FAO:2018uv; @Baudron:2020dj].
@@
 This process is especially important for cod and haddock due to their distribution variation within the Gulf [@Soboil:2006gw; @TRAC:2016wu].
-
-Side payments have been previously used to address changes in species distribution due to environmental forcings.
+However, since 2010, when the weighted method was implemented, the quota allocation has favored the US over Canada, especially in terms of haddock and yellowtail flounder [@Trinko:2019ou].
+A perpetuation of this trend with no mitigation policy could jeopardize the arrangement as Canada's quota reduction could disincentive cooperation (see Sumaila et al., this Special Feature).
+
+Side payments have been previously used to address changes in species distribution, including cases caused by environmental forcings.
 In game theory, a side payment is received by a player as a compensation from the other player in a shared resource agreement, with the premise that cooperation will result in a better overall outcome [@Bjorndal:2012vd; @Sumaila:2013hv].
@@
 Similarly, species' quota swaps are allowed, up to a degree, within regulatory areas of the European union [@Baudron:2020dj].
-Specifically, for northern European spring spawning Herring (*Clupea harengus*), Norway, Iceland, Faroe Islands, Russia and the EU reached an agreement to manage the stock after its collapsed, partially due to climate variations [@Miller:2013iv].
-Among the implemented rules, the agreement sets a dynamic quota allocation, allows members to fish part of their quota within Norway's EEZ, and land the catch in Norwegian ports.
-In North America, Canada and the US have previous history of applying side payments when in the 70's Pacific salmon shifted its distribution resulting in large interceptions of Canada's salmon by Alaskan fisheries [@Miller:2013iv].
-The conflict was resolved by the implementation of a conservation fund that work as a side payment for both Canada and the state of Alaska [@Miller:2013iv].
-The potential adaptation of side payments in terms of quota swaps or allowing free quota fishing within across the Gulf of Maine EEZs could be a potential solution as stocks shift due to climate change.
-
-[^NR]: Joint Fish, joint Russian-Norwegian Fisheries Commission available at http://www.jointfish.com/eng/THE-FISHERIES-COMMISSION/HISTORY.html
+Specifically, for northern European spring spawning herring (*Clupea harengus*), Norway, Iceland, Faroe Islands, Russia and the EU reached an agreement to manage the stock after its collapsed, partially due to climate variations [@Miller:2013iv].
+Among the implemented rules, the agreement established a dynamic quota allocation, allowing members to fish part of their quota within Norway's EEZ, and land the catch in Norwegian ports.
+In North America, Canada and the US have previous history with the utilization of side payments when in the 70's Pacific salmon shifted its distribution resulting in large interceptions of Canada's salmon by Alaskan fisheries [@Miller:2013iv; @Song:2017va].
+The conflict was resolved by the implementation of a conservation fund that worked as a side payment for both Canada and the state of Alaska [@Miller:2013iv; @Song:2017va].
+The potential adaptation of side payments in terms of quota swaps or allocating EEZ-fishing rights across the Gulf of Maine EEZs could be a potential solution as stocks shift due to climate change.
+
+[^NR]: Joint Fish, joint Russian-Norwegian Fisheries Commission [internet] http://www.jointfish.com/eng/THE-FISHERIES-COMMISSION/HISTORY.html
 
@@
 In our results, the "winners and losers" of climate change, and the intensity of the change, will be scenario dependent.
-For instance, stock-share of yellowtail flounder under a high emission scenario will be larger for the US while Canada's gain of haddock stock-share will be larger under a low emission scenario (Fig.
-6).
+For instance, stock-share of yellowtail flounder under a high emission scenario will be larger for the US while Canada's gain of cod stock-share will be larger under a low emission scenario (Fig.
+5).
 Applying previously describe strategies (e.g.
@@
 Models are attempts to represent reality (in our case a future reality) based on observational data, previously established theory, and future scenarios, and are thus, subjected to different degrees of uncertainty [@Payne:2016gn].
-An ensemble of models is a way to present a more robust result that accounts for differences in the structural composition of each model [@Cheung:2016gv].).
+An ensemble of models is a way to present a more robust result that accounts for differences in the structural composition of each model [@Cheung:2016gv].
 In here we used three ESMs to project future changes in species maximum catch potential.
@@
 However, some discrete areas show a positive change for yellowtail flounder by mid $21^{st}$ century (Fig.
-4), mainly driven by the GFDL model (Fig.
+3), mainly driven by the GFDL model (Fig.
 A2.3).
@@
 Shifts in stocks distribution due to climate change have the potential of creating local extinction of economically important stocks while enhancing fisheries in areas where they were not present before.
-In this paper, we have explored the potential impacts of climate change in the joint management of 33 transboundary stocks managed by Canada and the US.
+In this paper, we have explored the potential impacts of climate change in the joint management of selected transboundary stocks managed by Canada and the US.
 We found that, transboundary stocks are likely to shift in the upcoming years changing the proportion of the catch of jointly managed fisheries of Canada and the US.
@@
 
-<!-- # LITERATURE CITED -->
+# LITERATURE CITED
 
@@
 -->
+
+<!-- Poleward shifts in Eastern Atlantic off the coast of the US include American lobster (*Homarus americanus*), summer (*Paralichthys dentatus*) and flounders, and red hake (*Urophycis chuss*) from North Carolina to Maine [@Pinsky:2012kq].
+-->
+<!-- Species such as haddock in the Atlantic [@Morley:2018fn], and big skate (*Raja binoculata*) in the Pacific coast [@Pinsky:2013jo] have been projected to shift away from the poles. -->
+
+```{r Treaties_Table, eval = F, echo = F}
+
+# Foot note
+fn <- "*These species are also part of NAFO. This is an arrangement and not an official agreement between parties."
+
+data.table::data.table(Treaty =
+             c("International Pacific Halibut Commission (IPHC)",
+              "Pacific Salmon Commission (PSC)",
+              "Pacific Whiting Treaty (PWT)",
+              "Northwest Atlantic Fisheries Organization (NAFO)",
+              "Gulf of Maine's Arrangement (GoMA)"),
+            Species =
+             c(1,
+              5,
+              1,
+              26,
+              "3*"),
+            Coast =
+             c("Pacific",
+              "Pacific",
+              "Pacific",
+              "Atlantic",
+              "Atlantic")
+) %>% 
+ kable("latex",
+    caption = "Treaties and number of species included in the current analysis."
+    ) %>% 
+ add_footnote(fn)
+```
+
+<!-- # Option removing NAFO -->
+<!-- ### North American transboundary stocks are shifting poleward -->
+
+```{r Changes_Data_All, eval = F, echo = F, fig.height=8, fig.width=12}
+
+# Change North America Projection for Map
+
+North_America_Land <- North_America_Land %>% 
+ st_transform(crs = 4326)
+
+### Load shapefile the old way ###
+
+# Path to save the plots
+Path <- my_path("R",Extra_Path = "North_America")
+RCP = c("GFDL26F1","IPSL26F1","MPI26F1") #Low RCP
+
+#### New Future Method to account for mean +- sd of models #
+MCP_Data <- DBEM_Corrected %>% 
+  mutate(RCP = ifelse(Model %in% RCP,"Low_Emission","High_Emission")) %>% 
+  # Sum the MCP of all species in each index by model
+  group_by(INDEX,
+           Model,
+           RCP) %>% 
+  summarise_at(vars(Beg_In:End_End), sum,na.rm=T) %>% 
+  gather("Year","MCP",Beg_In:End_End) %>% 
+  # Indicate the three period times
+  mutate( 
+    Period = ifelse(Year >= Beg_In & Year <= Beg_End,"Beginning",
+                    ifelse(Year >= Mid_In & Year <= Mid_End,"Mid_Century",
+                           ifelse(Year >= End_In & Year <= End_End,"The_End_Century",
+                                  "Other_Years"))
+    )
+  ) %>% 
+  #Average per Time period
+  group_by(INDEX,Model,RCP,Period) %>% 
+  summarise(Mean_T_MCP =mean(MCP,na.rm=T)) %>% 
+  filter(Period != "Other_Years") %>% 
+  spread(Period,Mean_T_MCP) %>% #Spread to estimate MCP_Change
+  # Divide future values by present
+  mutate_at(vars(Mid_Century, 
+                 The_End_Century),
+            funs(ifelse(Begining > 0, ./Begining,.)) #if no species today value is the future
+  ) %>% 
+  # Estimate percentage change
+  mutate_at(vars(Mid_Century, 
+                 The_End_Century),
+            funs(ifelse(Begining == 0 & . == 0, 0, # If for no change than 0
+                        ifelse(Begining == 0 & . > 0, 100, # If changes from 0 to anything then 100
+                               round(-(1-.)*100) # Estimate percentage change
+                        )
+            )
+            )
+  ) %>% 
+  gather("Period","MCP_Change",Mid_Century,The_End_Century) %>% 
+  mutate(Direction = ifelse(MCP_Change >= 0, "Positive","Negative")) %>% 
+  # Average results per ESMs
+  group_by(INDEX,Period,RCP) %>% 
+  summarise_at(vars(MCP_Change),
+               funs("Mean_ESM_MCP_Chng"=mean,
+                    "sd_ESM_MCP_Chng"=sd,
+                    "N_ESMs"=n(),
+                    "Model_Agreement" = paste(length(unique(Direction)),collapse = ";")
+               )
+  ) %>%
+  mutate(
+    Model_Agreement = ifelse(Model_Agreement == 1, "Agree","Disagree"),
+    Model_Agreement_sd = ifelse(abs(Mean_ESM_MCP_Chng) < sd_ESM_MCP_Chng*2,"Disagree","Agree")
+  ) %>% 
+  left_join(DBEM_Coor,
+            by="INDEX") %>% 
+  # set everything over 100 to 100
+  mutate_at(vars(Mean_ESM_MCP_Chng,
+                 sd_ESM_MCP_Chng),
+            funs(ifelse(. > 100, 100,.)
+            )
+  )
+
+# Plot map for paper figure 
+Seq <- seq(-100,100,by=5) #Axis
+
+p <- ggplot(MCP_Data) +
+ geom_tile(data = subset(MCP_Data, Period == "Mid_Century"),
+      aes(
+       x = longitude,
+       y = latitude,
+       color = Mean_ESM_MCP_Chng,
+       fill = Mean_ESM_MCP_Chng
+      )
+ ) +
+ geom_point(data = subset(MCP_Data, Period == "Mid_Century" & Model_Agreement == "Disagree"),
+       aes(
+        x = longitude,
+        y = latitude
+       ),
+       size = 0.1,
+       # alpha = 0.5,
+       shape = 16,
+       color = "grey20"
+       ) +
+ geom_sf(data = North_America_Land, fill = "grey90") +
+ facet_wrap(~RCP) +
+ coord_sf(xlim = c(-190,-50)) +
+ scale_color_gradient2(
+  limits=c(-100,
+       100),
+  breaks = Seq) +
+ scale_fill_gradient2(
+  limits=c(-100,
+       100),
+  breaks = Seq) +
+ my_ggtheme_m()()
+
+ ggsave("Fig2.png",
+     plot = p,
+     width = 16,
+     height = 8,
+     units = "in",
+     path = Path)
+
+```
+
+<!-- # Option removing NAFO -->
+<!-- Shifts in the distribution of 33 jointly managed transboundary stocks of North America by 2050 relative to 2010 show that MCP of transboundary stocks will overall increase in Atlantic-Canadian and Alaskan waters and decrease in Pacific-Canadian and the US contiguous states waters (Fig.
+2).
+Such changes will be more intense under the high emission scenario (Fig.
+2A).
+For most regions, losses of MCP will be more intense under a high emission scenario (Fig.2A) than under a low emission scenario (Fig.2B), however, there will be no apparent change in gain intensity between scenarios.
+Impacts of climate change are expected to intensify towards the end of the $21^{st}$ century, although with greater uncertainty (Fig.A1.1).
+-->
+
+<!-- ![Fig.
+2.
+Percentage change of MCP of transboundary stocks of North America for mid $21^{st}$ century (2041-2060) relative to present (2005-2014) under a A) high emission scenario and; B) low emission scenario.
+Points represent areas where at least one model do not agree in the direction of change](./Figures/Figure 2.png) -->
+
+```{r Changes_Per_Species_T, eval = F, echo = F }
+
+# This table provides the percentage change in MCP for each species, EEZ and RCP as well as the percentage change in Stock-share ratio.
+
+#### Mid Century result Table ####
+Areas <- c(
+ "Canada (East Coast)",
+ "Canada (Pacific)",
+ "USA (East Coast)",
+ "USA (West Coast)",
+ "USA (Alaska, Arctic)",
+ "USA (Alaska, Subarctic)"
+)
+
+RCP <- c("GFDL26F1","IPSL26F1","MPI26F1")
+
+Selected_Areas <- EEZIDs_List %>% 
+ filter(Name %in% Areas)
+
+#### NEW ESTIMATES
+
+# Path to save the plots
+Path <- my_path("R",Extra_Path = "North_America")
+RCP = c("GFDL26F1","IPSL26F1","MPI26F1") #Low RCP
+
+# Aggregate MCP per Nation, Species, Model, RCP and Time period
+
+MCP_Species_Data <- DBEM_Corrected %>% 
+  left_join(EEZ_CellID,
+            by = "INDEX") %>% 
+  filter(EEZID %in% Selected_Areas$EEZID) %>% 
+  mutate(RCP = ifelse(Model %in% RCP,"Low_Emission","High_Emission"),
+         Nation = ifelse(EEZID >= 958, "Alaska",
+                         ifelse(EEZID == 925,"Can W",
+                                ifelse(EEZID == 851, "USA E",
+                                       ifelse( EEZID== 848, "USA W",
+                                               "Can E"))
+                         )),
+         Basin = ifelse(Nation %in% c("USA E","Can E"),"Atlantic","Pacific"),
+  ) %>% 
+  # Sum the MCP of each species by country
+  group_by(Species, Model, RCP, Nation, Basin) %>%
+  summarise_at(vars(Beg_In:End_End), sum,na.rm=T) %>% 
+  gather("Year","MCP",Beg_In:End_End) %>% 
+  mutate( # Indicate the three period times
+    Period = ifelse(Year >= Beg_In & Year <= Beg_End,"Beginning",
+                    ifelse(Year >= Mid_In & Year <= Mid_End,"Mid_Century",
+                           ifelse(Year >= End_In & Year <= End_End,"The_End_Century",
+                                  "Other_Years"))
+    )
+  ) %>% 
+  # Average by time period
+  group_by(Nation,Basin,Species,Model,RCP,Period) %>% 
+  summarise(Mean_T_MCP =mean(MCP,na.rm=T))
+
+### Estimate average change of all species ####
+
+MCP_Species_Change <- MCP_Species_Data %>% 
+  filter(Period != "Other_Years") %>% 
+  spread(Period,Mean_T_MCP) %>% #Spread to estimate MCP_Change
+  # Divide future values by present
+  mutate_at(vars(Mid_Century, 
+                 The_End_Century),
+            funs(ifelse(Begining > 0, ./Begining,.)) #if no species today value is the future
+  ) %>% 
+  # Estimate percentage change
+  mutate_at(vars(Mid_Century, 
+                 The_End_Century),
+            funs(ifelse(Begining == 0 & . == 0, 0, # If for no change than 0
+                        ifelse(Begining == 0 & . > 0, 100, # If changes from 0 to anything then 100
+                               round(-(1-.)*100) # Estimate percentage change
+                        )
+            )
+            )
+  ) %>% 
+  gather("Period","MCP_Change",Mid_Century,The_End_Century) %>% 
+  mutate(Direction = ifelse(MCP_Change >= 0, "Positive","Negative")) %>% 
+  # Average results per ESMs
+  group_by(Nation,Species,Period,RCP) %>% 
+  summarise_at(vars(MCP_Change),
+               funs("Mean_ESM_MCP_Chng"=mean,
+                    "sd_ESM_MCP_Chng"=sd,
+                    "N_ESMs"=n(),
+                    "Model_Agreement" = paste(length(unique(Direction)),collapse = ";")
+               )
+  ) %>%
+  mutate(
+    Model_Agreement = ifelse(Model_Agreement == 1, "Agree","Disagree")
+  ) %>% 
+  # set everything over 100 to 100
+  mutate_at(vars(Mean_ESM_MCP_Chng,
+                 sd_ESM_MCP_Chng),
+            funs(ifelse(. > 100, 100,.)
+            )
+  )
+
+#### Estimate Stock Share Change ####
+
+# Estimate total MCP of all species per basin
+Basin_Total <- MCP_Species_Data %>% 
+  group_by(Basin,Model,RCP,Period) %>% 
+  summarise(TB_MCP = sum(Mean_T_MCP))
+
+# Stock Share Change per EEZ
+SS_Change <- MCP_Species_Data %>% 
+  group_by(RCP,Period,Model,Nation,Basin) %>% # Estimate total MCP of all species per Nation 
+  summarise(Total_MCP = sum(Mean_T_MCP)) %>% 
+  left_join(Basin_Total,
+            by = c("RCP", "Period", "Model","Basin")) %>% 
+  mutate(Proportion = (Total_MCP/TB_MCP)*100) %>% # estimates each Country's catch proportion per period and RCP
+  group_by(Nation,RCP,Period) %>%  # Average ESMs
+  summarise(Mean_ESM_Proportion = paste(round(mean(Proportion),2)," (",round(sd(Proportion),2),")",sep="")
+  ) %>% 
+  filter(Period %in% c("Beginning","Mid_Century","The_End_Century")) %>% 
+  spread(Period,Mean_ESM_Proportion)
+
+Path <- my_path("R",Extra_Path = "North_America")
+
+#For paper (Table 2)
+write.csv(SS_Change,
+     paste(Path,"SS_Change.csv",sep=""),
+     row.names = F)
+
+```
+
+<!-- Consequently, each country’s share-ratio of different species will change with an overall benefit to northern regions, regardless of the RCP scenario.
+Overall, shifts will be amplified under the high emission scenario relative to the low greenhouse emission scenario pathway (Table 2).
+-->
+
+<!-- Table 2.
+Total stock-share of all 33 transboundary species by EEZ and emission scenario for the present, and mid and end of the $21^{st}$ century.
+Averages might not add to 100% due to model differences.
+Standard deviation of the projected values are provided in parentheses.
+-->

### 2020-06-12 Ecol/Manuscript_Draft.Rmd

@@
 <!-- ##### First paragraph of paper summary -->
-In 1982, the United Nations Law of the Seas Convention (UNCLOS) formalized the concept of economic exclusive zones (EEZs) creating what we know today as shared stocks [@UnitedNations:1986tl], i.e.
+In 1982, the United Nations Law of the Sea Convention (UNCLOS) formalized the concept of economic exclusive zones (EEZs) creating what we know today as shared stocks [@UnitedNations:1986tl], i.e.
 stocks that migrate between countries EEZs (known as transboundary stocks) or between EEZs and the high seas (also called straddling stocks) [@Song:2017iua].
@@
 1).
-Is worth mention that, while NAFO's regulatory areas were used in this study for domestic management, NAFO does not manage fisheries within the EEZs of Canada and the United States.
-Fisheries data was gathered from the Sea Around Us from 1951 to 2014 [@Zeller2016].
+Is worth mention that, while NAFO's divisional zones were used in this study for domestic management, NAFO does not manage fisheries within the EEZs of Canada and the United States.
+Fisheries data fpr the projections was gathered from the Sea Around Us from 1951 to 2014 [@Zeller2016].
 
@@
 
-![Fig.1. Map of Canada and the US with the regulatory areas of the International Pacific Halibut Commission and the NAFO sub-regions containing the Gulf of Maine arrangement.](./Figures/Figure 1.png)
+<!-- ![Fig.1.
+Map of Canada and the US with the regulatory areas of the International Pacific Halibut Commission and the NAFO sub-divisions containing the Gulf of Maine arrangement.](./Figures/Figure 1.png) -->
+
+<insert Figure 1>
 
@@
 
+<insert Table 1>
+
 ### The Gulf of Maine Arrangement
@@
 Since 1998 Canada and the US have used a "Resource Sharing Understanding" to inform the management of Eastern George Bank's Atlantic cod (*Gadus morhua*) and haddock (*Melanogrammus aeglefinus*) and, yellowtail flounder (*Limanda ferruginea*) [@Pudden:2007bo; @TRAC:2016wu; @Song:2017va].
-The GoMA suggests catch-limits based on a weighted method where 10% represents the stocks’ historical distribution (from 1967 to 1994) and 90% current distributions produced by quarterly surveys and catch [@TRAC:2016wu].
-In 2017, the allocation proposed for the GoMA was, Atlantic cod 80% Canada and 20% U.S, haddock 41% Canada and 59% U.S, and yellowtail flounder 31% Canada and 69% U.S [@TRAC:2016wu].
+From 2010 onward, the GoMA suggests catch-limits based on a weighted method where 10% represents the stocks’ historical distribution (from 1967 to 1994) and 90% current distributions produced by quarterly surveys and catch [@TRAC:2016wu].
+Since its introduction, the average quota allocation for each species proposed by the GoMA has been; Atlantic cod 77% Canada and 23% US, haddock 55% Canada and 45% US, and yellowtail flounder 34% Canada and 66% US [Table 1, @TRAC:2015wj; @TRAC:2015vp; @TRAC:2015tt; @TRAC:2018tw; @TRAC:2018tj; @TRAC:2018wx; @Trinko:2019ou].
 However, because this is an unofficial agreement, Canada and the US ultimately take single management decisions [@Soboil:2006gw].
@@
 Canada inshore vessels fish cod with longline and gillnet while haddock is mainly caught with bottom otter trawl gear [@Soboil:2006gw].
+
+<insert Table 2>
 
@@
 where *y* is year, *r* is region, *s* is species, *n* is total number of species, and $\hat{MCP}$ is the MCP averaged by the three ESMs.
-In the case of the GoMA, region was defined as the **$0.5^{\circ}$ x $0.5^{\circ}$** grid-cell within the specific NAFO regulatory areas.
+In the case of the GoMA, region was defined as the **$0.5^{\circ}$ x $0.5^{\circ}$** grid-cell within the specific NAFO divisional zones.
 For the IPHC analysis, region was defined as the Commission's regulatory areas (Fig.
@@
 2).
-It is likely that the stock shift from the U.S.
+It is likely that the stock shift from the US.
 contiguous states towards Canada will offset the shift of the later towards northern regions, resulting in undetectable changes in Canadian area 2B and Alaskan 2C under both climate change scenarios.
@@
 
-<!-- On the Atlantic coast, Canada and the US are parties to Northwest Atlantic Fisheries Organization (NAFO), which oversees the management of 19 stocks of 11 species, some of which traverse Canada’s EEZ and the Regulatory Area outside the EEZ (although around 41 taxa are fished within Canadian and U.S.
+<!-- On the Atlantic coast, Canada and the US are parties to Northwest Atlantic Fisheries Organization (NAFO), which oversees the management of 19 stocks of 11 species, some of which traverse Canada’s EEZ and the Regulatory Area outside the EEZ (although around 41 taxa are fished within Canadian and US.
 waters from the southern Gulf of Maine to Greenland) [^NAFO].

### 2020-06-12 Ecol/Reviewers/Submited_Response/Second_Round/Vanderzwagg_recomendatios.Rmd

---
title: "Second Round Reviews"
author: "Juliano Palacios Abrantes"
date: "17/05/2020"
output: pdf_document
bibliography: ../../../../References/Oceans_Canada_Biblio.bib
---

Recommendation Submitted by: David VanderZwaag
-----------------------------------------------------

 The authors have substantially addressed most of the reviewer comments
 but there are still some wording issues and more substantive issues that
 should be addressed.

 Wording issues:

 Line 22...should read United Nations Law of the Sea Convention

 - We have addressed this comment

 Line 28...UNCLOS is binding international law. Do authors mean not a
 domestic law?

 - We originally meant to state that UNCLOS creates and incentive for states to cooperate but these are not oblige to do so. We note that this was confusing and have modified the sentence. It now reads:

*Under Article 63, UNCLOS incentives actions to cooperate on the management of shared stocks [@UnitedNations:1986tl] as often management success depends on effective cooperation between parties [@Munro:2002uf; @Sumaila:2013hv].*

Line 122...celebrate? Better wording might be...have used a.

- We have change the wording as suggested

 Line 125...where nor were.

 - We have addressed this comment

 Line 350...wording needs correction...within across.

 - We have addressed this comment, it now reads:

*The potential adaptation of side payments in terms of quota swaps or allocating EEZ-fishing rights across the Gulf of Maine EEZs could be a potential solution as stocks shift due to climate change.*

 Line 377...Bering Sea not Berring Sea

 - We have addressed this comment

 There are quite a few past/present tense issues which will need to be
 corrected before publication.

- We have addressed this comment

 Substantive issues:

 1. A major problem still surrounds the treatment of NAFO in this paper
 and the proposition that NAFO involves joint
     Canada-USA management. NAFO only manages those stocks that are in the
 Regulatory Area ( high seas) and
     those that straddle the EEZs of coastal States and the high seas.
 While NAFO Convention zonal areas are used for domestic   
     management  purposes, NAFO does not manage fisheries within the EEZs
 of Canada and the United States. The NAFO website            
     presently only lists19 stocks and 11 species subject to NAFO
 management. Table 1 suggests 26 NAFO managed species and    
     also states that the Gulf of Maine Agreement (should be Arrangement)
 species are also managed by NAFO. That is not correct.
     If the NAFO treatment is retained in the paper, then the notion that
 the stock share ratio will only be a question between
     Canada and the United States needs to be reconsidered. There are 12
 Parties to the NAFO Convention.

 - We thank the editor for pointing out this particular issue. We agree with the comment regarding the straddling nature of NAFO's stocks and decided to focus the paper on the two case studies. We believe the paper does not lose its main focus with this change as most of our discussion was already based on the IPHC and Gulf of Maine case studies. On the contrary, this change made the article more concise and on point. Moreover, the manuscript now aligns even more with other papers in the Special Feature (e.g Sumaila et al. uses the same species). We show here the specific changes of each section that are reflected in the manuscript:

Introduction. No changes.

Methods. Treaties table has been removed and the first paragraph now reads;

*The current study used the International Pacific Halibut Commission (IPHC) and the Gulf of Maine arrangement (hereafter referred as GoMA) as case studies to discuss the implications that climate change could have in the management of transboundary stocks. For the IPHC, we used the most updated spatial regulatory data along its 12 regulatory areas [@IPHCSecreatriat:2017uz; @IPHC:2019wt]. For this specific case, we considered Alaska as a separate entity, the US contiguous states as a second one (Washington, Oregon and California), and lastly British Columbia (Canada). For the GoMA we used the Northwest Atlantic Fisheries Organization's (NAFO) divisions 5Y, 5Ze, and 4X[^NAFO] within latitudes 46.2°N and 41.5°S, and longitudes -72°W and -64°E (Fig. 1). Is worth mention that, while NAFO's regulatory areas were used in this study for domestic management, NAFO does not manage fisheries within the EEZs of Canada and the United States. Fisheries data was gathered from the Sea Around Us from 1951 to 2014 [@Zeller2016].*

Results. The first section of the results referent to all species was removed along with Figure 1 and Table 1. Results now focus on each one of the case studies but no text was added.

Discussion. We only modified the first paragraph that now reads:

 *The results of the present study suggest that climate change will alter the MCP of jointly managed transboundary fish stocks in North America consequently altering Canada’s and the US’s species’ stock-share ratio, regardless of the climate change scenario. These results are aligned with regional [@Morley:2018fn] projections suggesting that climate change will push marine species towards the poles and deeper water [@Pinsky:2013jo] in search of their ecological niche [@Poloczanska:2016kk]. Moreover, IPHC data[^IPHC] suggest that some of these shits are already happening. For example, since 2010, the distribution proportion of Pacific halibut has increased from 9% to 11% in region 2B, from 7.5% to 13% in region 2C, and from 12.3% to 13.5% in region 4CDE. On the other hand, regions 3A and 3B have seen the largest decreases in the IPHC regulatory areas since 2010, from 35.3% to 30.6% and 20.6% to 15.9%, respectively. Similarly, in the Gulf of Maine, the projected stock-share gain of yellowtail flounder and haddock by the US (Fig. 5) follows a historical trend where in 2019, Canada's stock-share decreased from 35% to 32% and 60% to 40% relative to 2010, respectively [@Trinko:2019ou].*

 Conclusion. No change

 2. The paper might provide details on how the distributions of George's
 Bank stocks have actually been shifting or not since 2010 
     when the 90% distribution formula became fully operational. Anonymous
 reviewer A raised this point but it has not been 
     adequately addressed in my opinion.

- We expanded the current paragraph that touches in this matter. It reads in the discussion on line 301:

*By allocating quotas based on yearly surveys along the Convention area, the IPHC should be able to capture shifts in Pacific halibut distribution due to climate change, reducing the chances of over exploitation of the stock due to this shifts [@Miller:2013iv]. Similarly, for the Gulf of Maine, since the GoMA’s method to estimate quota allocation is weighted based on stocks distribution (90%) and historical catch (10%) [@TRAC:2016wu]. This process is especially important for cod and haddock due to their distribution variation within the Gulf [@Soboil:2006gw; @TRAC:2016wu]. However, since 2010, when the weighted method was implemented, the quota allocation has favored the US over Canada, especially in terms of haddock and yellowtail flounder [@Trinko:2019ou]. A perpetuation of this trend with no mitigation policy could jeopardize the arrangement as Canada's quota reduction could disincentive cooperation (see Sumaila et al., this Special Feature).*

References:

### 2020-06-12 Ecol/Reviewers/Submited_Response/Third_Round/Vanderzwagg_recomendatios.Rmd

---
title: "Second Round Reviews"
author: "Juliano Palacios Abrantes"
date: "17/05/2020"
output: pdf_document
bibliography: ../../../../References/Oceans_Canada_Biblio.bib
---

-----------------------------------------------------
Recommendation Submitted by: David VanderZwaag
-----------------------------------------------------

The authors have now responded to my last comments and most importantly
they have largely clarified the relationship of NAFO and 
Canada-USA fisheries management in the Gulf of Maine. Just three
additional comments:

1. Line 23...United Nations Law of the Sea Convention...not Seas
- Corrected in text

2. Lines 118-120...the authors might refer to more recent TRAC proposals
(2018, 2019) and it might be useful to show how the distributions 
have actually varied.from 2010-2019.

- We changed the text to included the quota average from 2010 to 2020 (rather than an specific year) and included a table with the historic TRAC proposals from the same time period, plus a four-years historic average of before the weighted method implementation (2006 to 2009) It now reads:

*Since its introduction, the average quota allocation for each species proposed by the GoMA has been; Atlantic cod 77% Canada and 23% US, haddock 55% Canada and 45% US, and yellowtail flounder 34% Canada and 66% US [Table 1, @TRAC:2015wj; @TRAC:2015vp; @TRAC:2015tt; @TRAC:2018tw; @TRAC:2018tj; @TRAC:2018wx; @Trinko:2019ou]. However, because this is an unofficial agreement, Canada and the US ultimately take single management decisions [@Soboil:2006gw].*

3. Lines 95 and 161...the term NAFO regulatory areas should be replaced
with NAFO divisional zones. This is more accurate as the NAFO
Regulatory Area is the high seas area where NAFO actually does
regulate.

- Corrected in text

### 2020-06-12 Ecol/Manuscript_Draft.Rmd

@@
 ---
-title: "Challenges to transboundary fisheries management in North America under climate change"
-author: "Juliano Palacios-Abrantes^1^ U. Rashid Sumaila^1^ William W. L. Cheung^1^"
-subtitle: "[Response to Reviewers - Second Round]"
-date: "^1^ Institute for the Oceans and Fisheries, University of British Columbia, Vancouver, Canada"
 output:
- word_document: default
- pdf_document: default
-bibliography: ../References/Oceans_Canada_Biblio.bib
+  bookdown::pdf_book:
+    toc : false
+  # pdf_document: default
+  # word_document: default
 editor_options:
@@
 csl: ../References/E&S.csl
+bibliography: ../References/Oceans_Canada_Biblio.bib
+header-includes: #allows you to add in your own Latex packages
+- \usepackage{float} #use the 'float' package
+- \floatplacement{figure}{H} #make every figure with caption = h
 ---
@@
 
-## INTRODUCTION
+## Introduction
 
 <!-- ##### First paragraph of paper summary -->
+
 In 1982, the United Nations Law of the Sea Convention (UNCLOS) formalized the concept of economic exclusive zones (EEZs) creating what we know today as shared stocks [@UnitedNations:1986tl], i.e.
@@
 ```
-
 <!-- ![Fig.1.
@@
 
+```{r Figure1-map, eval = F, echo=FALSE, fig.height = 4, fig.width = 6, fig.cap="Map of Canada and the US with the regulatory areas of the International Pacific Halibut Commission and the NAFO sub-divisions containing the Gulf of Maine arrangement"}
+
+img <- readPNG("./Figures/Figure 1.png")
+grid.raster(img)
+
+```
 <insert Figure 1>
@@
 ```{r Figure_3, eval =F, echo = F}
-
 img <- readPNG(paste(my_path("F"),"Figure 3.png",sep=""))
@@
 
-# LITERATURE CITED
-
-# SUPPLEMENTS
+## LITERATURE CITED
+
+## Supplements
+
+```{r FigureS11, eval = T, echo = F, fig.cap = "Outliers GoMA"}
+
+FigS1 <- readPNG(paste(my_path("F"),"S11.png",sep=""))
+grid.raster(FigS11)
+
+```
+
+```{r FigureS12, eval = T, echo = F, fig.cap = "Outliers GoMA"}
+
+FigS12 <- readPNG(paste(my_path("F"),"S12.png",sep=""))
+grid.raster(FigS12)
+
+```
 
@@
 }
+
+```
+
+<!-- # ESM uncertainty -->
+<!-- This chunk explores the uncertainty build in the ESM-DBEM  -->
+
+```{r DBEM_Uncertanty, eval = F, echo = F}
+
+#### DBEM-ESM Uncertanty
+
+Today_Uncertanty <- DBEM_Corrected %>% 
+  filter(Species %in% Selected_Species) %>% 
+  left_join(IPHC_Reg_DBEM_df,
+            by = "INDEX") %>% 
+  filter(!is.na(RegArea)) %>% 
+  mutate(RCP = ifelse(Model %in% RCP,"Low Emission","High Emission")) %>% 
+  gather("Year","MCP",Beg_In:Beg_End) %>% 
+  mutate(Period = ifelse(Year >= Beg_In & Year <= Beg_End,"Beginning","NA")) %>% 
+  group_by(RegArea,Model,RCP,Year,Period) %>% 
+  summarise(Regional_MCP =sum(MCP,na.rm=T)) %>% 
+  group_by(RegArea,Model,RCP) %>% 
+  summarise(Today_MCP =mean(Regional_MCP,na.rm=T))
+
+IPHC_MCP_Change_Uncert <- DBEM_Corrected %>% 
+  filter(Species %in% Selected_Species) %>% 
+  left_join(IPHC_Reg_DBEM_df,
+            by = "INDEX") %>% 
+  filter(!is.na(RegArea)) %>% 
+  mutate(RCP = ifelse(Model %in% RCP,"Low Emission","High Emission")) %>% 
+  gather("Year","MCP",Beg_In:End_End) %>%
+  group_by(Model,RCP,Year,RegArea) %>%
+  summarise(Regional_MCP =sum(MCP,na.rm=T)) %>% 
+  group_by(RCP,Model,RegArea) %>% # Running mean as Kleisner & Pauly 2012
+  mutate(RMean = rollmean(x = Regional_MCP, 10,
+                          align = "right",
+                          fill = Regional_MCP)
+  ) %>% 
+  mutate(GCM = ifelse(Model == "GFDL26F1" | Model == "GFDL85F1","GFDL",
+                      ifelse(Model == "IPSL26F1" | Model == "IPSL85F1", "IPSL",
+                             ifelse(Model == "MPI26F1" | Model == "MPI85F1","MPI","NA"
+                             )
+                      )
+  )
+  ) %>% 
+  filter(Year >= 2015) %>% 
+  left_join(Today_Uncertanty,
+            by = c("RegArea","Model","RCP")) %>% 
+  mutate(Index = RMean/Today_MCP)
+
+# Create and save plot
+
+ggplot(IPHC_MCP_Change_Uncert) +
+  geom_line(
+    aes(
+      x = as.numeric(Year),
+      y = Index,
+      color = GCM,
+      linetype = RCP
+    )
+  ) +
+  facet_wrap(~RegArea,
+             scales = "free_y") +
+  labs(
+    x = "Year",
+    y ="Index (Future MCP/Present)"
+  ) +
+  scale_color_manual("Global Circulation model",
+                     values=c("#EEA410","#B53CB9","#2EBC67")
+  ) +
+  scale_x_continuous(breaks = seq(2010,2100,30),
+                     limits = c(2010,2100)
+  ) +
+  my_ggtheme_p()() +
+  # Save plot
+  ggsave("Model_Uncer_Sup.png",
+         plot = .,
+         width = 12,
+         height =8,
+         units = "in",
+         path = "./Results/Sup"
+  )
+
+```
+
+```{r FigureS1, eval = T, echo = F, fig.cap = "Variation of climate change scenarios"}
+
+FigS21 <- readPNG(paste(my_path("F"),"S21.png",sep=""))
+grid.raster(FigS21)
 
@@
 
-<!-- # ESM uncertainty -->
-<!-- This chunk explores the uncertainty build in the ESM-DBEM  -->
-
-```{r DBEM_Uncertanty, eval = F, echo = F}
-
-#### DBEM-ESM Uncertanty
-
-Today_Uncertanty <- DBEM_Corrected %>% 
-  filter(Species %in% Selected_Species) %>% 
-  left_join(IPHC_Reg_DBEM_df,
-            by = "INDEX") %>% 
-  filter(!is.na(RegArea)) %>% 
-  mutate(RCP = ifelse(Model %in% RCP,"Low Emission","High Emission")) %>% 
-  gather("Year","MCP",Beg_In:Beg_End) %>% 
-  mutate(Period = ifelse(Year >= Beg_In & Year <= Beg_End,"Beginning","NA")) %>% 
-  group_by(RegArea,Model,RCP,Year,Period) %>% 
-  summarise(Regional_MCP =sum(MCP,na.rm=T)) %>% 
-  group_by(RegArea,Model,RCP) %>% 
-  summarise(Today_MCP =mean(Regional_MCP,na.rm=T))
-
-IPHC_MCP_Change_Uncert <- DBEM_Corrected %>% 
-  filter(Species %in% Selected_Species) %>% 
-  left_join(IPHC_Reg_DBEM_df,
-            by = "INDEX") %>% 
-  filter(!is.na(RegArea)) %>% 
-  mutate(RCP = ifelse(Model %in% RCP,"Low Emission","High Emission")) %>% 
-  gather("Year","MCP",Beg_In:End_End) %>%
-  group_by(Model,RCP,Year,RegArea) %>%
-  summarise(Regional_MCP =sum(MCP,na.rm=T)) %>% 
-  group_by(RCP,Model,RegArea) %>% # Running mean as Kleisner & Pauly 2012
-  mutate(RMean = rollmean(x = Regional_MCP, 10,
-                          align = "right",
-                          fill = Regional_MCP)
-  ) %>% 
-  mutate(GCM = ifelse(Model == "GFDL26F1" | Model == "GFDL85F1","GFDL",
-                      ifelse(Model == "IPSL26F1" | Model == "IPSL85F1", "IPSL",
-                             ifelse(Model == "MPI26F1" | Model == "MPI85F1","MPI","NA"
-                             )
-                      )
-  )
-  ) %>% 
-  filter(Year >= 2015) %>% 
-  left_join(Today_Uncertanty,
-            by = c("RegArea","Model","RCP")) %>% 
-  mutate(Index = RMean/Today_MCP)
-
-# Create and save plot
-
-ggplot(IPHC_MCP_Change_Uncert) +
-  geom_line(
-    aes(
-      x = as.numeric(Year),
-      y = Index,
-      color = GCM,
-      linetype = RCP
-    )
-  ) +
-  facet_wrap(~RegArea,
-             scales = "free_y") +
-  labs(
-    x = "Year",
-    y ="Index (Future MCP/Present)"
-  ) +
-  scale_color_manual("Global Circulation model",
-                     values=c("#EEA410","#B53CB9","#2EBC67")
-  ) +
-  scale_x_continuous(breaks = seq(2010,2100,30),
-                     limits = c(2010,2100)
-  ) +
-  my_ggtheme_p()() +
-  # Save plot
-  ggsave("Model_Uncer_Sup.png",
-         plot = .,
-         width = 12,
-         height =8,
-         units = "in",
-         path = "./Results/Sup"
-  )
+```{r FigureS2, eval = T, echo = F, fig.cap = "Variation of climate change scenarios in IPHC regions 4E and 4D"}
+
+FigS22 <- readPNG(paste(my_path("F"),"S22.png",sep=""))
+grid.raster(FigS22)
 
@@
     path = Path)
+
+```
+
+```{r FigureS3, eval = T, echo = F, fig.cap = "Outliers GoMA"}
+
+FigS23 <- readPNG(paste(my_path("F"),"S23.png",sep=""))
+grid.raster(FigS23)
+
+```
+
+```{r FigureS13, eval = T, echo = F, fig.cap = "Outliers GoMA"}
+
+FigS13 <- readPNG(paste(my_path("F"),"S13.png",sep=""))
+grid.raster(FigS13)
 

### 2020-06-12 Ecol/Manuscript_Draft.Rmd
Updated thesis file from most recent manuscript

@@
 For this specific case, we considered Alaska as a separate entity, the US contiguous states as a second one (Washington, Oregon and California), and lastly British Columbia (Canada).
-For the GoMA we used the Northwest Atlantic Fisheries Organization's (NAFO) divisions 5Y, 5Ze, and 4X[^NAFO] within latitudes 46.2°N and 41.5°S, and longitudes -72°W and -64°E (Fig.
-1).
+For the GoMA we used the Northwest Atlantic Fisheries Organization's (NAFO) divisions 5Y, 5Ze, and 4X[^NAFO] within latitudes 46.2°N and 41.5°S, and longitudes -72°W and -64°E (Figure \ref{fig:Figure1-map}).
 Is worth mention that, while NAFO's divisional zones were used in this study for domestic management, NAFO does not manage fisheries within the EEZs of Canada and the United States.
@@
 ```
-<!-- ![Fig.1.
-Map of Canada and the US with the regulatory areas of the International Pacific Halibut Commission and the NAFO sub-divisions containing the Gulf of Maine arrangement.](./Figures/Figure 1.png) -->
-
-```{r Figure1-map, eval = F, echo=FALSE, fig.height = 4, fig.width = 6, fig.cap="Map of Canada and the US with the regulatory areas of the International Pacific Halibut Commission and the NAFO sub-divisions containing the Gulf of Maine arrangement"}
+
+```{r Figure1-map, eval = T, echo=FALSE, fig.height = 4, fig.width = 6, fig.cap="Map of Canada and the US with the regulatory areas of the International Pacific Halibut Commission and the NAFO sub-divisions containing the Gulf of Maine arrangement"}
 
@@
 ```
-<insert Figure 1>
 
@@
 The DBEM algorithm integrated ecophysiology and habitat suitability with spatial population dynamics of exploited fishes and invertebrates to project shifts in abundance and potential fisheries catches under climate change.
-The algorithm predicted species distribution based on depth and latitudinal range, habitat preferences and an index of species association with major habitat types to estimate changes in abundance distribution over a **0.5º x 0.5º** grid of the world ocean.
+The algorithm predicted species distribution based on depth and latitudinal range, habitat preferences and an index of species association with major habitat types to estimate changes in abundance distribution over a $0.5^{\circ}$ x $0.5^{\circ}$ grid of the world ocean.
 For each grid cell and time step, the model then calculated species carrying capacity according to sea surface temperature, salinity, oxygen content, sea ice extent (for polar species) and bathymetry, as well as the species preferences to these conditions.
@@
 We projected the DBEM using three Earth system models (ESM), the Geophysical Fluid Dynamics Laboratory Earth System Models 2M (GFDL)[^GFDL], the Institute Pierre Simon Laplace Climate Model 5 (IPSL-CM5)[^IPSL], and the Max Planck Institute for Meteorology Earth System Model (MPI)[^MPI].
-Each model was downscaled to match the DBEM **$0.5^{\circ}$ x $0.5^{\circ}$** grid using the nearest neighbor method, and in some cases, bilinear interpolation [@Cheung:2016hf].
+Each model was downscaled to match the DBEM $0.5^{\circ}$ x $0.5^{\circ}$ grid using the nearest neighbor method, and in some cases, bilinear interpolation [@Cheung:2016hf].
 Finally, we used the model outputs for two scenarios of the Intergovernmental Panel on Climate Change (IPCC)-Representative Concentration Pathways (RCP) 2.6 and 8.5 representing a low greenhouse gas emission (strong mitigation) and a high greenhouse gas emission (week mitigation) scenario, respectively [@IPCC:2014bz].
-To estimate model robustness and capture the structural uncertainty build within ESM models, we averaged the DBEM results for all three models **(<mu> +- <sigma>)** and marked regions where at least one ESM disagree in direction with the rest.
+To estimate model robustness and capture the structural uncertainty build within ESM models, we averaged the DBEM results for all three models ($\mu \pm \sigma$) and marked regions where at least one ESM disagree in direction with the rest.
 
@@
 where *y* is year, *r* is region, *s* is species, *n* is total number of species, and $\hat{MCP}$ is the MCP averaged by the three ESMs.
-In the case of the GoMA, region was defined as the **$0.5^{\circ}$ x $0.5^{\circ}$** grid-cell within the specific NAFO divisional zones.
-For the IPHC analysis, region was defined as the Commission's regulatory areas (Fig.
-1).
+In the case of the GoMA, region was defined as the $0.5^{\circ}$ x $0.5^{\circ}$ grid-cell within the specific NAFO divisional zones.
+For the IPHC analysis, region was defined as the Commission's regulatory areas (Figure \ref{fig:Figure1-map}).
 We then averaged the values in three time periods (*t*) to reduce temporal model sensitivity.
-Thus, we computed the regional percentage change in MCP **(<DELTA>MCPr)** as follows:
+Thus, we computed the regional percentage change in MCP ($\Delta MCP$) as follows:
 
@@
 Where $X_{t}$ is the future average MCP for each of the two time periods analyzed in this study and $t_0$ is the present averaged MCP (<mu> `r Beg_In`-`r Beg_End`).
-Note that in cases where $X_{0}$ = 0 and $X_{t}$ > 0, then **(<DELTA>MCPr)** = 100%, consequently, the opposite case would give a -100% result.
+Note that in cases where $X_{0}$ = 0 and $X_{t}$ > 0, then ($\Delta MCP$) = 100%, consequently, the opposite case would give a -100% result.
 This way, Equ.
-2 shows the percentage change in MCP by mid $21^{st}$ century when $X_t$ = <mu> `r Mid_In`-`r Mid_End`, and end of $21^{st}$ century when $X_t$ = <mu> `r End_In`-`r End_End`, relative to today ($t_0$).
-The rationale between choosing these time periods was to provide a relative short-term projection (mid-century) that would be more policy-relevant but also show the long-term trend (end of century).
+2 shows the percentage change in MCP by mid $21^{st}$ century when $X_t$ = $\mu$ `r Mid_In`-`r Mid_End`, and end of $21^{st}$ century when $X_t$ = $\mu$ `r End_In`-`r End_End`, relative to today ($t_0$).
+The rationale between choosing these time periods was to provide a relative short-term projection (mid-century) that would be more policy-relevant but also show the long-term trend (end of the century).
 
@@
 In addition, we borrowed the concept of “threat point” from game theory defined as the minimum payoff that a player is willing to receive in order to cooperate with other players (see Sumaila et al., this Special Feature).
-Thus, we estimated the change in the <DELTA>MCP (threat point) that each country (players) would have for each species (hereafter referred as stock-share ratio), for both the IPHC and the GoMA.
+Thus, we estimated the change in the ($\Delta MCP$) (threat point) that each country (players) would have for each species (hereafter referred as stock-share ratio), for both the IPHC and the GoMA.
 The stock-share ratio can be seen as the proportion of the stock’s distribution within the study area that each country has.
@@
 1, to estimate the aggregated yearly mean MCP of each species per region.
-We then averaged the results by the same previously motioned periods (present, mid and end of the **21st** century).
-Next, for each species we estimated the stock-share ratio **(<alpha> s)** that each region had during each time period:
+We then averaged the results by the same previously motioned periods (present, mid and end of the $21^{st}$ century).
+Next, for each species we estimated the stock-share ratio  ($\alpha_s$) that each region had during each time period:
 
@@
 
-Where **<theta>rt** is the species' aggregated $\hat{MCP}$ of each region at time period *t*, and **<delta>rt** is the species' aggregated $\hat{MCP}$ of the whole specie's distribution within the study area at the same time period.
-Finally, we estimated the percentage change in stock-share ratio substituting $X_{t_0}$ and $X_{t}$ by **<alpha>t0** and **<alpha>t**, respectively in Equ.
+Where $\theta_{rt}$* is the species' aggregated $\hat{MCP}$ of each region at time period *t*, and $\delta_{rt}$ is the species' aggregated $\hat{MCP}$ of the whole specie's distribution within the study area at the same time period.
+Finally, we estimated the percentage change in stock-share ratio substituting $X_{t_0}$ and $X_{t}$ by $\alpha_{t0}$ and $\alpha_t$, respectively in Equ.
 2.
-The process was carried out for each ESM and results presented as average **+-** standard deviation (sd).
+The process was carried out for each ESM and results presented as average $\pm$ standard deviation (sd).
 All of the analysis was done in the statistical software *R* version 3.5.2 (2018-12-20) with the associated packages, *data.table* [@Packagedatatable:2019uh], *ggrepel* [@PackageggrepelAut:2018to], *gridExtra* [@PackagegridExtraM:2017wx], *knirt* [@PackageknitrAGen:2020wt], *RColorBrewer* [@PackagerColorBrewer:2014uw], *sf* [@PackagesfSimpleF:2018vp], and *tidyverse* [@PackagetidyverseE:2017vq].
@@
 
-At least one third of the IPHC regulatory areas will see a reduction in MCP of Pacific halibut by 2050 relative to current MCP, regardless of the climate change scenario (Fig.
-2).
+At least one third of the IPHC regulatory areas will see a reduction in MCP of Pacific halibut by 2050 relative to current MCP, regardless of the climate change scenario (Figure \ref{fig:Figure2-IPHC}).
 It is likely that the stock shift from the US.
@@
 The potential movement of halibut westward will increase the MCP of regulatory areas 3B (under a low emission scenario) and 4ABCE along the Aleutian Islands and Bering Sea.
-Regions 4DE, the most poleward regulatory areas of the IPHC, are expected to gain MCP by mid (Fig.
-2) and end of the $21^{st}$ century (Fig.
+Regions 4DE, the most poleward regulatory areas of the IPHC, are expected to gain MCP by mid (Figure \ref{fig:Figure2-IPHC)) and end of the $21^{st}$ century (Fig.
 A1.1) under a high emission scenario due to the expansion of halibut suitable habitat as sea ice retreats (Fig.
 A2.1).
-In contrast, under a low emission scenario, sea ice is expected to stabilize towards mid 21st century, thus providing less “new” suitable habitat for Pacific halibut and resulting in undetectable changes in MCP for the region (Fig.
-2B) and decreasing even more towards 2100 (Fig.
+In contrast, under a low emission scenario, sea ice is expected to stabilize towards mid 21st century, thus providing less “new” suitable habitat for Pacific halibut and resulting in undetectable changes in MCP for the region (Figure \ref{fig:Figure2-IPHC)B) and decreasing even more towards 2100 (Fig.
 A1.1).
@@
 
-```{r Figure_3, eval =F, echo = F}
+```{r Figure2-IPHC, eval =F, echo = F, fig.cap="Percentage change of MCP for species managed by the IPHC for mid 21st century (2041-2060) relative to present 2005-2014 under a A) high emission scenario and B) low emission scenario.
+Labels marked with "*" represent regions where models do not agree in direction of change."}
+
 img <- readPNG(paste(my_path("F"),"Figure 3.png",sep=""))
@@
 
-![Fig.
+<!-- ![Fig.
 2.
 Percentage change of MCP for species managed by the IPHC for mid 21st century (2041-2060) relative to present 2005-2014 under a A) high emission scenario and B) low emission scenario.
-Labels marked with "*" represent regions where models do not agree in direction of change.](./Figures/Figure 3.png)
-
-The same poleward trend is expected in the change of Pacific halibut stock-share ratio with the average proportion increasing up to 25% in some northern regions and decreasing by 10% in southern regions, relative to the present proportion (Fig.
-3).
+Labels marked with "*" represent regions where models do not agree in direction of change.](./Figures/Figure 3.png) -->
+
+The same poleward trend is expected in the change of Pacific halibut stock-share ratio with the average proportion increasing up to 25% in some northern regions and decreasing by 10% in southern regions, relative to the present proportion (Figure \ref{fig:Figure3-IPHC-prop}).
 Maintaining emissions to lower levels through 2050 would potentially leave unchanged the stock-share ratio of three regulatory areas (3AC, and 4D) and negatively change regulatory area 2A.
@@
 
-```{r Figure_4, eval = F, echo = F}
+```{r Figure3-IPHC-prop, eval = F, echo = F, fig.cap="Percentage change of stock-share ratio for IPHC under A) high emission scenario and B) low emission scenario for mid 21st century (2041-2060) relative to present 2005-2014.
+Values represent the mean of 3 ESM; error bars represent $\pm$ sd."}
 
@@
 
-![Fig.
+<!-- ![Fig.
 3.
 Percentage change of stock-share ratio for IPHC under A) high emission scenario and B) low emission scenario for mid 21st century (2041-2060) relative to present 2005-2014.
-Values represent the mean of 3 ESM; error bars represent $\pm$ sd.](./Figures/Figure 4.png)
+Values represent the mean of 3 ESM; error bars represent $\pm$ sd.](./Figures/Figure 4.png) -->
 
@@
 
-While some regulatory areas of the IPHC will see an incremental increase in Pacific halibut MCP, the results for the Gulf of Maine show an overall decrease in MCP by 2050, regardless of the climate change scenario or ESM (Fig.
-4), intensifying by the end of the $21^{st}$ century (Fig.
+While some regulatory areas of the IPHC will see an incremental increase in Pacific halibut MCP, the results for the Gulf of Maine show an overall decrease in MCP by 2050, regardless of the climate change scenario or ESM (Figure \ref{fig:Figure4-GOMA}), intensifying by the end of the $21^{st}$ century (Fig.
 A1.2).
-For cod and haddock, MCP will decrease within the whole Gulf with no apparent win for any country in reference to the current period (Fig.
-4).
+For cod and haddock, MCP will decrease within the whole Gulf with no apparent win for any country in reference to the current period (Figure \ref{fig:Figure4-GOMA}).
 For yellowtail flounder, despite an overall reduction, some discrete areas are expected to increase with no particular pattern and high uncertainty, as ESMs in these regions do not agree in the direction of change (Fig.
@@
 
-![Fig.
+```{r Figure4-GOMA, eval = F, echo = F, fig.cap= "Percentage change of MCP in the Gulf of Maine under, A) high emission scenario; and B) low emission for mid-century (2041-2060) relative to present (2005-2014).
+Points represent regions where models do not agree in direction of change."}
+
+Fig4 <- readPNG(paste(my_path("F"),"Figure 4.png",sep=""))
+grid.raster(Fig4)
+
+```
+
+<!-- ![Fig.
 4.
 Percentage change of MCP in the Gulf of Maine under, A) high emission scenario; and B) low emission for mid-century (2041-2060) relative to present (2005-2014).
-Points represent regions where models do not agree in direction of change.](./Figures/Figure 5.png)
+Points represent regions where models do not agree in direction of change.](./Figures/Figure 5.png) -->
 
@@
 Following a high emission path will affect mostly Canada’s share of yellowtail flounder and in less degree haddock, with an increase of cod share.
-under the low emission scenario, haddock and cod patterns intensify, while yellowtail flounder’s share approaches almost no change (Fig.
-5).
+under the low emission scenario, haddock and cod patterns intensify, while yellowtail flounder’s share approaches almost no change (Figure \ref{fig:Figure5-GOMA-prop}).
 Such pattern is likely the combination of the bathymetry or the Gulf, the warming gradient, and the species distribution (see discussion).
@@
 
-![Fig.
+```{r Figure5-GOMA-prop, eval = T, echo = F, fig.cap="Changes in MCP stock-share ratio for Gulf of Maine under (A) high emission; and (B) low emission scenarios for mid 21st century (2041-2060) relative to present (2005-2014).
+Values represent the mean of 3 ESM; error bars represent $\pm$ sd."}
+
+Fig5 <- readPNG(paste(my_path("F"),"Figure 5.png",sep=""))
+grid.raster(Fig5)
+
+```
+
+<!-- ![Fig.
 5.
 Changes in MCP stock-share ratio for Gulf of Maine under (A) high emission; and (B) low emission scenarios for mid 21st century (2041-2060) relative to present (2005-2014).
-Values represent the mean of 3 ESM; error bars represent $\pm$ sd.](./Figures/Figure 6.gif)
+Values represent the mean of 3 ESM; error bars represent $\pm$ sd.](./Figures/Figure 6.gif) -->
 
@@
 On the other hand, regions 3A and 3B have seen the largest decreases in the IPHC regulatory areas since 2010, from 35.3% to 30.6% and 20.6% to 15.9%, respectively.
-Similarly, in the Gulf of Maine, the projected stock-share gain of yellowtail flounder and haddock by the US (Fig.
-5) follows a historical trend where in 2019, Canada's stock-share decreased from 35% to 32% and 60% to 40% relative to 2010, respectively [@Trinko:2019ou].
+Similarly, in the Gulf of Maine, the projected stock-share gain of yellowtail flounder and haddock by the US (Figure \ref{fig:Figure5-GOMA-prop}) follows a historical trend where in 2019, Canada's stock-share decreased from 35% to 32% and 60% to 40% relative to 2010, respectively [@Trinko:2019ou].
 
@@
 Geographic barriers [@Cheung:2015fm; @Kleisner:2016je], local temperature gradients [@Pinsky:2013jo], species interactions and human activities [@Serpetti:2017he] might change the rate and direction of species shifts.
-For the IPHC, geographic barriers might induce a westward increase of stock-share in IPHC regions where species can only migrate northward into the Arctic Ocean through the Bering Sea and Bering Strait [@Cheung:2015fm] (Fig.
-3).
+For the IPHC, geographic barriers might induce a westward increase of stock-share in IPHC regions where species can only migrate northward into the Arctic Ocean through the Bering Sea and Bering Strait [@Cheung:2015fm] (Figure \ref{fig:Figure3-IPHC-prop}).
 In the Gulf of Maine, future projections could be a response to a temperature gradient shift combined with geographic barriers as southern waters are deeper and warming slower than northern waters according to the ESMs (Fig.
@@
 In our results, the "winners and losers" of climate change, and the intensity of the change, will be scenario dependent.
-For instance, stock-share of yellowtail flounder under a high emission scenario will be larger for the US while Canada's gain of cod stock-share will be larger under a low emission scenario (Fig.
-5).
+For instance, stock-share of yellowtail flounder under a high emission scenario will be larger for the US while Canada's gain of cod stock-share will be larger under a low emission scenario (Figure \ref{fig:Figure5-GOMA-prop}).
 Applying previously describe strategies (e.g.
@@
 Overall, results for the Gulf of Maine agree with a reduction in MCP of all three species.
-However, some discrete areas show a positive change for yellowtail flounder by mid $21^{st}$ century (Fig.
-3), mainly driven by the GFDL model (Fig.
+However, some discrete areas show a positive change for yellowtail flounder by mid $21^{st}$ century (Figure \ref{fig:Figure3-IPHC-prop)), mainly driven by the GFDL model (Fig.
 A2.3).
@@
 <!-- # Option removing NAFO -->
-<!-- Shifts in the distribution of 33 jointly managed transboundary stocks of North America by 2050 relative to 2010 show that MCP of transboundary stocks will overall increase in Atlantic-Canadian and Alaskan waters and decrease in Pacific-Canadian and the US contiguous states waters (Fig.
-2).
+<!-- Shifts in the distribution of 33 jointly managed transboundary stocks of North America by 2050 relative to 2010 show that MCP of transboundary stocks will overall increase in Atlantic-Canadian and Alaskan waters and decrease in Pacific-Canadian and the US contiguous states waters (Figure \ref{fig:Figure2-IPHC}).
 Such changes will be more intense under the high emission scenario (Fig.

### 2020-06-12 Ecol/Manuscript_Draft.Rmd
Updated figures for thesis

@@
 
-Fig4 <- readPNG(paste(my_path("F"),"Figure 4.png",sep=""))
-grid.raster(Fig4)
+Fig4 <- readPNG(paste(my_path("F"),"Figure 5.png",sep=""))
+grid.raster(Fig5)
 
@@
 
-Fig5 <- readPNG(paste(my_path("F"),"Figure 5.png",sep=""))
-grid.raster(Fig5)
+Fig5 <- readPNG(paste(my_path("F"),"Figure 6.png",sep=""))
+grid.raster(Fig6)
 
@@
 
-## DISCUSSION
+## Discussion
 
@@
 
-## CONCLUSIONS
+## Conclusions
 
@@
 
-## LITERATURE CITED
+## References
 
@@
 
-```{r FigureS11, eval = T, echo = F, fig.cap = "Outliers GoMA"}
+```{r FigureS11, eval = F, echo = F, fig.cap = "Outliers GoMA"}
 

### 2020-06-12 Ecol/Manuscript_Draft.Rmd
Updated supplementals to show up

@@
 The potential movement of halibut westward will increase the MCP of regulatory areas 3B (under a low emission scenario) and 4ABCE along the Aleutian Islands and Bering Sea.
-Regions 4DE, the most poleward regulatory areas of the IPHC, are expected to gain MCP by mid (Figure \ref{fig:Figure2-IPHC)) and end of the $21^{st}$ century (Fig.
-A1.1) under a high emission scenario due to the expansion of halibut suitable habitat as sea ice retreats (Fig.
+Regions 4DE, the most poleward regulatory areas of the IPHC, are expected to gain MCP by mid (Figure \ref{fig:Figure2-IPHC)) and end of the $21^{st}$ century (Figure \ref{fig:FigureS11}) under a high emission scenario due to the expansion of halibut suitable habitat as sea ice retreats (Fig.
 A2.1).
-In contrast, under a low emission scenario, sea ice is expected to stabilize towards mid 21st century, thus providing less “new” suitable habitat for Pacific halibut and resulting in undetectable changes in MCP for the region (Figure \ref{fig:Figure2-IPHC)B) and decreasing even more towards 2100 (Fig.
-A1.1).
+In contrast, under a low emission scenario, sea ice is expected to stabilize towards mid 21st century, thus providing less “new” suitable habitat for Pacific halibut and resulting in undetectable changes in MCP for the region (Figure \ref{fig:Figure2-IPHC)B) and decreasing even more towards 2100 (Figure \ref{fig:FigureS11}).
 
@@
 
-```{r FigureS11, eval = F, echo = F, fig.cap = "Outliers GoMA"}
+<!-- End of the century change  -->
+
+```{r FigureS11, eval = F, echo = F, fig.cap = "Percentage change of MCP for species managed by the IPHC for end-century (2081–2100) referent to 2005–2014 under a (A) high emission scenario and (B) low emission scenario.
+Labels marked with "*" represent regions where models do not agree in direction of change."}
 
@@
 
-```{r FigureS12, eval = T, echo = F, fig.cap = "Outliers GoMA"}
+```{r FigureS12, eval = T, echo = F, fig.cap = "Percentage change of MCP in the Gulf of Maine under (RCP 8.5) high emission scenario and (RCP 2.6) low emission for end-century (2080–2100) referent to present (2005– 2014).
+Values represent the mean of 3 ESM.
+Points represent regions where ESMs do not agree in direction of change"}
 
@@
 <!-- NOTE: Remember to run the Results chunk to load all the data needed -->
+<!-- # ESM uncertainty -->
+<!-- This chunk explores the uncertainty build in the ESM-DBEM  -->
 
@@
 ```
-
-<!-- # ESM uncertainty -->
-<!-- This chunk explores the uncertainty build in the ESM-DBEM  -->
-
-```{r DBEM_Uncertanty, eval = F, echo = F}
-
-#### DBEM-ESM Uncertanty
-
-Today_Uncertanty <- DBEM_Corrected %>% 
-  filter(Species %in% Selected_Species) %>% 
-  left_join(IPHC_Reg_DBEM_df,
-            by = "INDEX") %>% 
-  filter(!is.na(RegArea)) %>% 
-  mutate(RCP = ifelse(Model %in% RCP,"Low Emission","High Emission")) %>% 
-  gather("Year","MCP",Beg_In:Beg_End) %>% 
-  mutate(Period = ifelse(Year >= Beg_In & Year <= Beg_End,"Beginning","NA")) %>% 
-  group_by(RegArea,Model,RCP,Year,Period) %>% 
-  summarise(Regional_MCP =sum(MCP,na.rm=T)) %>% 
-  group_by(RegArea,Model,RCP) %>% 
-  summarise(Today_MCP =mean(Regional_MCP,na.rm=T))
-
-IPHC_MCP_Change_Uncert <- DBEM_Corrected %>% 
-  filter(Species %in% Selected_Species) %>% 
-  left_join(IPHC_Reg_DBEM_df,
-            by = "INDEX") %>% 
-  filter(!is.na(RegArea)) %>% 
-  mutate(RCP = ifelse(Model %in% RCP,"Low Emission","High Emission")) %>% 
-  gather("Year","MCP",Beg_In:End_End) %>%
-  group_by(Model,RCP,Year,RegArea) %>%
-  summarise(Regional_MCP =sum(MCP,na.rm=T)) %>% 
-  group_by(RCP,Model,RegArea) %>% # Running mean as Kleisner & Pauly 2012
-  mutate(RMean = rollmean(x = Regional_MCP, 10,
-                          align = "right",
-                          fill = Regional_MCP)
-  ) %>% 
-  mutate(GCM = ifelse(Model == "GFDL26F1" | Model == "GFDL85F1","GFDL",
-                      ifelse(Model == "IPSL26F1" | Model == "IPSL85F1", "IPSL",
-                             ifelse(Model == "MPI26F1" | Model == "MPI85F1","MPI","NA"
-                             )
-                      )
-  )
-  ) %>% 
-  filter(Year >= 2015) %>% 
-  left_join(Today_Uncertanty,
-            by = c("RegArea","Model","RCP")) %>% 
-  mutate(Index = RMean/Today_MCP)
-
-# Create and save plot
-
-ggplot(IPHC_MCP_Change_Uncert) +
-  geom_line(
-    aes(
-      x = as.numeric(Year),
-      y = Index,
-      color = GCM,
-      linetype = RCP
-    )
-  ) +
-  facet_wrap(~RegArea,
-             scales = "free_y") +
-  labs(
-    x = "Year",
-    y ="Index (Future MCP/Present)"
-  ) +
-  scale_color_manual("Global Circulation model",
-                     values=c("#EEA410","#B53CB9","#2EBC67")
-  ) +
-  scale_x_continuous(breaks = seq(2010,2100,30),
-                     limits = c(2010,2100)
-  ) +
-  my_ggtheme_p()() +
-  # Save plot
-  ggsave("Model_Uncer_Sup.png",
-         plot = .,
-         width = 12,
-         height =8,
-         units = "in",
-         path = "./Results/Sup"
-  )
-
-```
-
-```{r FigureS1, eval = T, echo = F, fig.cap = "Variation of climate change scenarios"}
-
-FigS21 <- readPNG(paste(my_path("F"),"S21.png",sep=""))
-grid.raster(FigS21)
-
-```
-
-<!-- # Explore Regions 4d and 4e -->
 
@@
 
-```{r FigureS2, eval = T, echo = F, fig.cap = "Variation of climate change scenarios in IPHC regions 4E and 4D"}
-
-FigS22 <- readPNG(paste(my_path("F"),"S22.png",sep=""))
-grid.raster(FigS22)
+```{r DBEM_Uncertanty, eval = F, echo = F}
+
+#### DBEM-ESM Uncertanty
+
+Today_Uncertanty <- DBEM_Corrected %>% 
+  filter(Species %in% Selected_Species) %>% 
+  left_join(IPHC_Reg_DBEM_df,
+            by = "INDEX") %>% 
+  filter(!is.na(RegArea)) %>% 
+  mutate(RCP = ifelse(Model %in% RCP,"Low Emission","High Emission")) %>% 
+  gather("Year","MCP",Beg_In:Beg_End) %>% 
+  mutate(Period = ifelse(Year >= Beg_In & Year <= Beg_End,"Beginning","NA")) %>% 
+  group_by(RegArea,Model,RCP,Year,Period) %>% 
+  summarise(Regional_MCP =sum(MCP,na.rm=T)) %>% 
+  group_by(RegArea,Model,RCP) %>% 
+  summarise(Today_MCP =mean(Regional_MCP,na.rm=T))
+
+IPHC_MCP_Change_Uncert <- DBEM_Corrected %>% 
+  filter(Species %in% Selected_Species) %>% 
+  left_join(IPHC_Reg_DBEM_df,
+            by = "INDEX") %>% 
+  filter(!is.na(RegArea)) %>% 
+  mutate(RCP = ifelse(Model %in% RCP,"Low Emission","High Emission")) %>% 
+  gather("Year","MCP",Beg_In:End_End) %>%
+  group_by(Model,RCP,Year,RegArea) %>%
+  summarise(Regional_MCP =sum(MCP,na.rm=T)) %>% 
+  group_by(RCP,Model,RegArea) %>% # Running mean as Kleisner & Pauly 2012
+  mutate(RMean = rollmean(x = Regional_MCP, 10,
+                          align = "right",
+                          fill = Regional_MCP)
+  ) %>% 
+  mutate(GCM = ifelse(Model == "GFDL26F1" | Model == "GFDL85F1","GFDL",
+                      ifelse(Model == "IPSL26F1" | Model == "IPSL85F1", "IPSL",
+                             ifelse(Model == "MPI26F1" | Model == "MPI85F1","MPI","NA"
+                             )
+                      )
+  )
+  ) %>% 
+  filter(Year >= 2015) %>% 
+  left_join(Today_Uncertanty,
+            by = c("RegArea","Model","RCP")) %>% 
+  mutate(Index = RMean/Today_MCP)
+
+# Create and save plot
+
+ggplot(IPHC_MCP_Change_Uncert) +
+  geom_line(
+    aes(
+      x = as.numeric(Year),
+      y = Index,
+      color = GCM,
+      linetype = RCP
+    )
+  ) +
+  facet_wrap(~RegArea,
+             scales = "free_y") +
+  labs(
+    x = "Year",
+    y ="Index (Future MCP/Present)"
+  ) +
+  scale_color_manual("Global Circulation model",
+                     values=c("#EEA410","#B53CB9","#2EBC67")
+  ) +
+  scale_x_continuous(breaks = seq(2010,2100,30),
+                     limits = c(2010,2100)
+  ) +
+  my_ggtheme_p()() +
+  # Save plot
+  ggsave("Model_Uncer_Sup.png",
+         plot = .,
+         width = 12,
+         height =8,
+         units = "in",
+         path = "./Results/Sup"
+  )
 
 ```
+
+```{r FigureS21, eval = T, echo = F, fig.cap = "Projected environmental variables under climate change from 2010 to 2010 for Arctic regions of the IPHC (Top:4D, Bottom, 4E).
+The solid line represents the average of all three ESMs and the shaded area represents the model’s uncertainty (s.d.)."}
+
+FigS21 <- readPNG(paste(my_path("F"),"S21.png",sep=""))
+grid.raster(FigS21)
+
+```
+
+<!-- Explore environental differences withing GOMA -->
 
@@
 
-```{r FigureS3, eval = T, echo = F, fig.cap = "Outliers GoMA"}
-
-FigS23 <- readPNG(paste(my_path("F"),"S23.png",sep=""))
-grid.raster(FigS23)
+```{r FigureS22, eval = T, echo = F, fig.cap = "Depth profile (A) and bottom water warming of the Gulf of Maine.
+Everything deeper than 1000 meters is colored in green.
+B) Percentage change of bottom temperature relative to the present showing more intense warming in northern regions, especially under a high emission climate change scenario."}
+
+FigS23 <- readPNG(paste(my_path("F"),"S22.png",sep=""))
+grid.raster(FigS22)
 
@@
 
-```{r FigureS13, eval = T, echo = F, fig.cap = "Outliers GoMA"}
-
-FigS13 <- readPNG(paste(my_path("F"),"S13.png",sep=""))
-grid.raster(FigS13)
-
-```
+<!-- # Explore Regions 4d and 4e -->
 

### 2020-06-12 Ecol/Manuscript_Draft.Rmd
Included S24 code

@@
 
+```{r FigureS21, eval = T, echo = F, fig.cap = "Projected environmental variables under climate change from 2010 to 2010 for Arctic regions of the IPHC (Top:4D, Bottom, 4E).
+The solid line represents the average of all three ESMs and the shaded area represents the model’s uncertainty (s.d.)."}
+
+FigS21 <- readPNG(paste(my_path("F"),"S21.png",sep=""))
+grid.raster(FigS21)
+
+```
+
+<!-- Explore environental differences withing GOMA -->
+
+```{r GoM_Environ_outliers, eval = F, echo = F}
+
+# ------------------ #
+# Make maps PER model
+# ------------------ #
+
+Per_Model_Chng_GoM <- Atlantic_DBEM %>% 
+ mutate(RCP = ifelse(Model %in% c("GFDL26F1","IPSL26F1","MPI26F1"),"Low Emission","High Emission")) %>%
+ tidyr::gather("Year","Change",`2005`:`2099`) %>%
+ mutate(Change = replace_na(Change, 0)) %>% # Convert NA's into 0's
+ # Indicate the three period times
+  mutate(
+  Period = ifelse(Year >= Beg_In & Year <= Beg_End,"Beginning",
+          ifelse(Year >= Mid_In & Year <= Mid_End,"Mid_Century",
+              ifelse(Year >= End_In & Year <= End_End,"The_End_Century",
+                 "Other_Years"))
+  )
+ ) %>% 
+ filter(Period != "Other_Years",
+     Species %in% Outlier_Species) %>% # Remove unwanted years
+  # Temporal mean
+ group_by(INDEX,Model,RCP,Period,Species) %>%
+ summarise(
+  Mean_Temp = mean(Change, na.rm = T) 
+ ) %>% 
+ spread(Period,Mean_Temp) %>%
+  # Divide future values by present
+ mutate_at(vars(Mid_Century, 
+         The_End_Century),
+      funs(ifelse(Begining > 0, ./Begining,.)) #if no species today value is the future
+ ) %>% 
+   # Estimate percentage change
+ mutate_at(vars(Mid_Century,
+         The_End_Century),
+      funs(ifelse(Begining == 0 & . == 0, 0, # If for no change than 0
+            ifelse(Begining == 0 & . > 0, 100, # If changes from 0 to anything then 100
+                round(-(1-.)*100) # Estimate percentage change
+            )
+      )
+      )
+ )%>% 
+  # Set Outliers column
+ mutate(
+  Outlier = ifelse(INDEX %in% Outliers,"Yes","No")
+ ) %>% 
+ left_join(Coor) %>% 
+  # set everything over 100 to 100
+ mutate_at(vars(Mid_Century,
+         The_End_Century),
+      funs(ifelse(. > 100, 100,.)
+      ) 
+ ) #%>% 
+ # filter(Outlier == "Yes")
+
+# ----------- #
+# Plot results 
+# ----------- #
+
+ggplot(Per_Model_Chng_GoM) +
+  geom_tile(
+    aes(
+      x = Longitude,
+      y = Latitude,
+      fill = Mid_Century,
+      # fill = log10(abs(Mid_Century)),
+      color = Outlier
+      # fill = Depth
+    ),
+    size = 0.5
+  ) +
+  scale_fill_gradient2(paste("MCP Percentage Change of",Outlier_Species,"\n           (",Mid_In,"-",Mid_End,")"), # If not using the bins
+                       limits=c(Lim_Neg,
+                                Lim_Max),
+                       breaks = Seq,
+                       na.value = 'darkred' # NA values are present when the species is no more 
+  ) +
+  # Mark outliers in yellow
+  scale_color_manual(values=c(NA,"yellow")) + # for Bins option A
+  geom_sf(data = GM_Land, colour = "lightgrey") +
+  coord_sf(xlim = c(-71.0592, -63.33333),
+           ylim = c(41,45.5)
+  ) +
+  facet_wrap(~RCP+Model) +
+  my_ggtheme_m()() +
+  theme(legend.key.width =unit(6,"line"))
+
+# Name and save plot
+
+Name = "MCP_Chng_Mid_GoM_Outlier.png"
+
+ggsave(Name,
+    plot = last_plot(),
+    width = 14,
+    height = 10,
+    units = "in",
+    path = Path)
+
+```
+
+```{r FigureS22, eval = T, echo = F, fig.cap = "Depth profile (A) and bottom water warming of the Gulf of Maine.
+Everything deeper than 1000 meters is colored in green.
+B) Percentage change of bottom temperature relative to the present showing more intense warming in northern regions, especially under a high emission climate change scenario."}
+
+FigS22 <- readPNG(paste(my_path("F"),"S22.png",sep=""))
+grid.raster(FigS22)
+
+```
+
+<!-- GOMA Outliers analysis -->
+
+```{r FigureS23, eval = T, echo = F, fig.cap = "PChanges in maximum catch potential of yellowtail flounder (Limanda ferruginea) within the study area by mid-century relative to present time.
+Results for the three global circulation models (GFDL, IPSL, MPIS) used in the current study and two climate change scenarios (Top: High emission – RCP 8.5, Bottom: Low Emission – RCP 2.6).
+Grid-cells marked in yellow represent discrete areas where average MCP is projected to increase by mid-century."}
+
+FigS24 <- readPNG(paste(my_path("F"),"S24.png",sep=""))
+grid.raster(FigS24)
+
+```
+
+<!-- ESM-DBEM Uncertinty analysis -->
+
 ```{r DBEM_Uncertanty, eval = F, echo = F}
@@
 
-```{r FigureS21, eval = T, echo = F, fig.cap = "Projected environmental variables under climate change from 2010 to 2010 for Arctic regions of the IPHC (Top:4D, Bottom, 4E).
-The solid line represents the average of all three ESMs and the shaded area represents the model’s uncertainty (s.d.)."}
-
-FigS21 <- readPNG(paste(my_path("F"),"S21.png",sep=""))
-grid.raster(FigS21)
+```{r FigureS24, eval = T, echo = F, fig.cap = "Projected MCP change relative to present (2005-2014) for each IPHC regulatory area.
+Colors represents the different ESM used in the study.
+Solid line represents a high emission scenario (RCP 8.5) and dashed line represents a low emission scenario (RCP 2.6)"}
+
+FigS24 <- readPNG(paste(my_path("F"),"S24.png",sep=""))
+grid.raster(FigS24)
 
 ```
-
-<!-- Explore environental differences withing GOMA -->
-
-```{r GoM_Environ_outliers, eval = F, echo = F}
-
-# ------------------ #
-# Make maps PER model
-# ------------------ #
-
-Per_Model_Chng_GoM <- Atlantic_DBEM %>% 
- mutate(RCP = ifelse(Model %in% c("GFDL26F1","IPSL26F1","MPI26F1"),"Low Emission","High Emission")) %>%
- tidyr::gather("Year","Change",`2005`:`2099`) %>%
- mutate(Change = replace_na(Change, 0)) %>% # Convert NA's into 0's
- # Indicate the three period times
-  mutate(
-  Period = ifelse(Year >= Beg_In & Year <= Beg_End,"Beginning",
-          ifelse(Year >= Mid_In & Year <= Mid_End,"Mid_Century",
-              ifelse(Year >= End_In & Year <= End_End,"The_End_Century",
-                 "Other_Years"))
-  )
- ) %>% 
- filter(Period != "Other_Years",
-     Species %in% Outlier_Species) %>% # Remove unwanted years
-  # Temporal mean
- group_by(INDEX,Model,RCP,Period,Species) %>%
- summarise(
-  Mean_Temp = mean(Change, na.rm = T) 
- ) %>% 
- spread(Period,Mean_Temp) %>%
-  # Divide future values by present
- mutate_at(vars(Mid_Century, 
-         The_End_Century),
-      funs(ifelse(Begining > 0, ./Begining,.)) #if no species today value is the future
- ) %>% 
-   # Estimate percentage change
- mutate_at(vars(Mid_Century,
-         The_End_Century),
-      funs(ifelse(Begining == 0 & . == 0, 0, # If for no change than 0
-            ifelse(Begining == 0 & . > 0, 100, # If changes from 0 to anything then 100
-                round(-(1-.)*100) # Estimate percentage change
-            )
-      )
-      )
- )%>% 
-  # Set Outliers column
- mutate(
-  Outlier = ifelse(INDEX %in% Outliers,"Yes","No")
- ) %>% 
- left_join(Coor) %>% 
-  # set everything over 100 to 100
- mutate_at(vars(Mid_Century,
-         The_End_Century),
-      funs(ifelse(. > 100, 100,.)
-      ) 
- ) #%>% 
- # filter(Outlier == "Yes")
-
-# ----------- #
-# Plot results 
-# ----------- #
-
-ggplot(Per_Model_Chng_GoM) +
-  geom_tile(
-    aes(
-      x = Longitude,
-      y = Latitude,
-      fill = Mid_Century,
-      # fill = log10(abs(Mid_Century)),
-      color = Outlier
-      # fill = Depth
-    ),
-    size = 0.5
-  ) +
-  scale_fill_gradient2(paste("MCP Percentage Change of",Outlier_Species,"\n           (",Mid_In,"-",Mid_End,")"), # If not using the bins
-                       limits=c(Lim_Neg,
-                                Lim_Max),
-                       breaks = Seq,
-                       na.value = 'darkred' # NA values are present when the species is no more 
-  ) +
-  # Mark outliers in yellow
-  scale_color_manual(values=c(NA,"yellow")) + # for Bins option A
-  geom_sf(data = GM_Land, colour = "lightgrey") +
-  coord_sf(xlim = c(-71.0592, -63.33333),
-           ylim = c(41,45.5)
-  ) +
-  facet_wrap(~RCP+Model) +
-  my_ggtheme_m()() +
-  theme(legend.key.width =unit(6,"line"))
-
-# Name and save plot
-
-Name = "MCP_Chng_Mid_GoM_Outlier.png"
-
-ggsave(Name,
-    plot = last_plot(),
-    width = 14,
-    height = 10,
-    units = "in",
-    path = Path)
-
-```
-
-```{r FigureS22, eval = T, echo = F, fig.cap = "Depth profile (A) and bottom water warming of the Gulf of Maine.
-Everything deeper than 1000 meters is colored in green.
-B) Percentage change of bottom temperature relative to the present showing more intense warming in northern regions, especially under a high emission climate change scenario."}
-
-FigS23 <- readPNG(paste(my_path("F"),"S22.png",sep=""))
-grid.raster(FigS22)
-
-```
-
-<!-- # Explore Regions 4d and 4e -->
 

### 2020-06-12 Ecol/Manuscript_Draft.Rmd
outliers gom

@@
 
+```{r FigureS22, eval = T, echo = F, fig.cap = "Depth profile (A) and bottom water warming of the Gulf of Maine.
+Everything deeper than 1000 meters is colored in green.
+B) Percentage change of bottom temperature relative to the present showing more intense warming in northern regions, especially under a high emission climate change scenario."}
+
+FigS22 <- readPNG(paste(my_path("F"),"S22.png",sep=""))
+grid.raster(FigS22)
+
+```
+
+<!-- GOMA Outliers analysis -->
 ```{r GoM_Environ_outliers, eval = F, echo = F}
@@
 
-```{r FigureS22, eval = T, echo = F, fig.cap = "Depth profile (A) and bottom water warming of the Gulf of Maine.
-Everything deeper than 1000 meters is colored in green.
-B) Percentage change of bottom temperature relative to the present showing more intense warming in northern regions, especially under a high emission climate change scenario."}
-
-FigS22 <- readPNG(paste(my_path("F"),"S22.png",sep=""))
-grid.raster(FigS22)
-
-```
-
-<!-- GOMA Outliers analysis -->
-
-```{r FigureS23, eval = T, echo = F, fig.cap = "PChanges in maximum catch potential of yellowtail flounder (Limanda ferruginea) within the study area by mid-century relative to present time.
+```{r FigureS23, eval = T, echo = F, fig.cap = "Changes in maximum catch potential of yellowtail flounder (*Limanda ferruginea*) within the study area by mid-century relative to present time.
 Results for the three global circulation models (GFDL, IPSL, MPIS) used in the current study and two climate change scenarios (Top: High emission – RCP 8.5, Bottom: Low Emission – RCP 2.6).
@@
 
-FigS24 <- readPNG(paste(my_path("F"),"S24.png",sep=""))
-grid.raster(FigS24)
+FigS23 <- readPNG(paste(my_path("F"),"S23.png",sep=""))
+grid.raster(FigS23)
 

### 2020-06-12 Ecol/Manuscript_Draft.Rmd
Updates to thesis draft

@@
 The potential movement of halibut westward will increase the MCP of regulatory areas 3B (under a low emission scenario) and 4ABCE along the Aleutian Islands and Bering Sea.
-Regions 4DE, the most poleward regulatory areas of the IPHC, are expected to gain MCP by mid (Figure \ref{fig:Figure2-IPHC)) and end of the $21^{st}$ century (Figure \ref{fig:FigureS11}) under a high emission scenario due to the expansion of halibut suitable habitat as sea ice retreats (Fig.
-A2.1).
-In contrast, under a low emission scenario, sea ice is expected to stabilize towards mid 21st century, thus providing less “new” suitable habitat for Pacific halibut and resulting in undetectable changes in MCP for the region (Figure \ref{fig:Figure2-IPHC)B) and decreasing even more towards 2100 (Figure \ref{fig:FigureS11}).
+Regions 4DE, the most poleward regulatory areas of the IPHC, are expected to gain MCP by mid (Figure \ref{fig:Figure2-IPHC}) and end of the $21^{st}$ century (Figure \ref{fig:FigureS11}) under a high emission scenario due to the expansion of halibut suitable habitat as sea ice retreats (Figure \ref{fig:FigureS21}).
+In contrast, under a low emission scenario, sea ice is expected to stabilize towards mid 21st century, thus providing less “new” suitable habitat for Pacific halibut and resulting in undetectable changes in MCP for the region (Figure \ref{fig:Figure2-IPHC}B) and decreasing even more towards 2100 (Figure \ref{fig:FigureS11}).
 
@@
 
-```{r Figure2-IPHC, eval =F, echo = F, fig.cap="Percentage change of MCP for species managed by the IPHC for mid 21st century (2041-2060) relative to present 2005-2014 under a A) high emission scenario and B) low emission scenario.
-Labels marked with "*" represent regions where models do not agree in direction of change."}
-
-img <- readPNG(paste(my_path("F"),"Figure 3.png",sep=""))
-grid.raster(img)
+```{r Figure2-IPHC, eval = T, echo = F, fig.cap= "Percentage change of MCP for species managed by the IPHC for mid 21st century (2041-2060) relative to present 2005-2014 under a A) high emission scenario and B) low emission scenario.
+Labels marked with * represent regions where models do not agree in direction of change."}
+
+Fig2 <- readPNG(paste(my_path("F"),"Figure 2.png",sep=""))
+grid.raster(Fig2)
 
@@
 
-```{r Figure3-IPHC-prop, eval = F, echo = F, fig.cap="Percentage change of stock-share ratio for IPHC under A) high emission scenario and B) low emission scenario for mid 21st century (2041-2060) relative to present 2005-2014.
-Values represent the mean of 3 ESM; error bars represent $\pm$ sd."}
-
-Fig4 <- readPNG(paste(my_path("F"),"Figure 4.png",sep=""))
-grid.raster(Fig4)
+```{r Figure3-IPHC-prop, eval = T, echo = F, fig.cap="Percentage change of stock-share ratio for IPHC under A) high emission scenario and B) low emission scenario for mid 21st century (2041-2060) relative to present 2005-2014.
+Values represent the mean of 3 ESM; error bars represent \u00B1 sd."}
+
+Fig3 <- readPNG(paste(my_path("F"),"Figure 3.png",sep=""))
+grid.raster(Fig3)
 
@@
 
-While some regulatory areas of the IPHC will see an incremental increase in Pacific halibut MCP, the results for the Gulf of Maine show an overall decrease in MCP by 2050, regardless of the climate change scenario or ESM (Figure \ref{fig:Figure4-GOMA}), intensifying by the end of the $21^{st}$ century (Fig.
-A1.2).
+While some regulatory areas of the IPHC will see an incremental increase in Pacific halibut MCP, the results for the Gulf of Maine show an overall decrease in MCP by 2050, regardless of the climate change scenario or ESM (Figure \ref{fig:Figure4-GOMA}), intensifying by the end of the $21^{st}$ century (Figure \ref{fig:FigureS12}).
 For cod and haddock, MCP will decrease within the whole Gulf with no apparent win for any country in reference to the current period (Figure \ref{fig:Figure4-GOMA}).
-For yellowtail flounder, despite an overall reduction, some discrete areas are expected to increase with no particular pattern and high uncertainty, as ESMs in these regions do not agree in the direction of change (Fig.
-A2.3).
+For yellowtail flounder, despite an overall reduction, some discrete areas are expected to increase with no particular pattern and high uncertainty, as ESMs in these regions do not agree in the direction of change (Figure \ref{fig:FigureS23}).
 Despite the overall reduction in MCP for all three species in comparison to current values, there is a benefit of achieving a low emission scenario as reductions intensify under the high emission scenario.
@@
 
-```{r Figure4-GOMA, eval = F, echo = F, fig.cap= "Percentage change of MCP in the Gulf of Maine under, A) high emission scenario; and B) low emission for mid-century (2041-2060) relative to present (2005-2014).
+```{r Figure4-GOMA, eval = T, echo = F, fig.cap= "Percentage change of MCP in the Gulf of Maine under, A) high emission scenario; and B) low emission for mid-century (2041-2060) relative to present (2005-2014).
 Points represent regions where models do not agree in direction of change."}
 
-Fig4 <- readPNG(paste(my_path("F"),"Figure 5.png",sep=""))
-grid.raster(Fig5)
+Fig4 <- readPNG(paste(my_path("F"),"Figure 4.png",sep=""))
+grid.raster(Fig4)
 
@@
 ```{r Figure5-GOMA-prop, eval = T, echo = F, fig.cap="Changes in MCP stock-share ratio for Gulf of Maine under (A) high emission; and (B) low emission scenarios for mid 21st century (2041-2060) relative to present (2005-2014).
-Values represent the mean of 3 ESM; error bars represent $\pm$ sd."}
-
-Fig5 <- readPNG(paste(my_path("F"),"Figure 6.png",sep=""))
-grid.raster(Fig6)
+Values represent the mean of 3 ESM; error bars represent \u00B1 sd."}
+
+Fig5 <- readPNG(paste(my_path("F"),"Figure 5.png",sep=""))
+grid.raster(Fig5)
 
@@
 For the IPHC, geographic barriers might induce a westward increase of stock-share in IPHC regions where species can only migrate northward into the Arctic Ocean through the Bering Sea and Bering Strait [@Cheung:2015fm] (Figure \ref{fig:Figure3-IPHC-prop}).
-In the Gulf of Maine, future projections could be a response to a temperature gradient shift combined with geographic barriers as southern waters are deeper and warming slower than northern waters according to the ESMs (Fig.
-A2.2).
+In the Gulf of Maine, future projections could be a response to a temperature gradient shift combined with geographic barriers as southern waters are deeper and warming slower than northern waters according to the ESMs (Figure \ref{fig:FigureS22}).
 Moreover, Maine has seen its landings of yellowtail flounder increased at the expenses of southern states [@Pinsky:2012kq].
@@
 Overall, results for the Gulf of Maine agree with a reduction in MCP of all three species.
-However, some discrete areas show a positive change for yellowtail flounder by mid $21^{st}$ century (Figure \ref{fig:Figure3-IPHC-prop)), mainly driven by the GFDL model (Fig.
-A2.3).
+However, some discrete areas show a positive change for yellowtail flounder by mid $21^{st}$ century (Figure \ref{fig:Figure3-IPHC-prop)), mainly driven by the GFDL model (Figure \ref{fig:FigureS23}).
 Potential model artifacts could also be contributing to the results, especially in the northern part of the study area (Bay of Fundy) as most disagreeing grids are covered by land, which could be influencing the results.
-In contrast, considerable uncertainty exists in the change of MCP along the IPHC Convention area shown by a disagreement between ESMs (Fig.
-A2.4).
+In contrast, considerable uncertainty exists in the change of MCP along the IPHC Convention area shown by a disagreement between ESMs (Figure \ref{fig:FigureS24}).
 Off the coast of British Columbia, increasing temperature trends are consistent among ESMs, however, other processes such as acidification and deoxygenation are still not well understood from British Columbia to the Gulf of Alaska  [@TalloniAlvarez:2019gz].
@@
 
-## References
+<!-- ## References -->
 
@@
 
-```{r FigureS11, eval = F, echo = F, fig.cap = "Percentage change of MCP for species managed by the IPHC for end-century (2081–2100) referent to 2005–2014 under a (A) high emission scenario and (B) low emission scenario.
-Labels marked with "*" represent regions where models do not agree in direction of change."}
-
-FigS1 <- readPNG(paste(my_path("F"),"S11.png",sep=""))
+```{r FigureS11, eval = T, echo = F, fig.cap = "Percentage change of MCP for species managed by the IPHC for end-century (2081–2100) referent to 2005–2014 under a A) high emission scenario and B) low emission scenario.
+Labels marked with * represent regions where models do not agree in direction of change."}
+
+FigS11 <- readPNG(paste(my_path("F"),"S11.png",sep=""))
 grid.raster(FigS11)

### 2020-08-05 Ecol/Manuscript_Draft.Rmd
Changes for re-submission

--- 2020-06-12 Ecol/Manuscript_Draft.Rmd
@@
 
-In 1982, the United Nations Law of the Sea Convention (UNCLOS) formalized the concept of economic exclusive zones (EEZs) creating what we know today as shared stocks [@UnitedNations:1986tl], i.e.
+In 1982, the United Nations Law of the Sea Convention (UNCLOS) formalized the concept of economic exclusive zones (EEZs) creating what we know today as shared stocks **[@UnitedNations:1986tl]**, i.e.
 stocks that migrate between countries EEZs (known as transboundary stocks) or between EEZs and the high seas (also called straddling stocks) [@Song:2017iua].
@@
 For this specific case, we considered Alaska as a separate entity, the US contiguous states as a second one (Washington, Oregon and California), and lastly British Columbia (Canada).
-For the GoMA we used the Northwest Atlantic Fisheries Organization's (NAFO) divisions 5Y, 5Ze, and 4X[^NAFO] within latitudes 46.2°N and 41.5°S, and longitudes -72°W and -64°E (Figure \ref{fig:Figure1-map}).
+For the GoMA we used the Northwest Atlantic Fisheries Organization's (NAFO) divisions 5Y, 5Ze, and 4X[^NAFO] within latitudes 46.2°N and 41.5°S, and longitudes -72°W and -64°E (Fig.
+1).
 Is worth mention that, while NAFO's divisional zones were used in this study for domestic management, NAFO does not manage fisheries within the EEZs of Canada and the United States.
@@
 ```
-
-```{r Figure1-map, eval = T, echo=FALSE, fig.height = 4, fig.width = 6, fig.cap="Map of Canada and the US with the regulatory areas of the International Pacific Halibut Commission and the NAFO sub-divisions containing the Gulf of Maine arrangement"}
+<!-- ![Fig.1.
+Map of Canada and the US with the regulatory areas of the International Pacific Halibut Commission and the NAFO sub-divisions containing the Gulf of Maine arrangement.](./Figures/Figure 1.png) -->
+
+```{r Figure1-map, eval = F, echo=FALSE, fig.height = 4, fig.width = 6, fig.cap="Map of Canada and the US with the regulatory areas of the International Pacific Halibut Commission and the NAFO sub-divisions containing the Gulf of Maine arrangement"}
 
@@
 ```
+<insert Figure 1>
 
@@
 The DBEM algorithm integrated ecophysiology and habitat suitability with spatial population dynamics of exploited fishes and invertebrates to project shifts in abundance and potential fisheries catches under climate change.
-The algorithm predicted species distribution based on depth and latitudinal range, habitat preferences and an index of species association with major habitat types to estimate changes in abundance distribution over a $0.5^{\circ}$ x $0.5^{\circ}$ grid of the world ocean.
+The algorithm predicted species distribution based on depth and latitudinal range, habitat preferences and an index of species association with major habitat types to estimate changes in abundance distribution over a **0.5º x 0.5º** grid of the world ocean.
 For each grid cell and time step, the model then calculated species carrying capacity according to sea surface temperature, salinity, oxygen content, sea ice extent (for polar species) and bathymetry, as well as the species preferences to these conditions.
@@
 We projected the DBEM using three Earth system models (ESM), the Geophysical Fluid Dynamics Laboratory Earth System Models 2M (GFDL)[^GFDL], the Institute Pierre Simon Laplace Climate Model 5 (IPSL-CM5)[^IPSL], and the Max Planck Institute for Meteorology Earth System Model (MPI)[^MPI].
-Each model was downscaled to match the DBEM $0.5^{\circ}$ x $0.5^{\circ}$ grid using the nearest neighbor method, and in some cases, bilinear interpolation [@Cheung:2016hf].
+Each model was downscaled to match the DBEM **$0.5^{\circ}$ x $0.5^{\circ}$** grid using the nearest neighbor method, and in some cases, bilinear interpolation [@Cheung:2016hf].
 Finally, we used the model outputs for two scenarios of the Intergovernmental Panel on Climate Change (IPCC)-Representative Concentration Pathways (RCP) 2.6 and 8.5 representing a low greenhouse gas emission (strong mitigation) and a high greenhouse gas emission (week mitigation) scenario, respectively [@IPCC:2014bz].
-To estimate model robustness and capture the structural uncertainty build within ESM models, we averaged the DBEM results for all three models ($\mu \pm \sigma$) and marked regions where at least one ESM disagree in direction with the rest.
+To estimate model robustness and capture the structural uncertainty build within ESM models, we averaged the DBEM results for all three models **(<mu> +- <sigma>)** and marked regions where at least one ESM disagree in direction with the rest.
 
@@
 where *y* is year, *r* is region, *s* is species, *n* is total number of species, and $\hat{MCP}$ is the MCP averaged by the three ESMs.
-In the case of the GoMA, region was defined as the $0.5^{\circ}$ x $0.5^{\circ}$ grid-cell within the specific NAFO divisional zones.
-For the IPHC analysis, region was defined as the Commission's regulatory areas (Figure \ref{fig:Figure1-map}).
+In the case of the GoMA, region was defined as the **$0.5^{\circ}$ x $0.5^{\circ}$** grid-cell within the specific NAFO divisional zones.
+For the IPHC analysis, region was defined as the Commission's regulatory areas (Fig.
+1).
 We then averaged the values in three time periods (*t*) to reduce temporal model sensitivity.
-Thus, we computed the regional percentage change in MCP ($\Delta MCP$) as follows:
+Thus, we computed the regional percentage change in MCP **(<DELTA>MCPr)** as follows:
 
@@
 Where $X_{t}$ is the future average MCP for each of the two time periods analyzed in this study and $t_0$ is the present averaged MCP (<mu> `r Beg_In`-`r Beg_End`).
-Note that in cases where $X_{0}$ = 0 and $X_{t}$ > 0, then ($\Delta MCP$) = 100%, consequently, the opposite case would give a -100% result.
+Note that in cases where $X_{0}$ = 0 and $X_{t}$ > 0, then **(<DELTA>MCPr)** = 100%, consequently, the opposite case would give a -100% result.
 This way, Equ.
-2 shows the percentage change in MCP by mid $21^{st}$ century when $X_t$ = $\mu$ `r Mid_In`-`r Mid_End`, and end of $21^{st}$ century when $X_t$ = $\mu$ `r End_In`-`r End_End`, relative to today ($t_0$).
-The rationale between choosing these time periods was to provide a relative short-term projection (mid-century) that would be more policy-relevant but also show the long-term trend (end of the century).
+2 shows the percentage change in MCP by mid $21^{st}$ century when $X_t$ = <mu> `r Mid_In`-`r Mid_End`, and end of $21^{st}$ century when $X_t$ = <mu> `r End_In`-`r End_End`, relative to today ($t_0$).
+The rationale between choosing these time periods was to provide a relative short-term projection (mid-century) that would be more policy-relevant but also show the long-term trend (end of century).
 
@@
 In addition, we borrowed the concept of “threat point” from game theory defined as the minimum payoff that a player is willing to receive in order to cooperate with other players (see Sumaila et al., this Special Feature).
-Thus, we estimated the change in the ($\Delta MCP$) (threat point) that each country (players) would have for each species (hereafter referred as stock-share ratio), for both the IPHC and the GoMA.
+Thus, we estimated the change in the <DELTA>MCP (threat point) that each country (players) would have for each species (hereafter referred as stock-share ratio), for both the IPHC and the GoMA.
 The stock-share ratio can be seen as the proportion of the stock’s distribution within the study area that each country has.
@@
 1, to estimate the aggregated yearly mean MCP of each species per region.
-We then averaged the results by the same previously motioned periods (present, mid and end of the $21^{st}$ century).
-Next, for each species we estimated the stock-share ratio  ($\alpha_s$) that each region had during each time period:
+We then averaged the results by the same previously motioned periods (present, mid and end of the **21st** century).
+Next, for each species we estimated the stock-share ratio **(<alpha> s)** that each region had during each time period:
 
@@
 
-Where $\theta_{rt}$* is the species' aggregated $\hat{MCP}$ of each region at time period *t*, and $\delta_{rt}$ is the species' aggregated $\hat{MCP}$ of the whole specie's distribution within the study area at the same time period.
-Finally, we estimated the percentage change in stock-share ratio substituting $X_{t_0}$ and $X_{t}$ by $\alpha_{t0}$ and $\alpha_t$, respectively in Equ.
+Where **<theta>rt** is the species' aggregated $\hat{MCP}$ of each region at time period *t*, and **<delta>rt** is the species' aggregated $\hat{MCP}$ of the whole specie's distribution within the study area at the same time period.
+Finally, we estimated the percentage change in stock-share ratio substituting $X_{t_0}$ and $X_{t}$ by **<alpha>t0** and **<alpha>t**, respectively in Equ.
 2.
-The process was carried out for each ESM and results presented as average $\pm$ standard deviation (sd).
+The process was carried out for each ESM and results presented as average **+-** standard deviation (sd).
 All of the analysis was done in the statistical software *R* version 3.5.2 (2018-12-20) with the associated packages, *data.table* [@Packagedatatable:2019uh], *ggrepel* [@PackageggrepelAut:2018to], *gridExtra* [@PackagegridExtraM:2017wx], *knirt* [@PackageknitrAGen:2020wt], *RColorBrewer* [@PackagerColorBrewer:2014uw], *sf* [@PackagesfSimpleF:2018vp], and *tidyverse* [@PackagetidyverseE:2017vq].
@@
 
-At least one third of the IPHC regulatory areas will see a reduction in MCP of Pacific halibut by 2050 relative to current MCP, regardless of the climate change scenario (Figure \ref{fig:Figure2-IPHC}).
+At least one third of the IPHC regulatory areas will see a reduction in MCP of Pacific halibut by 2050 relative to current MCP, regardless of the climate change scenario (Fig.
+2).
 It is likely that the stock shift from the US.
@@
 The potential movement of halibut westward will increase the MCP of regulatory areas 3B (under a low emission scenario) and 4ABCE along the Aleutian Islands and Bering Sea.
-Regions 4DE, the most poleward regulatory areas of the IPHC, are expected to gain MCP by mid (Figure \ref{fig:Figure2-IPHC)) and end of the $21^{st}$ century (Figure \ref{fig:FigureS11}) under a high emission scenario due to the expansion of halibut suitable habitat as sea ice retreats (Fig.
+Regions 4DE, the most poleward regulatory areas of the IPHC, are expected to gain MCP by mid (Fig.
+2) and end of the $21^{st}$ century (Fig.
+A1.1) under a high emission scenario due to the expansion of halibut suitable habitat as sea ice retreats (Fig.
 A2.1).
-In contrast, under a low emission scenario, sea ice is expected to stabilize towards mid 21st century, thus providing less “new” suitable habitat for Pacific halibut and resulting in undetectable changes in MCP for the region (Figure \ref{fig:Figure2-IPHC)B) and decreasing even more towards 2100 (Figure \ref{fig:FigureS11}).
+In contrast, under a low emission scenario, sea ice is expected to stabilize towards mid 21st century, thus providing less “new” suitable habitat for Pacific halibut and resulting in undetectable changes in MCP for the region (Fig.
+2B) and decreasing even more towards 2100 (Fig.
+A1.1).
 
@@
 
-```{r Figure2-IPHC, eval =F, echo = F, fig.cap="Percentage change of MCP for species managed by the IPHC for mid 21st century (2041-2060) relative to present 2005-2014 under a A) high emission scenario and B) low emission scenario.
-Labels marked with "*" represent regions where models do not agree in direction of change."}
-
+```{r Figure_3, eval =F, echo = F}
 img <- readPNG(paste(my_path("F"),"Figure 3.png",sep=""))
@@
 
-<!-- ![Fig.
+![Fig.
 2.
 Percentage change of MCP for species managed by the IPHC for mid 21st century (2041-2060) relative to present 2005-2014 under a A) high emission scenario and B) low emission scenario.
-Labels marked with "*" represent regions where models do not agree in direction of change.](./Figures/Figure 3.png) -->
-
-The same poleward trend is expected in the change of Pacific halibut stock-share ratio with the average proportion increasing up to 25% in some northern regions and decreasing by 10% in southern regions, relative to the present proportion (Figure \ref{fig:Figure3-IPHC-prop}).
+Labels marked with "*" represent regions where models do not agree in direction of change.](./Figures/Figure 3.png)
+
+The same poleward trend is expected in the change of Pacific halibut stock-share ratio with the average proportion increasing up to 25% in some northern regions and decreasing by 10% in southern regions, relative to the present proportion (Fig.
+3).
 Maintaining emissions to lower levels through 2050 would potentially leave unchanged the stock-share ratio of three regulatory areas (3AC, and 4D) and negatively change regulatory area 2A.
@@
 
-```{r Figure3-IPHC-prop, eval = F, echo = F, fig.cap="Percentage change of stock-share ratio for IPHC under A) high emission scenario and B) low emission scenario for mid 21st century (2041-2060) relative to present 2005-2014.
-Values represent the mean of 3 ESM; error bars represent $\pm$ sd."}
+```{r Figure_4, eval = F, echo = F}
 
@@
 
-<!-- ![Fig.
+![Fig.
 3.
 Percentage change of stock-share ratio for IPHC under A) high emission scenario and B) low emission scenario for mid 21st century (2041-2060) relative to present 2005-2014.
-Values represent the mean of 3 ESM; error bars represent $\pm$ sd.](./Figures/Figure 4.png) -->
+Values represent the mean of 3 ESM; error bars represent $\pm$ sd.](./Figures/Figure 4.png)
 
@@
 
-While some regulatory areas of the IPHC will see an incremental increase in Pacific halibut MCP, the results for the Gulf of Maine show an overall decrease in MCP by 2050, regardless of the climate change scenario or ESM (Figure \ref{fig:Figure4-GOMA}), intensifying by the end of the $21^{st}$ century (Fig.
+While some regulatory areas of the IPHC will see an incremental increase in Pacific halibut MCP, the results for the Gulf of Maine show an overall decrease in MCP by 2050, regardless of the climate change scenario or ESM (Fig.
+4), intensifying by the end of the $21^{st}$ century (Fig.
 A1.2).
-For cod and haddock, MCP will decrease within the whole Gulf with no apparent win for any country in reference to the current period (Figure \ref{fig:Figure4-GOMA}).
+For cod and haddock, MCP will decrease within the whole Gulf with no apparent win for any country in reference to the current period (Fig.
+4).
 For yellowtail flounder, despite an overall reduction, some discrete areas are expected to increase with no particular pattern and high uncertainty, as ESMs in these regions do not agree in the direction of change (Fig.
@@
 
-```{r Figure4-GOMA, eval = F, echo = F, fig.cap= "Percentage change of MCP in the Gulf of Maine under, A) high emission scenario; and B) low emission for mid-century (2041-2060) relative to present (2005-2014).
-Points represent regions where models do not agree in direction of change."}
-
-Fig4 <- readPNG(paste(my_path("F"),"Figure 5.png",sep=""))
-grid.raster(Fig5)
-
-```
-
-<!-- ![Fig.
+![Fig.
 4.
 Percentage change of MCP in the Gulf of Maine under, A) high emission scenario; and B) low emission for mid-century (2041-2060) relative to present (2005-2014).
-Points represent regions where models do not agree in direction of change.](./Figures/Figure 5.png) -->
+Points represent regions where models do not agree in direction of change.](./Figures/Figure 5.png)
 
@@
 Following a high emission path will affect mostly Canada’s share of yellowtail flounder and in less degree haddock, with an increase of cod share.
-under the low emission scenario, haddock and cod patterns intensify, while yellowtail flounder’s share approaches almost no change (Figure \ref{fig:Figure5-GOMA-prop}).
+under the low emission scenario, haddock and cod patterns intensify, while yellowtail flounder’s share approaches almost no change (Fig.
+5).
 Such pattern is likely the combination of the bathymetry or the Gulf, the warming gradient, and the species distribution (see discussion).
@@
 
-```{r Figure5-GOMA-prop, eval = T, echo = F, fig.cap="Changes in MCP stock-share ratio for Gulf of Maine under (A) high emission; and (B) low emission scenarios for mid 21st century (2041-2060) relative to present (2005-2014).
-Values represent the mean of 3 ESM; error bars represent $\pm$ sd."}
-
-Fig5 <- readPNG(paste(my_path("F"),"Figure 6.png",sep=""))
-grid.raster(Fig6)
-
-```
-
-<!-- ![Fig.
+![Fig.
 5.
 Changes in MCP stock-share ratio for Gulf of Maine under (A) high emission; and (B) low emission scenarios for mid 21st century (2041-2060) relative to present (2005-2014).
-Values represent the mean of 3 ESM; error bars represent $\pm$ sd.](./Figures/Figure 6.gif) -->
-
-## Discussion
+Values represent the mean of 3 ESM; error bars represent $\pm$ sd.](./Figures/Figure 6.gif)
+
+## DISCUSSION
 
@@
 On the other hand, regions 3A and 3B have seen the largest decreases in the IPHC regulatory areas since 2010, from 35.3% to 30.6% and 20.6% to 15.9%, respectively.
-Similarly, in the Gulf of Maine, the projected stock-share gain of yellowtail flounder and haddock by the US (Figure \ref{fig:Figure5-GOMA-prop}) follows a historical trend where in 2019, Canada's stock-share decreased from 35% to 32% and 60% to 40% relative to 2010, respectively [@Trinko:2019ou].
+Similarly, in the Gulf of Maine, the projected stock-share gain of yellowtail flounder and haddock by the US (Fig.
+5) follows a historical trend where in 2019, Canada's stock-share decreased from 35% to 32% and 60% to 40% relative to 2010, respectively [@Trinko:2019ou].
 
@@
 Geographic barriers [@Cheung:2015fm; @Kleisner:2016je], local temperature gradients [@Pinsky:2013jo], species interactions and human activities [@Serpetti:2017he] might change the rate and direction of species shifts.
-For the IPHC, geographic barriers might induce a westward increase of stock-share in IPHC regions where species can only migrate northward into the Arctic Ocean through the Bering Sea and Bering Strait [@Cheung:2015fm] (Figure \ref{fig:Figure3-IPHC-prop}).
+For the IPHC, geographic barriers might induce a westward increase of stock-share in IPHC regions where species can only migrate northward into the Arctic Ocean through the Bering Sea and Bering Strait [@Cheung:2015fm] (Fig.
+3).
 In the Gulf of Maine, future projections could be a response to a temperature gradient shift combined with geographic barriers as southern waters are deeper and warming slower than northern waters according to the ESMs (Fig.
@@
 In our results, the "winners and losers" of climate change, and the intensity of the change, will be scenario dependent.
-For instance, stock-share of yellowtail flounder under a high emission scenario will be larger for the US while Canada's gain of cod stock-share will be larger under a low emission scenario (Figure \ref{fig:Figure5-GOMA-prop}).
+For instance, stock-share of yellowtail flounder under a high emission scenario will be larger for the US while Canada's gain of cod stock-share will be larger under a low emission scenario (Fig.
+5).
 Applying previously describe strategies (e.g.
@@
 Overall, results for the Gulf of Maine agree with a reduction in MCP of all three species.
-However, some discrete areas show a positive change for yellowtail flounder by mid $21^{st}$ century (Figure \ref{fig:Figure3-IPHC-prop)), mainly driven by the GFDL model (Fig.
+However, some discrete areas show a positive change for yellowtail flounder by mid $21^{st}$ century (Fig.
+3), mainly driven by the GFDL model (Fig.
 A2.3).
@@
 
-## Conclusions
+## CONCLUSIONS
 
@@
 
-## References
+## LITERATURE CITED
 
@@
 
-<!-- End of the century change  -->
-
-```{r FigureS11, eval = F, echo = F, fig.cap = "Percentage change of MCP for species managed by the IPHC for end-century (2081–2100) referent to 2005–2014 under a (A) high emission scenario and (B) low emission scenario.
-Labels marked with "*" represent regions where models do not agree in direction of change."}
+```{r FigureS11, eval = T, echo = F, fig.cap = "Outliers GoMA"}
 
@@
 
-```{r FigureS12, eval = T, echo = F, fig.cap = "Percentage change of MCP in the Gulf of Maine under (RCP 8.5) high emission scenario and (RCP 2.6) low emission for end-century (2080–2100) referent to present (2005– 2014).
-Values represent the mean of 3 ESM.
-Points represent regions where ESMs do not agree in direction of change"}
+```{r FigureS12, eval = T, echo = F, fig.cap = "Outliers GoMA"}
 
@@
 <!-- NOTE: Remember to run the Results chunk to load all the data needed -->
-<!-- # ESM uncertainty -->
-<!-- This chunk explores the uncertainty build in the ESM-DBEM  -->
 
@@
 ```
+
+<!-- # ESM uncertainty -->
+<!-- This chunk explores the uncertainty build in the ESM-DBEM  -->
+
+```{r DBEM_Uncertanty, eval = F, echo = F}
+
+#### DBEM-ESM Uncertanty
+
+Today_Uncertanty <- DBEM_Corrected %>% 
+  filter(Species %in% Selected_Species) %>% 
+  left_join(IPHC_Reg_DBEM_df,
+            by = "INDEX") %>% 
+  filter(!is.na(RegArea)) %>% 
+  mutate(RCP = ifelse(Model %in% RCP,"Low Emission","High Emission")) %>% 
+  gather("Year","MCP",Beg_In:Beg_End) %>% 
+  mutate(Period = ifelse(Year >= Beg_In & Year <= Beg_End,"Beginning","NA")) %>% 
+  group_by(RegArea,Model,RCP,Year,Period) %>% 
+  summarise(Regional_MCP =sum(MCP,na.rm=T)) %>% 
+  group_by(RegArea,Model,RCP) %>% 
+  summarise(Today_MCP =mean(Regional_MCP,na.rm=T))
+
+IPHC_MCP_Change_Uncert <- DBEM_Corrected %>% 
+  filter(Species %in% Selected_Species) %>% 
+  left_join(IPHC_Reg_DBEM_df,
+            by = "INDEX") %>% 
+  filter(!is.na(RegArea)) %>% 
+  mutate(RCP = ifelse(Model %in% RCP,"Low Emission","High Emission")) %>% 
+  gather("Year","MCP",Beg_In:End_End) %>%
+  group_by(Model,RCP,Year,RegArea) %>%
+  summarise(Regional_MCP =sum(MCP,na.rm=T)) %>% 
+  group_by(RCP,Model,RegArea) %>% # Running mean as Kleisner & Pauly 2012
+  mutate(RMean = rollmean(x = Regional_MCP, 10,
+                          align = "right",
+                          fill = Regional_MCP)
+  ) %>% 
+  mutate(GCM = ifelse(Model == "GFDL26F1" | Model == "GFDL85F1","GFDL",
+                      ifelse(Model == "IPSL26F1" | Model == "IPSL85F1", "IPSL",
+                             ifelse(Model == "MPI26F1" | Model == "MPI85F1","MPI","NA"
+                             )
+                      )
+  )
+  ) %>% 
+  filter(Year >= 2015) %>% 
+  left_join(Today_Uncertanty,
+            by = c("RegArea","Model","RCP")) %>% 
+  mutate(Index = RMean/Today_MCP)
+
+# Create and save plot
+
+ggplot(IPHC_MCP_Change_Uncert) +
+  geom_line(
+    aes(
+      x = as.numeric(Year),
+      y = Index,
+      color = GCM,
+      linetype = RCP
+    )
+  ) +
+  facet_wrap(~RegArea,
+             scales = "free_y") +
+  labs(
+    x = "Year",
+    y ="Index (Future MCP/Present)"
+  ) +
+  scale_color_manual("Global Circulation model",
+                     values=c("#EEA410","#B53CB9","#2EBC67")
+  ) +
+  scale_x_continuous(breaks = seq(2010,2100,30),
+                     limits = c(2010,2100)
+  ) +
+  my_ggtheme_p()() +
+  # Save plot
+  ggsave("Model_Uncer_Sup.png",
+         plot = .,
+         width = 12,
+         height =8,
+         units = "in",
+         path = "./Results/Sup"
+  )
+
+```
+
+```{r FigureS1, eval = T, echo = F, fig.cap = "Variation of climate change scenarios"}
+
+FigS21 <- readPNG(paste(my_path("F"),"S21.png",sep=""))
+grid.raster(FigS21)
+
+```
+
+<!-- # Explore Regions 4d and 4e -->
 
@@
 
-```{r FigureS21, eval = T, echo = F, fig.cap = "Projected environmental variables under climate change from 2010 to 2010 for Arctic regions of the IPHC (Top:4D, Bottom, 4E).
-The solid line represents the average of all three ESMs and the shaded area represents the model’s uncertainty (s.d.)."}
-
-FigS21 <- readPNG(paste(my_path("F"),"S21.png",sep=""))
-grid.raster(FigS21)
+```{r FigureS2, eval = T, echo = F, fig.cap = "Variation of climate change scenarios in IPHC regions 4E and 4D"}
+
+FigS22 <- readPNG(paste(my_path("F"),"S22.png",sep=""))
+grid.raster(FigS22)
 
 ```
-
-<!-- Explore environental differences withing GOMA -->
 
@@
 
-```{r FigureS22, eval = T, echo = F, fig.cap = "Depth profile (A) and bottom water warming of the Gulf of Maine.
-Everything deeper than 1000 meters is colored in green.
-B) Percentage change of bottom temperature relative to the present showing more intense warming in northern regions, especially under a high emission climate change scenario."}
-
-FigS22 <- readPNG(paste(my_path("F"),"S22.png",sep=""))
-grid.raster(FigS22)
+```{r FigureS3, eval = T, echo = F, fig.cap = "Outliers GoMA"}
+
+FigS23 <- readPNG(paste(my_path("F"),"S23.png",sep=""))
+grid.raster(FigS23)
 
@@
 
-<!-- GOMA Outliers analysis -->
-
-```{r FigureS23, eval = T, echo = F, fig.cap = "PChanges in maximum catch potential of yellowtail flounder (Limanda ferruginea) within the study area by mid-century relative to present time.
-Results for the three global circulation models (GFDL, IPSL, MPIS) used in the current study and two climate change scenarios (Top: High emission – RCP 8.5, Bottom: Low Emission – RCP 2.6).
-Grid-cells marked in yellow represent discrete areas where average MCP is projected to increase by mid-century."}
-
-FigS24 <- readPNG(paste(my_path("F"),"S24.png",sep=""))
-grid.raster(FigS24)
-
-```
-
-<!-- ESM-DBEM Uncertinty analysis -->
-
-```{r DBEM_Uncertanty, eval = F, echo = F}
-
-#### DBEM-ESM Uncertanty
-
-Today_Uncertanty <- DBEM_Corrected %>% 
-  filter(Species %in% Selected_Species) %>% 
-  left_join(IPHC_Reg_DBEM_df,
-            by = "INDEX") %>% 
-  filter(!is.na(RegArea)) %>% 
-  mutate(RCP = ifelse(Model %in% RCP,"Low Emission","High Emission")) %>% 
-  gather("Year","MCP",Beg_In:Beg_End) %>% 
-  mutate(Period = ifelse(Year >= Beg_In & Year <= Beg_End,"Beginning","NA")) %>% 
-  group_by(RegArea,Model,RCP,Year,Period) %>% 
-  summarise(Regional_MCP =sum(MCP,na.rm=T)) %>% 
-  group_by(RegArea,Model,RCP) %>% 
-  summarise(Today_MCP =mean(Regional_MCP,na.rm=T))
-
-IPHC_MCP_Change_Uncert <- DBEM_Corrected %>% 
-  filter(Species %in% Selected_Species) %>% 
-  left_join(IPHC_Reg_DBEM_df,
-            by = "INDEX") %>% 
-  filter(!is.na(RegArea)) %>% 
-  mutate(RCP = ifelse(Model %in% RCP,"Low Emission","High Emission")) %>% 
-  gather("Year","MCP",Beg_In:End_End) %>%
-  group_by(Model,RCP,Year,RegArea) %>%
-  summarise(Regional_MCP =sum(MCP,na.rm=T)) %>% 
-  group_by(RCP,Model,RegArea) %>% # Running mean as Kleisner & Pauly 2012
-  mutate(RMean = rollmean(x = Regional_MCP, 10,
-                          align = "right",
-                          fill = Regional_MCP)
-  ) %>% 
-  mutate(GCM = ifelse(Model == "GFDL26F1" | Model == "GFDL85F1","GFDL",
-                      ifelse(Model == "IPSL26F1" | Model == "IPSL85F1", "IPSL",
-                             ifelse(Model == "MPI26F1" | Model == "MPI85F1","MPI","NA"
-                             )
-                      )
-  )
-  ) %>% 
-  filter(Year >= 2015) %>% 
-  left_join(Today_Uncertanty,
-            by = c("RegArea","Model","RCP")) %>% 
-  mutate(Index = RMean/Today_MCP)
-
-# Create and save plot
-
-ggplot(IPHC_MCP_Change_Uncert) +
-  geom_line(
-    aes(
-      x = as.numeric(Year),
-      y = Index,
-      color = GCM,
-      linetype = RCP
-    )
-  ) +
-  facet_wrap(~RegArea,
-             scales = "free_y") +
-  labs(
-    x = "Year",
-    y ="Index (Future MCP/Present)"
-  ) +
-  scale_color_manual("Global Circulation model",
-                     values=c("#EEA410","#B53CB9","#2EBC67")
-  ) +
-  scale_x_continuous(breaks = seq(2010,2100,30),
-                     limits = c(2010,2100)
-  ) +
-  my_ggtheme_p()() +
-  # Save plot
-  ggsave("Model_Uncer_Sup.png",
-         plot = .,
-         width = 12,
-         height =8,
-         units = "in",
-         path = "./Results/Sup"
-  )
-
-```
-
-```{r FigureS24, eval = T, echo = F, fig.cap = "Projected MCP change relative to present (2005-2014) for each IPHC regulatory area.
-Colors represents the different ESM used in the study.
-Solid line represents a high emission scenario (RCP 8.5) and dashed line represents a low emission scenario (RCP 2.6)"}
-
-FigS24 <- readPNG(paste(my_path("F"),"S24.png",sep=""))
-grid.raster(FigS24)
+```{r FigureS13, eval = T, echo = F, fig.cap = "Outliers GoMA"}
+
+FigS13 <- readPNG(paste(my_path("F"),"S13.png",sep=""))
+grid.raster(FigS13)
 
@@
 <!-- # Option removing NAFO -->
-<!-- Shifts in the distribution of 33 jointly managed transboundary stocks of North America by 2050 relative to 2010 show that MCP of transboundary stocks will overall increase in Atlantic-Canadian and Alaskan waters and decrease in Pacific-Canadian and the US contiguous states waters (Figure \ref{fig:Figure2-IPHC}).
+<!-- Shifts in the distribution of 33 jointly managed transboundary stocks of North America by 2050 relative to 2010 show that MCP of transboundary stocks will overall increase in Atlantic-Canadian and Alaskan waters and decrease in Pacific-Canadian and the US contiguous states waters (Fig.
+2).
 Such changes will be more intense under the high emission scenario (Fig.

### 2020-09-15 Ecol/Manuscript_Draft.Rmd
Included table 1

--- 2020-06-12 Ecol/Manuscript_Draft.Rmd
@@
 
-<insert Table 1>
-
 ### The Gulf of Maine Arrangement
@@
 From 2010 onward, the GoMA suggests catch-limits based on a weighted method where 10% represents the stocks’ historical distribution (from 1967 to 1994) and 90% current distributions produced by quarterly surveys and catch [@TRAC:2016wu].
-Since its introduction, the average quota allocation for each species proposed by the GoMA has been; Atlantic cod 77% Canada and 23% US, haddock 55% Canada and 45% US, and yellowtail flounder 34% Canada and 66% US [Table 1, @TRAC:2015wj; @TRAC:2015vp; @TRAC:2015tt; @TRAC:2018tw; @TRAC:2018tj; @TRAC:2018wx; @Trinko:2019ou].
+Since its introduction, the average quota allocation for each species proposed by the GoMA has been (Table \ref{tab:table_1}); Atlantic cod 77% Canada and 23% US, haddock 55% Canada and 45% US, and yellowtail flounder 34% Canada and 66% US [@TRAC:2015wj; @TRAC:2015vp; @TRAC:2015tt; @TRAC:2018tw; @TRAC:2018tj; @TRAC:2018wx; @Trinko:2019ou].
 However, because this is an unofficial agreement, Canada and the US ultimately take single management decisions [@Soboil:2006gw].
@@
 
-<insert Table 2>
+```{table_1, eval = T, echo = F}
+
+table_1 <- read_excel("Ecol/Tables/Tables.xlsx") 
+colnames(table_1) <- c("Year","Canada","US","Canada","US","Canada","US")
+
+table_1 %>% 
+  kable("latex",
+        booktabs = T,
+        caption = "Historic quota allocation suggested for Atlantic cod, haddock and yellowtail flounder in the Gulf of Maine "
+  ) %>% 
+  kable_styling(full_width = F,
+                position = "center") %>%
+  add_header_above(c(" ", "Atlantic cod" = 2, "Haddock" = 2, "Yellowtail flounder" = 2)
+  ) %>% 
+  footnote(general = c("* Average from 2006 to 2009, before the implementation of the weighted method",
+                       "' Since the implementation of the weighted method",
+                       "'' Standard deviation of the wiighted average",
+                       "^ TRAC (2015abc)",
+                       "† TRAC (2018abc)",
+                       "‡ Lake (2019)"
+  )
+  )
+
+```
 

### 2020-09-15 Ecol/Manuscript_Draft.Rmd
There is no need for abstract in the thesis

@@
 
-## Abstract
-
-Climate change is shifting the distribution of fish stocks that straddle between Exclusive Economic Zones (EEZ), challenging transboundary fisheries management.
+<!-- ## Abstract -->
+
+<!-- Climate change is shifting the distribution of fish stocks that straddle between Exclusive Economic Zones (EEZ), challenging transboundary fisheries management.
 Here, we examine the projected sharing of jointly managed transboundary fish stocks between Canada and the United States.
@@
 Based on the simulation results, we examine possible solution options to reduce climate risks on transboundary fish stocks and fisheries.
-
-Keywords: *Transboundary fisheries management; climate change; joint fisheries management; species distribution shift*
+-->
+
+<!-- Keywords: *Transboundary fisheries management; climate change; joint fisheries management; species distribution shift* -->
 

### 2020-10-12 Ecol/Manuscript_Draft.Rmd
misc,

@@
 
-In 1982, the United Nations Law of the Sea Convention (UNCLOS) formalized the concept of economic exclusive zones (EEZs) creating what we know today as shared stocks [@UnitedNations:1986tl], i.e.
+In 1982, the United Nations Law of the Sea Convention (UNCLOS) formalized the concept of exclusive economic zones (EEZs) creating what we know today as shared stocks [@UnitedNations:1986tl], i.e.
 stocks that migrate between countries EEZs (known as transboundary stocks) or between EEZs and the high seas (also called straddling stocks) [@Song:2017iua].
@@
 
-## Methods
-
-### Study Area and Fisheries
+## Materials and Methods
+
+### Study area and fisheries
 
@@
 From 2010 onward, the GoMA suggests catch-limits based on a weighted method where 10% represents the stocks’ historical distribution (from 1967 to 1994) and 90% current distributions produced by quarterly surveys and catch [@TRAC:2016wu].
-Since its introduction, the average quota allocation for each species proposed by the GoMA has been (Table \ref{tab:table_1}); Atlantic cod 77% Canada and 23% US, haddock 55% Canada and 45% US, and yellowtail flounder 34% Canada and 66% US [@TRAC:2015wj; @TRAC:2015vp; @TRAC:2015tt; @TRAC:2018tw; @TRAC:2018tj; @TRAC:2018wx; @Trinko:2019ou].
+Since its introduction, the average quota allocation for each species proposed by the GoMA has been (Table \ref{tab:Table1}); Atlantic cod 77% Canada and 23% US, haddock 55% Canada and 45% US, and yellowtail flounder 34% Canada and 66% US [@TRAC:2015wj; @TRAC:2015vp; @TRAC:2015tt; @TRAC:2018tw; @TRAC:2018tj; @TRAC:2018wx; @Trinko:2019ou].
 However, because this is an unofficial agreement, Canada and the US ultimately take single management decisions [@Soboil:2006gw].
@@
 
-```{table_1, eval = T, echo = F}
-
-table_1 <- read_excel("Ecol/Tables/Tables.xlsx") 
+```{r Table1, eval = T, echo = F}
+
+table_1 <- read_excel("./Tables/Tables.xlsx") 
 colnames(table_1) <- c("Year","Canada","US","Canada","US","Canada","US")
@@
 
-### Projecting Future Species Distribution
+### Projecting future species distributions
 
@@
 
-### Estimation of Maximum Catch Potential Change
+### Estimation of Maximum Catch Potential change
 
@@
 Moreover, overlapping shifting stocks could interfere in gear-limitation management rules of multiple fisheries generating conflicts between fleets [@VanDerVoo:2016uc].
-The effectiveness of the IPHC-Closed Area ("CA" in Fig.1.) in terms of protecting juveniles has been historically questioned as trawling for other species is still allowed in the area [@Karim:2010ut; @IPHC:2017CA].
+The effectiveness of the IPHC-Closed Area ("CA" in Figure \ref{fig:Figure2-IPHC}) in terms of protecting juveniles has been historically questioned as trawling for other species is still allowed in the area [@Karim:2010ut; @IPHC:2017CA].
 In 2015, for example, 97% of the trawl by-catch in areas 4CDE and the Closed Area were juveniles [@IPHC:2017CA].

### 2020-10-14 Ecol/Manuscript_Draft.Rmd
included proofs

@@
 
-The ocean is getting warmer [@Rheim:2013fv], less oxygenated [@Schmidtko:2017cl], and increasing in acidity [@Ross:2011kd; @IPCC:2019to].
+The ocean is getting warmer [@Rheim:2013fv], less oxygenated [@Schmidtko:2017cl], and increasing in acidity [@Ross:2011kd; @IPCC:2019tn].
 To cope with these changes in ocean biophysic properties, marine species, including shared fish stocks, have been shifting their distribution towards the poles and/or deeper waters [@Poloczanska:2016kk].
@@
 
-For estimating the percentage change of MCP at the regional scale, we first aggregated the yearly mean MCP of all species per region ($X_{yr}$) and period:
+For estimating the percentage change of MCP at the regional scale, we first aggregated the yearly mean MCP of all gridcells per region ($X_{yr}$) and period:
 
@@
 Thus, the commission has been asked to open the closed area for Pacific halibut fishing, under the premise that the expansion of the trawl fishery is likely reducing any conservation goal for juvenile Pacific halibut [@IPHC:2017CA].
-Although not assessed in this study, some trawling target species like Pacific cod (*Gadus macrocephalus*), flathead sole (*Hippoglossoides elassodon*), and Alaskan plaice (*Limanda aspera*) have already shift their distributions due to warming waters [@Stram:2009xc] and some are expected to continue shifting in similar direction than Pacific halibut [@Pinsky:2013jo].
+Although not assessed in this study, some trawling target species like Pacific cod (*Gadus macrocephalus*), flathead sole (*Hippoglossoides elassodon*), and Alaskan plaice (*Pleuronectes quadrituberculatus*) have already shift their distributions due to warming waters [@Stram:2009xc] and some are expected to continue shifting in similar direction than Pacific halibut [@Pinsky:2013jo].
 The overlap of target species could be addressed by applying ecosystem-based management and dynamic management tools [@Hazen:2018fa] to manage these fisheries and reduce potential loss of sustainable harvest for both the halibut and the trawl fisheries.
@@
 Side payments do not have to be in monetary form and are widely used in transboundary stocks around the world.
-For example, Norway and Russia have implemented a quota swap strategy for jointly managed stocks of cod, haddock and capelin in the Barents Sea [^NR].
+For example, Norway and Russia have implemented a quota swap strategy for jointly managed stocks of cod, haddock and capelin (*Mallotus villosus*) in the Barents Sea [^NR].
 Similarly, species' quota swaps are allowed, up to a degree, within regulatory areas of the European union [@Baudron:2020dj].
@@
 Off the coast of British Columbia, increasing temperature trends are consistent among ESMs, however, other processes such as acidification and deoxygenation are still not well understood from British Columbia to the Gulf of Alaska  [@TalloniAlvarez:2019gz].
-Moreover, considerable uncertainty exists along the Bering Sea [@Douglas:2010Mb] and Antarctic Pacific regarding the extent and intensity of future sea-ice reduction under climate change [@Steiner:2015hc; @IPCC:2019to].
+Moreover, considerable uncertainty exists along the Bering Sea [@Douglas:2010Mb] and Antarctic Pacific regarding the extent and intensity of future sea-ice reduction under climate change [@Steiner:2015hc; @IPCC:2019tn].
 Regarding the DBEM, its structural uncertainty has been previously tested for agreement against commonly used species distribution algorithms such as Maxent [@Phillips:2006ff] and AquaMaps [@Kaschner:2011hi; @Ready:2010wr] resulting in no qualitative differences in trends between algorithms [@Cheung:2016jd].
@@
 
-```{r FigureS11, eval = T, echo = F, fig.cap = "Percentage change of MCP for species managed by the IPHC for end-century (2081–2100) referent to 2005–2014 under a A) high emission scenario and B) low emission scenario.
+```{r FigureS11, eval = T, echo = F, fig.cap = "Percentage change of MCP for species managed by the IPHC for end-century (2081–2100) relative to 2005–2014 under a A) high emission scenario and B) low emission scenario.
 Labels marked with * represent regions where models do not agree in direction of change."}

### 2020-10-15 Ecol/Manuscript_Draft.Rmd
typos

@@
 
-```{r Table1, eval = T, echo = F}
+```{r Table1, eval = T, echo = F, warning=F, message=F, fig.align="H"}
 
@@
 The results of the present study suggest that climate change will alter the MCP of jointly managed transboundary fish stocks in North America consequently altering Canada’s and the US’s species’ stock-share ratio, regardless of the climate change scenario.
-These results are aligned with regional [@Morley:2018fn] projections suggesting that climate change will push marine species towards the poles and deeper water [@Pinsky:2013jo] in search of their ecological niche [@Poloczanska:2016kk].
+These results are aligned with regional [@Morley:2018fn] projections suggesting that climate change will push marine species towards the poles and deeper water [@Pinsky:2013ab] in search of their ecological niche [@Poloczanska:2016kk].
 Moreover, IPHC data[^IPHC] suggest that some of these shits are already happening.
@@
 
-Geographic barriers [@Cheung:2015fm; @Kleisner:2016je], local temperature gradients [@Pinsky:2013jo], species interactions and human activities [@Serpetti:2017he] might change the rate and direction of species shifts.
+Geographic barriers [@Cheung:2015fm; @Kleisner:2016je], local temperature gradients [@Pinsky:2013ab], species interactions and human activities [@Serpetti:2017he] might change the rate and direction of species shifts.
 For the IPHC, geographic barriers might induce a westward increase of stock-share in IPHC regions where species can only migrate northward into the Arctic Ocean through the Bering Sea and Bering Strait [@Cheung:2015fm] (Figure \ref{fig:Figure3-IPHC-prop}).
@@
 Thus, the commission has been asked to open the closed area for Pacific halibut fishing, under the premise that the expansion of the trawl fishery is likely reducing any conservation goal for juvenile Pacific halibut [@IPHC:2017CA].
-Although not assessed in this study, some trawling target species like Pacific cod (*Gadus macrocephalus*), flathead sole (*Hippoglossoides elassodon*), and Alaskan plaice (*Pleuronectes quadrituberculatus*) have already shift their distributions due to warming waters [@Stram:2009xc] and some are expected to continue shifting in similar direction than Pacific halibut [@Pinsky:2013jo].
+Although not assessed in this study, some trawling target species like Pacific cod (*Gadus macrocephalus*), flathead sole (*Hippoglossoides elassodon*), and Alaskan plaice (*Pleuronectes quadrituberculatus*) have already shift their distributions due to warming waters [@Stram:2009xc] and some are expected to continue shifting in similar direction than Pacific halibut [@Pinsky:2013ab].
 The overlap of target species could be addressed by applying ecosystem-based management and dynamic management tools [@Hazen:2018fa] to manage these fisheries and reduce potential loss of sustainable harvest for both the halibut and the trawl fisheries.
@@
 -->
-<!-- Species such as haddock in the Atlantic [@Morley:2018fn], and big skate (*Raja binoculata*) in the Pacific coast [@Pinsky:2013jo] have been projected to shift away from the poles. -->
+<!-- Species such as haddock in the Atlantic [@Morley:2018fn], and big skate (*Raja binoculata*) in the Pacific coast [@Pinsky:2013ab] have been projected to shift away from the poles. -->
 

### 2020-11-16 Ecol/Manuscript_Draft.Rmd
thesis details

@@
 Since the definition of shared stocks, game theory has been one of the most common approaches used to analyze the management of these type of stocks.
-However, shared stocks' management can be convoluted due to the participation of several fishing “players”, different countries and sometimes jurisdictions within a country, the migration patterns of the stock, and their abundance fluctuation within space and time [@Munro:2002uf, Engler and Saunders this Special Feature].
-In addition, international treaties might not be prepared to address the effects that climate change will bring to shared fish stocks (Engler and Saunders this Special Feature, Koubrak and VanderZwaag, this Special Feature).
+However, shared stocks' management can be convoluted due to the participation of several fishing “players”, different countries and sometimes jurisdictions within a country, the migration patterns of the stock, and their abundance fluctuation within space and time [@Munro:2002uf, Engler and Saunders *in press*].
+In addition, international treaties might not be prepared to address the effects that climate change will bring to shared fish stocks (Engler and Saunders *in press*, Koubrak and VanderZwaag, *in press*).
 
@@
 
-The shifts in distribution of shared fish stocks will impact the economics of their fisheries [@Pinsky:2012kq; @Sumaila:2019gh, Sumaila et al., this Special Feature], and create international disputes between countries [@Munro:2002uf; @Spijkers:2017ij; @Pinsky:2018cb].
+The shifts in distribution of shared fish stocks will impact the economics of their fisheries [@Pinsky:2012kq; @Sumaila:2019gh, @Sumaila:2020tp], and create international disputes between countries [@Munro:2002uf; @Spijkers:2017ij; @Pinsky:2018cb].
 Canada and the US share important transboundary stocks of salmon (*Oncorhynchus spp.*), Pacific halibut (*Hippoglossus stenolepis*), and Atlantic cod (*Gadus morhua*) offering a unique lens to understand the extent to which climate-induced distributional shifts will challenge the future sustainability of transboundary fisheries.
@@
 
-```{r Table1, eval = T, echo = F, warning=F, message=F, fig.align="H"}
+```{r Table1, eval = T, echo = F, warning=F, message=F}
 
@@
 
-$$ X_{yr} = \sum_{s = 1}^n \hat{MCP_s}$$
+<!-- $$ X_{yr} = \sum_{s = 1}^n \hat{MCP_s}$$ -->
 <!-- <eqn1> -->
+
+\begin{equation}
+\label{eq:one}
+X_{yr} = \sum_{s = 1}^n \hat{MCP_s}
+\end{equation}
 
@@
 
-$$\Delta MCP_r = -(1-\frac{X_{t}}{X_{t_0}})*100 $$
+<!-- $$\Delta MCP_r = -(1-\frac{X_{t}}{X_{t_0}})*100 $$ -->
+\begin{equation}
+\label{eq:two}
+\Delta MCP_r = -(1-\frac{X_{t}}{X_{t_0}})*100
+\end{equation}
+
 <!-- <eqn2> -->
@@
 
-In addition, we borrowed the concept of “threat point” from game theory defined as the minimum payoff that a player is willing to receive in order to cooperate with other players (see Sumaila et al., this Special Feature).
+In addition, we borrowed the concept of “threat point” from game theory defined as the minimum payoff that a player is willing to receive in order to cooperate with other players [@Sumaila:2020tp].
 Thus, we estimated the change in the ($\Delta MCP$) (threat point) that each country (players) would have for each species (hereafter referred as stock-share ratio), for both the IPHC and the GoMA.
@@
 
-$$\alpha_{s} = \frac{\theta_{rt}}{\delta_{rt}}$$
+<!-- $$\alpha_{s} = \frac{\theta_{rt}}{\delta_{rt}}$$ -->
+\begin{equation}
+\label{eq:three}
+\alpha_{s} = \frac{\theta_{rt}}{\delta_{rt}}
+\end{equation}
 
 Where $\theta_{rt}$* is the species' aggregated $\hat{MCP}$ of each region at time period *t*, and $\delta_{rt}$ is the species' aggregated $\hat{MCP}$ of the whole specie's distribution within the study area at the same time period.
-Finally, we estimated the percentage change in stock-share ratio substituting $X_{t_0}$ and $X_{t}$ by $\alpha_{t0}$ and $\alpha_t$, respectively in Equ.
-2.
+Finally, we estimated the percentage change in stock-share ratio substituting $X_{t_0}$ and $X_{t}$ by $\alpha_{t0}$ and $\alpha_t$, respectively in Equation \@ref(eq:two).
 The process was carried out for each ESM and results presented as average $\pm$ standard deviation (sd).
-All of the analysis was done in the statistical software *R* version 3.5.2 (2018-12-20) with the associated packages, *data.table* [@Packagedatatable:2019uh], *ggrepel* [@PackageggrepelAut:2018to], *gridExtra* [@PackagegridExtraM:2017wx], *knirt* [@PackageknitrAGen:2020wt], *RColorBrewer* [@PackagerColorBrewer:2014uw], *sf* [@PackagesfSimpleF:2018vp], and *tidyverse* [@PackagetidyverseE:2017vq].
+All of the analysis was done in the statistical software R version 3.5.2 (2018-12-20) with the associated packages, *data.table* [@Packagedatatable:2019uh], *ggrepel* [@PackageggrepelAut:2018to], *gridExtra* [@PackagegridExtraM:2017wx], *knirt* [@PackageknitrAGen:2020wt], *RColorBrewer* [@PackagerColorBrewer:2014uw], *sf* [@PackagesfSimpleF:2018vp], and *tidyverse* [@PackagetidyverseE:2017vq].
 All code is available at http://www.github.com/jepa/OC_Transboundary.
@@
 under the low emission scenario, haddock and cod patterns intensify, while yellowtail flounder’s share approaches almost no change (Figure \ref{fig:Figure5-GOMA-prop}).
-Such pattern is likely the combination of the bathymetry or the Gulf, the warming gradient, and the species distribution (see discussion).
+Such pattern is likely the combination of the bathymetry or the Gulf, the warming gradient, and the species distribution (see Discussion).
 
@@
 However, since 2010, when the weighted method was implemented, the quota allocation has favored the US over Canada, especially in terms of haddock and yellowtail flounder [@Trinko:2019ou].
-A perpetuation of this trend with no mitigation policy could jeopardize the arrangement as Canada's quota reduction could disincentive cooperation (see Sumaila et al., this Special Feature).
+A perpetuation of this trend with no mitigation policy could jeopardize the arrangement as Canada's quota reduction could disincentive cooperation [@Sumaila:2020tp].
 
@@
 Side payments do not have to be in monetary form and are widely used in transboundary stocks around the world.
-For example, Norway and Russia have implemented a quota swap strategy for jointly managed stocks of cod, haddock and capelin (*Mallotus villosus*) in the Barents Sea [^NR].
+For example, Norway and Russia have implemented a quota swap strategy for jointly managed stocks of cod, haddock and capelin (*Mallotus villosus*) in the Barents Sea [@FAO:2020vw].
 Similarly, species' quota swaps are allowed, up to a degree, within regulatory areas of the European union [@Baudron:2020dj].
@@
 
-[^NR]: Joint Fish, joint Russian-Norwegian Fisheries Commission [internet] http://www.jointfish.com/eng/THE-FISHERIES-COMMISSION/HISTORY.html
-
 Transboundary fisheries management have to be prepared for the uncertainty that comes with a changing world.
@@
 Overall, results for the Gulf of Maine agree with a reduction in MCP of all three species.
-However, some discrete areas show a positive change for yellowtail flounder by mid $21^{st}$ century (Figure \ref{fig:Figure3-IPHC-prop)), mainly driven by the GFDL model (Figure \ref{fig:FigureS23}).
+However, some discrete areas show a positive change for yellowtail flounder by mid $21^{st}$ century (Figure \@ref(fig:Figure3-IPHC-prop)), mainly driven by the GFDL model (Figure \@ref(fig:FigureS23)).
 Potential model artifacts could also be contributing to the results, especially in the northern part of the study area (Bay of Fundy) as most disagreeing grids are covered by land, which could be influencing the results.
-In contrast, considerable uncertainty exists in the change of MCP along the IPHC Convention area shown by a disagreement between ESMs (Figure \ref{fig:FigureS24}).
+In contrast, considerable uncertainty exists in the change of MCP along the IPHC Convention area shown by a disagreement between ESMs (Figure \@ref(fig:FigureS24)).
 Off the coast of British Columbia, increasing temperature trends are consistent among ESMs, however, other processes such as acidification and deoxygenation are still not well understood from British Columbia to the Gulf of Alaska  [@TalloniAlvarez:2019gz].

### 2020-11-21 Ecol/Manuscript_Draft.Rmd
Update to manuscript

@@
 
-The shifts in distribution of shared fish stocks will impact the economics of their fisheries [@Pinsky:2012kq; @Sumaila:2019gh, @Sumaila:2020tp], and create international disputes between countries [@Munro:2002uf; @Spijkers:2017ij; @Pinsky:2018cb].
+The shifts in distribution of shared fish stocks will impact the economics of their fisheries [@Pinsky:2012kq; @Sumaila:2019gh; @Sumaila:2020tp], and create international disputes between countries [@Munro:2002uf; @Spijkers:2017ij; @Pinsky:2018cb].
 Canada and the US share important transboundary stocks of salmon (*Oncorhynchus spp.*), Pacific halibut (*Hippoglossus stenolepis*), and Atlantic cod (*Gadus morhua*) offering a unique lens to understand the extent to which climate-induced distributional shifts will challenge the future sustainability of transboundary fisheries.
@@
 For this specific case, we considered Alaska as a separate entity, the US contiguous states as a second one (Washington, Oregon and California), and lastly British Columbia (Canada).
-For the GoMA we used the Northwest Atlantic Fisheries Organization's (NAFO) divisions 5Y, 5Ze, and 4X[^NAFO] within latitudes 46.2°N and 41.5°S, and longitudes -72°W and -64°E (Figure \ref{fig:Figure1-map}).
+For the GoMA we used the Northwest Atlantic Fisheries Organization's (NAFO) divisions 5Y, 5Ze, and 4X[^NAFO] within latitudes 46.2°N and 41.5°S, and longitudes -72°W and -64°E (Figure \ref(fig:ocFigure1-map)).
 Is worth mention that, while NAFO's divisional zones were used in this study for domestic management, NAFO does not manage fisheries within the EEZs of Canada and the United States.
@@
 
-```{r Figure1-map, eval = T, echo=FALSE, fig.height = 4, fig.width = 6, fig.cap="Map of Canada and the US with the regulatory areas of the International Pacific Halibut Commission and the NAFO sub-divisions containing the Gulf of Maine arrangement"}
+```{r ocFigure1-map, eval = T, echo=FALSE, fig.height = 4, fig.width = 6, fig.cap="Map of Canada and the US with the regulatory areas of the International Pacific Halibut Commission and the NAFO sub-divisions containing the Gulf of Maine arrangement"}
 
@@
 From 2010 onward, the GoMA suggests catch-limits based on a weighted method where 10% represents the stocks’ historical distribution (from 1967 to 1994) and 90% current distributions produced by quarterly surveys and catch [@TRAC:2016wu].
-Since its introduction, the average quota allocation for each species proposed by the GoMA has been (Table \ref{tab:Table1}); Atlantic cod 77% Canada and 23% US, haddock 55% Canada and 45% US, and yellowtail flounder 34% Canada and 66% US [@TRAC:2015wj; @TRAC:2015vp; @TRAC:2015tt; @TRAC:2018tw; @TRAC:2018tj; @TRAC:2018wx; @Trinko:2019ou].
+Since its introduction, the average quota allocation for each species proposed by the GoMA has been (Table \@ref(tab:ocTable1); Atlantic cod 77% Canada and 23% US, haddock 55% Canada and 45% US, and yellowtail flounder 34% Canada and 66% US [@TRAC:2015wj; @TRAC:2015vp; @TRAC:2015tt; @TRAC:2018tw; @TRAC:2018tj; @TRAC:2018wx; @Trinko:2019ou].
 However, because this is an unofficial agreement, Canada and the US ultimately take single management decisions [@Soboil:2006gw].
@@
 
-```{r Table1, eval = T, echo = F, warning=F, message=F}
+```{r ocTable1, eval = T, echo = F, warning=F, message=F}
 
@@
 In the case of the GoMA, region was defined as the $0.5^{\circ}$ x $0.5^{\circ}$ grid-cell within the specific NAFO divisional zones.
-For the IPHC analysis, region was defined as the Commission's regulatory areas (Figure \ref{fig:Figure1-map}).
+For the IPHC analysis, region was defined as the Commission's regulatory areas (Figure \ref(fig:ocFigure1-map)).
 We then averaged the values in three time periods (*t*) to reduce temporal model sensitivity.
@@
 The process was carried out for each ESM and results presented as average $\pm$ standard deviation (sd).
-All of the analysis was done in the statistical software R version 3.5.2 (2018-12-20) with the associated packages, *data.table* [@Packagedatatable:2019uh], *ggrepel* [@PackageggrepelAut:2018to], *gridExtra* [@PackagegridExtraM:2017wx], *knirt* [@PackageknitrAGen:2020wt], *RColorBrewer* [@PackagerColorBrewer:2014uw], *sf* [@PackagesfSimpleF:2018vp], and *tidyverse* [@PackagetidyverseE:2017vq].
+All of the analysis was done in the statistical software R version 3.5.2 (2018-12-20) with the associated packages, data.table [@Packagedatatable:2019uh], ggrepel [@PackageggrepelAut:2018to], gridExtra [@PackagegridExtraM:2017wx], knirt [@PackageknitrAGen:2020wt], RColorBrewer [@PackagerColorBrewer:2014uw], sf [@PackagesfSimpleF:2018vp], and tidyverse [@PackagetidyverseE:2017vq].
 All code is available at http://www.github.com/jepa/OC_Transboundary.
@@
 
-At least one third of the IPHC regulatory areas will see a reduction in MCP of Pacific halibut by 2050 relative to current MCP, regardless of the climate change scenario (Figure \ref{fig:Figure2-IPHC}).
+At least one third of the IPHC regulatory areas will see a reduction in MCP of Pacific halibut by 2050 relative to current MCP, regardless of the climate change scenario (Figure \ref(fig:ocFigure2-IPHC)).
 It is likely that the stock shift from the US.
@@
 The potential movement of halibut westward will increase the MCP of regulatory areas 3B (under a low emission scenario) and 4ABCE along the Aleutian Islands and Bering Sea.
-Regions 4DE, the most poleward regulatory areas of the IPHC, are expected to gain MCP by mid (Figure \ref{fig:Figure2-IPHC}) and end of the $21^{st}$ century (Figure \ref{fig:FigureS11}) under a high emission scenario due to the expansion of halibut suitable habitat as sea ice retreats (Figure \ref{fig:FigureS21}).
-In contrast, under a low emission scenario, sea ice is expected to stabilize towards mid 21st century, thus providing less “new” suitable habitat for Pacific halibut and resulting in undetectable changes in MCP for the region (Figure \ref{fig:Figure2-IPHC}B) and decreasing even more towards 2100 (Figure \ref{fig:FigureS11}).
+Regions 4DE, the most poleward regulatory areas of the IPHC, are expected to gain MCP by mid (Figure \ref(fig:ocFigure2-IPHC)) and end of the $21^{st}$ century (Figure \ref(fig:ocFigureS11)) under a high emission scenario due to the expansion of halibut suitable habitat as sea ice retreats (Figure \ref(fig:ocFigureS21)).
+In contrast, under a low emission scenario, sea ice is expected to stabilize towards mid 21st century, thus providing less “new” suitable habitat for Pacific halibut and resulting in undetectable changes in MCP for the region (Figure \ref(fig:ocFigure2-IPHC)B) and decreasing even more towards 2100 (Figure \ref(fig:ocFigureS11)).
 
@@
 IPHC_DBEM_sf <- IPHC_DBEM_sf %>% 
- # filter(Period == "Mid_Century") %>% # Paper figure
+ # filter(Period == "Mid_Century") %>% # Paper ocFigure
  filter(Period == "The_End_Century") %>%# Supplemental figure
@@
 
-```{r Figure2-IPHC, eval = T, echo = F, fig.cap= "Percentage change of MCP for species managed by the IPHC for mid 21st century (2041-2060) relative to present 2005-2014 under a A) high emission scenario and B) low emission scenario.
+```{r ocFigure2-IPHC, eval = T, echo = F, fig.cap= "Percentage change of MCP for species managed by the IPHC for mid 21st century (2041-2060) relative to present 2005-2014 under a A) high emission scenario and B) low emission scenario.
 Labels marked with * represent regions where models do not agree in direction of change."}
@@
 
-The same poleward trend is expected in the change of Pacific halibut stock-share ratio with the average proportion increasing up to 25% in some northern regions and decreasing by 10% in southern regions, relative to the present proportion (Figure \ref{fig:Figure3-IPHC-prop}).
+The same poleward trend is expected in the change of Pacific halibut stock-share ratio with the average proportion increasing up to 25% in some northern regions and decreasing by 10% in southern regions, relative to the present proportion (Figure \ref(fig:ocFigure3-IPHC-prop)).
 Maintaining emissions to lower levels through 2050 would potentially leave unchanged the stock-share ratio of three regulatory areas (3AC, and 4D) and negatively change regulatory area 2A.
@@
 
-```{r Figure3-IPHC-prop, eval = T, echo = F, fig.cap="Percentage change of stock-share ratio for IPHC under A) high emission scenario and B) low emission scenario for mid 21st century (2041-2060) relative to present 2005-2014.
+```{r ocFigure3-IPHC-prop, eval = T, echo = F, fig.cap="Percentage change of stock-share ratio for IPHC under A) high emission scenario and B) low emission scenario for mid 21st century (2041-2060) relative to present 2005-2014.
 Values represent the mean of 3 ESM; error bars represent \u00B1 sd."}
@@
 
-While some regulatory areas of the IPHC will see an incremental increase in Pacific halibut MCP, the results for the Gulf of Maine show an overall decrease in MCP by 2050, regardless of the climate change scenario or ESM (Figure \ref{fig:Figure4-GOMA}), intensifying by the end of the $21^{st}$ century (Figure \ref{fig:FigureS12}).
-For cod and haddock, MCP will decrease within the whole Gulf with no apparent win for any country in reference to the current period (Figure \ref{fig:Figure4-GOMA}).
-For yellowtail flounder, despite an overall reduction, some discrete areas are expected to increase with no particular pattern and high uncertainty, as ESMs in these regions do not agree in the direction of change (Figure \ref{fig:FigureS23}).
+While some regulatory areas of the IPHC will see an incremental increase in Pacific halibut MCP, the results for the Gulf of Maine show an overall decrease in MCP by 2050, regardless of the climate change scenario or ESM (Figure \ref(fig:ocFigure4-GOMA)), intensifying by the end of the $21^{st}$ century (Figure \ref(fig:ocFigureS12)).
+For cod and haddock, MCP will decrease within the whole Gulf with no apparent win for any country in reference to the current period (Figure \ref(fig:ocFigure4-GOMA)).
+For yellowtail flounder, despite an overall reduction, some discrete areas are expected to increase with no particular pattern and high uncertainty, as ESMs in these regions do not agree in the direction of change (Figure \ref(fig:ocFigureS23)).
 Despite the overall reduction in MCP for all three species in comparison to current values, there is a benefit of achieving a low emission scenario as reductions intensify under the high emission scenario.
@@
 
-```{r Figure4-GOMA, eval = T, echo = F, fig.cap= "Percentage change of MCP in the Gulf of Maine under, A) high emission scenario; and B) low emission for mid-century (2041-2060) relative to present (2005-2014).
+```{r ocFigure4-GOMA, eval = T, echo = F, fig.cap= "Percentage change of MCP in the Gulf of Maine under, A) high emission scenario; and B) low emission for mid-century (2041-2060) relative to present (2005-2014).
 Points represent regions where models do not agree in direction of change."}
@@
 Following a high emission path will affect mostly Canada’s share of yellowtail flounder and in less degree haddock, with an increase of cod share.
-under the low emission scenario, haddock and cod patterns intensify, while yellowtail flounder’s share approaches almost no change (Figure \ref{fig:Figure5-GOMA-prop}).
+under the low emission scenario, haddock and cod patterns intensify, while yellowtail flounder’s share approaches almost no change (Figure \ref(fig:ocFigure5-GOMA-prop)).
 Such pattern is likely the combination of the bathymetry or the Gulf, the warming gradient, and the species distribution (see Discussion).
@@
 
-```{r Figure5-GOMA-prop, eval = T, echo = F, fig.cap="Changes in MCP stock-share ratio for Gulf of Maine under (A) high emission; and (B) low emission scenarios for mid 21st century (2041-2060) relative to present (2005-2014).
+```{r ocFigure5-GOMA-prop, eval = T, echo = F, fig.cap="Changes in MCP stock-share ratio for Gulf of Maine under (A) high emission; and (B) low emission scenarios for mid 21st century (2041-2060) relative to present (2005-2014).
 Values represent the mean of 3 ESM; error bars represent \u00B1 sd."}
@@
 On the other hand, regions 3A and 3B have seen the largest decreases in the IPHC regulatory areas since 2010, from 35.3% to 30.6% and 20.6% to 15.9%, respectively.
-Similarly, in the Gulf of Maine, the projected stock-share gain of yellowtail flounder and haddock by the US (Figure \ref{fig:Figure5-GOMA-prop}) follows a historical trend where in 2019, Canada's stock-share decreased from 35% to 32% and 60% to 40% relative to 2010, respectively [@Trinko:2019ou].
+Similarly, in the Gulf of Maine, the projected stock-share gain of yellowtail flounder and haddock by the US (Figure \ref(fig:ocFigure5-GOMA-prop)) follows a historical trend where in 2019, Canada's stock-share decreased from 35% to 32% and 60% to 40% relative to 2010, respectively [@Trinko:2019ou].
 
@@
 Geographic barriers [@Cheung:2015fm; @Kleisner:2016je], local temperature gradients [@Pinsky:2013ab], species interactions and human activities [@Serpetti:2017he] might change the rate and direction of species shifts.
-For the IPHC, geographic barriers might induce a westward increase of stock-share in IPHC regions where species can only migrate northward into the Arctic Ocean through the Bering Sea and Bering Strait [@Cheung:2015fm] (Figure \ref{fig:Figure3-IPHC-prop}).
-In the Gulf of Maine, future projections could be a response to a temperature gradient shift combined with geographic barriers as southern waters are deeper and warming slower than northern waters according to the ESMs (Figure \ref{fig:FigureS22}).
+For the IPHC, geographic barriers might induce a westward increase of stock-share in IPHC regions where species can only migrate northward into the Arctic Ocean through the Bering Sea and Bering Strait [@Cheung:2015fm] (Figure \ref(fig:ocFigure3-IPHC-prop)).
+In the Gulf of Maine, future projections could be a response to a temperature gradient shift combined with geographic barriers as southern waters are deeper and warming slower than northern waters according to the ESMs (Figure \ref(fig:ocFigureS22)).
 Moreover, Maine has seen its landings of yellowtail flounder increased at the expenses of southern states [@Pinsky:2012kq].
@@
 Moreover, overlapping shifting stocks could interfere in gear-limitation management rules of multiple fisheries generating conflicts between fleets [@VanDerVoo:2016uc].
-The effectiveness of the IPHC-Closed Area ("CA" in Figure \ref{fig:Figure2-IPHC}) in terms of protecting juveniles has been historically questioned as trawling for other species is still allowed in the area [@Karim:2010ut; @IPHC:2017CA].
+The effectiveness of the IPHC-Closed Area ("CA" in Figure \ref(fig:ocFigure2-IPHC)) in terms of protecting juveniles has been historically questioned as trawling for other species is still allowed in the area [@Karim:2010ut; @IPHC:2017CA].
 In 2015, for example, 97% of the trawl by-catch in areas 4CDE and the Closed Area were juveniles [@IPHC:2017CA].
@@
 In our results, the "winners and losers" of climate change, and the intensity of the change, will be scenario dependent.
-For instance, stock-share of yellowtail flounder under a high emission scenario will be larger for the US while Canada's gain of cod stock-share will be larger under a low emission scenario (Figure \ref{fig:Figure5-GOMA-prop}).
+For instance, stock-share of yellowtail flounder under a high emission scenario will be larger for the US while Canada's gain of cod stock-share will be larger under a low emission scenario (Figure \ref(fig:ocFigure5-GOMA-prop)).
 Applying previously describe strategies (e.g.
@@
 Overall, results for the Gulf of Maine agree with a reduction in MCP of all three species.
-However, some discrete areas show a positive change for yellowtail flounder by mid $21^{st}$ century (Figure \@ref(fig:Figure3-IPHC-prop)), mainly driven by the GFDL model (Figure \@ref(fig:FigureS23)).
+However, some discrete areas show a positive change for yellowtail flounder by mid $21^{st}$ century (Figure \@ref(fig:ocFigure3-IPHC-prop)), mainly driven by the GFDL model (Figure \@ref(fig:ocFigureS23)).
 Potential model artifacts could also be contributing to the results, especially in the northern part of the study area (Bay of Fundy) as most disagreeing grids are covered by land, which could be influencing the results.
-In contrast, considerable uncertainty exists in the change of MCP along the IPHC Convention area shown by a disagreement between ESMs (Figure \@ref(fig:FigureS24)).
+In contrast, considerable uncertainty exists in the change of MCP along the IPHC Convention area shown by a disagreement between ESMs (Figure \@ref(fig:ocFigureS24)).
 Off the coast of British Columbia, increasing temperature trends are consistent among ESMs, however, other processes such as acidification and deoxygenation are still not well understood from British Columbia to the Gulf of Alaska  [@TalloniAlvarez:2019gz].
@@
 
-## Supplements
+<!-- ## Supplements -->
 
@@
 
-```{r FigureS11, eval = T, echo = F, fig.cap = "Percentage change of MCP for species managed by the IPHC for end-century (2081–2100) relative to 2005–2014 under a A) high emission scenario and B) low emission scenario.
+```{r ocFigureS11, eval = F, echo = F, fig.cap = "Percentage change of MCP for species managed by the IPHC for end-century (2081–2100) relative to 2005–2014 under a A) high emission scenario and B) low emission scenario.
 Labels marked with * represent regions where models do not agree in direction of change."}
@@
 
-```{r FigureS12, eval = T, echo = F, fig.cap = "Percentage change of MCP in the Gulf of Maine under (RCP 8.5) high emission scenario and (RCP 2.6) low emission for end-century (2080–2100) referent to present (2005– 2014).
+```{r ocFigureS12, eval = F, echo = F, fig.cap = "Percentage change of MCP in the Gulf of Maine under (RCP 8.5) high emission scenario and (RCP 2.6) low emission for end-century (2080–2100) referent to present (2005– 2014).
 Values represent the mean of 3 ESM.
@@
 
-```{r FigureS21, eval = T, echo = F, fig.cap = "Projected environmental variables under climate change from 2010 to 2010 for Arctic regions of the IPHC (Top:4D, Bottom, 4E).
+```{r ocFigureS21, eval = F, echo = F, fig.cap = "Projected environmental variables under climate change from 2010 to 2010 for Arctic regions of the IPHC (Top:4D, Bottom, 4E).
 The solid line represents the average of all three ESMs and the shaded area represents the model’s uncertainty (s.d.)."}
@@
 
-```{r FigureS22, eval = T, echo = F, fig.cap = "Depth profile (A) and bottom water warming of the Gulf of Maine.
+```{r ocFigureS22, eval = F, echo = F, fig.cap = "Depth profile (A) and bottom water warming of the Gulf of Maine.
 Everything deeper than 1000 meters is colored in green.
@@
 
-```{r FigureS23, eval = T, echo = F, fig.cap = "Changes in maximum catch potential of yellowtail flounder (*Limanda ferruginea*) within the study area by mid-century relative to present time.
+```{r ocFigureS23, eval = T, echo = F, fig.cap = "Changes in maximum catch potential of yellowtail flounder (*Limanda ferruginea*) within the study area by mid-century relative to present time.
 Results for the three global circulation models (GFDL, IPSL, MPIS) used in the current study and two climate change scenarios (Top: High emission – RCP 8.5, Bottom: Low Emission – RCP 2.6).
@@
 
-```{r FigureS24, eval = T, echo = F, fig.cap = "Projected MCP change relative to present (2005-2014) for each IPHC regulatory area.
+```{r ocFigureS24, eval = T, echo = F, fig.cap = "Projected MCP change relative to present (2005-2014) for each IPHC regulatory area.
 Colors represents the different ESM used in the study.
@@
 
-```{r Figure_out_outliers, eval = F, echo = F}
+```{r ocFigure_out_outliers, eval = F, echo = F}
 
@@
 
-# Plot map for paper figure 
+# Plot map for paper ocFigure 
 Seq <- seq(-100,100,by=5) #Axis
@@
 <!-- # Option removing NAFO -->
-<!-- Shifts in the distribution of 33 jointly managed transboundary stocks of North America by 2050 relative to 2010 show that MCP of transboundary stocks will overall increase in Atlantic-Canadian and Alaskan waters and decrease in Pacific-Canadian and the US contiguous states waters (Figure \ref{fig:Figure2-IPHC}).
+<!-- Shifts in the distribution of 33 jointly managed transboundary stocks of North America by 2050 relative to 2010 show that MCP of transboundary stocks will overall increase in Atlantic-Canadian and Alaskan waters and decrease in Pacific-Canadian and the US contiguous states waters (Figure \ref(fig:ocFigure2-IPHC)).
 Such changes will be more intense under the high emission scenario (Fig.

### 2020-11-21 Ecol/Supplements.Rmd
Update to manuscript

--- 2020-11-16 Ecol/Manuscript_Draft.Rmd
@@
   bookdown::pdf_book:
-    toc : false
-  # pdf_document: default
-  # word_document: default
-editor_options:
-  chunk_output_type: console
-csl: ../References/E&S.csl
-bibliography: ../References/Oceans_Canada_Biblio.bib
+    toc : no
+    keep_tex: no
+    number_sections: yes
 header-includes: #allows you to add in your own Latex packages
@@
 - \floatplacement{figure}{H} #make every figure with caption = h
+- \floatplacement{table}{H}
+- \usepackage{caption}
+- \captionsetup[figure]{name = Figure A4}
+- \captionsetup[table]{name = Table A4}
 ---
 
-```{r setup_oc, eval = T, echo = F, warning = F, message = F, results = 'hide'}
-
-#### READ ME !!! ####
-# Run this chunk before knit so you make sure you have all pkgs installed in R
-
+```{r setup, eval = T, echo=F, warning=F,message=F, results='hide'}
 library(MyFunctions)
-
 #### Library ####
 packages <- c(
- "readxl", # Read dataframe
   "dplyr", # Data manipulation
- "tidyr", # Data manipulation
- "ggplot2", #Nice grpahs and spatial analysis
- "cowplot",
- "rgdal",
- "RColorBrewer",
   "knitr",
   "kableExtra",
- "data.table",
- "ggrepel",
- "gridExtra",
- "ggmap",
- "rgeos",
- "sf",
- "sp",
- "rgdal", #Spatial analysis 
- "tools", #Spatial analysis 
- "png", # For reading plots in chunk codes
- "grid", # For reading plots in chunk codes
- "here"
+  "png",
+  "grid",
+  "janitor"
 )
-
 my_lib(packages)
-
-##________________________________________________##
-
- # Current time
-Beg_In <- paste(2005); Beg_In
-Beg_End <- paste(2014); Beg_End
-
-# Mid century
-Mid_In <- paste(2041);Mid_In # 2046
-Mid_End <- paste(2060);Mid_End
-
-# End Century
-End_In <- paste(2080);End_In # 2090
-End_End <- paste(2099);End_End
 ```
-
-<!-- ## Abstract -->
-
-<!-- Climate change is shifting the distribution of fish stocks that straddle between Exclusive Economic Zones (EEZ), challenging transboundary fisheries management.
-Here, we examine the projected sharing of jointly managed transboundary fish stocks between Canada and the United States.
-We hypothesize that ocean warming will alter the sharing of fish stocks between the two countries, and that such changes will intensify under a high carbon emission scenario.
-We look at the specific cases of the International Pacific Halibut Commission that manages Pacific halibut (*Hippoglossus stenolepis*) and a resource sharing arrangement in the Gulf of Maine for cod (*Gadus morhua*), haddock (*Melanogrammus aeglefinus*) and yellowtail flounder (*Limanda ferruginea*) to discuss the management consequences of shifts in transboundary stocks.
-We rely on multiple Earth system models’ simulations and species distribution models to estimate the change in catch potential and stock share ratio of each transboundary stock in the $21^{st}$ century under two climate change scenarios.
-Results show that, even under a low emission scenario, most transboundary fish stocks sharing ratios, i.e., the proportion of the total catch of a fish stock taken by a given country, will change by 2050 relative to present.
-The overall reduction in catch potential, in addition to the changes in stock-share will further exacerbate trade-offs between changes in species catch potential.
-Such trade-offs in the Atlantic and Pacific regions will be amplified if a high emission scenario is followed, relative to a low carbon emission scenario.
-Based on the simulation results, we examine possible solution options to reduce climate risks on transboundary fish stocks and fisheries.
--->
-
-<!-- Keywords: *Transboundary fisheries management; climate change; joint fisheries management; species distribution shift* -->
-
-## Introduction
-
-<!-- ##### First paragraph of paper summary -->
-
-In 1982, the United Nations Law of the Sea Convention (UNCLOS) formalized the concept of exclusive economic zones (EEZs) creating what we know today as shared stocks [@UnitedNations:1986tl], i.e.
-stocks that migrate between countries EEZs (known as transboundary stocks) or between EEZs and the high seas (also called straddling stocks) [@Song:2017iua].
-Today, an estimated 347 [@Teh:2015gd] to 1500 [@Caddy:1997ue] fish stocks cross national borders, some of them jointly managed by two or more countries.
-These stocks are responsible for almost 50% of these countries total fish catches [@Teh:2015gd].
-Under Article 63, UNCLOS incentives actions to cooperate on the management of shared stocks [@UnitedNations:1986tl] as often management success depends on effective cooperation between parties [@Munro:2002uf; @Sumaila:2013hv].
-Since the definition of shared stocks, game theory has been one of the most common approaches used to analyze the management of these type of stocks.
-However, shared stocks' management can be convoluted due to the participation of several fishing “players”, different countries and sometimes jurisdictions within a country, the migration patterns of the stock, and their abundance fluctuation within space and time [@Munro:2002uf, Engler and Saunders *in press*].
-In addition, international treaties might not be prepared to address the effects that climate change will bring to shared fish stocks (Engler and Saunders *in press*, Koubrak and VanderZwaag, *in press*).
-
-<!-- ##### Climate Change and Transboundary Fisheries -->
-
-The ocean is getting warmer [@Rheim:2013fv], less oxygenated [@Schmidtko:2017cl], and increasing in acidity [@Ross:2011kd; @IPCC:2019tn].
-To cope with these changes in ocean biophysic properties, marine species, including shared fish stocks, have been shifting their distribution towards the poles and/or deeper waters [@Poloczanska:2016kk].
-As climate change reshapes the ocean's environment worldwide [@Gattuso:2015jz], shared fisheries' delicate governance is threatened as new migration patterns may arise [@Miller:2013iv; @Pinsky:2018cb], historic distribution and abundances might shift [@Cheung:2010dt], and species basic natural traits may modify [@Pauly:2017hpa].
-Catches of shared stocks like tunas, have significantly increased in some regions such as the subtropical Atlantic and western Pacific Oceans and are projected to continue [@MonllorHurtado:2017cm; @ErauskinExtramiana:2019fw].
-Multiple shared species in North America have been observed to shift in distribution following changes in optimal conditions such as sockeye salmon (*Oncorhynchus nerka*) [@McDaniels:2010vn], Atlantic cod [@Pershing:2015gq], and flounders [@Pinsky:2012kq].
-Moreover, these shifts are projected to continue towards the end of the $21^{st}$ century [@Cheung:2018hz].
-As a result, some countries or management jurisdictions may see more shared fisheries and their catches shifting into their waters while others will stand to lose [@Oremus:2020id; @Pinsky:2018cb].
-Nevertheless, management rules for shared stocks (e.g.
-quota or spatial delimitation) are often determined based on current and/or historic knowledge of the stock's distribution and do not consider future shifts in distributions [@FredstonHermann:2018kp].
-
-<!-- ##### Past Conflicts of shifting stocks -->
-
-The shifts in distribution of shared fish stocks will impact the economics of their fisheries [@Pinsky:2012kq; @Sumaila:2019gh, @Sumaila:2020tp], and create international disputes between countries [@Munro:2002uf; @Spijkers:2017ij; @Pinsky:2018cb].
-Canada and the US share important transboundary stocks of salmon (*Oncorhynchus spp.*), Pacific halibut (*Hippoglossus stenolepis*), and Atlantic cod (*Gadus morhua*) offering a unique lens to understand the extent to which climate-induced distributional shifts will challenge the future sustainability of transboundary fisheries.
-These countries have a long history of fisheries cooperation participating in diverse, jointly managed, commercial transboundary stocks through various fisheries management organizations [@NOAA:2018tu].
-Furthermore, climate-related fluctuations in stocks' distribution have historically created disputes between Canada and the US, increasing international conflict and threatening the health of diverse transboundary stocks [@Munro:2002uf; @CIA:2017uta].
-
-It is expected that climate induced shifts in stocks’ distribution will affect the rules in place that keep international treaties alive.
-Therefore, the main objective of this article is to assess the level of exposure that bi-lateral transboundary fisheries treaties between Canada and the US have to climate change through shifts in stock distributions.
-Specifically, we rely on a species distribution model and scenario planning to project the changes in the distribution of selected fish stocks jointly managed by Canada and the United States focusing on two case studies (the International Pacific Halibut Commission and a fisheries arrangement for the Gulf of Maine) Finally, we explore similar situations around the world and identify opportunities to improve the adaptability of transboundary stocks management to climate change in North America.
-Despite an overall expectation of species following a poleward shift, important geographic constraints (e.g.
-Gulf of Alaska representing a latitudinal block) [@Kleisner:2016je], geo-political features (e.g.
-the localization of Alaska in reference to Canada and the contiguous states), and management rules (e.g.
-quota allocations, spatial management rules) may play an important role in the redistribution of benefits.
-Understanding these stocks shifts will shed a light on future conditions and inform decision-makers on the paths to follow under a changing climate.
-
-## Materials and Methods
-
-### Study area and fisheries
-
-The current study used the International Pacific Halibut Commission (IPHC) and the Gulf of Maine arrangement (hereafter referred as GoMA) as case studies to discuss the implications that climate change could have in the management of transboundary stocks.
-For the IPHC, we used the most updated spatial regulatory data along its 12 regulatory areas [@IPHCSecreatriat:2017uz; @IPHC:2019wt].
-For this specific case, we considered Alaska as a separate entity, the US contiguous states as a second one (Washington, Oregon and California), and lastly British Columbia (Canada).
-For the GoMA we used the Northwest Atlantic Fisheries Organization's (NAFO) divisions 5Y, 5Ze, and 4X[^NAFO] within latitudes 46.2°N and 41.5°S, and longitudes -72°W and -64°E (Figure \ref{fig:Figure1-map}).
-Is worth mention that, while NAFO's divisional zones were used in this study for domestic management, NAFO does not manage fisheries within the EEZs of Canada and the United States.
-Fisheries data fpr the projections was gathered from the Sea Around Us from 1951 to 2014 [@Zeller2016].
-
-[^NAFO]: Northwest Atlantic Fisheries Organization, Available at https://www.nafo.int/Science/
-
-```{r Study_Area_Map, eval = F, echo = F, warning=F, message=F}
-
-Countries <- c("Canada","United States")
-
-### North America Initial Map ####
-path_world <- my_path("G",Extra_Path = "Spatial/TM_WORLD_BORDERS-0.3")
-file_name <- "TM_WORLD_BORDERS"
-
-World_Land_sf <- st_read(dsn = path_world, 
-layer = file_path_sans_ext(file_name)
-) %>% 
-st_transform(crs = 3832)
-
-# names(World_Land_sf)
-
-North_America_Land <- World_Land_sf %>% 
-filter(NAME %in% Countries) %>% 
-st_transform(crs = 3832)
-
-# head(North_America)
-
-# ggplot(North_America_Land) +
-#  geom_sf() +
-#  coord_sf(ylim = c(3051701,11528813)
-#  )
-
-### North America EEZs Map ####
-path_eez <- my_path("G",Extra_Path = "Spatial/World_EEZ_v10_2018-0.3")
-#The File
-fnam_eez <- "eez_v10.shp"
-
-eez_world_sf <- st_read(dsn = path_eez, 
-            layer = file_path_sans_ext(fnam_eez)
-) %>% 
- st_transform(crs = 3832)
-
-Nort_America_EEZ <- eez_world_sf %>% 
-filter(Territory1 %in% Countries)
-
-# Testing
-ggplot(Nort_America_EEZ) +
-geom_sf()
-
-# Testing together
-
-ggplot(North_America_Land) +
- geom_sf() +
- geom_sf(data = Nort_America_EEZ, colour = "black") +
- coord_sf(ylim = c(3051701,11528813)
- )
-
-#### IPHC Regulatory Areas ####
-
-path_IPHC <- my_path("D",Extra_Path = "IPHC/IPHC_RegulatoryAreas/")
-
-# The Canada file
-fnam_IPHC_C <- "IPHC_RegulatoryAreas_CAN"
-
-IPHC_Reg_C <- st_read(dsn = path_IPHC, 
-           layer = file_path_sans_ext(fnam_IPHC_C)
-) %>% 
- select(
-  ID,
-  Country = COUNTRY,
-  State = PROV_EN,
-  RegArea
- ) %>% 
- mutate(Comments = "NA") %>% 
- st_transform(crs = 3832)
-
-# 4326 use this to merge with DBEM data
-# 3832 use this to center the map and plot
-
-# ggplot(IPHC_Reg_C) +
-# geom_sf()
-
-# The US File
-fnam_IPHC_US <- "IPHC_RegulatoryAreas_US"
-
-IPHC_Reg_US <- st_read(dsn = path_IPHC,
-            layer = file_path_sans_ext(fnam_IPHC_US)
-) %>%
- st_transform(crs = 3832)
-
-# head(IPHC_Reg_US)
-ggplot(IPHC_Reg_US) +
- geom_sf()
-
-### Combine both shapefiles
-
-IPHC_Reg <- rbind(IPHC_Reg_US,IPHC_Reg_C)
-
-ggplot(IPHC_Reg) +
- geom_sf()
-
-##### NAFO Regulatory Area ####
-
-path_NAFO <- paste(Data_path,"Spatial/NAFO")
-#The File
-fnam_NAFO <- "Divisions"
-
-NAFO_Area <- st_read(dsn = path_NAFO,
-           layer =file_path_sans_ext(fnam_NAFO))%>% 
- st_transform(crs = 3832)
-
-Zones <- c(
- "5Ze",
- # "5Zw",
- "5Y",
- "4X"
-)
-
-NAFO_5z <- NAFO_Area %>% 
-filter(ZONE %in% Zones)
-
-# head(NAFO_5z)
-
-ggplot() +
-geom_sf(data = North_America_Land,
-    fill = "lightgrey",
-    colour = "black") +
- my_ggtheme_m()()
-
-#### The final Map ####
-
-# Homonize collors 
-brewer.pal(name="Set2",5)
-
-# Canada "#grey80"
-# US "#grey40", 
-# NAFO "#66CC99"
-# IPHC #f01282
-
-#North America point of view
-
-North_A <- ggplot() +
- geom_sf(data = North_America_Land, 
-     aes(fill = NAME),
-     colour = "black"
- ) +
- geom_sf(data = IPHC_Reg, 
-     aes(fill = "IPHC") ,
-     colour = "black"
- ) +
- geom_sf(data = NAFO_5z, 
-     aes(fill = "NAFO"),
-     colour = "black"
- ) +
- my_ggtheme_m()() +
- scale_fill_manual("Region",
-          breaks = c("Canada","IPHC","NAFO", "United States"), 
-          values=c("grey80","#CC6666","#66CC99","grey40")
-          ) +
- theme(legend.position = "right")
-
-ggsave("Fig1_NA.png",
-    plot = North_A,
-    width = 6,
-    height = 5,
-    units = "in",
-    path = Results_Path)
-
-#NAFO #
-
-NAFO <- ggplot() +
- geom_sf(data = NAFO_5z, #NAFO regions
-     aes(fill = "NAFO"),
-     colour = "black"
- )+
- geom_sf_label(data = NAFO_5z, # RegAreas labels
-        aes(
-         label = ZONE#,
-         # fill = "NAFO"
-        ),
-        alpha = 0.5
- ) +
- geom_sf(data = North_America_Land, # North America Land
-     aes(fill=NAME),
-     colour = "black"
- ) +
- coord_sf(ylim = c(5951701,4728813),
-      xlim = c(15373019,16573019)
- ) +
- # scale_fill_brewer("Region",palette = "Set2") +
- theme(
-  panel.background = element_blank(),
-  panel.border   = element_blank(),
-  panel.grid.minor = element_blank(),
-  panel.grid.major = element_line(color = "transparent"),
-  legend.position = "bottom",
-  axis.title = element_blank()
- ) +
- scale_fill_manual("Region",breaks = c("Canada", "NAFO", "United States"), 
-          # values = c("#E78AC3","#A6D854","8DA0CB")
-          values=c("grey80", "#66CC99", "grey40")
-          ); NAFO
-
-# Save plot for manuscrip
-ggsave("Fig1_NAFO.png",
-    plot = NAFO,
-    width = 6,
-    height = 5,
-    units = "in",
-    path = my_path("R"))
-
-# IPHC
-
-IPHC_Reg$RegArea <- gsub("Closed Area","CA",IPHC_Reg$RegArea)
-
-IPHC <- ggplot() +
- geom_sf(data = IPHC_Reg,
-     aes(fill = "IPHC"),
-     colour = "black"
- ) + 
- geom_sf(data = North_America_Land, # North America Land
-     aes(fill=NAME),
-     colour = "black"
- ) +
- geom_sf_label(data = IPHC_Reg, # RegAreas labels
-        aes(
-         label = RegArea#,
-         # fill = Percentage
-        ),
-        alpha = 0.5
- ) +
-
- coord_sf(xlim = c(1963800, 10041910), # Subsets north america
-      ylim = c(3651701,9728813)
- ) +
- theme(
-  panel.background = element_blank(),
-  panel.border   = element_blank(),
-  panel.grid.minor = element_blank(),
-  panel.grid.major = element_line(color = "transparent"),
-  legend.position = "bottom",
-  axis.title = element_blank()
- ) +
- scale_fill_manual("Region",breaks = c("Canada", "IPHC", "United States"), 
-          values=c("grey80", "#CC6666", "grey40")
-          )
-
-# Save plot for manuscrip
-ggsave("Fig1_IPHC.png",
-    plot = IPHC,
-    width = 6,
-    height = 5,
-    units = "in",
-    path = my_path("R"))
-
-```
-
-```{r Figure1-map, eval = T, echo=FALSE, fig.height = 4, fig.width = 6, fig.cap="Map of Canada and the US with the regulatory areas of the International Pacific Halibut Commission and the NAFO sub-divisions containing the Gulf of Maine arrangement"}
-
-img <- readPNG("./Figures/Figure 1.png")
-grid.raster(img)
-
-```
-
-```{r Spatial_data, eval = F, echo = F, warning=F, message=F, results = 'hide'}
-
-# List of DBEM INDEX within the EEZ
-#Data provided by Vicki Lam
-EEZIDs_List <- my_path("G",Extra_Path = "Spatial/DBEM",Name="Updated_EEZList_17June2016.xlsx",Read = TRUE)
-
-EEZ_CellID <- my_path("G",Extra_Path = "Spatial/DBEM",Name="EEZ_CellID.xlsx",Read = TRUE)
-colnames(EEZ_CellID) <- c("EEZID","INDEX")
-
-# DBEM Coordinate system
-Coor <- my_path("G",Extra_Path = "Spatial/DBEM", Name = "Lon_Lat_DBEM.txt", Read = TRUE)
-colnames(Coor) <- c("INDEX","Longitude","Latitude")
-
-### Select EEZs
-EEZs <- c(
- "Canada (Pacific)",
- "Canada (Arctic)",
- "USA (West Coast)",
- "USA (Alaska, Arctic)",
- "USA (Alaska, Subarctic)",
- "Canada (Arctic)",
- "Canada (East Coast)",
- "USA (East Coast)"
-)
-
-### North America Initial Map ####
-
-path_world <- my_path("D",Extra_Path = "Spatial/TM_WORLD_BORDERS")
-file_name <- "TM_WORLD_BORDERS"
-
-World_Land_sf <- st_read(dsn = path_world, 
-             layer = file_path_sans_ext(file_name)
-) %>% 
- st_transform(crs = 4326)
-
-# names(World_Land_sf)
-
-North_America_Land <- World_Land_sf %>% 
- filter(NAME %in% c("Canada","United States")) %>% 
- st_transform(crs = 3832) # 4326 use this to merge with DBEM data
-# 3832 use this to center the map and plot
-
-#### _____________________TEST _____________________ #
-# head(North_America_Land)
-# ggplot(North_America_Land) +
-#  geom_sf() +
-#  coord_sf(xlim = c(-120, -179),
-#      ylim = c(30,70)
-#  )
-##__________________________________________ #
-
-### North America EEZs Map ####
-
-path_eez <- my_path("D",Extra_Path = "Spatial/World_EEZ_v10_2018")
-#The File
-fnam_eez <- "eez_v10.shp"
-
-eez_world_sf <- st_read(dsn = path_eez, 
-            layer = file_path_sans_ext(fnam_eez)
-) %>% 
- st_transform(crs = 4326)# 4326 use this to merge with DBEM data
-# 3832 use this to center the map and plot
-
-#### _____________________TEST _____________________ #
-# head(eez_world_sf)
-### Test this map
-# ggplot(ezz_North_America) +
-#  geom_sf()
-##__________________________________________##
-
-#### IPHC Regulatory areas ####
-
-## Correct DBEM for Alaska ####
-IHPC_EEZs <- c(
- "Canada (Pacific)",
- # "Canada (Arctic)"
- "USA (West Coast)",
- "USA (Alaska, Arctic)",
- "USA (Alaska, Subarctic)"#,
- # "Russia (Far East)"
-)
-
-IPHC_EEZsID <- EEZIDs_List %>% 
- filter(Name %in%IHPC_EEZs) %>% 
- left_join(EEZ_CellID,
-      by = "EEZID") %>% 
- left_join(Coor,
-      by = "INDEX")
-
-# "Move" the map so results are not in the other side of the world and it matches the projection I want
-IPHC_Coor_Corrected <- IPHC_EEZsID %>% 
- filter(Longitude > 0) %>% 
- mutate(Longitude = Longitude-360)
-
-IPHC_Coor_Corrected <- IPHC_EEZsID %>% 
- filter(Longitude < 0) %>% 
- bind_rows(IPHC_Coor_Corrected) %>% 
- filter(Latitude > 25)
-
-# Create new column to merge with shapefiles
-
-IPHC_Coor_Corrected_Clean <- IPHC_Coor_Corrected %>% 
- mutate(
-  State = ifelse(Name == "Canada (Pacific)", "British Columbia",
-          ifelse(Name == "USA (West Coast)","WAORCA","Alaska"))
- ) %>% 
- select(
-  # State,
-  INDEX,
-  longitude = Longitude,
-  latitude = Latitude)
-
-# Now we load IPHC shapefiles ####
-path_IPHC <- my_path("D",Extra_Path = "Spatial/IPHC_RegulatoryAreas")
-# The Canada file
-fnam_IPHC_C <- "IPHC_RegulatoryAreas_CAN"
-
-IPHC_Reg_C <- st_read(dsn = path_IPHC, 
-           layer = file_path_sans_ext(fnam_IPHC_C)
-) %>% 
- select(
-  ID,
-  Country = COUNTRY,
-  State = PROV_EN,
-  RegArea
- ) %>% 
- mutate(Comments = "NA") %>% 
- st_transform(crs = 4326)
-
-# 4326 use this to merge with DBEM data
-# 3832 use this to center the map and plot
-
-#### _____________________TEST _____________________##
-# head(IPHC_Reg_C)
-# ggplot(IPHC_Reg_C) +
-# geom_sf()
-##_________________________________________________##
-# The US File
-fnam_IPHC_US <- "IPHC_RegulatoryAreas_US"
-
-IPHC_Reg_US <- st_read(dsn = path_IPHC, 
-            layer = file_path_sans_ext(fnam_IPHC_US)
-) %>% 
- st_transform(crs = 4326)
-
-#### _____________________TEST _____________________ #
-# head(IPHC_Reg_US)
-# ggplot(IPHC_Reg_US) +
-#  geom_sf()
-##_________________________________________________##
-
-### Combine both shapefiles
-
-IPHC_Reg <- rbind(IPHC_Reg_US,IPHC_Reg_C)
-
-#### _____________________TEST _____________________ #
-# head(IPHC_Reg,12)
-# tail(IPHC_Reg)
-# unique(IPHC_Reg$State)
-
-# It's going to take a while... 
-# ggplot(IPHC_Reg) +
-#  geom_sf()
-##_________________________________________________##
-
-# Now join the Shapefile with the DBEM lat/long dataset
-
-# Convert DBEM to sf
-IPHC_Coor_sf = st_as_sf(IPHC_Coor_Corrected_Clean,
-            coords = c("longitude", "latitude")) %>% 
- st_set_crs(4326) %>% # to match shapefiles
- st_transform(4326) # to match shapefiles
-
-# head(IPHC_Coor_sf)
-
-# Merge DBEM sf to polygons
-IPHC_Reg_DBEM <- st_join(IPHC_Reg,
-             IPHC_Coor_sf, join = st_contains) %>% 
- filter(!is.na(INDEX)) %>%
- arrange(INDEX) 
-# %>% 
-#  st_transform(3832) # Go back to original projection otherwise doesnt like to plot
-
-IPHC_Reg_DBEM_df <- as.data.frame(IPHC_Reg_DBEM) %>% 
- select(INDEX,RegArea)
-
-#### _____________________TEST _____________________ #
-# head(IPHC_Reg_DBEM_df)
-# IPHC_Reg_DBEM_df %>% 
-#  arrange(INDEX) %>% 
-# head()
-##_________________________________________________##
-
-### STOP 
-## Go to the results and now estimate the %change by region using IPHC_Reg_DBEM_df then, convert it to sf and merge it with IPHC_Reg
-
-# Gulf of Maine ####
-#### NAFO data ####
-
-# path_NAFO <- paste(Data_Path,"/Spatial/NAFO",sep="")
-#The File
-# fnam_NAFO <- "Divisions"
-
-# NAFO_Area <- st_read(dsn = path_NAFO,
-# layer =file_path_sans_ext(fnam_NAFO))
-
-Zones <- c(
- "5Ze",
- # "5Zw",
- "5Y",
- "4X"
-)
-
-# NAFO_5z <- NAFO_Area %>% 
-# filter(ZONE %in% Zones)
-
-#### _____________________TEST _____________________ #
-# head(NAFO_5z)
-
-# ggplot(NAFO_5z) +
-# geom_sf()
-# geom_sf(aes (fill = ZONE))
-##_________________________________________________##
-
-### Atlantic EEZ polygon (I don't think we need this for now) ####
-
-Atlantic_EEZs <- c(
- "Canada (Arctic)",
- "Canada (East Coast)",
- "USA (East Coast)"
-)
-
-Atlantic_EEZsID <- EEZIDs_List %>%
- filter(Name %in% Atlantic_EEZs) %>%
- left_join(EEZ_CellID,
-      by = "EEZID") %>%
- left_join(Coor,
-      by = "INDEX")
-
-### Atlantic DBEM Data ####
-
-GB_Coor <- Coor %>% 
- filter(INDEX %in% Atlantic_EEZsID$INDEX) %>% 
- mutate(one = 1)
-
-# Atlantic Land polygon ####
-
-Countries <- c(
- "Canada",
- "United States"
-)
-
-### EEZ GM ####
-eez_GM <- eez_world_sf %>% 
- filter(Territory1 %in% Countries)
-
-#### _____________________TEST _____________________ #
-# ggplot() +
-#  geom_sf(data = eez_GM) +
-#  coord_sf(xlim = c(-71.0592, -63.33333),
-#      ylim = c(40.5,45.9759)
-#      )
-##_________________________________________________##
-
-GM_Land <- World_Land_sf %>% 
- filter(NAME %in% Countries)
-
-```
-
-### The International Pacific Halibut Commission
-
-The IPHC was established by Canada and the United States to oversee the management of Pacific halibut (*Hippoglossus stenolepis*) [@IPHC:2014tz].
-There are 12 regulatory areas from which 3AB holds 51.2% of the stock, followed by regions 2ABC and 4ACDE with 23.1% and 20.4%, respectively, and lastly region 4B with only 5.2% of the stock distribution [@IPHC:2018vz].
-In terms of management, the IPHC implements a total allowable catch (TAC) based on a yearly sampling of the Convention area in addition to a series of regulations to control fishing effort [@IPHC:2018vz].
-The TAC is divided between recreational, subsistence and commercial fishery, with a portion set aside for bycatch of other fisheries [@IPHC:2019wt].
-The commercial fishing season starts in March ending around November with restrictions allowing only set line gear with J-type hooks targeting individuals over 81.3 cm of total length [@IPHC:2019wt].
-
-### The Gulf of Maine Arrangement
-
-Since 1998 Canada and the US have used a "Resource Sharing Understanding" to inform the management of Eastern George Bank's Atlantic cod (*Gadus morhua*) and haddock (*Melanogrammus aeglefinus*) and, yellowtail flounder (*Limanda ferruginea*) [@Pudden:2007bo; @TRAC:2016wu; @Song:2017va].
-From 2010 onward, the GoMA suggests catch-limits based on a weighted method where 10% represents the stocks’ historical distribution (from 1967 to 1994) and 90% current distributions produced by quarterly surveys and catch [@TRAC:2016wu].
-Since its introduction, the average quota allocation for each species proposed by the GoMA has been (Table \ref{tab:Table1}); Atlantic cod 77% Canada and 23% US, haddock 55% Canada and 45% US, and yellowtail flounder 34% Canada and 66% US [@TRAC:2015wj; @TRAC:2015vp; @TRAC:2015tt; @TRAC:2018tw; @TRAC:2018tj; @TRAC:2018wx; @Trinko:2019ou].
-However, because this is an unofficial agreement, Canada and the US ultimately take single management decisions [@Soboil:2006gw].
-In terms of management, the US has a multi species harvest control with area and season closures, mesh sizes, effort control, and mobile gear vessels that use bottom otter trawl gear [@Soboil:2006gw].
-In contrast, Canada has a quota system in addition to limited-entry licensing, fleet allocations, and mesh and fish size regulation, among other input controls.
-Canada inshore vessels fish cod with longline and gillnet while haddock is mainly caught with bottom otter trawl gear [@Soboil:2006gw].
-
-```{r Table1, eval = T, echo = F, warning=F, message=F}
-
-table_1 <- read_excel("./Tables/Tables.xlsx") 
-colnames(table_1) <- c("Year","Canada","US","Canada","US","Canada","US")
-
-table_1 %>% 
-  kable("latex",
-        booktabs = T,
-        caption = "Historic quota allocation suggested for Atlantic cod, haddock and yellowtail flounder in the Gulf of Maine "
-  ) %>% 
-  kable_styling(full_width = F,
-                position = "center") %>%
-  add_header_above(c(" ", "Atlantic cod" = 2, "Haddock" = 2, "Yellowtail flounder" = 2)
-  ) %>% 
-  footnote(general = c("* Average from 2006 to 2009, before the implementation of the weighted method",
-                       "' Since the implementation of the weighted method",
-                       "'' Standard deviation of the wiighted average",
-                       "^ TRAC (2015abc)",
-                       "† TRAC (2018abc)",
-                       "‡ Lake (2019)"
-  )
-  )
-
-```
-
-### Projecting future species distributions
-
-We used a Dynamic Bioclimatic Envelope Model (DBEM) to project the distribution of species from 2015 to 2100 under two scenarios of climate change [@Cheung:2010dt; @Cheung:2016jd].
-The DBEM algorithm integrated ecophysiology and habitat suitability with spatial population dynamics of exploited fishes and invertebrates to project shifts in abundance and potential fisheries catches under climate change.
-The algorithm predicted species distribution based on depth and latitudinal range, habitat preferences and an index of species association with major habitat types to estimate changes in abundance distribution over a $0.5^{\circ}$ x $0.5^{\circ}$ grid of the world ocean.
-For each grid cell and time step, the model then calculated species carrying capacity according to sea surface temperature, salinity, oxygen content, sea ice extent (for polar species) and bathymetry, as well as the species preferences to these conditions.
-It then incorporated the intrinsic population growth, settled larvae, and net migration of adults from surrounding cells using an advection-diffusion-reaction equation.
-Finally, the model also simulated the effects of changes in temperature and oxygen content on growth of individuals [@Cheung:2013gk; @Cheung:2016jd].
-Ultimately, the model simulated spatial and temporal population dynamics, and estimated a proxy of maximum sustainable yield (MSY) by applying fishing at MSY level for each grid cell, hereafter referred as maximum catch potential (MCP).
-
-We projected the DBEM using three Earth system models (ESM), the Geophysical Fluid Dynamics Laboratory Earth System Models 2M (GFDL)[^GFDL], the Institute Pierre Simon Laplace Climate Model 5 (IPSL-CM5)[^IPSL], and the Max Planck Institute for Meteorology Earth System Model (MPI)[^MPI].
-Each model was downscaled to match the DBEM $0.5^{\circ}$ x $0.5^{\circ}$ grid using the nearest neighbor method, and in some cases, bilinear interpolation [@Cheung:2016hf].
-Finally, we used the model outputs for two scenarios of the Intergovernmental Panel on Climate Change (IPCC)-Representative Concentration Pathways (RCP) 2.6 and 8.5 representing a low greenhouse gas emission (strong mitigation) and a high greenhouse gas emission (week mitigation) scenario, respectively [@IPCC:2014bz].
-To estimate model robustness and capture the structural uncertainty build within ESM models, we averaged the DBEM results for all three models ($\mu \pm \sigma$) and marked regions where at least one ESM disagree in direction with the rest.
-
-[^GFDL]: Geophysical Fluid Dynamics Laboratory Earth System Models 2M [online] https://www.gfdl.noaa.gov
-[^IPSL]:Institute Pierre Simon Laplace Climate Model 5 [online] https://www.icmc.ipsl.fr
-[^MPI]: Max Planck Institute for Meteorology Earth System Model [online] https://www.mpimet.mpg.de/en/science/models
-
-```{r Data_Loading_For_DBEM, eval = F, echo = F, warning = F ,message = F}
-
-# Species data (Names, treaties, etc)
-# DBEM exploited species list (ONLY ON DROBO)
-exploited_species_list <- fread("/Volumes/DATA/PROJECTION exploited species ENM/exploited_species_list.csv")
-
-# IPHC and GB species
-Selected_Species <- fread(paste(Data_Path,"Species/List_Species.csv",sep=""))
-
-# NAFO Species
-# This is the subset of species Fished on canada and US waters of all NAFO's species list
-NAFO_Species <- read.csv(paste(Data_Path,"Species/NAFO_Species.csv",sep="")) %>%
- mutate(Treaty = "NAFO")
-
-```
-
-```{r DBEM_Data_For_All, eval = F, echo = F, warning = F, message = F}
-
-#-------------------- NOTE --------------------#
-# Chunk to be ran in Hall100 connected to DROBO
-#---------------------------------------------#
-
-All_Species <- exploited_species_list %>% 
- # filter(TaxonName %in% c("Hippoglossus stenolepis","Anoplopoma fimbria")) %>% 
- filter(TaxonName %in% NAFO_Species$TaxonName) %>%
- mutate(Treaty = "NAFO") %>% 
- bind_rows(Selected_Species) %>% 
- filter(! duplicated(TaxonName)) %>% # Removes duplicated
- select(TaxonName,
-     TaxonKey,
-     CommonName,
-     Treaty)
-
-# For suplement Material ####
-# Suplemental_table <- All_Species %>% 
-#  select(-TaxonKey) %>% 
-#  mutate(Treaty = ifelse(TaxonName %in% NAFO_Species$TaxonName,"NAFO",
-#             ifelse(TaxonName %in% c("Hippoglossus stenolepis",
-#                         "Anoplopoma fimbria"),
-#                 "IPHC",
-#                 "PSC")
-#             )
-#  ) %>% 
-#  rename("Scientific name" = TaxonName,
-#     "Common name" = CommonName) 
-# 
-#  write.csv(Suplemental_table,
-#       "Final_Species_List.csv",
-#       row.names = F)
-
-#_____________________________END SUPLEMENTAL TABLE_______________________________#
-
-Models <- c(
- "GFDL26F1",
- "GFDL85F1",
- "IPSL26F1",
- "IPSL85F1",
- "MPI26F1",
- "MPI85F1"
-)
-
-for(m in 1:length(Models)){
- # for(s in 1:2){ #For tensting models
- for(s in 1:nrow(All_Species)){
-
-  # Imports all data once#
-
-  x <-dbem_Import(All_Species[s,2],# Include Treaties information
-          2005,
-          2099,
-          Model = Models[m],
-          Data_Type= "Catch"
-  )
-
-  # } # For testing the dbem_Import function
-
-  ### If statement for abstent species ##
-
-  if(length(x >= 1)){
-
-   # Merging with lat/long ###
-   Spp_Pro <- x %>% 
-    left_join(Coor,
-         by = "INDEX")
-
-   # If statement for those species not found within national EEZ
-   if(nrow(Spp_Pro) <= 1){
-
-    print("No data within Area Selected")
-
-   }else{
-
-    # Include Species Name
-    Spp_Pro$Species <- paste(All_Species[s,1])
-    # Include Treaties information
-    Spp_Pro$Treaty <- paste(All_Species[s,4])
-
-    Spp_Pro_I <- as.data.table(Spp_Pro)
-
-    # Groups all species together in one database
-    if(s == 1){
-     Data_P <- copy(Spp_Pro_I) # <- copies the previouse data.table
-    }else{
-     setkey(Data_P, # <- sets the data.table as "reference" ?setkey
-         Species); setkey(Spp_Pro_I,
-                 Species);
-     list <- list(Data_P, # <- creates a list to merge the tables
-            Spp_Pro_I)
-
-     Data_P <- rbindlist(list, #<- Merges all the data in one single file.
-               use.names = TRUE, # <- This will merge columns by Name
-               fill = TRUE, # <- This allows for the NA's
-               idcol = NULL) # Columns id
-    }
-   }
-  } #if statement for species outside EEZ
- } # Species loop end
-
- #Include wich model the data is from
- Data_P$Model <- paste(Models[m])
-
- # Groups all models together in one database
- if(m == 1){
-  DBEM_Results <- copy(Data_P) # <- copies the previouse data.table
- }else{
-  setkey(DBEM_Results, # <- sets the data.table as "reference" ?setkey
-      Species); setkey(Data_P,
-              Species);
-  list <- list(DBEM_Results, # <- creates a list to merge the tables
-         Data_P)
-
-  DBEM_Results <- rbindlist(list, #<- Merges all the data in one single file.
-               use.names = TRUE, # <- This will merge columns by Name
-               fill = TRUE, # <- This allows for the NA's
-               idcol = NULL) # Columns id
- }
-
-} #End of loops
-
-#### _____________________TEST _____________________ #
-# names(DBEM_Results)
-# unique(DBEM_Results$Model)
-# unique(DBEM_Results$Species)
-# unique(DBEM_Results$Treaty)
-# length(unique(DBEM_Results$Species))
-# head(DBEM_Results)
-
-# Check that each species has 6 per INDEX or less (GFDL x2 + IPSL x2 + MPIS x2)
-
-# DBEM_Results %>%
-#  group_by(Species,INDEX) %>%
-#  summarise(n()) %>%
-#  View()
-
-# DBEM_Results %>% 
-#  filter(Species == "Alosa pseudoharengus",
-#     INDEX == 52809)
-
-# Checked!
-
-# Test that NAFO species are actually NAFO species
-
-# DBEM_Results %>% 
-#  filter(Treaty == "NAFO") %>% 
-#  group_by(Species) %>% 
-#  summarise(n())
-
-# Checked!
-
-### Check for potential repeated cells
-
-# DBEM_Results <- Raw_DBEM_Results %>% 
-#  select(INDEX,Species,Model,everything())
-# 
-# DBEM_Results_Clean <- DBEM_Results[!duplicated(DBEM_Results[1:3]), ]
-
-# Checked!
-
-### Russia distribution check ###
-# In the Far East sea... 
-# 
-# Russia <- EEZIDs_List %>% 
-#  filter(Name == "Russia (Far East)") 
-# 
-# Russia_EEZsID <- EEZIDs_List %>% 
-#  filter(Name %in% Russia$Name) %>% 
-#  left_join(EEZ_CellID,
-#       by = "EEZID")
-# 
-# names(Russia_EEZsID)[3] <- "INDEX"
-# 
-# unique(Russia_EEZsID$Name)
-# 
-# Salmones <- c("Oncorhynchus tshawytscha",
-#        "Oncorhynchus keta",
-#        "Oncorhynchus kisutch",
-#        "Oncorhynchus gorbuscha"
-#        )
-# 
-# DBEM_Results %>% 
-#  filter(INDEX %in% Russia_EEZsID$INDEX) %>%
-#  filter(Longitude > 0 ) %>% 
-#  group_by(INDEX, Longitude, Latitude) %>%
-#  summarise(n =n()) %>%
-#  ggplot(.,
-#     aes(x = Longitude,
-#       y = Latitude,
-#       fill = n
-#     ),
-#     size = 0.05,
-#     alpha = 0.5) +
-#  geom_tile() + 
-#  coord_map(projection = "mercator")
-
-# Looks fine... Just like when you past it the other way...
-
-#### _____________________END TEST _____________________ #
-
-### Save the dataset
-# write.csv(DBEM_Results,
-#      "Raw_Data.csv",
-#      row.names = FALSE)
-
-```
-
-### Estimation of Maximum Catch Potential change
-
-For estimating the percentage change of MCP at the regional scale, we first aggregated the yearly mean MCP of all gridcells per region ($X_{yr}$) and period:
-
-<!-- $$ X_{yr} = \sum_{s = 1}^n \hat{MCP_s}$$ -->
-<!-- <eqn1> -->
-
-\begin{equation}
-\label{eq:one}
-X_{yr} = \sum_{s = 1}^n \hat{MCP_s}
-\end{equation}
-
-where *y* is year, *r* is region, *s* is species, *n* is total number of species, and $\hat{MCP}$ is the MCP averaged by the three ESMs.
-In the case of the GoMA, region was defined as the $0.5^{\circ}$ x $0.5^{\circ}$ grid-cell within the specific NAFO divisional zones.
-For the IPHC analysis, region was defined as the Commission's regulatory areas (Figure \ref{fig:Figure1-map}).
-We then averaged the values in three time periods (*t*) to reduce temporal model sensitivity.
-Thus, we computed the regional percentage change in MCP ($\Delta MCP$) as follows:
-
-<!-- $$\Delta MCP_r = -(1-\frac{X_{t}}{X_{t_0}})*100 $$ -->
-\begin{equation}
-\label{eq:two}
-\Delta MCP_r = -(1-\frac{X_{t}}{X_{t_0}})*100
-\end{equation}
-
-<!-- <eqn2> -->
-
-Where $X_{t}$ is the future average MCP for each of the two time periods analyzed in this study and $t_0$ is the present averaged MCP (<mu> `r Beg_In`-`r Beg_End`).
-Note that in cases where $X_{0}$ = 0 and $X_{t}$ > 0, then ($\Delta MCP$) = 100%, consequently, the opposite case would give a -100% result.
-This way, Equ.
-2 shows the percentage change in MCP by mid $21^{st}$ century when $X_t$ = $\mu$ `r Mid_In`-`r Mid_End`, and end of $21^{st}$ century when $X_t$ = $\mu$ `r End_In`-`r End_End`, relative to today ($t_0$).
-The rationale between choosing these time periods was to provide a relative short-term projection (mid-century) that would be more policy-relevant but also show the long-term trend (end of the century).
-
-<!-- #### Estimation of Changes in Catch Proportion -->
-
-In addition, we borrowed the concept of “threat point” from game theory defined as the minimum payoff that a player is willing to receive in order to cooperate with other players [@Sumaila:2020tp].
-Thus, we estimated the change in the ($\Delta MCP$) (threat point) that each country (players) would have for each species (hereafter referred as stock-share ratio), for both the IPHC and the GoMA.
-The stock-share ratio can be seen as the proportion of the stock’s distribution within the study area that each country has.
-For this, we first modified Equ.
-1, to estimate the aggregated yearly mean MCP of each species per region.
-We then averaged the results by the same previously motioned periods (present, mid and end of the $21^{st}$ century).
-Next, for each species we estimated the stock-share ratio  ($\alpha_s$) that each region had during each time period:
-
-<!-- $$\alpha_{s} = \frac{\theta_{rt}}{\delta_{rt}}$$ -->
-\begin{equation}
-\label{eq:three}
-\alpha_{s} = \frac{\theta_{rt}}{\delta_{rt}}
-\end{equation}
-
-Where $\theta_{rt}$* is the species' aggregated $\hat{MCP}$ of each region at time period *t*, and $\delta_{rt}$ is the species' aggregated $\hat{MCP}$ of the whole specie's distribution within the study area at the same time period.
-Finally, we estimated the percentage change in stock-share ratio substituting $X_{t_0}$ and $X_{t}$ by $\alpha_{t0}$ and $\alpha_t$, respectively in Equation \@ref(eq:two).
-The process was carried out for each ESM and results presented as average $\pm$ standard deviation (sd).
-All of the analysis was done in the statistical software R version 3.5.2 (2018-12-20) with the associated packages, *data.table* [@Packagedatatable:2019uh], *ggrepel* [@PackageggrepelAut:2018to], *gridExtra* [@PackagegridExtraM:2017wx], *knirt* [@PackageknitrAGen:2020wt], *RColorBrewer* [@PackagerColorBrewer:2014uw], *sf* [@PackagesfSimpleF:2018vp], and *tidyverse* [@PackagetidyverseE:2017vq].
-All code is available at http://www.github.com/jepa/OC_Transboundary.
-
-<!-- Finally, we estimated the ($\alpha$) percentage change ($\Delta\alpha$) for each region as follows: -->
-<!-- $$\Delta\alpha = -(-1-\frac{\alpha_{f}}{\alpha_{p}})*100 $$ -->
-<!-- where $\alpha_{f}$ is the future MCP proportion of each region (mid 21^st^ century and end of the 21^st^ century). -->
-
-## Results
-
-```{r Load_Data, echo = F, eval = F, results='hide', warning=F,message=F}
-
-# List of DBEM INDEX within the EEZ
-#Data provided by Vicki Lam
-EEZIDs_List <- read_excel(paste(my_path("G",Extra_Path = "Spatial/DBEM"),"Updated_EEZList_17June2016.xlsx",sep=""))
-
-EEZ_CellID <- read_excel(paste(my_path("G",Extra_Path = "Spatial/DBEM"),"EEZ_CellID.xlsx",sep=""))
-colnames(EEZ_CellID) <- c("EEZID","INDEX")
-
-# DBEM Coordinate system
-Coor <- my_path("G",Extra_Path = "Spatial/DBEM", Name = "Lon_Lat_DBEM.txt", Read = TRUE)
-colnames(Coor) <- c("INDEX","Longitude","Latitude")
-
-# Raw DBEM results
-Raw_DBEM_Results <- my_path("D",Extra_Path = "Ecol/Distribution", Name = "Raw_Data.csv", Read = TRUE)
-
-%>% 
- filter(Species != "Anoplopoma fimbria") #Remove
-
-### Number of stocks per treaty##
-Raw_DBEM_Results %>%
- group_by(Treaty) %>%
- summarise(x= length(unique(Species)))
-
-#### North American EEZs ####
-
-EEZs <- c(
- "Canada (Pacific)",
- "USA (West Coast)",
- "USA (Alaska, Arctic)",
- "USA (Alaska, Subarctic)",
- "Canada (Arctic)",
- "Canada (East Coast)",
- "USA (East Coast)"
-)
-
-All_EEZs <- EEZIDs_List %>% 
- filter(Name %in% EEZs) %>% 
- left_join(EEZ_CellID,
-      by = "EEZID")
-
-names(All_EEZs)[3] <- "INDEX"
-
-# LAT LONG Corrections for Alaska
-
-DBEM_Corrected <- Raw_DBEM_Results %>% 
- filter(INDEX %in% All_EEZs$INDEX) %>% 
- filter(Longitude > 0) %>% 
- mutate(Longitude = Longitude - 360)
-
-DBEM_Corrected <- Raw_DBEM_Results %>% 
- filter(INDEX %in% All_EEZs$INDEX) %>% 
- filter(Longitude < 0) %>% 
- bind_rows(DBEM_Corrected)
-
-#### __________________TEST NA Map _____________________ #
-
-# DBEM_Corrected %>%
-#  group_by(INDEX, Longitude, Latitude) %>%
-#  summarise(n =n()) %>%
-#  ggplot(.,
-#     aes(x = Longitude,
-#       y = Latitude,
-#       fill = n
-#     ),
-#     size = 0.05,
-#     alpha = 0.5) +
-#  geom_tile() #+
-# coord_map(projection = "mercator")
-
-#### __________________All good_____________________________ #
-
-### Get ridd of Pacific Species in the Atlantic
-
-NAFO_E <- DBEM_Corrected %>% 
- filter(Longitude >= -100)
-
-Pacific <- DBEM_Corrected %>% 
- filter(Treaty != "NAFO")
-
-DBEM_Corrected <- NAFO_E %>% 
- bind_rows(Pacific)
-
-# Species on dataset
-# unique(DBEM_Corrected$Species)
-
-# Number of species on dataset
-# length(unique(DBEM_Corrected$Species))
-
-### Get ridd of Atlantic Species in the Pacific
-
-Pacific_Spp <- DBEM_Corrected %>% 
- filter(Longitude <= -100)
-
-Atlantic <- DBEM_Corrected %>% 
- filter(Treaty == "NAFO")
-
-DBEM_Corrected <- Pacific_Spp %>% 
- bind_rows(Atlantic)
-
-###______ Double chack species distributions are correct ###
-
-# DBEM_Corrected %>%
-#  ggplot(.,
-#     aes(
-#      x = Longitude,
-#      y = Latitude,
-#      fill = log(INDEX)
-#     )
-#     ) +
-#  geom_tile() +
-#  facet_wrap(~Treaty+Species)
-
-#### __________________All good_____________________________ #
-
-### Final step for shapefile no need for knitting
-
-DBEM_Coor <- DBEM_Corrected %>%
- group_by(INDEX,Longitude,Latitude) %>%
- summarise(n=n()) %>%
- select(-n,
-     longitude =Longitude,
-     latitude = Latitude)
-
-## Create shapefile for merging with analysis and IPHC shapefile
-
-DBEM_Coor_sf = st_as_sf(DBEM_Coor,
-             coords = c("longitude", "latitude")) %>%
- st_set_crs(4326) %>% # to match shapefiles
- st_transform(4326) # to match shapefiles
-
-#### _____________________TEST _____________________ #
-# head(DBEM_Coor_sf)
-# 
-# ggplot(DBEM_Coor_sf) +
-#  geom_sf() +
-#  geom_sf(data=North_America_Land)
-# 
-#### _______________________________________________ #
-
-```
-
-### Projected change to species managed by the IPHC
-
-At least one third of the IPHC regulatory areas will see a reduction in MCP of Pacific halibut by 2050 relative to current MCP, regardless of the climate change scenario (Figure \ref{fig:Figure2-IPHC}).
-It is likely that the stock shift from the US.
-contiguous states towards Canada will offset the shift of the later towards northern regions, resulting in undetectable changes in Canadian area 2B and Alaskan 2C under both climate change scenarios.
-The potential movement of halibut westward will increase the MCP of regulatory areas 3B (under a low emission scenario) and 4ABCE along the Aleutian Islands and Bering Sea.
-Regions 4DE, the most poleward regulatory areas of the IPHC, are expected to gain MCP by mid (Figure \ref{fig:Figure2-IPHC}) and end of the $21^{st}$ century (Figure \ref{fig:FigureS11}) under a high emission scenario due to the expansion of halibut suitable habitat as sea ice retreats (Figure \ref{fig:FigureS21}).
-In contrast, under a low emission scenario, sea ice is expected to stabilize towards mid 21st century, thus providing less “new” suitable habitat for Pacific halibut and resulting in undetectable changes in MCP for the region (Figure \ref{fig:Figure2-IPHC}B) and decreasing even more towards 2100 (Figure \ref{fig:FigureS11}).
-
-```{r IPHC_Map_Result_Regions, eval = F, echo = F}
-
-Selected_Species <- c("Hippoglossus stenolepis") # Halibut
-
-# Path for saving plots
-Path <- my_path("R",Extra_Path = "IPHC")
-RCP = c("GFDL26F1","IPSL26F1","MPI26F1") #Low RCP
-#### New version
-
-# ------------------ #
-# Estimate IPHC change 
-# ------------------ #
-
-IPHC_MCP_Change <- DBEM_Corrected %>% 
-  filter(Species %in% Selected_Species) %>% 
-  left_join(IPHC_Reg_DBEM_df,
-            by = "INDEX") %>% 
-  filter(!is.na(RegArea)) %>% 
-  mutate(RCP = ifelse(Model %in% RCP,"Low_Emission","High_Emission")) %>% 
-  gather("Year","MCP",Beg_In:End_End) %>% 
-  # Indicate the three period times
-  mutate( 
-    Period = ifelse(Year >= Beg_In & Year <= Beg_End,"Beginning",
-                    ifelse(Year >= Mid_In & Year <= Mid_End,"Mid_Century",
-                           ifelse(Year >= End_In & Year <= End_End,"The_End_Century",
-                                  "Other_Years"))
-    )
-  ) %>% 
-  # Sum of Index per Region
-  group_by(RegArea,Model,RCP,Year,Period) %>% 
-  summarise(Regional_MCP =sum(MCP,na.rm=T)) %>% 
-  # Average pero Time period
-  group_by(RegArea,Model,RCP,Period) %>% 
-  summarise(Mean_T_MCP =mean(Regional_MCP,na.rm=T)) %>%
-  filter(Period != "Other_Years") %>% 
-  spread(Period,Mean_T_MCP) %>% 
-  # Divide future values by present
-  mutate_at(vars(Mid_Century,
-                 The_End_Century),
-            funs(ifelse(Begining > 0, ./Begining,.)) #if no species today value is the future
-  ) %>% 
-  # Estimate percentage change
-  mutate_at(vars(Mid_Century, 
-                 The_End_Century),
-            funs(ifelse(Begining == 0 & . == 0, 0, # If for no change than 0
-                        ifelse(Begining == 0 & . > 0, 100, # If changes from 0 to anything then 100
-                               round(-(1-.)*100) # Estimate percentage change
-                        )
-            )
-            )
-  ) %>% 
-  gather("Period","MCP_Change",Mid_Century,The_End_Century) %>% 
-  mutate(Direction = ifelse(MCP_Change >= 0, "Positive","Negative")) %>% 
-  # Average results per ESMs
-  group_by(RegArea,Period,RCP) %>% 
-  summarise_at(vars(MCP_Change),
-               funs("Mean_ESM_MCP_Chng"=mean,
-                    "sd_ESM_MCP_Chng"=sd,
-                    "N_ESMs"=n(),
-                    "Model_Agreement_Index" = paste(length(unique(Direction)),collapse = ";"),
-                    "Model_Agreement_Direction" = paste(Direction,collapse = ";")
-               )
-  ) %>%
-  mutate(
-    Model_Agreement = ifelse(Model_Agreement_Index == 1, "","*"),
-    Model_Agreement_sd = ifelse(abs(Mean_ESM_MCP_Chng) < sd_ESM_MCP_Chng*2,"No","Yes")
-  ) %>% 
-  ungroup() %>% 
-  # set everything over 100 to 100
-  mutate_at(vars(Mean_ESM_MCP_Chng,
-                 sd_ESM_MCP_Chng),
-            funs(ifelse(. > 100, 100,.)
-            ) 
-  )
-
-# ------------------ #
-# Plot and save figure
-# ------------------ #
-
-# Spatial Step for regional analysis
-
-IPHC_DBEM_sf <- IPHC_Reg %>% 
- left_join(IPHC_MCP_Change,
-      by = "RegArea") %>% 
- st_transform(3832)
-
-# head(IPHC_DBEM_sf)
-
-# Change name so it fits the plot
-IPHC_DBEM_sf$RegArea <- gsub("Closed Area","CA",IPHC_DBEM_sf$RegArea)
-
-# Data to plot
-
-# ------- NOTE ------ # 
-# Change for main figure and S3 figure
-# ---------------------- #
-
-IPHC_DBEM_sf <- IPHC_DBEM_sf %>% 
- # filter(Period == "Mid_Century") %>% # Paper figure
- filter(Period == "The_End_Century") %>%# Supplemental figure
- mutate(RegArea = paste(RegArea,Model_Agreement,sep=""))
-
-# North America shapefile
-North_America_Land <- North_America_Land %>% 
- st_transform(crs = 3832)
-
-# Limit Axis
-Seq <- seq(-50,50,by=5)
-
-# Plot it!
-P1 <- ggplot() +
-  geom_sf(data = North_America_Land, colour = "lightgrey") + # Land Map of North America
-  geom_sf(data = subset(IPHC_DBEM_sf, Country == "United States"), # DBEM Of the US
-          aes(fill = Mean_ESM_MCP_Chng)
-  ) +
-  geom_sf(data = subset(IPHC_DBEM_sf, RegArea == "2B*"), # DBEM of Canada
-          aes(fill = Mean_ESM_MCP_Chng)
-  ) +
-  geom_sf_label(data = IPHC_DBEM_sf, # RegAreas labels
-                aes(
-                  label = RegArea,
-                  fill = Mean_ESM_MCP_Chng
-                ),
-                colour = "black"
-  ) +
-  geom_label(data=IPHC_DBEM_sf, aes(label = RCP, x =4080637 , y = 4551701, colour = RCP), #RCP labels for grid plot
-             show.legend = FALSE,
-             size = 10
-  ) +
-  facet_wrap(~RCP, # For grid plot, comment in one plot each
-             ncol = 2) +
-  # scale_colour_manual(values=c("blue", "red")) + #Labels colors for grid plot
-  scale_fill_gradient2("",
-                       limits=c(-50,50),
-                       breaks = Seq) +
-  my_ggtheme_m()() +
-  theme(
-    legend.key = element_rect(size = 4),
-    legend.key.width =unit(8,"line"),
-    legend.text = element_text(size = 16),
-    strip.text.x = element_blank()
-  ) +
-  coord_sf(xlim = c(1963800, 10041910), # Subsets North America map
-           ylim = c(3651701,9728813)
-  ) +
-  annotate("text", label = "Alaska", x = 6280637, y = 9228813, size = 6, colour = "black") +
-  annotate("text", label = "Canada", x = 9629910, y = 9228813, size = 6, colour = "black") +
-  annotate("text", label = "US Contiguous\n States", x =10000000, y = 5151701, size = 6, colour = "black", angle = -90)
-
-# Save plot 
-# Name = paste("New_IPHC_Reg_26_85_2050.png")
-Name = paste("New_IPHC_Reg_26_85_2100.png")
-
-ggsave(Name,
-    plot = P1,
-    width = 15,
-    height = 10,
-    units = "in",
-    path = Path)
-
-```
-
-```{r Figure2-IPHC, eval = T, echo = F, fig.cap= "Percentage change of MCP for species managed by the IPHC for mid 21st century (2041-2060) relative to present 2005-2014 under a A) high emission scenario and B) low emission scenario.
-Labels marked with * represent regions where models do not agree in direction of change."}
-
-Fig2 <- readPNG(paste(my_path("F"),"Figure 2.png",sep=""))
-grid.raster(Fig2)
-
-```
-
-<!-- If rendered to word use ![](), otherwise use chunk -->
-
-<!-- ![Fig.
-2.
-Percentage change of MCP for species managed by the IPHC for mid 21st century (2041-2060) relative to present 2005-2014 under a A) high emission scenario and B) low emission scenario.
-Labels marked with "*" represent regions where models do not agree in direction of change.](./Figures/Figure 3.png) -->
-
-The same poleward trend is expected in the change of Pacific halibut stock-share ratio with the average proportion increasing up to 25% in some northern regions and decreasing by 10% in southern regions, relative to the present proportion (Figure \ref{fig:Figure3-IPHC-prop}).
-Maintaining emissions to lower levels through 2050 would potentially leave unchanged the stock-share ratio of three regulatory areas (3AC, and 4D) and negatively change regulatory area 2A.
-On the other hand, failing to achieve such target will decrease the stock-share ratio in the most productive regulatory areas (2AC, 3AB).
-
-```{r IPHC_Proportion_Regions, eval = F, echo = F, message=F, warning=F}
-
-# Set saving path
-Path <- my_path("R",Extra_Path = "IPHC/Proportion")
-IPHC_Species <- c("Hippoglossus stenolepis") # Halibut
-
-#### FIlter EEZs ###
-
-EEZs <- c(
- "Canada (Pacific)",
- "USA (West Coast)",
- "USA (Alaska, Arctic)",
- "USA (Alaska, Subarctic)"
-)
-
-RCP <- c("GFDL26F1","IPSL26F1","MPI26F1")
-
-EEZsID <- EEZIDs_List %>% 
- filter(Name %in%EEZs) %>% 
- left_join(EEZ_CellID,
-      by = "EEZID")
-
-names(EEZsID)[3] <- "INDEX"
-
-# ------------------------- #
-# Changes in proportion 
-# referent to (2005-2014)
-# ------------------------- #
-
-# Estimate IPHC total values
-
-IPHC_Absolutes <- DBEM_Corrected %>%
-  mutate(RCP = ifelse(Model %in% c("GFDL26F1","IPSL26F1","MPI26F1"),"Low Emission","High Emission")) %>% # Assigns RCP by model
-  filter(Species %in% IPHC_Species,
-         INDEX %in% IPHC_Reg_DBEM_df$INDEX) %>% #Selects only IPHC species within regulatory areas
-  left_join(IPHC_Reg_DBEM_df,
-            by = "INDEX") %>% # Include Regulatory areas
-  gather("Year","MCP",`2005`:`2099`) %>% 
-  group_by(RCP,RegArea,Year,Model) %>%
-  summarise(MCP = sum(MCP, na.rm = T))
-
-# Estimate total MCP of each RCP per year
-Proportion_Total <- IPHC_Absolutes %>% 
-  group_by(RCP,Year,Model) %>% 
-  summarise(Total = sum(MCP))
-
-# Estimates the proportion of each RegArea catch pero RCP and Year
-Proportion_Data <- IPHC_Absolutes %>% 
-  left_join(Proportion_Total,
-            by = c("RCP","Year","Model")) %>% 
-  mutate(Proportion = (MCP/Total)*100)
-
-# Proportion change in the future (NOTE: not plotting by timeframe because of boxplot)
-Proportion_Change <- Proportion_Data %>% 
-  mutate(Time_Step = ifelse(Year <= Beg_End, "Beginning_Prop",
-                            ifelse(Year >= Mid_In & Year <= Mid_End,"Mid_Century_Prop",
-                                   ifelse(Year >= End_In,"The_End_Century_Prop","Others")
-                            )
-  ),
-  Nation = ifelse(RegArea == "2A","US Contiguous",
-                  ifelse(RegArea == "2B","Canada","Alaska")
-  )
-  ) %>% 
-  # Get mean proportion by timeframe
-  group_by(RCP,
-           RegArea,
-           Model,
-           Time_Step) %>% 
-  summarise(Mean_Temp_Prop = mean(Proportion)) %>% 
-  spread(Time_Step,Mean_Temp_Prop) %>% 
-  # Divide future values by present
-  mutate_at(vars(Mid_Century_Prop, 
-                 The_End_Century_Prop),
-            funs(ifelse(Begining_Prop > 0, ./Begining_Prop,.)) #if no species today value is the future
-  ) %>% 
-  # Estimate percentage change
-  mutate_at(vars(Mid_Century_Prop, 
-                 The_End_Century_Prop),
-            funs(ifelse(Begining_Prop == 0 & . == 0, 0, # If for no change than 0
-                        ifelse(Begining_Prop == 0 & . > 0, 100, # If changes from 0 to anything then 100
-                               round(-(1-.)*100) # Estimate percentage change
-                        )
-            )
-            )
-  ) %>%
-  gather("Time_Step","Prop_Change",Mid_Century_Prop,The_End_Century_Prop) %>% 
-  # Average results per ESMs
-  group_by(RegArea,Time_Step,RCP) %>% 
-  summarise_at(vars(Prop_Change),
-               funs("Mean_ESM_MCP_Chng"=mean,
-                    "sd_ESM_MCP_Chng"=sd,
-                    "N_ESMs"=n()
-               )
-  ) %>% 
-  mutate(Order = as.character(RegArea),
-         Nation = ifelse(RegArea == "2A","US Contiguous",
-                         ifelse(RegArea == "2B","Canada","Alaska")
-         )
-  )
-
-Proportion_Change$RegArea <- gsub("2B","2B",Proportion_Change$RegArea)
-
-# Plot and save figure
-ggplot(data = subset(Proportion_Change, Time_Step == "Mid_Century_Prop"),
-       aes(
-         x = reorder(RegArea,Order), # from forcasts` package
-         y = Mean_ESM_MCP_Chng,
-         fill = Nation,
-         colour = Nation
-       )
-) +
-  geom_bar(stat = "identity") +
-  geom_errorbar(data = subset(Proportion_Change, Time_Step == "Mid_Century_Prop"),
-                aes(
-                  x = reorder(RegArea,Order),
-                  ymin=Mean_ESM_MCP_Chng-sd_ESM_MCP_Chng, # mean +- sd
-                  ymax=Mean_ESM_MCP_Chng+sd_ESM_MCP_Chng,
-                  colour=Nation,
-                ),
-                width=.2,
-                linetype = 2,
-                size = 0.6,
-                alpha = 0.5
-  ) +
-  coord_flip() +
-  ylab("") +
-  geom_hline(yintercept = 0, linetype = "dashed") +
-  my_ggtheme_p()() +
-  scale_fill_brewer("Region",palette = "Set2") +
-  scale_colour_brewer("Region",palette = "Set2") +
-  scale_y_continuous(breaks = seq(-40,40,20),
-                     limits = c(-40,40)
-  )+
-  facet_wrap(~RCP,
-             nrow = 1) +
-  labs(
-    x = "",
-    y = "Stock Share Ratio Change (%)"
-  ) +
-  ggsave("Proportion_gom_Mid.png",
-         plot = .,
-         width = 8,
-         height =8,
-         units = "in",
-         path = Path
-  )
-
-```
-
-```{r Figure3-IPHC-prop, eval = T, echo = F, fig.cap="Percentage change of stock-share ratio for IPHC under A) high emission scenario and B) low emission scenario for mid 21st century (2041-2060) relative to present 2005-2014.
-Values represent the mean of 3 ESM; error bars represent \u00B1 sd."}
-
-Fig3 <- readPNG(paste(my_path("F"),"Figure 3.png",sep=""))
-grid.raster(Fig3)
-
-```
-
-<!-- If rendered to word use ![](), otherwise use chunk -->
-
-<!-- ![Fig.
-3.
-Percentage change of stock-share ratio for IPHC under A) high emission scenario and B) low emission scenario for mid 21st century (2041-2060) relative to present 2005-2014.
-Values represent the mean of 3 ESM; error bars represent $\pm$ sd.](./Figures/Figure 4.png) -->
-
-### Projected change to species managed under the Gulf of Maine arrangement
-
-While some regulatory areas of the IPHC will see an incremental increase in Pacific halibut MCP, the results for the Gulf of Maine show an overall decrease in MCP by 2050, regardless of the climate change scenario or ESM (Figure \ref{fig:Figure4-GOMA}), intensifying by the end of the $21^{st}$ century (Figure \ref{fig:FigureS12}).
-For cod and haddock, MCP will decrease within the whole Gulf with no apparent win for any country in reference to the current period (Figure \ref{fig:Figure4-GOMA}).
-For yellowtail flounder, despite an overall reduction, some discrete areas are expected to increase with no particular pattern and high uncertainty, as ESMs in these regions do not agree in the direction of change (Figure \ref{fig:FigureS23}).
-Despite the overall reduction in MCP for all three species in comparison to current values, there is a benefit of achieving a low emission scenario as reductions intensify under the high emission scenario.
-
-```{r GB_Results_Spp, eval = F, echo = F, fig.width=12}
-
-#### Filter Species ####
-Atlantic_Species <- c(
-  "Gadus morhua", # Cod
-  "Limanda ferruginea", # Yellowtail flounder
-  "Melanogrammus aeglefinus" # Haddock
-)
-
-# Run Spatial chuck for the Atlantic
-# NAFO_5z$geometry
-
-# Filter DBEM results for three specific species within the region of the GoM
-N_Lim <- 45.9759
-S_Lim <- 41
-W_Lim <- -72.0592
-E_Lim <- -63.33333
-
-# Limit the area to GoM species
-Atlantic_DBEM <- Raw_DBEM_Results %>% 
-  filter(Species %in% Atlantic_Species) %>% 
-  filter( 
-    Latitude < N_Lim, # North
-    Latitude > S_Lim, # South 
-    Longitude > W_Lim, # West
-    Longitude < E_Lim
-  )
-
-# Path for saving plots
-Path <- my_path("R",Extra_Path = "GoM")
-
-# -------------------- #
-### MCP Change Analysis
-# -------------------- #
-
-Mean_Data_GoM <- Atlantic_DBEM %>% 
-  mutate(RCP = ifelse(Model %in% c("GFDL26F1","IPSL26F1","MPI26F1"),"Low Emission","High Emission")) %>%
-  tidyr::gather("Year","Change",`2005`:`2099`) %>%
-  mutate(Change = replace_na(Change, 0)) %>% # Convert NA's into 0's
-  # Indicate the three period times
-  mutate(
-    Period = ifelse(Year >= Beg_In & Year <= Beg_End,"Beginning",
-                    ifelse(Year >= Mid_In & Year <= Mid_End,"Mid_Century",
-                           ifelse(Year >= End_In & Year <= End_End,"The_End_Century",
-                                  "Other_Years"))
-    )
-  ) %>% 
-  filter(Period != "Other_Years") %>% # Remove unwanted years
-  # Temporal mean
-  group_by(INDEX,Model,RCP,Period,Species) %>%
-  summarise(
-    Mean_Temp = mean(Change, na.rm = T) 
-  ) %>% 
-  spread(Period,Mean_Temp) %>%
-  # Divide future values by present
-  mutate_at(vars(Mid_Century, 
-                 The_End_Century),
-            funs(ifelse(Begining > 0, ./Begining,.)) # if no species today value is the future
-  ) %>% 
-  # Estimate percentage change
-  mutate_at(vars(Mid_Century, 
-                 The_End_Century),
-            funs(ifelse(Begining == 0 & . == 0, 0, # If for no change than 0
-                        ifelse(Begining == 0 & . > 0, 100, # If changes from 0 to anything then 100
-                               round(-(1-.)*100) # Estimate percentage change
-                        )
-            )
-            )
-  ) %>% 
-  gather("Period","MCP_Chng",Mid_Century,The_End_Century) %>% 
-  mutate(Direction = ifelse(MCP_Chng >= 0, "Positive","Negative")) %>% 
-  %>% # Average results per ESMs
-  group_by(INDEX,Species,Period,RCP) 
-summarise_at(vars(MCP_Chng),
-             funs("Mean_ESM_MCP_Chng"=mean,
-                  "sd_ESM_MCP_Chng"=sd,
-                  "N_ESMs"=n(),
-                  "Model_Agreement" = paste(length(unique(Direction)),collapse = ";")
-             )
-) %>%
-  mutate(
-    Model_Agreement = ifelse(Model_Agreement == 1, "Agree","Disagree")
-  ) %>% 
-  # set everything over 100 to 100
-  mutate_at(vars(Mean_ESM_MCP_Chng,
-                 sd_ESM_MCP_Chng),
-            funs(ifelse(. > 100, 100,.)
-            ) 
-  ) %>% 
-  left_join(GB_Coor,
-            by ="INDEX")
-
- # Set Bins for better plotting
- Mean_Data_GoM$Bins <- cut(Mean_Data_GoM$Mean_ESM_MCP_Chng,breaks = 4)
- # unique(New_Mean_Data_GoM$Bins)
-
-# -------------------- #
-# Plotting results
-# -------------------- #
-Seq <- seq(-100,100,10)
-
-Lim_Neg <- min(Seq)
-Lim_Max <- max(Seq)
-
-# Use bins and collors yellow orange light red and dark red
-
-# Mean_Data_GoM <- Mean_Data_GoM %>% # In case you want filter a specific species
-#  filter(Species == "Limanda ferruginea",
-#     Mean_ESM_MCP_Chng >= 0)
-
-pgm <- ggplot(Mean_Data_GoM) +
-  geom_tile(data = subset(Mean_Data_GoM, Period == "Mid_Century"),
-            aes(
-              x = Longitude,
-              y = Latitude,
-              color = Mean_ESM_MCP_Chng,
-              fill = Mean_ESM_MCP_Chng
-            )
-  ) +
-  geom_point(data = subset(Mean_Data_GoM, Period == "Mid_Century" & Model_Agreement == "Disagree"),
-             aes(
-               x = Longitude,
-               y = Latitude
-             ),
-             size = 1,
-             # alpha = 0.3,
-             shape = 16,
-             color = "grey20"
-  ) +
-  scale_fill_gradient2(paste("MCP Percentage Change \n",Mid_In,"-",Mid_End,")"), # If not using the bins
-                       limits=c(Lim_Neg,
-                                Lim_Max),
-                       breaks = Seq,
-                       na.value = 'darkred' # NA values are present when the species is no more 
-  ) +
-  scale_colour_gradient2(paste("MCP Percentage Change \n",Mid_In,"-",Mid_End,")"),
-                         limits=c(Lim_Neg,
-                                  Lim_Max),
-                         breaks = Seq,
-                         na.value = 'darkred' # NA values are present when the species is no more
-  ) +
-  geom_sf(data = GM_Land, colour = "lightgrey") +
-  geom_sf(data = eez_GM, fill = NA) +
-  coord_sf(xlim = c(-71.0592, -63.33333),
-           ylim = c(41,45.5)
-  ) +
-  annotate("text", label = "United States", x = -70, y = 45, size = 4, colour = "black") +
-  annotate("text", label = "Canada", x = -66.8, y = 45.4, size = 4, colour = "black") +
-  annotate("text", label = "Canada", x = -65.4, y = 44.2, size = 4, colour = "black") +
-  my_ggtheme_m()() +
-  theme(
-    axis.line = element_line(colour = "black", size = .5),
-    axis.ticks = element_line(size = .5),
-    axis.text.x = element_text(size = 12,
-                               angle = 0,
-                               face = "plain"),
-    axis.text.y = element_text(size = 12),
-    legend.key = element_rect(size = 3),
-    legend.key.width =unit(8,"line"),
-    legend.title = element_text(size = 20),
-    legend.text = element_text(size = 18)
-  ) +
-  facet_wrap(~RCP + Species, 
-             ncol = 3
-  )
-
-# Name and save
-Name = paste("Change_GB_26_85_Mid.png",sep="_")
-
-ggsave(Name,
-    plot = pgm,
-    width = 20,
-    height = 10,
-    units = "in",
-    path = Path)
-
-```
-
-```{r Figure4-GOMA, eval = T, echo = F, fig.cap= "Percentage change of MCP in the Gulf of Maine under, A) high emission scenario; and B) low emission for mid-century (2041-2060) relative to present (2005-2014).
-Points represent regions where models do not agree in direction of change."}
-
-Fig4 <- readPNG(paste(my_path("F"),"Figure 4.png",sep=""))
-grid.raster(Fig4)
-
-```
-
-<!-- ![Fig.
-4.
-Percentage change of MCP in the Gulf of Maine under, A) high emission scenario; and B) low emission for mid-century (2041-2060) relative to present (2005-2014).
-Points represent regions where models do not agree in direction of change.](./Figures/Figure 5.png) -->
-
-Despite the expected decrease in MCP for the region, changes in the stock-share ratio of species within the Gulf of Maine show different outcomes dependent on the climate change scenario and species in question.
-Following a high emission path will affect mostly Canada’s share of yellowtail flounder and in less degree haddock, with an increase of cod share.
-under the low emission scenario, haddock and cod patterns intensify, while yellowtail flounder’s share approaches almost no change (Figure \ref{fig:Figure5-GOMA-prop}).
-Such pattern is likely the combination of the bathymetry or the Gulf, the warming gradient, and the species distribution (see Discussion).
-
-```{r GB_Proportion_Species, eval = F, echo = F}
-
-### Analysis by Species ####
-Path <- my_path("R", Extra_Path = "GoM")
-
-# names(DBEM_Results)
-
-Atlantic_Species <- c(
-  "Gadus morhua", # Cod
-  "Limanda ferruginea", # Yellowtail flounder
-  "Melanogrammus aeglefinus" # haddock 
-)
-
-N_Lim <- 45.9759
-S_Lim <- 41
-W_Lim <- -72.0592
-E_Lim <- -63.33333
-
-# Run Spatial chuck for the Atlantic
-
-Atlantic_DBEM <- Raw_DBEM_Results %>% 
-  filter(Species %in% Atlantic_Species) %>% 
-  filter( # Limit the area to George's bank
-    Latitude < N_Lim, # North
-    Latitude > S_Lim, # South 
-    Longitude > W_Lim, # West
-    Longitude < E_Lim
-  )
-
-EEZs <- c(
-  "Canada (East Coast)",
-  "USA (East Coast)"
-)
-
-RCP = c("GFDL26F1","IPSL26F1","MPI26F1")
-
-EEZsID <- EEZIDs_List %>% 
-  filter(Name %in%EEZs) %>% 
-  left_join(EEZ_CellID,
-            by = "EEZID")
-
-names(EEZsID)[3] <- "INDEX"
-
-GB_Coor <- Coor %>% 
-  filter(INDEX %in% EEZsID$INDEX) %>% 
-  # mutate(one = 1) %>% 
-  filter( # Limit the area to George's bank
-    Latitude < N_Lim, # North
-    Latitude > S_Lim, # South 
-    Longitude > -71, # West
-    Longitude < E_Lim
-  )
-
-# ---------------------------- #
-# Estimate GoM proportion change 
-# ---------------------------- #
-
-GoM_Absolutes <- Atlantic_DBEM %>% 
-  mutate(RCP = ifelse(Model %in% c("GFDL26F1","IPSL26F1","MPI26F1"),"Low Emission","High Emission")) %>% # Assigns RCP by model
-  filter(Species %in% Atlantic_Species,
-         INDEX %in% GB_Coor$INDEX) %>% #Selects only GoM species within regulatory areas
-  left_join(EEZsID,
-            by = "INDEX") %>% 
-  gather("Year","MCP",`2005`:`2099`) %>% 
-  group_by(Species,RCP,Name,Year,Model) %>%
-  summarise(MCP = sum(MCP, na.rm = T))
-
-# Estimate total MCP of each RCP per year
-Proportion_Total <- GoM_Absolutes %>% 
- group_by(Species,RCP,Year,Model) %>% 
- summarise(Total = sum(MCP))
-
-# Estimates Proportion cahnge in each region and species
-Proportion_Change_GoM <- GoM_Absolutes %>% 
-  left_join(Proportion_Total,
-            by = c("RCP","Year","Model","Species")) %>% 
-  mutate(Proportion = (MCP/Total)*100) %>% 
-  mutate(Time_Step = ifelse(Year <= Beg_End, "Beginning_Prop",
-                            ifelse(Year >= Mid_In & Year <= Mid_End,"Mid_Century_Prop",
-                                   ifelse(Year >= End_In,"The_End_Century_Prop","Others")
-                            )
-  )
-  ) %>% 
-  # Temporal mean
-  group_by(Species, RCP, Name, Model, Time_Step) %>% 
-  summarise(Mean_Temp_Prop = mean(Proportion)) %>% 
-  spread(Time_Step,Mean_Temp_Prop) %>% 
-  mutate_at(vars(Mid_Century_Prop, # Divide future values by present
-                 The_End_Century_Prop),
-            funs(ifelse(Begining_Prop > 0, ./Begining_Prop,.)) #if no species today value is the future
-  ) %>% 
-  # Estimate percentage change
-  mutate_at(vars(Mid_Century_Prop, 
-                 The_End_Century_Prop),
-            funs(ifelse(Begining_Prop == 0 & . == 0, 0, # If for no change than 0
-                        ifelse(Begining_Prop == 0 & . > 0, 100, # If changes from 0 to anything then 100
-                               round(-(1-.)*100) # Estimate percentage change
-                        )
-            )
-            )
-  ) %>%
-  gather("Time_Step","Prop_Change",Mid_Century_Prop,The_End_Century_Prop) %>% 
-  # Average results per ESMs
-  group_by(Species,Name,Time_Step,RCP) %>%
-  summarise_at(vars(Prop_Change),
-               funs("Mean_ESM_MCP_Chng"=mean,
-                    "sd_ESM_MCP_Chng"=sd,
-                    "N_ESMs"=n()
-               )
-  ) %>% 
-  mutate(
-    Order = ifelse(Species== "Gadus morhua", 2,
-                   ifelse( Species == "Melanogrammus aeglefinus",1,3))
-  )
-
-# ------------------- #
-# Create and save plot 
-# ------------------- #
-
-# The plot
-ggplot(data = subset(Proportion_Change_GoM, Time_Step == "Mid_Century_Prop"),
-       aes(
-         x = reorder(Species,Order),
-         # x = Species
-         y = Mean_ESM_MCP_Chng,
-         fill = Name,
-         colour = Name
-       )
-) +
-  geom_bar(stat = "identity") +
-  geom_errorbar(data = subset(Proportion_Change_GoM, Time_Step == "Mid_Century_Prop"),
-                aes(
-                  x = reorder(Species,Order),
-                  # x = Species,
-                  ymin=Mean_ESM_MCP_Chng-sd_ESM_MCP_Chng, # mean +- sd
-                  ymax=Mean_ESM_MCP_Chng+sd_ESM_MCP_Chng,
-                  colour=Name,
-                ),
-                width=.2,
-                linetype = 2,
-                size = 0.6,
-                alpha = 0.5
-  ) +
-  scale_y_continuous(breaks = seq(-15,15,5),
-                     limits = c(-15,15)
-  )+
-  xlab ("") +
-  geom_hline(yintercept = 0, linetype = "dashed") +
-  my_ggtheme_p() + 
-  scale_fill_brewer("Region",palette = "Set2") +
-  scale_colour_brewer("Region",palette = "Set2") +
-  facet_wrap(~RCP,
-             nrow = 1) +
-  labs(
-    x = "",
-    y = "Stock Share Ratio Change (%)"
-  ) +
-  theme(legend.position = c(0.3, 1),
-        legend.direction = "horizontal",
-        strip.text.x = element_blank(),
-        axis.text.x = element_text(size = 12,
-                                   # angle = 0,
-                                   face = "italic",
-                                   # hjust = 0
-        )
-  ) + 
-  ggsave("GoM_Proportion_Mid.png",
-    plot = .,
-    width = 12,
-    height = 6,
-    units = "in",
-    path = Path
-    )
-
-```
-
-```{r Figure5-GOMA-prop, eval = T, echo = F, fig.cap="Changes in MCP stock-share ratio for Gulf of Maine under (A) high emission; and (B) low emission scenarios for mid 21st century (2041-2060) relative to present (2005-2014).
-Values represent the mean of 3 ESM; error bars represent \u00B1 sd."}
-
-Fig5 <- readPNG(paste(my_path("F"),"Figure 5.png",sep=""))
-grid.raster(Fig5)
-
-```
-
-<!-- ![Fig.
-5.
-Changes in MCP stock-share ratio for Gulf of Maine under (A) high emission; and (B) low emission scenarios for mid 21st century (2041-2060) relative to present (2005-2014).
-Values represent the mean of 3 ESM; error bars represent $\pm$ sd.](./Figures/Figure 6.gif) -->
-
-## Discussion
-
-```{r, iphc_distr, eval = F, echo = F}
-
-library("tidyverse")
-
-iphc_2019_tsd_005 <- read_excel("/Volumes/HALL2000/Data/OC_Transboundary/iphc-2019-tsd-005.xlsx")
-
-iphc_2019_tsd_005 %>% 
-  gather("Region","Prop",-Year) %>% 
-  # filter(Year >= 2010) %>% 
-  # group_by(Region) %>% 
-  # summarise(me=mean(Prop)) %>% 
-  ggplot() +
-  # geom_bar(
-  #   aes(
-  #     x = Region,
-  #     y = me,
-  #     color = Region
-  #   ),
-  #   stat="identity"
-  # )
-  geom_line(
-    aes(
-      x = Year,
-      y = Prop,
-      color = Region
-    )
-  )
-
-```
-
-The results of the present study suggest that climate change will alter the MCP of jointly managed transboundary fish stocks in North America consequently altering Canada’s and the US’s species’ stock-share ratio, regardless of the climate change scenario.
-These results are aligned with regional [@Morley:2018fn] projections suggesting that climate change will push marine species towards the poles and deeper water [@Pinsky:2013ab] in search of their ecological niche [@Poloczanska:2016kk].
-Moreover, IPHC data[^IPHC] suggest that some of these shits are already happening.
-For example, since 2010, the distribution proportion of Pacific halibut has increased from 9% to 11% in region 2B, from 7.5% to 13% in region 2C, and from 12.3% to 13.5% in region 4CDE.
-On the other hand, regions 3A and 3B have seen the largest decreases in the IPHC regulatory areas since 2010, from 35.3% to 30.6% and 20.6% to 15.9%, respectively.
-Similarly, in the Gulf of Maine, the projected stock-share gain of yellowtail flounder and haddock by the US (Figure \ref{fig:Figure5-GOMA-prop}) follows a historical trend where in 2019, Canada's stock-share decreased from 35% to 32% and 60% to 40% relative to 2010, respectively [@Trinko:2019ou].
-
-[^IPHC]: See IPHC Time Series Datasets, Modelled FISS Stock Distribution Estimates [internet] https://www.iphc.int/data/time-series-datasets
-
-Geographic barriers [@Cheung:2015fm; @Kleisner:2016je], local temperature gradients [@Pinsky:2013ab], species interactions and human activities [@Serpetti:2017he] might change the rate and direction of species shifts.
-For the IPHC, geographic barriers might induce a westward increase of stock-share in IPHC regions where species can only migrate northward into the Arctic Ocean through the Bering Sea and Bering Strait [@Cheung:2015fm] (Figure \ref{fig:Figure3-IPHC-prop}).
-In the Gulf of Maine, future projections could be a response to a temperature gradient shift combined with geographic barriers as southern waters are deeper and warming slower than northern waters according to the ESMs (Figure \ref{fig:FigureS22}).
-Moreover, Maine has seen its landings of yellowtail flounder increased at the expenses of southern states [@Pinsky:2012kq].
-This could be influencing the US gain in MCP in the GoMA in relation to Canada as species shift their distribution from lower latitudes naturally reaching the US (lower) region first.
-As the effects of climate change endure, even with high mitigation, joint plans should prepare to face changes in the stock-share ratio of transboundary stocks along both coast of North America.
-
-The shifts in the distribution of transboundary stocks can jeopardize management objectives such as conservation measures and gear operation.
-Fish moving out of fishing grounds and into protected areas could result in a pressure increase to open such area to fishing.
-Moreover, overlapping shifting stocks could interfere in gear-limitation management rules of multiple fisheries generating conflicts between fleets [@VanDerVoo:2016uc].
-The effectiveness of the IPHC-Closed Area ("CA" in Figure \ref{fig:Figure2-IPHC}) in terms of protecting juveniles has been historically questioned as trawling for other species is still allowed in the area [@Karim:2010ut; @IPHC:2017CA].
-In 2015, for example, 97% of the trawl by-catch in areas 4CDE and the Closed Area were juveniles [@IPHC:2017CA].
-Consequently, the Alaskan trawl fisheries has been closed before reaching annual quota due to the attainment of Pacific halibut bycatch quota limits [@Karim:2010ut].
-Thus, the commission has been asked to open the closed area for Pacific halibut fishing, under the premise that the expansion of the trawl fishery is likely reducing any conservation goal for juvenile Pacific halibut [@IPHC:2017CA].
-Although not assessed in this study, some trawling target species like Pacific cod (*Gadus macrocephalus*), flathead sole (*Hippoglossoides elassodon*), and Alaskan plaice (*Pleuronectes quadrituberculatus*) have already shift their distributions due to warming waters [@Stram:2009xc] and some are expected to continue shifting in similar direction than Pacific halibut [@Pinsky:2013ab].
-The overlap of target species could be addressed by applying ecosystem-based management and dynamic management tools [@Hazen:2018fa] to manage these fisheries and reduce potential loss of sustainable harvest for both the halibut and the trawl fisheries.
-
-Quota allocation ruled by historic distributions will most likely be outdated incentivizing maladaptation [@FAO:2018uv; @Gaines:2018sg; @Miller:2013iv].
-In Europe, for example, the EU Common Fisheries Policy quota allocation is based on historic reference period of the 70's [@Harte:2019us].
-However, climate change has shifted the distribution of multiple European commercial stocks [@Baudron:2020dj], outdating the fixed quotas and thus compromising the sustainability of European fisheries [@FAO:2018uv; @Baudron:2020dj].
-Management regimes that include a dynamic harvest control (e.g.
-adjusting the quota based on the stocks distribution) have the potential of increasing fish biomass, harvest and profits under climate change [@Gaines:2018sg].
-In North America, poleward shifts of Pacific halibut along the coast of Oregon, Washington and British Columbia have been previously addressed by the IPHC resulting in the adoption of a dynamic quota allocation method [@McCaughran:1992uw].
-By allocating quotas based on yearly surveys along the Convention area, the IPHC should be able to capture shifts in Pacific halibut distribution due to climate change, reducing the chances of over exploitation of the stock due to this shifts [@Miller:2013iv].
-Similarly, for the Gulf of Maine, since the GoMA’s method to estimate quota allocation is weighted based on stocks distribution (90%) and historical catch (10%) [@TRAC:2016wu].
-This process is especially important for cod and haddock due to their distribution variation within the Gulf [@Soboil:2006gw; @TRAC:2016wu].
-However, since 2010, when the weighted method was implemented, the quota allocation has favored the US over Canada, especially in terms of haddock and yellowtail flounder [@Trinko:2019ou].
-A perpetuation of this trend with no mitigation policy could jeopardize the arrangement as Canada's quota reduction could disincentive cooperation [@Sumaila:2020tp].
-
-Side payments have been previously used to address changes in species distribution, including cases caused by environmental forcings.
-In game theory, a side payment is received by a player as a compensation from the other player in a shared resource agreement, with the premise that cooperation will result in a better overall outcome [@Bjorndal:2012vd; @Sumaila:2013hv].
-Side payments do not have to be in monetary form and are widely used in transboundary stocks around the world.
-For example, Norway and Russia have implemented a quota swap strategy for jointly managed stocks of cod, haddock and capelin (*Mallotus villosus*) in the Barents Sea [@FAO:2020vw].
-Similarly, species' quota swaps are allowed, up to a degree, within regulatory areas of the European union [@Baudron:2020dj].
-Specifically, for northern European spring spawning herring (*Clupea harengus*), Norway, Iceland, Faroe Islands, Russia and the EU reached an agreement to manage the stock after its collapsed, partially due to climate variations [@Miller:2013iv].
-Among the implemented rules, the agreement established a dynamic quota allocation, allowing members to fish part of their quota within Norway's EEZ, and land the catch in Norwegian ports.
-In North America, Canada and the US have previous history with the utilization of side payments when in the 70's Pacific salmon shifted its distribution resulting in large interceptions of Canada's salmon by Alaskan fisheries [@Miller:2013iv; @Song:2017va].
-The conflict was resolved by the implementation of a conservation fund that worked as a side payment for both Canada and the state of Alaska [@Miller:2013iv; @Song:2017va].
-The potential adaptation of side payments in terms of quota swaps or allocating EEZ-fishing rights across the Gulf of Maine EEZs could be a potential solution as stocks shift due to climate change.
-
-Transboundary fisheries management have to be prepared for the uncertainty that comes with a changing world.
-Future climate change will depend on the path society as a whole will take, and thus we rely on scenario planning to account for the uncertainty build in future decision making [@vanVuuren:2011ef].
-In our results, the "winners and losers" of climate change, and the intensity of the change, will be scenario dependent.
-For instance, stock-share of yellowtail flounder under a high emission scenario will be larger for the US while Canada's gain of cod stock-share will be larger under a low emission scenario (Figure \ref{fig:Figure5-GOMA-prop}).
-Applying previously describe strategies (e.g.
-quota swaps or EEZ-fishing rights) could increase the resilience of treaties by preventing members from leaving the agreement due to a shift in threat points, as happened in the Pacific salmon case [@Miller:2013iv].
-
-Models are attempts to represent reality (in our case a future reality) based on observational data, previously established theory, and future scenarios, and are thus, subjected to different degrees of uncertainty [@Payne:2016gn].
-An ensemble of models is a way to present a more robust result that accounts for differences in the structural composition of each model [@Cheung:2016gv].
-In here we used three ESMs to project future changes in species maximum catch potential.
-The levels of uncertainty related to the ESMs differ among case studies.
-Overall, results for the Gulf of Maine agree with a reduction in MCP of all three species.
-However, some discrete areas show a positive change for yellowtail flounder by mid $21^{st}$ century (Figure \@ref(fig:Figure3-IPHC-prop)), mainly driven by the GFDL model (Figure \@ref(fig:FigureS23)).
-Potential model artifacts could also be contributing to the results, especially in the northern part of the study area (Bay of Fundy) as most disagreeing grids are covered by land, which could be influencing the results.
-In contrast, considerable uncertainty exists in the change of MCP along the IPHC Convention area shown by a disagreement between ESMs (Figure \@ref(fig:FigureS24)).
-Off the coast of British Columbia, increasing temperature trends are consistent among ESMs, however, other processes such as acidification and deoxygenation are still not well understood from British Columbia to the Gulf of Alaska  [@TalloniAlvarez:2019gz].
-Moreover, considerable uncertainty exists along the Bering Sea [@Douglas:2010Mb] and Antarctic Pacific regarding the extent and intensity of future sea-ice reduction under climate change [@Steiner:2015hc; @IPCC:2019tn].
-Regarding the DBEM, its structural uncertainty has been previously tested for agreement against commonly used species distribution algorithms such as Maxent [@Phillips:2006ff] and AquaMaps [@Kaschner:2011hi; @Ready:2010wr] resulting in no qualitative differences in trends between algorithms [@Cheung:2016jd].
-Finally, is worth mentioning that future changes to species distributions could be influenced by factors not captured by our model such as interactions between species [@Pecl:2017hu], adaptation of species to environmental changes, and anthropogenic factors [@Serpetti:2017he].
-However, these factors are expected to increase the rate of range-shifting of the species making our results conservative [@Cheung:2010dt; @Serpetti:2017he].
-
-## Conclusions
-
-Shifts in stocks distribution due to climate change have the potential of creating local extinction of economically important stocks while enhancing fisheries in areas where they were not present before.
-In this paper, we have explored the potential impacts of climate change in the joint management of selected transboundary stocks managed by Canada and the US.
-We found that, transboundary stocks are likely to shift in the upcoming years changing the proportion of the catch of jointly managed fisheries of Canada and the US.
-Lessons from other countries can provide solutions to such challenges.
-More specific, side payments, dynamic management, and interchangeable quotas were identified as potential solutions for North American region.
-While not directly addressed in this study, socio-economic impacts of shifting transboundary stocks could add an extra layer of complexity to the problem.
-Addressing shifts in stocks distribution sooner rather than latter could avert the so called “fish wars”, improve sustainability of jointly managed stocks, and secure the livelihood of thousands of families that depend on stocks that move freely between national jurisdictions.
-Finally, preparing for an uncertain future is key to achieve sustainable fisheries.
-
-<!-- Comented out for thesis -->
-<!-- # ACKNOWLEDGEMENTS -->
-
-<!-- This is a product of the *OceanCanada* Partnership funded by the Social Sciences and Humanities Research Council of Canada. -->
-
-<!-- ## References -->
-
-## Supplements
-
-<!-- End of the century change  -->
 
@@
 grid.raster(FigS12)
-
-```
-
-<!-- This was included to address the reviewers comments on the region 4D of Pacific Halibut -->
-<!-- NOTE: Remember to run the Results chunk to load all the data needed -->
-<!-- # ESM uncertainty -->
-<!-- This chunk explores the uncertainty build in the ESM-DBEM  -->
-
-```{r Functions, eval = F, echo = F}
-
-# This functions extract the information used for each species to project the changes in MCP.
-
-getTaxInfo <- function(TaxNumber,TaxPath=NA, Sal = "NA"){
-
-  # Set automatic path, change if needed
-  TaxPath <- "/Volumes/DATA/JULIANO_NEYMAR/PristineSeasData/Species/TaxonDataC0/"
-
-  # Sets the tac and path 
-  To_Read <- paste(TaxPath,TaxNumber,".txt",sep = "")
-
-  if(Sal == "Y"){
-    Spp_Info <- suppressWarnings(
-      read_table2(To_Read, 
-                  col_names = FALSE, col_types = cols(`0` = col_character(), 
-                                                      X2 = col_number(), X3 = col_number(), 
-                                                      X4 = col_number(), X5 = col_number(), 
-                                                      X6 = col_number()), 
-                  skip = 16)
-    ) 
-    Spp_Info <- Spp_Info[1,2:6]
-  }else{
-    # Reads in file
-    Spp_Info <- suppressMessages(
-      readr::read_delim(To_Read, 
-                        "\t", escape_double = FALSE, col_names = FALSE, 
-                        # col_types = cols(X2 = col_number()),
-                        trim_ws = TRUE)
-    )
-  }
-  return(Spp_Info)
-}
-
-getTTP <- function(TaxNumber,yr,TaxPath=NA){
-
-  # Set automatic path, change if needed
-  TaxPath <- paste("/Volumes/DATA/JULIANO_NEYMAR/PristineSeasData/TPP",yr,"",sep="/")
-
-  # Sets the tac and path 
-  To_Read <- paste(TaxPath,"TPPotp",TaxNumber,".csv",sep = "")
-
-  TPPotp <- read.csv(To_Read)
-
-  return(TPPotp)
-}
-
-getEnvVar=function(yr,ModelRCP,RCP,Variable){
-
-  if(ModelRCP == "IPSL"){
-    ModelRCP = "IPSL-CM5A-MR"
-    Filepath <- paste("/Volumes/DATA/DATA/Environmental data/Model Climate data/CMIP5/txt CMIP5/Reformatted",ModelRCP,RCP,"",sep="/")
-  }
-
-  if(ModelRCP == "MPI"){
-    ModelRCP = "MPI-ESM-MR"
-    Filepath <- paste("/Volumes/DATA/DATA/Environmental data/Model Climate data/CMIP5/txt CMIP5/Reformatted",ModelRCP,RCP,"",sep="/")
-  }
-
-  if(ModelRCP == "GFDL"){
-
-    if(RCP == "rcp26"){
-      ModelRCP <- "GFDL26"
-    }else{
-      ModelRCP <- "GFDL85"
-    }
-    Filepath <- paste("/Volumes/DATA/JULIANO_NEYMAR/PristineSeasData/Climate",ModelRCP,"",sep="/")
-  }
-
-  if(Variable == "Ice"){
-
-    Bottom <- paste("IceExt_",yr,".txt",sep="")
-
-  }
-
-  if(Variable == "Temperature"){
-
-    Bottom = paste("botTemp_",yr,".txt",sep="")
-
-  }
-
-  if(Variable == "Salinity"){
-    # Bottom
-    Bottom = paste("Salinity_btm_",yr,".txt",sep="")
-
-  }
-
-  Read_me <- paste(Filepath,Bottom,sep="")[1]
-  Bottom_Data <- read.csv(Read_me,header=F)
-
-  # Retrun
-
-  getTemp <- Bottom_Data 
-}
-
-```
-
-```{r 4DE_exploration, eval = F, echo = F,message=F, warning=F}
-
-# Exploring why 4D is negative under RCP 2.6 but positive under RCP 8.5
-# This chunk will use functions build for the work to estimate carring capacity (K)
-
-### Exploration at the spatial level
-
-Spatial_4DE <- DBEM_Corrected %>% 
-  mutate(RCP = ifelse(Model %in% c("GFDL26F1","IPSL26F1","MPI26F1"),"RCP 2.6","RCP 8.5")) %>% # Set the RCPs
-  filter(Species == "Hippoglossus stenolepis") %>% 
-  left_join(IPHC_Reg_DBEM_df,
-            by = "INDEX") %>% 
-  filter(RegArea %in% c("4D","4E")) %>%
-   #Sum grid-cells by regulatory area, RCP and Model
-  group_by(RegArea,RCP,Model) %>%
-  summarise_at(vars(`2005`:`2099`), sum,na.rm=T) %>% 
-  tidyr::gather("Year","Total_MCP",`2005`:`2099`) %>% 
-  group_by(RegArea,RCP,Year) %>% 
-  summarise(
-    m=mean(Total_MCP),
-    sd=sd(Total_MCP)
-  )
-
-# ggplot(Spatial_4DE) +
-#  geom_point(
-#   aes(
-#    x = Year,
-#    y = m,
-#    colour = RCP
-#   )
-#  ) +
-#  facet_wrap(~RegArea,
-#        scales = "free")
-
-### Environmental varibales of the region
-
-## Temp
-
-# Variables
-Model = c("GFDL","IPSL","MPI")
-RCP = c("rcp26","rcp85")
-
-Grid <- DBEM_Corrected %>% 
-  select(INDEX) %>% 
-  left_join(IPHC_Reg_DBEM_df,
-            by = "INDEX") %>% 
-  filter(RegArea %in% c("4D","4E")) %>% 
-  select(INDEX)
-
-Variables <- c("Temperature","Salinity","Ice")
-
-F_BData <- NULL 
-F_SData <- NULL 
-F_MData <- NULL # 
-F_RData <- NULL
-Years <- seq(2005,2100,1)
-
-all_Grid <- seq(1,259200,1)
-
-# Embarrasing for loop to get data
-
-for(v in 1:3){
-  # Loop through RCPs
-  for(r in 1:2){
-    # Loop through variables
-    for(m in 1:3){
-      # Loop through years
-      for(y in 1:length(Years)){
-
-        Data <- getEnvVar(yr = Years[y],
-                          Model = Model[m],
-                          Variable = Variables[v],
-                          RCP = RCP[r]
-        ) %>% 
-          mutate(INDEX = all_Grid) %>% 
-          filter(INDEX %in% Grid$INDEX)
-
-        if(y == 1){
-
-          F_BData <- Data[1]
-
-        }else{
-
-          F_BData <- cbind(Data[1],F_BData)
-
-        }
-      }
-
-      colnames(F_BData) <- Years
-
-      F_BData <- F_BData %>% 
-        gather(Year,Value,1:426) %>% 
-        mutate(Model = Model[m],
-               RCP = RCP[r],
-               Variable = Variables[v])
-
-      if(m == 1){
-
-        F_MData <- F_BData
-
-      }else{
-
-        F_MData <- rbind(F_BData,F_MData)
-      }
-    }
-
-    if(r == 1){
-
-      F_RData <- F_MData
-
-    }else{
-
-      F_RData <- rbind(F_RData,F_MData)
-    }
-  }
-
-  if(v == 1){
-
-    F_VData <- F_RData
-
-  }else{
-
-    F_VData <- rbind(F_VData,F_RData)
-  }
-
-} # closes variable loop
-
-write_csv(F_VData,
-     "Environmental_Data_Halibut.csv")
-
-#Load Halibut Species preferences
-Halibut <- getTaxInfo(600514)
-# Demersal
-# HabAssocSal 0 1 1 -1 -1
-# HabAssocIce 0
-
-# Temp
-TTPop <- getTTP(600514,"Avg") %>% 
-  filter(TempPP > 0)
-
-Min_T <- min(TTPop$Temp)
-Max_T <- max(TTPop$Temp)
-
-# Halibut_Temp 2
-# quant05 -2 
-# quant25 0 
-# quant50 2
-# quant75 5
-# quant95 11
-```
-
-```{r halibut_enviro, eval = F, echo = F}
-
-# Read Data
-Environmental_Data_Halibut <- read.csv(paste(my_path("D","Distribution"),"Environmental_Data_Halibut.csv",sep=""))
-
-# Isolate Regions
-DE_Regions <- IPHC_Reg_DBEM_df %>% 
-  filter(RegArea %in% c("4D","4E")) %>% 
-  left_join(Environmental_Data_Halibut,
-            by ="INDEX") %>% 
-  # Average variable per regulatory area
-  group_by(Model,RCP,Variable,Year,RegArea) %>% 
-  summarise(
-    Mean_Reg = mean(Value,na.rm=T)
-  ) %>% 
-  # Model (GCM) average and sd
-  group_by(RCP,Variable,Year,RegArea) %>% 
-  summarise(
-    Mean_GCMs = mean(Mean_Reg,na.rm=T),
-    sd_GCMs = sd(Mean_Reg,na.rm=T)
-  ) %>% 
-  # Running mean of variables
-  group_by(RCP,Variable,RegArea) %>% 
-  mutate(RMean = rollmean(x = Mean_GCMs, 10,
-                          align = "right",
-                          fill = Mean_GCMs),
-         Rsd = rollmean(x = Mean_GCMs, 10,
-                        align = "right",
-                        fill = sd_GCMs)
-  ) %>% 
-  filter(Year >= 2015) %>% 
-  ungroup() %>% 
-  # For plot
-  mutate(
-    RCP = ifelse(RCP == "rcp26","Low Emission","High Emission"),
-    Variable = ifelse(Variable == "Ice","Ice Extension",
-                      ifelse(Variable == "Temperature","Bottom Temperature (ºC)","Bottom Salinity")
-    )
-  )
-
-# Plot figure for supplements
-ggplot(DE_Regions) + 
-  geom_ribbon(aes(
-    x = Year,
-    ymin = RMean - sd_GCMs,
-    ymax = RMean + sd_GCMs,
-    fill = RCP
-  ),
-  alpha = 0.2
-  ) +
-  geom_line(
-    aes(
-      x = Year,
-      y = RMean,
-      colour = RCP
-    )
-  ) +
-  facet_wrap(~RegArea +Variable,
-             scales ="free_x") +
-  my_ggtheme_p()() +
-  scale_x_continuous(breaks = seq(2010,2100,30),
-                     limits = c(2010,2100)
-  ) +
-  scale_color_manual("Climate Change Scenario",
-                     values=c("red","blue")
-  ) + 
-  scale_fill_manual("Climate Change Scenario",
-                    values=c("red","blue")
-  ) + 
-  ylab("Running Mean (10 yrs)")
-
-ggsave("Environ_Sup.png",
-    plot = last_plot(),
-    width = 10,
-    height =8,
-    units = "in",
-    path = "./Results/Sup"
-    )
 
@@
 
-<!-- GOMA Outliers analysis -->
-```{r GoM_Environ_outliers, eval = F, echo = F}
-
-# ------------------ #
-# Make maps PER model
-# ------------------ #
-
-Per_Model_Chng_GoM <- Atlantic_DBEM %>% 
- mutate(RCP = ifelse(Model %in% c("GFDL26F1","IPSL26F1","MPI26F1"),"Low Emission","High Emission")) %>%
- tidyr::gather("Year","Change",`2005`:`2099`) %>%
- mutate(Change = replace_na(Change, 0)) %>% # Convert NA's into 0's
- # Indicate the three period times
-  mutate(
-  Period = ifelse(Year >= Beg_In & Year <= Beg_End,"Beginning",
-          ifelse(Year >= Mid_In & Year <= Mid_End,"Mid_Century",
-              ifelse(Year >= End_In & Year <= End_End,"The_End_Century",
-                 "Other_Years"))
-  )
- ) %>% 
- filter(Period != "Other_Years",
-     Species %in% Outlier_Species) %>% # Remove unwanted years
-  # Temporal mean
- group_by(INDEX,Model,RCP,Period,Species) %>%
- summarise(
-  Mean_Temp = mean(Change, na.rm = T) 
- ) %>% 
- spread(Period,Mean_Temp) %>%
-  # Divide future values by present
- mutate_at(vars(Mid_Century, 
-         The_End_Century),
-      funs(ifelse(Begining > 0, ./Begining,.)) #if no species today value is the future
- ) %>% 
-   # Estimate percentage change
- mutate_at(vars(Mid_Century,
-         The_End_Century),
-      funs(ifelse(Begining == 0 & . == 0, 0, # If for no change than 0
-            ifelse(Begining == 0 & . > 0, 100, # If changes from 0 to anything then 100
-                round(-(1-.)*100) # Estimate percentage change
-            )
-      )
-      )
- )%>% 
-  # Set Outliers column
- mutate(
-  Outlier = ifelse(INDEX %in% Outliers,"Yes","No")
- ) %>% 
- left_join(Coor) %>% 
-  # set everything over 100 to 100
- mutate_at(vars(Mid_Century,
-         The_End_Century),
-      funs(ifelse(. > 100, 100,.)
-      ) 
- ) #%>% 
- # filter(Outlier == "Yes")
-
-# ----------- #
-# Plot results 
-# ----------- #
-
-ggplot(Per_Model_Chng_GoM) +
-  geom_tile(
-    aes(
-      x = Longitude,
-      y = Latitude,
-      fill = Mid_Century,
-      # fill = log10(abs(Mid_Century)),
-      color = Outlier
-      # fill = Depth
-    ),
-    size = 0.5
-  ) +
-  scale_fill_gradient2(paste("MCP Percentage Change of",Outlier_Species,"\n           (",Mid_In,"-",Mid_End,")"), # If not using the bins
-                       limits=c(Lim_Neg,
-                                Lim_Max),
-                       breaks = Seq,
-                       na.value = 'darkred' # NA values are present when the species is no more 
-  ) +
-  # Mark outliers in yellow
-  scale_color_manual(values=c(NA,"yellow")) + # for Bins option A
-  geom_sf(data = GM_Land, colour = "lightgrey") +
-  coord_sf(xlim = c(-71.0592, -63.33333),
-           ylim = c(41,45.5)
-  ) +
-  facet_wrap(~RCP+Model) +
-  my_ggtheme_m()() +
-  theme(legend.key.width =unit(6,"line"))
-
-# Name and save plot
-
-Name = "MCP_Chng_Mid_GoM_Outlier.png"
-
-ggsave(Name,
-    plot = last_plot(),
-    width = 14,
-    height = 10,
-    units = "in",
-    path = Path)
-
-```
-
 ```{r FigureS23, eval = T, echo = F, fig.cap = "Changes in maximum catch potential of yellowtail flounder (*Limanda ferruginea*) within the study area by mid-century relative to present time.
@@
 grid.raster(FigS23)
-
-```
-
-<!-- ESM-DBEM Uncertinty analysis -->
-
-```{r DBEM_Uncertanty, eval = F, echo = F}
-
-#### DBEM-ESM Uncertanty
-
-Today_Uncertanty <- DBEM_Corrected %>% 
-  filter(Species %in% Selected_Species) %>% 
-  left_join(IPHC_Reg_DBEM_df,
-            by = "INDEX") %>% 
-  filter(!is.na(RegArea)) %>% 
-  mutate(RCP = ifelse(Model %in% RCP,"Low Emission","High Emission")) %>% 
-  gather("Year","MCP",Beg_In:Beg_End) %>% 
-  mutate(Period = ifelse(Year >= Beg_In & Year <= Beg_End,"Beginning","NA")) %>% 
-  group_by(RegArea,Model,RCP,Year,Period) %>% 
-  summarise(Regional_MCP =sum(MCP,na.rm=T)) %>% 
-  group_by(RegArea,Model,RCP) %>% 
-  summarise(Today_MCP =mean(Regional_MCP,na.rm=T))
-
-IPHC_MCP_Change_Uncert <- DBEM_Corrected %>% 
-  filter(Species %in% Selected_Species) %>% 
-  left_join(IPHC_Reg_DBEM_df,
-            by = "INDEX") %>% 
-  filter(!is.na(RegArea)) %>% 
-  mutate(RCP = ifelse(Model %in% RCP,"Low Emission","High Emission")) %>% 
-  gather("Year","MCP",Beg_In:End_End) %>%
-  group_by(Model,RCP,Year,RegArea) %>%
-  summarise(Regional_MCP =sum(MCP,na.rm=T)) %>% 
-  group_by(RCP,Model,RegArea) %>% # Running mean as Kleisner & Pauly 2012
-  mutate(RMean = rollmean(x = Regional_MCP, 10,
-                          align = "right",
-                          fill = Regional_MCP)
-  ) %>% 
-  mutate(GCM = ifelse(Model == "GFDL26F1" | Model == "GFDL85F1","GFDL",
-                      ifelse(Model == "IPSL26F1" | Model == "IPSL85F1", "IPSL",
-                             ifelse(Model == "MPI26F1" | Model == "MPI85F1","MPI","NA"
-                             )
-                      )
-  )
-  ) %>% 
-  filter(Year >= 2015) %>% 
-  left_join(Today_Uncertanty,
-            by = c("RegArea","Model","RCP")) %>% 
-  mutate(Index = RMean/Today_MCP)
-
-# Create and save plot
-
-ggplot(IPHC_MCP_Change_Uncert) +
-  geom_line(
-    aes(
-      x = as.numeric(Year),
-      y = Index,
-      color = GCM,
-      linetype = RCP
-    )
-  ) +
-  facet_wrap(~RegArea,
-             scales = "free_y") +
-  labs(
-    x = "Year",
-    y ="Index (Future MCP/Present)"
-  ) +
-  scale_color_manual("Global Circulation model",
-                     values=c("#EEA410","#B53CB9","#2EBC67")
-  ) +
-  scale_x_continuous(breaks = seq(2010,2100,30),
-                     limits = c(2010,2100)
-  ) +
-  my_ggtheme_p()() +
-  # Save plot
-  ggsave("Model_Uncer_Sup.png",
-         plot = .,
-         width = 12,
-         height =8,
-         units = "in",
-         path = "./Results/Sup"
-  )
 
@@
 ```
-
-<!-- # OLD ANALYSIS -->
-
-```{r Old analysis, eval = F, echo = F}
-
-#### Old North America Estimation ####
-
-for(r in 1:2){
-
- if(r == 1){
-  RCP = c("GFDL26F1","IPSL26F1","MPI26F1") #Low RCP
- }else{
-  RCP = c("GFDL85F1","IPSL85F1","MPI285F1") #High RCP
- }
-
- # OLD VERSION _________________________________________
- # Mean for each cel from 2005-2014
- Mean_Data <- DBEM_Corrected %>% 
-  filter(Model %in% RCP) %>% 
-  group_by(INDEX,
-       Model) %>% 
-  summarise_at(vars(Beg_In:End_End), sum,na.rm=T) %>% # Sum the MCP of all species in each index by model
-  select(INDEX,Beg_In:Beg_End) %>% 
-  group_by(INDEX) %>% 
-  summarise_at(vars(Beg_In:Beg_End), mean,na.rm=T) %>% # Yearly average of three models (Structural uncertanty)
-  mutate(Mean = rowMeans(.[,2:11])) %>% # Decal average (2005-2014) of results (Uncertanty related to climate variabillity)
-  select(INDEX,Mean) %>% 
-  arrange(INDEX)
-
- #The future
- Future <- DBEM_Corrected %>% 
-  filter(Model %in% RCP) %>% 
-  group_by(INDEX,
-       Model) %>% 
-  summarise_at(vars(Beg_In:End_End), sum,na.rm=T) %>% # Sum the MCP of all species in each index by model
-  group_by(INDEX) %>% 
-  summarise_at(vars(`2015`:End_End), mean,na.rm=T) %>% # Yearly average of three models
-  arrange(INDEX)
-
- #SD future
- # for this we have to first average the temporal variabillity for each model and then average the models, that way we will have the SD resulted of the model average and not the termporal variation
-
- SD_Future <- DBEM_Corrected %>%
-  # filter( INDEX == 67071) %>%
-  filter(Model %in% RCP) %>%
-  group_by(INDEX,
-       Model) %>%
-  summarise_at(vars(`2005`:`2099`), sum,na.rm=T) %>% # Sum the MCP of all species in each index by model
-  tidyr::gather("Year","Change",3:97) %>%
-  filter(Year >= 2045 & Year <= 2054) %>% # Select mid century
-  group_by(INDEX,Model) %>%
-  summarise(
-   Mean_Temp = mean(Change, na.rm = T), # Temporal Mean and SD 
-   SD_Temp = sd(Change, na.rm = T)
-  ) %>%
-  group_by(INDEX) %>%
-  summarise(
-   Mean_M = mean(Mean_Temp, na.rm = T), # Model mean
-   SD_M = sd(Mean_Temp, na.rm = T) # Model SD
-  ) %>%
-  filter(!is.na(SD_M)) %>%
-  mutate(SD_Plus = ifelse((SD_M*2) > Mean_M,"No agreement","Agree")) %>% # If 2xSD is bigger than the mean, then models don't agree, otherwise they do
-  # filter(SD_Plus > 0) %>%
-  left_join(DBEM_Coor,
-       by="INDEX")
-
- #### Overall agreement. Number of cells where models don't match
-
- # SD_Future %>%
- #  group_by(SD_Plus) %>%
- #  summarise(n())
-
- # RCp 2.6 30% of grids don't agree
- # Agree 3825
- # Don't agree 1140
-
- # RCp 8.5 32% of grids don't agree
- # Agree     3564
- # No agreement 1151
-
- # #Divide one by the other
-
- #### _______________________________________________ #
-
- # Divide future projections by "today's"" projections
-
- Cell_Index <- sweep(Future[2:86],#Future catch p.
-           1, #1 goes by row and 2 goes by colum
-           Mean_Data$Mean, #the means
-           "/") %>% 
-  mutate(INDEX = Future$INDEX) %>% 
-  select(INDEX,everything())
-
- Mid_Century <- Cell_Index %>% 
-  select(INDEX,
-      Mid_In:Mid_End) %>% 
-  mutate(Mean = rowMeans(.[,2:11])) %>% # Temporal average
-  # left_join(NorthA_Coor_df,
-       # by ="INDEX") %>% 
-  mutate(Percentage = round(-(1-Mean)*100)) %>% # Convert to percentage change
-  mutate("Percentage Change" = ifelse(Percentage > 100, 100,Percentage)) %>% # set everything over 100 to 100
-  filter(!is.na(`Percentage Change`)) %>% 
-  left_join(DBEM_Coor,
-       by="INDEX")
-
-  #### North America Transboundary Plot ####
-
- Seq <- seq(-100,100,by=20) #Axis
-
- ggplot() +
-  geom_tile(data = Mid_Century, # Percentage change data
-       aes(
-        x = longitude,
-        y = latitude,
-        colour = `Percentage Change`,
-        fill = `Percentage Change`
-       )
-  ) +
-  geom_point(data = subset(SD_Future, SD_Plus == "No agreement"), # ESM model uncertanty
-        aes(
-         x = longitude,
-         y = latitude
-        ),
-        size = 0.05,
-        alpha = 0.5,
-        shape = 6,
-        colour = "grey20") +
-  geom_sf(data = North_America_Land, fill = "grey90") + # Base map
-  coord_sf(xlim = c(-190,-50)) +
-  scale_colour_gradient2(
-   limits=c(-100,
-        100),
-   breaks = Seq) +
-  scale_fill_gradient2(
-   limits=c(-100,
-        100),
-   breaks = Seq) +
-  my_ggtheme_m()()
-
-  if(r == 1){
-  Name = paste("North_America_Change_26_2050.png")
- }else{
-  Name = paste("North_America_Change_85_2050.png")
- }
-
- ggsave(Name,
-     plot = last_plot(),
-     width = 12,
-     height = 10,
-     units = "in",
-     path = Path)
-
- ### now we average the results from the models for END century ###
-
- End_Century <- Cell_Index %>% 
-  select(INDEX,
-      `2090`:`2099`) %>% 
-  mutate(Mean = rowMeans(.[,2:11])) %>% 
-  mutate(Percentage = round(-(1-Mean)*100)) %>% # Convert to percentage
-  mutate("Percentage Change" = ifelse(Percentage > 100, 100,Percentage)) %>% # set everything over 100 to 100
-  filter(!is.na(`Percentage Change`)) %>% 
-  left_join(DBEM_Coor,
-       by="INDEX")
-
- SD_End <- DBEM_Corrected %>% 
-  # filter( INDEX == 67071) %>% 
-  filter(Model %in% RCP) %>% 
-  group_by(INDEX,
-       Model) %>% 
-  summarise_at(vars(`2005`:`2099`), sum,na.rm=T) %>% 
-  tidyr::gather("Year","Change",3:97) %>% 
-  filter(Year >= 2090 & Year <= 2099) %>% 
-  group_by(INDEX,Model) %>% 
-  summarise(
-   Mean_Temp = mean(Change, na.rm = T), # Mean temporal
-   SD_Temp = sd(Change, na.rm = T) #Sd of 10 years average
-  ) %>% 
-  group_by(INDEX) %>% 
-  summarise(
-   Mean_M = mean(Mean_Temp, na.rm = T), # Models mean
-   SD_M = sd(Mean_Temp, na.rm = T) #Models Sd
-  ) %>% 
-  filter(!is.na(SD_M)) %>% 
-  mutate(SD_Plus = ifelse((SD_M*2) > Mean_M,"No agreement","Agree")) %>% 
-  # filter(SD_Plus > 0) %>% 
-  left_join(DBEM_Coor,
-       by="INDEX")
-
- ggplot() +
-  geom_tile(data = End_Century,
-       aes(
-        x = longitude,
-        y = latitude,
-        colour = `Percentage Change`,
-        fill = `Percentage Change`
-       )
-  ) +
-  geom_point(data = subset(SD_End, SD_Plus == "No agreement"),
-        aes(
-         x = longitude,
-         y = latitude
-        ),
-        size = 0.05,
-        alpha = 0.5,
-        shape = 6,
-        colour = "grey20") +
-  geom_sf(data = North_America_Land, fill = "grey90") +
-  coord_sf(xlim = c(-190,-50)) +
-  scale_colour_gradient2(
-   limits=c(-100,
-        100),
-   breaks = Seq) +
-  scale_fill_gradient2(
-   limits=c(-100,
-        100),
-   breaks = Seq) +
-  my_ggtheme_m()()
-
- if(r == 1){
-  Name_End = paste("North_America_Change_26_2100.png")
- }else{
-  Name_End = paste("North_America_Change_85_2100.png")
- }
-
- ggsave(Name_End,
-     plot = last_plot(),
-     width = 12,
-     height = 10,
-     units = "in",
-     path = Path)
-
-}
-
-#### Old IPHC estimation ####
-
-# Future change in MCP of IPHC per region
-IPHC_MCP_Change <- DBEM_Corrected %>% 
- mutate(RCP = ifelse(Model %in% c("GFDL26F1","IPSL26F1","MPI26F1"),"RCP 2.6","RCP 8.5")) %>% # Set the RCPs
- filter(Species %in% Selected_Species#,
-     # INDEX %in% IPHC_Reg_DBEM_df$INDEX
-     ) %>% # Filter species to halibut and the region for the IPHC regulatory area
- # group_by(INDEX,Model,RCP,Species) %>% # Add values per species
- # summarise_at(vars(`2005`:`2099`), sum,na.rm=T) %>%
- left_join(IPHC_Reg_DBEM_df,
-      by = "INDEX") %>% # Include the regulatory areas info
- group_by(RegArea,RCP,Model) %>% #Sum grid-cells by regulatory area, RCP and Model
- summarise_at(vars(`2005`:`2099`), sum,na.rm=T) %>% 
- tidyr::gather("Year","Change",`2005`:`2099`) %>%
- mutate(# Indicate the three period times
-  Period = ifelse(Year >= 2005 & Year <= 2014,"Today",
-          ifelse(Year >= 2046 & Year <= 2055,"Mid Century",
-              ifelse(Year >= 2090 & Year <= 2099,"End Century",
-                 "Other_Years"))
-  )
- ) %>% 
- filter(Period != "Other_Years") %>% # Remove unwanted years
- group_by(RegArea,Model,RCP,Period) %>%
- summarise(
-  Mean_Temp = mean(Change, na.rm = T), # Temporal mean
-  SD_Temp = sd(Change, na.rm = T) #Temporal sd
- ) %>% 
- group_by(RegArea,RCP,Period) %>% # Models (GFDL,IPSL,MPIs) mean and SD
- summarise(
-  Mean_M = mean(Mean_Temp, na.rm = T),
-  SD_M = sd(Mean_Temp, na.rm = T)
- ) %>% 
- filter(!is.na(SD_M)) %>% 
- mutate(Robust = ifelse((SD_M*2) > Mean_M,"No agreement","Agree")) %>% # Flags robustness in data
- # filter(Robust > 0) %>%
- select(RegArea,RCP,Period,Mean_M) %>% # They all agree except for 4D mid century
- spread(Period,Mean_M) %>% 
- mutate( # Estimate the percentage change
-  Change_Mid = `Mid Century`/Today,
-  Change_End = `End Century`/Today,
-  Percentage_Mid = round(-(1-Change_Mid)*100),
-  Percentage_End = round(-(1-Change_End)*100)
- ) %>% 
- select(RegArea, RCP, Percentage_Mid,Percentage_End)
-
-#### Species Table for SS proportion change ####
-
-#### OLD VERSION
-
-# Average (GFDL, MPI, IPSL) MCP of each species from 2005-2099 for both RCP's
-Overall <- DBEM_Corrected %>%
- left_join(EEZ_CellID,
-      by = "INDEX") %>% 
- # head() %>%
- filter(EEZID %in% Selected_Areas$EEZID) %>% 
- mutate( # determine what nation is wach region, what result is fr each RCP and Basin
-  Nation = ifelse(EEZID >= 958, "Alaska",
-          ifelse(EEZID == 925,"Can W",
-              ifelse(EEZID == 851, "USA E",
-                 ifelse( EEZID== 848, "USA W",
-                     "Can E"))
-          )),
-  RCP = ifelse(Model %in% RCP,"Low_Emission","High_Emission"), # determine which model is ehat RCP
-  Basin = ifelse(Nation %in% c("USA E","Can E"),"Atlantic","Pacific"),
- ) %>% 
- group_by(Species,Nation,Basin,RCP,Model) %>% # Adds each species' MCP of all INDEX-cells within each "nation" EEZ
- summarise_if(is.numeric,sum,na.rm=T) %>% # sum of values 
- group_by(Species,Nation,Basin,RCP) %>% 
- summarise_at(vars(`2005`:`2099`),mean,na.rm=T) %>% # Average the MCP results from the three ESMs
- gather("Year","MCP",`2005`:`2099`) %>% 
- mutate( # Indicate the three period times
-  Period = ifelse(Year >= 2004 & Year <= 2014,"Today",
-          ifelse(Year >= 2046 & Year <= 2055,"Mid_Century",
-              ifelse(Year >= 2090 & Year <= 2099,"End_Century",
-                 "Other_Years"))
-  )
- ) %>% # Set the three time periods 
- filter(Period != "Other_Years") %>% # Remove whatever is in the middle
- group_by(Species,Nation,Basin,RCP,Period) %>% 
- summarise(Period_MCP = mean(MCP)) #Temporal average of results
-
-#### Percentage Change in MCP for each species period, and RCP ####
-
-MCP_Spp_Change <- Overall %>%
- spread(Period,Period_MCP) %>% 
- mutate( # Divides the different timeframes by the present and estimates percentage change
-  Change_End = `End_Century`/Today,
-  Change_Mid = `Mid_Century`/Today,
-  Mid_Century = -(1-Change_Mid)*100,
-  The_End_Century = -(1-Change_End)*100
- ) %>%
- gather("Period","Percentage_Change",Mid_Century:The_End_Century) %>% 
- ungroup() %>% 
- select(-5)
-
-# group_by(Nation,Period,RCP) %>% # Average the results per species
-#  summarise(
-#   Mean_All = mean(Percentage_Change, na.rm = T),
-#   sd_All = sd(Percentage_Change, na.rm = T)
-#  ) %>%
-#  View() # Average proportion change of all species
-
- #### Compare versions
-
- # Comparring <- MCP_Species_Data %>% 
- #  select(1:5) %>% 
- #  left_join(MCP_Spp_Change) %>% 
- #  mutate(Diff = Mean_ESM_MCP_Chng - Percentage_Change)
- # 
- # 
- #
-
-#### Percentage Change in stock-share ratio for each species period, and RCP ####
-
-SS_Change <- Overall %>%
- group_by(RCP,Basin,Species,Period) %>% 
- summarise(Total_MCP = sum(Period_MCP)) %>% #Estimate todays's total (both EEZs added) MCP for each species (for each Basin!)
- left_join(Overall) %>% # Inlude each nation's MCP
- mutate(
-  Proportion = (Period_MCP/Total_MCP)*100 # estimates each Country's catch proportion per period
- ) %>% 
- select(Species,Nation,Basin,RCP,Period,Proportion) %>% 
- spread(Period,Proportion) %>% # Spread for easier mutation
- mutate( # Estimate the percentage change
-  SSR_Change_Mid = `Mid Century`/Today,
-  SSR_Change_End = `End Century`/Today,
-  SSR_Percentage_Mid = round(-(1-SSR_Change_Mid)*100),
-  SSR_Percentage_End = round(-(1-SSR_Change_End)*100)
- ) %>% 
- # View() # Average change in MCP proportion per Nation (comment it to have a mean +-sd of all areas)
- group_by(RCP,Nation) %>% 
-  summarise(mean = mean(SSR_Percentage_End),
-       sd = sd(SSR_Percentage_End)
-       )
-
-#### IPHC proportion change
-
-#### Old version
-
-IPHC_Absolutes <- DBEM_Corrected %>% 
- mutate(RCP = ifelse(Model %in% c("GFDL26F1","IPSL26F1","MPI26F1"),"RCP 2.6","RCP 8.5")) %>% # Assigns RCP by model
- filter(Species %in% IPHC_Species,
-     INDEX %in% IPHC_Reg_DBEM_df$INDEX) %>% #Selects only IPHC species within regulatory areas
- left_join(IPHC_Reg_DBEM_df,
-      by = "INDEX") %>% # Include Regulatory areas
- gather("Year","MCP",`2005`:`2099`) %>% 
- group_by(RCP,RegArea,Year,Model) %>%
- summarise(Total_MCP = sum(MCP, na.rm = T)) %>% # Sums INDEX MCP per RegArea
- group_by(RCP,RegArea,Year) %>% 
- summarise(Mean_MCP = mean(Total_MCP, na.rm = T), #Yearly mean per ESM model
-      SD_MCP = sd(Total_MCP, na.rm = )
- ) %>% 
- mutate(Year = as.numeric(Year))
-
-# Changes in the proportion in comparrison of the mean (2004-2014) proportion ####
-
-# Estimate total MCP of each RCP per year
-Proportion_Total <- IPHC_Absolutes %>% 
- group_by(RCP,Year) %>% 
- summarise(
-  Total = sum(Mean_MCP),
-  Total_SD = sum(SD_MCP)
- )
-
-# head(Proportion_Total)
-
-# Estimates the proportion of each RegArea catch pero RCP and Year
-Proportion_Change <- IPHC_Absolutes %>% 
- left_join(Proportion_Total,
-      by = c("RCP","Year")) %>% 
- mutate(Proportion = (Mean_MCP/Total)*100)
-
-# Todays proportion
-Early_Proportion <- Proportion_Change %>% 
- filter(Year <= Beg_End) %>% 
- group_by(RCP,
-      RegArea) %>% 
- summarise(Mean_Prop = mean(Proportion))
-
-# Proportion change in the future (NOTE: not plotting by timeframe because of boxplot)
-Proportion_Change <- IPHC_Absolutes %>% 
- left_join(Proportion_Total,
-      by = c("RCP","Year")) %>% # Join with total MCP
- mutate(Proportion = (Mean_MCP/Total)*100) %>% # Get proportions
- left_join(Early_Proportion,
-      by= c("RCP","RegArea")) %>% # Include baseline proportion
- mutate(Change = Proportion/Mean_Prop) %>% # devide future changes by baseline
- mutate(Percentage = round(-(1-Change)*100,2),
-     Year = as.numeric(Year)) %>% 
- arrange(RCP) %>% 
-  mutate(Time_Step = ifelse(Year >= Mid_In & Year <= Mid_End,"Mid Century",
-              ifelse(Year >= End_In,"End Century","NA")),
-     Nation = ifelse(RegArea == "2A","US Contiguous",
-             ifelse(RegArea == "2B","Canada","Alaska")
-             )
-     ) %>% 
- filter(Time_Step != "NA",
-     RegArea != "NA",
-     Time_Step == "End Century")
-
-Proportion_Change$RegArea <- gsub("2B","2B",Proportion_Change$RegArea)
-
-#### Option all in one####
-PL <- ggplot(subset(Proportion_Change, RCP == "RCP 2.6"),
-     aes(
-      x = reorder(RegArea,Percentage, FUN = median), # from forcasts` package
-      # x = Nation, # from forcasts` package
-       y = Percentage,
-       # fill = Nation,
-      colour = Nation
-     )
- ) +
- geom_boxplot() +
- ylab("") +
- xlab ("") +
- geom_hline(yintercept = 0, linetype = "dashed") +
- my_ggtheme_p()() +
- # scale_fill_brewer("Region",palette = "Set2") +
- scale_colour_brewer("Region",palette = "Set2") +
- theme(legend.position = c(0.2, 0.98),
-    legend.direction = "horizontal") #+ 
- # geom_label(data=Proportion_Change, aes(label = "RCP 2.6", x = "2A" , y = 18, fill = NA), #RCP labels for grid plot
- #      colour = "blue",
- #      show.legend = FALSE,
- #      size = 5
- # )
-
-PH <- ggplot(subset(Proportion_Change, RCP == "RCP 8.5"),
-     aes(
-      x = reorder(RegArea,Percentage, FUN = median), # from forcasts` package
-      # x = Nation, # from forcasts` package
-       y = Percentage,
-       # fill = Nation,
-      colour = Nation
-     )
- ) +
- geom_boxplot() +
- my_ggtheme_p()() +
- ylab("") +
- xlab ("IPHC Regulatory Area") +
- geom_hline(yintercept = 0, linetype = "dashed") +
- my_ggtheme_p()() +
- # scale_fill_brewer("Region",palette = "Set2",guide=FALSE) + 
- scale_colour_brewer("Region",palette = "Set2",guide=FALSE) #+
- # geom_label(data=Proportion_Change, aes(label = "RCP 8.5", x = "3B" , y = 18, fill = NA), #RCP labels for grid plot
- #      colour = "red",
- #      show.legend = FALSE,
- #      size = 5
- # )
-
-ggdraw() +
- draw_plot(PL, x = 0, y = 0.5, width = 1, height = 0.5) +
- draw_plot(PH, x = 0, y = 0, width = 1, height = 0.5) +
- draw_plot_label(label = c("A", "B"), size = 15,
-         x = c(0, 0), 
-         y = c(1, 0.5)) +
- draw_plot_label(label = "Stock-Share Percentage Change", size = 12, angle = 90, fontface = "plain",
-         x = 0.02,
-         y =0.11999)
-
-### OLD VERION GOM
-
-#### Old analysis ##3
-Mean_Data_GoM <- Atlantic_DBEM %>% 
- mutate(RCP = ifelse(Model %in% c("GFDL26F1","IPSL26F1","MPI26F1"),"RCP 2.6","RCP 8.5")) %>%
- tidyr::gather("Year","Change",`2005`:`2099`) %>%
- mutate(# Indicate the three period times
-  Period = ifelse(Year >= 2005 & Year <= 2014,"Today",
-          ifelse(Year >= 2046 & Year <= 2055,"Mid Century",
-              ifelse(Year >= 2090 & Year <= 2099,"End Century",
-                 "Other_Years"))
-  )
- ) %>% 
- filter(Period != "Other_Years") %>% # Remove unwanted years
- group_by(INDEX,Model,RCP,Period,Species) %>%
- summarise(
-  Mean_Temp = mean(Change, na.rm = T), # Temporal mean
-  SD_Temp = sd(Change, na.rm = T) #Temporal sd
- ) %>% 
- group_by(INDEX,RCP,Period,Species) %>% # Models (GFDL,IPSL,MPIs) mean and SD
- summarise(
-  Mean_M = mean(Mean_Temp, na.rm = T),
-  SD_M = sd(Mean_Temp, na.rm = T)
- ) %>% 
- filter(!is.na(SD_M)) %>% 
- mutate(Robust = ifelse((SD_M*2) > Mean_M,"No agreement","Agree")) %>% # Flags robustness in data
- filter(Robust > 0) %>%
- select(INDEX,Species,RCP,Period,Mean_M) %>% # They all agree except for 4D mid century
- spread(Period,Mean_M) %>% 
- mutate( # Estimate the percentage change
-  Change_Mid = `Mid Century`/Today,
-  Change_End = `End Century`/Today,
-  Percentage_Mid = ifelse(round(-(1-Change_Mid)*100) > 100, 100,round(-(1-Change_Mid)*100)),
-  Percentage_End = ifelse(round(-(1-Change_End)*100) > 100, 100,round(-(1-Change_End)*100))
-  ) %>% 
- select(INDEX, Species, RCP, Percentage_Mid,Percentage_End) %>% 
-  left_join(GB_Coor,
-      by ="INDEX")
-
-#  mutate("Percentage Change" = ifelse(Percentage > 100, 100,Percentage)) %>% # set everything over 100 to 
-#  filter(!is.na(Longitude)) %>% 
-#  filter(Latitude <= 50)
-
-Mean_Data_GoM$Bins <- cut(Mean_Data_GoM$Mid_Century,breaks = 4)
-# unique(Mid_Century$Bins)
-
-# _______________________________________________________
-
-# The plot 
-Seq <- seq(-100,100,10)
-
-Lim_Neg <- min(Seq)
-Lim_Max <- max(Seq)
-
-# Use bins and collors yellow orange light red and dark red
-
-# Mean_Data_GoMb <- Mean_Data_GoM %>% # In case you want filter a specific species
-#  filter(Species == "Limanda ferruginea")
-
-ggplot() +
- geom_tile(data = Mean_Data_GoM,
-      aes(
-       x = Longitude,
-       y = Latitude,
-       fill = Percentage_Mid,
-       colour = Percentage_Mid
-       # fill = reorder(Bins,-Percentage),
-       # colour = reorder(Bins,-Percentage)
-      )
- ) +
- # scale_color_manual("MCP % Change",values=c("darkblue","lightblue","red","darkred")) + # for Bins option A
- # scale_fill_manual("MCP % Change",values=c("darkblue","lightblue","red","darkred")) + # for Bins option A
- # scale_color_brewer("MCP % Change",type='seq', palette='Reds') + # for Bins option B
- # scale_fill_brewer("MCP % Change",type='seq', palette='Reds') + # for Bins option B
- scale_fill_gradient2("MCP Percentage Change \n(2046-2055)", # If not using the bins
-            limits=c(Lim_Neg,
-                Lim_Max),
-            breaks = Seq,
-            na.value = 'darkred' # NA values are present when the species is no more 
- ) +
- scale_colour_gradient2("MCP Percentage Change \n(2046-2055)",
-             limits=c(Lim_Neg,
-                 Lim_Max),
-             breaks = Seq,
-             na.value = 'darkred' # NA values are present when the species is no more
- ) +
- # geom_label(data = Mean_Data_GoMb,
- #      aes(
- #       x = Longitude,
- #       y = Latitude,
- #       label = INDEX
- #      )
- # ) +
- geom_sf(data = GM_Land, colour = "lightgrey") +
- geom_sf(data = eez_GM, fill = NA) +
- annotate("text", label = "United States", x = -70, y = 45, size = 4, colour = "black") +
- annotate("text", label = "Canada", x = -66.8, y = 45.4, size = 4, colour = "black") +
- annotate("text", label = "Canada", x = -65.4, y = 44.2, size = 4, colour = "black") +
- coord_sf(xlim = c(-71.0592, -63.33333),
-      ylim = c(41,45.5)
- ) +
- my_ggtheme_m()() +
- theme(
-  axis.line = element_line(colour = "black", size = .5),
-  axis.ticks = element_line(size = .5),
-  axis.text.x = element_text(size = 12,
-                angle = 0,
-                face = "plain"),
-  axis.text.y = element_text(size = 12),
-  legend.key = element_rect(size = 3),
-  legend.key.width =unit(8,"line"),
-  legend.title = element_text(size = 20),
-  legend.text = element_text(size = 18)
- ) +
- facet_wrap(~RCP + Species, 
-       ncol = 3
- )
-
-Name = paste("Change_GB_26_85_2050.png",sep="_")
-
-ggsave(Name,
-    plot = last_plot(),
-    width = 20,
-    height = 10,
-    units = "in",
-    path = Path)
-
-```
-
-```{r IPHC_Proportion_EEZ, eval = F, echo = F, message=F, warning=F}
-
-Path <- "/Users/jpalacios/Documents/UBC/Oceans_Project/Manuscript/Results"
-# names(DBEM_Results)
-
-IPHC_Species <- c(
- "Anoplopoma fimbria", # Sablefish
- "Hippoglossus stenolepis" # Halibut
-)
-
-#### FIlter EEZs ###
-
-EEZs <- c(
- "Canada (Pacific)",
- "USA (West Coast)",
- # "USA (Alaska, Arctic)",
- "USA (Alaska, Subarctic)"
-)
-
-RCP <- c("GFDL26F1","IPSL26F1","MPI26F1")
-
-EEZsID <- EEZIDs_List %>% 
- filter(Name %in%EEZs) %>% 
- left_join(EEZ_CellID,
-      by = "EEZID")
-
-names(EEZsID)[3] <- "INDEX"
-# 
-# head(EEZsID)
-# head(EEZIDs_List)
-# unique(EEZsID$Name)
-
-IPHC_Absolutes <- DBEM_Results %>% 
- filter(Species %in% IPHC_Species) %>% #Selects only IPHC species
- filter(INDEX %in% EEZsID$INDEX) %>% # Inside EEZ
- left_join(EEZsID,
-      by = "INDEX",
-      all = FALSE) %>%
- # filter(!duplicated(.)) %>% 
- gather("Year","MCP",2:96) %>% # Removes duplicated
- mutate(RCP = ifelse(Model %in% RCP, "RCP 2.6","RCP 8.5"),
-     Nation = ifelse(grepl('Alaska',Name),"Alaska",Name)) %>% 
- group_by(Model,RCP,Nation,Year) %>%
- summarise(Total_MCP = sum(MCP, na.rm = T)) %>% # Sums MCP per EEZ
- group_by(RCP,Nation,Year) %>% 
- summarise(Mean_MCP = mean(Total_MCP, na.rm = T), #Mean per ESM model
-      SD_MCP = sd(Total_MCP, na.rm = )
- ) %>% 
- mutate(Year = as.numeric(Year))
-
-# Changes in the proportion in comparrison of the mean (2004-2014) proportion ####
-
-Proportion_Total <- IPHC_Absolutes %>% 
- group_by(RCP,Year) %>% 
- summarise(
-  Total = sum(Mean_MCP),
-  Total_SD = sum(SD_MCP)
- )
-
-# head(Proportion_Total)
-
-Proportion_Change <- IPHC_Absolutes %>% 
- left_join(Proportion_Total,
-      by = c("RCP","Year")) %>% 
- mutate(Proportion = (Mean_MCP/Total)*100)
-
-Early_Proportion <- Proportion_Change %>% 
- filter(Year <= 2014) %>% 
- group_by(RCP,
-      Nation) %>% 
- summarise(Mean_Prop = mean(Proportion))
-
-Proportion_Change <- IPHC_Absolutes %>% 
- left_join(Proportion_Total,
-      by = c("RCP","Year")) %>% 
- mutate(Proportion = (Mean_MCP/Total)*100) %>% 
- left_join(Early_Proportion,
-      by= c("RCP",
-         "Nation")) %>% 
- mutate(Change = Proportion/Mean_Prop) %>% 
- mutate(Percentage = round(-(1-Change)*100,2)) %>% 
- arrange(RCP)
-
-#### The actual plot ####
-
-ggplot(Proportion_Change) +
- aes(x = Year,
-   y = Percentage,
-   color = Nation) +
- geom_line() +
- # geom_smooth(method = "lm", se = TRUE) +
- ylim(-15,10)+
- ylab("Percentage Change")+
- facet_wrap(~RCP,
-       nrow = 1
-       # scales = "free_y"
- ) +
- scale_colour_manual(
-  values = c("purple","red","blue"),
-  labels = c("Alaska", "Canada", "US")
- )+
- geom_hline(yintercept = 0) +
- theme_classic()+
- theme(plot.title=element_blank(), #clears title
-    panel.background=element_blank(), #clears background 
-    axis.text.x=element_text(size=20), # Size of axis labels
-    axis.text.y =element_text(size=20), # Size of axis labels
-    axis.title=element_text(size=20), # Size of axis title
-    axis.title.x = element_text(vjust = .5), # Alignment of axis title
-    # axis.ticks = element_blank(), # Removes axis ticks
-    # axis.line = element_blank(), # Removes axis line,
-    legend.position = "top", # bottom, top, right, left
-    # legend.key = element_rect(size = 15), # Legend box size
-    # legend.key.height =unit(1,"line"),
-    # legend.key.width =unit(1,"line"),
-    legend.background = element_rect(),
-    legend.text = element_text(size = 18), #Legend text size
-    legend.title = element_blank(), # Legend title size
-    strip.background = element_blank(), #Facewrap options
-    strip.text = element_text(size = 20)
- )
-
-# Save figure
-
-# ggsave("Fig3.png",
-#    plot = last_plot(),
-#    width = 12,
-#    height = 6,
-#    units = "in",
-#    path = Path)
-
-### Box plot ###
-
-Proportion_Change %>% 
- mutate(Time_Step = ifelse(Year >= 2046 & Year <= 2055,"Mid Century",
-              ifelse(Year >= 2089,"End Century","NA"))) %>% 
- filter(Time_Step != "NA") %>% 
- ggplot(.,
-     aes(x = fct_rev(Time_Step), # from forcasts` package
-       y = Percentage,
-       fill = Nation
-     )
- ) +
- geom_boxplot() +
- ylab("Percentage Change") +
- xlab ("Time Step") +
- facet_wrap(~RCP,
-       nrow = 1#,
-       # scales = "free_y"
- ) +
- scale_fill_manual(
-  values = c("purple","red","blue"),
-  labels = c("Alaska", "Canada", "US")
- )+
- geom_hline(yintercept = 0) +
- theme_classic() +
- theme(plot.title=element_blank(), #clears title
-    panel.background=element_blank(), #clears background 
-    axis.text.x=element_text(size=20), # Size of axis labels
-    axis.text.y =element_text(size=20), # Size of axis labels
-    axis.title=element_text(size=20), # Size of axis title
-    axis.title.x = element_text(vjust = .5), # Alignment of axis title
-    # axis.ticks = element_blank(), # Removes axis ticks
-    # axis.line = element_blank(), # Removes axis line,
-    legend.position = "top", # bottom, top, right, left
-    # legend.key = element_rect(size = 15), # Legend box size
-    # legend.key.height =unit(1,"line"),
-    # legend.key.width =unit(1,"line"),
-    legend.background = element_rect(),
-    legend.text = element_text(size = 18), #Legend text size
-    legend.title = element_blank(), # Legend title size
-    strip.background = element_blank(), #Facewrap options
-    strip.text = element_text(size = 20)
- )
-
-```
-
-```{r GB_Results_All, eval = F, echo = F}
-
-#### Filter Species ####
-
-Atlantic_Species <- c(
- "Gadus morhua", # Cod
- "Limanda ferruginea", # Yellowtail flounder
- "Melanogrammus aeglefinus"
-)
-
-# Run Spatial chuck for the Atlantic
-# NAFO_5z$geometry
-
-Atlantic_DBEM <- DBEM_Results %>% 
- filter(Species %in% Atlantic_Species) %>% 
- filter( # Limit the area to George's bank
-  Latitude < 45.9759, # North
-  Latitude > 35, # South 
-  Longitude > -71.0592, # West
-  Longitude < -63.33333
- )
-
-# Path for saving plots
-Path <- "/Users/jpalacios/Documents/UBC/Oceans_Project/Manuscript/Results/GB/All"
-
-### MCP Change Analysis ####
-
-for(r in 1:2){
-
- if(r == 1){
-  RCP = c("GFDL26F1","IPSL26F1","MPI26F1") #Low RCP
- }else{
-  RCP = c("GFDL85F1","IPSL85F1","MPI285F1") #High RCP
- }
-
- # Mean for each cel from 2004-2014
- Mean_Data <- Atlantic_DBEM %>% 
-  filter(Model %in% RCP) %>% 
-  group_by(INDEX,
-       Model) %>% 
-  summarise_at(vars(`2005`:`2099`), sum,na.rm=T) %>% 
-  select(INDEX,`2005`:`2014`) %>% 
-  group_by(INDEX) %>% 
-  summarise_at(vars(`2005`:`2014`), mean,na.rm=T) %>% 
-  mutate(Mean = rowMeans(.[,2:11])) %>%
-  # mutate(SD = rowSds(.[,2:11])) %>%
-  select(INDEX,Mean) %>% 
-  arrange(INDEX)
-
- #The future
- Future <- Atlantic_DBEM %>% 
-  filter(Model %in% RCP) %>% 
-  group_by(INDEX,
-       Model) %>% 
-  summarise_at(vars(`2005`:`2099`), sum,na.rm=T) %>% 
-  group_by(INDEX) %>% 
-  summarise_at(vars(`2015`:`2099`), mean,na.rm=T) %>% 
-  arrange(INDEX)
-
- # #Divide one by the other
- Cell_Index <- sweep(Future[2:86],#Future catch p.
-           1, #1 goes by row and 2 goes by colum
-           Mean_Data$Mean, #the means
-           "/") %>% 
-  mutate(INDEX = Future$INDEX) %>% 
-  select(INDEX,everything()) %>% 
-  left_join(GB_Coor, #And now we include Lat-Long
-       by="INDEX")
-
- Mid_Century <- Cell_Index %>% 
-  select(INDEX,
-      `2046`:`2055`) %>% 
-  mutate(Mean = rowMeans(.[,2:11])) %>% 
-  left_join(GB_Coor,
-       by ="INDEX") %>% 
-  mutate(Percentage = round(-(1-Mean)*100)) %>% # Convert to percentage
-  mutate("Percentage Change" = ifelse(Percentage > 100, 100,Percentage)) %>% # set everything over 100 to 
-  filter(!is.na(Longitude)) %>% 
-  filter(Latitude <= 50)
-
- Mid_Century$Bins <- cut(Mid_Century$Percentage,breaks = 5)
-
- # _______________________________________________________
-
- # The plot
-
- # Lim_Neg <- min(Seq)
- # Lim_Max <- max(Seq)
-
- ggplot() +
-  geom_tile(data = Mid_Century,
-       aes(
-        x = Longitude,
-        y = Latitude,
-        # fill = Percentage,
-        # colour = Percentage
-        fill = reorder(Bins,-Percentage),
-        colour = reorder(Bins,-Percentage)
-       )
-  ) +
-  scale_color_brewer("MCP % Change",type='seq', palette='Reds') +
-  scale_fill_brewer("MCP % Change",type='seq', palette='Reds') +
-  # scale_fill_gradient2(limits=c(Lim_Neg, # If not using the bins
-  #                Lim_Max),
-  #           breaks = Seq#,
-  #           ) +
-  # scale_colour_gradient2(limits=c(Lim_Neg,
-  #                 Lim_Max),
-  #            breaks = Seq#,
-  #            ) +
-  geom_sf(data = GM_Land, colour = "lightgrey") +
-  geom_sf(data = eez_GM, fill = NA) +
-  annotate("text", label = "United States", x = -70, y = 45, size = 4, colour = "black") +
-  annotate("text", label = "Canada", x = -66.7, y = 45.4, size = 4, colour = "black") +
-  annotate("text", label = "Canada", x = -65.4, y = 44.2, size = 4, colour = "black") +
-  coord_sf(xlim = c(-71.0592, -63.33333),
-       ylim = c(40.5,45.5)
-  ) +
-  my_ggtheme_m()() +
-  theme(
-   axis.line = element_line(colour = "black", size = .5),
-   axis.ticks = element_line(size = .5),
-   axis.text.x = element_text(size = 12,
-                 angle = 0,
-                 face = "plain"),
-   axis.text.y = element_text(size = 12)
-  )
-
- if(r == 1){
-  Name = paste("Change_GB_26_2050.png")
- }else{
-  Name = paste("Change_GB_85_2050.png")
- }
-
- ggsave(Name,
-     plot = last_plot(),
-     width = 8,
-     height = 7,
-     units = "in",
-     path = Path)
-
- ### now we average the results from the models for END century ###
-
- End_Century <- Cell_Index %>% 
-  select(INDEX,
-      `2090`:`2099`) %>% 
-  mutate(Mean = rowMeans(.[,2:11])) %>% 
-  left_join(GB_Coor,
-       by ="INDEX")%>% 
-  mutate(Percentage = round(-(1-Mean)*100)) %>% # Convert to percentage
-  mutate("Percentage Change" = ifelse(Percentage > 100, 100,Percentage)) %>% # set everything over 100 to 100
-  filter(!is.na(Longitude)) %>% 
-  filter(Latitude <= 50)
-
- End_Century$Bins <- cut(End_Century$Percentage,breaks = 5)
-
- # _______________________________________________________
-
- # The plot
-
- ggplot() +
-  geom_tile(data = End_Century,
-       aes(
-        x = Longitude,
-        y = Latitude,
-        # fill = Percentage,
-        # colour = Percentage
-        fill = reorder(Bins,-Percentage),
-        colour = reorder(Bins,-Percentage)
-       )
-  ) +
-  scale_color_brewer("MCP % Change",type='seq', palette='Reds') +
-  scale_fill_brewer("MCP % Change",type='seq', palette='Reds') +
-  # scale_fill_gradient2(limits=c(Lim_Neg, # If not using the bins
-  #                Lim_Max),
-  #           breaks = Seq#,
-  #           ) +
-  # scale_colour_gradient2(limits=c(Lim_Neg,
-  #                 Lim_Max),
-  #            breaks = Seq#,
-  #            ) +
-  geom_sf(data = GM_Land, colour = "lightgrey") +
-  geom_sf(data = eez_GM, fill = NA) +
-  annotate("text", label = "United States", x = -70, y = 45, size = 4, colour = "black") +
-  annotate("text", label = "Canada", x = -66.7, y = 45.4, size = 4, colour = "black") +
-  annotate("text", label = "Canada", x = -65.4, y = 44.2, size = 4, colour = "black") +
-  coord_sf(xlim = c(-71.0592, -63.33333),
-       ylim = c(40.5,45.5)
-  ) +
-  my_ggtheme_m()() +
-  theme(
-   axis.line = element_line(colour = "black", size = .5),
-   axis.ticks = element_line(size = .5),
-   axis.text.x = element_text(size = 12,
-                 angle = 0,
-                 face = "plain"),
-   axis.text.y = element_text(size = 12)
-  )
-
- if(r == 1){
-  Name_End = paste("Change_GB_26_2100.png")
- }else{
-  Name_End = paste("Change_GB_85_2100.png")
- }
-
- ggsave(Name_End,
-     plot = last_plot(),
-     width = 6,
-     height = 5,
-     units = "in",
-     path = Path)
-
-} # Close overall production loop
-
-### Proportion change gom
-
-#### Filter EEZs ###
-
-GB_Absolutes <- Atlantic_DBEM %>%
- mutate(RCP = ifelse(Model %in% c("GFDL26F1","IPSL26F1","MPI26F1"),"RCP 2.6","RCP 8.5")) %>% # Assigns RCP by model
- filter(Species %in% Atlantic_Species,
-     INDEX %in% GB_Coor$INDEX) %>% #Selects only IPHC species within regulatory areas
- left_join(EEZsID,
-      by = "INDEX") %>% 
- gather("Year","MCP",`2005`:`2099`) %>%
- group_by(RCP,Name,Year,Model,Species) %>%
- summarise(Total_MCP = sum(MCP, na.rm = T)) #%>% # Sums INDEX MCP per EEZ
- # group_by(RCP,Name,Year,Species) %>%
- # summarise(Mean_MCP = mean(Total_MCP, na.rm = T), #Yearly mean per ESM model
- #      SD_MCP = sd(Total_MCP, na.rm = )
- # )
-
-# Changes in the proportion in comparrison of the mean (2004-2014) proportion ####
-
-Proportion_Total <- GB_Absolutes %>% 
- group_by(RCP,Year,Species,Model) %>% 
- summarise(
-  Total = sum(Total_MCP)
- )
-
-# head(Proportion_Total)
-
-Proportion_Change <- GB_Absolutes %>% 
- left_join(Proportion_Total,
-      by = c("RCP","Year","Species","Model")) %>% 
- mutate(Proportion = (Total_MCP/Total)*100)
-
-Early_Proportion <- Proportion_Change %>% 
- filter(Year <= 2014) %>% 
- # group_by(RCP,
- #     Name) %>%
- group_by(RCP,Name,Species,Model) %>% # Species test
- summarise(Mean_Prop = mean(Proportion))
-
-Proportion_Change <- GB_Absolutes %>% 
- left_join(Proportion_Total,
-      by = c("RCP","Year","Species","Model")) %>% 
- mutate(Proportion = (Total_MCP/Total)*100) %>% 
- left_join(Early_Proportion,
-      by= c("RCP",
-         "Name",
-         "Species",
-         "Model")) %>% 
- mutate(Change = Proportion/Mean_Prop) %>% 
- mutate(Percentage = round(-(1-Change)*100,2)) %>% 
- arrange(RCP)
-
-#### The actual plot ####
-
-### Box plot ###
-
-PL <- Proportion_Change %>% 
- mutate(Time_Step = ifelse(Year >= 2046 & Year <= 2055,"Mid Century",
-              ifelse(Year >= 2089,"End Century","NA"))) %>% 
- filter(Time_Step == "Mid Century",
-     RCP == "RCP 2.6") %>% 
- ggplot(.,
-     aes(
-      # x = Species,
-       x = reorder(Species,Percentage, FUN = median), # from forcasts` package
-       # x = (Time_Step), # from forcasts` package
-       y = Percentage,
-       fill = Name
-     )
- ) +
- geom_boxplot() +
- ylab("") +
- xlab ("") +
- geom_hline(yintercept = 0, linetype = "dashed") +
- my_ggtheme_p()() +
-  ylim(-10, 10) +
-scale_fill_brewer("Region",palette = "Set2") + 
- geom_label(data=Proportion_Change, 
-       aes(label = "RCP 2.6",
-         x = "Melanogrammus aeglefinus", 
-         y = 10,
-         fill = NA), #RCP labels for grid plot
-       colour = "blue",
-       show.legend = FALSE,
-       size = 5,
-       hjust = 1.5
- ) +
- theme(legend.position = c(0.2, 0.98),
-    legend.direction = "horizontal",
-    axis.text.x = element_text(size = 10,
-                angle = 0,
-                face = "italic")
- )
-
-PH <- Proportion_Change %>%
- mutate(Time_Step = ifelse(Year >= 2046 & Year <= 2055,"Mid Century",
-              ifelse(Year >= 2089,"End Century","NA"))) %>% 
- filter(Time_Step == "Mid Century",
-     RCP == "RCP 8.5") %>% 
- ggplot(.,
-     aes(
-      # x = Species,
-       x = reorder(Species,Percentage, FUN = median), # from forcasts` package
-       # x = (Time_Step), # from forcasts` package
-       y = Percentage,
-       fill = Name
-     )
- ) +
- geom_boxplot() +
- ylab("") +
- xlab ("") +
- geom_hline(yintercept = 0, linetype = "dashed") +
- my_ggtheme_p()() +
- theme(
-     axis.text.x = element_text(size = 10,
-                angle = 0,
-                face = "italic")
- ) +
-scale_fill_brewer("Region",palette = "Set2",guide=FALSE) + 
- geom_label(data=Proportion_Change, aes(label = "RCP 8.5", x = "Melanogrammus aeglefinus", y = 10, fill = NA), #RCP labels for grid plot
-       colour = "red",
-       show.legend = FALSE,
-       size = 5,
-       hjust = 1.5
- )
-
-ggdraw() +
- draw_plot(PL, x = 0, y = 0.5, width = 1, height = 0.5) +
- draw_plot(PH, x = 0, y = 0, width = 1, height = 0.5) +
- draw_plot_label(label = c("A", "B"), size = 15,
-         x = c(0, 0), 
-         y = c(1, 0.5)) +
- draw_plot_label(label = "Stock-share percentage change",
-         size = 12, angle = 90, fontface = "plain",
-         x = 0.02,
-         y =0.11999)
-
-ggsave("Fig6.png",
-    plot = last_plot(),
-    width = 8,
-    height = 6,
-    units = "in",
-    path = Path)
-
-### Stock share ratio (/Table 2)
-
-SS_Changesp <- MCP_Species_Data %>% 
- group_by(RCP,Species,Period,Model) %>% 
- summarise(Total_MCP = sum(Mean_T_MCP)) %>% #Estimate todays's total (both EEZs added) MCP for each species 
- left_join(MCP_Species_Data) %>% # Inlude each nation's MCP
- mutate(Proportion = (Mean_T_MCP/Total_MCP)*100) %>% # estimates each Country's catch proportion per period
- select(-Total_MCP,-Basin,-Mean_T_MCP) %>% 
- group_by(Nation,RCP,Species,Period) %>% #Mean of all species
- summarise(Mean_Spp_Proportion =mean(Proportion),
-      sd_Spp_Proportion =sd(Proportion)
- ) %>% #Mean of all ESMs
- group_by(Nation,RCP,Period) %>% 
- summarise(Mean_ESM_Proportion = paste(round(mean(Mean_Spp_Proportion),2)," (",round(sd(Mean_Spp_Proportion),2),")",sep="")
- ) %>% 
- filter(Period %in% c("Mid_Century","The_End_Century")) %>% 
- spread(Period,Mean_ESM_Proportion)
-
-```
-
-```{r Figure_out_outliers, eval = F, echo = F}
-
-Outliers <- c(64310,64311,64312,65028,65029,67180,67181,69344,69345,70066)
-
-Environmental_Data_GoM <- read.csv("~/Documents/UBC/OC_Special_Issue/Ecol/Data/Environ/Environmental_Data_GoM.csv")
-
-Outlier_Species <- c(
- # "Gadus morhua", # Cod 600069, Demersal, 600 depth
- "Limanda ferruginea"#, # Yellowtail flounder 600521, Demersal 82 depth
- # "Melanogrammus aeglefinus" # Haddock 601381, Demersal 450
-)
-
-N_Lim <- 45.9759
-S_Lim <- 41
-W_Lim <- -72.0592
-E_Lim <- -63.33333
-
-### Averag depth data
-EleAvg <- read.table("~/Documents/UBC/OC_Special_Issue/Ecol/Data/Environ/EleAvg.txt", quote="\"", comment.char="") %>% 
- mutate(INDEX = seq(1,259200,1)) %>% 
- rename(Depth = V1) %>% 
- filter(INDEX %in% Atlantic_EEZsID$INDEX) %>% 
- left_join(Atlantic_EEZsID, by = "INDEX") %>% 
- filter( # Limit the area to George's bank
-  Latitude < N_Lim, # North
-  Latitude > S_Lim, # South 
-  Longitude > W_Lim, # West
-  Longitude < E_Lim
- ) %>% 
- mutate(
-  Outlier = ifelse(INDEX %in% Outliers,"Yes","No"),
-  Depth = ifelse(Depth <= -800,-800,
-          ifelse(Depth >=0,0,Depth))
- )
-
-elev_plot <-
-ggplot(EleAvg) +
- geom_tile(
-  aes(
-   x = Longitude,
-   y = Latitude,
-   # fill = log10(abs(Depth)),
-   fill = Depth
-  )
- ) +
- scale_fill_gradientn( "Depth (m)",
-  colours = terrain.colors(10),
-            limits=c(-1000,0),
-            breaks =seq(-1000,0,200)
- ) +
- geom_sf(data = GM_Land, colour = "lightgrey") +
- geom_sf(data = eez_GM, fill = NA) +
- coord_sf(xlim = c(-71.0592, -63.33333),
-      ylim = c(41,45.5)
- ) +
- my_ggtheme_m()() +
- theme(
-  axis.line = element_line(colour = "black", size = .5),
-  axis.ticks = element_line(size = .5),
-  axis.text.x = element_text(size = 8,
-                angle = 0,
-                face = "plain"),
-  axis.text.y = element_text(size = 8),
-  # legend.key = element_rect(size = 3),
-  legend.key.height = unit(2,"line"),
-  legend.title = element_text(size = 10),
-  legend.text = element_text(size = 10),
-  legend.position = "right"
- )
-
-Name = "Elevation_GoM.png"
-
-ggsave(Name,
-    plot = last_plot(),
-    width = 20,
-    height = 10,
-    units = "in",
-    path = Path)
-
-Specie <- "Limanda ferruginea"
-
-Enviro_chng_gom <- Environmental_Data_GoM %>% 
- mutate(# Indicate the three period times
-  Period = ifelse(Year >= Beg_In & Year <= Beg_End,"Beginning",
-          ifelse(Year >= Mid_In & Year <= Mid_End,"Mid_Century",
-              ifelse(Year >= End_In & Year <= End_End,"The_End_Century",
-                 "Other_Years"))
-  )
- ) %>% 
- filter(Period != "Other_Years",
-     Variable == "Temperature") %>% # Remove unwanted years
- group_by(INDEX,Model,RCP,Period,Variable) %>%
- summarise(
-  Mean_Temp = mean(Value, na.rm = T) # Temporal mean
- ) %>% 
- spread(Period,Mean_Temp) %>% 
- mutate_at(vars(Mid_Century, # Divide future values by present
-         The_End_Century),
-      funs(ifelse(Begining > 0, ./Begining,.)) #if no species today value is the future
- ) %>% 
- mutate_at(vars(Mid_Century, # Estimate percentage change
-         The_End_Century),
-      funs(ifelse(Begining == 0 & . == 0, 0, # If for no change than 0
-            ifelse(Begining == 0 & . > 0, 100, # If changes from 0 to anything then 100
-                round(-(1-.)*100) # Estimate percentage change
-            )
-      )
-      )
- ) %>% 
- ungroup() %>% 
- mutate(
-  Outlier = ifelse(INDEX %in% Outliers,"Yes","No"),
-  RCP = ifelse(RCP == "rcp26","Low Emission","High Emission")
- ) %>% 
- group_by(INDEX,RCP,Variable,Outlier) %>% 
- summarise(
-  Mean_Model = mean(Mid_Century,na.rm=T)
- ) %>% 
- left_join(Coor)
-
-temp_plot <- ggplot(Enviro_chng_gom) +
- geom_tile(
-  aes(
-   x = Longitude,
-   y = Latitude,
-   fill = Mean_Model
-  ),
-  size = 0.5
- ) +
- scale_fill_gradientn(paste("Percentage Change of bottom temperature\n           (",Mid_In,"-",Mid_End,")"), 
-            limits=c(3,18),
-            breaks =seq(3,18,3),
-            colours = terrain.colors(10)
- ) +
- geom_sf(data = GM_Land, colour = "lightgrey") +
- geom_sf(data = eez_GM, fill = NA) +
- coord_sf(xlim = c(-71.0592, -63.33333),
-      ylim = c(41,45.5)
-      ) +
- facet_wrap(~RCP) +
- my_ggtheme_m()() +
- theme(
-  axis.line = element_line(colour = "black", size = .5),
-  axis.ticks = element_line(size = .5),
-  axis.text.x = element_text(size = 8,
-                angle = 0,
-                face = "plain"),
-  axis.text.y = element_text(size = 8),
-  # legend.key = element_rect(size = 3),
-  legend.key.width = unit(2,"line"),
-  legend.title = element_text(size = 10),
-  legend.text = element_text(size = 10)
- )
-
-Name = "Temp_Cnhg_Mid_GoM.png"
-
-ggsave(Name,
-    plot = last_plot(),
-    width = 6,
-    height = 4,
-    units = "in",
-    path = Path)
-
-###### Elevation and temperature plots
-
-temp_ele <- grid.arrange(elev_plot,temp_plot,
-       ncol = 1)
-
-Name = "Temp_ele_GoM.png"
-
-ggsave(Name,
-    plot = temp_ele,
-    width = 6,
-    height = 6,
-    units = "in",
-    path = Path)
-
-#### Make maps PER model
-
-#### New analysis ####
-Per_Model_Chng_GoM <- Atlantic_DBEM %>% 
- mutate(RCP = ifelse(Model %in% c("GFDL26F1","IPSL26F1","MPI26F1"),"Low Emission","High Emission")) %>%
- tidyr::gather("Year","Change",`2005`:`2099`) %>%
- mutate(Change = replace_na(Change, 0)) %>% # Convert NA's into 0's
- mutate(# Indicate the three period times
-  Period = ifelse(Year >= Beg_In & Year <= Beg_End,"Beginning",
-          ifelse(Year >= Mid_In & Year <= Mid_End,"Mid_Century",
-              ifelse(Year >= End_In & Year <= End_End,"The_End_Century",
-                 "Other_Years"))
-  )
- ) %>% 
- filter(Period != "Other_Years",
-     Species %in% Outlier_Species) %>% # Remove unwanted years
- group_by(INDEX,Model,RCP,Period,Species) %>%
- summarise(
-  Mean_Temp = mean(Change, na.rm = T) # Temporal mean
- ) %>% 
- spread(Period,Mean_Temp) %>% 
- mutate_at(vars(Mid_Century, # Divide future values by present
-         The_End_Century),
-      funs(ifelse(Begining > 0, ./Begining,.)) #if no species today value is the future
- ) %>% 
- mutate_at(vars(Mid_Century, # Estimate percentage change
-         The_End_Century),
-      funs(ifelse(Begining == 0 & . == 0, 0, # If for no change than 0
-            ifelse(Begining == 0 & . > 0, 100, # If changes from 0 to anything then 100
-                round(-(1-.)*100) # Estimate percentage change
-            )
-      )
-      )
- )%>% 
- mutate(
-  Outlier = ifelse(INDEX %in% Outliers,"Yes","No")
- ) %>% 
- left_join(Coor) %>% 
- mutate_at(vars(Mid_Century,
-         The_End_Century),
-      funs(ifelse(. > 100, 100,.)
-      ) # set everything over 100 to 100
- ) #%>% 
- # filter(Outlier == "Yes")
-
-# plot results 
-ggplot(Per_Model_Chng_GoM) +
- geom_tile(
-  aes(
-   x = Longitude,
-   y = Latitude,
-   fill = Mid_Century,
-   # fill = log10(abs(Mid_Century)),
-   color = Outlier
-   # fill = Depth
-  ),
-  size = 0.5
- ) +
- scale_fill_gradient2(paste("MCP Percentage Change of",Outlier_Species,"\n           (",Mid_In,"-",Mid_End,")"), # If not using the bins
-            limits=c(Lim_Neg,
-                Lim_Max),
-            breaks = Seq,
-            na.value = 'darkred' # NA values are present when the species is no more 
- ) +
- scale_color_manual(values=c(NA,"yellow")) + # for Bins option A
- geom_sf(data = GM_Land, colour = "lightgrey") +
- coord_sf(xlim = c(-71.0592, -63.33333),
-      ylim = c(41,45.5)
- ) +
- facet_wrap(~RCP+Model) +
- my_ggtheme_m()() +
- theme(legend.key.width =unit(6,"line"))
-
-Name = "MCP_Cnhg_Mid_GoM_Outlier.png"
-
-ggsave(Name,
-    plot = last_plot(),
-    width = 14,
-    height = 10,
-    units = "in",
-    path = Path)
-
-#### Check those outliers in the GFDL
-
-GFDL_Out <- Atlantic_DBEM %>% 
- filter(Model == "GFDL26F1",
-     Species %in% Outlier_Species,
-     INDEX %in% Outliers) %>%
- tidyr::gather("Year","Change",`2005`:`2099`) %>%
- # mutate(Change = replace_na(Change, 0)) %>% # Convert NA's into 0's
- mutate(# Indicate the three period times
-  Period = ifelse(Year >= Beg_In & Year <= Beg_End,"Beginning",
-          ifelse(Year >= Mid_In & Year <= Mid_End,"Mid_Century",
-              ifelse(Year >= End_In & Year <= End_End,"The_End_Century",
-                 "Other_Years"))
-  )
- ) %>% 
- filter(Period != "Other_Years") %>% # Remove unwanted years
- group_by(INDEX,Model,Period,Species) %>%
- summarise(
-  Mean_Temp = mean(Change, na.rm = T) # Temporal mean
- ) %>% 
- spread(Period,Mean_Temp) %>% 
- mutate(
-  Mid_Chng = ifelse(Begining > 0, Mid_Century/Begining,Mid_Century),
-  End_Chng =ifelse(Begining > 0, The_End_Century/Begining,The_End_Century)
- ) %>% 
- mutate_at(vars(Mid_Chng, # Estimate percentage change
-         End_Chng),
-      funs(ifelse(Begining == 0 & . == 0, 0, # If for no change than 0
-            ifelse(Begining == 0 & . > 0, 100, # If changes from 0 to anything then 100
-                round(-(1-.)*100) # Estimate percentage change
-            )
-      )
-      )
- )
-
-####Plot Time hisotry o
-
-GFDL_Hist_Out <- Atlantic_DBEM %>% 
- filter(Model == "GFDL26F1",
-     Species %in% Outlier_Species,
-     INDEX %in% Outliers) %>%
- tidyr::gather("Year","Change",`2005`:`2099`) %>%
- # mutate(Change = replace_na(Change, 0)) %>% # Convert NA's into 0's
- mutate(# Indicate the three period times
-  Period = ifelse(Year >= Beg_In & Year <= Beg_End,"Beginning",
-          ifelse(Year >= Mid_In & Year <= Mid_End,"Mid_Century",
-              ifelse(Year >= End_In & Year <= End_End,"The_End_Century",
-                 "Other_Years"))
-  )
- ) %>% 
- mutate(Change = replace_na(Change, 0))
-
-ggplot(GFDL_Hist_Out) +
- geom_line(
-  aes(
-   x = as.numeric(Year),
-   y= Change,
-   color = as.character(INDEX)
-  )
- ) +
- facet_wrap(~INDEX)
-
-```
-
-<!-- # OLD TEXT -->
-
- <!-- As climate change alters the sharing of fish stocks between countries to an extent that is beyond historical changes, existing policies and governance structures may not be able to cope with these changes [@Pinsky:2012kq].
-Consequently, countries may not be satisfied with the sharing or allocation of access to resources, leading to international disputes [@Pinsky:2018cb].
--->
-
-<!-- It has been suggested that agreements that make cooperation the preferred strategy for all players are stronger.
-However, the level of government at which negotiations are held can directly impact management outcomes, as unofficial agreements might lack proper penalties for non-cooperative behavior [@Miller:2013iv].
-In this sence the GoM agreement covers itself quite well.
-In one hand, the informal quota allocation method has managed to ease tensions between neighbouring countries, implement a share allocation that addresses shifts in species distributions.
-While in the other hand, the official enforcement agreement signed by the governments of Canada and the US [@GovermentofCanada:l5W8_7Lz] has helped reduce illegal fishing in the border [@Pudden:2007bo].
-However, despite the quota suggestions under the GoM agreement are done internationally, Canada and the US ultimately set the quota domestically [@Pudden:2007bo].
-In this sence, the agreement might not be resilient to climate-induced shifts members are not bonded to any rule.
-Officiating treaties like the case of the Gulf of Maine could provide better ground for the management rules and increase treaty resilience and capacity to adapt to unpredictable changes [@Miller:2013iv].
-Changes in the distribution of shared stocks have created tension between countries [@Spijkers:2017ij] including Canada and the US in the case of the Pacific salmon [@Miller:2013iv; @Munro:2002uf; @Song:2017va].
--->
-
-<!-- On the Atlantic coast, Canada and the US are parties to Northwest Atlantic Fisheries Organization (NAFO), which oversees the management of 19 stocks of 11 species, some of which traverse Canada’s EEZ and the Regulatory Area outside the EEZ (although around 41 taxa are fished within Canadian and US.
-waters from the southern Gulf of Maine to Greenland) [^NAFO].
-On the Pacific coast, Pacific halibut (*Hippoglossus stenolepis*) is managed under the International Pacific Halibut Commission (IPHC) [@IPHCSecreatriat:2017uz].
-All five salmon species (chinook, *Oncorhynchus tshawytscha*; chum, *O.
-keta*; coho, *O.
-kisutch*; pink, *O.
-gorbuscha*; and sockeye *O.
-nerka*), are managed by the Pacific Salmon Commission [@PSC:2017tb].
-Finally, under the Pacific Whiting Treaty, Canada and the United states jointly manage the coastal stock of this Pacific hake species (*Merluccius productus*) [@Merten:2015tu].
--->
-
- <!-- Disputes over Pacific salmon between Canada and the US arose in the 1990s because of climate-related changes in stock abundance and migratory behavior [@Miller:2013iv; @Munro:2002uf; @Song:2017va].
-Currently, Europe is involved in an unsolved dispute over *Scomber scombrus* known as the "mackerel wars".
-The conflict erupted in 2007 when the stock shifted their distribution from the Norwegian Sea towards northern and western regions of the Nordic Seas, consequently spreading into Iceland's national waters [@Spijkers:2017ij].
--->
-
-<!-- Transboundary fisheries are defined as those fishing stocks that move freely between (*i*) Countries economic exclusive zones (EEZs) and (*ii*) between EEZs and the high seas ( called transboundary stocks) [@Song:2017iua].
-Game theory is one of the most common approaches used to analyze the management of transboundary stocks, as often, success depends on effective cooperation between parties [@Munro:2002uf; @Sumaila:2013hv].
-Therefore, in DV 1982, the United Nations incentivized actions to cooperate on the management of transboundary stocks through the Law of the Seas (UNCLOS) [@UnitedNations:1986tl].
--->
-
-<!-- While in 2050, the average shift of species will be higher for East Canada and lower for East US under the high emission scenario, the stock-share ratio of some species is expected to increase more than 50% as in the case of Atlantic menhaden (*Brevoortia tyrannus*) in Eastern Canada, and decrease by more than 50% for species such as Cusk (*Brosme brosme*) in the Eastern US under a low emission scenario.
-By the end of the $21^{st}$ century, losses will intensify with the eastern US potentially losing on average 15.2% or 46% of stock-share, depending on the scenario.
--->
-
-<!-- Another example is the Nauru Agreement (PNA), responsible for managing the world's largest sustainable skipjack tuna (*Katsuwonus pelamis*) purse seine fishery [^PNA].
-The PNA has a system of internationally tradable fisheries access that allows members to adapt to the effects of the El Niño Southern Oscillation [@Aqorau:2018bh].
-While this is a good way to address climate variation within members of a treaty, it might fall short to address the newcomer issue, a situation that can threaten the sustainability of the stock [@Pinsky:2018cb].
-A combination of the methods employed by PNA with the proper modification to incorporate new fishing nations could help mitigate future conflicts in stocks like the Pacific halibut.
-Finally, -->
-<!-- [^PNA]: The Parties to the Nauru Agreement (PNA), available at http://www.pnatuna.com/ -->
-
-<!-- In the current paper we follow a modeling approach to explore the potential impacts that climate change will have in the management of transboundary stocks in North America.
-Models are attempts to represent reality (in our case a future reality) based on observational data, previously established theory, and future scenarios, and are thus, subjected to different degrees of uncertainty [@Payne:2016gn].
-First, our study incorporates multiple earth system models to project the future distribution of transboundary stocks while accounting the structural uncertainty built within each ESM [@Bopp:2013fg].
-In terms of the structural uncertainty build within the DBEM, previous analysis shown that the trends of changes in MCP are not affected by its structural uncertainty [@Cheung:2016jd].
-Secondly, scenario planning has been widely used in climate change studies as a method to account for the uncertainty build in future decision making [@vanVuuren:2011ef].
-In this aspect we considered two extreme RCPs that comprises the vast spectrum of possibilities proposed by the IPCC [@IPCC:2014bz].
-A lower-than-2.6 RCP (1.5º warming) was discussed at the recent Paris Agreement sessions celebrated in Paris France.
-While we did not include this scenario in our analysis, previous research suggest that stronger mitigation efforts would bring large benefits to fisheries [@Cheung:2016tt].
-Finally, future changes to species distributions could be influenced by interactions between species [@Pecl:2017hu], adaptation of species to environmental changes, and anthropogenic factors [@Serpetti:2017he].
-However, these factors are expected to increase the rate of range-shifting of the species making our results conservative [@Cheung:2010dt; @Serpetti:2017he].
--->
-
-<!-- Poleward shifts in Eastern Atlantic off the coast of the US include American lobster (*Homarus americanus*), summer (*Paralichthys dentatus*) and flounders, and red hake (*Urophycis chuss*) from North Carolina to Maine [@Pinsky:2012kq].
--->
-<!-- Species such as haddock in the Atlantic [@Morley:2018fn], and big skate (*Raja binoculata*) in the Pacific coast [@Pinsky:2013ab] have been projected to shift away from the poles. -->
-
-```{r Treaties_Table, eval = F, echo = F}
-
-# Foot note
-fn <- "*These species are also part of NAFO. This is an arrangement and not an official agreement between parties."
-
-data.table::data.table(Treaty =
-             c("International Pacific Halibut Commission (IPHC)",
-              "Pacific Salmon Commission (PSC)",
-              "Pacific Whiting Treaty (PWT)",
-              "Northwest Atlantic Fisheries Organization (NAFO)",
-              "Gulf of Maine's Arrangement (GoMA)"),
-            Species =
-             c(1,
-              5,
-              1,
-              26,
-              "3*"),
-            Coast =
-             c("Pacific",
-              "Pacific",
-              "Pacific",
-              "Atlantic",
-              "Atlantic")
-) %>% 
- kable("latex",
-    caption = "Treaties and number of species included in the current analysis."
-    ) %>% 
- add_footnote(fn)
-```
-
-<!-- # Option removing NAFO -->
-<!-- ### North American transboundary stocks are shifting poleward -->
-
-```{r Changes_Data_All, eval = F, echo = F, fig.height=8, fig.width=12}
-
-# Change North America Projection for Map
-
-North_America_Land <- North_America_Land %>% 
- st_transform(crs = 4326)
-
-### Load shapefile the old way ###
-
-# Path to save the plots
-Path <- my_path("R",Extra_Path = "North_America")
-RCP = c("GFDL26F1","IPSL26F1","MPI26F1") #Low RCP
-
-#### New Future Method to account for mean +- sd of models #
-MCP_Data <- DBEM_Corrected %>% 
-  mutate(RCP = ifelse(Model %in% RCP,"Low_Emission","High_Emission")) %>% 
-  # Sum the MCP of all species in each index by model
-  group_by(INDEX,
-           Model,
-           RCP) %>% 
-  summarise_at(vars(Beg_In:End_End), sum,na.rm=T) %>% 
-  gather("Year","MCP",Beg_In:End_End) %>% 
-  # Indicate the three period times
-  mutate( 
-    Period = ifelse(Year >= Beg_In & Year <= Beg_End,"Beginning",
-                    ifelse(Year >= Mid_In & Year <= Mid_End,"Mid_Century",
-                           ifelse(Year >= End_In & Year <= End_End,"The_End_Century",
-                                  "Other_Years"))
-    )
-  ) %>% 
-  #Average per Time period
-  group_by(INDEX,Model,RCP,Period) %>% 
-  summarise(Mean_T_MCP =mean(MCP,na.rm=T)) %>% 
-  filter(Period != "Other_Years") %>% 
-  spread(Period,Mean_T_MCP) %>% #Spread to estimate MCP_Change
-  # Divide future values by present
-  mutate_at(vars(Mid_Century, 
-                 The_End_Century),
-            funs(ifelse(Begining > 0, ./Begining,.)) #if no species today value is the future
-  ) %>% 
-  # Estimate percentage change
-  mutate_at(vars(Mid_Century, 
-                 The_End_Century),
-            funs(ifelse(Begining == 0 & . == 0, 0, # If for no change than 0
-                        ifelse(Begining == 0 & . > 0, 100, # If changes from 0 to anything then 100
-                               round(-(1-.)*100) # Estimate percentage change
-                        )
-            )
-            )
-  ) %>% 
-  gather("Period","MCP_Change",Mid_Century,The_End_Century) %>% 
-  mutate(Direction = ifelse(MCP_Change >= 0, "Positive","Negative")) %>% 
-  # Average results per ESMs
-  group_by(INDEX,Period,RCP) %>% 
-  summarise_at(vars(MCP_Change),
-               funs("Mean_ESM_MCP_Chng"=mean,
-                    "sd_ESM_MCP_Chng"=sd,
-                    "N_ESMs"=n(),
-                    "Model_Agreement" = paste(length(unique(Direction)),collapse = ";")
-               )
-  ) %>%
-  mutate(
-    Model_Agreement = ifelse(Model_Agreement == 1, "Agree","Disagree"),
-    Model_Agreement_sd = ifelse(abs(Mean_ESM_MCP_Chng) < sd_ESM_MCP_Chng*2,"Disagree","Agree")
-  ) %>% 
-  left_join(DBEM_Coor,
-            by="INDEX") %>% 
-  # set everything over 100 to 100
-  mutate_at(vars(Mean_ESM_MCP_Chng,
-                 sd_ESM_MCP_Chng),
-            funs(ifelse(. > 100, 100,.)
-            )
-  )
-
-# Plot map for paper figure 
-Seq <- seq(-100,100,by=5) #Axis
-
-p <- ggplot(MCP_Data) +
- geom_tile(data = subset(MCP_Data, Period == "Mid_Century"),
-      aes(
-       x = longitude,
-       y = latitude,
-       color = Mean_ESM_MCP_Chng,
-       fill = Mean_ESM_MCP_Chng
-      )
- ) +
- geom_point(data = subset(MCP_Data, Period == "Mid_Century" & Model_Agreement == "Disagree"),
-       aes(
-        x = longitude,
-        y = latitude
-       ),
-       size = 0.1,
-       # alpha = 0.5,
-       shape = 16,
-       color = "grey20"
-       ) +
- geom_sf(data = North_America_Land, fill = "grey90") +
- facet_wrap(~RCP) +
- coord_sf(xlim = c(-190,-50)) +
- scale_color_gradient2(
-  limits=c(-100,
-       100),
-  breaks = Seq) +
- scale_fill_gradient2(
-  limits=c(-100,
-       100),
-  breaks = Seq) +
- my_ggtheme_m()()
-
- ggsave("Fig2.png",
-     plot = p,
-     width = 16,
-     height = 8,
-     units = "in",
-     path = Path)
-
-```
-
-<!-- # Option removing NAFO -->
-<!-- Shifts in the distribution of 33 jointly managed transboundary stocks of North America by 2050 relative to 2010 show that MCP of transboundary stocks will overall increase in Atlantic-Canadian and Alaskan waters and decrease in Pacific-Canadian and the US contiguous states waters (Figure \ref{fig:Figure2-IPHC}).
-Such changes will be more intense under the high emission scenario (Fig.
-2A).
-For most regions, losses of MCP will be more intense under a high emission scenario (Fig.2A) than under a low emission scenario (Fig.2B), however, there will be no apparent change in gain intensity between scenarios.
-Impacts of climate change are expected to intensify towards the end of the $21^{st}$ century, although with greater uncertainty (Fig.A1.1).
--->
-
-<!-- ![Fig.
-2.
-Percentage change of MCP of transboundary stocks of North America for mid $21^{st}$ century (2041-2060) relative to present (2005-2014) under a A) high emission scenario and; B) low emission scenario.
-Points represent areas where at least one model do not agree in the direction of change](./Figures/Figure 2.png) -->
-
-```{r Changes_Per_Species_T, eval = F, echo = F }
-
-# This table provides the percentage change in MCP for each species, EEZ and RCP as well as the percentage change in Stock-share ratio.
-
-#### Mid Century result Table ####
-Areas <- c(
- "Canada (East Coast)",
- "Canada (Pacific)",
- "USA (East Coast)",
- "USA (West Coast)",
- "USA (Alaska, Arctic)",
- "USA (Alaska, Subarctic)"
-)
-
-RCP <- c("GFDL26F1","IPSL26F1","MPI26F1")
-
-Selected_Areas <- EEZIDs_List %>% 
- filter(Name %in% Areas)
-
-#### NEW ESTIMATES
-
-# Path to save the plots
-Path <- my_path("R",Extra_Path = "North_America")
-RCP = c("GFDL26F1","IPSL26F1","MPI26F1") #Low RCP
-
-# Aggregate MCP per Nation, Species, Model, RCP and Time period
-
-MCP_Species_Data <- DBEM_Corrected %>% 
-  left_join(EEZ_CellID,
-            by = "INDEX") %>% 
-  filter(EEZID %in% Selected_Areas$EEZID) %>% 
-  mutate(RCP = ifelse(Model %in% RCP,"Low_Emission","High_Emission"),
-         Nation = ifelse(EEZID >= 958, "Alaska",
-                         ifelse(EEZID == 925,"Can W",
-                                ifelse(EEZID == 851, "USA E",
-                                       ifelse( EEZID== 848, "USA W",
-                                               "Can E"))
-                         )),
-         Basin = ifelse(Nation %in% c("USA E","Can E"),"Atlantic","Pacific"),
-  ) %>% 
-  # Sum the MCP of each species by country
-  group_by(Species, Model, RCP, Nation, Basin) %>%
-  summarise_at(vars(Beg_In:End_End), sum,na.rm=T) %>% 
-  gather("Year","MCP",Beg_In:End_End) %>% 
-  mutate( # Indicate the three period times
-    Period = ifelse(Year >= Beg_In & Year <= Beg_End,"Beginning",
-                    ifelse(Year >= Mid_In & Year <= Mid_End,"Mid_Century",
-                           ifelse(Year >= End_In & Year <= End_End,"The_End_Century",
-                                  "Other_Years"))
-    )
-  ) %>% 
-  # Average by time period
-  group_by(Nation,Basin,Species,Model,RCP,Period) %>% 
-  summarise(Mean_T_MCP =mean(MCP,na.rm=T))
-
-### Estimate average change of all species ####
-
-MCP_Species_Change <- MCP_Species_Data %>% 
-  filter(Period != "Other_Years") %>% 
-  spread(Period,Mean_T_MCP) %>% #Spread to estimate MCP_Change
-  # Divide future values by present
-  mutate_at(vars(Mid_Century, 
-                 The_End_Century),
-            funs(ifelse(Begining > 0, ./Begining,.)) #if no species today value is the future
-  ) %>% 
-  # Estimate percentage change
-  mutate_at(vars(Mid_Century, 
-                 The_End_Century),
-            funs(ifelse(Begining == 0 & . == 0, 0, # If for no change than 0
-                        ifelse(Begining == 0 & . > 0, 100, # If changes from 0 to anything then 100
-                               round(-(1-.)*100) # Estimate percentage change
-                        )
-            )
-            )
-  ) %>% 
-  gather("Period","MCP_Change",Mid_Century,The_End_Century) %>% 
-  mutate(Direction = ifelse(MCP_Change >= 0, "Positive","Negative")) %>% 
-  # Average results per ESMs
-  group_by(Nation,Species,Period,RCP) %>% 
-  summarise_at(vars(MCP_Change),
-               funs("Mean_ESM_MCP_Chng"=mean,
-                    "sd_ESM_MCP_Chng"=sd,
-                    "N_ESMs"=n(),
-                    "Model_Agreement" = paste(length(unique(Direction)),collapse = ";")
-               )
-  ) %>%
-  mutate(
-    Model_Agreement = ifelse(Model_Agreement == 1, "Agree","Disagree")
-  ) %>% 
-  # set everything over 100 to 100
-  mutate_at(vars(Mean_ESM_MCP_Chng,
-                 sd_ESM_MCP_Chng),
-            funs(ifelse(. > 100, 100,.)
-            )
-  )
-
-#### Estimate Stock Share Change ####
-
-# Estimate total MCP of all species per basin
-Basin_Total <- MCP_Species_Data %>% 
-  group_by(Basin,Model,RCP,Period) %>% 
-  summarise(TB_MCP = sum(Mean_T_MCP))
-
-# Stock Share Change per EEZ
-SS_Change <- MCP_Species_Data %>% 
-  group_by(RCP,Period,Model,Nation,Basin) %>% # Estimate total MCP of all species per Nation 
-  summarise(Total_MCP = sum(Mean_T_MCP)) %>% 
-  left_join(Basin_Total,
-            by = c("RCP", "Period", "Model","Basin")) %>% 
-  mutate(Proportion = (Total_MCP/TB_MCP)*100) %>% # estimates each Country's catch proportion per period and RCP
-  group_by(Nation,RCP,Period) %>%  # Average ESMs
-  summarise(Mean_ESM_Proportion = paste(round(mean(Proportion),2)," (",round(sd(Proportion),2),")",sep="")
-  ) %>% 
-  filter(Period %in% c("Beginning","Mid_Century","The_End_Century")) %>% 
-  spread(Period,Mean_ESM_Proportion)
-
-Path <- my_path("R",Extra_Path = "North_America")
-
-#For paper (Table 2)
-write.csv(SS_Change,
-     paste(Path,"SS_Change.csv",sep=""),
-     row.names = F)
-
-```
-
-<!-- Consequently, each country’s share-ratio of different species will change with an overall benefit to northern regions, regardless of the RCP scenario.
-Overall, shifts will be amplified under the high emission scenario relative to the low greenhouse emission scenario pathway (Table 2).
--->
-
-<!-- Table 2.
-Total stock-share of all 33 transboundary species by EEZ and emission scenario for the present, and mid and end of the $21^{st}$ century.
-Averages might not add to 100% due to model differences.
-Standard deviation of the projected values are provided in parentheses.
--->

### 2020-11-25 Ecol/Manuscript_Draft.Rmd
typos and we for I

@@
 As a result, some countries or management jurisdictions may see more shared fisheries and their catches shifting into their waters while others will stand to lose [@Oremus:2020id; @Pinsky:2018cb].
-Nevertheless, management rules for shared stocks (e.g.
-quota or spatial delimitation) are often determined based on current and/or historic knowledge of the stock's distribution and do not consider future shifts in distributions [@FredstonHermann:2018kp].
+Nevertheless, management rules for shared stocks (e.g., quota or spatial delimitation) are often determined based on current and/or historic knowledge of the stock's distribution and do not consider future shifts in distributions [@FredstonHermann:2018kp].
 
@@
 Therefore, the main objective of this article is to assess the level of exposure that bi-lateral transboundary fisheries treaties between Canada and the US have to climate change through shifts in stock distributions.
-Specifically, we rely on a species distribution model and scenario planning to project the changes in the distribution of selected fish stocks jointly managed by Canada and the United States focusing on two case studies (the International Pacific Halibut Commission and a fisheries arrangement for the Gulf of Maine) Finally, we explore similar situations around the world and identify opportunities to improve the adaptability of transboundary stocks management to climate change in North America.
-Despite an overall expectation of species following a poleward shift, important geographic constraints (e.g.
-Gulf of Alaska representing a latitudinal block) [@Kleisner:2016je], geo-political features (e.g.
-the localization of Alaska in reference to Canada and the contiguous states), and management rules (e.g.
-quota allocations, spatial management rules) may play an important role in the redistribution of benefits.
+Specifically, I rely on a species distribution model and scenario planning to project the changes in the distribution of selected fish stocks jointly managed by Canada and the United States focusing on two case studies (the International Pacific Halibut Commission and a fisheries arrangement for the Gulf of Maine) Finally, I explore similar situations around the world and identify opportunities to improve the adaptability of transboundary stocks management to climate change in North America.
+Despite an overall expectation of species following a poleward shift, important geographic constraints (e.g., Gulf of Alaska representing a latitudinal block) [@Kleisner:2016je], geo-political features (e.g., the localization of Alaska in reference to Canada and the contiguous states), and management rules (e.g., quota allocations, spatial management rules) may play an important role in the redistribution of benefits.
 Understanding these stocks shifts will shed a light on future conditions and inform decision-makers on the paths to follow under a changing climate.
@@
 
-The current study used the International Pacific Halibut Commission (IPHC) and the Gulf of Maine arrangement (hereafter referred as GoMA) as case studies to discuss the implications that climate change could have in the management of transboundary stocks.
-For the IPHC, we used the most updated spatial regulatory data along its 12 regulatory areas [@IPHCSecreatriat:2017uz; @IPHC:2019wt].
-For this specific case, we considered Alaska as a separate entity, the US contiguous states as a second one (Washington, Oregon and California), and lastly British Columbia (Canada).
-For the GoMA we used the Northwest Atlantic Fisheries Organization's (NAFO) divisions 5Y, 5Ze, and 4X[^NAFO] within latitudes 46.2°N and 41.5°S, and longitudes -72°W and -64°E (Figure \ref(fig:ocFigure1-map)).
+The current study used the International Pacific Halibut Commission (IPHC) and the Gulf of Maine arrangement (hereafter referred as GoMa) as case studies to discuss the implications that climate change could have in the management of transboundary stocks.
+For the IPHC, I used the most updated spatial regulatory data along its 12 regulatory areas [@IPHCSecreatriat:2017uz; @IPHC:2019wt].
+For this specific case, I considered Alaska as a separate entity, the US contiguous states as a second one (Washington, Oregon and California), and lastly British Columbia (Canada).
+For the GoMa I used the Northwest Atlantic Fisheries Organization's (NAFO) divisions 5Y, 5Ze, and 4X[^NAFO] within latitudes 46.2°N and 41.5°S, and longitudes -72°W and -64°E (Figure \@ref(fig:ocFigure1)).
 Is worth mention that, while NAFO's divisional zones were used in this study for domestic management, NAFO does not manage fisheries within the EEZs of Canada and the United States.
-Fisheries data fpr the projections was gathered from the Sea Around Us from 1951 to 2014 [@Zeller2016].
+Fisheries data for the projections was gathered from the Sea Around Us from 1951 to 2014 [@Zeller2016].
 
@@
 
-```{r ocFigure1-map, eval = T, echo=FALSE, fig.height = 4, fig.width = 6, fig.cap="Map of Canada and the US with the regulatory areas of the International Pacific Halibut Commission and the NAFO sub-divisions containing the Gulf of Maine arrangement"}
+```{r ocFigure1, eval = T, echo=FALSE, fig.height = 4, fig.width = 6, fig.cap="Map of Canada and the US with the regulatory areas of the International Pacific Halibut Commission and the NAFO sub-divisions containing the Gulf of Maine arrangement"}
 
@@
 Since 1998 Canada and the US have used a "Resource Sharing Understanding" to inform the management of Eastern George Bank's Atlantic cod (*Gadus morhua*) and haddock (*Melanogrammus aeglefinus*) and, yellowtail flounder (*Limanda ferruginea*) [@Pudden:2007bo; @TRAC:2016wu; @Song:2017va].
-From 2010 onward, the GoMA suggests catch-limits based on a weighted method where 10% represents the stocks’ historical distribution (from 1967 to 1994) and 90% current distributions produced by quarterly surveys and catch [@TRAC:2016wu].
-Since its introduction, the average quota allocation for each species proposed by the GoMA has been (Table \@ref(tab:ocTable1); Atlantic cod 77% Canada and 23% US, haddock 55% Canada and 45% US, and yellowtail flounder 34% Canada and 66% US [@TRAC:2015wj; @TRAC:2015vp; @TRAC:2015tt; @TRAC:2018tw; @TRAC:2018tj; @TRAC:2018wx; @Trinko:2019ou].
+From 2010 onward, the GoMa suggests catch-limits based on a weighted method where 10% represents the stocks’ historical distribution (from 1967 to 1994) and 90% current distributions produced by quarterly surveys and catch [@TRAC:2016wu].
+Since its introduction, the average quota allocation for each species proposed by the GoMa has been (Table \@ref(tab:ocTable1); Atlantic cod 77% Canada and 23% US, haddock 55% Canada and 45% US, and yellowtail flounder 34% Canada and 66% US [@TRAC:2015wj; @TRAC:2015vp; @TRAC:2015tt; @TRAC:2018tw; @TRAC:2018tj; @TRAC:2018wx; @Trinko:2019ou].
 However, because this is an unofficial agreement, Canada and the US ultimately take single management decisions [@Soboil:2006gw].
@@
 
-We used a Dynamic Bioclimatic Envelope Model (DBEM) to project the distribution of species from 2015 to 2100 under two scenarios of climate change [@Cheung:2010dt; @Cheung:2016jd].
+I used a Dynamic Bioclimatic Envelope Model (DBEM) to project the distribution of species from 2015 to 2100 under two scenarios of climate change [@Cheung:2010dt; @Cheung:2016jd].
 The DBEM algorithm integrated ecophysiology and habitat suitability with spatial population dynamics of exploited fishes and invertebrates to project shifts in abundance and potential fisheries catches under climate change.
@@
 
-We projected the DBEM using three Earth system models (ESM), the Geophysical Fluid Dynamics Laboratory Earth System Models 2M (GFDL)[^GFDL], the Institute Pierre Simon Laplace Climate Model 5 (IPSL-CM5)[^IPSL], and the Max Planck Institute for Meteorology Earth System Model (MPI)[^MPI].
+I projected the DBEM using three Earth system models (ESM), the Geophysical Fluid Dynamics Laboratory Earth System Models 2M (GFDL)[^GFDL], the Institute Pierre Simon Laplace Climate Model 5 (IPSL-CM5)[^IPSL], and the Max Planck Institute for Meteorology Earth System Model (MPI)[^MPI].
 Each model was downscaled to match the DBEM $0.5^{\circ}$ x $0.5^{\circ}$ grid using the nearest neighbor method, and in some cases, bilinear interpolation [@Cheung:2016hf].
-Finally, we used the model outputs for two scenarios of the Intergovernmental Panel on Climate Change (IPCC)-Representative Concentration Pathways (RCP) 2.6 and 8.5 representing a low greenhouse gas emission (strong mitigation) and a high greenhouse gas emission (week mitigation) scenario, respectively [@IPCC:2014bz].
-To estimate model robustness and capture the structural uncertainty build within ESM models, we averaged the DBEM results for all three models ($\mu \pm \sigma$) and marked regions where at least one ESM disagree in direction with the rest.
+Finally, I used the model outputs for two scenarios of the Intergovernmental Panel on Climate Change (IPCC)-Representative Concentration Pathways (RCP) 2.6 and 8.5 representing a low greenhouse gas emission (strong mitigation) and a high greenhouse gas emission (week mitigation) scenario, respectively [@IPCC:2014bz].
+To estimate model robustness and capture the structural uncertainty build within ESM models, I averaged the DBEM results for all three models ($\mu \pm \sigma$) and marked regions where at least one ESM disagree in direction with the rest.
 
@@
 
-For estimating the percentage change of MCP at the regional scale, we first aggregated the yearly mean MCP of all gridcells per region ($X_{yr}$) and period:
+For estimating the percentage change of MCP at the regional scale, I first aggregated the yearly mean MCP of all grid cells per region ($X_{yr}$) and period:
 
@@
 \begin{equation}
-\label{eq:one}
+\label{eq:ocone}
 X_{yr} = \sum_{s = 1}^n \hat{MCP_s}
@@
 where *y* is year, *r* is region, *s* is species, *n* is total number of species, and $\hat{MCP}$ is the MCP averaged by the three ESMs.
-In the case of the GoMA, region was defined as the $0.5^{\circ}$ x $0.5^{\circ}$ grid-cell within the specific NAFO divisional zones.
-For the IPHC analysis, region was defined as the Commission's regulatory areas (Figure \ref(fig:ocFigure1-map)).
-We then averaged the values in three time periods (*t*) to reduce temporal model sensitivity.
-Thus, we computed the regional percentage change in MCP ($\Delta MCP$) as follows:
+In the case of the GoMa, region was defined as the $0.5^{\circ}$ x $0.5^{\circ}$ grid-cell within the specific NAFO divisional zones.
+For the IPHC analysis, region was defined as the Commission's regulatory areas (Figure \@ref(fig:ocFigure1)).
+I then averaged the values in three time periods (*t*) to reduce temporal model sensitivity.
+Thus, I computed the regional percentage change in MCP ($\Delta MCP$) as follows:
 
@@
 \begin{equation}
-\label{eq:two}
+\label{eq:octwo}
 \Delta MCP_r = -(1-\frac{X_{t}}{X_{t_0}})*100
@@
 
-Where $X_{t}$ is the future average MCP for each of the two time periods analyzed in this study and $t_0$ is the present averaged MCP (<mu> `r Beg_In`-`r Beg_End`).
+where $X_{t}$ is the future average MCP for each of the two time periods analyzed in this study and $t_0$ is the present averaged MCP (\mu `r Beg_In`-`r Beg_End`).
 Note that in cases where $X_{0}$ = 0 and $X_{t}$ > 0, then ($\Delta MCP$) = 100%, consequently, the opposite case would give a -100% result.
-This way, Equ.
-2 shows the percentage change in MCP by mid $21^{st}$ century when $X_t$ = $\mu$ `r Mid_In`-`r Mid_End`, and end of $21^{st}$ century when $X_t$ = $\mu$ `r End_In`-`r End_End`, relative to today ($t_0$).
+This way, equation \@ref(eq:octwo) shows the percentage change in MCP by mid $21^{st}$ century when $X_t$ = $\mu$ `r Mid_In`-`r Mid_End`, and end of $21^{st}$ century when $X_t$ = $\mu$ `r End_In`-`r End_End`, relative to today ($t_0$).
 The rationale between choosing these time periods was to provide a relative short-term projection (mid-century) that would be more policy-relevant but also show the long-term trend (end of the century).
@@
 
-In addition, we borrowed the concept of “threat point” from game theory defined as the minimum payoff that a player is willing to receive in order to cooperate with other players [@Sumaila:2020tp].
-Thus, we estimated the change in the ($\Delta MCP$) (threat point) that each country (players) would have for each species (hereafter referred as stock-share ratio), for both the IPHC and the GoMA.
+In addition, I borrowed the concept of “threat point” from game theory defined as the minimum payoff that a player is willing to receive in order to cooperate with other players [@Sumaila:2020tp].
+Thus, I estimated the change in the ($\Delta MCP$) (threat point) that each country (players) would have for each species (hereafter referred as stock-share ratio), for both the IPHC and the GoMa.
 The stock-share ratio can be seen as the proportion of the stock’s distribution within the study area that each country has.
-For this, we first modified Equ.
-1, to estimate the aggregated yearly mean MCP of each species per region.
-We then averaged the results by the same previously motioned periods (present, mid and end of the $21^{st}$ century).
-Next, for each species we estimated the stock-share ratio  ($\alpha_s$) that each region had during each time period:
+For this, I first modified equation \@ref(eq:ocone), to estimate the aggregated yearly mean MCP of each species per region.
+I then averaged the results by the same previously motioned periods (present, mid and end of the $21^{st}$ century).
+Next, for each species I estimated the stock-share ratio  ($\alpha_s$) that each region had during each time period:
 
@@
 Where $\theta_{rt}$* is the species' aggregated $\hat{MCP}$ of each region at time period *t*, and $\delta_{rt}$ is the species' aggregated $\hat{MCP}$ of the whole specie's distribution within the study area at the same time period.
-Finally, we estimated the percentage change in stock-share ratio substituting $X_{t_0}$ and $X_{t}$ by $\alpha_{t0}$ and $\alpha_t$, respectively in Equation \@ref(eq:two).
+Finally, I estimated the percentage change in stock-share ratio substituting $X_{t_0}$ and $X_{t}$ by $\alpha_{t0}$ and $\alpha_t$, respectively in equation \@ref(eq:octwo).
 The process was carried out for each ESM and results presented as average $\pm$ standard deviation (sd).
@@
 
-At least one third of the IPHC regulatory areas will see a reduction in MCP of Pacific halibut by 2050 relative to current MCP, regardless of the climate change scenario (Figure \ref(fig:ocFigure2-IPHC)).
+At least one third of the IPHC regulatory areas will see a reduction in MCP of Pacific halibut by 2050 relative to current MCP, regardless of the climate change scenario (Figure \@ref(fig:ocFigure2-IPHC)).
 It is likely that the stock shift from the US.
@@
 The potential movement of halibut westward will increase the MCP of regulatory areas 3B (under a low emission scenario) and 4ABCE along the Aleutian Islands and Bering Sea.
-Regions 4DE, the most poleward regulatory areas of the IPHC, are expected to gain MCP by mid (Figure \ref(fig:ocFigure2-IPHC)) and end of the $21^{st}$ century (Figure \ref(fig:ocFigureS11)) under a high emission scenario due to the expansion of halibut suitable habitat as sea ice retreats (Figure \ref(fig:ocFigureS21)).
-In contrast, under a low emission scenario, sea ice is expected to stabilize towards mid 21st century, thus providing less “new” suitable habitat for Pacific halibut and resulting in undetectable changes in MCP for the region (Figure \ref(fig:ocFigure2-IPHC)B) and decreasing even more towards 2100 (Figure \ref(fig:ocFigureS11)).
+Regions 4DE, the most poleward regulatory areas of the IPHC, are expected to gain MCP by mid (Figure \@ref(fig:ocFigure2-IPHC)) and end of the $21^{st}$ century (Figure \@ref(fig:ocFigureS11)) under a high emission scenario due to the expansion of halibut suitable habitat as sea ice retreats (Figure \@ref(fig:ocFigureS21)).
+In contrast, under a low emission scenario, sea ice is expected to stabilize towards mid 21st century, thus providing less “new” suitable habitat for Pacific halibut and resulting in undetectable changes in MCP for the region (Figure \@ref(fig:ocFigure2-IPHC)B) and decreasing even more towards 2100 (Figure \@ref(fig:ocFigureS11)).
 
@@
 
-The same poleward trend is expected in the change of Pacific halibut stock-share ratio with the average proportion increasing up to 25% in some northern regions and decreasing by 10% in southern regions, relative to the present proportion (Figure \ref(fig:ocFigure3-IPHC-prop)).
+The same poleward trend is expected in the change of Pacific halibut stock-share ratio with the average proportion increasing up to 25% in some northern regions and decreasing by 10% in southern regions, relative to the present proportion (Figure \@ref(fig:ocFigure3-IPHC-prop)).
 Maintaining emissions to lower levels through 2050 would potentially leave unchanged the stock-share ratio of three regulatory areas (3AC, and 4D) and negatively change regulatory area 2A.
@@
 
-While some regulatory areas of the IPHC will see an incremental increase in Pacific halibut MCP, the results for the Gulf of Maine show an overall decrease in MCP by 2050, regardless of the climate change scenario or ESM (Figure \ref(fig:ocFigure4-GOMA)), intensifying by the end of the $21^{st}$ century (Figure \ref(fig:ocFigureS12)).
-For cod and haddock, MCP will decrease within the whole Gulf with no apparent win for any country in reference to the current period (Figure \ref(fig:ocFigure4-GOMA)).
-For yellowtail flounder, despite an overall reduction, some discrete areas are expected to increase with no particular pattern and high uncertainty, as ESMs in these regions do not agree in the direction of change (Figure \ref(fig:ocFigureS23)).
+While some regulatory areas of the IPHC will see an incremental increase in Pacific halibut MCP, the results for the Gulf of Maine show an overall decrease in MCP by 2050, regardless of the climate change scenario or ESM (Figure \@ref(fig:ocFigure4-GoMa)), intensifying by the end of the $21^{st}$ century (Figure \@ref(fig:ocFigureS12)).
+For cod and haddock, MCP will decrease within the whole Gulf with no apparent win for any country in reference to the current period (Figure \@ref(fig:ocFigure4-GoMa)).
+For yellowtail flounder, despite an overall reduction, some discrete areas are expected to increase with no particular pattern and high uncertainty, as ESMs in these regions do not agree in the direction of change (Figure \@ref(fig:ocFigureS23)).
 Despite the overall reduction in MCP for all three species in comparison to current values, there is a benefit of achieving a low emission scenario as reductions intensify under the high emission scenario.
@@
 
-```{r ocFigure4-GOMA, eval = T, echo = F, fig.cap= "Percentage change of MCP in the Gulf of Maine under, A) high emission scenario; and B) low emission for mid-century (2041-2060) relative to present (2005-2014).
+```{r ocFigure4-GoMa, eval = T, echo = F, fig.cap= "Percentage change of MCP in the Gulf of Maine under, A) high emission scenario; and B) low emission for mid-century (2041-2060) relative to present (2005-2014).
 Points represent regions where models do not agree in direction of change."}
@@
 Following a high emission path will affect mostly Canada’s share of yellowtail flounder and in less degree haddock, with an increase of cod share.
-under the low emission scenario, haddock and cod patterns intensify, while yellowtail flounder’s share approaches almost no change (Figure \ref(fig:ocFigure5-GOMA-prop)).
+under the low emission scenario, haddock and cod patterns intensify, while yellowtail flounder’s share approaches almost no change (Figure \@ref(fig:ocFigure5-GoMa-prop)).
 Such pattern is likely the combination of the bathymetry or the Gulf, the warming gradient, and the species distribution (see Discussion).
@@
 
-```{r ocFigure5-GOMA-prop, eval = T, echo = F, fig.cap="Changes in MCP stock-share ratio for Gulf of Maine under (A) high emission; and (B) low emission scenarios for mid 21st century (2041-2060) relative to present (2005-2014).
+```{r ocFigure5-GoMa-prop, eval = T, echo = F, fig.cap="Changes in MCP stock-share ratio for Gulf of Maine under (A) high emission; and (B) low emission scenarios for mid 21st century (2041-2060) relative to present (2005-2014).
 Values represent the mean of 3 ESM; error bars represent \u00B1 sd."}
@@
 On the other hand, regions 3A and 3B have seen the largest decreases in the IPHC regulatory areas since 2010, from 35.3% to 30.6% and 20.6% to 15.9%, respectively.
-Similarly, in the Gulf of Maine, the projected stock-share gain of yellowtail flounder and haddock by the US (Figure \ref(fig:ocFigure5-GOMA-prop)) follows a historical trend where in 2019, Canada's stock-share decreased from 35% to 32% and 60% to 40% relative to 2010, respectively [@Trinko:2019ou].
+Similarly, in the Gulf of Maine, the projected stock-share gain of yellowtail flounder and haddock by the US (Figure \@ref(fig:ocFigure5-GoMa-prop)) follows a historical trend where in 2019, Canada's stock-share decreased from 35% to 32% and 60% to 40% relative to 2010, respectively [@Trinko:2019ou].
 
@@
 Geographic barriers [@Cheung:2015fm; @Kleisner:2016je], local temperature gradients [@Pinsky:2013ab], species interactions and human activities [@Serpetti:2017he] might change the rate and direction of species shifts.
-For the IPHC, geographic barriers might induce a westward increase of stock-share in IPHC regions where species can only migrate northward into the Arctic Ocean through the Bering Sea and Bering Strait [@Cheung:2015fm] (Figure \ref(fig:ocFigure3-IPHC-prop)).
-In the Gulf of Maine, future projections could be a response to a temperature gradient shift combined with geographic barriers as southern waters are deeper and warming slower than northern waters according to the ESMs (Figure \ref(fig:ocFigureS22)).
+For the IPHC, geographic barriers might induce a westward increase of stock-share in IPHC regions where species can only migrate northward into the Arctic Ocean through the Bering Sea and Bering Strait [@Cheung:2015fm] (Figure \@ref(fig:ocFigure3-IPHC-prop)).
+In the Gulf of Maine, future projections could be a response to a temperature gradient shift combined with geographic barriers as southern waters are deeper and warming slower than northern waters according to the ESMs (Figure \@ref(fig:ocFigureS22)).
 Moreover, Maine has seen its landings of yellowtail flounder increased at the expenses of southern states [@Pinsky:2012kq].
-This could be influencing the US gain in MCP in the GoMA in relation to Canada as species shift their distribution from lower latitudes naturally reaching the US (lower) region first.
+This could be influencing the US gain in MCP in the GoMa in relation to Canada as species shift their distribution from lower latitudes naturally reaching the US (lower) region first.
 As the effects of climate change endure, even with high mitigation, joint plans should prepare to face changes in the stock-share ratio of transboundary stocks along both coast of North America.
@@
 Moreover, overlapping shifting stocks could interfere in gear-limitation management rules of multiple fisheries generating conflicts between fleets [@VanDerVoo:2016uc].
-The effectiveness of the IPHC-Closed Area ("CA" in Figure \ref(fig:ocFigure2-IPHC)) in terms of protecting juveniles has been historically questioned as trawling for other species is still allowed in the area [@Karim:2010ut; @IPHC:2017CA].
+The effectiveness of the IPHC-Closed Area ("CA" in Figure \@ref(fig:ocFigure2-IPHC)) in terms of protecting juveniles has been historically questioned as trawling for other species is still allowed in the area [@Karim:2010ut; @IPHC:2017CA].
 In 2015, for example, 97% of the trawl by-catch in areas 4CDE and the Closed Area were juveniles [@IPHC:2017CA].
@@
 However, climate change has shifted the distribution of multiple European commercial stocks [@Baudron:2020dj], outdating the fixed quotas and thus compromising the sustainability of European fisheries [@FAO:2018uv; @Baudron:2020dj].
-Management regimes that include a dynamic harvest control (e.g.
-adjusting the quota based on the stocks distribution) have the potential of increasing fish biomass, harvest and profits under climate change [@Gaines:2018sg].
+Management regimes that include a dynamic harvest control (e.g., adjusting the quota based on the stocks distribution) have the potential of increasing fish biomass, harvest and profits under climate change [@Gaines:2018sg].
 In North America, poleward shifts of Pacific halibut along the coast of Oregon, Washington and British Columbia have been previously addressed by the IPHC resulting in the adoption of a dynamic quota allocation method [@McCaughran:1992uw].
-By allocating quotas based on yearly surveys along the Convention area, the IPHC should be able to capture shifts in Pacific halibut distribution due to climate change, reducing the chances of over exploitation of the stock due to this shifts [@Miller:2013iv].
-Similarly, for the Gulf of Maine, since the GoMA’s method to estimate quota allocation is weighted based on stocks distribution (90%) and historical catch (10%) [@TRAC:2016wu].
+By allocating quotas based on yearly surveys along the Convention area, the IPHC should be able to capture shifts in Pacific halibut distribution due to climate change, reducing the chances of over exploitation of the stock due to these shifts [@Miller:2013iv].
+Similarly, for the Gulf of Maine, since the GoMa’s method to estimate quota allocation is weighted based on stocks distribution (90%) and historical catch (10%) [@TRAC:2016wu].
 This process is especially important for cod and haddock due to their distribution variation within the Gulf [@Soboil:2006gw; @TRAC:2016wu].
@@
 Transboundary fisheries management have to be prepared for the uncertainty that comes with a changing world.
-Future climate change will depend on the path society as a whole will take, and thus we rely on scenario planning to account for the uncertainty build in future decision making [@vanVuuren:2011ef].
+Future climate change will depend on the path society as a whole will take, and thus I rely on scenario planning to account for the uncertainty build in future decision making [@vanVuuren:2011ef].
 In our results, the "winners and losers" of climate change, and the intensity of the change, will be scenario dependent.
-For instance, stock-share of yellowtail flounder under a high emission scenario will be larger for the US while Canada's gain of cod stock-share will be larger under a low emission scenario (Figure \ref(fig:ocFigure5-GOMA-prop)).
-Applying previously describe strategies (e.g.
-quota swaps or EEZ-fishing rights) could increase the resilience of treaties by preventing members from leaving the agreement due to a shift in threat points, as happened in the Pacific salmon case [@Miller:2013iv].
+For instance, stock-share of yellowtail flounder under a high emission scenario will be larger for the US while Canada's gain of cod stock-share will be larger under a low emission scenario (Figure \@ref(fig:ocFigure5-GoMa-prop)).
+Applying previously describe strategies (e.g., quota swaps or EEZ-fishing rights) could increase the resilience of treaties by preventing members from leaving the agreement due to a shift in threat points, as happened in the Pacific salmon case [@Miller:2013iv].
 
@@
 An ensemble of models is a way to present a more robust result that accounts for differences in the structural composition of each model [@Cheung:2016gv].
-In here we used three ESMs to project future changes in species maximum catch potential.
+In here I used three ESMs to project future changes in species maximum catch potential.
 The levels of uncertainty related to the ESMs differ among case studies.
@@
 Shifts in stocks distribution due to climate change have the potential of creating local extinction of economically important stocks while enhancing fisheries in areas where they were not present before.
-In this paper, we have explored the potential impacts of climate change in the joint management of selected transboundary stocks managed by Canada and the US.
-We found that, transboundary stocks are likely to shift in the upcoming years changing the proportion of the catch of jointly managed fisheries of Canada and the US.
+In this chapter, I have explored the potential impacts of climate change in the joint management of selected transboundary stocks managed by Canada and the US.
+I found that, transboundary stocks are likely to shift in the upcoming years changing the proportion of the catch of jointly managed fisheries of Canada and the US.
 Lessons from other countries can provide solutions to such challenges.
@@
 
-<!-- Explore environental differences withing GOMA -->
+<!-- Explore environental differences withing GoMa -->
 
@@
 
-<!-- GOMA Outliers analysis -->
+<!-- GoMa Outliers analysis -->
 ```{r GoM_Environ_outliers, eval = F, echo = F}
@@
 
-```{r ocFigureS23, eval = T, echo = F, fig.cap = "Changes in maximum catch potential of yellowtail flounder (*Limanda ferruginea*) within the study area by mid-century relative to present time.
+```{r ocFigureS23, eval = F, echo = F, fig.cap = "Changes in maximum catch potential of yellowtail flounder (*Limanda ferruginea*) within the study area by mid-century relative to present time.
 Results for the three global circulation models (GFDL, IPSL, MPIS) used in the current study and two climate change scenarios (Top: High emission – RCP 8.5, Bottom: Low Emission – RCP 2.6).
@@
 
-```{r ocFigureS24, eval = T, echo = F, fig.cap = "Projected MCP change relative to present (2005-2014) for each IPHC regulatory area.
+```{r ocFigureS24, eval = F, echo = F, fig.cap = "Projected MCP change relative to present (2005-2014) for each IPHC regulatory area.
 Colors represents the different ESM used in the study.
@@
               "Northwest Atlantic Fisheries Organization (NAFO)",
-              "Gulf of Maine's Arrangement (GoMA)"),
+              "Gulf of Maine's Arrangement (GoMa)"),
             Species =
@@
 <!-- # Option removing NAFO -->
-<!-- Shifts in the distribution of 33 jointly managed transboundary stocks of North America by 2050 relative to 2010 show that MCP of transboundary stocks will overall increase in Atlantic-Canadian and Alaskan waters and decrease in Pacific-Canadian and the US contiguous states waters (Figure \ref(fig:ocFigure2-IPHC)).
+<!-- Shifts in the distribution of 33 jointly managed transboundary stocks of North America by 2050 relative to 2010 show that MCP of transboundary stocks will overall increase in Atlantic-Canadian and Alaskan waters and decrease in Pacific-Canadian and the US contiguous states waters (Figure \@ref(fig:ocFigure2-IPHC)).
 Such changes will be more intense under the high emission scenario (Fig.

### 2020-11-26 Ecol/Manuscript_Draft.Rmd
blocked kableextra  for word

@@
  "knitr",
- "kableExtra",
+ # "kableExtra",
  "data.table",
@@
 table_1 %>% 
-  kable("latex",
-        booktabs = T,
-        caption = "Historic quota allocation suggested for Atlantic cod, haddock and yellowtail flounder in the Gulf of Maine "
-  ) %>% 
-  kable_styling(full_width = F,
-                position = "center") %>%
-  add_header_above(c(" ", "Atlantic cod" = 2, "Haddock" = 2, "Yellowtail flounder" = 2)
-  ) %>% 
-  footnote(general = c("* Average from 2006 to 2009, before the implementation of the weighted method",
-                       "' Since the implementation of the weighted method",
-                       "'' Standard deviation of the wiighted average",
-                       "^ TRAC (2015abc)",
-                       "† TRAC (2018abc)",
-                       "‡ Lake (2019)"
-  )
-  )
+  kable(caption = "Historic quota allocation suggested for Atlantic cod, haddock and yellowtail flounder in the Gulf of Maine")
+  # kable("latex",
+  #       booktabs = T,
+  #       caption = "Historic quota allocation suggested for Atlantic cod, haddock and yellowtail flounder in the Gulf of Maine "
+  # ) %>% 
+  # kable_styling(full_width = F,
+  #               position = "center") %>%
+  # add_header_above(c(" ", "Atlantic cod" = 2, "Haddock" = 2, "Yellowtail flounder" = 2)
+  # ) %>% 
+  # footnote(general = c("* Average from 2006 to 2009, before the implementation of the weighted method",
+  #                      "' Since the implementation of the weighted method",
+  #                      "'' Standard deviation of the wiighted average",
+  #                      "^ TRAC (2015abc)",
+  #                      "† TRAC (2018abc)",
+  #                      "‡ Lake (2019)"
+  # )
+  # )
 
@@
 
-where *y* is year, *r* is region, *s* is species, *n* is total number of species, and $\hat{MCP}$ is the MCP averaged by the three ESMs.
+where *y* is year, *r* is region, *s* is grid, *n* is total number of grids in  the region, and $\hat{MCP}$ is the MCP of each species.
 In the case of the GoMa, region was defined as the $0.5^{\circ}$ x $0.5^{\circ}$ grid-cell within the specific NAFO divisional zones.
@@
 
-where $X_{t}$ is the future average MCP for each of the two time periods analyzed in this study and $t_0$ is the present averaged MCP (\mu `r Beg_In`-`r Beg_End`).
+where $X_{t}$ is the future average MCP for each of the two time periods analyzed in this study and $t_0$ is the present averaged MCP ($\mu$ `r Beg_In`-`r Beg_End`).
 Note that in cases where $X_{0}$ = 0 and $X_{t}$ > 0, then ($\Delta MCP$) = 100%, consequently, the opposite case would give a -100% result.
@@
 
-Where $\theta_{rt}$* is the species' aggregated $\hat{MCP}$ of each region at time period *t*, and $\delta_{rt}$ is the species' aggregated $\hat{MCP}$ of the whole specie's distribution within the study area at the same time period.
+Where $\theta_{rt}$* is the species' aggregated $\hat{MCP}$ of each region at time period *t*, and $\delta_{ts}$ is the species' aggregated $\hat{MCP}$ of the whole specie's distribution within the study area at the same time period.
 Finally, I estimated the percentage change in stock-share ratio substituting $X_{t_0}$ and $X_{t}$ by $\alpha_{t0}$ and $\alpha_t$, respectively in equation \@ref(eq:octwo).
@@
 
-At least one third of the IPHC regulatory areas will see a reduction in MCP of Pacific halibut by 2050 relative to current MCP, regardless of the climate change scenario (Figure \@ref(fig:ocFigure2-IPHC)).
+At least one third of the IPHC regulatory areas will see a reduction in MCP of Pacific halibut by 2050 relative to current MCP, regardless of the climate change scenario (Figure \@ref(fig:ocFigure2)).
 It is likely that the stock shift from the US.
@@
 The potential movement of halibut westward will increase the MCP of regulatory areas 3B (under a low emission scenario) and 4ABCE along the Aleutian Islands and Bering Sea.
-Regions 4DE, the most poleward regulatory areas of the IPHC, are expected to gain MCP by mid (Figure \@ref(fig:ocFigure2-IPHC)) and end of the $21^{st}$ century (Figure \@ref(fig:ocFigureS11)) under a high emission scenario due to the expansion of halibut suitable habitat as sea ice retreats (Figure \@ref(fig:ocFigureS21)).
-In contrast, under a low emission scenario, sea ice is expected to stabilize towards mid 21st century, thus providing less “new” suitable habitat for Pacific halibut and resulting in undetectable changes in MCP for the region (Figure \@ref(fig:ocFigure2-IPHC)B) and decreasing even more towards 2100 (Figure \@ref(fig:ocFigureS11)).
+Regions 4DE, the most poleward regulatory areas of the IPHC, are expected to gain MCP by mid (Figure \@ref(fig:ocFigure2)) and end of the $21^{st}$ century (Figure \@ref(fig:ocFigureS11)) under a high emission scenario due to the expansion of halibut suitable habitat as sea ice retreats (Figure \@ref(fig:ocFigureS21)).
+In contrast, under a low emission scenario, sea ice is expected to stabilize towards mid 21st century, thus providing less “new” suitable habitat for Pacific halibut and resulting in undetectable changes in MCP for the region (Figure \@ref(fig:ocFigure2)B) and decreasing even more towards 2100 (Figure \@ref(fig:ocFigureS11)).
 
@@
 
-```{r ocFigure2-IPHC, eval = T, echo = F, fig.cap= "Percentage change of MCP for species managed by the IPHC for mid 21st century (2041-2060) relative to present 2005-2014 under a A) high emission scenario and B) low emission scenario.
+```{r ocFigure2, eval = T, echo = F, fig.cap= "Percentage change of MCP for species managed by the IPHC for mid 21st century (2041-2060) relative to present 2005-2014 under a A) high emission scenario and B) low emission scenario.
 Labels marked with * represent regions where models do not agree in direction of change."}
@@
 
-The same poleward trend is expected in the change of Pacific halibut stock-share ratio with the average proportion increasing up to 25% in some northern regions and decreasing by 10% in southern regions, relative to the present proportion (Figure \@ref(fig:ocFigure3-IPHC-prop)).
+The same poleward trend is expected in the change of Pacific halibut stock-share ratio with the average proportion increasing up to 25% in some northern regions and decreasing by 10% in southern regions, relative to the present proportion (Figure \@ref(fig:ocFigure3)).
 Maintaining emissions to lower levels through 2050 would potentially leave unchanged the stock-share ratio of three regulatory areas (3AC, and 4D) and negatively change regulatory area 2A.
@@
 
-```{r ocFigure3-IPHC-prop, eval = T, echo = F, fig.cap="Percentage change of stock-share ratio for IPHC under A) high emission scenario and B) low emission scenario for mid 21st century (2041-2060) relative to present 2005-2014.
+```{r ocFigure3, eval = T, echo = F, fig.cap="Percentage change of stock-share ratio for IPHC under A) high emission scenario and B) low emission scenario for mid 21st century (2041-2060) relative to present 2005-2014.
 Values represent the mean of 3 ESM; error bars represent \u00B1 sd."}
@@
 
-While some regulatory areas of the IPHC will see an incremental increase in Pacific halibut MCP, the results for the Gulf of Maine show an overall decrease in MCP by 2050, regardless of the climate change scenario or ESM (Figure \@ref(fig:ocFigure4-GoMa)), intensifying by the end of the $21^{st}$ century (Figure \@ref(fig:ocFigureS12)).
-For cod and haddock, MCP will decrease within the whole Gulf with no apparent win for any country in reference to the current period (Figure \@ref(fig:ocFigure4-GoMa)).
+While some regulatory areas of the IPHC will see an incremental increase in Pacific halibut MCP, the results for the Gulf of Maine show an overall decrease in MCP by 2050, regardless of the climate change scenario or ESM (Figure \@ref(fig:ocFigure4)), intensifying by the end of the $21^{st}$ century (Figure \@ref(fig:ocFigureS12)).
+For cod and haddock, MCP will decrease within the whole Gulf with no apparent win for any country in reference to the current period (Figure \@ref(fig:ocFigure4)).
 For yellowtail flounder, despite an overall reduction, some discrete areas are expected to increase with no particular pattern and high uncertainty, as ESMs in these regions do not agree in the direction of change (Figure \@ref(fig:ocFigureS23)).
@@
 
-```{r ocFigure4-GoMa, eval = T, echo = F, fig.cap= "Percentage change of MCP in the Gulf of Maine under, A) high emission scenario; and B) low emission for mid-century (2041-2060) relative to present (2005-2014).
+```{r ocFigure4, eval = T, echo = F, fig.cap= "Percentage change of MCP in the Gulf of Maine under, A) high emission scenario; and B) low emission for mid-century (2041-2060) relative to present (2005-2014).
 Points represent regions where models do not agree in direction of change."}
@@
 Following a high emission path will affect mostly Canada’s share of yellowtail flounder and in less degree haddock, with an increase of cod share.
-under the low emission scenario, haddock and cod patterns intensify, while yellowtail flounder’s share approaches almost no change (Figure \@ref(fig:ocFigure5-GoMa-prop)).
+under the low emission scenario, haddock and cod patterns intensify, while yellowtail flounder’s share approaches almost no change (Figure \@ref(fig:ocFigure5)).
 Such pattern is likely the combination of the bathymetry or the Gulf, the warming gradient, and the species distribution (see Discussion).
@@
 
-```{r ocFigure5-GoMa-prop, eval = T, echo = F, fig.cap="Changes in MCP stock-share ratio for Gulf of Maine under (A) high emission; and (B) low emission scenarios for mid 21st century (2041-2060) relative to present (2005-2014).
+```{r ocFigure5, eval = T, echo = F, fig.cap="Changes in MCP stock-share ratio for Gulf of Maine under (A) high emission; and (B) low emission scenarios for mid 21st century (2041-2060) relative to present (2005-2014).
 Values represent the mean of 3 ESM; error bars represent \u00B1 sd."}
@@
 On the other hand, regions 3A and 3B have seen the largest decreases in the IPHC regulatory areas since 2010, from 35.3% to 30.6% and 20.6% to 15.9%, respectively.
-Similarly, in the Gulf of Maine, the projected stock-share gain of yellowtail flounder and haddock by the US (Figure \@ref(fig:ocFigure5-GoMa-prop)) follows a historical trend where in 2019, Canada's stock-share decreased from 35% to 32% and 60% to 40% relative to 2010, respectively [@Trinko:2019ou].
+Similarly, in the Gulf of Maine, the projected stock-share gain of yellowtail flounder and haddock by the US (Figure \@ref(fig:ocFigure5)) follows a historical trend where in 2019, Canada's stock-share decreased from 35% to 32% and 60% to 40% relative to 2010, respectively [@Trinko:2019ou].
 
@@
 Geographic barriers [@Cheung:2015fm; @Kleisner:2016je], local temperature gradients [@Pinsky:2013ab], species interactions and human activities [@Serpetti:2017he] might change the rate and direction of species shifts.
-For the IPHC, geographic barriers might induce a westward increase of stock-share in IPHC regions where species can only migrate northward into the Arctic Ocean through the Bering Sea and Bering Strait [@Cheung:2015fm] (Figure \@ref(fig:ocFigure3-IPHC-prop)).
+For the IPHC, geographic barriers might induce a westward increase of stock-share in IPHC regions where species can only migrate northward into the Arctic Ocean through the Bering Sea and Bering Strait [@Cheung:2015fm] (Figure \@ref(fig:ocFigure3)).
 In the Gulf of Maine, future projections could be a response to a temperature gradient shift combined with geographic barriers as southern waters are deeper and warming slower than northern waters according to the ESMs (Figure \@ref(fig:ocFigureS22)).
@@
 Moreover, overlapping shifting stocks could interfere in gear-limitation management rules of multiple fisheries generating conflicts between fleets [@VanDerVoo:2016uc].
-The effectiveness of the IPHC-Closed Area ("CA" in Figure \@ref(fig:ocFigure2-IPHC)) in terms of protecting juveniles has been historically questioned as trawling for other species is still allowed in the area [@Karim:2010ut; @IPHC:2017CA].
+The effectiveness of the IPHC-Closed Area ("CA" in Figure \@ref(fig:ocFigure2)) in terms of protecting juveniles has been historically questioned as trawling for other species is still allowed in the area [@Karim:2010ut; @IPHC:2017CA].
 In 2015, for example, 97% of the trawl by-catch in areas 4CDE and the Closed Area were juveniles [@IPHC:2017CA].
@@
 In our results, the "winners and losers" of climate change, and the intensity of the change, will be scenario dependent.
-For instance, stock-share of yellowtail flounder under a high emission scenario will be larger for the US while Canada's gain of cod stock-share will be larger under a low emission scenario (Figure \@ref(fig:ocFigure5-GoMa-prop)).
+For instance, stock-share of yellowtail flounder under a high emission scenario will be larger for the US while Canada's gain of cod stock-share will be larger under a low emission scenario (Figure \@ref(fig:ocFigure5)).
 Applying previously describe strategies (e.g., quota swaps or EEZ-fishing rights) could increase the resilience of treaties by preventing members from leaving the agreement due to a shift in threat points, as happened in the Pacific salmon case [@Miller:2013iv].
@@
 Overall, results for the Gulf of Maine agree with a reduction in MCP of all three species.
-However, some discrete areas show a positive change for yellowtail flounder by mid $21^{st}$ century (Figure \@ref(fig:ocFigure3-IPHC-prop)), mainly driven by the GFDL model (Figure \@ref(fig:ocFigureS23)).
+However, some discrete areas show a positive change for yellowtail flounder by mid $21^{st}$ century (Figure \@ref(fig:ocFigure3)), mainly driven by the GFDL model (Figure \@ref(fig:ocFigureS23)).
 Potential model artifacts could also be contributing to the results, especially in the northern part of the study area (Bay of Fundy) as most disagreeing grids are covered by land, which could be influencing the results.
@@
 
-```{r ocFigureS11, eval = F, echo = F, fig.cap = "Percentage change of MCP for species managed by the IPHC for end-century (2081–2100) relative to 2005–2014 under a A) high emission scenario and B) low emission scenario.
+```{r FigureS11, eval = F, echo = F, fig.cap = "Percentage change of MCP for species managed by the IPHC for end-century (2081–2100) relative to 2005–2014 under a A) high emission scenario and B) low emission scenario.
 Labels marked with * represent regions where models do not agree in direction of change."}
@@
 
-```{r ocFigureS12, eval = F, echo = F, fig.cap = "Percentage change of MCP in the Gulf of Maine under (RCP 8.5) high emission scenario and (RCP 2.6) low emission for end-century (2080–2100) referent to present (2005– 2014).
+```{r FigureS12, eval = F, echo = F, fig.cap = "Percentage change of MCP in the Gulf of Maine under (RCP 8.5) high emission scenario and (RCP 2.6) low emission for end-century (2080–2100) referent to present (2005– 2014).
 Values represent the mean of 3 ESM.
@@
 
-```{r ocFigureS21, eval = F, echo = F, fig.cap = "Projected environmental variables under climate change from 2010 to 2010 for Arctic regions of the IPHC (Top:4D, Bottom, 4E).
+```{r FigureS21, eval = F, echo = F, fig.cap = "Projected environmental variables under climate change from 2010 to 2010 for Arctic regions of the IPHC (Top:4D, Bottom, 4E).
 The solid line represents the average of all three ESMs and the shaded area represents the model’s uncertainty (s.d.)."}
@@
 
-```{r ocFigureS22, eval = F, echo = F, fig.cap = "Depth profile (A) and bottom water warming of the Gulf of Maine.
+```{r FigureS22, eval = F, echo = F, fig.cap = "Depth profile (A) and bottom water warming of the Gulf of Maine.
 Everything deeper than 1000 meters is colored in green.
@@
 
-```{r ocFigureS23, eval = F, echo = F, fig.cap = "Changes in maximum catch potential of yellowtail flounder (*Limanda ferruginea*) within the study area by mid-century relative to present time.
+```{r FigureS23, eval = F, echo = F, fig.cap = "Changes in maximum catch potential of yellowtail flounder (*Limanda ferruginea*) within the study area by mid-century relative to present time.
 Results for the three global circulation models (GFDL, IPSL, MPIS) used in the current study and two climate change scenarios (Top: High emission – RCP 8.5, Bottom: Low Emission – RCP 2.6).
@@
 
-```{r ocFigureS24, eval = F, echo = F, fig.cap = "Projected MCP change relative to present (2005-2014) for each IPHC regulatory area.
+```{r FigureS24, eval = F, echo = F, fig.cap = "Projected MCP change relative to present (2005-2014) for each IPHC regulatory area.
 Colors represents the different ESM used in the study.
@@
 
-```{r ocFigure_out_outliers, eval = F, echo = F}
+```{r Figure_out_outliers, eval = F, echo = F}
 
@@
 <!-- # Option removing NAFO -->
-<!-- Shifts in the distribution of 33 jointly managed transboundary stocks of North America by 2050 relative to 2010 show that MCP of transboundary stocks will overall increase in Atlantic-Canadian and Alaskan waters and decrease in Pacific-Canadian and the US contiguous states waters (Figure \@ref(fig:ocFigure2-IPHC)).
+<!-- Shifts in the distribution of 33 jointly managed transboundary stocks of North America by 2050 relative to 2010 show that MCP of transboundary stocks will overall increase in Atlantic-Canadian and Alaskan waters and decrease in Pacific-Canadian and the US contiguous states waters (Figure \@ref(fig:ocFigure2)).
 Such changes will be more intense under the high emission scenario (Fig.

### 2020-11-26 Ecol/Supplements.Rmd
blocked kableextra  for word

@@
   "knitr",
-  "kableExtra",
+  # "kableExtra",
   "png",
@@
 
-```{r FigureS11, eval = T, echo = F, fig.cap = "Percentage change of MCP for species managed by the IPHC for end-century (2081–2100) relative to 2005–2014 under a A) high emission scenario and B) low emission scenario.
+```{r ocFigureS11, eval = T, echo = F, fig.cap = "Percentage change of MCP for species managed by the IPHC for end-century (2081–2100) relative to 2005–2014 under a A) high emission scenario and B) low emission scenario.
 Labels marked with * represent regions where models do not agree in direction of change."}
@@
 
-```{r FigureS12, eval = T, echo = F, fig.cap = "Percentage change of MCP in the Gulf of Maine under (RCP 8.5) high emission scenario and (RCP 2.6) low emission for end-century (2080–2100) referent to present (2005– 2014).
+```{r ocFigureS12, eval = T, echo = F, fig.cap = "Percentage change of MCP in the Gulf of Maine under (RCP 8.5) high emission scenario and (RCP 2.6) low emission for end-century (2080–2100) referent to present (2005– 2014).
 Values represent the mean of 3 ESM.
@@
 
-```{r FigureS21, eval = T, echo = F, fig.cap = "Projected environmental variables under climate change from 2010 to 2010 for Arctic regions of the IPHC (Top:4D, Bottom, 4E).
+```{r ocFigureS21, eval = T, echo = F, fig.cap = "Projected environmental variables under climate change from 2010 to 2010 for Arctic regions of the IPHC (Top:4D, Bottom, 4E).
 The solid line represents the average of all three ESMs and the shaded area represents the model’s uncertainty (s.d.)."}
@@
 
-```{r FigureS22, eval = T, echo = F, fig.cap = "Depth profile (A) and bottom water warming of the Gulf of Maine.
+```{r ocFigureS22, eval = T, echo = F, fig.cap = "Depth profile (A) and bottom water warming of the Gulf of Maine.
 Everything deeper than 1000 meters is colored in green.

### 2020-11-26 Ecol/Manuscript_Draft.Rmd
changed reference for chapters

@@
 stocks that migrate between countries EEZs (known as transboundary stocks) or between EEZs and the high seas (also called straddling stocks) [@Song:2017iua].
-Today, an estimated 347 [@Teh:2015gd] to 1500 [@Caddy:1997ue] fish stocks cross national borders, some of them jointly managed by two or more countries.
-These stocks are responsible for almost 50% of these countries total fish catches [@Teh:2015gd].
+Today, an estimated of 347 [@Teh:2015gd] to 633 (Chapter 2) fish stocks cross national borders, some of them jointly managed by two or more countries.
+These stocks are responsible for more than 70% of these countries total fish catches (Chapter 2).
 Under Article 63, UNCLOS incentives actions to cooperate on the management of shared stocks [@UnitedNations:1986tl] as often management success depends on effective cooperation between parties [@Munro:2002uf; @Sumaila:2013hv].
@@
 Moreover, these shifts are projected to continue towards the end of the $21^{st}$ century [@Cheung:2018hz].
-As a result, some countries or management jurisdictions may see more shared fisheries and their catches shifting into their waters while others will stand to lose [@Oremus:2020id; @Pinsky:2018cb].
+As a result, some countries or management jurisdictions may see more shared fisheries and their catches shifting into their waters while others will stand to lose [@Oremus:2020id; @Pinsky:2018cb, Chapter 3].
 Nevertheless, management rules for shared stocks (e.g., quota or spatial delimitation) are often determined based on current and/or historic knowledge of the stock's distribution and do not consider future shifts in distributions [@FredstonHermann:2018kp].

### 2020-12-14 Ecol/Manuscript_Draft.Rmd
Villy and Tay's comments

@@
 
-In 1982, the United Nations Law of the Sea Convention (UNCLOS) formalized the concept of exclusive economic zones (EEZs) creating what we know today as shared stocks [@UnitedNations:1986tl], i.e.
+In 1982, the United Nations Law of the Sea Convention (UNCLOS) formalized the concept of exclusive economic zones (EEZs) creating the concept that we know today as shared stocks [@UnitedNations:1986tl], i.e.
 stocks that migrate between countries EEZs (known as transboundary stocks) or between EEZs and the high seas (also called straddling stocks) [@Song:2017iua].
-Today, an estimated of 347 [@Teh:2015gd] to 633 (Chapter 2) fish stocks cross national borders, some of them jointly managed by two or more countries.
-These stocks are responsible for more than 70% of these countries total fish catches (Chapter 2).
-Under Article 63, UNCLOS incentives actions to cooperate on the management of shared stocks [@UnitedNations:1986tl] as often management success depends on effective cooperation between parties [@Munro:2002uf; @Sumaila:2013hv].
+Today, an estimated 347 [@Teh:2015gd] to 633 (Chapter 2) fish stocks have distributions that cross national borders, some of them jointly managed by two or more countries.
+These species are responsible for more than 70% of these countries total fish catches (Chapter 2).
+Under Article 63, UNCLOS incentives actions to cooperate on the management of shared stocks [@UnitedNations:1986tl] as management success often depends on effective cooperation between parties [@Munro:2002uf; @Sumaila:2013hv].
 Since the definition of shared stocks, game theory has been one of the most common approaches used to analyze the management of these type of stocks.
@@
 The ocean is getting warmer [@Rheim:2013fv], less oxygenated [@Schmidtko:2017cl], and increasing in acidity [@Ross:2011kd; @IPCC:2019tn].
-To cope with these changes in ocean biophysic properties, marine species, including shared fish stocks, have been shifting their distribution towards the poles and/or deeper waters [@Poloczanska:2016kk].
-As climate change reshapes the ocean's environment worldwide [@Gattuso:2015jz], shared fisheries' delicate governance is threatened as new migration patterns may arise [@Miller:2013iv; @Pinsky:2018cb], historic distribution and abundances might shift [@Cheung:2010dt], and species basic natural traits may modify [@Pauly:2017hpa].
+To cope with these changes in ocean biophysical properties, marine species, including shared fish stocks, have been shifting their distribution towards the poles and/or deeper waters [@Poloczanska:2016kk].
+As climate change reshapes the ocean's environment worldwide [@Gattuso:2015jz], shared fisheries' governance is threatened as new migration patterns may arise [@Miller:2013iv; @Pinsky:2018cb], historic distribution and abundances might shift [@Cheung:2010dt], and species basic natural traits may modify [@Pauly:2017hpa].
 Catches of shared stocks like tunas, have significantly increased in some regions such as the subtropical Atlantic and western Pacific Oceans and are projected to continue [@MonllorHurtado:2017cm; @ErauskinExtramiana:2019fw].
@@
 
-The IPHC was established by Canada and the United States to oversee the management of Pacific halibut (*Hippoglossus stenolepis*) [@IPHC:2014tz].
+The IPHC was established in 1923 by Canada and the United States to oversee the management of Pacific halibut (*Hippoglossus stenolepis*) [@IPHC:2014tz].
 There are 12 regulatory areas from which 3AB holds 51.2% of the stock, followed by regions 2ABC and 4ACDE with 23.1% and 20.4%, respectively, and lastly region 4B with only 5.2% of the stock distribution [@IPHC:2018vz].
@@
 
-Since 1998 Canada and the US have used a "Resource Sharing Understanding" to inform the management of Eastern George Bank's Atlantic cod (*Gadus morhua*) and haddock (*Melanogrammus aeglefinus*) and, yellowtail flounder (*Limanda ferruginea*) [@Pudden:2007bo; @TRAC:2016wu; @Song:2017va].
-From 2010 onward, the GoMa suggests catch-limits based on a weighted method where 10% represents the stocks’ historical distribution (from 1967 to 1994) and 90% current distributions produced by quarterly surveys and catch [@TRAC:2016wu].
+Since 1998 Canada and the US have used a "Resource Sharing Understanding" to inform the management of Eastern George Bank's Atlantic cod (*Gadus morhua*), haddock (*Melanogrammus aeglefinus*) and yellowtail flounder (*Limanda ferruginea*) [@Pudden:2007bo; @TRAC:2016wu; @Song:2017va].
+From 2010 onward, the GoMa suggests catch-limits based on a weighted method where 10% represents the stocks’ historical distribution (from 1967 to 1994) and 90% current distributions as determined by quarterly surveys and catch [@TRAC:2016wu].
 Since its introduction, the average quota allocation for each species proposed by the GoMa has been (Table \@ref(tab:ocTable1); Atlantic cod 77% Canada and 23% US, haddock 55% Canada and 45% US, and yellowtail flounder 34% Canada and 66% US [@TRAC:2015wj; @TRAC:2015vp; @TRAC:2015tt; @TRAC:2018tw; @TRAC:2018tj; @TRAC:2018wx; @Trinko:2019ou].
 However, because this is an unofficial agreement, Canada and the US ultimately take single management decisions [@Soboil:2006gw].
-In terms of management, the US has a multi species harvest control with area and season closures, mesh sizes, effort control, and mobile gear vessels that use bottom otter trawl gear [@Soboil:2006gw].
+In terms of management, the US has a multi species harvest control rule with area and season closures, mesh sizes, effort control, and mobile gear vessels that use bottom otter trawl gear [@Soboil:2006gw].
 In contrast, Canada has a quota system in addition to limited-entry licensing, fleet allocations, and mesh and fish size regulation, among other input controls.
@@
 Despite the expected decrease in MCP for the region, changes in the stock-share ratio of species within the Gulf of Maine show different outcomes dependent on the climate change scenario and species in question.
-Following a high emission path will affect mostly Canada’s share of yellowtail flounder and in less degree haddock, with an increase of cod share.
-under the low emission scenario, haddock and cod patterns intensify, while yellowtail flounder’s share approaches almost no change (Figure \@ref(fig:ocFigure5)).
-Such pattern is likely the combination of the bathymetry or the Gulf, the warming gradient, and the species distribution (see Discussion).
+Following a high emission path will negatively affect mostly Canada’s share of yellowtail flounder and in less degree haddock, with an increase of cod share.
+Under the low emission scenario, haddock and cod share patterns intensify, while yellowtail flounder’s share approaches almost no change (Figure \@ref(fig:ocFigure5)).
+Such pattern is likely due to the combination of the bathymetry or the Gulf, the warming gradient, and the species distribution (see Discussion).
 
@@
 These results are aligned with regional [@Morley:2018fn] projections suggesting that climate change will push marine species towards the poles and deeper water [@Pinsky:2013ab] in search of their ecological niche [@Poloczanska:2016kk].
-Moreover, IPHC data[^IPHC] suggest that some of these shits are already happening.
+Moreover, IPHC data[^IPHC] suggest that some of these shifts are already happening.
 For example, since 2010, the distribution proportion of Pacific halibut has increased from 9% to 11% in region 2B, from 7.5% to 13% in region 2C, and from 12.3% to 13.5% in region 4CDE.
@@
 In the Gulf of Maine, future projections could be a response to a temperature gradient shift combined with geographic barriers as southern waters are deeper and warming slower than northern waters according to the ESMs (Figure \@ref(fig:ocFigureS22)).
-Moreover, Maine has seen its landings of yellowtail flounder increased at the expenses of southern states [@Pinsky:2012kq].
+Moreover, Maine has seen its landings of yellowtail flounder increase at the expenses of southern states [@Pinsky:2012kq].
 This could be influencing the US gain in MCP in the GoMa in relation to Canada as species shift their distribution from lower latitudes naturally reaching the US (lower) region first.
@@
 Thus, the commission has been asked to open the closed area for Pacific halibut fishing, under the premise that the expansion of the trawl fishery is likely reducing any conservation goal for juvenile Pacific halibut [@IPHC:2017CA].
-Although not assessed in this study, some trawling target species like Pacific cod (*Gadus macrocephalus*), flathead sole (*Hippoglossoides elassodon*), and Alaskan plaice (*Pleuronectes quadrituberculatus*) have already shift their distributions due to warming waters [@Stram:2009xc] and some are expected to continue shifting in similar direction than Pacific halibut [@Pinsky:2013ab].
+Although not assessed in this study, some trawling target species like Pacific cod (*Gadus macrocephalus*), flathead sole (*Hippoglossoides elassodon*), and Alaskan plaice (*Pleuronectes quadrituberculatus*) have already shifted their distributions due to warming waters [@Stram:2009xc] and some are expected to continue shifting in similar direction as Pacific halibut [@Pinsky:2013ab].
 The overlap of target species could be addressed by applying ecosystem-based management and dynamic management tools [@Hazen:2018fa] to manage these fisheries and reduce potential loss of sustainable harvest for both the halibut and the trawl fisheries.
@@
 
-Side payments have been previously used to address changes in species distribution, including cases caused by environmental forcings.
+Side payments have been previously used to address changes in species distribution, including cases caused by environmental forcing.
 In game theory, a side payment is received by a player as a compensation from the other player in a shared resource agreement, with the premise that cooperation will result in a better overall outcome [@Bjorndal:2012vd; @Sumaila:2013hv].
@@
 For instance, stock-share of yellowtail flounder under a high emission scenario will be larger for the US while Canada's gain of cod stock-share will be larger under a low emission scenario (Figure \@ref(fig:ocFigure5)).
-Applying previously describe strategies (e.g., quota swaps or EEZ-fishing rights) could increase the resilience of treaties by preventing members from leaving the agreement due to a shift in threat points, as happened in the Pacific salmon case [@Miller:2013iv].
+Applying previously described strategies (e.g., quota swaps or EEZ-fishing rights) could increase the resilience of treaties by preventing members from leaving the agreement due to a shift in threat points, as happened in the Pacific salmon case [@Miller:2013iv].
 
@@
 An ensemble of models is a way to present a more robust result that accounts for differences in the structural composition of each model [@Cheung:2016gv].
-In here I used three ESMs to project future changes in species maximum catch potential.
+In here, I used three ESMs to project future changes in species maximum catch potential.
 The levels of uncertainty related to the ESMs differ among case studies.

### 2020-12-14 Ecol/Manuscript_Draft.Rmd
standarized stocks and species

@@
 
-where *y* is year, *r* is region, *s* is grid, *n* is total number of grids in  the region, and $\hat{MCP}$ is the MCP of each species.
+where *y* is year, *r* is region, *s* is grid, *n* is total number of grids in  the region, and $\hat{MCP}$ is the MCP of each stock.
 In the case of the GoMa, region was defined as the $0.5^{\circ}$ x $0.5^{\circ}$ grid-cell within the specific NAFO divisional zones.
@@
 In addition, I borrowed the concept of “threat point” from game theory defined as the minimum payoff that a player is willing to receive in order to cooperate with other players [@Sumaila:2020tp].
-Thus, I estimated the change in the ($\Delta MCP$) (threat point) that each country (players) would have for each species (hereafter referred as stock-share ratio), for both the IPHC and the GoMa.
+Thus, I estimated the change in the ($\Delta MCP$) (threat point) that each country (players) would have for each stock (hereafter referred as stock-share ratio), for both the IPHC and the GoMa.
 The stock-share ratio can be seen as the proportion of the stock’s distribution within the study area that each country has.
-For this, I first modified equation \@ref(eq:ocone), to estimate the aggregated yearly mean MCP of each species per region.
+For this, I first modified equation \@ref(eq:ocone), to estimate the aggregated yearly mean MCP of each stock per region.
 I then averaged the results by the same previously motioned periods (present, mid and end of the $21^{st}$ century).
-Next, for each species I estimated the stock-share ratio  ($\alpha_s$) that each region had during each time period:
+Next, for each stock I estimated the stock-share ratio ($\alpha_s$) that each region had during each time period:
 
@@
 
-Where $\theta_{rt}$* is the species' aggregated $\hat{MCP}$ of each region at time period *t*, and $\delta_{ts}$ is the species' aggregated $\hat{MCP}$ of the whole specie's distribution within the study area at the same time period.
+Where $\theta_{rt}$* is the stock's aggregated $\hat{MCP}$ of each region at time period *t*, and $\delta_{ts}$ is the stock's aggregated $\hat{MCP}$ of the whole stock's distribution within the study area at the same time period.
 Finally, I estimated the percentage change in stock-share ratio substituting $X_{t_0}$ and $X_{t}$ by $\alpha_{t0}$ and $\alpha_t$, respectively in equation \@ref(eq:octwo).
@@
 
-### Projected change to species managed by the IPHC
+### Projected change to stocks managed by the IPHC
 
@@
 
-```{r ocFigure2, eval = T, echo = F, fig.cap= "Percentage change of MCP for species managed by the IPHC for mid 21st century (2041-2060) relative to present 2005-2014 under a A) high emission scenario and B) low emission scenario.
+```{r ocFigure2, eval = T, echo = F, fig.cap= "Percentage change of MCP for stocks managed by the IPHC for mid 21st century (2041-2060) relative to present 2005-2014 under a A) high emission scenario and B) low emission scenario.
 Labels marked with * represent regions where models do not agree in direction of change."}
@@
 
-### Projected change to species managed under the Gulf of Maine arrangement
+### Projected change to stocks managed under the Gulf of Maine arrangement
 
@@
 For yellowtail flounder, despite an overall reduction, some discrete areas are expected to increase with no particular pattern and high uncertainty, as ESMs in these regions do not agree in the direction of change (Figure \@ref(fig:ocFigureS23)).
-Despite the overall reduction in MCP for all three species in comparison to current values, there is a benefit of achieving a low emission scenario as reductions intensify under the high emission scenario.
+Despite the overall reduction in MCP for all three stocks in comparison to current values, there is a benefit of achieving a low emission scenario as reductions intensify under the high emission scenario.
 
@@
 
-Despite the expected decrease in MCP for the region, changes in the stock-share ratio of species within the Gulf of Maine show different outcomes dependent on the climate change scenario and species in question.
+Despite the expected decrease in MCP for the region, changes in the stock-share ratio of stocks within the Gulf of Maine show different outcomes dependent on the climate change scenario and stock in question.
 Following a high emission path will negatively affect mostly Canada’s share of yellowtail flounder and in less degree haddock, with an increase of cod share.
 Under the low emission scenario, haddock and cod share patterns intensify, while yellowtail flounder’s share approaches almost no change (Figure \@ref(fig:ocFigure5)).
-Such pattern is likely due to the combination of the bathymetry or the Gulf, the warming gradient, and the species distribution (see Discussion).
+Such pattern is likely due to the combination of the bathymetry or the Gulf, the warming gradient, and the stock's distribution (see Discussion).
 
@@
 
-The results of the present study suggest that climate change will alter the MCP of jointly managed transboundary fish stocks in North America consequently altering Canada’s and the US’s species’ stock-share ratio, regardless of the climate change scenario.
+The results of the present study suggest that climate change will alter the MCP of jointly managed transboundary fish stocks in North America consequently altering Canada’s and the US’s stock’s stock-share ratio, regardless of the climate change scenario.
 These results are aligned with regional [@Morley:2018fn] projections suggesting that climate change will push marine species towards the poles and deeper water [@Pinsky:2013ab] in search of their ecological niche [@Poloczanska:2016kk].
@@
 Geographic barriers [@Cheung:2015fm; @Kleisner:2016je], local temperature gradients [@Pinsky:2013ab], species interactions and human activities [@Serpetti:2017he] might change the rate and direction of species shifts.
-For the IPHC, geographic barriers might induce a westward increase of stock-share in IPHC regions where species can only migrate northward into the Arctic Ocean through the Bering Sea and Bering Strait [@Cheung:2015fm] (Figure \@ref(fig:ocFigure3)).
+For the IPHC, geographic barriers might induce a westward increase of stock-share in IPHC regions where the stock can only migrate northward into the Arctic Ocean through the Bering Sea and Bering Strait [@Cheung:2015fm] (Figure \@ref(fig:ocFigure3)).
 In the Gulf of Maine, future projections could be a response to a temperature gradient shift combined with geographic barriers as southern waters are deeper and warming slower than northern waters according to the ESMs (Figure \@ref(fig:ocFigureS22)).
 Moreover, Maine has seen its landings of yellowtail flounder increase at the expenses of southern states [@Pinsky:2012kq].
-This could be influencing the US gain in MCP in the GoMa in relation to Canada as species shift their distribution from lower latitudes naturally reaching the US (lower) region first.
+This could be influencing the US gain in MCP in the GoMa in relation to Canada as stocks shift their distribution from lower latitudes naturally reaching the US (lower) region first.
 As the effects of climate change endure, even with high mitigation, joint plans should prepare to face changes in the stock-share ratio of transboundary stocks along both coast of North America.
@@
 
-Side payments have been previously used to address changes in species distribution, including cases caused by environmental forcing.
+Side payments have been previously used to address changes in stock's distribution, including cases caused by environmental forcing.
 In game theory, a side payment is received by a player as a compensation from the other player in a shared resource agreement, with the premise that cooperation will result in a better overall outcome [@Bjorndal:2012vd; @Sumaila:2013hv].
@@
 The levels of uncertainty related to the ESMs differ among case studies.
-Overall, results for the Gulf of Maine agree with a reduction in MCP of all three species.
+Overall, results for the Gulf of Maine agree with a reduction in MCP of all three stocks.
 However, some discrete areas show a positive change for yellowtail flounder by mid $21^{st}$ century (Figure \@ref(fig:ocFigure3)), mainly driven by the GFDL model (Figure \@ref(fig:ocFigureS23)).
@@
 
-```{r FigureS11, eval = F, echo = F, fig.cap = "Percentage change of MCP for species managed by the IPHC for end-century (2081–2100) relative to 2005–2014 under a A) high emission scenario and B) low emission scenario.
+```{r FigureS11, eval = F, echo = F, fig.cap = "Percentage change of MCP for stocks managed by the IPHC for end-century (2081–2100) relative to 2005–2014 under a A) high emission scenario and B) low emission scenario.
 Labels marked with * represent regions where models do not agree in direction of change."}

### 2020-12-15 Ecol/Manuscript_Draft.Rmd
William final comments

@@
  "knitr",
- # "kableExtra",
+ "kableExtra",
  "data.table",
@@
 For this specific case, I considered Alaska as a separate entity, the US contiguous states as a second one (Washington, Oregon and California), and lastly British Columbia (Canada).
-For the GoMa I used the Northwest Atlantic Fisheries Organization's (NAFO) divisions 5Y, 5Ze, and 4X[^NAFO] within latitudes 46.2°N and 41.5°S, and longitudes -72°W and -64°E (Figure \@ref(fig:ocFigure1)).
+For the GoMa I used the Northwest Atlantic Fisheries Organization's (NAFO)[^NAFO] divisions 5Y, 5Ze, and 4X within latitudes 46.2°N and 41.5°S, and longitudes -72°W and -64°E (Figure \@ref(fig:ocFigure1)).
 Is worth mention that, while NAFO's divisional zones were used in this study for domestic management, NAFO does not manage fisheries within the EEZs of Canada and the United States.
@@
 table_1 %>% 
-  kable(caption = "Historic quota allocation suggested for Atlantic cod, haddock and yellowtail flounder in the Gulf of Maine")
-  # kable("latex",
-  #       booktabs = T,
-  #       caption = "Historic quota allocation suggested for Atlantic cod, haddock and yellowtail flounder in the Gulf of Maine "
-  # ) %>% 
-  # kable_styling(full_width = F,
-  #               position = "center") %>%
-  # add_header_above(c(" ", "Atlantic cod" = 2, "Haddock" = 2, "Yellowtail flounder" = 2)
-  # ) %>% 
-  # footnote(general = c("* Average from 2006 to 2009, before the implementation of the weighted method",
-  #                      "' Since the implementation of the weighted method",
-  #                      "'' Standard deviation of the wiighted average",
-  #                      "^ TRAC (2015abc)",
-  #                      "† TRAC (2018abc)",
-  #                      "‡ Lake (2019)"
-  # )
-  # )
+  # kable(caption = "Historic quota allocation suggested for Atlantic cod, haddock and yellowtail flounder in the Gulf of Maine")
+  kable("latex",
+        booktabs = T,
+        caption = "Historic quota allocation suggested for Atlantic cod, haddock and yellowtail flounder in the Gulf of Maine "
+  ) %>%
+  kable_styling(full_width = F,
+                position = "center") %>%
+  add_header_above(c(" ", "Atlantic cod" = 2, "Haddock" = 2, "Yellowtail flounder" = 2)
+  ) %>%
+  footnote(general = c("* Average from 2006 to 2009, before the implementation of the weighted method",
+                       "' Since the implementation of the weighted method",
+                       "'' Standard deviation of the wiighted average",
+                       "^ TRAC (2015abc)",
+                       "† TRAC (2018abc)",
+                       "‡ Lake (2019)"
+  )
+  )
 
 ```
+
+\clearpage
 
@@
 Future climate change will depend on the path society as a whole will take, and thus I rely on scenario planning to account for the uncertainty build in future decision making [@vanVuuren:2011ef].
-In our results, the "winners and losers" of climate change, and the intensity of the change, will be scenario dependent.
+In these results, the "winners and losers" of climate change, and the intensity of the change, will be scenario dependent.
 For instance, stock-share of yellowtail flounder under a high emission scenario will be larger for the US while Canada's gain of cod stock-share will be larger under a low emission scenario (Figure \@ref(fig:ocFigure5)).
@@
 
-Models are attempts to represent reality (in our case a future reality) based on observational data, previously established theory, and future scenarios, and are thus, subjected to different degrees of uncertainty [@Payne:2016gn].
+Models are attempts to represent reality (in this case a future reality) based on observational data, previously established theory, and future scenarios, and are thus, subjected to different degrees of uncertainty [@Payne:2016gn].
 An ensemble of models is a way to present a more robust result that accounts for differences in the structural composition of each model [@Cheung:2016gv].
@@
 Regarding the DBEM, its structural uncertainty has been previously tested for agreement against commonly used species distribution algorithms such as Maxent [@Phillips:2006ff] and AquaMaps [@Kaschner:2011hi; @Ready:2010wr] resulting in no qualitative differences in trends between algorithms [@Cheung:2016jd].
-Finally, is worth mentioning that future changes to species distributions could be influenced by factors not captured by our model such as interactions between species [@Pecl:2017hu], adaptation of species to environmental changes, and anthropogenic factors [@Serpetti:2017he].
-However, these factors are expected to increase the rate of range-shifting of the species making our results conservative [@Cheung:2010dt; @Serpetti:2017he].
+Finally, is worth mentioning that future changes to species distributions could be influenced by factors not captured by my model such as interactions between species [@Pecl:2017hu], adaptation of species to environmental changes, and anthropogenic factors [@Serpetti:2017he].
+However, these factors are expected to increase the rate of range-shifting of the species making my results conservative [@Cheung:2010dt; @Serpetti:2017he].
 
@@
 
-```{r FigureS21, eval = F, echo = F, fig.cap = "Projected environmental variables under climate change from 2010 to 2010 for Arctic regions of the IPHC (Top:4D, Bottom, 4E).
+```{r xFigureS21, eval = F, echo = F, fig.cap = "Projected environmental variables under climate change from 2010 to 2010 for Arctic regions of the IPHC (Top:4D, Bottom, 4E).
 The solid line represents the average of all three ESMs and the shaded area represents the model’s uncertainty (s.d.)."}

### 2020-12-15 Ecol/Supplements.Rmd
William final comments

@@
 
-```{r ocFigureS11, eval = T, echo = F, fig.cap = "Percentage change of MCP for species managed by the IPHC for end-century (2081–2100) relative to 2005–2014 under a A) high emission scenario and B) low emission scenario.
+```{r ocFigureS11, eval = T, echo = F, fig.cap = "Percentage change of MCP for stocks managed by the IPHC for end-century (2081–2100) relative to 2005–2014 under a A) high emission scenario and B) low emission scenario.
 Labels marked with * represent regions where models do not agree in direction of change."}

### 2021-01-28 Ecol/Manuscript_Draft.Rmd
final thesis changes

@@
 Catches of shared stocks like tunas, have significantly increased in some regions such as the subtropical Atlantic and western Pacific Oceans and are projected to continue [@MonllorHurtado:2017cm; @ErauskinExtramiana:2019fw].
-Multiple shared species in North America have been observed to shift in distribution following changes in optimal conditions such as sockeye salmon (*Oncorhynchus nerka*) [@McDaniels:2010vn], Atlantic cod [@Pershing:2015gq], and flounders [@Pinsky:2012kq].
+Multiple shared species in North America have been observed to shift in distribution following changes in optimal conditions such as sockeye salmon (*Oncorhynchus nerka*) [@McDaniels:2010vn; @Miller:2013iv; @Song:2017va], Atlantic cod [@Pershing:2015gq], and flounders [@Pinsky:2012kq].
 Moreover, these shifts are projected to continue towards the end of the $21^{st}$ century [@Cheung:2018hz].
@@
 
-## Materials and Methods
+## Materials and methods
 
@@
 ```{r ocFigure2, eval = T, echo = F, fig.cap= "Percentage change of MCP for stocks managed by the IPHC for mid 21st century (2041-2060) relative to present 2005-2014 under a A) high emission scenario and B) low emission scenario.
-Labels marked with * represent regions where models do not agree in direction of change."}
+Labels marked with * represent regions where models do not agree in direction of change.", fig.scap="Percentage change of MCP for stocks managed by the IPHC", out.extra=''}
 
@@
 ```{r ocFigure3, eval = T, echo = F, fig.cap="Percentage change of stock-share ratio for IPHC under A) high emission scenario and B) low emission scenario for mid 21st century (2041-2060) relative to present 2005-2014.
-Values represent the mean of 3 ESM; error bars represent \u00B1 sd."}
+Values represent the mean of 3 ESM; error bars represent \u00B1 sd.", fig.scap="Percentage change of stock-share ratio for IPHC", out.extra=''}
 
@@
 
-```{r ocFigure4, eval = T, echo = F, fig.cap= "Percentage change of MCP in the Gulf of Maine under, A) high emission scenario; and B) low emission for mid-century (2041-2060) relative to present (2005-2014).
-Points represent regions where models do not agree in direction of change."}
+```{r ocFigure4, eval = T, echo = F, fig.cap= "Percentage change of MCP in the Gulf of Maine under, A) high emission scenario; and B) low emission for the mid 21st century (2041-2060) relative to present (2005-2014).
+Points represent regions where models do not agree in direction of change.", fig.scap="Percentage change of MCP in the Gulf of Maine", out.extra=''}
 
@@
 ```{r ocFigure5, eval = T, echo = F, fig.cap="Changes in MCP stock-share ratio for Gulf of Maine under (A) high emission; and (B) low emission scenarios for mid 21st century (2041-2060) relative to present (2005-2014).
-Values represent the mean of 3 ESM; error bars represent \u00B1 sd."}
+Values represent the mean of 3 ESM; error bars represent \u00B1 sd.", fig.scap="Changes in MCP stock-share ratio for Gulf of Maine", out.extra=''}
 
@@
 
-```{r FigureS11, eval = F, echo = F, fig.cap = "Percentage change of MCP for stocks managed by the IPHC for end-century (2081–2100) relative to 2005–2014 under a A) high emission scenario and B) low emission scenario.
-Labels marked with * represent regions where models do not agree in direction of change."}
+```{r FigureS11, eval = F, echo = F, fig.cap = "Percentage change of MCP for stocks managed by the IPHC for for the end of the 21st century (2081–2100) relative to 2005–2014 under a A) high emission scenario and B) low emission scenario.
+Labels marked with * represent regions where models do not agree in direction of change.", fig.scap="Percentage change of MCP for stocks managed by the IPHC for the end of the 21st century (2081–2100) relative to 2005–2014", out.extra=''}
 

### 2021-01-28 Ecol/Supplements.Rmd
final thesis changes

@@
 ```{r ocFigureS11, eval = T, echo = F, fig.cap = "Percentage change of MCP for stocks managed by the IPHC for end-century (2081–2100) relative to 2005–2014 under a A) high emission scenario and B) low emission scenario.
-Labels marked with * represent regions where models do not agree in direction of change."}
+Labels marked with * represent regions where models do not agree in direction of change.", fig.scap="Percentage change of MCP for stocks managed by the IPHC for end-century (2081–2100) relative to 2005–2014", out.extra=''}
 
@@
 
-```{r ocFigureS12, eval = T, echo = F, fig.cap = "Percentage change of MCP in the Gulf of Maine under (RCP 8.5) high emission scenario and (RCP 2.6) low emission for end-century (2080–2100) referent to present (2005– 2014).
+```{r ocFigureS12, eval = T, echo = F, fig.cap = "Percentage change of MCP in the Gulf of Maine under (RCP 8.5) high emission scenario and (RCP 2.6) low emission for the end of the 21stcentury (2080–2100) relative to present (2005– 2014).
 Values represent the mean of 3 ESM.
-Points represent regions where ESMs do not agree in direction of change"}
+Points represent regions where ESMs do not agree in direction of change", fig.scap="Percentage change of MCP in the Gulf of Maine for the end of the 21st century (2080–2100) relative to present (2005– 2014).", out.extra=''}
 
@@
 ```{r ocFigureS21, eval = T, echo = F, fig.cap = "Projected environmental variables under climate change from 2010 to 2010 for Arctic regions of the IPHC (Top:4D, Bottom, 4E).
-The solid line represents the average of all three ESMs and the shaded area represents the model’s uncertainty (s.d.)."}
+The solid line represents the average of all three ESMs and the shaded area represents the model’s uncertainty (s.d.).", fig.scap="Projected environmental variables under climate change from 2010 to 2010 for Arctic regions of the IPHC", out.extra=''}
 
@@
 Everything deeper than 1000 meters is colored in green.
-B) Percentage change of bottom temperature relative to the present showing more intense warming in northern regions, especially under a high emission climate change scenario."}
+B) Percentage change of bottom temperature relative to the present showing more intense warming in northern regions, especially under a high emission climate change scenario.", fig.scap="Depth profile of the Gulf of Maine", out.extra=''}
 
@@
 Results for the three global circulation models (GFDL, IPSL, MPIS) used in the current study and two climate change scenarios (Top: High emission – RCP 8.5, Bottom: Low Emission – RCP 2.6).
-Grid-cells marked in yellow represent discrete areas where average MCP is projected to increase by mid-century."}
+Grid-cells marked in yellow represent discrete areas where average MCP is projected to increase by mid-century.", fig.scap="Changes in maximum catch potential of yellowtail flounder (*Limanda ferruginea*) within the study area by mid-century relative to present time.", out.extra=''}
 
@@
 Colors represents the different ESM used in the study.
-Solid line represents a high emission scenario (RCP 8.5) and dashed line represents a low emission scenario (RCP 2.6)"}
+Solid line represents a high emission scenario (RCP 8.5) and dashed line represents a low emission scenario (RCP 2.6)", fig.scap="Projected MCP change relative to present (2005-2014) for each IPHC regulatory area.", out.extra=''}
 

### 2021-03-11 Ecol/Manuscript_Draft.Rmd
Modifications in response to scott's comments

@@
 A perpetuation of this trend with no mitigation policy could jeopardize the arrangement as Canada's quota reduction could disincentive cooperation [@Sumaila:2020tp].
+**Previous international action suggests that quota allocation should not only be centered in highly valuable fisheries (i.e., in terms of catch or economic value).
+For example, Atlantic mackerel (*Scomber scombrus*) represents a small proportion of the total catch of the EU, Norway, and the Faroe Islands (Denmark) who share the stock.
+Yet, they have all been in dispute with Iceland over quota allocation and rights since the stock shifted in 2017 reaching Icelandic waters [@Spijkers:2017ij, Chapter 2].
+Similar, Peru has recently signed an agreement with Chile to manage the southern stock of Anchoveta (*Engraulis ringens*) which is substantially smaller than the northern Peruvian stock [@Cashion:2018cg; @UNDP:2016wp].
+These examples suggest that a future change in shared proportion of even a "small" fishery, or fraction of, could still require management adaptations in order to reduce international conflict and sustain the stock.
+Naturally, no strategy to mitigate climate change impacts will be beneficial if a fishery is exploited to extinction, however, reformulation of fisheries management could actually offset many of the negative effects of climate change [@Gaines:2018sg].
+Thus, the impacts and solutions presented here need to be align with sustainable fisheries management.**
 

### 2021-03-19 Ecol/Manuscript_Draft.Rmd
grammar fix

@@
 
-In 1982, the United Nations Law of the Sea Convention (UNCLOS) formalized the concept of exclusive economic zones (EEZs) creating the concept that we know today as shared stocks [@UnitedNations:1986tl], i.e.
-stocks that migrate between countries EEZs (known as transboundary stocks) or between EEZs and the high seas (also called straddling stocks) [@Song:2017iua].
+In 1982, the United Nations Law of the Sea Convention (UNCLOS) formalized the concept of exclusive economic zones (EEZs) creating the concept that we know today as shared stocks [@UnitedNations:1986tl], i.e., stocks that migrate between countries EEZs (known as transboundary stocks) or between EEZs and the high seas (also called straddling stocks) [@Song:2017iua].
 Today, an estimated 347 [@Teh:2015gd] to 633 (Chapter 2) fish stocks have distributions that cross national borders, some of them jointly managed by two or more countries.
@@
 Since the definition of shared stocks, game theory has been one of the most common approaches used to analyze the management of these type of stocks.
-However, shared stocks' management can be convoluted due to the participation of several fishing “players”, different countries and sometimes jurisdictions within a country, the migration patterns of the stock, and their abundance fluctuation within space and time [@Munro:2002uf, Engler and Saunders *in press*].
-In addition, international treaties might not be prepared to address the effects that climate change will bring to shared fish stocks (Engler and Saunders *in press*, Koubrak and VanderZwaag, *in press*).
-
+However, shared stocks' management can be convoluted due to the participation of several fishing “players”, different countries and sometimes jurisdictions within a country, the migration patterns of the stock, and their abundance fluctuation within space and time [@Munro:2002uf; @Engler2020].
+In addition, international treaties might not be prepared to address the effects that climate change will bring to shared fish stocks [@Engler2020; @Kubrack2020]
 <!-- ##### Climate Change and Transboundary Fisheries -->
@@
 Catches of shared stocks like tunas, have significantly increased in some regions such as the subtropical Atlantic and western Pacific Oceans and are projected to continue [@MonllorHurtado:2017cm; @ErauskinExtramiana:2019fw].
-Multiple shared species in North America have been observed to shift in distribution following changes in optimal conditions such as sockeye salmon (*Oncorhynchus nerka*) [@McDaniels:2010vn; @Miller:2013iv; @Song:2017va], Atlantic cod [@Pershing:2015gq], and flounders [@Pinsky:2012kq].
+Multiple shared species in North America have been observed to shift in distribution following, in part, changes in optimal conditions such as sockeye salmon (*Oncorhynchus nerka*) [@McDaniels:2010vn; @Miller:2013iv; @Song:2017va], Atlantic cod [@Pershing:2015gq], and flounders [@Pinsky:2012kq].
 Moreover, these shifts are projected to continue towards the end of the $21^{st}$ century [@Cheung:2018hz].
@@
 Therefore, the main objective of this article is to assess the level of exposure that bi-lateral transboundary fisheries treaties between Canada and the US have to climate change through shifts in stock distributions.
-Specifically, I rely on a species distribution model and scenario planning to project the changes in the distribution of selected fish stocks jointly managed by Canada and the United States focusing on two case studies (the International Pacific Halibut Commission and a fisheries arrangement for the Gulf of Maine) Finally, I explore similar situations around the world and identify opportunities to improve the adaptability of transboundary stocks management to climate change in North America.
+Specifically, I rely on a species distribution model and scenario planning to project the changes in the distribution of selected fish stocks jointly managed by Canada and the US focusing on two case studies (the International Pacific Halibut Commission and a fisheries arrangement for the Gulf of Maine) Finally, I explore similar situations around the world and identify opportunities to improve the adaptability of transboundary stocks management to climate change in North America.
 Despite an overall expectation of species following a poleward shift, important geographic constraints (e.g., Gulf of Alaska representing a latitudinal block) [@Kleisner:2016je], geo-political features (e.g., the localization of Alaska in reference to Canada and the contiguous states), and management rules (e.g., quota allocations, spatial management rules) may play an important role in the redistribution of benefits.
@@
 
-The current study used the International Pacific Halibut Commission (IPHC) and the Gulf of Maine arrangement (hereafter referred as GoMa) as case studies to discuss the implications that climate change could have in the management of transboundary stocks.
+In this chapter, I used the International Pacific Halibut Commission (IPHC) and the Gulf of Maine arrangement (hereafter referred as GoMa) as case studies to discuss the implications that climate change could have in the management of transboundary stocks.
 For the IPHC, I used the most updated spatial regulatory data along its 12 regulatory areas [@IPHCSecreatriat:2017uz; @IPHC:2019wt].
 For this specific case, I considered Alaska as a separate entity, the US contiguous states as a second one (Washington, Oregon and California), and lastly British Columbia (Canada).
-For the GoMa I used the Northwest Atlantic Fisheries Organization's (NAFO)[^NAFO] divisions 5Y, 5Ze, and 4X within latitudes 46.2°N and 41.5°S, and longitudes -72°W and -64°E (Figure \@ref(fig:ocFigure1)).
-Is worth mention that, while NAFO's divisional zones were used in this study for domestic management, NAFO does not manage fisheries within the EEZs of Canada and the United States.
+For the GoMa, I used the Northwest Atlantic Fisheries Organization's (NAFO)[^NAFO] divisions 5Y, 5Ze, and 4X within latitudes 46.2°N and 41.5°S, and longitudes -72°W and -64°E (Figure \@ref(fig:ocFigure1)).
+It is worth mention that, while NAFO's divisional zones were used in this study for domestic management, NAFO does not manage fisheries within the EEZs of Canada and the United States.
 Fisheries data for the projections was gathered from the Sea Around Us from 1951 to 2014 [@Zeller2016].
@@
 
-The IPHC was established in 1923 by Canada and the United States to oversee the management of Pacific halibut (*Hippoglossus stenolepis*) [@IPHC:2014tz].
+The IPHC was established in 1923 by Canada and the US to oversee the management of Pacific halibut (*Hippoglossus stenolepis*) [@IPHC:2014tz].
 There are 12 regulatory areas from which 3AB holds 51.2% of the stock, followed by regions 2ABC and 4ACDE with 23.1% and 20.4%, respectively, and lastly region 4B with only 5.2% of the stock distribution [@IPHC:2018vz].
@@
 
-The results of the present study suggest that climate change will alter the MCP of jointly managed transboundary fish stocks in North America consequently altering Canada’s and the US’s stock’s stock-share ratio, regardless of the climate change scenario.
+The results of the present chapter suggest that climate change will alter the MCP of jointly managed transboundary fish stocks in North America consequently altering Canada’s and the US’s stock’s stock-share ratio, regardless of the climate change scenario.
 These results are aligned with regional [@Morley:2018fn] projections suggesting that climate change will push marine species towards the poles and deeper water [@Pinsky:2013ab] in search of their ecological niche [@Poloczanska:2016kk].
@@
 More specific, side payments, dynamic management, and interchangeable quotas were identified as potential solutions for North American region.
-While not directly addressed in this study, socio-economic impacts of shifting transboundary stocks could add an extra layer of complexity to the problem.
+While not directly addressed in this chapter, socio-economic impacts of shifting transboundary stocks could add an extra layer of complexity to the problem.
 Addressing shifts in stocks distribution sooner rather than latter could avert the so called “fish wars”, improve sustainability of jointly managed stocks, and secure the livelihood of thousands of families that depend on stocks that move freely between national jurisdictions.

### 2021-03-22 Ecol/Manuscript_Draft.Rmd
William comments included

@@
 Since the definition of shared stocks, game theory has been one of the most common approaches used to analyze the management of these type of stocks.
-However, shared stocks' management can be convoluted due to the participation of several fishing “players”, different countries and sometimes jurisdictions within a country, the migration patterns of the stock, and their abundance fluctuation within space and time [@Munro:2002uf; @Engler2020].
-In addition, international treaties might not be prepared to address the effects that climate change will bring to shared fish stocks [@Engler2020; @Kubrack2020]
+However, shared stocks' management can be convoluted due to the participation of several fishing “players”, different countries and sometimes jurisdictions within a country, the migration patterns of the stock, and their abundance fluctuation within space and time [@Munro:2002uf; @Engler:2020bg].
+In addition, international treaties might not be prepared to address the effects that climate change will bring to shared fish stocks [@Engler:2020bg; @Koubrak:2020hw]
 <!-- ##### Climate Change and Transboundary Fisheries -->
@@
 A perpetuation of this trend with no mitigation policy could jeopardize the arrangement as Canada's quota reduction could disincentive cooperation [@Sumaila:2020tp].
-**Previous international action suggests that quota allocation should not only be centered in highly valuable fisheries (i.e., in terms of catch or economic value).
+Previous international action suggests that shifts in transboundary fish stocks distributions for fisheries with relatively low catch or economic value could lead to international disputes in quota allocation.
 For example, Atlantic mackerel (*Scomber scombrus*) represents a small proportion of the total catch of the EU, Norway, and the Faroe Islands (Denmark) who share the stock.
 Yet, they have all been in dispute with Iceland over quota allocation and rights since the stock shifted in 2017 reaching Icelandic waters [@Spijkers:2017ij, Chapter 2].
-Similar, Peru has recently signed an agreement with Chile to manage the southern stock of Anchoveta (*Engraulis ringens*) which is substantially smaller than the northern Peruvian stock [@Cashion:2018cg; @UNDP:2016wp].
-These examples suggest that a future change in shared proportion of even a "small" fishery, or fraction of, could still require management adaptations in order to reduce international conflict and sustain the stock.
+Similarly, Peru has recently signed an agreement with Chile to manage the southern stock of Anchoveta (*Engraulis ringens*) which is substantially smaller than the northern Peruvian stock [@Cashion:2018cg; @UNDP:2016wp].
+These examples highlight the need for adaptation of transboundary fisheries management to climate change for all a broad range of species in order to reduce the risk of international conflict and unsustainable fisheries development.
 Naturally, no strategy to mitigate climate change impacts will be beneficial if a fishery is exploited to extinction, however, reformulation of fisheries management could actually offset many of the negative effects of climate change [@Gaines:2018sg].
-Thus, the impacts and solutions presented here need to be align with sustainable fisheries management.**
+Thus, the impacts and solutions presented here need to be align with sustainable fisheries management.
 
